### 2020-02-21 main.tex
Initial Overleaf Import

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
% flush right qed marks, e.g. at end of proof
\smartqed

\usepackage[lofdepth,lotdepth]{subfig}
% \usepackage{graphicx}
%
\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{epstopdf}
\usepackage{mathrsfs} % para formato de letra
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{array}
\usepackage{tabularx}
\usepackage{supertabular}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{color}
\usepackage{makeidx}
\usepackage{xstring}
\usepackage{setspace}
\usepackage{epsfig}

\usepackage{pgf}
% \usepgfplotslibrary{external} 
% \tikzexternalize

%\usepackage{subfigure}
\usepackage{preview}
% Packages to write pseudo-algorithms %
\usepackage{algorithm}
\usepackage{algorithmic}

% Tikz
\usepackage{stanli}
\usepackage[ugly]{units}

%\usepackage{latexsym}
% etc.
%

% Matrix and vector nodes
\newcommand{\Matrix}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\Vector}[1]{
  \ensuremath{\mathbf{{#1}}}
}

% Divergence
\newcommand{\Div}[1]{
  \ensuremath{\nabla \cdot {#1}}
}
% Gradient
\newcommand{\Grad}[1]{
  \ensuremath{\nabla{#1}}
}

% Partial derivative
\newcommand{\Deriv}[3][]{
  \ensuremath{\frac{\partial^{#1}{#2}}{ \partial {#3}^{#1} }}
}

% Integral
\newcommand{\Integral}[2]{
  \IfStrEqCase{#1}{
    {1}{\ensuremath{\int_{\Gamma}{#2}\ d\Gamma}}
    {2}{\ensuremath{\int_{\Sigma}{#2}\ d\Sigma}}
    {3}{\ensuremath{\int_{\Omega}{#2}\ d\Omega}}
  }
}

%
% Insert the name of "your journal" with
\journalname{Computational Particle Mechanics}
%
\begin{document}

\title{Suitability of the local-maximum entropy approximation under
  the Material Point Method framework for dynamic problems. \thanks{Funding: This
    study was funded by Agustín de Betancourt Foundation (grant number
    262390106114).}
}
% \subtitle{}

\titlerunning{Suitability of the LME approximation under
  the MPM framework for dynamic problems.}        % if too long for running head

\author{Miguel Molinos \and
  Pedro Navas \and
  Manuel Pastor \and
  Miguel Martín Stickle
}

%\authorrunning{Short form of author list} % if too long for running head

% \institute{Miguel Molinos \at
%   E.T.S de Ingenieros de Caminos, Canales y Puertos. \\
%   Universidad Politéctnica de Madrid, 28040 Madrid, Spain \\
%   \email{m.molinos@alumnos.upm.es}
%   % \emph{Present address:} of F. Author  %  if needed
%   \and
%   Pedro Navas 
%   \and
%   Manuel Pastor
%   \and
%   Miguel Martín Stickle
% }
% \institute{Miguel Molinos, Pedro Navas and Manuel Pastor \at E.T.S
%   de Ingenieros de Caminos, Canales y Puertos, Universidad Politéctnica de Madrid, 28040 Madrid, Spain, \; \email{m.molinos@outlook.es, pedro.navas@upm.es, manuel.pastor@upm.es}
% }

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle
\begin{abstract}
  This document is devoted to describe the suitability of the Local
  \textit{maximum-entropy} (LME) meshfree approximation technique under the framework of the
  Material Point Method for dynamic problems. 
  \keywords{LME \and MPM \and Dynamic problems}
  % \PACS{PACS code1 \and PACS code2 \and more}
  % \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
Since the proposal of the Material Point Method (\textbf{MPM}) by Sulsky {\it
  et al.} (1994)\cite{Sulsky1994}, as a generalization of
a particle-in-cell method \cite{Harlow1956} and a fluid implicit
particle (FLIP) method \cite{Brackbill1986}, MPM has been used to
simulate dynamic problems. However, in the simulations made with the
originalMPM, there are numerical noises \cite{Tran2019e} when it is faced to solve
classic dynamic benchmarks like the one proposed by Dyka \& Ingel
(1995)\cite{Dyka1995}.

The aim of this paper is to mitigate this spurious oscillations by the
employ of the maximum-entropy (or local \textit{max-ent}) shape
function under the MPM framework. First introduced by
\cite{Arroyo2006}, it belongs to the class of convex 
approximation schemes and provides a seamless transition between
finite elements (\textbf{FE}) and mesh-free interpolations. The
approximation scheme is based on a compromise between minimizing the
width of the shape function support and maximizing the information
entropy of the approximation. The local \textit{max-ent} approximation
may be regarded as a regularization, or \textit{thermalization}, of
Delaunay triangulation which effectively resolves the degenerate cases
resulting from the lack of uniqueness of the triangulation. Local
\textit{max-ent} basis functions possess many desirable properties for
meshfree algorithms. First of all, they are entirely defined by the
nodal set and the domain of analysis. They are also non-negative, satisfy the partition of unity
property, and provide an exact approximation for affine functions \cite{Arroyo2006}.

This approximation scheme has been proof to have a good performance
under the dynamic regime by other researchers like Navas {\it et al.}
(2018)\cite{Navas2018a} and Li {\it et al.} (2012)\cite{Li2012} for
Optimal Transportation Meshfree (\textbf{OTM}) method.

a comparison between both methods employing \textit{max-ent}  shape
function is performed in this paper

as well a parametric study for the $\gamma$ parameter

finally, conclusions and future research topics are exposed

\section{Overview of the MPM}
\label{sec:mpm-overview}
In this section, we provide an overview of the standard explicit MPM
algorithm as presented by \cite{Sulsky1994}. The method has three main
steps: a variational recovery process to project particle data to the
nodes of the grid, a Eulerian step where balance of momentum is
compute by solving internal and external forces in the nodes, and
finally the advection of the Lagrangian particles. We will first give
a introduction to the governing equations and then follow by an
algorithmic description of the process.

\subsection{Derivation of the MPM}
\label{sec:derivation-mpm}
In the MPM approach a continuum is considered. The continuum behaviour
can be described by a set of governing equations which are the balance
of momentum equation ($\rho \vect{a} = \Div{\tens{\sigma}} + \rho
\vect{b}$), the compatibility equation ($\dot{\tens{\varepsilon}} =
\Grad{\vect{v}}$), the constitutive equation ($\dot{\tens{\sigma}} =
\tens{D} \colon \dot{\tens{\varepsilon}}$), and the balance of mass equation
($\frac{D \rho}{D t} = \dot{\rho} + \rho \Grad{\vect{v}}$). The balance of momentum can be
formulated in weak form by introducing an arbitrary test function $\vec{\psi}$, yielding
\begin{equation}
  \label{eq:BalanceMomentum_wf}
  \Integral{3}{\rho\ \Deriv{\vec{v}}{t}\ \vec{\psi}} = -
  \Integral{3}{\tens{\sigma} \colon \Grad{\vec{\psi}}} +
  \Integral{2}{\vec{t}\ \vec{\psi}} + \Integral{3}{
  \rho\ \vec{b}\ \vec{\psi}}.
\end{equation}\\

In order to arrive to a finite set of equations, the continuum domain
$\Omega$ is discretized with a finite sum of particles (material points), each one 
represent a part of the domain $\Omega_p$ with $p = 1,2\ldots ,N_p$
where $N_p$ is the number of particles. The index $p$ is
used for the particles, while the index $I$ is reserved in this
notation for denoting grid nodes. The material point $\vec{x}_p$ is
defined at the centroid of $\Omega_p$. Further, a computational grid
is formed of a finite set of grid points with coordinates $\vec{x}_I\
, I = 1,2\ldots ,N_n$, where $N_n$ is the number of grid nodes. Each material point is assigned with initial values of position,
velocity, mass, volume and stress denoted by $\vec{x}_p$,  $\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$. The problem is then integrated using a discrete number of time
steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
is the total number of time steps.  So employing the definition of the
material integral, individual terms of \eqref{eq:BalanceMomentum_wf}
are solved as follows. 
\begin{itemize}
\item Acceleration forces :
\begin{equation}
    \label{eq:particle_acceleration_forces}
    \Integral{3}{\rho\ \vec{a}\ \vec{\psi}} =& \sum^{N_p}_{p}
   \dot{\vec{v}}_{p}\ \vec{\psi}_{p}\ m_p.
  \end{equation}\\
\item Internal forces :
  \begin{equation}
    \label{eq:particle_internal_forces}
    \Integral{3}{\tens{\sigma}\ \colon \Grad{\vec{\psi}}} = \sum^{N_p}_{p}
   \tens{\sigma}_{p}\ \Grad{\tens{\psi}_{p}}\ V_p.
  \end{equation}\\
\item Body forces :
\begin{equation}
  \label{eq:particle_body_forces}
  \Integral{3}{\rho\ \vec{b}\ \vec{\psi} } = \sum^{N_p}_{p}
  \vec{b}_{p}\ \vec{\psi}_{p}\ m_p.
\end{equation}\\
\item Loads :
\begin{equation}
  \begin{aligned}
    \label{eq:particle_load_forces}
    \Integral{2}{\vec{t}\ \vec{\psi}} = \Integral{2}{\rho\
      \vec{t}^s\ \vec{\psi}} = \sum^{N_p}_{p} \vec{t}^s_{p}\ \vec{\psi}_{p}\ h^{-1}\ m_p ,
  \end{aligned} 
\end{equation}
\end{itemize}
where $h$ is the thickness of the continuum in a 2D case. Introducing \eqref{eq:particle_acceleration_forces},
\eqref{eq:particle_internal_forces}, \eqref{eq:particle_body_forces},
and \eqref{eq:particle_load_forces} in \eqref{eq:BalanceMomentum_wf}
we reach to the particle balance of forces of the continuum,
\begin{equation}
  \label{eq:particle_balance_forces2}
  \sum^{N_p}_{p}\vec{\psi}_{p}\ m_p\ \dot{\vec{v}}_{p} = \sum^{N_p}_{p}
  \vec{\psi}_{p}\ m_p\ \vec{b}_{p} + \sum^{N_p}_{p}
  \vec{\psi}_{p}\ m_p\ h^{-1}\ \bar{\vec{t}}^s_{p} -
  \sum^{N_p}_{p} \Grad{\vec{\psi}_{p}}\ \frac{m_p}{\rho_p}\
  \tens{\sigma}_{p}.
\end{equation}\\

Approximating the virtual displacement of the particle $\vec{\psi}_{p}$
using a suitable approximation scheme we get \eqref{eq:VirtualDisplacementParticle}.
\begin{equation}
  \label{eq:VirtualDisplacementParticle}
  \vec{\psi}_{p} = N_{Ip}\cdot \vect{1} = N_{Ip},
\end{equation}
where $N_{Ip} = N_I(\vec{x}_p)$ it is the nodal value of the shape
function evaluated in the material point coordinates denoted by $\vec{x}_p$. Substituting \eqref{eq:VirtualDisplacementParticle} in
\eqref{eq:particle_balance_forces2} we get :
\begin{equation}
  \label{eq:particle_balance_forces3}
  \dot{\vec{p}}_{I}= \tens{m}_{IJ}\dot{\vec{v}}_{J} = \vec{f}_{I}^{int} + \vec{f}_{I}^{ext},
\end{equation}
where $\dot{\vec{p}}_{I}$ is the rate of momentum at grid node $I$, the nodal mass matrix $\tens{m}_{IJ}$ is,
\begin{equation}
  \label{eq:particle_nod_mass}
  \tens{m}_{IJ} =
  \sum^{Np}_{p} N_{Ip} m_p N_{Jp},
\end{equation}
and internal and external forces are computed as follows,
\begin{equation}
  \label{eq:nodal_internal_forces}
  \vec{f}_{I}^{int} = - \sum^{N_p}_{p} \Grad{N_{Ip}}
  \tens{\sigma}_{p} \frac{m_p}{\rho_p}
\end{equation}
\begin{equation}
  \label{eq:nodal_external_forces}
  \vec{f}_{I}^{ext} = \sum^{N_p}_{p} N_{Ip} m_p \vec{b}_{p} + \sum^{N_p}_{p}
  N_{Ip} m_p h^{-1} \vec{t}^s_{p}
\end{equation}
where $\tens{\sigma}_{p} = \tens{\sigma}_{p}(\tens{\varepsilon}_{p})$
is the particle $p$ stress field, which can be integrated employing
the suitable constitutive model. The strain tensor is updated employing the rate of stress tensor $\dot{ \tens{\varepsilon}}_{p}$ used to update the
strain tensor is as follows \eqref{eq:IncrStrainPoint}.
\begin{equation}
  \label{eq:IncrStrainPoint}
  \dot{\tens{\varepsilon}_{p}} = \frac{\Delta
    \tens{\varepsilon}_{p}}{\Delta t} =
  \frac{1}{2}\left[\Grad{N_{Ip}}\ \vec{v}_{I} + \Grad{N_{Ip}}^T\
    \vec{v}_{I}\right].
\end{equation}
Later, imposing $\frac{D \rho}{D t} = 0$, we ensures the mass
conservation and update the density field.
\begin{equation}
  \label{eq:MassConservation}
\dot{\rho} = - \rho\ \mathit{tra} \left( \dot{\tens{\varepsilon}} \right)
\end{equation}

To improve the computational efficiency and stability, the nodal mass matrix
\eqref{eq:particle_nod_mass} can be substituted by the lumped mass
matrix $\tens{m}_I$. Therefore the nodal balance of momentum equation \eqref{eq:particle_balance_forces3} can be simplified to
\begin{equation}
  \label{eq:SimplyNodalMomentum}
  \dot{\vec{p}}_{I} = \tens{m}_I\ \vec{a}_{I} = \vec{f}_{I}^{int} + \vec{f}_{I}^{ext}.
\end{equation}
To solve the equation \eqref{eq:SimplyNodalMomentum}, a second order
temporal integration scheme is required. The next step is to advect
the particles solving,
\begin{equation}
  \label{eq:Updated_Lagrangian}
  \dot{\vec{v}}_p = \sum^{N_n}_{I}\vec{a}_{I}\ N_{Ip},\quad and\quad \dot{\vec{x}}_{p} = \sum^{N_n}_{I}\vec{v}_{I}\ N_{Ip}  
\end{equation}
To solve this equations, the forward Euler algorithm is the common
choose for this in the MPM literature. In next lines, a complete
description of the standard MPM algorithm will be described.

\section{Explicit predictor-corrector scheme for MPM.}
\label{sec:epc-algor-mpm}

To solve equations \eqref{eq:SimplyNodalMomentum} and
\eqref{eq:Updated_Lagrangian}, a time integration scheme is
required. It has been described in detail by many researchers
\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and summarized
in Figure \ref{fig:MPM_algorithm}. Other authors have proposed many
others time integration alternatives like
\cite{Guilkey2003}, \cite{Tran2019e}, \cite{Charlton2017}. In the first publication on
the MPM \cite{Sulsky1994}, the nodal acceleration in employed to
update the particles as
\begin{equation}
  \label{eq:Sulsky-1994-UL-v-x}
  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
  \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{a}_{I}^{k},\quad and\quad
  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{v}_{I}^{k}.
\end{equation}

However, in Andersen (2009)\cite{thesis_Andersen_2009} this
algorithm has been shown to be numerically unstable due to that
$\vect{f}_I^{int,k}$ can be finite for an infinitesimal nodal mass
$\tens{m}$. This can lead to numerical issues when nodal acceleration
is obtained for evaluating \eqref{eq:Sulsky-1994-UL-v-x}. Hence, a
corrected version of this algorithm in shown in Zhang {\it et al.}
(2016)\cite{Zhang_book_2016}
\begin{equation}
  \label{eq:Zhang-2016-UL-v-x}
  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
  \sum^{N_n}_{I}\frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I},\quad and\quad
  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \sum^{N_n}_{I} \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}.  
\end{equation}

Later Tran \& Solowski (2019)\cite{Tran2019e} presented a
generalized-$\alpha$ scheme for the MPM inspired in the explicit time
integration algorithm proposed by Chung \& Hulbert
(1993)\cite{Geranlized_alpha_1993}, but with the particularity that
the acceleration is evaluated both in the beginning and the end of the
time step.
\begin{align}
  \label{eq:Tran-2019-GA-v}
  & \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
    \sum^{N_n}_{I} N_{Ip}^{k}\ \left[(1 - \gamma)\ \vect{a}_I^{k} +
    \gamma\ \vect{a}_I^{k+1} \right]\\
  \label{eq:Tran-2019-GA-x}
  & \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\
    \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{v}_{I}^{k} + \Delta t^2
    \sum^{N_n}_{I}N_{Ip}^{k} \left[ (\frac{1}{2} - \beta)\
    \vec{a}_{I}^{k} + \beta\ \vec{a}_{I}^{k+1} \right]
\end{align}
and
\begin{equation}
  \label{eq:Tran-2019-GA-a}
   \vect{a}_p^{k+1} = \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{a}_{I}^{k+1}.
\end{equation}

This scheme has prof to damps out the higher frequency noises
\cite{Tran2019e}. But it can present the same numerical instabilities
as in \eqref{eq:Sulsky-1994-UL-v-x} when nodal masses become infinitesimal.
Here we propose a explicit predictor-corrector scheme for MPM based on the Newmark a-form with
$\gamma = 0.5$ and $\beta = 0$ which is the central difference
explicit. This method is devoted to solve a system of equations of type
\begin{equation*}
  \Matrix{M}_{IJ}\ddot{\Vector{d}}_{J} + \Matrix{C}_{IJ}\dot{\Vector{d}}_{J} +
  \Matrix{K}_{IJ}\Vector{d}_{J} = \Vector{F}_{I}
\end{equation*}
Nevertheless it can be applied for an isolated mass, therefore it is
possible to apply this methods successfully in the MPM framework as
was proved by \cite{Tran2019e}. Taking the predictor
definition from the classic literature \cite{Hughes2000} and
calculating particles velocity and acceleration as described in 
\cite{Zhang_book_2016}, we get the following expression for the
\textbf{predictor} stage for both velocity and displacement.
\begin{align}
  \label{eq:Predictor-displacement}
  &\vec{x}_p^{n+1} = \vec{x}_p^n + \Delta t\ \underbrace{\sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}}_{\vec{v}_p^{n}} + \frac{1}{2}\Delta t^2\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}}_{\vec{a}_p^{n}}\\
  \label{eq:Predictor-velocity}
  &\vec{v}_p^{n+1} = \vec{v}_p^n + (1 - \gamma)\ \Delta t\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}}_{\vec{a}_p^{n}}        
\end{align}

Consequently, the \textbf{corrector} stage for the particles velocity is in the
following way
\begin{equation*}
  \vec{v}_{p}^{k+1} = \vec{v}_{p}^{k+1} +
  \gamma\ \Delta t\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k+1}\ N_{Ip}^{k+1}}{\tens{m}_I^{k+1}}}_{\vec{a}_p^{n+1}}  
\end{equation*}

Notice that the predictor of the particle displacement is
computed using information only from the predictor of the
previous step. However, velocities are computed using half information
of the past corrector and half of the past predictor. Therefore here we share
similarities with the \textbf{leapfrog integration} which updates the
position at full time step, but updates the velocity at half time
steps. Due to its simplicity allows be implemented with minor modifications
over a standard forward Euler. It is summarized in shape of
pseudo-algorithm \ref{alg:PCE-algorithm}.

\begin{algorithm}
\floatname{algorithm}{Algorithm}
\renewcommand{\thealgorithm}{}
\caption{Explicit scheme : Newmark central difference}
\label{alg:Second_step_MPM_2STG}
\begin{algorithmic}[1]
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
  \STATE \textbf{Explicit Newmark Predictor} ($\gamma = 0.5$) :
  \begin{align*}
    &\vec{x}_p^{n+1} = \vec{x}_p^n + \Delta t\ \sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k} + \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}\\
    &\vec{v}_p^{n+1} = \vec{v}_p^n + (1 - \gamma)\  \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}\Delta t        
  \end{align*}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \STATE \textbf{Discard the previous nodal values}.
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \STATE \textbf{Transference of particles kinetics information to the
    mesh}:\\
  Calculate the lumped mass matrix \eqref{eq:Lumped-mass-matrix},
  and later the nodal momentum \eqref{eq:Nodal-momentum} of the
  corrected values.
  \begin{equation*}
    \tens{m}_{I} = \sum_{p}^{N_p} m_p\ N_{Ip}^{k+1},\quad
    \vec{p}_{I}^{k+1} = \sum_{p}^{N_p} m_p\ \vec{v}_{p}^{k+1}\ N_{Ip}^{k+1},\quad
    \vec{v}_{I}^{k+1} = \frac{\vec{p}_{I}^{k+1}}{\tens{m}_I}.
  \end{equation*}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \STATE \textbf{Impose essential boundary conditions over the nodal
    values}:\\
  At the fixed boundary, set $\vec{p}_{I}^{k+1} = 0$.
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \STATE \textbf{Deformation tensor increment calculation}.
  \begin{align*}
    &\dot{\tens{\varepsilon}_{p}}^{k+1} = \frac{1}{2}\ \sum_{I}^{N_n}
    \Grad{N_{Ip}^{k+1}}\vec{v}_{I}^{k+1} +
      (\Grad{N_{Ip}^{k+1}}\vec{v}_{I}^{k+1})^T \\
    &\Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\ \dot{\tens{\varepsilon}_{p}}^{k+1}
  \end{align*}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \STATE \textbf{Update the density field}:\\
  Imposing the mass conservation in the total derivative expression of
  the density field we reach to a suitable way of update it.
  \begin{equation*}
    \rho_p^{k+1} = \frac{\rho_p^k}{1 + \mathit{tra}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.
  \end{equation*}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \STATE \textbf{Balance of forces calculation}:\\
  Calculate the grid nodal internal forces $\vec{f}_{I}^{int,k+1}$, external
  forces $\vec{f}_{I}^{ext,k+1}$, and the total grid nodal force $\vec{f}_{I}^{k+1} =
  \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
  \eqref{eq:nodal_internal_forces} and
  \eqref{eq:nodal_external_forces} in the time step $k+1$. In the
  grid node $I$ is fixed in one of the spatial dimensions, set it to
  zero to make the grid nodal acceleration zero in that direction.\\
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \STATE \textbf{Integrate the grid nodal momentum equation :}\\
  Following the definition \eqref{eq:particle_balance_forces3}
  calculate the nodal momentum $\vec{p}_{I}$ in $k+1$. 
  \begin{equation*}
    \vec{p}_{I}^{k+1} = \vec{p}_{I}^{k} + \vec{f}_{I}^{k+1}\Delta t
  \end{equation*}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \STATE \textbf{Explicit Newmark Predictor}:
  \begin{equation*}
    \vec{v}_{p}^{k+1} = \vec{v}_{p}^{k+1} +
    \gamma \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k+1}\ N_{Ip}^{k+1}}{\tens{m}_I^{k+1}}\Delta t  
  \end{equation*}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\end{algorithmic}
\end{algorithm}

\begin{figure}\sidecaption
  \centering
  \resizebox{0.6\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/MPM_scheme}
  }
  \caption{MPM standard algorithm.}
  \label{alg:PCE-algorithm}
\end{figure}

\section{Local max-ent approximants}
\label{sec:local-max-ent}

The previous lines describe the main algorithm without defining an
interpolation technique. A direct consequence of this, is that it is
possible to adopt a width range of shape functions and interpolation techniques. The MPM has been
successfully applied to a wide range of problems due to its ability to
deal with large strain problems without mesh distorsion issues inherent to
mesh based methods like FE. However, in the simulations made with the
original MPM, there are numerical noises when particles crossing
the cell boundaries. These numerical inaccuracies give rise to the
development of other interpolation techniques. Some of this
alternatives techniques are the generalized interpolation material
point method (GIMP) Bardenhagen \& Kober (2004)\cite{Bardenhagen2004},
the dual domain material point method (DDMP) Zhang {\it et al.}
(2011)\cite{Zhang2011a}, the B-Spline MPM Tran {\it et al.}
(2019)\cite{Tran2019a}, the Conservative Taylor Least
Squares reconstruction Wobbes {\it et al.}
(2018)\cite{E_Wobbes_2018} and more recently the local
maximum-entropy (or local \textit{max-ent}) shape function first
introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} has been tested
under the MPM framework by Wobbes {\it et al.}
(2020)\cite{Wobbes2020} where they prof that simulations performed with the maxent basis functions
show considerably more accurate stress approximations for
MPM. Although, in \cite{Wobbes2020} authors does not deep in $\beta$
parameter benefits

The maximum-entropy estimate is defined as the type of statistical
inference, which is the least biased possible on the given information
\cite{Jaynes1957}. The basic idea of the shape functions based on such an estimate is to interpret the shape function $N_I(\vec{x})$ as the probability of $\vec{x}$ to obtain the value $\vec{x}_I$,  $I=1, \dots, n$. Here $n$ is the number of nodes in the domain. Taking Shannon's entropy as the starting point:
\begin{equation}
  \label{eq:Shannon-entropy}
  H(p_1(\vec{x}),...,p_n(\vec{x})) = -\sum^{N_n}_{I=1}{p_I(\vec{x})\log p_I }
\end{equation}
where $p_I(\vec{x})$ is the probability, equivalent to the mentioned
shape function $N_I(\vec{x})$,  satisfying both the zeroth and
first-order consistency. The least-biased approximation scheme is given by
\begin{eqnarray}
  \text{(ME)} \hspace{0.2cm} \text{Maximize} \hspace{0.1cm}H(p) &=&  -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I } \nonumber \\
  \text{subject to} \hspace{0.5cm} p_I &\ge& 0, \hspace{0.5cm} \text{I=1, ..., n} \nonumber \\
  \sum_{I=1}^{N_n}{p_I} &=& 1 \nonumber \\
  \sum_{I=1}^{N_n}{p_I \vec{x}_I} &=& \vec{x} \nonumber 
\end{eqnarray}
The local max-ent approximation schemes (LME) as a Pareto set,
defined by \cite{Arroyo2006} is as follows 
\begin{eqnarray}
  \text{(LME)}_{\beta} \hspace{0.5cm} \text{For fixed} \hspace{0.2cm} \vec{x} \hspace{0.2cm} \text{minimise}  \nonumber \\
  \hspace{0.5cm}f_{\beta}(\vec{x}, p) &=& \beta H(\vec{x},p) - H(p)  \nonumber  \\
  \text{subject to} \hspace{0.5cm} p_I &\ge& 0, \hspace{0.2cm} \text{I=1, ..., n}  \nonumber \\
  \sum_{I=1}^{N_n}{p_I} &=& 1  \nonumber \\
  \sum_{I=1}^{N_n}{p_I \, \vec{x}_I} &=& \vec{x}    \nonumber 
\end{eqnarray}
for $\beta \in (0,\infty)$ is Pareto optimal. The unique solution of
the local max-ent problem (LME)$_\beta$ is: 
\begin{equation}
  \label{eq:LME-p}
p(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +  \vec{\lambda}  \;  (\vec{x}-\vec{x}_I)         \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
\end{equation}
where
\begin{equation}
  \label{eq:LME-Z}
Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \, | \vec{x}-\vec{x}_I|^2 + \vec{\lambda}  \,  (\vec{x}-\vec{x}_I)  \right]}
\end{equation}
being $\vec{\lambda}^*(\vec{x})$ the unique minimiser  for $\log Z(\vec{x}, \vec{\lambda})$

In order to obtain the first derivatives of the shape function, it is  also necessary to compute~$\nabla p^*_I$ 
\begin{equation}
  \label{eq:LME-grad-p}
\nabla p^*_I=p^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} p^*_J \, \nabla f^*_J\right)
\end{equation}
where
\begin{equation}
  \label{eq:LME-f}
f^*_I(\vec{x},  \vec{\lambda},\beta)=-\beta \, |\vec{x}-\vec{x}_I|^2 + \vec{\lambda}   \,  (\vec{x}-\vec{x}_I)
\end{equation}
Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression:
\begin{eqnarray}
\nabla p^*_I &=& -p^*_I \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I) \label{eq26} 
\end{eqnarray}
%&&\mbox{
where \tens{J} is the Hessian matrix, defined by:
%} \nonumber \\&& \nonumber \\
\begin{eqnarray}
\tens{J}(\vec{x},  \vec{\lambda},\beta) &=& \frac{\partial \vec{r}}{\partial  \vec{\lambda}} \label{eq27} \\ 
%&& \nonumber \\
\vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \partial_{\vec{\lambda}}{\log{ Z( \vec{x},\vec{\lambda}})} 
%\nonumber \\ &=&
  =\sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I) \label{eq28} 
\end{eqnarray}
Note that, the objective of the above procedure is to find the $\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. 
The traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27}) to calculate small increments of $\partial\vec{\lambda}$ in a Newton-Raphson approach.

Similar to alternative non-polynomial meshfree basis functions, the LME approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem. Due to the FE-compatibility, the LME shape function is degenerated to linear finite element shape function if $d+1$ neighbouring nodes are chosen as the support. The support size of LME shape functions may be controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$ (e.g. two dimensional example shown in Fig. \ref{fig:LME_MPM})\cite{Arroyo2006}.
Since  $p_I$  is defined in  the entire domain, in practice,  the function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance, 10$^{-6}$, for example,  would ensure a reasonable range of neighbours, see \cite{Arroyo2006} for details. This  tolerance defines the limit values of the influence radius and   is used thereafter to find the neighbour nodes of a given integration point.

\begin{figure}
  \centering
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/MPM_Shape_Fun.png}
    % \resizebox{0.3\columnwidth}{!}{%
    % \input{Figures/MPM_Shape_Fun.png}
    % }
    \label{fig:MPM_Shape_Fun}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/MPM_Shape_Fun_dx.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/MPM_Shape_Fun_dx.png}
    % }
    \label{fig:MPM_Shape_Fun_dx}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/MPM_Shape_Fun_dy.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/MPM_Shape_Fun_dy.pgf}
    % }
    \label{fig:MPM_Shape_Fun_dy}
  }
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \qquad
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_17.3_Shape_Fun.png}
    % \resizebox{0.3\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun.png}
    % }
    \label{fig:LME_17.3_Shape_Fun}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_17.3_Shape_Fun_dx.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
    % }
    \label{fig:LME_17.3_Shape_Fun_dx}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_17.3_Shape_Fun_dy.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
    % }
    \label{fig:LME_17.3_Shape_Fun_dy}
  }
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \qquad
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/GIMP_Shape_Fun.png}
    % \resizebox{0.3\columnwidth}{!}{%
    % \input{Figures/GIMP_Shape_Fun.png}
    % }
    \label{fig:GIMP_Shape_Fun}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/GIMP_Shape_Fun_dx.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/GIMP_Shape_Fun_dx.png}
    % }
    \label{fig:GIMP_Shape_Fun_dx}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/GIMP_Shape_Fun_dy.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/GIMP_Shape_Fun_dy.pgf}
    % }
    \label{fig:GIMP_Shape_Fun_dy}
  }
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \qquad
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_10.0_Shape_Fun.png}
    % \resizebox{0.3\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun.png}
    % }
    \label{fig:LME_10.0_Shape_Fun}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_10.0_Shape_Fun_dx.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
    % }
    \label{fig:LME_10.0_Shape_Fun_dx}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_10.0_Shape_Fun_dy.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
    % }
    \label{fig:LME_10.0_Shape_Fun_dy}
  }
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \qquad
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_7.0_Shape_Fun.png}
    % \resizebox{0.3\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun.png}
    % }
    \label{fig:LME_7.0_Shape_Fun}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_7.0_Shape_Fun_dx.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
    % }
    \label{fig:LME_7.0_Shape_Fun_dx}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_7.0_Shape_Fun_dy.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
    % }
    \label{fig:LME_7.0_Shape_Fun_dy}
  }
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \qquad
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_5.0_Shape_Fun.png}
    % \resizebox{0.3\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun.png}
    % }
    \label{fig:LME_5.0_Shape_Fun}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_5.0_Shape_Fun_dx.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
    % }
    \label{fig:LME_5.0_Shape_Fun_dx}
  }
  \subfloat{
    \includegraphics[width=0.35\columnwidth]{Figures/LME_5.0_Shape_Fun_dy.png}
    % \resizebox{0.54\columnwidth}{!}{%
    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
    % }
    \label{fig:LME_5.0_Shape_Fun_dy}
  }
  \caption{Local max-ent shape functions for a two-dimensional
    arrangement of nodes, and spatial derivatives for several values
    of $\gamma = \beta/h^2$.}
  \label{fig:LME_MPM}
\end{figure}

\section{Numerical results : 1D Elastic bar}
\label{sec:dynamic-benchmark}

In this section, the benchmark proposed by Dyka \& Ingel
(1995)\cite{Dyka1995} is considered to illustrate the
capacity of MPM \cite{Sulsky1994} and OTM
models to avoid tensile instabilities.

In the one-dimensional bar sketched in
the figure \ref{fig:Dyka_Bar}, the left end of the bar is fixed and
the right and an initial velocity $v_0 = 5\ m/s$ is given to the last
quarter of it in the x positive direction. The length of it is 0.1333
meters with an unit section. The elastic parameters consider for this
test are:
\begin{itemize} 
\item  Density : $7833\ kg/m3$
\item  Poisson ratio : $0$
\item  Elastic modulus : $200 \cdot 10^9\ Pa$
\end{itemize}

The results are provided for the explicit predictor-corrector version of the
MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM algorithms. For MPM, piecewise-
linear, uGIMP and \textit{max-ent} basis functions are employed. The OTM
algorithm is used only with \textit{max-ent} shape functions.

\begin{figure}\sidecaption
  \centering
  \resizebox{0.8\hsize}{!}{
    \input{Figures/Dyka_bar.tex}}
  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar. }
  \label{fig:Dyka_Bar}
\end{figure}

The boundary conditions are:
\begin{equation}
  \label{eq:3}
  \sigma \rvert_{x=L} = 0 \quad , \quad v \rvert_{x=0} = 0
\end{equation}

The analytical solution in terms of velocity
\ref{fig:vel_analytics_dyka}, and stress
\ref{fig:stress_analytics_dyka} can be found in the appendix
\ref{app:analytical_sol} given by the Method of characteristics. For
the convergence analysis, the root-mean-square (RMS) error in the
displacement is computed. RMS error is defined as follows

\begin{equation}
  \label{eq:RMS}
  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)}
\end{equation}

\subsection{Error analysis MPM vs uGIMP vs MPM-\textit{max-ent}}
\label{sec:study-error}

\subsection{MPM versus OTM}
\label{sec:mpm-versus-otm}

\section{Conclusions}
\label{sec:conclusions}

Building upon the idea of anisotropic shape functions
\cite{Arroyo2006}, \cite{Kochmann2019} introduced an enhanced version of the
original local max-ent scheme, which uses an anisotropic support to
deal with tensile inestability.

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
\section*{Conflict of interest}
%
The authors declare that they have no conflict of interest.

\appendix
\section{The analytical solution of the 1D Dyka benchmark}
\label{app:analytical_sol}

For the derivation of this analytical solution we will consider  the
dynamic behaviour of a 1D elastic bar. The governing equations are the
following: (i) The balance of linear momentum,
\begin{equation}
  \label{eq:1D-balance-linear-momentum}
  \rho\ \Deriv{v}{t} = \Deriv{\sigma}{x} + \rho\ b,
\end{equation}
where $\sigma$ is the stress value, $\rho$ is the density,
$v$ is the velocity, and $b$ are the body
forces. (ii) The constitutive model, which for convenience of the
following developments will be written in terms of displacement and
velocities as, 
\begin{equation}
  \label{eq:1D-constitutive-equation}
  \Deriv{\sigma}{t} = E \Deriv{\varepsilon}{t},
\end{equation}
where $E$ is the elastic modulus. (iii) The compatibility equation
also in terms of the velocity field,
\begin{equation}
  \label{eq:CompatibilityEquation_e}
  \Deriv{\varepsilon}{t} = \Deriv{v}{x}.
\end{equation}
Next for simplicity, we remove the body forces from
\eqref{eq:1D-balance-linear-momentum}, and we will introduce
\eqref{eq:CompatibilityEquation_e} in
\eqref{eq:1D-constitutive-equation}, so we get the following system of equations,
\begin{align}
  \label{eq:1D-balance-linear-momentum-II}
  \Deriv{v}{t} &= \frac{1}{\rho}\ \Deriv{\sigma}{x}, \\
  \label{eq:1D-constitutive-equation-II}
  \Deriv{\sigma}{t} &= E\ \Deriv{v}{x}.
\end{align}

Introducing \eqref{eq:1D-constitutive-equation-II} in
\eqref{eq:1D-balance-linear-momentum-II} and expressing the remaining
equation in terms of the displacement, we reach the 1D wave
equation for linear elastic materials,
\begin{equation}
  \label{eq:1D-wave-elastic}
  \Deriv[2]{u}{t} = \frac{E}{\rho}\ \Deriv[2]{u}{x} = c^2\ \Deriv[2]{u}{x}
\end{equation}
where we have introduced the wave celerity $c$ as,
\begin{equation}
  \label{eq:1D-elastic-wave-celerity}
  c = \sqrt{\frac{E}{\rho}}
\end{equation}
Alternative, rearranging both equations
\eqref{eq:1D-balance-linear-momentum-II} and
\eqref{eq:1D-constitutive-equation-II} it is possible to join them in a
single system of equations as,
\begin{equation}
  \label{eq:System-stress-velocity}
  \Deriv{}{t} \left[
    \begin{array}{c}
      \sigma \\
      v
    \end{array}
  \right] + \left[
    \begin{array}{cc}
      0 & - E \\
      - 1/\rho & 0 
    \end{array} \right] \left[
    \begin{array}{c}
      \Deriv{\sigma}{x} \\
      \Deriv{v}{x}
    \end{array}
  \right] = \Vector{0}.
\end{equation}
This expression can be written in a more compact format as,
\begin{equation}
  \label{eq:System-stress-velocity-II}
  \Deriv{\Vector{\phi}}{t} + \Matrix{A}\Deriv{\Vector{\phi}}{x} = \Vector{0}
\end{equation}
where both variables are joined in a single vectorial variable
$\Vector{\phi}$ and $\Matrix{A}$ in coupling matrix between both equations,
\begin{equation*}
  \Vector{\phi} = \left[
    \begin{array}{c}
      \sigma \\
      v
    \end{array}
  \right],\quad 
  \Matrix{A} =  \left[
    \begin{array}{cc}
      0 & - E\\
      - 1/\rho & 0 
    \end{array} \right].
\end{equation*}
Note that the nature of \label{eq:eq:System-stress-velocity-II} is still
hyperbolic despite the fact it does not have a second order
temporal derivative as \eqref{eq:1D-wave-elastic}. A proof of this can
be easily obtained if we get the zeros of the hypersurface defined by
\eqref{eq:1D-wave-elastic}. And later the eigenvalues of $\Matrix{A}$
in \eqref{eq:System-stress-velocity-II}. In both cases, eigenvalues
are real and distinct ($\lambda = \pm \sqrt{\frac{E}{\rho}}$),
therefore the system is called strictly hyperbolic.

For a more general description in the following, we will assume that $\Matrix{A}$ has $n$
different eigenvalues $\{ \lambda_1, \lambda_2, \ldots, \lambda_i, \ldots
\lambda_n \}$ and $n$ eigenvectors $\{ \vec{x}^1, \vec{x}^2, \ldots,
\vec{x}^i, \ldots \vec{x}^n \}$ satisfying that $\tens{A} \vec{x} =
\lambda \vec{x} $. Now we introduce the matrix $\Matrix{P}$ whose columns are the $n$
eigenvalues $\Vector{x}$
\begin{equation}
  \label{eq:P-matrix}
\Matrix{P} = \{ \vec{x}^1, \vec{x}^2, \vec{x}^3, \ldots \vec{x}^n \}.
\end{equation}
Diagonalizing $\Matrix{A}$ using $\Matrix{P}$ we get
\begin{equation}
  \label{eq:Lambda-matrix}
  \Lambda = \Matrix{P}^{-1} \Matrix{A}\ \Matrix{P},
\end{equation}
where $ \Lambda_{ii} = \lambda_i$. Next we will define a vector $\Vector{\Re}$ such that:
\begin{equation}
  \label{eq:Riemann-definition}
  \Vector{\phi} = \Matrix{P}\ \Vector{\Re}
\end{equation}
we will assume to be integrable. Expanding the above expression with
the chain rule and passing the matrix $\Matrix{P}$ to left hand side
of the equality we get,
\begin{equation}
  \label{eq:Riemann-II}
  d \vec{\Vector{\Re}} = \Deriv{\Vector{\Re}}{t}dt + \Deriv{\Vector{\Re}}{x}dx =
  \tens{P}^{-1}\left(\Deriv{\phi}{t}dt + \Deriv{\phi}{x}dx \right)
\end{equation}
and setting the terms we get,
\begin{equation}
  \label{eq:Riemann-III}
  \Deriv{\Vector{\Re}}{t} = \Matrix{P}^{-1}\Deriv{\Vector{\phi}}{t},\quad 
  \Deriv{\Vector{\Re}}{x} = \Matrix{P}^{-1}\Deriv{\Vector{\phi}}{x}
\end{equation}
Next, if we multiply \eqref{eq:System-stress-velocity-II} by
$\Matrix{P}^{-1}$ we get:
\begin{equation}
  \label{eq:System-stress-velocity-III}
  \Matrix{P}^{-1}\Deriv{\Vector{\phi}}{t} + \left(\Matrix{P}^{-1}\Matrix{A}\Matrix{P}
  \right)\Matrix{P}^{-1} \Deriv{\Vector{\phi}}{x} = \Vector{0}
\end{equation}
finally introducing the expressions \eqref{eq:Riemann-III} we reach to
\begin{equation}
  \label{eq:System-stress-velocity-IV}
  \Deriv{\Vector{\Re}}{t} + \Lambda \Deriv{\Vector{\Re}}{x} = \Vector{0}  
\end{equation}
which consists of $n$ uncoupled equations as $\Lambda$ is
diagonal matrix as we can see in \eqref{eq:Lambda-matrix}. Each of this
equations are 1D scalar convective transport equations, with solutions
of the form:
\begin{equation}
  \label{eq:SystemEquations_sigma_v_VI}
  \Re^{(i)} = F^{(i)} \left(x - \lambda^{(i)} t \right)
\end{equation}

This uncoupled system, has, therefore, a set of $n$ characteristics.
These magnitudes $\Re_i$ which propagate along characteristics are
known as ``Riemann invariants'' of the problem. Here we have a 1D
configuration, so the domain is $\Omega : \left(0, L\right) x \left(0,
  T\right)$. For the closure of the problem we require:
\begin{itemize}
\item ``n'' initial conditions of the form $\Re_i (x,t=0) = h_i(x)$,
  where $i = {0, \ldots, n}$, and $h_i(x)$ is a vectorial function
  given by the physical variables of the problem.
\item ``n'' boundary conditions.
\end{itemize}

Now particularizing the previous equations for the 1D elastic bar
described in \cite{Dyka1995}, we get that the matrix $\Matrix{P}$
is the following:
\begin{equation*}
    \Matrix{P} =  \left[
    \begin{array}{cc}
      -\sqrt{E\rho} & \sqrt{E\rho}\\
       1 & 1 
    \end{array} \right]
\end{equation*}
and its inverse is:
\begin{equation*}
    \Matrix{P}^{-1} = \frac{1}{2} \left[
    \begin{array}{cc}
      -\frac{1}{\sqrt{E\rho}} & 1\\
      \frac{1}{\sqrt{E\rho}} & 1 
    \end{array} \right]
\end{equation*}

And introducing the value of the inverse matrix $\Matrix{P}^1$ in the
Riemann definition \eqref{eq:Riemann-definition} we get the following
system of equations,
\begin{align}
  \label{eq:Riemann-I-1D-elastic-bar}
  &\Re^{I} = \frac{1}{2\sqrt{\rho E}}\left(-\sigma + v\ \sqrt{\rho E}
    \right)\\
  \label{eq:Riemann-II-1D-elastic-bar}
  &\Re^{II} = \frac{1}{2\sqrt{\rho E}}\left(\sigma + v\ \sqrt{\rho E} \right)
\end{align}

From \eqref{eq:Riemann-I-1D-elastic-bar} and
\eqref{eq:Riemann-II-1D-elastic-bar} we can obtain the values of the
stress and the velocity as:
\begin{equation}
  \label{eq:Riemann-stress-velocity}
  v = \Re^{I} + \Re^{II} \quad , \quad \sigma = \sqrt{E \rho}\left(\Re^{II} - \Re^{I} \right)
\end{equation}

The boundary conditions are in both cases of radiation as there is not
wave in-going from the exterior. So for the left side (fixed
boundary) we get the following conditions:
\begin{equation*}
  &\Re^{I} = 0 \quad and \quad v_{x=0} = 0
\end{equation*}
Therefore $\sigma_{x=0} = \sqrt{\rho E}\Re^{II}$. And in the left side
(free boundary) we get the following conditions:
\begin{equation*}
  &\Re^{II} = 0 \quad and \quad \sigma_{x=L} = 0
\end{equation*}
Therefore $v_{x=L} = \Re^{I}$. Finally, applying this conditions in
the elastic bar sketched in \ref{fig:Dyka_Bar}, is possible to obtain
the velocity history in the right side of the bar
\ref{fig:vel_analytics_dyka} and the stress in the last quarter side of the Dyka
bar \ref{fig:stress_analytics_dyka} as is demanded in \cite{Dyka1995}.

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\columnwidth]{Figures/1D_right_Velocity.png}
  }
  \caption[Velocities values in the right side of the Dyka
  bar]{Analytical solution for the velocity in the right side of the Dyka bar.}
  \label{fig:vel_analytics_dyka}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\columnwidth]{Figures/1D_left_Stress.png}
  }
  \caption[Stress values in the last quarter side of the Dyka
  bar]{Analytical solution for the stress in the last quarter of the Dyka bar.}
  \label{fig:stress_analytics_dyka}
\end{figure}

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{Biblio.bib}   % name your BibTeX data base

\end{document}
% end of file template.tex

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-02-21 Figures/Dyka_Analytical.py
Figuras y codigos python

@@ -1,0 +1,361 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+from matplotlib import cm
+from matplotlib.ticker import LinearLocator
+from matplotlib.ticker import FixedLocator
+from matplotlib.ticker import FormatStrFormatter
+
+
+def find_nearest(array, value):
+    array = np.asarray(array)
+    idx = (np.abs(array - value)).argmin()
+    return idx
+
+def Get_Riemann_I(Stress_I,Velocity_I):
+    R_I = (0.5/StaticVisco)*(- Stress_I + Velocity_I*StaticVisco)
+    return R_I
+
+def Get_Riemann_II(Stress_II,Velocity_II):
+    R_II = (0.5/StaticVisco)*(Stress_II + Velocity_II*StaticVisco)
+    return R_II
+
+# Material properties
+L = 0.1333
+E = 200*10**9 # Pa
+rho = 7833 # kg/m³
+CEL = 5033 # m/s , np.sqrt(E/rho)
+# L = 1
+# E = 1 # Pa
+# rho = 1 # kg/m³
+# CEL = 1 # m/s
+
+T_go = L/CEL #
+T_end = 16*T_go
+
+# Spatial mesh
+# dx = 0.000001
+dx = 0.001
+
+# Time mesh
+dt =  0.000001
+# dt =  0.1
+
+# Discretize domain
+N_x = int(L/dx)
+X = np.linspace(0,L,N_x)
+# Discretize time
+N_t = int(T_end/dt)
+T = np.linspace(0,T_end,N_t)
+
+# Initial conditions
+v0 = -5
+# v0 = -1
+Stress = np.zeros([N_t,N_x])
+Velocity = np.zeros([N_t,N_x])
+for x in range(0,N_x):
+    if X[x] <= 0.25*L :
+        Velocity[0,x] = v0
+    else :
+        Velocity[0,x] = 0
+
+        
+# Get the static viscosity
+StaticVisco = np.sqrt(E*rho)
+
+        
+# figures
+Show_grafs = True
+format_fig = 'png'
+        
+################################################################
+####################### Loop in time ###########################
+################################################################
+for t in range(0,N_t):
+    
+    ############################################################    
+    ##################### Solve domain #########################
+    ############################################################
+    for x in range(1,N_x-1):
+
+        # Get boundary values through characteristics lines
+        t_I = T[t] - X[x]/CEL
[…]

### 2020-02-21 _region_.tex
Cambios 21-2-2020

--- 2020-02-21 main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+\message{ !name(main.tex)}%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
 %
@@
 % Gradient
-\newcommand{\Grad}[1]{
-  \ensuremath{\nabla{#1}}
-}
+\newcommand\Grad[1]{\nabla{#1}}
+\newcommand\GradS[1]{\nabla^s{#1}}
+\newcommand\GradT[1]{\nabla^T{#1}}
 
@@
   \IfStrEqCase{#1}{
-    {1}{\ensuremath{\int_{\Gamma}{#2}\ d\Gamma}}
-    {2}{\ensuremath{\int_{\Sigma}{#2}\ d\Sigma}}
-    {3}{\ensuremath{\int_{\Omega}{#2}\ d\Omega}}
+    {2}{\ensuremath{\int_{\varGamma_d}{#2}\ d\varGamma}}
+    {3}{\ensuremath{\int_{\varOmega}{#2}\ d\varOmega}}
   }
@@
 \begin{document}
+
+\message{ !name(main.tex) !offset(-3) }
 
@@
 
-\section{Overview of the MPM}
-\label{sec:mpm-overview}
+\section{Notation}
+\label{sec:Notation}
+In what follows, we will adopt the following convention:
+\begin{table}[h]
+  \centering
+  \caption{Physical variables involved in the problem}
+  \label{tab:notation-table}
+  \begin{tabular}{c c}
+    $\rho$ & Density field \\
+    $\vect{a}$ & Acceleration field \\
+    $\vect{v}$ & Velocity field \\
+    $\vect{u}$ & Displacement field \\
+    $\tens{\sigma}$ & Cauchy stress tensor \\
+    $\tens{\varepsilon}$ & Cauchy strain tensor\\
+    $\tens{D}$ & Constitutive tensor \\
+  \end{tabular}
+\end{table}
+
+The subscript $p$ is used to define a particle variable. While the subscript $I$ is reserved in this
+notation for denoting nodal variables.
+
+\section{Derivation of the MPM}
+\label{sec:derivation-mpm}
 In this section, we provide an overview of the standard explicit MPM
@@
 
-\subsection{Derivation of the MPM}
-\label{sec:derivation-mpm}
+\subsection{Governing equations }
+\label{sec:governing-equations}
 In the MPM approach a continuum is considered. The continuum behaviour
-can be described by a set of governing equations which are the balance
-of momentum equation ($\rho \vect{a} = \Div{\tens{\sigma}} + \rho
-\vect{b}$), the compatibility equation ($\dot{\tens{\varepsilon}} =
-\Grad{\vect{v}}$), the constitutive equation ($\dot{\tens{\sigma}} =
-\tens{D} \colon \dot{\tens{\varepsilon}}$), and the balance of mass equation
-($\frac{D \rho}{D t} = \dot{\rho} + \rho \Grad{\vect{v}}$). The balance of momentum can be
-formulated in weak form by introducing an arbitrary test function $\vec{\psi}$, yielding
+can be described by a set of governing equations which are
+
+the balance of momentum equation
+\begin{equation}
+  \label{eq:Balance-momentum}
+\rho \vect{a} = \Div{\tens{\sigma}} + \rho \vect{b},
+\end{equation}
+where $\Div{\qed}$ denotes the divergence operator. To ensure that the
+velocity field is compatible with the strain field is necessary that
+them satisfy the compatibility equation,
+\begin{equation}
+  \label{eq:Compatibility-equation}
+  \dot{\tens{\varepsilon}} = \GradS{\vect{v}} = \frac{1}{2}\left(
+    \Grad{\vect{v}} +  \GradT{\vect{v}} \right),
+\end{equation}
+where $\GradS{\qed}$ denotes the symmetric part of the gradient
+operation. Thorough the constitutive equation, the rate of the Cauchy stress
+tensor is defined to be
+\begin{equation}
+  \label{eq:Constitutive-equation}
+\dot{\tens{\sigma}} = \tens{D} \colon \dot{\tens{\varepsilon}},
+\end{equation}
+where $\tens{D}$ is the classical elasticity tensor. Finally we
+introduce the total derivative expression over the density field,
+\begin{equation}
+  \label{eq:Rho-material-derivative}
+\frac{D \rho}{D t} = \dot{\rho} + \rho \Grad{\vect{v}}.
+\end{equation}
+Where if we impose $\frac{D \rho}{D t}$ to be zero, the conservation
+of mass is guarantee.
+
+\subsection{Variational formulation}
+\label{sec:variational-formulation}
+To write the variational statement of the problem, let us define a
+virtual velocity field such that
+\begin{equation}
+  \label{eq:Hilbert-space}
+  \vect{v}^{\psi} \in \mathcal{H}^1_0(\Omega) = \{ \vect{v}^{\psi} \in
+  \mathcal{H}^1 \mid \vect{v}^{\psi} = \vect{0}\ \text{on}\ \Gamma_d \}.
+\end{equation}
+And which satisfies that the Cauchy sequences are convergent in $\varOmega$
+\begin{equation}
+  \label{eq:cauchy-secuence}
+  \Integral{3}{\vect{v}^{\psi}} < \infty\ \quad\text{and}\quad \Integral{3}{\Grad{\vect{v}^{\psi}}} < \infty
+\end{equation}
+The principle of virtual work states that the equilibrium solution to
+the boundary value problem of elasticity is the function $\vect{v} \in
+\mathcal{H}^1_0$ such that, for $\vect{v}^{\psi} \in
+\mathcal{H}^1_0$, the following holds:
 \begin{equation}
   \label{eq:BalanceMomentum_wf}
-  \Integral{3}{\rho\ \Deriv{\vec{v}}{t}\ \vec{\psi}} = -
-  \Integral{3}{\tens{\sigma} \colon \Grad{\vec{\psi}}} +
-  \Integral{2}{\vec{t}\ \vec{\psi}} + \Integral{3}{
-  \rho\ \vec{b}\ \vec{\psi}}.
+  \Integral{3}{\rho\ \left( \Deriv{\vec{v}}{t}\ - \vec{b} \right) \cdot \vec{v}^{\psi}} =
+  \Integral{2}{\vec{t}\ \cdot \vec{v}^{\psi}} - \Integral{3}{\tens{\sigma} \cdot
+    \tens{\varepsilon}^{\psi}},
 \end{equation}\\
-
+therefore (\ref{eq:BalanceMomentum_wf}) is the balance of momentum formulated in
+its weak form.
+
+\subsection{Galerkin procedure}
+\label{sec:Galerkin-procedure}
 In order to arrive to a finite set of equations, the continuum domain
-$\Omega$ is discretized with a finite sum of particles (material points), each one 
-represent a part of the domain $\Omega_p$ with $p = 1,2\ldots ,N_p$
-where $N_p$ is the number of particles. The index $p$ is
-used for the particles, while the index $I$ is reserved in this
-notation for denoting grid nodes. The material point $\vec{x}_p$ is
-defined at the centroid of $\Omega_p$. Further, a computational grid
+$\Omega$ is discretized with a finite sum of material points (in the
+following particles), each one represent a part of the discretized domain $\Omega_p$ with $p = 1,2\ldots ,N_p$
+where $N_p$ is the number of particles. The material point $\vec{x}_p$ is
+defined at the centroid of each $\Omega_p$. Further, a computational grid
 is formed of a finite set of grid points with coordinates $\vec{x}_I\
-, I = 1,2\ldots ,N_n$, where $N_n$ is the number of grid nodes. Each material point is assigned with initial values of position,
+, I = 1,2\ldots ,N_n$, where $N_n$ is the number of grid nodes.
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Discretization_MPM}
+  }
+  \caption{MPM discretization.}
+  \label{fig:MPM-discretization}
+\end{figure}
+
+Each material point is assigned with initial values of position,
 velocity, mass, volume and stress denoted by $\vec{x}_p$,  $\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$. The problem is then integrated using a discrete number of time
@@
     \label{eq:particle_acceleration_forces}
-    \Integral{3}{\rho\ \vec{a}\ \vec{\psi}} =& \sum^{N_p}_{p}
-   \dot{\vec{v}}_{p}\ \vec{\psi}_{p}\ m_p.
+    \Integral{3}{\rho\ \vec{a}\ \vect{v}^{\psi}} =& \sum^{N_p}_{p}
+   \dot{\vec{v}}_{p}\ \vect{v}^{\psi}_{p}\ m_p.
   \end{equation}\\
@@
   \label{eq:particle_body_forces}
-  \Integral{3}{\rho\ \vec{b}\ \vec{\psi} } = \sum^{N_p}_{p}
-  \vec{b}_{p}\ \vec{\psi}_{p}\ m_p.
+  \Integral{3}{\rho\ \vec{b}\ \vect{v}^{\psi} } = \sum^{N_p}_{p}
+  \vec{b}_{p}\ \vect{v}^{\psi}_p\ m_p.
 \end{equation}\\
@@
     \label{eq:particle_load_forces}
-    \Integral{2}{\vec{t}\ \vec{\psi}} = \Integral{2}{\rho\
-      \vec{t}^s\ \vec{\psi}} = \sum^{N_p}_{p} \vec{t}^s_{p}\ \vec{\psi}_{p}\ h^{-1}\ m_p ,
+    \Integral{2}{\vec{t}\ \vect{v}^{\psi}} = \Integral{2}{\rho\
+      \vec{t}^s\ \vect{v}^{\psi}} = \sum^{N_p}_{p} \vec{t}^s_{p}\ \vect{v}^{\psi}_{p}\ h^{-1}\ m_p ,
   \end{aligned} 
@@
 \eqref{eq:particle_internal_forces}, \eqref{eq:particle_body_forces},
-and \eqref{eq:particle_load_forces} in \eqref{eq:BalanceMomentum_wf}
-we reach to the particle balance of forces of the continuum,
-\begin{equation}
-  \label{eq:particle_balance_forces2}
-  \sum^{N_p}_{p}\vec{\psi}_{p}\ m_p\ \dot{\vec{v}}_{p} = \sum^{N_p}_{p}
-  \vec{\psi}_{p}\ m_p\ \vec{b}_{p} + \sum^{N_p}_{p}
-  \vec{\psi}_{p}\ m_p\ h^{-1}\ \bar{\vec{t}}^s_{p} -
-  \sum^{N_p}_{p} \Grad{\vec{\psi}_{p}}\ \frac{m_p}{\rho_p}\
-  \tens{\sigma}_{p}.
-\end{equation}\\
-
-Approximating the virtual displacement of the particle $\vec{\psi}_{p}$
-using a suitable approximation scheme we get \eqref{eq:VirtualDisplacementParticle}.
-\begin{equation}
-  \label{eq:VirtualDisplacementParticle}
-  \vec{\psi}_{p} = N_{Ip}\cdot \vect{1} = N_{Ip},
-\end{equation}
-where $N_{Ip} = N_I(\vec{x}_p)$ it is the nodal value of the shape
-function evaluated in the material point coordinates denoted by $\vec{x}_p$. Substituting \eqref{eq:VirtualDisplacementParticle} in
-\eqref{eq:particle_balance_forces2} we get :
+and \eqref{eq:particle_load_forces} in \eqref{eq:BalanceMomentum_wf},
+and approximating the virtual displacement of the particle $p$ as
+$\vec{\psi}_{p} = N_I(\vec{x}_p)\cdot \vect{1} = N_{Ip}$. We reach to
+the particle balance of forces of the continuum,
 \begin{equation}
@@
 \begin{equation}
-  \label{eq:Sulsky-1994-UL-v-x}
+  \label{eq:Sulsky-1994-UL-v}
   \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
-  \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{a}_{I}^{k},\quad and\quad
+  \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{a}_{I}^{k}
+\end{equation}
+\begin{equation}
+  \label{eq:Sulsky-1994-UL-x}
   \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{v}_{I}^{k}.
 \end{equation}
-
 However, in Andersen (2009)\cite{thesis_Andersen_2009} this
@@
 $\tens{m}$. This can lead to numerical issues when nodal acceleration
-is obtained for evaluating \eqref{eq:Sulsky-1994-UL-v-x}. Hence, a
+is obtained for evaluating \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v}. Hence, a
 corrected version of this algorithm in shown in Zhang {\it et al.}
@@
 \begin{equation}
-  \label{eq:Zhang-2016-UL-v-x}
+  \label{eq:Zhang-2016-UL-x}
+  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \sum^{N_n}_{I} \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}.  
+\end{equation}
+\begin{equation}
+  \label{eq:Zhang-2016-UL-v}
   \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
-  \sum^{N_n}_{I}\frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I},\quad and\quad
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \sum^{N_n}_{I} \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}.  
-\end{equation}
-
+  \sum^{N_n}_{I}\frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I},
+\end{equation}
 Later Tran \& Solowski (2019)\cite{Tran2019e} presented a
@@
 time step.
-\begin{align}
+\begin{equation}
   \label{eq:Tran-2019-GA-v}
-  & \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
+  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
   \sum^{N_n}_{I} N_{Ip}^{k}\ \left[(1 - \gamma)\ \vect{a}_I^{k} +
-    \gamma\ \vect{a}_I^{k+1} \right]\\
+    \gamma\ \vect{a}_I^{k+1} \right],\\
+\end{equation}
+\begin{equation}
 \label{eq:Tran-2019-GA-x}
-  & \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\
-    \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{v}_{I}^{k} + \Delta t^2
-    \sum^{N_n}_{I}N_{Ip}^{k} \left[ (\frac{1}{2} - \beta)\
-    \vec{a}_{I}^{k} + \beta\ \vec{a}_{I}^{k+1} \right]
-\end{align}
-and
+  \vect{x}_p^{k+1} = \vect{x}_p^{k} + 
+  \sum^{N_n}_{I}N_{Ip}^{k} \left[ \Delta t\ \vec{v}_{I}^{k}+ \Delta t^2\left( (\frac{1}{2} - \beta)\
+    \vec{a}_{I}^{k} + \beta\ \vec{a}_{I}^{k+1} \right) \right]
+\end{equation}
 \begin{equation}
@@
 \cite{Tran2019e}. But it can present the same numerical instabilities
-as in \eqref{eq:Sulsky-1994-UL-v-x} when nodal masses become infinitesimal.
+as in \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v} when nodal masses become infinitesimal.
 Here we propose a explicit predictor-corrector scheme for MPM based on the Newmark a-form with
@@
 \textbf{predictor} stage for both velocity and displacement.
-\begin{align}
-  \label{eq:Predictor-displacement}
-  &\vec{x}_p^{n+1} = \vec{x}_p^n + \Delta t\ \underbrace{\sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}}_{\vec{v}_p^{n}} + \frac{1}{2}\Delta t^2\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}}_{\vec{a}_p^{n}}\\
+\begin{equation}
+  \label{eq:5}
+  \vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
+  \underbrace{\sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\
+      N_{Ip}^k}{\tens{m}_I^k}}_{\vec{v}_p^{k}} + \frac{1}{2}\Delta
+  t^2\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\
+      N_{Ip}^k}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
+\end{equation}
+\begin{equation}
   \label{eq:Predictor-velocity}
-  &\vec{v}_p^{n+1} = \vec{v}_p^n + (1 - \gamma)\ \Delta t\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}}_{\vec{a}_p^{n}}        
-\end{align}
+  \vec{v}_p^{k+1} = \vec{v}_p^n + (1 - \gamma)\ \Delta t\
+  \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\
+      N_{Ip}^k}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
+\end{equation}
 
@@
 following way
-\begin{equation*}
+\begin{equation}
   \vec{v}_{p}^{k+1} = \vec{v}_{p}^{k+1} +
-  \gamma\ \Delta t\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k+1}\ N_{Ip}^{k+1}}{\tens{m}_I^{k+1}}}_{\vec{a}_p^{n+1}}  
-\end{equation*}
+  \gamma\ \Delta t\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k+1}\ N_{Ip}^{k+1}}{\tens{m}_I^{k+1}}}_{\vec{a}_p^{k+1}}  
+\end{equation}
 
@@
   \begin{align*}
-    &\vec{x}_p^{n+1} = \vec{x}_p^n + \Delta t\ \sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k} + \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}\\
-    &\vec{v}_p^{n+1} = \vec{v}_p^n + (1 - \gamma)\  \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}\Delta t        
+    &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\ \sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k} + \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k}\\
+    &\vec{v}_p^{k+1} = \vec{v}_p^n + (1 - \gamma)\  \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k}\Delta t        
   \end{align*}
@@
     mesh}:\\
-  Calculate the lumped mass matrix \eqref{eq:Lumped-mass-matrix},
-  and later the nodal momentum \eqref{eq:Nodal-momentum} of the
-  corrected values.
+  Calculate the lumped mass matrix $\tens{M}_{I}$,
+  and the nodal momentum $\vec{p}_{I}$ with the predicted values.
   \begin{equation*}
-    \tens{m}_{I} = \sum_{p}^{N_p} m_p\ N_{Ip}^{k+1},\quad
-    \vec{p}_{I}^{k+1} = \sum_{p}^{N_p} m_p\ \vec{v}_{p}^{k+1}\ N_{Ip}^{k+1},\quad
-    \vec{v}_{I}^{k+1} = \frac{\vec{p}_{I}^{k+1}}{\tens{m}_I}.
+    \tens{M}_{I} = \sum_{p}^{N_p} m_p\ N_{Ip}^{k+1},
+  \end{equation*}
+  \begin{equation*}
+    \vec{p}_{I}^{k+1} = \sum_{p}^{N_p} m_p\ \vec{v}_{p}^{k+1}\ N_{Ip}^{k+1},
   \end{equation*}
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \STATE \textbf{Impose essential boundary conditions over the nodal
+  \STATE \textbf{Impose essential boundary conditions over momentum nodal
     values}:\\
-  At the fixed boundary, set $\vec{p}_{I}^{k+1} = 0$.
+  At the fixed boundary, set $\vec{p}_{I}^{k+1} = 0$. Later, get the
+  nodal values of the velocity field $\vec{v}_{I}^{k+1} =
+  \frac{\vec{p}_{I}^{k+1}}{\tens{M}_{I}}$
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
   \STATE \textbf{Update the density field}:\\
-  Imposing the mass conservation in the total derivative expression of
-  the density field we reach to a suitable way of update it.
   \begin{equation*}
@@
   \STATE \textbf{Balance of forces calculation}:\\
-  Calculate the grid nodal internal forces $\vec{f}_{I}^{int,k+1}$, external
-  forces $\vec{f}_{I}^{ext,k+1}$, and the total grid nodal force $\vec{f}_{I}^{k+1} =
+  Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
   \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
-  \eqref{eq:nodal_internal_forces} and
-  \eqref{eq:nodal_external_forces} in the time step $k+1$. In the
+  \eqref{eq:nodal_internal_forces} and \eqref{eq:nodal_external_forces} in the time step $k+1$. In the
   grid node $I$ is fixed in one of the spatial dimensions, set it to
@@
   \STATE \textbf{Integrate the grid nodal momentum equation :}\\
-  Following the definition \eqref{eq:particle_balance_forces3}
-  calculate the nodal momentum $\vec{p}_{I}$ in $k+1$. 
+  Calculate the nodal momentum $\vec{p}_{I}$ in $k+1$. 
   \begin{equation*}
@@
 
-\begin{figure}\sidecaption
+\begin{figure*}\sidecaption
   \centering
@@
   \caption{MPM standard algorithm.}
-  \label{alg:PCE-algorithm}
-\end{figure}
+  \label{fig:MPM_algorithm}
+\end{figure*}
 
@@
 inference, which is the least biased possible on the given information
-\cite{Jaynes1957}.
-The basic idea of the shape functions based on such an estimate is to interpret the shape function $N_I(\vec{x})$ as the probability of $\vec{x}$ to obtain the value $\vec{x}_I$,  $I=1, \dots, n$.
-Here $n$ is the number of nodes in the domain.
+\cite{Jaynes1957}. The basic idea of the shape functions based on such
+an estimate is to interpret the shape function $N_I(\vec{x})$ as the
+probability of $\vec{x}$ to obtain the value $\vec{x}_I$,  $I=1,
+\dots, n$. Here $n$ is the number of nodes in the domain.
 Taking Shannon's entropy as the starting point:
@@
   \label{eq:Shannon-entropy}
-  H(p_1(\vec{x}),...,p_n(\vec{x})) = -\sum^{N_n}_{I=1}{p_I(\vec{x})\log p_I }
+  H(p_1(\vec{x}),\ldots,p_n(\vec{x})) = -\sum^{N_n}_{I=1}{p_I(\vec{x})\log p_I }
 \end{equation}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/MPM_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/MPM_Shape_Fun.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun}
     \label{fig:MPM_Shape_Fun}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/MPM_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/MPM_Shape_Fun_dx.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun_dx}
     \label{fig:MPM_Shape_Fun_dx}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/MPM_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/MPM_Shape_Fun_dy.pgf}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun_dy}
     \label{fig:MPM_Shape_Fun_dy}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_17.3_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun}
     \label{fig:LME_17.3_Shape_Fun}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_17.3_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun_dx}
     \label{fig:LME_17.3_Shape_Fun_dx}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_17.3_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun_dy}
     \label{fig:LME_17.3_Shape_Fun_dy}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/GIMP_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/GIMP_Shape_Fun.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun}
     \label{fig:GIMP_Shape_Fun}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/GIMP_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/GIMP_Shape_Fun_dx.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun_dx}
     \label{fig:GIMP_Shape_Fun_dx}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/GIMP_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/GIMP_Shape_Fun_dy.pgf}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun_dy}
     \label{fig:GIMP_Shape_Fun_dy}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_10.0_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun}
     \label{fig:LME_10.0_Shape_Fun}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_10.0_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun_dx}
     \label{fig:LME_10.0_Shape_Fun_dx}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_10.0_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun_dy}
     \label{fig:LME_10.0_Shape_Fun_dy}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_7.0_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun}
     \label{fig:LME_7.0_Shape_Fun}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_7.0_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun_dx}
     \label{fig:LME_7.0_Shape_Fun_dx}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_7.0_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun_dy}
     \label{fig:LME_7.0_Shape_Fun_dy}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_5.0_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun}
     \label{fig:LME_5.0_Shape_Fun}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_5.0_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun_dx}
     \label{fig:LME_5.0_Shape_Fun_dx}
@@
   \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_5.0_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun_dy}
     \label{fig:LME_5.0_Shape_Fun_dy}
@@
   \label{eq:System-stress-velocity-IV}
-  \Deriv{\Vector{\Re}}{t} + \Lambda \Deriv{\Vector{\Re}}{x} = \Vector{0}  
-\end{equation}
-which consists of $n$ uncoupled equations as $\Lambda$ is
+  \Deriv{\Vector{\Re}}{t} + \varLambda \Deriv{\Vector{\Re}}{x} = \Vector{0}  
+\end{equation}
+which consists of $n$ uncoupled equations as $\varLambda$ is
 diagonal matrix as we can see in \eqref{eq:Lambda-matrix}. Each of this
@@
 %%% End:
+
+\message{ !name(main.tex) !offset(-1152) }

### 2020-02-24 main.tex
Cambios 24-2-2020

@@
 
-a comparison between both methods employing \textit{max-ent}  shape
-function is performed in this paper
-
-as well a parametric study for the $\gamma$ parameter
-
-finally, conclusions and future research topics are exposed
-
-\section{Overview of the MPM}
-\label{sec:mpm-overview}
+The article is organized as follows. Section \ref{sec:Notation}
+briefly reviews the notation here employed. Next, Section \ref{sec:derivation-mpm}
+is devoted to present briefly the governing equations of the elastic
+problem, the variational formulation and the Galerkin procedure. In Section \ref{sec:epc-algor-mpm} an explicit predictor-corrector
+time integration scheme for the MPM is proposed. Section
+\ref{sec:local-max-ent} briefly reviews the local \textit{max-ent}
+basis functions here employed. In Section \ref{sec:dynamic-benchmark}
+a comparison between both methods MPM and OTM employing \textit{max-ent} shape
+function is performed as well a parametric study for the $\gamma$
+parameter. Finally, conclusions and future research topics are exposed
+in Section \ref{sec:conclusions}.
+
+\section{Notation}
+\label{sec:Notation}
+In what follows, we will adopt the following convention:
+\begin{table}[h]
+  \centering
+  \caption{Physical variables involved in the problem}
+  \label{tab:notation-table}
+  \begin{tabular}{c c c}
+    $\rho$ & Density field & Scalar \\
+    $\vect{a}$ & Acceleration field & First order tensor \\
+    $\vect{v}$ & Velocity field & First order tensor \\
+    $\vect{u}$ & Displacement field & Second order tensor \\
+    $\tens{\sigma}$ & Cauchy stress tensor & Second order tensor \\
+    $\tens{\varepsilon}$ & Cauchy strain tensor & Second order tensor \\
+    $\tens{D}$ & Constitutive tensor & Fourth order tensor\\
+  \end{tabular}
+\end{table}
+
+The subscript $p$ is used to define a particle variable. While the
+subscript $I$ is reserved in this notation for denoting nodal
+variables.
+
+The superscript $\psi$ involves a virtual magnitude.
+
+$\dot{\qed}$ 
+where $\Div{\qed}$ denotes the divergence operator.
+
+where $\GradS{\qed}$ denotes the symmetric part of the gradient
+operation.
+
+$\varGamma_d$  $\varGamma_n$
+\section{Derivation of the MPM}
+\label{sec:derivation-mpm}
 In this section, we provide an overview of the standard explicit MPM
@@
 
-\subsection{Derivation of the MPM}
-\label{sec:derivation-mpm}
-In the MPM approach a continuum is considered. The continuum behaviour
-can be described by a set of governing equations which are the balance
-of momentum equation ($\rho \vect{a} = \Div{\tens{\sigma}} + \rho
-\vect{b}$), the compatibility equation ($\dot{\tens{\varepsilon}} =
-\Grad{\vect{v}}$), the constitutive equation ($\dot{\tens{\sigma}} =
-\tens{D} \colon \dot{\tens{\varepsilon}}$), and the balance of mass equation
-($\frac{D \rho}{D t} = \dot{\rho} + \rho \Grad{\vect{v}}$). The balance of momentum can be
-formulated in weak form by introducing an arbitrary test function $\vec{\psi}$, yielding
+\subsection{Governing equations }
+\label{sec:governing-equations}
+In the MPM approach a continuum is considered. Let define a
+$\varOmega$ domain occupied by an elastic body, and $\partial
+\varOmega$ the boundary of the domain, where $\partial
+\varOmega = \Gamma_d \bigcup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n =
+\emptyset$. The behaviour of the continuum can be described by a set
+of governing equations which are (i) the balance of momentum equation
+\begin{equation}
+  \label{eq:Balance-momentum}
+\rho \vect{a} = \Div{\tens{\sigma}} + \rho \vect{b},
+\end{equation}
+next (ii) the compatibility equation with ensure that the velocity
+field is compatible with the Cauchy strain field,
+\begin{equation}
+  \label{eq:Compatibility-equation}
+  \dot{\tens{\varepsilon}} = \GradS{\vect{v}} = \frac{1}{2}\left(
+    \Grad{\vect{v}} +  \GradT{\vect{v}} \right),
+\end{equation}
+later (iii) the constitutive equation, which relates the rate of Cauchy strain
+tensor with the rate of Cauchy stress tensor,
+\begin{equation}
+  \label{eq:Constitutive-equation}
+\dot{\tens{\sigma}} = \tens{D} \colon \dot{\tens{\varepsilon}},
+\end{equation}
+finally we introduce (iv) the mass conservation, which if obtained by
+setting to zero the total derivative of the density field,
+\begin{equation}
+  \label{eq:Rho-material-derivative}
+  \frac{D \rho}{D t} = \dot{\rho} + \rho \Grad{\vect{v}} = 0.
+\end{equation}
+
+\subsection{Variational formulation}
+\label{sec:variational-formulation}
+To write the variational statement of the problem, let us define a
+virtual velocity field such that
+\begin{equation}
+  \label{eq:Hilbert-space}
+  \vect{v}^{\psi} \in \mathcal{H}^1_0(\Omega) = \{ \vect{v}^{\psi} \in
+  \mathcal{H}^1 \mid \vect{v}^{\psi} = \vect{0}\ \text{on}\ \Gamma_d \}.
+\end{equation}
+And which satisfies that the Cauchy sequences are convergent in $\varOmega$
+\begin{equation}
+  \label{eq:cauchy-secuence}
+  \Integral{3}{\vect{v}^{\psi}} < \infty\ \quad\text{and}\quad \Integral{3}{\Grad{\vect{v}^{\psi}}} < \infty
+\end{equation}
+The principle of virtual work states that the equilibrium solution to
+the boundary value problem of elasticity is the function $\vect{v} \in
+\mathcal{H}^1_0$ such that, for $\vect{v}^{\psi} \in
+\mathcal{H}^1_0$, the following holds:
 \begin{equation}
   \label{eq:BalanceMomentum_wf}
-  \Integral{3}{\rho\ \Deriv{\vec{v}}{t}\ \vec{\psi}} = -
-  \Integral{3}{\tens{\sigma} \colon \Grad{\vec{\psi}}} +
-  \Integral{2}{\vec{t}\ \vec{\psi}} + \Integral{3}{
-  \rho\ \vec{b}\ \vec{\psi}}.
+  \Integral{3}{\rho\ \left( \Deriv{\vec{v}}{t}\ - \vec{b} \right) \cdot \vec{v}^{\psi}} =
+  \Integral{2}{\vec{t}\ \cdot \vec{v}^{\psi}} - \Integral{3}{\tens{\sigma} \cdot
+    \tens{\varepsilon}^{\psi}},
 \end{equation}\\
-
-In order to arrive to a finite set of equations, the continuum domain
-$\Omega$ is discretized with a finite sum of particles (material points), each one 
-represent a part of the domain $\Omega_p$ with $p = 1,2\ldots ,N_p$
-where $N_p$ is the number of particles. The index $p$ is
-used for the particles, while the index $I$ is reserved in this
-notation for denoting grid nodes. The material point $\vec{x}_p$ is
-defined at the centroid of $\Omega_p$. Further, a computational grid
-is formed of a finite set of grid points with coordinates $\vec{x}_I\
-, I = 1,2\ldots ,N_n$, where $N_n$ is the number of grid nodes. Each material point is assigned with initial values of position,
-velocity, mass, volume and stress denoted by $\vec{x}_p$,  $\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$. The problem is then integrated using a discrete number of time
-steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
-is the total number of time steps.  So employing the definition of the
-material integral, individual terms of \eqref{eq:BalanceMomentum_wf}
-are solved as follows. 
+therefore (\ref{eq:BalanceMomentum_wf}) is the balance of momentum formulated in
+its weak form.
+
+\subsection{Galerkin procedure}
+\label{sec:Galerkin-procedure}
+In order to arrive to a finite set of equations, in contrast with the
+FEM, in the MPM a double discretization procedure is performed as we will
+describe here below. First, the continuum domain
+$\Omega$ is discretized with a finite sum of material points (in the
+following particles), each one
+represent a part of the discretized domain $\varOmega_p \subset
+\varOmega$ with $p = 1,2\ldots ,N_p$ where $N_p$ is the number of
+particles. The material point $\vec{x}_p$ is defined at the centroid
+of each $\Omega_p$, figure \ref{fig:MPM-discretization}.
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Discretization_MPM}
+  }
+  \caption{MPM discretization.}
+  \label{fig:MPM-discretization}
+\end{figure}
+
+Each material point is assigned with initial values of position,
+velocity, mass, volume and stress denoted by $\vec{x}_p$,
+$\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$, but also the
+virtual field $\vect{v}^{\psi}_{p}$. So employing the definition of the
+material integral, where we recover the Riemann integral definition as
+an addition  of a finite set of points. Therefore individual terms in
+\eqref{eq:BalanceMomentum_wf} are solved as follows. 
 \begin{itemize}
@@
     \Integral{3}{\tens{\sigma}\ \colon \Grad{\vec{\psi}}} = \sum^{N_p}_{p}
-   \tens{\sigma}_{p}\ \Grad{\tens{\psi}_{p}}\ V_p.
+   \tens{\sigma}_{p}\ \colon \Grad{\tens{\psi}_{p}}\ V_p.
   \end{equation}\\
@@
 \end{itemize}
-where $h$ is the thickness of the continuum in a 2D case. Introducing \eqref{eq:particle_acceleration_forces},
+where $h$ is the thickness of the continuum in a 2D case. Here is
+where the second discretization procedure appears. A background mesh
+composed by a finite set of grid points with coordinates $\vec{x}_I\
+, I = 1,2\ldots ,N_n$, is generated. Where $N_n$ is the number of grid
+nodes. This mesh is employed as a support to compute gradients and divergences.
+
+Introducing \eqref{eq:particle_acceleration_forces},
 \eqref{eq:particle_internal_forces}, \eqref{eq:particle_body_forces}, 
-and \eqref{eq:particle_load_forces} in \eqref{eq:BalanceMomentum_wf}
+and \eqref{eq:particle_load_forces} in \eqref{eq:BalanceMomentum_wf},
+and approximating the real and virtual velocity  field of the particle
+$p$ as
+\begin{equation}
+  \label{eq:Approx-velocity-mesh}
+  \vec{v}_{p} = \sum^{Nn}_I N_I(\vec{x}_p)\cdot \vect{v}_I
+  \quad \text{and} \quad \vec{v}^{\psi}_{p} = \sum^{Nn}_I N_I(\vec{x}_p)\cdot \vect{1},
+\end{equation}
 we reach to the particle balance of forces of the continuum,
-\begin{equation}
-  \label{eq:particle_balance_forces2}
-  \sum^{N_p}_{p}\vec{\psi}_{p}\ m_p\ \dot{\vec{v}}_{p} = \sum^{N_p}_{p}
-  \vec{\psi}_{p}\ m_p\ \vec{b}_{p} + \sum^{N_p}_{p}
-  \vec{\psi}_{p}\ m_p\ h^{-1}\ \bar{\vec{t}}^s_{p} -
-  \sum^{N_p}_{p} \Grad{\vec{\psi}_{p}}\ \frac{m_p}{\rho_p}\
-  \tens{\sigma}_{p}.
-\end{equation}\\
-
-Approximating the virtual displacement of the particle $\vec{\psi}_{p}$
-using a suitable approximation scheme we get \eqref{eq:VirtualDisplacementParticle}.
-\begin{equation}
-  \label{eq:VirtualDisplacementParticle}
-  \vec{\psi}_{p} = N_{Ip}\cdot \vect{1} = N_{Ip},
-\end{equation}
-where $N_{Ip} = N_I(\vec{x}_p)$ it is the nodal value of the shape
-function evaluated in the material point coordinates denoted by $\vec{x}_p$. Substituting \eqref{eq:VirtualDisplacementParticle} in
-\eqref{eq:particle_balance_forces2} we get :
 \begin{equation}
@@
   \tens{m}_{IJ} =
-  \sum^{Np}_{p} N_{Ip} m_p N_{Jp},
-\end{equation}
-and internal and external forces are computed as follows,
+  \sum^{Np}_{p} N_{Ip} m_p N_{Jp}.
+\end{equation}
+To improve the computational efficiency and stability, the nodal mass matrix
+\eqref{eq:particle_nod_mass} can be substituted by the lumped mass
+matrix $\tens{m}_{IJ}^{lumped}$.
+Later, internal and external forces are computed as follows,
 \begin{equation}
   \label{eq:nodal_internal_forces}
-  \vec{f}_{I}^{int} = - \sum^{N_p}_{p} \Grad{N_{Ip}}
-  \tens{\sigma}_{p} \frac{m_p}{\rho_p}
+  \vec{f}_{I}^{int} = - \sum^{N_p}_{p} \tens{\sigma}_{p} \colon \Grad{N_{Ip}} \frac{m_p}{\rho_p}
 \end{equation}
@@
   \label{eq:nodal_external_forces}
-  \vec{f}_{I}^{ext} = \sum^{N_p}_{p} N_{Ip} m_p \vec{b}_{p} + \sum^{N_p}_{p}
-  N_{Ip} m_p h^{-1} \vec{t}^s_{p}
+  \vec{f}_{I}^{ext} = \sum^{N_p}_{p} \vec{b}_{p} N_{Ip} m_p  + \sum^{N_p}_{p}
+  N_{Ip} \vec{t}^s_{p} m_p h^{-1} 
 \end{equation}
@@
     \tens{\varepsilon}_{p}}{\Delta t} =
-  \frac{1}{2}\left[\Grad{N_{Ip}}\ \vec{v}_{I} + \Grad{N_{Ip}}^T\
-    \vec{v}_{I}\right].
-\end{equation}
-Later, imposing $\frac{D \rho}{D t} = 0$, we ensures the mass
+  \frac{1}{2} \sum^{Nn}_I \left[\Grad{N_{Ip}}\ \otimes \vec{v}_{I} + \vec{v}_{I} \otimes
+    \Grad{N_{Ip}}\ \right].
+\end{equation}
+Next, imposing $\frac{D \rho}{D t} = 0$, we ensures the mass
 conservation and update the density field.
@@
 
-To improve the computational efficiency and stability, the nodal mass matrix
-\eqref{eq:particle_nod_mass} can be substituted by the lumped mass
-matrix $\tens{m}_I$. Therefore the nodal balance of momentum equation \eqref{eq:particle_balance_forces3} can be simplified to
-\begin{equation}
-  \label{eq:SimplyNodalMomentum}
-  \dot{\vec{p}}_{I} = \tens{m}_I\ \vec{a}_{I} = \vec{f}_{I}^{int} + \vec{f}_{I}^{ext}.
-\end{equation}
-To solve the equation \eqref{eq:SimplyNodalMomentum}, a second order
-temporal integration scheme is required. The next step is to advect
-the particles solving,
+Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order
+temporal integration scheme is required. Therefore, time is
+discretized in to a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
+is the total number of time steps. Once the nodal equilibrium equation it is solved, the values in the nodes are
+interpolated back in to the particles and each particle it is advected
+to the new position,
 \begin{equation}
@@
 \end{equation}
-To solve this equations, the forward Euler algorithm is the common
-choose for this in the MPM literature. In next lines, a complete
-description of the standard MPM algorithm will be described.
+In the MPM literature, this equations
+(\ref{eq:particle_balance_forces3}) and (\ref{eq:Updated_Lagrangian}),
+are solved with a forward Euler algorithm. In the next section, an
+alternative time integration scheme based on the Newmark a-form is proposed.
 
@@
 
-To solve equations \eqref{eq:SimplyNodalMomentum} and
-\eqref{eq:Updated_Lagrangian}, a time integration scheme is
-required. It has been described in detail by many researchers
+The time integration scheme of the MPM has been described in detail by many researchers
 \cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and summarized
@@
 \begin{equation}
-  \label{eq:Sulsky-1994-UL-v-x}
+  \label{eq:Sulsky-1994-UL-v}
   \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
-  \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{a}_{I}^{k},\quad and\quad
+  \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{a}_{I}^{k}
+\end{equation}
+\begin{equation}
+  \label{eq:Sulsky-1994-UL-x}
   \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{v}_{I}^{k}.
 \end{equation}
-
-However, in Andersen (2009)\cite{thesis_Andersen_2009} this
+However, as Andersen (2009)\cite{thesis_Andersen_2009} point out, this
 algorithm has been shown to be numerically unstable due to that
@@
 \begin{algorithm}
+  \label{alg:PCE-algorithm}
   \floatname{algorithm}{Algorithm}
@@
   \caption{Explicit scheme : Newmark central difference}
-\label{alg:Second_step_MPM_2STG}
   \begin{algorithmic}[1]
@@
     \begin{align*}
-    &\vec{x}_p^{n+1} = \vec{x}_p^n + \Delta t\ \sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k} + \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}\\
-    &\vec{v}_p^{n+1} = \vec{v}_p^n + (1 - \gamma)\  \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{m}_I^k}\Delta t        
+      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\ \sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k} + \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k}\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + (1 - \gamma)\  \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k}\Delta t        
     \end{align*}
@@
       mesh}:\\
-  Calculate the lumped mass matrix \eqref{eq:Lumped-mass-matrix},
-  and later the nodal momentum \eqref{eq:Nodal-momentum} of the
-  corrected values.
+    Calculate the lumped mass matrix $\tens{M}_{I}$,
+    and the nodal momentum $\vec{p}_{I}$ with the predicted values.
     \begin{equation*}
-    \tens{m}_{I} = \sum_{p}^{N_p} m_p\ N_{Ip}^{k+1},\quad
-    \vec{p}_{I}^{k+1} = \sum_{p}^{N_p} m_p\ \vec{v}_{p}^{k+1}\ N_{Ip}^{k+1},\quad
-    \vec{v}_{I}^{k+1} = \frac{\vec{p}_{I}^{k+1}}{\tens{m}_I}.
+      \tens{M}_{I} = \sum_{p}^{N_p} m_p\ N_{Ip}^{k+1},
+    \end{equation*}
+    \begin{equation*}
+      \vec{p}_{I}^{k+1} = \sum_{p}^{N_p} m_p\ \vec{v}_{p}^{k+1}\ N_{Ip}^{k+1},
     \end{equation*}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \STATE \textbf{Impose essential boundary conditions over the nodal
+    \STATE \textbf{Impose essential boundary conditions over momentum nodal
       values}:\\
-  At the fixed boundary, set $\vec{p}_{I}^{k+1} = 0$.
+    At the fixed boundary, set $\vec{p}_{I}^{k+1} = 0$. Later, get the
+    nodal values of the velocity field $\vec{v}_{I}^{k+1} =
+    \frac{\vec{p}_{I}^{k+1}}{\tens{M}_{I}}$
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
     \STATE \textbf{Update the density field}:\\
-  Imposing the mass conservation in the total derivative expression of
-  the density field we reach to a suitable way of update it.
     \begin{equation*}
@@
     \STATE \textbf{Balance of forces calculation}:\\
-  Calculate the grid nodal internal forces $\vec{f}_{I}^{int,k+1}$, external
-  forces $\vec{f}_{I}^{ext,k+1}$, and the total grid nodal force $\vec{f}_{I}^{k+1} =
+    Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
     \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
-  \eqref{eq:nodal_internal_forces} and
-  \eqref{eq:nodal_external_forces} in the time step $k+1$. In the
+    \eqref{eq:nodal_internal_forces} and \eqref{eq:nodal_external_forces} in the time step $k+1$. In the
     grid node $I$ is fixed in one of the spatial dimensions, set it to
@@
     \STATE \textbf{Integrate the grid nodal momentum equation :}\\
-  Following the definition \eqref{eq:particle_balance_forces3}
-  calculate the nodal momentum $\vec{p}_{I}$ in $k+1$. 
+    Calculate the nodal momentum $\vec{p}_{I}$ in $k+1$. 
     \begin{equation*}
@@
   \caption{MPM standard algorithm.}
-  \label{alg:PCE-algorithm}
+  \label{fig:MPM_algorithm}
 \end{figure}
@@
 interpolation technique. A direct consequence of this, is that it is
-possible to adopt a width range of shape functions and interpolation techniques. The MPM has been
+possible to adopt a width range of them. The MPM has been
 successfully applied to a wide range of problems due to its ability to
@@
 first-order consistency. The least-biased approximation scheme is given by
-\begin{eqnarray}
-  \text{(ME)} \hspace{0.2cm} \text{Maximize} \hspace{0.1cm}H(p) &=&  -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I } \nonumber \\
-  \text{subject to} \hspace{0.5cm} p_I &\ge& 0, \hspace{0.5cm} \text{I=1, ..., n} \nonumber \\
-  \sum_{I=1}^{N_n}{p_I} &=& 1 \nonumber \\
-  \sum_{I=1}^{N_n}{p_I \vec{x}_I} &=& \vec{x} \nonumber 
-\end{eqnarray}
+\begin{align*}
+  \text{(LME)} \hspace{0.15cm} \text{Maximize} \hspace{0.15cm} &H(p) = -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I } \nonumber \\
+  \text{subject to} \hspace{0.15cm} &p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \nonumber \\
+  &\sum_{I=1}^{N_n}{p_I} = 1 \nonumber \\
+  &\sum_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \nonumber 
+\end{align*}
 The local max-ent approximation schemes (LME) as a Pareto set,
 defined by \cite{Arroyo2006} is as follows 
-\begin{eqnarray}
-  \text{(LME)}_{\beta} \hspace{0.5cm} \text{For fixed} \hspace{0.2cm} \vec{x} \hspace{0.2cm} \text{minimise}  \nonumber \\
-  \hspace{0.5cm}f_{\beta}(\vec{x}, p) &=& \beta H(\vec{x},p) - H(p)  \nonumber  \\
-  \text{subject to} \hspace{0.5cm} p_I &\ge& 0, \hspace{0.2cm} \text{I=1, ..., n}  \nonumber \\
-  \sum_{I=1}^{N_n}{p_I} &=& 1  \nonumber \\
-  \sum_{I=1}^{N_n}{p_I \, \vec{x}_I} &=& \vec{x}    \nonumber 
-\end{eqnarray}
+\begin{align*}
+  \text{(LME)}_{\beta} \hspace{0.15cm} \text{For fixed} \hspace{0.15cm}
+  \vec{x} \hspace{0.15cm} \text{minimise}  \nonumber \hspace{0.15cm} &f_{\beta}(\vec{x}, p) = \beta H(\vec{x},p) - H(p) \\
+  \text{subject to} \hspace{0.15cm} &p_I \ge 0, \hspace{0.2cm} \text{I=1, ..., n}  \\
+                                                                   &\sum_{I=1}^{N_n}{p_I} = 1 \\
+                                                                   &\sum_{I=1}^{N_n}{p_I \, \vec{x}_I} = \vec{x}
+\end{align*}
 for $\beta \in (0,\infty)$ is Pareto optimal. The unique solution of
@@
 \end{eqnarray}
-Note that, the objective of the above procedure is to find the $\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. 
-The traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27}) to calculate small increments of $\partial\vec{\lambda}$ in a Newton-Raphson approach.
-
-Similar to alternative non-polynomial meshfree basis functions, the LME approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem.
-Due to the FE-compatibility, the LME shape function is degenerated to linear finite element shape function if $d+1$ neighbouring nodes are chosen as the support.
-The support size of LME shape functions may be controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$ (e.g.
-two dimensional example shown in Fig.
-\ref{fig:LME_MPM})\cite{Arroyo2006}.
-Since  $p_I$  is defined in  the entire domain, in practice,  the function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance, 10$^{-6}$, for example,  would ensure a reasonable range of neighbours, see \cite{Arroyo2006} for details.
-This  tolerance defines the limit values of the influence radius and   is used thereafter to find the neighbour nodes of a given integration point.
+Note that, the objective of the above procedure is to find the
+$\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. The
+traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27})
+to calculate small increments of $\partial\vec{\lambda}$ in a
+Newton-Raphson approach. 
+Similar to alternative non-polynomial meshfree basis functions, the
+LME approximation scheme requires more than $d+1$ nodes to determine
+the values of the shape functions as well as their derivatives at any
+point in the convex hull of the nodal set, where $d$ is the dimension
+of the problem. Due to the FE-compatibility, the LME shape function is
+degenerated to linear finite element shape function if $d+1$
+neighbouring nodes are chosen as the support. The support size of LME
+shape functions may be controlled by adjusting a dimensionless
+parameter, $\gamma=\beta h^2$ (e.g. two dimensional example shown in
+figure. \ref{fig:LME_MPM})\cite{Arroyo2006}.
 
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/MPM_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/MPM_Shape_Fun.png}
-    % }
+  \subfloat[Piecewise linear (Q4).]{
+    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun}
+    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun_dx}
+    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun_dy}
     \label{fig:MPM_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/MPM_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/MPM_Shape_Fun_dx.png}
-    % }
-    \label{fig:MPM_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/MPM_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/MPM_Shape_Fun_dy.pgf}
-    % }
-    \label{fig:MPM_Shape_Fun_dy}
   }
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_17.3_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun.png}
-    % }
+  \subfloat[Local \textit{max-ent} $\gamma=17$.]{
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun}
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun_dx}
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun_dy}
     \label{fig:LME_17.3_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_17.3_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
-    \label{fig:LME_17.3_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_17.3_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
-    \label{fig:LME_17.3_Shape_Fun_dy}
   }
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/GIMP_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/GIMP_Shape_Fun.png}
-    % }
+  \subfloat[Uniform generalized interpolated material point.]{
+    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun}
+    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun_dx}
+    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun_dy}
     \label{fig:GIMP_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/GIMP_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/GIMP_Shape_Fun_dx.png}
-    % }
-    \label{fig:GIMP_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/GIMP_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/GIMP_Shape_Fun_dy.pgf}
-    % }
-    \label{fig:GIMP_Shape_Fun_dy}
   }
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_10.0_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun.png}
-    % }
+  \subfloat[Local \textit{max-ent} $\gamma=10$.]{
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun}
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun_dx}
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun_dy}
     \label{fig:LME_10.0_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_10.0_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
-    \label{fig:LME_10.0_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_10.0_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
-    \label{fig:LME_10.0_Shape_Fun_dy}
   }
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_7.0_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun.png}
-    % }
+  \subfloat[Local \textit{max-ent} $\gamma=7$.]{
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun}
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun_dx}
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun_dy}
     \label{fig:LME_7.0_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_7.0_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
-    \label{fig:LME_7.0_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_7.0_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
-    \label{fig:LME_7.0_Shape_Fun_dy}
   }
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_5.0_Shape_Fun.png}
-    % \resizebox{0.3\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun.png}
-    % }
+  \subfloat[Local \textit{max-ent} $\gamma=5$.]{
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun}
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun_dx}
+    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun_dy}
     \label{fig:LME_5.0_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_5.0_Shape_Fun_dx.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
-    \label{fig:LME_5.0_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.35\columnwidth]{Figures/LME_5.0_Shape_Fun_dy.png}
-    % \resizebox{0.54\columnwidth}{!}{%
-    % \input{Figures/LME_17.3_Shape_Fun_dx.png}
-    % }
-    \label{fig:LME_5.0_Shape_Fun_dy}
   }
@@
 \end{figure}
+
+Since  $p_I$  is defined in the entire domain, in practice, the
+function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
+10$^{-6}$, for example,  would ensure a reasonable range of
+neighbours, see \cite{Arroyo2006} for details. This tolerance defines
+the limit values of the influence radius and is used thereafter to
+find the neighbour nodes of a given integration point.
+In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
+influence area of the shape function is controlled by the Euclidean
+norm, therefore the search area is geometrically a circle in 2D, or a
+sphere in 3D. Building upon the idea of anisotropic shape functions,
+\cite{Kochmann2019} introduced an enhanced version of the original
+local max-ent scheme, which uses an anisotropic support to deal with
+tensile inestability. Nonetheless this is out of the scope of the
+present document but will be incorporated in future research.
 
@@
 
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-MPM-uGIMP-LME}
+\end{figure}
+
 \subsection{MPM versus OTM}
@@
 \label{sec:conclusions}
-
-Building upon the idea of anisotropic shape functions
-\cite{Arroyo2006}, \cite{Kochmann2019} introduced an enhanced version of the
-original local max-ent scheme, which uses an anisotropic support to
-deal with tensile inestability.
 

### 2020-02-25 main.tex
Cambios 25-2-2020

@@
 simulate dynamic problems. However, in the simulations made with the
-originalMPM, there are numerical noises \cite{Tran2019e} when it is faced to solve
+original MPM, there are numerical noises \cite{Tran2019e} when it is faced to solve
 classic dynamic benchmarks like the one proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995}.
+(1995)\cite{Dyka1995}. These numerical inaccuracies give rise to the
+development of other interpolation techniques to overcome this limitation. Some of this
+alternatives techniques are the generalized interpolation material
+point method (GIMP) Bardenhagen \& Kober (2004)\cite{Bardenhagen2004},
+the dual domain material point method (DDMP) Zhang {\it et al.}
+(2011)\cite{Zhang2011a}, the B-Spline MPM Tran {\it et al.}
+(2019)\cite{Tran2019a}, the Conservative Taylor Least
+Squares reconstruction Wobbes {\it et al.}
+(2018)\cite{E_Wobbes_2018} and more recently the local
+maximum-entropy (or local \textit{max-ent}) shape function first
+introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} has been tested
+under the MPM framework by Wobbes {\it et al.}
+(2020)\cite{Wobbes2020}. Alternatively to change the spatial
+interpolation technique other researchers have overcome the well known
+wiggle that tends to appear in this dynamic simulations by filtering
+high-frequencies with an alternative time integration scheme, the
+implicit GIMP (iGIMP) Charlton {\it et al.}
+(2017)\nocite{Charlton2017} or the generalised-$\alpha$ scheme for the
+MPM proposed by Tran \& Solowski (2019)\nocite{Tran2019e}.
 
 The aim of this paper is to mitigate this spurious oscillations by the
-employ of the maximum-entropy (or local \textit{max-ent}) shape
-function under the MPM framework. First introduced by
-\cite{Arroyo2006}, it belongs to the class of convex 
+employ of a suitable combination of the maximum-entropy (or local
+\textit{max-ent}) shape functions, and the proposal of a explicit
+predictor-corrector scheme. Local \textit{max-ent} shape functions was
+first introduced by \cite{Arroyo2006}, it belongs to the class of convex 
 approximation schemes and provides a seamless transition between
@@
 meshfree algorithms. First of all, they are entirely defined by the
-nodal set and the domain of analysis. They are also non-negative, satisfy the partition of unity
-property, and provide an exact approximation for affine functions \cite{Arroyo2006}.
-
-This approximation scheme has been proof to have a good performance
-under the dynamic regime by other researchers like Navas {\it et al.}
+nodal set and the domain of analysis. They are also non-negative,
+satisfy the partition of unity property, and provide an exact
+approximation for affine functions \cite{Arroyo2006}. This
+approximation scheme has been proof to have a good performance under
+the dynamic regime by other researchers like Navas {\it et al.}
 (2018)\cite{Navas2018a} and Li {\it et al.} (2012)\cite{Li2012} for
-Optimal Transportation Meshfree (\textbf{OTM}) method.
+Optimal Transportation Meshfree (\textbf{OTM}) method. On the other
+hand, the time integration scheme here proposed is an accommodation of
+the Newmark a-form with $\gamma = 0.5$ and $\beta = 0$ which is the central difference
+explicit (CD). We have choose this method among other suitable
+alternatives as Wilson {\it et al.} (1972)\nocite{Wilson1972} or Chung
+\& Hulbert (1993)\nocite{Geranlized_alpha_1993} because it simplicity
+and it good performance dealing with solids dynamics problems like those
+presented in \cite{Navas2018a}.
 
@@
 
-\section{Notation}
+\section{Brief note concerning the notation}
 \label{sec:Notation}
-In what follows, we will adopt the following convention:
-\begin{table}[h]
+In what follows, we will adopt the following convention. All the
+physical variables involved in this problem are collected in Table
+\ref{tab:notation-table}.
+
+\begin{table}
   \centering
@@
 
-The subscript $p$ is used to define a particle variable. While the
-subscript $I$ is reserved in this notation for denoting nodal
-variables.
-
-The superscript $\psi$ involves a virtual magnitude.
-
-$\dot{\qed}$ 
-where $\Div{\qed}$ denotes the divergence operator.
-
-where $\GradS{\qed}$ denotes the symmetric part of the gradient
-operation.
-
-$\varGamma_d$  $\varGamma_n$
+Three kind of subscript or superscript are used within paper. The
+subscript $\qed_p$ is used to define a particle variable. While the
+subscript $\qed_I$ is reserved in this notation for denoting nodal
+variables. And finally, the superscript $\qed^{\psi}$ involves a virtual
+magnitude. For the operators, the convention is : $\dot{\qed}$ and
+$\ddot{\qed}$ for the first and second time derivative, $\qued \otimes
+\qued$ means the dyadic operator, $(\cdot)$ and $(\colon)$ means the first
+and second contraction of a tensor, $\Div{\qed}$
+denotes the divergence operator, and finally $\Grad{\qed}$ and
+$\GradS{\qed}$ denotes the gradient and its symmetric part.
+
 \section{Derivation of the MPM}
@@
 \varOmega = \Gamma_d \bigcup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n =
-\emptyset$. The behaviour of the continuum can be described by a set
-of governing equations which are (i) the balance of momentum equation
+\emptyset$. Note that $\varGamma_d$ is reserved for Dirichlet boundary
+conditions, and  $\varGamma_n$ for the Neumann. The behaviour of the
+continuum can be described by a set of governing equations which are
+(i) the balance of momentum equation
 \begin{equation}
@@
   \label{eq:Rho-material-derivative}
-  \frac{D \rho}{D t} = \dot{\rho} + \rho \Grad{\vect{v}} = 0.
+  \frac{D \rho}{D t} = \dot{\rho} + \rho \Div\vect{v}} = 0.
 \end{equation}
@@
   \centering
-  \resizebox{\hsize}{!}{
+  \resizebox{0.9\hsize}{!}{
     \includegraphics[width=\textwidth]{./Figures/Discretization_MPM}
@@
     \label{eq:particle_internal_forces}
-    \Integral{3}{\tens{\sigma}\ \colon \Grad{\vec{\psi}}} = \sum^{N_p}_{p}
-   \tens{\sigma}_{p}\ \colon \Grad{\tens{\psi}_{p}}\ V_p.
+    \Integral{3}{\tens{\sigma}\ \cdot \Grad{\vec{\psi}}} = \sum^{N_p}_{p}
+   \tens{\sigma}_{p}\ \cdot \Grad{\tens{\psi}_{p}}\ V_p.
   \end{equation}\\
@@
   \label{eq:Approx-velocity-mesh}
-  \vec{v}_{p} = \sum^{Nn}_I N_I(\vec{x}_p)\cdot \vect{v}_I
-  \quad \text{and} \quad \vec{v}^{\psi}_{p} = \sum^{Nn}_I N_I(\vec{x}_p)\cdot \vect{1},
+  \vec{v}_{p} = \sum^{Nn}_I N_I(\vec{x}_p) \vect{v}_I
+  \quad \text{and} \quad \vec{v}^{\psi}_{p} = \sum^{Nn}_I N_I(\vec{x}_p) \vect{1},
 \end{equation}
@@
   \label{eq:nodal_internal_forces}
-  \vec{f}_{I}^{int} = - \sum^{N_p}_{p} \tens{\sigma}_{p} \colon \Grad{N_{Ip}} \frac{m_p}{\rho_p}
+  \vec{f}_{I}^{int} = - \sum^{N_p}_{p} \tens{\sigma}_{p} \cdot \Grad{N_{Ip}} \frac{m_p}{\rho_p}
 \end{equation}
@@
   \label{eq:nodal_external_forces}
-  \vec{f}_{I}^{ext} = \sum^{N_p}_{p} \vec{b}_{p} N_{Ip} m_p  + \sum^{N_p}_{p}
+  \vec{f}_{I}^{ext} = \sum^{N_p}_{p} N_{Ip} \vec{b}_{p} m_p  + \sum^{N_p}_{p}
   N_{Ip} \vec{t}^s_{p} m_p h^{-1} 
@@
   \label{eq:Updated_Lagrangian}
-  \dot{\vec{v}}_p = \sum^{N_n}_{I}\vec{a}_{I}\ N_{Ip},\quad and\quad \dot{\vec{x}}_{p} = \sum^{N_n}_{I}\vec{v}_{I}\ N_{Ip}  
+  \dot{\vec{v}}_p = \sum^{N_n}_{I}N_{Ip}\ \vec{a}_{I},\quad and\quad
+  \dot{\vec{x}}_{p} = \sum^{N_n}_{I}N_{Ip}\ \vec{v}_{I}  
 \end{equation}
@@
   \vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
-  \underbrace{\sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\
-      N_{Ip}^k}{\tens{m}_I^k}}_{\vec{v}_p^{k}} + \frac{1}{2}\Delta
-  t^2\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\
-      N_{Ip}^k}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
+  \underbrace{\sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{p}_{I}^{k}}{\tens{m}_I^k}}_{\vec{v}_p^{k}} + \frac{1}{2}\Delta
+  t^2\ \underbrace{\sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{f}_{I}^{k}}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
 \end{equation}
@@
   \vec{v}_p^{k+1} = \vec{v}_p^n + (1 - \gamma)\ \Delta t\
-  \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\
-      N_{Ip}^k}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
+  \underbrace{\sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{f}_{I}^{k}}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
 \end{equation}
@@
   \vec{v}_{p}^{k+1} = \vec{v}_{p}^{k+1} +
-  \gamma\ \Delta t\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k+1}\ N_{Ip}^{k+1}}{\tens{m}_I^{k+1}}}_{\vec{a}_p^{k+1}}  
+  \gamma\ \Delta t\ \underbrace{\sum^{N_n}_{I}\frac{N_{Ip}^{k+1}\ \vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}}_{\vec{a}_p^{k+1}}  
 \end{equation}
@@
     \begin{align*}
-      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\ \sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k} + \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k}\\
-      &\vec{v}_p^{k+1} = \vec{v}_p^n + (1 - \gamma)\  \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k}\Delta t        
+      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
+        \sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{p}_{I}^{k}}{\tens{M}_I^k} +
+        \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{f}_{I}^{k}}{\tens{M}_I^k}\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + (1 - \gamma)\
+        \sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{f}_{I}^{k}}{\tens{M}_I^k}\Delta t        
     \end{align*}
@@
     \begin{equation*}
-      \tens{M}_{I} = \sum_{p}^{N_p} m_p\ N_{Ip}^{k+1},
+      \tens{M}_{I} = \sum_{p}^{N_p}N_{Ip}^{k+1}\ m_p,
     \end{equation*}
     \begin{equation*}
-      \vec{p}_{I}^{k+1} = \sum_{p}^{N_p} m_p\ \vec{v}_{p}^{k+1}\ N_{Ip}^{k+1},
+      \vec{p}_{I}^{k+1} = \sum_{p}^{N_p} N_{Ip}^{k+1}\ m_p\ \vec{v}_{p}^{k+1},
     \end{equation*}
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Explicit Newmark Predictor}:
+    \STATE \textbf{Explicit Newmark Corrector}:
     \begin{equation*}
       \vec{v}_{p}^{k+1} = \vec{v}_{p}^{k+1} +
-      \gamma \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k+1}\ N_{Ip}^{k+1}}{\tens{m}_I^{k+1}}\Delta t  
+      \gamma \sum^{N_n}_{I}\frac{N_{Ip}^{k+1}\ \vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}\Delta t  
     \end{equation*}
@@
 original MPM, there are numerical noises when particles crossing
-the cell boundaries. These numerical inaccuracies give rise to the
-development of other interpolation techniques. Some of this
-alternatives techniques are the generalized interpolation material
-point method (GIMP) Bardenhagen \& Kober (2004)\cite{Bardenhagen2004},
-the dual domain material point method (DDMP) Zhang {\it et al.}
-(2011)\cite{Zhang2011a}, the B-Spline MPM Tran {\it et al.}
-(2019)\cite{Tran2019a}, the Conservative Taylor Least
-Squares reconstruction Wobbes {\it et al.}
-(2018)\cite{E_Wobbes_2018} and more recently the local
-maximum-entropy (or local \textit{max-ent}) shape function first
-introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} has been tested
-under the MPM framework by Wobbes {\it et al.}
-(2020)\cite{Wobbes2020} where they prof that simulations performed with the maxent basis functions
-show considerably more accurate stress approximations for
-MPM. Although, in \cite{Wobbes2020} authors does not deep in $\beta$
-parameter benefits
+the cell boundaries. Recently the local maximum-entropy (or local
+\textit{max-ent}) shape function first introduced by Arroyo \& Ortiz
+(2006)\cite{Arroyo2006} has been tested under the MPM framework by
+Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
+simulations performed with the maxent basis functions show
+considerably more accurate stress approximations for MPM. Although, in
+\cite{Wobbes2020} authors does not deep in $\beta$ parameter
+benefits. In this publication a parametric analysis of $\Beta$ will be
+performed in order to reach a compromise value that minimize the
+presence of wiggle without introducing an additional spurious behaviour.
 
@@
 capacity of MPM \cite{Sulsky1994} and OTM
-models to avoid tensile instabilities.
-
-In the one-dimensional bar sketched in
-the figure \ref{fig:Dyka_Bar}, the left end of the bar is fixed and
-the right and an initial velocity $v_0 = 5\ m/s$ is given to the last
-quarter of it in the x positive direction. The length of it is 0.1333
-meters with an unit section. The elastic parameters consider for this
-test are:
+models to avoid tensile instabilities. Here we employ our in-house
+codes for both MPM and OTM simulations.
+
+In the one-dimensional bar sketched in the figure \ref{fig:Dyka_Bar},
+the left end of the bar is fixed and the right and an initial velocity
+$v_0 = 5\ m/s$ is given to the last quarter of it in the x positive
+direction. The length of it is 0.1333 meters with an unit section. The
+elastic parameters consider for this test are:
 \begin{itemize} 
@@
 
-The results are provided for the explicit predictor-corrector version of the
-MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM algorithms. For MPM, piecewise-
-linear, uGIMP and \textit{max-ent} basis functions are employed. The OTM
-algorithm is used only with \textit{max-ent} shape functions.
+The results are provided for the explicit predictor-corrector version
+of the MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM
+algorithms. For MPM, piecewise-linear, uGIMP and \textit{max-ent}
+basis functions are employed. The OTM algorithm is used only with
+\textit{max-ent} shape functions.
 
@@
   \centering
-  \resizebox{0.8\hsize}{!}{
+  \resizebox{\hsize}{!}{
     \input{Figures/Dyka_bar.tex}}
-  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar. }
+  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
   \label{fig:Dyka_Bar}
@@
 \end{equation}
+
+The total simulation time is 0.0002 seconds, a direct consequence of
+that is we let the elastic wave generated travel thorough the bar
+(from A to C and back to A) at least four times. For the spatial
+discretization we will set five different values of the it : 0.1,
+0.05, 0.01, 0.005 and 0.001 millimeters. The initial mesh will be
+composed by a single particle in the center of the element. Regarding
+this, here we give one consideration to properly modellize this
+benchmark under the MPM framework. Notice that the free border of the
+bar has a horizontal displacement of 0.033 millimeters, therefore a
+computational domain with an extra gap of 0.033 millimeters is required in
+order to accommodate the unconstrained displacement of the particles in the
+left border of the bar. Here below the time step is controlled by the courant number, in
+this case, we adopt a middle value of it (CFL=0.5) as a compromise
+between stability and numerical accuracy.
 
@@
   \label{eq:RMS}
-  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)}
-\end{equation}
+  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)^2},
+\end{equation}
+
+where $\phi_p$ and $\hat{\phi}_p$ are respectively the analytical and
+numerical solutions evaluated in the final time step in the position
+of each particle.
 
@@
 \begin{equation*}
-    \Matrix{P}^{-1} = \frac{1}{2} \left[
+    \Matrix{P}^{-1} = \frac{1}{2\ \sqrt{E\rho}} \left[
     \begin{array}{cc}
-      -\frac{1}{\sqrt{E\rho}} & 1\\
-      \frac{1}{\sqrt{E\rho}} & 1 
+      -1 & \frac{1}{\sqrt{E\rho}}\\
+      1 & \frac{1}{\sqrt{E\rho}} 
     \end{array} \right]
@@
 The boundary conditions are in both cases of radiation as there is not
-wave in-going from the exterior. So for the left side (fixed
+wave in-going from the exterior. So for the right side (fixed
 boundary) we get the following conditions:
 \begin{equation*}
-  &\Re^{I} = 0 \quad and \quad v_{x=0} = 0
+  \Re^{II} = 0 \quad and \quad v_{x=L} = 0
 \end{equation*}
-Therefore $\sigma_{x=0} = \sqrt{\rho E}\Re^{II}$. And in the left side
+Therefore $\sigma_{x=L} = -2*\sqrt{\rho E}\Re^{I}$. And in the left side
 (free boundary) we get the following conditions:
 \begin{equation*}
-  &\Re^{II} = 0 \quad and \quad \sigma_{x=L} = 0
+  \Re^{I} = 0 \quad and \quad \sigma_{x=0} = 0
 \end{equation*}
-Therefore $v_{x=L} = \Re^{I}$. Finally, applying this conditions in
+Therefore $v_{x=0} = 2\Re^{II}$. Finally, applying this conditions in
 the elastic bar sketched in \ref{fig:Dyka_Bar}, is possible to obtain

### 2020-03-02 main.tex
cambios 1-02-2020

@@
 
-\title{Suitability of the local-maximum entropy approximation under
-  the Material Point Method framework for dynamic problems. \thanks{Funding: This
+\title{Novel improvements in the Material Point Method to face
+  dynamic problems: 
+  Local-maximum entropy approximation and an explicit   predictor-corrector scheme. \thanks{Funding: This
     study was funded by Agustín de Betancourt Foundation (grant number
@@
 
-\titlerunning{Suitability of the LME approximation under
-  the MPM framework for dynamic problems.} % if too long for running head
+\titlerunning{Novel improvements in the Material Point Method to face
+  dynamic problems.} % if too long for running head
 
@@
 \label{intro}
-Since the proposal of the Material Point Method (\textbf{MPM}) by Sulsky {\it
-  et al.} (1994)\cite{Sulsky1994}, as a generalization of
-a particle-in-cell method \cite{Harlow1956} and a fluid implicit
-particle (FLIP) method \cite{Brackbill1986}, MPM has been used to
-simulate dynamic problems. However, in the simulations made with the
-original MPM, there are numerical noises \cite{Tran2019e} when it is faced to solve
-classic dynamic benchmarks like the one proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995}. These numerical inaccuracies give rise to the
-development of other interpolation techniques to overcome this limitation. Some of this
-alternatives techniques are the generalized interpolation material
-point method (GIMP) Bardenhagen \& Kober (2004)\cite{Bardenhagen2004},
-the dual domain material point method (DDMP) Zhang {\it et al.}
+Since the proposal of the Material Point Method (\textbf{MPM}) by
+Sulsky {\it  et al.} (1994)\cite{Sulsky1994} as a generalization to
+solids of the fluid implicit particle (FLIP) method
+\cite{Brackbill1986}. It popularity has increased due to its ability
+to deal with large strain regime without suffer mesh distortion
+inaccuracies. However, this method suffers other kind of
+instabilities, such those when material points crossing cell
+boundaries. This give rise to the development of other interpolation
+techniques to overcome this limitation such as the generalized
+interpolation material point method (GIMP) Bardenhagen \& Kober
+(2004)\cite{Bardenhagen2004}, the dual
+domain material point method (DDMP) Zhang {\it et al.}
 (2011)\cite{Zhang2011a}, the B-Spline MPM Tran {\it et al.}
-(2019)\cite{Tran2019a}, the Conservative Taylor Least
-Squares reconstruction Wobbes {\it et al.}
-(2018)\cite{E_Wobbes_2018} and more recently the local
-maximum-entropy (or local \textit{max-ent}) shape function first
-introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} has been tested
-under the MPM framework by Wobbes {\it et al.}
-(2020)\cite{Wobbes2020}. Alternatively to change the spatial
-interpolation technique other researchers have overcome the well known
-wiggle that tends to appear in this dynamic simulations by filtering
-high-frequencies with an alternative time integration scheme, the
-implicit GIMP (iGIMP) Charlton {\it et al.}
+(2019)\cite{Tran2019a} or the Conservative Taylor
+Least Squares reconstruction Wobbes {\it et al.}
+(2018)\cite{E_Wobbes_2018}. This techniques are devoted to mitigate the
+``grid crossing'' error.
+Nevertheless, in the presence of shock waves spurious
+numerical noises appears despite of this using techniques \cite{Tran2019e}. These numerical
+inaccuracies also known as wiggles are due to the time discretization
+technique. A simple approach to face those spurious noises is to add a
+damping source to the equilibrium equations. To overcome this
+limitation, many researchers has proposed alternative time integration
+schemes which reduce them by filtering high-frequencies. Some of these
+attempts are the implicit GIMP (iGIMP) Charlton {\it et al.}
 (2017)\nocite{Charlton2017} or the generalised-$\alpha$ scheme for the
@@
 employ of a suitable combination of the maximum-entropy (or local
-\textit{max-ent}) shape functions, and the proposal of a explicit
+\textit{max-ent}) $\gamma$ family shape functions, and the proposal of a explicit 
 predictor-corrector scheme. Local \textit{max-ent} shape functions was
-first introduced by \cite{Arroyo2006}, it belongs to the class of convex 
+first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006}, it belongs to the class of convex 
 approximation schemes and provides a seamless transition between
@@
 \textit{max-ent} basis functions possess many desirable properties for
-meshfree algorithms. First of all, they are entirely defined by the
+mesh-free algorithms. First of all, they are entirely defined by the
 nodal set and the domain of analysis. They are also non-negative,
 satisfy the partition of unity property, and provide an exact
-approximation for affine functions \cite{Arroyo2006}. This
+approximation for affine functions \cite{Arroyo2006}. Furthermore, as
+it is not based in a voxel discretization as the GIMP, it is no prone to suffer
+voxel domains overlap, which can introduce severe inaccuracies. This
 approximation scheme has been proof to have a good performance under
@@
 (2018)\cite{Navas2018a} and Li {\it et al.} (2012)\cite{Li2012} for
-Optimal Transportation Meshfree (\textbf{OTM}) method. On the other
-hand, the time integration scheme here proposed is an accommodation of
-the Newmark a-form with $\gamma = 0.5$ and $\beta = 0$ which is the central difference
+Optimal Transportation Meshfree (\textbf{OTM}) method. And more
+recently under the MPM framework by Wobbes {\it et
+  al.}(2020)\cite{Wobbes2020} but limiting the $\gamma$ parameter to
+zero. On the other hand, the time integration scheme here proposed is an accommodation of
+the Newmark a-form ($\gamma = 0.5$ and $\beta = 0$)\footnote{Notice
+that these $\gamma$ and $\beta$ parameters does not have the same
+meaning for the LME shape functions.} which is the central difference
 explicit (CD). We have choose this method among other suitable
@@
 function is performed as well a parametric study for the $\gamma$
-parameter. Finally, conclusions and future research topics are exposed
-in Section \ref{sec:conclusions}.
+parameter. Both techniques will face to solve a classic dynamic
+benchmark proposed by Dyka \& Ingel (1995)\cite{Dyka1995}. Finally,
+conclusions and future research topics are exposed in Section \ref{sec:conclusions}.
 
@@
 \label{sec:derivation-mpm}
-In this section, we provide an overview of the standard explicit MPM
-algorithm as presented by \cite{Sulsky1994}. The method has three main
-steps: a variational recovery process to project particle data to the
-nodes of the grid, a Eulerian step where balance of momentum is
-compute by solving internal and external forces in the nodes, and
-finally the advection of the Lagrangian particles. We will first give
-a introduction to the governing equations and then follow by an
-algorithmic description of the process.
+The aim of this section is to provide an overview of
+the standard explicit MPM algorithm \cite{Sulsky1994}. Therefore, it
+is structured in the following shape: we will first give a
+introduction to the governing equations \ref{sec:governing-equations},
+later the variational statement of the problem will be presented \ref{sec:variational-formulation}, and
+finally a discretization procedure thorough Galerkin is performed \ref{sec:Galerkin-procedure}.
+
+The method has three main steps: (i) a variational recovery process,
+where particle data is projected to the grid nodes, (ii) an Eulerian
+step, where balance of momentum equation is expressed as a nodal
+equilibrium equation thorough a FEM-like procedure, and finally (iii) a Lagrangian advection of the particles.
 
@@
 \emptyset$. Note that $\varGamma_d$ is reserved for Dirichlet boundary
-conditions, and  $\varGamma_n$ for the Neumann. The behaviour of the
-continuum can be described by a set of governing equations which are
+conditions, and  $\varGamma_n$ for the Neumann. The behaviour of the continuum can be described by a set of governing equations which are
 (i) the balance of momentum equation
@@
 \end{equation}
-next (ii) the compatibility equation with ensure that the velocity
+(ii) the compatibility equation with ensure that the velocity
 field is compatible with the Cauchy strain field,
@@
 \end{equation}
-later (iii) the constitutive equation, which relates the rate of Cauchy strain
+(iii) the constitutive equation, which relates the rate of Cauchy strain
 tensor with the rate of Cauchy stress tensor,
@@
 \end{equation}
-finally we introduce (iv) the mass conservation, which if obtained by
+and finally (iv) the mass conservation, which can be obtained by
 setting to zero the total derivative of the density field,
@@
   \label{eq:cauchy-secuence}
-  \Integral{3}{\vect{v}^{\psi}} < \infty\ \quad\text{and}\quad \Integral{3}{\Grad{\vect{v}^{\psi}}} < \infty
+  \Integral{3}{\vect{v}^{\psi}} < \infty\ \quad\text{and}\quad \Integral{3}{\tens{\varepsilon}^{\psi}} < \infty
 \end{equation}
@@
 (\ref{eq:particle_balance_forces3}) and (\ref{eq:Updated_Lagrangian}),
-are solved with a forward Euler algorithm. In the next section, an
-alternative time integration scheme based on the Newmark a-form is proposed.
+are solved with an explicit forward Euler algorithm. In the next
+section, an alternative time integration scheme based on the Newmark a-form is presented.
 
@@
 \cite{Guilkey2003}, \cite{Tran2019e}, \cite{Charlton2017}. In the first publication on
-the MPM \cite{Sulsky1994}, the nodal acceleration in employed to
+the MPM \cite{Sulsky1994}, the nodal acceleration was employed to
 update the particles as
@@
 \end{equation}
-However, as Andersen (2009)\cite{thesis_Andersen_2009} point out, this
-algorithm has been shown to be numerically unstable due to that
+However, as Andersen (2009)\cite{thesis_Andersen_2009} point out, this algorithm has been shown to be numerically unstable due to that
 $\vect{f}_I^{int,k}$ can be finite for an infinitesimal nodal mass
@@
 
-\begin{figure}\sidecaption
+\begin{figure*}\sidecaption
   \centering
-  \resizebox{\hsize}{!}{
+  \resizebox{0.7\hsize}{!}{
     \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
@@
   \label{fig:Dyka-MPM-uGIMP-LME}
-\end{figure}
+\end{figure*}
 
@@
   \label{eq:1D-balance-linear-momentum}
-  \rho\ \Deriv{v}{t} = \Deriv{\sigma}{x} + \rho\ b,
-\end{equation}
-where $\sigma$ is the stress value, $\rho$ is the density,
-$v$ is the velocity, and $b$ are the body
-forces. (ii) The constitutive model, which for convenience of the
+  \rho\ \Deriv{v}{t} = \Deriv{\sigma}{x},
+\end{equation}
+where $\sigma$ is the stress value, $\rho$ is the density, and 
+$v$ is the velocity. (ii) The constitutive model, which for convenience of the
 following developments will be written in terms of displacement and
@@
 \end{equation}
-Next for simplicity, we remove the body forces from
-\eqref{eq:1D-balance-linear-momentum}, and we will introduce
-\eqref{eq:CompatibilityEquation_e} in
+Next for simplicity, we will introduce \eqref{eq:CompatibilityEquation_e} in 
 \eqref{eq:1D-constitutive-equation}, so we get the following system of equations,
@@
 \end{equation*}
-Therefore $\sigma_{x=L} = -2*\sqrt{\rho E}\Re^{I}$. And in the left side
+Therefore $\sigma_{x=L} = -2\sqrt{\rho E}\ \Re^{I}$. And in the left side
 (free boundary) we get the following conditions:

### 2020-03-06 main.tex
Cambios 6-3-2020

@@
 (\ref{eq:particle_balance_forces3}) and (\ref{eq:Updated_Lagrangian}),
-are solved with an explicit forward Euler algorithm. In the next
-section, an alternative time integration scheme based on the Newmark a-form is presented.
-
-\section{Explicit predictor-corrector scheme for MPM.}
-\label{sec:epc-algor-mpm}
-
-The time integration scheme of the MPM has been described in detail by many researchers
+are solved with an explicit forward Euler algorithm. The time integration scheme of the MPM has been described in detail by many researchers
 \cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and summarized
-in Figure \ref{fig:MPM_algorithm}. Other authors have proposed many
-others time integration alternatives like
-\cite{Guilkey2003}, \cite{Tran2019e}, \cite{Charlton2017}. In the first publication on
-the MPM \cite{Sulsky1994}, the nodal acceleration was employed to
-update the particles as
+in Figure \ref{fig:MPM_algorithm}.
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.55\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/MPM_scheme}
+  }
+  \caption{MPM standard algorithm.}
+  \label{fig:MPM_algorithm}
+\end{figure}
+
+Other authors have proposed many others time integration alternatives
+like \cite{Guilkey2003}, \cite{Tran2019e}, \cite{Charlton2017}. In the
+first publication on the MPM \cite{Sulsky1994}, the nodal acceleration
+was employed to update the particles as
 \begin{equation}
@@
 \cite{Tran2019e}. But it can present the same numerical instabilities
-as in \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v} when nodal masses become infinitesimal.
-Here we propose a explicit predictor-corrector scheme for MPM based on the Newmark a-form with
+as in \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v} when
+nodal masses become infinitesimal.
+
+\section{Explicit predictor-corrector scheme for MPM.}
+\label{sec:epc-algor-mpm}
+
+In this section, an explicit predictor-corrector time integration
+scheme is presented. It is based in the Newmark a-form 
 $\gamma = 0.5$ and $\beta = 0$ which is the central difference
@@
   \Matrix{M}_{IJ}\ddot{\Vector{d}}_{J} + \Matrix{C}_{IJ}\dot{\Vector{d}}_{J} +
-  \Matrix{K}_{IJ}\Vector{d}_{J} = \Vector{F}_{I}
+  \Matrix{K}_{IJ}\Vector{d}_{J} = \Vector{F}_{I}.
 \end{equation*}
-Nevertheless it can be applied for an isolated mass, therefore it is
-possible to apply this methods successfully in the MPM framework as
-was proved by \cite{Tran2019e}. Taking the predictor
-definition from the classic literature \cite{Hughes2000} and
-calculating particles velocity and acceleration as described in 
-\cite{Zhang_book_2016}, we get the following expression for the
+
+As the MPM has a nodal stage, it is possible to apply this methods
+successfully in the MPM framework as was proved by
+\cite{Tran2019e}. Taking the predictor definition from the classic
+literature \cite{Hughes2000} and calculating nodal velocity, and
+updating particles position employing nodal values of velocity and
+acceleration. Therefore we get the following expression for the
 \textbf{predictor} stage for both velocity and displacement.
@@
   \vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
-  \underbrace{\sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{p}_{I}^{k}}{\tens{m}_I^k}}_{\vec{v}_p^{k}} + \frac{1}{2}\Delta
+  \underbrace{\sum^{N_n}_{I}N_{Ip}^k\ \vec{v}_{I}^{k}}_{\vec{v}_p^{k}} + \frac{1}{2}\Delta
   t^2\ \underbrace{\sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{f}_{I}^{k}}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
@@
   \label{eq:Predictor-velocity}
-  \vec{v}_p^{k+1} = \vec{v}_p^n + (1 - \gamma)\ \Delta t\
-  \underbrace{\sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{f}_{I}^{k}}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
-\end{equation}
-
-Consequently, the \textbf{corrector} stage for the particles velocity is in the
+  \vec{v}_I^{k+1} = \vec{v}_I^n + (1 - \gamma)\ \Delta t\ \vec{a}_I^k
+  \quad , \quad \vec{a}_I^k = \frac{\vec{f}_{I}^{k}}{\tens{m}_I^k}
+\end{equation}
+
+Consequently, the \textbf{corrector} stage for the nodal velocity is in the
 following way
 \begin{equation}
-  \vec{v}_{p}^{k+1} = \vec{v}_{p}^{k+1} +
-  \gamma\ \Delta t\ \underbrace{\sum^{N_n}_{I}\frac{N_{Ip}^{k+1}\ \vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}}_{\vec{a}_p^{k+1}}  
+  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{k+1} + \gamma\ \Delta t\
+  \vec{a}_I^{k+1} \quad , \quad  \vec{a}_I^{k+1} = \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}} 
 \end{equation}
@@
 position at full time step, but updates the velocity at half time
-steps. Due to its simplicity allows be implemented with minor modifications
+steps. Notice also that with this approach the calculation of nodal
+momentum vales in not required, and particles velocities is just a
+post-process. So during the lagrangian step only the particles
+position is truly computed. This minimizes the information
+transference between the particles and nodes, and in consequence
+minimizes the associated error to this process.
+
+Due to its simplicity allows be implemented with minor modifications
 over a standard forward Euler. It is summarized in shape of
@@
   \renewcommand{\thealgorithm}{}
-  \caption{Explicit scheme : Newmark central difference}
+  \caption{Explicit Predictor-Corrector scheme}
   \begin{algorithmic}[1]
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
-    \STATE \textbf{Explicit Newmark Predictor} ($\gamma = 0.5$) :
-    \begin{align*}
-      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
-        \sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{p}_{I}^{k}}{\tens{M}_I^k} +
-        \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{f}_{I}^{k}}{\tens{M}_I^k}\\
-      &\vec{v}_p^{k+1} = \vec{v}_p^n + (1 - \gamma)\
-        \sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{f}_{I}^{k}}{\tens{M}_I^k}\Delta t        
-    \end{align*}
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Discard the previous nodal values}.
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Transference of particles kinetics information to the
-      mesh}:\\
-    Calculate the lumped mass matrix $\tens{M}_{I}$,
-    and the nodal momentum $\vec{p}_{I}$ with the predicted values.
+    \STATE \textbf{Explicit Newmark Predictor} ($\gamma = 0.5$):
     \begin{equation*}
-      \tens{M}_{I} = \sum_{p}^{N_p}N_{Ip}^{k+1}\ m_p,
-    \end{equation*}
-    \begin{equation*}
-      \vec{p}_{I}^{k+1} = \sum_{p}^{N_p} N_{Ip}^{k+1}\ m_p\ \vec{v}_{p}^{k+1},
+      \vec{v}_I^{k+1} = \vec{v}_I^n + (1 - \gamma)\ \Delta t\ \vec{a}_I^k
+      \quad , \quad \vec{a}_I^k = \frac{\vec{f}_{I}^{k}}{\tens{m}_I^k}      
     \end{equation*}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Impose essential boundary conditions over momentum nodal
-      values}:\\
-    At the fixed boundary, set $\vec{p}_{I}^{k+1} = 0$. Later, get the
-    nodal values of the velocity field $\vec{v}_{I}^{k+1} =
-    \frac{\vec{p}_{I}^{k+1}}{\tens{M}_{I}}$
+    \STATE \textbf{Impose essential boundary conditions}:\\
+    At the fixed boundary, set $\vec{v}_{I}^{k+1} = 0$. 
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    % \STATE \textbf{Discard the previous nodal values}.
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \STATE \textbf{Update mass matrix}:
+    \begin{equation*}
+      \tens{m}_{I} = \sum_{p}^{N_p}N_{Ip}^{k+1}\ m_p,
+    \end{equation*}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Update the density field}:\\
+    \STATE \textbf{Update the density field}:
     \begin{equation*}
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Integrate the grid nodal momentum equation :}\\
-    Calculate the nodal momentum $\vec{p}_{I}$ in $k+1$. 
+    \STATE \textbf{Explicit Newmark Corrector} ($\gamma = 0.5$):
     \begin{equation*}
-      \vec{p}_{I}^{k+1} = \vec{p}_{I}^{k} + \vec{f}_{I}^{k+1}\Delta t
+      \vec{v}_{I}^{k+1} = \vec{v}_{I}^{k+1} + \gamma\ \Delta t\
+      \vec{a}_I^{k+1} \quad , \quad  \vec{a}_I^{k+1} = \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}  
     \end{equation*}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \STATE \textbf{Explicit Newmark Corrector}:
-    \begin{equation*}
-      \vec{v}_{p}^{k+1} = \vec{v}_{p}^{k+1} +
-      \gamma \sum^{N_n}_{I}\frac{N_{Ip}^{k+1}\ \vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}\Delta t  
-    \end{equation*}
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \STATE \textbf{Update particles position and velocity}:
+    \begin{align*}
+      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
+        \sum^{N_n}_{I} N_{Ip}^k\ \vec{v}_{I}^{k} +
+        \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{N_{Ip}^k\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
+        \sum^{N_n}_{I}\frac{N_{Ip}^k\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}
+    \end{align*}
   \end{algorithmic}
@@
 
+\subsection{Analysis of the Explicit Predictor-Corrector accuracy}
+\label{sec:EPC-accuracy}
+
+In this section, the benchmark proposed by Dyka \& Ingel
+(1995)\cite{Dyka1995} is considered to illustrate the
+capacity of the proposed time integration algorithm to avoid velocity
+fields instabilities.
+
+In the one-dimensional bar sketched in the figure \ref{fig:Dyka_Bar},
+the left end of the bar is fixed and the right and an initial velocity
+$v_0 = 5\ m/s$ is given to the last quarter of it in the x positive
+direction. The length of it is 0.1333 meters with an unit section.
+
 \begin{figure}\sidecaption
   \centering
-  \resizebox{0.6\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/MPM_scheme}
-  }
-  \caption{MPM standard algorithm.}
-  \label{fig:MPM_algorithm}
+  \resizebox{\hsize}{!}{
+    \input{Figures/Dyka_bar.tex}}
+  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
+  \label{fig:Dyka_Bar}
+\end{figure}
+
+The elastic parameters consider for this test are:
+\begin{itemize} 
+\item  Density : $7833\ kg/m3$
+\item  Poisson ratio : $0$
+\item  Elastic modulus : $200 \cdot 10^9\ Pa$
+\end{itemize}
+
+The boundary conditions are:
+\begin{equation}
+  \label{eq:3}
+  \sigma \rvert_{x=L} = 0 \quad , \quad v \rvert_{x=0} = 0
+\end{equation}
+
+The total simulation time is 0.0002 seconds, a direct consequence of
+that is we let the elastic wave generated travel thorough the bar
+(from A to C and back to A) at least four times. For the spatial
+discretization we will set a mesh size of 3.3325 millimeters. The
+initial mesh will be composed by a single particle in the center of
+the element. Regarding this, here we give one consideration to
+properly modellize this benchmark under the MPM framework. Notice that
+the free border of the bar has a horizontal displacement of 0.033
+millimeters, therefore a computational domain with an extra gap of
+0.033 millimeters is required in order to accommodate the
+unconstrained displacement of the particles in the left border of the
+bar. Here below the time step is controlled by the courant number, in
+this case, we adopt a middle value of it (CFL=0.5) as a compromise
+between stability and numerical accuracy.
+
+The analytical solution in terms of velocity
+\ref{fig:vel_analytics_dyka}, and stress
+\ref{fig:stress_analytics_dyka} can be found in the appendix
+\ref{app:analytical_sol} given by the Method of characteristics.
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/FE_vs_PCE_CFL_05}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-PCE-FE}
 \end{figure}
@@
 
-\section{Numerical results : 1D Elastic bar}
-\label{sec:dynamic-benchmark}
-
-In this section, the benchmark proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995} is considered to illustrate the
-capacity of MPM \cite{Sulsky1994} and OTM
+\subsection{Error analysis MPM vs uGIMP vs MPM-\textit{max-ent}}
+\label{sec:study-error}
+
+For the convergence analysis, the root-mean-square (RMS) error in the
+displacement is computed. RMS error is defined as follows
+
+\begin{equation}
+  \label{eq:RMS}
+  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)^2},
+\end{equation}
+
+where $\phi_p$ and $\hat{\phi}_p$ are respectively the analytical and
+numerical solutions evaluated in the final time step in the position
+of each particle.
+
+\begin{figure*}\sidecaption
+  \centering
+  \resizebox{0.7\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-MPM-uGIMP-LME}
+\end{figure*}
+
+\subsection{MPM versus OTM}
+\label{sec:mpm-versus-otm}
+
+MPM \cite{Sulsky1994} and OTM
 models to avoid tensile instabilities. Here we employ our in-house
 codes for both MPM and OTM simulations.
-
-In the one-dimensional bar sketched in the figure \ref{fig:Dyka_Bar},
-the left end of the bar is fixed and the right and an initial velocity
-$v_0 = 5\ m/s$ is given to the last quarter of it in the x positive
-direction. The length of it is 0.1333 meters with an unit section. The
-elastic parameters consider for this test are:
-\begin{itemize} 
-\item  Density : $7833\ kg/m3$
-\item  Poisson ratio : $0$
-\item  Elastic modulus : $200 \cdot 10^9\ Pa$
-\end{itemize}
 
@@
 \textit{max-ent} shape functions.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \input{Figures/Dyka_bar.tex}}
-  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
-  \label{fig:Dyka_Bar}
-\end{figure}
-
-The boundary conditions are:
-\begin{equation}
-  \label{eq:3}
-  \sigma \rvert_{x=L} = 0 \quad , \quad v \rvert_{x=0} = 0
-\end{equation}
-
-The total simulation time is 0.0002 seconds, a direct consequence of
-that is we let the elastic wave generated travel thorough the bar
-(from A to C and back to A) at least four times. For the spatial
-discretization we will set five different values of the it : 0.1,
-0.05, 0.01, 0.005 and 0.001 millimeters. The initial mesh will be
-composed by a single particle in the center of the element. Regarding
-this, here we give one consideration to properly modellize this
-benchmark under the MPM framework. Notice that the free border of the
-bar has a horizontal displacement of 0.033 millimeters, therefore a
-computational domain with an extra gap of 0.033 millimeters is required in
-order to accommodate the unconstrained displacement of the particles in the
-left border of the bar. Here below the time step is controlled by the courant number, in
-this case, we adopt a middle value of it (CFL=0.5) as a compromise
-between stability and numerical accuracy.
-
-The analytical solution in terms of velocity
-\ref{fig:vel_analytics_dyka}, and stress
-\ref{fig:stress_analytics_dyka} can be found in the appendix
-\ref{app:analytical_sol} given by the Method of characteristics. For
-the convergence analysis, the root-mean-square (RMS) error in the
-displacement is computed. RMS error is defined as follows
-
-\begin{equation}
-  \label{eq:RMS}
-  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)^2},
-\end{equation}
-
-where $\phi_p$ and $\hat{\phi}_p$ are respectively the analytical and
-numerical solutions evaluated in the final time step in the position
-of each particle.
-
-\subsection{Error analysis MPM vs uGIMP vs MPM-\textit{max-ent}}
-\label{sec:study-error}
-
-\begin{figure*}\sidecaption
-  \centering
-  \resizebox{0.7\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-MPM-uGIMP-LME}
-\end{figure*}
-
-\subsection{MPM versus OTM}
-\label{sec:mpm-versus-otm}
 

### 2020-03-10 main.tex
Cambios 10-3-2020

@@
 \newcommand{\Div}[1]{
-  \ensuremath{\nabla \cdot {#1}}
+  \ensuremath{div({#1})}
 }
 % Gradient
-\newcommand\Grad[1]{\nabla{#1}}
-\newcommand\GradS[1]{\nabla^s{#1}}
-\newcommand\GradT[1]{\nabla^T{#1}}
+\newcommand\Grad[1]{grad({#1})}
+\newcommand\GradS[1]{grad^s({#1})}
+\newcommand\GradT[1]{grad^T({#1})}
 
@@
 denotes the divergence operator, and finally $\Grad{\qed}$ and
-$\GradS{\qed}$ denotes the gradient and its symmetric part.
+$\GradS{\qed}$ denotes the gradient and its symmetric part. Einstain
+subscripts convention is adopted so repeated index means addition.
 
@@
 introduction to the governing equations \ref{sec:governing-equations},
-later the variational statement of the problem will be presented \ref{sec:variational-formulation}, and
-finally a discretization procedure thorough Galerkin is performed \ref{sec:Galerkin-procedure}.
+later the variational statement of the problem will be presented
+\ref{sec:variational-formulation}, and finally a discretization
+procedure thorough Galerkin is performed \ref{sec:Galerkin-procedure}.
 
@@
 \emptyset$. Note that $\varGamma_d$ is reserved for Dirichlet boundary
-conditions, and  $\varGamma_n$ for the Neumann. The behaviour of the continuum can be described by a set of governing equations which are
+conditions, and  $\varGamma_n$ for the Neumann. In a inifinitesimal
+strain context, the behaviour of the continuum can be described by the
+following set of equations:
 (i) the balance of momentum equation
@@
   \label{eq:Compatibility-equation}
-  \dot{\tens{\varepsilon}} = \GradS{\vect{v}} = \frac{1}{2}\left(
-    \Grad{\vect{v}} +  \GradT{\vect{v}} \right),
+  \dot{\tens{\varepsilon}} = \GradS{\vect{v}},
 \end{equation}
@@
   \label{eq:Rho-material-derivative}
-  \frac{D \rho}{D t} = \dot{\rho} + \rho \Div\vect{v}} = 0.
+  \frac{D \rho}{D t} = \dot{\rho} + \rho \Div{\vect{v}} = 0.
 \end{equation}
@@
   \Integral{3}{\rho\ \left( \Deriv{\vec{v}}{t}\ - \vec{b} \right) \cdot \vec{v}^{\psi}} =
-  \Integral{2}{\vec{t}\ \cdot \vec{v}^{\psi}} - \Integral{3}{\tens{\sigma} \cdot
+  \Integral{2}{\vec{t}\ \cdot \vec{v}^{\psi}} - \Integral{3}{\tens{\sigma} \colon
     \tens{\varepsilon}^{\psi}},
@@
     \label{eq:particle_acceleration_forces}
-    \Integral{3}{\rho\ \vec{a}\ \vect{v}^{\psi}} =& \sum^{N_p}_{p}
-   \dot{\vec{v}}_{p}\ \vect{v}^{\psi}_{p}\ m_p.
+    \Integral{3}{\rho\ \vec{a} \cdot \vect{v}^{\psi}} =
+    \dot{\vec{v}}_{p} \cdot \vect{v}^{\psi}_{p}\ m_p.
   \end{equation}\\
@@
     \label{eq:particle_internal_forces}
-    \Integral{3}{\tens{\sigma}\ \cdot \Grad{\vec{\psi}}} = \sum^{N_p}_{p}
-   \tens{\sigma}_{p}\ \cdot \Grad{\tens{\psi}_{p}}\ V_p.
+    \Integral{3}{\tens{\sigma}\ \colon \tens{\varepsilon}^{\psi}} =
+   \tens{\sigma}_{p}\ \colon \tens{\varepsilon}^{\psi}_p \ V_p.
   \end{equation}\\
@@
   \label{eq:particle_body_forces}
-  \Integral{3}{\rho\ \vec{b}\ \vect{v}^{\psi} } = \sum^{N_p}_{p}
-  \vec{b}_{p}\ \vect{v}^{\psi}_p\ m_p.
+  \Integral{3}{\rho\ \vec{b} \cdot \vect{v}^{\psi} } = 
+  \vec{b}_{p} \cdot \vect{v}^{\psi}_p\ m_p.
 \end{equation}\\
@@
     \Integral{2}{\vec{t}\ \vect{v}^{\psi}} = \Integral{2}{\rho\
-      \vec{t}^s\ \vect{v}^{\psi}} = \sum^{N_p}_{p} \vec{t}^s_{p}\ \vect{v}^{\psi}_{p}\ h^{-1}\ m_p ,
+      \vec{t}^s \cdot \vect{v}^{\psi}} = \vec{t}^s_{p} \cdot \vect{v}^{\psi}_{p}\ h^{-1}\ m_p ,
   \end{aligned} 
@@
   \label{eq:Approx-velocity-mesh}
-  \vec{v}_{p} = \sum^{Nn}_I N_I(\vec{x}_p) \vect{v}_I
-  \quad \text{and} \quad \vec{v}^{\psi}_{p} = \sum^{Nn}_I N_I(\vec{x}_p) \vect{1},
+  \vec{v}_{p} = N_I(\vec{x}_p) \vect{v}_I
+  \quad \text{and} \quad \vec{v}^{\psi}_{p} = N_I(\vec{x}_p) \vect{v}_I^{\psi},
+\end{equation}
+\begin{equation}
+  \label{eq:Approx-gradvelocity-mesh}
+  \Grad{\vect{v}}_p = \vect{v}_I N_I(\vec{x}_p)
+  \quad \text{and} \quad \vec{v}^{\psi}_{p} = \sum^{Nn}_I N_I(\vec{x}_p) \vect{v}_I^{\psi},
 \end{equation}

### 2020-03-10 Figures/Block.tex
Cambios II 10-3-2020

\begin{tikzpicture} 
  \scaling{1};

% Nodos
\point{1}{0}{10};
\point{2}{2}{10};
\point{3}{0}{8};
\point{4}{2}{8};
\point{5}{4}{10};
\point{6}{0}{6};
\point{7}{2}{6};
\point{8}{4}{8};
\point{9}{4}{6};
\point{10}{6}{10};
\point{11}{0}{4};            
\point{12}{2}{4};            
\point{13}{6}{8};            
\point{14}{4}{4};            
\point{15}{6}{6};            
\point{16}{8}{10};            
\point{17}{0}{2};            
\point{18}{2}{2};            
\point{19}{8}{8};            
\point{20}{6}{4};            
\point{21}{4}{2};            
\point{22}{8}{6};            
\point{23}{0}{0};            
\point{24}{10}{10};            
\point{25}{6}{2};            
\point{26}{8}{4};
\point{27}{2}{0};            
\point{28}{10}{8};            
\point{29}{4}{0};            
\point{30}{10}{6};            
\point{31}{8}{2};            
\point{32}{6}{0};            
\point{33}{10}{4};            
\point{34}{8}{0};            
\point{35}{10}{2};            
\point{36}{10}{0};

% Barras
\beam{2}{27}{18};
\beam{2}{18}{17};
\beam{2}{17}{23};
\beam{2}{23}{27};

\beam{2}{29}{21};
\beam{2}{21}{18};
\beam{2}{18}{27};
\beam{2}{29}{27};

\beam{2}{32}{25};
\beam{2}{25}{21};
\beam{2}{21}{29};
\beam{2}{32}{29};

\beam{2}{34}{31};
\beam{2}{31}{25};
\beam{2}{25}{32};
\beam{2}{34}{32};

\beam{2}{36}{35};
\beam{2}{35}{31};
\beam{2}{31}{34};
\beam{2}{36}{34};

%%%%%%%%%%%%%%%%
\beam{2}{18}{12};
\beam{2}{12}{11};
\beam{2}{11}{17};
\beam{2}{18}{17};

\beam{2}{21}{14};
\beam{2}{14}{12};
\beam{2}{12}{18};
\beam{2}{21}{18};

\beam{2}{25}{20};
\beam{2}{20}{14};
\beam{2}{14}{21};
\beam{2}{25}{21};

\beam{2}{31}{26};
\beam{2}{26}{20};
\beam{2}{20}{25};
\beam{2}{31}{25};

\beam{2}{35}{33};
\beam{2}{33}{26};
\beam{2}{26}{31};
\beam{2}{35}{31};

%%%%%%%%%%%%%%%%
\beam{2}{12}{7};
\beam{2}{7}{6};
\beam{2}{6}{11};
\beam{2}{12}{11};

\beam{2}{14}{9};
\beam{2}{9}{7};
\beam{2}{7}{12};
\beam{2}{14}{12};

\beam{2}{20}{15};
\beam{2}{15}{9};
\beam{2}{9}{14};
\beam{2}{20}{14};

\beam{2}{26}{22};
\beam{2}{22}{15};
\beam{2}{15}{20};
\beam{2}{26}{20};

\beam{2}{33}{30};
\beam{2}{30}{22};
\beam{2}{22}{26};
\beam{2}{33}{26};

%%%%%%%%%%%%%%%%
\beam{2}{7}{4};
\beam{2}{4}{3};
\beam{2}{3}{6};
\beam{2}{7}{6};

\beam{2}{9}{8};
\beam{2}{8}{4};
\beam{2}{4}{7};
\beam{2}{9}{7};

\beam{2}{15}{13};
\beam{2}{13}{8};
\beam{2}{8}{9};
\beam{2}{15}{9};

\beam{2}{22}{19};
\beam{2}{19}{13};
\beam{2}{13}{15};
\beam{2}{22}{15};

\beam{2}{30}{28};
\beam{2}{28}{19};
\beam{2}{19}{22};
\beam{2}{30}{22};

%%%%%%%%%%%%%%%%
\beam{2}{4}{2};
\beam{2}{2}{1};
\beam{2}{1}{3};
\beam{2}{4}{3};

\beam{2}{8}{5};
\beam{2}{5}{2};
\beam{2}{2}{4};
\beam{2}{8}{4};

\beam{2}{13}{10};
\beam{2}{10}{5};
\beam{2}{5}{8};
\beam{2}{13}{8};

\beam{2}{19}{16};
\beam{2}{16}{10};
\beam{2}{10}{13};
\beam{2}{19}{13};

\beam{2}{28}{24};
\beam{2}{24}{16};
\beam{2}{16}{19};
\beam{2}{28}{19};

% Bottom
\support {1}{23}[315];
\support {1}{27}[0];
\support {1}{29}[0];
\support {1}{32}[0];
\support {1}{34}[0];
\support {1}{36}[45];

% \support {2}{23}[270];
\support {2}{1}[270];
\support {2}{3}[270];
\support {2}{6}[270];
\support {2}{11}[270];
\support {2}{17}[270];

\support {2}{24}[90];
\support {2}{28}[90];
\support {2}{30}[90];
\support {2}{33}[90];
\support {2}{35}[90];
% \support {2}{36}[90];

% Gravity
\point{g}{12}{5};
\load{1}{g}[90][3][0];

% Cotas
\dimensioning{1}{23}{36}{-1.5}[$10~m$];
\dimensioning{2}{23}{1}{-1.5}[$10~m$];

\end{tikzpicture}

% % Apoyos
% \support{3}{c}[90];
% % Fuerzas
% \lineload{4}{b}{a}[1][0.2];
% \notation{5}{a}{b}[$-5\ m/s$][.5][below][2];
% % Nombres de nodos
% \notation{1}{a}{A}[below left];
% \notation{1}{b}{B}[below left];
% \notation{1}{c}{C}[below left];
% % Cotas
% \dimensioning{1}{a}{b}{0.5}[{\unit[1/4]{L}}];
% \dimensioning{1}{b}{c}{0.5}[{\unit[3/4]{L}}];

% End Elements

### 2020-03-11 Figures/Block.tex
Cambios 11-3-2020

@@
 
-%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%
 \beam{2}{12}{7};
@@
 
-%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%
 \beam{2}{7}{4};
@@
 % Gravity
-\point{g}{12}{5};
-\load{1}{g}[90][3][0];
+\draw[->, line width=1mm] (12,6)--(12,4);
+\node[color=black, very thick] at (17,5)
+{\LARGE$\mathbf{g}(t)= \left\{
+    \begin{array}{ll}
+      0.5 \mathbf{g} (\sin(\frac{2t \pi}{T} - \frac{\pi}{2})+1)  & \mbox{if } t \leq T/2 \\
+      \mathbf{g} & \mbox{if } t > T/2
+    \end{array}
+  \right.$};
 
 % Cotas
-\dimensioning{1}{23}{36}{-1.5}[$10~m$];
-\dimensioning{2}{23}{1}{-1.5}[$10~m$];
+\dimensioning{1}{23}{36}{-2}[\LARGE$10~m$];
+\dimensioning{2}{23}{1}{-2}[\LARGE$10~m$];
+
+% GPS
+\draw plot [only marks, mark=square*] coordinates {(0.422650, 1.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(1.577350, 1.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(0.422650, 0.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(1.577350, 0.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(2.422650, 1.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(3.577350, 1.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(2.422650, 0.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(3.577350, 0.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(4.422650, 1.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(5.577350, 1.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(4.422650, 0.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(5.577350, 0.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(6.422650, 1.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(7.577350, 1.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(6.422650, 0.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(7.577350, 0.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(8.422650, 1.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(9.577350, 1.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(8.422650, 0.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(9.577350, 0.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(0.422650, 3.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(1.577350, 3.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(0.422650, 2.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(1.577350, 2.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(2.422650, 3.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(3.577350, 3.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(2.422650, 2.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(3.577350, 2.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(4.422650, 3.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(5.577350, 3.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(4.422650, 2.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(5.577350, 2.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(6.422650, 3.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(7.577350, 3.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(6.422650, 2.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(7.577350, 2.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(8.422650, 3.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(9.577350, 3.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(8.422650, 2.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(9.577350, 2.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(0.422650, 5.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(1.577350, 5.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(0.422650, 4.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(1.577350, 4.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(2.422650, 5.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(3.577350, 5.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(2.422650, 4.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(3.577350, 4.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(4.422650, 5.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(5.577350, 5.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(4.422650, 4.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(5.577350, 4.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(6.422650, 5.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(7.577350, 5.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(6.422650, 4.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(7.577350, 4.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(8.422650, 5.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(9.577350, 5.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(8.422650, 4.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(9.577350, 4.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(0.422650, 7.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(1.577350, 7.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(0.422650, 6.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(1.577350, 6.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(2.422650, 7.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(3.577350, 7.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(2.422650, 6.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(3.577350, 6.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(4.422650, 7.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(5.577350, 7.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(4.422650, 6.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(5.577350, 6.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(6.422650, 7.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(7.577350, 7.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(6.422650, 6.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(7.577350, 6.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(8.422650, 7.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(9.577350, 7.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(8.422650, 6.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(9.577350, 6.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(0.422650, 9.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(1.577350, 9.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(0.422650, 8.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(1.577350, 8.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(2.422650, 9.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(3.577350, 9.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(2.422650, 8.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(3.577350, 8.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(4.422650, 9.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(5.577350, 9.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(4.422650, 8.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(5.577350, 8.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(6.422650, 9.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(7.577350, 9.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(6.422650, 8.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(7.577350, 8.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(8.422650, 9.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(9.577350, 9.577350)}; 
+\draw plot [only marks, mark=square*] coordinates {(8.422650, 8.422650)}; 
+\draw plot [only marks, mark=square*] coordinates {(9.577350, 8.422650)};
 

### 2020-03-11 main.tex
Cambios II 10-3-2020
Cambios 11-3-2020
Cambios II 11-3-2020

@@
 \usepackage[ugly]{units}
+% \usetikzlibrary{decorations}
+% \usetikzlibrary{arrows}
+\usetikzlibrary{plotmarks}
 
@@
 % etc.
+
 %
@@
 
-\title{Novel improvements in the Material Point Method to face
-  dynamic problems: 
-  Local-maximum entropy approximation and an explicit   predictor-corrector scheme. \thanks{Funding: This
+% \title{Novel improvements in the Material Point Method to face
+%   dynamic problems: 
+%   Local-maximum entropy approximation and an explicit predictor-corrector scheme. \thanks{Funding: This
+%     study was funded by Agustín de Betancourt Foundation (grant number
+%     262390106114).}
+% }
+
+\title{Enhanced Material Point Method to face
+  dynamic problems:\thanks{Funding: This
     study was funded by Agustín de Betancourt Foundation (grant number
@@
 }
-% \subtitle{}
+\subtitle{Local-maximum entropy approximation and an explicit
+  predictor-corrector scheme}
 
@@
 
-\subsection{Analysis of the Explicit Predictor-Corrector accuracy}
-\label{sec:EPC-accuracy}
-
-In this section, the benchmark proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995} is considered to illustrate the
-capacity of the proposed time integration algorithm to avoid velocity
-fields instabilities.
-
-In the one-dimensional bar sketched in the figure \ref{fig:Dyka_Bar},
-the left end of the bar is fixed and the right and an initial velocity
-$v_0 = 5\ m/s$ is given to the last quarter of it in the x positive
-direction. The length of it is 0.1333 meters with an unit section.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \input{Figures/Dyka_bar.tex}}
-  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
-  \label{fig:Dyka_Bar}
-\end{figure}
-
-The elastic parameters consider for this test are:
-\begin{itemize} 
-\item  Density : $7833\ kg/m3$
-\item  Poisson ratio : $0$
-\item  Elastic modulus : $200 \cdot 10^9\ Pa$
-\end{itemize}
-
-The boundary conditions are:
-\begin{equation}
-  \label{eq:3}
-  \sigma \rvert_{x=L} = 0 \quad , \quad v \rvert_{x=0} = 0
-\end{equation}
-
-The total simulation time is 0.0002 seconds, a direct consequence of
-that is we let the elastic wave generated travel thorough the bar
-(from A to C and back to A) at least four times. For the spatial
-discretization we will set a mesh size of 3.3325 millimeters. The
-initial mesh will be composed by a single particle in the center of
-the element. Regarding this, here we give one consideration to
-properly modellize this benchmark under the MPM framework. Notice that
-the free border of the bar has a horizontal displacement of 0.033
-millimeters, therefore a computational domain with an extra gap of
-0.033 millimeters is required in order to accommodate the
-unconstrained displacement of the particles in the left border of the
-bar. Here below the time step is controlled by the courant number, in
-this case, we adopt a middle value of it (CFL=0.5) as a compromise
-between stability and numerical accuracy.
-
-The analytical solution in terms of velocity
-\ref{fig:vel_analytics_dyka}, and stress
-\ref{fig:stress_analytics_dyka} can be found in the appendix
-\ref{app:analytical_sol} given by the Method of characteristics.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/FE_vs_PCE_CFL_05}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-PCE-FE}
-\end{figure}
-
 \section{Local max-ent approximants}
@@
 
-\subsection{Error analysis MPM vs uGIMP vs MPM-\textit{max-ent}}
-\label{sec:study-error}
-
-For the convergence analysis, the root-mean-square (RMS) error in the
-displacement is computed. RMS error is defined as follows
-
-\begin{equation}
-  \label{eq:RMS}
-  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)^2},
-\end{equation}
-
-where $\phi_p$ and $\hat{\phi}_p$ are respectively the analytical and
-numerical solutions evaluated in the final time step in the position
-of each particle.
-
-\begin{figure*}\sidecaption
+% \subsection{Error analysis MPM vs uGIMP vs MPM-\textit{max-ent}}
+% \label{sec:study-error}
+
+% For the convergence analysis, the root-mean-square (RMS) error in the
+% displacement is computed. RMS error is defined as follows
+
+% \begin{equation}
+%   \label{eq:RMS}
+%   RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)^2},
+% \end{equation}
+
+% where $\phi_p$ and $\hat{\phi}_p$ are respectively the analytical and
+% numerical solutions evaluated in the final time step in the position
+% of each particle.
+
+\section{Analysis of the proposed improvements.}
+\label{sec:Analysis-proposed-improvements.}
+
+This section is devoted to test the ability of both predictor-corrector
+time integration scheme and the local \textit{max-ent} approximants to
+overcome spurious oscillations due to the grid crossing and high
+frequency loads under the context of the MPM.
+
+\subsection{Dyka bar}
+\label{sec:dyka-bar}
+
+High frequency , the benchmark proposed by Dyka \& Ingel
+(1995)\cite{Dyka1995} is considered to illustrate the
+capacity of the proposed time integration algorithm to avoid velocity
+fields instabilities.
+
+In the one-dimensional bar sketched in the figure \ref{fig:Dyka_Bar},
+the left end of the bar is fixed and the right and an initial velocity
+$v_0 = 5\ m/s$ is given to the last quarter of it in the x positive
+direction. The length of it is 0.1333 meters with an unit section.
+
+\begin{figure}\sidecaption
   \centering
-  \resizebox{0.7\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
+  \resizebox{\hsize}{!}{
+    \input{Figures/Dyka_bar.tex}}
+  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
+  \label{fig:Dyka_Bar}
+\end{figure}
+
+The elastic parameters consider for this test are:
+\begin{itemize} 
+\item  Density : $7833\ kg/m3$
+\item  Poisson ratio : $0$
+\item  Elastic modulus : $200 \cdot 10^9\ Pa$
+\end{itemize}
+
+The boundary conditions are:
+\begin{equation}
+  \label{eq:3}
+  \sigma \rvert_{x=L} = 0 \quad , \quad v \rvert_{x=0} = 0
+\end{equation}
+
+The total simulation time is 0.0002 seconds, a direct consequence of
+that is we let the elastic wave generated travel thorough the bar
+(from A to C and back to A) at least four times. For the spatial
+discretization we will set a mesh size of 3.3325 millimeters. The
+initial mesh will be composed by a single particle in the center of
+the element. Regarding this, here we give one consideration to
+properly modellize this benchmark under the MPM framework. Notice that
+the free border of the bar has a horizontal displacement of 0.033
+millimeters, therefore a computational domain with an extra gap of
+0.033 millimeters is required in order to accommodate the
+unconstrained displacement of the particles in the left border of the
+bar. Here below the time step is controlled by the courant number, in
+this case, we adopt a middle value of it (CFL=0.5) as a compromise
+between stability and numerical accuracy.
+
+The analytical solution in terms of velocity
+\ref{fig:vel_analytics_dyka}, and stress
+\ref{fig:stress_analytics_dyka} can be found in the appendix
+\ref{app:analytical_sol} given by the Method of characteristics.
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/FE_vs_PCE_CFL_05}
   }
   \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-MPM-uGIMP-LME}
-\end{figure*}
-
-\subsection{MPM versus OTM}
-\label{sec:mpm-versus-otm}
-
-MPM \cite{Sulsky1994} and OTM
-models to avoid tensile instabilities. Here we employ our in-house
-codes for both MPM and OTM simulations.
-
-The results are provided for the explicit predictor-corrector version
-of the MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM
-algorithms. For MPM, piecewise-linear, uGIMP and \textit{max-ent}
-basis functions are employed. The OTM algorithm is used only with
-\textit{max-ent} shape functions.
+  \label{fig:Dyka-PCE-FE}
+\end{figure}
+
+\subsection{Andersen block}
+\label{sec:andersen-block}
+
+In order to test the ability of this interpolation technique to deal
+with grid crossing instabilities, we will simulate the compression of
+a linear elastic soft soil due to the gravity force, \ref{fig:block}.
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \input{Figures/Block.tex}}
+  \caption{Geometrical description of a soil block }.}
+  \label{fig:block}
+\end{figure}
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/FE_vs_PCE_CFL_05}
+  }
+  \caption{Geometrical description of a soil block.}
+  \label{fig:block-MPM}
+\end{figure}
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_MPM.png}
+  }
+  \caption{Geometrical description of a soil block }.}
+\label{fig:block-MPM}
+\end{figure}
+
+% \subsection{MPM versus OTM}
+% \label{sec:mpm-versus-otm}
+
+% MPM \cite{Sulsky1994} and OTM
+% models to avoid tensile instabilities. Here we employ our in-house
+% codes for both MPM and OTM simulations.
+
+% The results are provided for the explicit predictor-corrector version
+% of the MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM
+% algorithms. For MPM, piecewise-linear, uGIMP and \textit{max-ent}
+% basis functions are employed. The OTM algorithm is used only with
+% \textit{max-ent} shape functions.
+
+% \begin{figure*}\sidecaption
+%   \centering
+%   \resizebox{0.7\hsize}{!}{
+%     \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
+%   }
+%   \caption{Velocity evolution at the point in the bar left side.}
+%   \label{fig:Dyka-MPM-uGIMP-LME}
+% \end{figure*}
 

### 2020-03-13 main.tex
Cambios 12-3-2020

@@
 
-\section{Analysis of the proposed improvements.}
-\label{sec:Analysis-proposed-improvements.}
+\section{Application to linear elasticity dynamic problems.}
+\label{sec:Application-linear-elasticity-dynamic-problems}
 
@@
 initial mesh will be composed by a single particle in the center of
-the element. Regarding this, here we give one consideration to
-properly modellize this benchmark under the MPM framework. Notice that
-the free border of the bar has a horizontal displacement of 0.033
-millimeters, therefore a computational domain with an extra gap of
-0.033 millimeters is required in order to accommodate the
-unconstrained displacement of the particles in the left border of the
-bar. Here below the time step is controlled by the courant number, in
-this case, we adopt a middle value of it (CFL=0.5) as a compromise
-between stability and numerical accuracy.
+the element.
+
+Regarding this, here we give one consideration to properly modellize
+this benchmark under the MPM framework. Notice that the free border of
+the bar has a horizontal displacement of 0.033 millimeters, therefore
+a computational domain with an extra gap of 0.033 millimeters is
+required in order to accommodate the unconstrained displacement of the
+particles in the left border of the bar. Here below the time step is
+controlled by the courant number, in this case, we adopt a middle
+value of it (CFL=0.5) as a compromise between stability and numerical
+accuracy.
 
@@
 In order to test the ability of this interpolation technique to deal
-with grid crossing instabilities, we will simulate the compression of
-a linear elastic soft soil due to the gravity force, \ref{fig:block}.
+with grid crossing instabilities we will simulate the vertical
+compression of a square block (10 by 10 meters) of soft soil sketched
+in figure \ref{fig:block} and loaded using an incremental gravitation scheme.
 
@@
 
+This test was taken from Andersen (2009)\cite{thesis_Andersen_2009}. The
+elastic parameters consider for this test are: 
+\begin{itemize} 
+\item  Initial density : $6\cdot 10^3\ kg/m^3$
+\item  Poisson ratio : $0$
+\item  Elastic modulus : $5\ MPa$
+\end{itemize}
+The gravity force is a apply as an external force according to the
+equations \eqref{eq:particle_body_forces},
+\eqref{eq:nodal_external_forces}. Using a total time period of T (20
+seconds) to apply the gravity, it is increased from 0 to 9.81$m/s$
+with a sinus function until T/2 and then maintained constant until T
+in order to arrive to a state of equilibrium, 
+\begin{equation}
+  \label{eq:gravity-load-block}
+ \mathbf{g}(t) = \left\{
+    \begin{array}{ll}
+      0.5 \mathbf{g} (\sin(\frac{2t \pi}{T} - \frac{\pi}{2})+1)  & \mbox{if } t \leq T/2 \\
+      \mathbf{g} & \mbox{if } t > T/2
+    \end{array}
+  \right.
+\end{equation}
+
+In order to get a stable solution, we will adopt a time step conducted
+by a Courant number of 0.1. On the other hand, the explicit predictor-corrector
+scheme is here employed looking forward getting better results. For the
+initial spatial discretization we will employ four particles per cell
+($\Delta x = 2\ m$). The initial setting of particles inside of the
+cell changes according to the interpolation technique adopted. For the
+bi-linear shape functions (Q4) and the LME shape functions, the initial
+position corresponds to the location of the gauss-points in a standard
+quadratic finite element. For the uniform-GIMP (uGIMP) shape function
+the initial position of each particle is located in the center of each
+voxel, due to the fact that in the initial situation, the voxel domain
+should not overlap each others, Steffen {\it et al.}
+(2008)\cite{Steffen2008}. Figure \ref{fig:vertical-displacement-block}
+shows the vertical displacement evolution of a point in the free
+surface of the block.
 \begin{figure}\sidecaption
@@
   \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/FE_vs_PCE_CFL_05}
-  }
-  \caption{Geometrical description of a soil block.}
-  \label{fig:block-MPM}
+    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
+  }
+  \caption{Comparative of the vertical displacement evolution in a
+    point located in the free surface employing different
+    interpolation schemes and numerical techniques.} 
+  \label{fig:vertical-displacement-block}
 \end{figure}
 
-\begin{figure}\sidecaption
+As we can see the simulation using the Q4 interpolation technique
+turns out to be unstable and in the second 15 it fails. The uGIMP
+simulation is more stable than the one performed by the Q4. Despite
+this is still unstable and could trigger severe oscillations if we
+pretend to simulate non-linear materials. The LME simulation was
+performed using two kinds of shape functions, one with a low value of
+the dimensionless parameter, $\gamma = 0.8$, and other with a larger
+value of it, $\gamma = 3.0$. Notice that the results are both
+stable, but the larger values of $\gamma$ give us a very stable
+solution. This is due to the fact that with larger value of $\gamma$,
+the shape functions behaves in a similar way to the FEM, which performs
+very accurate in those cases with a reasonable mesh distorsion, and
+with a lower value it behaves in a similar way to the uGIMP. This
+behaviour was noticed previously by \cite{Arroyo2006}, were authors
+highlight how by adjusting the spatial variation of $\beta(\vect{x})$,
+it is possible to select regions of the domain of analysis which are
+treated by finite elements and regions that are treated in the style
+of meshfree methods, with seamless transitions between those regions.
+
+Figure \ref{fig:Block-LME3} shows the evolution of the vertical stress
+during the loading process. The result is physically realistic as
+stress increments linearly from the top to the bottom of the specimen,
+and the value of the vertical stress in a material point located in
+the bottom of the specimen oscillates centered in $5.2 MPa$, which is
+the analytic value given by $\sigma_{yy} = \rho g h_y$.
+
+\begin{figure}
   \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_MPM.png}
-  }
-  \caption{Geometrical description of a soil block }.}
-\label{fig:block-MPM}
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[t = 0 seconds.]{
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_t0}
+    \label{fig:Block-LME3-PCE-t0}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \qquad
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[t = 5 seconds.]{
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_t025}
+    \label{fig:Block-LME3-PCE-t025}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \qquad
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[t = 20 seconds]{
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_t1}
+    \label{fig:Block-LME3-PCE-t1}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \caption{Vertical normal stress and position of material points
+    during the loading process for a soft soil ($E = 5\ MPa$, $\rho_0
+    = 6\cdot 10^3\ kg/m^3$). Numerical parameters considered for the
+    simulation are : Local \textit{max-ent} shape function $\gamma =3$
+    and explicit PC scheme with CFL 0.1.}
+  \label{fig:Block-LME3}
 \end{figure}

### 2020-03-14 ListaFiguras.tex
Pdf con fotos

--- 2020-03-10 main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is a general template file for the LaTeX package SVJour
-% for Springer journals.          Springer Heidelberg 2010/09/16
-%
-% Copy it to a new file with a new name and use it as the basis
-% for your article. Delete % signs as needed.
-%
-% This template includes a few options for different layouts and
-% content for various journals. Please consult a previous issue of
-% your journal as needed.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% First comes an example EPS file -- just ignore it and
-% proceed on the \documentclass line
-% your LaTeX will extract the file if required
-\begin{filecontents*}{example.eps}
-%!PS-Adobe-3.0 EPSF-3.0
-%%BoundingBox: 19 19 221 221
-%%CreationDate: Mon Sep 29 1997
-%%Creator: programmed by hand (JK)
-%%EndComments
-gsave
-newpath
-  20 20 moveto
-  20 220 lineto
-  220 220 lineto
-  220 20 lineto
-closepath
-2 setlinewidth
-gsave
-  .4 setgray fill
-grestore
-stroke
-grestore
-\end{filecontents*}
-%
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-% flush right qed marks, e.g. at end of proof
-\smartqed
+\documentclass{article}
 
 \usepackage[lofdepth,lotdepth]{subfig}
-% \usepackage{graphicx}
+
 %
@@
 \usepackage[ugly]{units}
+% \usetikzlibrary{decorations}
+% \usetikzlibrary{arrows}
+\usetikzlibrary{plotmarks}
 
-%\usepackage{latexsym}
-% etc.
-%
-
-% Matrix and vector nodes
-\newcommand{\Matrix}[1]{
-  \ensuremath{\mathbf{{#1}}}
-}
-\newcommand{\Vector}[1]{
-  \ensuremath{\mathbf{{#1}}}
-}
-
-% Divergence
-\newcommand{\Div}[1]{
-  \ensuremath{div({#1})}
-}
-% Gradient
-\newcommand\Grad[1]{grad({#1})}
-\newcommand\GradS[1]{grad^s({#1})}
-\newcommand\GradT[1]{grad^T({#1})}
-
-% Partial derivative
-\newcommand{\Deriv}[3][]{
-  \ensuremath{\frac{\partial^{#1}{#2}}{ \partial {#3}^{#1} }}
-}
-
-% Integral
-\newcommand{\Integral}[2]{
-  \IfStrEqCase{#1}{
-    {2}{\ensuremath{\int_{\varGamma_d}{#2}\ d\varGamma}}
-    {3}{\ensuremath{\int_{\varOmega}{#2}\ d\varOmega}}
-  }
-}
-
-%
-% Insert the name of "your journal" with
-\journalname{Computational Particle Mechanics}
-%
 \begin{document}
 
-\title{Novel improvements in the Material Point Method to face
-  dynamic problems: 
-  Local-maximum entropy approximation and an explicit   predictor-corrector scheme. \thanks{Funding: This
-    study was funded by Agustín de Betancourt Foundation (grant number
-    262390106114).}
-}
-% \subtitle{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\titlerunning{Novel improvements in the Material Point Method to face
-  dynamic problems.} % if too long for running head
-
-\author{Miguel Molinos \and
-  Pedro Navas \and
-  Manuel Pastor \and
-  Miguel Martín Stickle
-}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-% \institute{Miguel Molinos \at
-%   E.T.S de Ingenieros de Caminos, Canales y Puertos. \\
-%   Universidad Politéctnica de Madrid, 28040 Madrid, Spain \\
-%   \email{m.molinos@alumnos.upm.es}
-%   % \emph{Present address:} of F. Author  %  if needed
-%   \and
-%   Pedro Navas 
-%   \and
-%   Manuel Pastor
-%   \and
-%   Miguel Martín Stickle
-% }
-% \institute{Miguel Molinos, Pedro Navas and Manuel Pastor \at E.T.S
-%   de Ingenieros de Caminos, Canales y Puertos, Universidad Politéctnica de Madrid, 28040 Madrid, Spain, \; \email{m.molinos@outlook.es, pedro.navas@upm.es, manuel.pastor@upm.es}
-% }
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-\begin{abstract}
-  This document is devoted to describe the suitability of the Local
-  \textit{maximum-entropy} (LME) meshfree approximation technique under the framework of the
-  Material Point Method for dynamic problems. 
-  \keywords{LME \and MPM \and Dynamic problems}
-  % \PACS{PACS code1 \and PACS code2 \and more}
-  % \subclass{MSC code1 \and MSC code2 \and more}
-\end{abstract}
-
-\section{Introduction}
-\label{intro}
-Since the proposal of the Material Point Method (\textbf{MPM}) by
-Sulsky {\it  et al.} (1994)\cite{Sulsky1994} as a generalization to
-solids of the fluid implicit particle (FLIP) method
-\cite{Brackbill1986}. It popularity has increased due to its ability
-to deal with large strain regime without suffer mesh distortion
-inaccuracies. However, this method suffers other kind of
-instabilities, such those when material points crossing cell
-boundaries. This give rise to the development of other interpolation
-techniques to overcome this limitation such as the generalized
-interpolation material point method (GIMP) Bardenhagen \& Kober
-(2004)\cite{Bardenhagen2004}, the dual
-domain material point method (DDMP) Zhang {\it et al.}
-(2011)\cite{Zhang2011a}, the B-Spline MPM Tran {\it et al.}
-(2019)\cite{Tran2019a} or the Conservative Taylor
-Least Squares reconstruction Wobbes {\it et al.}
-(2018)\cite{E_Wobbes_2018}. This techniques are devoted to mitigate the
-``grid crossing'' error.
-Nevertheless, in the presence of shock waves spurious
-numerical noises appears despite of this using techniques \cite{Tran2019e}. These numerical
-inaccuracies also known as wiggles are due to the time discretization
-technique. A simple approach to face those spurious noises is to add a
-damping source to the equilibrium equations. To overcome this
-limitation, many researchers has proposed alternative time integration
-schemes which reduce them by filtering high-frequencies. Some of these
-attempts are the implicit GIMP (iGIMP) Charlton {\it et al.}
-(2017)\nocite{Charlton2017} or the generalised-$\alpha$ scheme for the
-MPM proposed by Tran \& Solowski (2019)\nocite{Tran2019e}.
-
-The aim of this paper is to mitigate this spurious oscillations by the
-employ of a suitable combination of the maximum-entropy (or local
-\textit{max-ent}) $\gamma$ family shape functions, and the proposal of a explicit 
-predictor-corrector scheme. Local \textit{max-ent} shape functions was
-first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006}, it belongs to the class of convex 
-approximation schemes and provides a seamless transition between
-finite elements (\textbf{FE}) and mesh-free interpolations. The
-approximation scheme is based on a compromise between minimizing the
-width of the shape function support and maximizing the information
-entropy of the approximation. The local \textit{max-ent} approximation
-may be regarded as a regularization, or \textit{thermalization}, of
-Delaunay triangulation which effectively resolves the degenerate cases
-resulting from the lack of uniqueness of the triangulation. Local
-\textit{max-ent} basis functions possess many desirable properties for
-mesh-free algorithms. First of all, they are entirely defined by the
-nodal set and the domain of analysis. They are also non-negative,
-satisfy the partition of unity property, and provide an exact
-approximation for affine functions \cite{Arroyo2006}. Furthermore, as
-it is not based in a voxel discretization as the GIMP, it is no prone to suffer
-voxel domains overlap, which can introduce severe inaccuracies. This
-approximation scheme has been proof to have a good performance under
-the dynamic regime by other researchers like Navas {\it et al.}
-(2018)\cite{Navas2018a} and Li {\it et al.} (2012)\cite{Li2012} for
-Optimal Transportation Meshfree (\textbf{OTM}) method. And more
-recently under the MPM framework by Wobbes {\it et
-  al.}(2020)\cite{Wobbes2020} but limiting the $\gamma$ parameter to
-zero. On the other hand, the time integration scheme here proposed is an accommodation of
-the Newmark a-form ($\gamma = 0.5$ and $\beta = 0$)\footnote{Notice
-that these $\gamma$ and $\beta$ parameters does not have the same
-meaning for the LME shape functions.} which is the central difference
-explicit (CD). We have choose this method among other suitable
-alternatives as Wilson {\it et al.} (1972)\nocite{Wilson1972} or Chung
-\& Hulbert (1993)\nocite{Geranlized_alpha_1993} because it simplicity
-and it good performance dealing with solids dynamics problems like those
-presented in \cite{Navas2018a}.
-
-The article is organized as follows. Section \ref{sec:Notation}
-briefly reviews the notation here employed. Next, Section \ref{sec:derivation-mpm}
-is devoted to present briefly the governing equations of the elastic
-problem, the variational formulation and the Galerkin procedure. In Section \ref{sec:epc-algor-mpm} an explicit predictor-corrector
-time integration scheme for the MPM is proposed. Section
-\ref{sec:local-max-ent} briefly reviews the local \textit{max-ent}
-basis functions here employed. In Section \ref{sec:dynamic-benchmark}
-a comparison between both methods MPM and OTM employing \textit{max-ent} shape
-function is performed as well a parametric study for the $\gamma$
-parameter. Both techniques will face to solve a classic dynamic
-benchmark proposed by Dyka \& Ingel (1995)\cite{Dyka1995}. Finally,
-conclusions and future research topics are exposed in Section \ref{sec:conclusions}.
-
-\section{Brief note concerning the notation}
-\label{sec:Notation}
-In what follows, we will adopt the following convention. All the
-physical variables involved in this problem are collected in Table
-\ref{tab:notation-table}.
-
-\begin{table}
-  \centering
-  \caption{Physical variables involved in the problem}
-  \label{tab:notation-table}
-  \begin{tabular}{c c c}
-    $\rho$ & Density field & Scalar \\
-    $\vect{a}$ & Acceleration field & First order tensor \\
-    $\vect{v}$ & Velocity field & First order tensor \\
-    $\vect{u}$ & Displacement field & Second order tensor \\
-    $\tens{\sigma}$ & Cauchy stress tensor & Second order tensor \\
-    $\tens{\varepsilon}$ & Cauchy strain tensor & Second order tensor \\
-    $\tens{D}$ & Constitutive tensor & Fourth order tensor\\
-  \end{tabular}
-\end{table}
-
-Three kind of subscript or superscript are used within paper. The
-subscript $\qed_p$ is used to define a particle variable. While the
-subscript $\qed_I$ is reserved in this notation for denoting nodal
-variables. And finally, the superscript $\qed^{\psi}$ involves a virtual
-magnitude. For the operators, the convention is : $\dot{\qed}$ and
-$\ddot{\qed}$ for the first and second time derivative, $\qued \otimes
-\qued$ means the dyadic operator, $(\cdot)$ and $(\colon)$ means the first
-and second contraction of a tensor, $\Div{\qed}$
-denotes the divergence operator, and finally $\Grad{\qed}$ and
-$\GradS{\qed}$ denotes the gradient and its symmetric part. Einstain
-subscripts convention is adopted so repeated index means addition.
-
-\section{Derivation of the MPM}
-\label{sec:derivation-mpm}
-The aim of this section is to provide an overview of
-the standard explicit MPM algorithm \cite{Sulsky1994}. Therefore, it
-is structured in the following shape: we will first give a
-introduction to the governing equations \ref{sec:governing-equations},
-later the variational statement of the problem will be presented
-\ref{sec:variational-formulation}, and finally a discretization
-procedure thorough Galerkin is performed \ref{sec:Galerkin-procedure}.
-
-The method has three main steps: (i) a variational recovery process,
-where particle data is projected to the grid nodes, (ii) an Eulerian
-step, where balance of momentum equation is expressed as a nodal
-equilibrium equation thorough a FEM-like procedure, and finally (iii) a Lagrangian advection of the particles.
-
-\subsection{Governing equations }
-\label{sec:governing-equations}
-In the MPM approach a continuum is considered. Let define a
-$\varOmega$ domain occupied by an elastic body, and $\partial
-\varOmega$ the boundary of the domain, where $\partial
-\varOmega = \Gamma_d \bigcup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n =
-\emptyset$. Note that $\varGamma_d$ is reserved for Dirichlet boundary
-conditions, and  $\varGamma_n$ for the Neumann. In a inifinitesimal
-strain context, the behaviour of the continuum can be described by the
-following set of equations:
-(i) the balance of momentum equation
-\begin{equation}
-  \label{eq:Balance-momentum}
-\rho \vect{a} = \Div{\tens{\sigma}} + \rho \vect{b},
-\end{equation}
-(ii) the compatibility equation with ensure that the velocity
-field is compatible with the Cauchy strain field,
-\begin{equation}
-  \label{eq:Compatibility-equation}
-  \dot{\tens{\varepsilon}} = \GradS{\vect{v}},
-\end{equation}
-(iii) the constitutive equation, which relates the rate of Cauchy strain
-tensor with the rate of Cauchy stress tensor,
-\begin{equation}
-  \label{eq:Constitutive-equation}
-\dot{\tens{\sigma}} = \tens{D} \colon \dot{\tens{\varepsilon}},
-\end{equation}
-and finally (iv) the mass conservation, which can be obtained by
-setting to zero the total derivative of the density field,
-\begin{equation}
-  \label{eq:Rho-material-derivative}
-  \frac{D \rho}{D t} = \dot{\rho} + \rho \Div{\vect{v}} = 0.
-\end{equation}
-
-\subsection{Variational formulation}
-\label{sec:variational-formulation}
-To write the variational statement of the problem, let us define a
-virtual velocity field such that
-\begin{equation}
-  \label{eq:Hilbert-space}
-  \vect{v}^{\psi} \in \mathcal{H}^1_0(\Omega) = \{ \vect{v}^{\psi} \in
-  \mathcal{H}^1 \mid \vect{v}^{\psi} = \vect{0}\ \text{on}\ \Gamma_d \}.
-\end{equation}
-And which satisfies that the Cauchy sequences are convergent in $\varOmega$
-\begin{equation}
-  \label{eq:cauchy-secuence}
-  \Integral{3}{\vect{v}^{\psi}} < \infty\ \quad\text{and}\quad \Integral{3}{\tens{\varepsilon}^{\psi}} < \infty
-\end{equation}
-The principle of virtual work states that the equilibrium solution to
-the boundary value problem of elasticity is the function $\vect{v} \in
-\mathcal{H}^1_0$ such that, for $\vect{v}^{\psi} \in
-\mathcal{H}^1_0$, the following holds:
-\begin{equation}
-  \label{eq:BalanceMomentum_wf}
-  \Integral{3}{\rho\ \left( \Deriv{\vec{v}}{t}\ - \vec{b} \right) \cdot \vec{v}^{\psi}} =
-  \Integral{2}{\vec{t}\ \cdot \vec{v}^{\psi}} - \Integral{3}{\tens{\sigma} \colon
-    \tens{\varepsilon}^{\psi}},
-\end{equation}\\
-therefore (\ref{eq:BalanceMomentum_wf}) is the balance of momentum formulated in
-its weak form.
-
-\subsection{Galerkin procedure}
-\label{sec:Galerkin-procedure}
-In order to arrive to a finite set of equations, in contrast with the
-FEM, in the MPM a double discretization procedure is performed as we will
-describe here below. First, the continuum domain
-$\Omega$ is discretized with a finite sum of material points (in the
-following particles), each one
-represent a part of the discretized domain $\varOmega_p \subset
-\varOmega$ with $p = 1,2\ldots ,N_p$ where $N_p$ is the number of
-particles. The material point $\vec{x}_p$ is defined at the centroid
-of each $\Omega_p$, figure \ref{fig:MPM-discretization}.
 \begin{figure}\sidecaption
@@
   }
-  \caption{MPM discretization.}
+  \caption{Discretization used in the material point method.}
   \label{fig:MPM-discretization}
@@
 
-Each material point is assigned with initial values of position,
-velocity, mass, volume and stress denoted by $\vec{x}_p$,
-$\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$, but also the
-virtual field $\vect{v}^{\psi}_{p}$. So employing the definition of the
-material integral, where we recover the Riemann integral definition as
-an addition  of a finite set of points. Therefore individual terms in
-\eqref{eq:BalanceMomentum_wf} are solved as follows. 
-\begin{itemize}
-\item Acceleration forces :
-\begin{equation}
-    \label{eq:particle_acceleration_forces}
-    \Integral{3}{\rho\ \vec{a} \cdot \vect{v}^{\psi}} =
-    \dot{\vec{v}}_{p} \cdot \vect{v}^{\psi}_{p}\ m_p.
-  \end{equation}\\
-\item Internal forces :
-  \begin{equation}
-    \label{eq:particle_internal_forces}
-    \Integral{3}{\tens{\sigma}\ \colon \tens{\varepsilon}^{\psi}} =
-   \tens{\sigma}_{p}\ \colon \tens{\varepsilon}^{\psi}_p \ V_p.
-  \end{equation}\\
-\item Body forces :
-\begin{equation}
-  \label{eq:particle_body_forces}
-  \Integral{3}{\rho\ \vec{b} \cdot \vect{v}^{\psi} } = 
-  \vec{b}_{p} \cdot \vect{v}^{\psi}_p\ m_p.
-\end{equation}\\
-\item Loads :
-\begin{equation}
-  \begin{aligned}
-    \label{eq:particle_load_forces}
-    \Integral{2}{\vec{t}\ \vect{v}^{\psi}} = \Integral{2}{\rho\
-      \vec{t}^s \cdot \vect{v}^{\psi}} = \vec{t}^s_{p} \cdot \vect{v}^{\psi}_{p}\ h^{-1}\ m_p ,
-  \end{aligned} 
-\end{equation}
-\end{itemize}
-where $h$ is the thickness of the continuum in a 2D case. Here is
-where the second discretization procedure appears. A background mesh
-composed by a finite set of grid points with coordinates $\vec{x}_I\
-, I = 1,2\ldots ,N_n$, is generated. Where $N_n$ is the number of grid
-nodes. This mesh is employed as a support to compute gradients and divergences.
-
-Introducing \eqref{eq:particle_acceleration_forces},
-\eqref{eq:particle_internal_forces}, \eqref{eq:particle_body_forces}, 
-and \eqref{eq:particle_load_forces} in \eqref{eq:BalanceMomentum_wf},
-and approximating the real and virtual velocity  field of the particle
-$p$ as
-\begin{equation}
-  \label{eq:Approx-velocity-mesh}
-  \vec{v}_{p} = N_I(\vec{x}_p) \vect{v}_I
-  \quad \text{and} \quad \vec{v}^{\psi}_{p} = N_I(\vec{x}_p) \vect{v}_I^{\psi},
-\end{equation}
-\begin{equation}
-  \label{eq:Approx-gradvelocity-mesh}
-  \Grad{\vect{v}}_p = \vect{v}_I N_I(\vec{x}_p)
-  \quad \text{and} \quad \vec{v}^{\psi}_{p} = \sum^{Nn}_I N_I(\vec{x}_p) \vect{v}_I^{\psi},
-\end{equation}
-we reach to the particle balance of forces of the continuum,
-\begin{equation}
-  \label{eq:particle_balance_forces3}
-  \dot{\vec{p}}_{I}= \tens{m}_{IJ}\dot{\vec{v}}_{J} = \vec{f}_{I}^{int} + \vec{f}_{I}^{ext},
-\end{equation}
-where $\dot{\vec{p}}_{I}$ is the rate of momentum at grid node $I$, the nodal mass matrix $\tens{m}_{IJ}$ is,
-\begin{equation}
-  \label{eq:particle_nod_mass}
-  \tens{m}_{IJ} =
-  \sum^{Np}_{p} N_{Ip} m_p N_{Jp}.
-\end{equation}
-To improve the computational efficiency and stability, the nodal mass matrix
-\eqref{eq:particle_nod_mass} can be substituted by the lumped mass
-matrix $\tens{m}_{IJ}^{lumped}$.
-Later, internal and external forces are computed as follows,
-\begin{equation}
-  \label{eq:nodal_internal_forces}
-  \vec{f}_{I}^{int} = - \sum^{N_p}_{p} \tens{\sigma}_{p} \cdot \Grad{N_{Ip}} \frac{m_p}{\rho_p}
-\end{equation}
-\begin{equation}
-  \label{eq:nodal_external_forces}
-  \vec{f}_{I}^{ext} = \sum^{N_p}_{p} N_{Ip} \vec{b}_{p} m_p  + \sum^{N_p}_{p}
-  N_{Ip} \vec{t}^s_{p} m_p h^{-1} 
-\end{equation}
-where $\tens{\sigma}_{p} = \tens{\sigma}_{p}(\tens{\varepsilon}_{p})$
-is the particle $p$ stress field, which can be integrated employing
-the suitable constitutive model. The strain tensor is updated employing the rate of stress tensor $\dot{ \tens{\varepsilon}}_{p}$ used to update the
-strain tensor is as follows \eqref{eq:IncrStrainPoint}.
-\begin{equation}
-  \label{eq:IncrStrainPoint}
-  \dot{\tens{\varepsilon}_{p}} = \frac{\Delta
-    \tens{\varepsilon}_{p}}{\Delta t} =
-  \frac{1}{2} \sum^{Nn}_I \left[\Grad{N_{Ip}}\ \otimes \vec{v}_{I} + \vec{v}_{I} \otimes
-    \Grad{N_{Ip}}\ \right].
-\end{equation}
-Next, imposing $\frac{D \rho}{D t} = 0$, we ensures the mass
-conservation and update the density field.
-\begin{equation}
-  \label{eq:MassConservation}
-\dot{\rho} = - \rho\ \mathit{tra} \left( \dot{\tens{\varepsilon}} \right)
-\end{equation}
-
-Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order
-temporal integration scheme is required. Therefore, time is
-discretized in to a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
-is the total number of time steps. Once the nodal equilibrium equation it is solved, the values in the nodes are
-interpolated back in to the particles and each particle it is advected
-to the new position,
-\begin{equation}
-  \label{eq:Updated_Lagrangian}
-  \dot{\vec{v}}_p = \sum^{N_n}_{I}N_{Ip}\ \vec{a}_{I},\quad and\quad
-  \dot{\vec{x}}_{p} = \sum^{N_n}_{I}N_{Ip}\ \vec{v}_{I}  
-\end{equation}
-In the MPM literature, this equations
-(\ref{eq:particle_balance_forces3}) and (\ref{eq:Updated_Lagrangian}),
-are solved with an explicit forward Euler algorithm. The time integration scheme of the MPM has been described in detail by many researchers
-\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and summarized
-in Figure \ref{fig:MPM_algorithm}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   \centering
-  \resizebox{0.55\hsize}{!}{
+  \resizebox{0.4\hsize}{!}{
     \includegraphics[width=\textwidth]{./Figures/MPM_scheme}
   }
-  \caption{MPM standard algorithm.}
+  \caption{Classic material point method algorithm.}
   \label{fig:MPM_algorithm}
@@
 
-Other authors have proposed many others time integration alternatives
-like \cite{Guilkey2003}, \cite{Tran2019e}, \cite{Charlton2017}. In the
-first publication on the MPM \cite{Sulsky1994}, the nodal acceleration
-was employed to update the particles as
-\begin{equation}
-  \label{eq:Sulsky-1994-UL-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
-  \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{a}_{I}^{k}
-\end{equation}
-\begin{equation}
-  \label{eq:Sulsky-1994-UL-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{v}_{I}^{k}.
-\end{equation}
-However, as Andersen (2009)\cite{thesis_Andersen_2009} point out, this algorithm has been shown to be numerically unstable due to that
-$\vect{f}_I^{int,k}$ can be finite for an infinitesimal nodal mass
-$\tens{m}$. This can lead to numerical issues when nodal acceleration
-is obtained for evaluating \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v}. Hence, a
-corrected version of this algorithm in shown in Zhang {\it et al.}
-(2016)\cite{Zhang_book_2016}
-\begin{equation}
-  \label{eq:Zhang-2016-UL-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \sum^{N_n}_{I} \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}.  
-\end{equation}
-\begin{equation}
-  \label{eq:Zhang-2016-UL-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
-  \sum^{N_n}_{I}\frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I},
-\end{equation}
-Later Tran \& Solowski (2019)\cite{Tran2019e} presented a
-generalized-$\alpha$ scheme for the MPM inspired in the explicit time
-integration algorithm proposed by Chung \& Hulbert
-(1993)\cite{Geranlized_alpha_1993}, but with the particularity that
-the acceleration is evaluated both in the beginning and the end of the
-time step.
-\begin{equation}
-  \label{eq:Tran-2019-GA-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
-  \sum^{N_n}_{I} N_{Ip}^{k}\ \left[(1 - \gamma)\ \vect{a}_I^{k} +
-    \gamma\ \vect{a}_I^{k+1} \right],\\
-\end{equation}
-\begin{equation}
-\label{eq:Tran-2019-GA-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + 
-  \sum^{N_n}_{I}N_{Ip}^{k} \left[ \Delta t\ \vec{v}_{I}^{k}+ \Delta t^2\left( (\frac{1}{2} - \beta)\
-    \vec{a}_{I}^{k} + \beta\ \vec{a}_{I}^{k+1} \right) \right]
-\end{equation}
-\begin{equation}
-  \label{eq:Tran-2019-GA-a}
-  \vect{a}_p^{k+1} = \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{a}_{I}^{k+1}.
-\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-This scheme has prof to damps out the higher frequency noises
-\cite{Tran2019e}. But it can present the same numerical instabilities
-as in \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v} when
-nodal masses become infinitesimal.
+\begin{figure}
+  \centering
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[Piecewise linear (Q4).]{
+    \includegraphics[width=0.23\columnwidth]{Figures/MPM_Shape_Fun}
+    \includegraphics[width=0.23\columnwidth]{Figures/MPM_Shape_Fun_dx}
+    \includegraphics[width=0.23\columnwidth]{Figures/MPM_Shape_Fun_dy}
+    \label{fig:MPM_Shape_Fun}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \qquad
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[Local \textit{max-ent} $\gamma=17$.]{
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_17_3_Shape_Fun}
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_17_3_Shape_Fun_dx}
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_17_3_Shape_Fun_dy}
+    \label{fig:LME_17.3_Shape_Fun}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \qquad
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[Uniform GIMP (uGIMP).]{
+    \includegraphics[width=0.23\columnwidth]{Figures/GIMP_Shape_Fun}
+    \includegraphics[width=0.23\columnwidth]{Figures/GIMP_Shape_Fun_dx}
+    \includegraphics[width=0.23\columnwidth]{Figures/GIMP_Shape_Fun_dy}
+    \label{fig:GIMP_Shape_Fun}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \qquad
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \subfloat[Local \textit{max-ent} $\gamma=10$.]{
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_10_0_Shape_Fun}
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_10_0_Shape_Fun_dx}
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_10_0_Shape_Fun_dy}
+    \label{fig:LME_10.0_Shape_Fun}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \qquad
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
+  \subfloat[Local \textit{max-ent} $\gamma=7$.]{
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_7_0_Shape_Fun}
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_7_0_Shape_Fun_dx}
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_7_0_Shape_Fun_dy}
+    \label{fig:LME_7.0_Shape_Fun}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \qquad
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
+  \subfloat[Local \textit{max-ent} $\gamma=5$.]{
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_5_0_Shape_Fun}
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_5_0_Shape_Fun_dx}
+    \includegraphics[width=0.23\columnwidth]{Figures/LME_5_0_Shape_Fun_dy}
+    \label{fig:LME_5.0_Shape_Fun}
+  }
+  \caption{Comparison of the local \textit{max-ent} shape function for
+    different values of $\gamma = \beta h^2$, the piecewise linear shape function
+    and the uniform GIMP shape function. The picture shows the nodal value
+    of each shape function and its derivatives evaluated in a material
+    point located in the center of the domain.}
+  \label{fig:LME_MPM}
+\end{figure}
 
-\section{Explicit predictor-corrector scheme for MPM.}
-\label{sec:epc-algor-mpm}
-
-In this section, an explicit predictor-corrector time integration
-scheme is presented. It is based in the Newmark a-form 
-$\gamma = 0.5$ and $\beta = 0$ which is the central difference
-explicit. This method is devoted to solve a system of equations of type
-\begin{equation*}
-  \Matrix{M}_{IJ}\ddot{\Vector{d}}_{J} + \Matrix{C}_{IJ}\dot{\Vector{d}}_{J} +
-  \Matrix{K}_{IJ}\Vector{d}_{J} = \Vector{F}_{I}.
-\end{equation*}
-
-As the MPM has a nodal stage, it is possible to apply this methods
-successfully in the MPM framework as was proved by
-\cite{Tran2019e}. Taking the predictor definition from the classic
-literature \cite{Hughes2000} and calculating nodal velocity, and
-updating particles position employing nodal values of velocity and
-acceleration. Therefore we get the following expression for the
-\textbf{predictor} stage for both velocity and displacement.
-\begin{equation}
-  \label{eq:5}
-  \vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
-  \underbrace{\sum^{N_n}_{I}N_{Ip}^k\ \vec{v}_{I}^{k}}_{\vec{v}_p^{k}} + \frac{1}{2}\Delta
-  t^2\ \underbrace{\sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{f}_{I}^{k}}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
-\end{equation}
-\begin{equation}
-  \label{eq:Predictor-velocity}
-  \vec{v}_I^{k+1} = \vec{v}_I^n + (1 - \gamma)\ \Delta t\ \vec{a}_I^k
-  \quad , \quad \vec{a}_I^k = \frac{\vec{f}_{I}^{k}}{\tens{m}_I^k}
-\end{equation}
-
-Consequently, the \textbf{corrector} stage for the nodal velocity is in the
-following way
-\begin{equation}
-  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{k+1} + \gamma\ \Delta t\
-  \vec{a}_I^{k+1} \quad , \quad  \vec{a}_I^{k+1} = \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}} 
-\end{equation}
-
-Notice that the predictor of the particle displacement is
-computed using information only from the predictor of the
-previous step. However, velocities are computed using half information
-of the past corrector and half of the past predictor. Therefore here we share
-similarities with the \textbf{leapfrog integration} which updates the
-position at full time step, but updates the velocity at half time
-steps. Notice also that with this approach the calculation of nodal
-momentum vales in not required, and particles velocities is just a
-post-process. So during the lagrangian step only the particles
-position is truly computed. This minimizes the information
-transference between the particles and nodes, and in consequence
-minimizes the associated error to this process.
-
-Due to its simplicity allows be implemented with minor modifications
-over a standard forward Euler. It is summarized in shape of
-pseudo-algorithm \ref{alg:PCE-algorithm}.
-
-\begin{algorithm}
-  \label{alg:PCE-algorithm}
-  \floatname{algorithm}{Algorithm}
-  \renewcommand{\thealgorithm}{}
-  \caption{Explicit Predictor-Corrector scheme}
-  \begin{algorithmic}[1]
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
-    \STATE \textbf{Explicit Newmark Predictor} ($\gamma = 0.5$):
-    \begin{equation*}
-      \vec{v}_I^{k+1} = \vec{v}_I^n + (1 - \gamma)\ \Delta t\ \vec{a}_I^k
-      \quad , \quad \vec{a}_I^k = \frac{\vec{f}_{I}^{k}}{\tens{m}_I^k}      
-    \end{equation*}
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Impose essential boundary conditions}:\\
-    At the fixed boundary, set $\vec{v}_{I}^{k+1} = 0$. 
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    % \STATE \textbf{Discard the previous nodal values}.
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Update mass matrix}:
-    \begin{equation*}
-      \tens{m}_{I} = \sum_{p}^{N_p}N_{Ip}^{k+1}\ m_p,
-    \end{equation*}
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Deformation tensor increment calculation}.
-    \begin{align*}
-      &\dot{\tens{\varepsilon}_{p}}^{k+1} = \frac{1}{2}\ \sum_{I}^{N_n}
-        \Grad{N_{Ip}^{k+1}}\vec{v}_{I}^{k+1} +
-        (\Grad{N_{Ip}^{k+1}}\vec{v}_{I}^{k+1})^T \\
-      &\Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\ \dot{\tens{\varepsilon}_{p}}^{k+1}
-    \end{align*}
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Update the density field}:
-    \begin{equation*}
-      \rho_p^{k+1} = \frac{\rho_p^k}{1 + \mathit{tra}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.
-    \end{equation*}
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Balance of forces calculation}:\\
-    Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
-    \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
-    \eqref{eq:nodal_internal_forces} and \eqref{eq:nodal_external_forces} in the time step $k+1$. In the
-    grid node $I$ is fixed in one of the spatial dimensions, set it to
-    zero to make the grid nodal acceleration zero in that direction.\\
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Explicit Newmark Corrector} ($\gamma = 0.5$):
-    \begin{equation*}
-      \vec{v}_{I}^{k+1} = \vec{v}_{I}^{k+1} + \gamma\ \Delta t\
-      \vec{a}_I^{k+1} \quad , \quad  \vec{a}_I^{k+1} = \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}  
-    \end{equation*}
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \STATE \textbf{Update particles position and velocity}:
-    \begin{align*}
-      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
-        \sum^{N_n}_{I} N_{Ip}^k\ \vec{v}_{I}^{k} +
-        \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
-      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
-        \sum^{N_n}_{I}\frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k}
-    \end{align*}
-  \end{algorithmic}
-\end{algorithm}
-
-\subsection{Analysis of the Explicit Predictor-Corrector accuracy}
-\label{sec:EPC-accuracy}
-
-In this section, the benchmark proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995} is considered to illustrate the
-capacity of the proposed time integration algorithm to avoid velocity
-fields instabilities.
-
-In the one-dimensional bar sketched in the figure \ref{fig:Dyka_Bar},
-the left end of the bar is fixed and the right and an initial velocity
-$v_0 = 5\ m/s$ is given to the last quarter of it in the x positive
-direction. The length of it is 0.1333 meters with an unit section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The elastic parameters consider for this test are:
-\begin{itemize} 
-\item  Density : $7833\ kg/m3$
-\item  Poisson ratio : $0$
-\item  Elastic modulus : $200 \cdot 10^9\ Pa$
-\end{itemize}
-
-The boundary conditions are:
-\begin{equation}
-  \label{eq:3}
-  \sigma \rvert_{x=L} = 0 \quad , \quad v \rvert_{x=0} = 0
-\end{equation}
-
-The total simulation time is 0.0002 seconds, a direct consequence of
-that is we let the elastic wave generated travel thorough the bar
-(from A to C and back to A) at least four times. For the spatial
-discretization we will set a mesh size of 3.3325 millimeters. The
-initial mesh will be composed by a single particle in the center of
-the element. Regarding this, here we give one consideration to
-properly modellize this benchmark under the MPM framework. Notice that
-the free border of the bar has a horizontal displacement of 0.033
-millimeters, therefore a computational domain with an extra gap of
-0.033 millimeters is required in order to accommodate the
-unconstrained displacement of the particles in the left border of the
-bar. Here below the time step is controlled by the courant number, in
-this case, we adopt a middle value of it (CFL=0.5) as a compromise
-between stability and numerical accuracy.
-
-The analytical solution in terms of velocity
-\ref{fig:vel_analytics_dyka}, and stress
-\ref{fig:stress_analytics_dyka} can be found in the appendix
-\ref{app:analytical_sol} given by the Method of characteristics.
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_05}
+  }
+  \caption{Velocity evolution in the bar left side. This picture
+    shows a comparison of both time integration algorithms,
+    the Forward-Euler (FE) and the Predictor-Corrector explicit (PCE).}
+  \label{fig:Velocity-Dyka-PCE-FE}
+\end{figure}
 
@@
   \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/FE_vs_PCE_CFL_05}
+    \includegraphics[width=\textwidth]{./Figures/Stress_FE_vs_PCE_CFL_05}
+  }
+  \caption{Stress evolution in the bar left side. This picture
+    shows a comparison of both time integration algorithms,
+    the Forward-Euler (FE) and the Predictor-Corrector explicit (PCE).}
+  \label{fig:Stress-Dyka-PCE-FE}
+\end{figure}
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_LME_gamma_comparative}
   }
   \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-PCE-FE}
+  \label{fig:Velocity-Dyka-LME-gamma-comparative}
 \end{figure}
 
-\section{Local max-ent approximants}
-\label{sec:local-max-ent}
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Velocity-Dyka-MPM-vs-OTM}
+\end{figure}
 
-The previous lines describe the main algorithm without defining an
-interpolation technique. A direct consequence of this, is that it is
-possible to adopt a width range of them. The MPM has been
-successfully applied to a wide range of problems due to its ability to
-deal with large strain problems without mesh distorsion issues inherent to
-mesh based methods like FE. However, in the simulations made with the
-original MPM, there are numerical noises when particles crossing
-the cell boundaries. Recently the local maximum-entropy (or local
-\textit{max-ent}) shape function first introduced by Arroyo \& Ortiz
-(2006)\cite{Arroyo2006} has been tested under the MPM framework by
-Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
-simulations performed with the maxent basis functions show
-considerably more accurate stress approximations for MPM. Although, in
-\cite{Wobbes2020} authors does not deep in $\beta$ parameter
-benefits. In this publication a parametric analysis of $\Beta$ will be
-performed in order to reach a compromise value that minimize the
-presence of wiggle without introducing an additional spurious behaviour.
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_Q4_vs_uGIMP_LME_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Velocity-Dyka-Q4-uGIMP-LME}
+\end{figure}
 
-The maximum-entropy estimate is defined as the type of statistical
-inference, which is the least biased possible on the given information
-\cite{Jaynes1957}. The basic idea of the shape functions based on such
-an estimate is to interpret the shape function $N_I(\vec{x})$ as the
-probability of $\vec{x}$ to obtain the value $\vec{x}_I$,  $I=1,
-\dots, n$. Here $n$ is the number of nodes in the domain.
-Taking Shannon's entropy as the starting point:
-\begin{equation}
-  \label{eq:Shannon-entropy}
-  H(p_1(\vec{x}),\ldots,p_n(\vec{x})) = -\sum^{N_n}_{I=1}{p_I(\vec{x})\log p_I }
-\end{equation}
-where $p_I(\vec{x})$ is the probability, equivalent to the mentioned
-shape function $N_I(\vec{x})$,  satisfying both the zeroth and
-first-order consistency. The least-biased approximation scheme is given by
-\begin{align*}
-  \text{(LME)} \hspace{0.15cm} \text{Maximize} \hspace{0.15cm} &H(p) = -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I } \nonumber \\
-  \text{subject to} \hspace{0.15cm} &p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \nonumber \\
-  &\sum_{I=1}^{N_n}{p_I} = 1 \nonumber \\
-  &\sum_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \nonumber 
-\end{align*}
-The local max-ent approximation schemes (LME) as a Pareto set,
-defined by \cite{Arroyo2006} is as follows 
-\begin{align*}
-  \text{(LME)}_{\beta} \hspace{0.15cm} \text{For fixed} \hspace{0.15cm}
-  \vec{x} \hspace{0.15cm} \text{minimise}  \nonumber \hspace{0.15cm} &f_{\beta}(\vec{x}, p) = \beta H(\vec{x},p) - H(p) \\
-  \text{subject to} \hspace{0.15cm} &p_I \ge 0, \hspace{0.2cm} \text{I=1, ..., n}  \\
-                                                                   &\sum_{I=1}^{N_n}{p_I} = 1 \\
-                                                                   &\sum_{I=1}^{N_n}{p_I \, \vec{x}_I} = \vec{x}
-\end{align*}
-for $\beta \in (0,\infty)$ is Pareto optimal. The unique solution of
-the local max-ent problem (LME)$_\beta$ is: 
-\begin{equation}
-  \label{eq:LME-p}
-p(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +  \vec{\lambda}  \;  (\vec{x}-\vec{x}_I)         \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
-\end{equation}
-where
-\begin{equation}
-  \label{eq:LME-Z}
-Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \, | \vec{x}-\vec{x}_I|^2 + \vec{\lambda}  \,  (\vec{x}-\vec{x}_I)  \right]}
-\end{equation}
-being $\vec{\lambda}^*(\vec{x})$ the unique minimiser  for $\log Z(\vec{x}, \vec{\lambda})$
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-In order to obtain the first derivatives of the shape function, it is  also necessary to compute~$\nabla p^*_I$ 
-\begin{equation}
-  \label{eq:LME-grad-p}
-\nabla p^*_I=p^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} p^*_J \, \nabla f^*_J\right)
-\end{equation}
-where
-\begin{equation}
-  \label{eq:LME-f}
-f^*_I(\vec{x},  \vec{\lambda},\beta)=-\beta \, |\vec{x}-\vec{x}_I|^2 + \vec{\lambda}   \,  (\vec{x}-\vec{x}_I)
-\end{equation}
-Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression:
-\begin{eqnarray}
-\nabla p^*_I &=& -p^*_I \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I) \label{eq26} 
-\end{eqnarray}
-%&&\mbox{
-where \tens{J} is the Hessian matrix, defined by:
-%} \nonumber \\&& \nonumber \\
-\begin{eqnarray}
-\tens{J}(\vec{x},  \vec{\lambda},\beta) &=& \frac{\partial \vec{r}}{\partial  \vec{\lambda}} \label{eq27} \\ 
-%&& \nonumber \\
-\vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \partial_{\vec{\lambda}}{\log{ Z( \vec{x},\vec{\lambda}})} 
-%\nonumber \\ &=&
-  =\sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I) \label{eq28} 
-\end{eqnarray}
-Note that, the objective of the above procedure is to find the
-$\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. The
-traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27})
-to calculate small increments of $\partial\vec{\lambda}$ in a
-Newton-Raphson approach. 
-Similar to alternative non-polynomial meshfree basis functions, the
-LME approximation scheme requires more than $d+1$ nodes to determine
-the values of the shape functions as well as their derivatives at any
-point in the convex hull of the nodal set, where $d$ is the dimension
-of the problem. Due to the FE-compatibility, the LME shape function is
-degenerated to linear finite element shape function if $d+1$
-neighbouring nodes are chosen as the support. The support size of LME
-shape functions may be controlled by adjusting a dimensionless
-parameter, $\gamma=\beta h^2$ (e.g. two dimensional example shown in
-figure. \ref{fig:LME_MPM})\cite{Arroyo2006}.
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \input{Figures/Block.tex}}
+  \caption{Geometrical description of a soil block }.}
+  \label{fig:block}
+\end{figure}
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
+  }
+  \caption{Comparative of the vertical displacement evolution in a
+    point located in the free surface employing different
+    interpolation schemes and numerical techniques.} 
+  \label{fig:vertical-displacement-block}
+\end{figure}
 
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[Piecewise linear (Q4).]{
-    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun_dy}
-    \label{fig:MPM_Shape_Fun}
+  \subfloat[t = 0 seconds.]{
+    \includegraphics[width=0.5\columnwidth]{Figures/Block_LME3_PCE_a_t0}
+    \label{fig:Block-LME3-PCE-t0}
   }
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[Local \textit{max-ent} $\gamma=17$.]{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun_dy}
-    \label{fig:LME_17.3_Shape_Fun}
+  \subfloat[t = 5 seconds.]{
+    \includegraphics[width=0.5\columnwidth]{Figures/Block_LME3_PCE_b_t025}
+    \label{fig:Block-LME3-PCE-t025}
   }
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[Uniform generalized interpolated material point.]{
-    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun_dy}
-    \label{fig:GIMP_Shape_Fun}
+  \subfloat[t = 20 seconds]{
+    \includegraphics[width=0.5\columnwidth]{Figures/Block_LME3_PCE_c_t1}
+    \label{fig:Block-LME3-PCE-t1}
   }
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \subfloat[Local \textit{max-ent} $\gamma=10$.]{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun_dy}
-    \label{fig:LME_10.0_Shape_Fun}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
-  \subfloat[Local \textit{max-ent} $\gamma=7$.]{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun_dy}
-    \label{fig:LME_7.0_Shape_Fun}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
-  \subfloat[Local \textit{max-ent} $\gamma=5$.]{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun_dy}
-    \label{fig:LME_5.0_Shape_Fun}
-  }
-  \caption{Local max-ent shape functions for a two-dimensional
-    arrangement of nodes, and spatial derivatives for several values
-    of $\gamma = \beta/h^2$.}
-  \label{fig:LME_MPM}
+  \caption{Vertical normal stress and position of material points
+    during the loading process for a soft soil ($E = 5\ MPa$, $\rho_0
+    = 6\cdot 10^3\ kg/m^3$). Numerical parameters considered for the
+    simulation are : Local \textit{max-ent} shape function $\gamma =3$
+    and explicit PC scheme with CFL 0.1.}
+  \label{fig:Block-LME3}
 \end{figure}
 
-Since  $p_I$  is defined in the entire domain, in practice, the
-function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
-10$^{-6}$, for example,  would ensure a reasonable range of
-neighbours, see \cite{Arroyo2006} for details. This tolerance defines
-the limit values of the influence radius and is used thereafter to
-find the neighbour nodes of a given integration point.
-In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
-influence area of the shape function is controlled by the Euclidean
-norm, therefore the search area is geometrically a circle in 2D, or a
-sphere in 3D. Building upon the idea of anisotropic shape functions,
-\cite{Kochmann2019} introduced an enhanced version of the original
-local max-ent scheme, which uses an anisotropic support to deal with
-tensile inestability. Nonetheless this is out of the scope of the
-present document but will be incorporated in future research.
-
-\subsection{Error analysis MPM vs uGIMP vs MPM-\textit{max-ent}}
-\label{sec:study-error}
-
-For the convergence analysis, the root-mean-square (RMS) error in the
-displacement is computed. RMS error is defined as follows
-
-\begin{equation}
-  \label{eq:RMS}
-  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)^2},
-\end{equation}
-
-where $\phi_p$ and $\hat{\phi}_p$ are respectively the analytical and
-numerical solutions evaluated in the final time step in the position
-of each particle.
-
-\begin{figure*}\sidecaption
-  \centering
-  \resizebox{0.7\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-MPM-uGIMP-LME}
-\end{figure*}
-
-\subsection{MPM versus OTM}
-\label{sec:mpm-versus-otm}
-
-MPM \cite{Sulsky1994} and OTM
-models to avoid tensile instabilities. Here we employ our in-house
-codes for both MPM and OTM simulations.
-
-The results are provided for the explicit predictor-corrector version
-of the MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM
-algorithms. For MPM, piecewise-linear, uGIMP and \textit{max-ent}
-basis functions are employed. The OTM algorithm is used only with
-\textit{max-ent} shape functions.
-
-\section{Conclusions}
-\label{sec:conclusions}
-
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
-%
-\section*{Conflict of interest}
-%
-The authors declare that they have no conflict of interest.
-
-\appendix
-\section{The analytical solution of the 1D Dyka benchmark}
-\label{app:analytical_sol}
-
-For the derivation of this analytical solution we will consider  the
-dynamic behaviour of a 1D elastic bar. The governing equations are the
-following: (i) The balance of linear momentum,
-\begin{equation}
-  \label{eq:1D-balance-linear-momentum}
-  \rho\ \Deriv{v}{t} = \Deriv{\sigma}{x},
-\end{equation}
-where $\sigma$ is the stress value, $\rho$ is the density, and 
-$v$ is the velocity. (ii) The constitutive model, which for convenience of the
-following developments will be written in terms of displacement and
-velocities as, 
-\begin{equation}
-  \label{eq:1D-constitutive-equation}
-  \Deriv{\sigma}{t} = E \Deriv{\varepsilon}{t},
-\end{equation}
-where $E$ is the elastic modulus. (iii) The compatibility equation
-also in terms of the velocity field,
-\begin{equation}
-  \label{eq:CompatibilityEquation_e}
-  \Deriv{\varepsilon}{t} = \Deriv{v}{x}.
-\end{equation}
-Next for simplicity, we will introduce \eqref{eq:CompatibilityEquation_e} in 
-\eqref{eq:1D-constitutive-equation}, so we get the following system of equations,
-\begin{align}
-  \label{eq:1D-balance-linear-momentum-II}
-  \Deriv{v}{t} &= \frac{1}{\rho}\ \Deriv{\sigma}{x}, \\
-  \label{eq:1D-constitutive-equation-II}
-  \Deriv{\sigma}{t} &= E\ \Deriv{v}{x}.
-\end{align}
-
-Introducing \eqref{eq:1D-constitutive-equation-II} in
-\eqref{eq:1D-balance-linear-momentum-II} and expressing the remaining
-equation in terms of the displacement, we reach the 1D wave
-equation for linear elastic materials,
-\begin{equation}
-  \label{eq:1D-wave-elastic}
-  \Deriv[2]{u}{t} = \frac{E}{\rho}\ \Deriv[2]{u}{x} = c^2\ \Deriv[2]{u}{x}
-\end{equation}
-where we have introduced the wave celerity $c$ as,
-\begin{equation}
-  \label{eq:1D-elastic-wave-celerity}
-  c = \sqrt{\frac{E}{\rho}}
-\end{equation}
-Alternative, rearranging both equations
-\eqref{eq:1D-balance-linear-momentum-II} and
-\eqref{eq:1D-constitutive-equation-II} it is possible to join them in a
-single system of equations as,
-\begin{equation}
-  \label{eq:System-stress-velocity}
-  \Deriv{}{t} \left[
-    \begin{array}{c}
-      \sigma \\
-      v
-    \end{array}
-  \right] + \left[
-    \begin{array}{cc}
-      0 & - E \\
-      - 1/\rho & 0 
-    \end{array} \right] \left[
-    \begin{array}{c}
-      \Deriv{\sigma}{x} \\
-      \Deriv{v}{x}
-    \end{array}
-  \right] = \Vector{0}.
-\end{equation}
-This expression can be written in a more compact format as,
-\begin{equation}
-  \label{eq:System-stress-velocity-II}
-  \Deriv{\Vector{\phi}}{t} + \Matrix{A}\Deriv{\Vector{\phi}}{x} = \Vector{0}
-\end{equation}
-where both variables are joined in a single vectorial variable
-$\Vector{\phi}$ and $\Matrix{A}$ in coupling matrix between both equations,
-\begin{equation*}
-  \Vector{\phi} = \left[
-    \begin{array}{c}
-      \sigma \\
-      v
-    \end{array}
-  \right],\quad 
-  \Matrix{A} =  \left[
-    \begin{array}{cc}
-      0 & - E\\
-      - 1/\rho & 0 
-    \end{array} \right].
-\end{equation*}
-Note that the nature of \label{eq:eq:System-stress-velocity-II} is still
-hyperbolic despite the fact it does not have a second order
-temporal derivative as \eqref{eq:1D-wave-elastic}. A proof of this can
-be easily obtained if we get the zeros of the hypersurface defined by
-\eqref{eq:1D-wave-elastic}. And later the eigenvalues of $\Matrix{A}$
-in \eqref{eq:System-stress-velocity-II}. In both cases, eigenvalues
-are real and distinct ($\lambda = \pm \sqrt{\frac{E}{\rho}}$),
-therefore the system is called strictly hyperbolic.
-
-For a more general description in the following, we will assume that $\Matrix{A}$ has $n$
-different eigenvalues $\{ \lambda_1, \lambda_2, \ldots, \lambda_i, \ldots
-\lambda_n \}$ and $n$ eigenvectors $\{ \vec{x}^1, \vec{x}^2, \ldots,
-\vec{x}^i, \ldots \vec{x}^n \}$ satisfying that $\tens{A} \vec{x} =
-\lambda \vec{x} $. Now we introduce the matrix $\Matrix{P}$ whose columns are the $n$
-eigenvalues $\Vector{x}$
-\begin{equation}
-  \label{eq:P-matrix}
-\Matrix{P} = \{ \vec{x}^1, \vec{x}^2, \vec{x}^3, \ldots \vec{x}^n \}.
-\end{equation}
-Diagonalizing $\Matrix{A}$ using $\Matrix{P}$ we get
-\begin{equation}
-  \label{eq:Lambda-matrix}
-  \Lambda = \Matrix{P}^{-1} \Matrix{A}\ \Matrix{P},
-\end{equation}
-where $ \Lambda_{ii} = \lambda_i$. Next we will define a vector $\Vector{\Re}$ such that:
-\begin{equation}
-  \label{eq:Riemann-definition}
-  \Vector{\phi} = \Matrix{P}\ \Vector{\Re}
-\end{equation}
-we will assume to be integrable. Expanding the above expression with
-the chain rule and passing the matrix $\Matrix{P}$ to left hand side
-of the equality we get,
-\begin{equation}
-  \label{eq:Riemann-II}
-  d \vec{\Vector{\Re}} = \Deriv{\Vector{\Re}}{t}dt + \Deriv{\Vector{\Re}}{x}dx =
-  \tens{P}^{-1}\left(\Deriv{\phi}{t}dt + \Deriv{\phi}{x}dx \right)
-\end{equation}
-and setting the terms we get,
-\begin{equation}
-  \label{eq:Riemann-III}
-  \Deriv{\Vector{\Re}}{t} = \Matrix{P}^{-1}\Deriv{\Vector{\phi}}{t},\quad 
-  \Deriv{\Vector{\Re}}{x} = \Matrix{P}^{-1}\Deriv{\Vector{\phi}}{x}
-\end{equation}
-Next, if we multiply \eqref{eq:System-stress-velocity-II} by
-$\Matrix{P}^{-1}$ we get:
-\begin{equation}
-  \label{eq:System-stress-velocity-III}
-  \Matrix{P}^{-1}\Deriv{\Vector{\phi}}{t} + \left(\Matrix{P}^{-1}\Matrix{A}\Matrix{P}
-  \right)\Matrix{P}^{-1} \Deriv{\Vector{\phi}}{x} = \Vector{0}
-\end{equation}
-finally introducing the expressions \eqref{eq:Riemann-III} we reach to
-\begin{equation}
-  \label{eq:System-stress-velocity-IV}
-  \Deriv{\Vector{\Re}}{t} + \varLambda \Deriv{\Vector{\Re}}{x} = \Vector{0}  
-\end{equation}
-which consists of $n$ uncoupled equations as $\varLambda$ is
-diagonal matrix as we can see in \eqref{eq:Lambda-matrix}. Each of this
-equations are 1D scalar convective transport equations, with solutions
-of the form:
-\begin{equation}
-  \label{eq:SystemEquations_sigma_v_VI}
-  \Re^{(i)} = F^{(i)} \left(x - \lambda^{(i)} t \right)
-\end{equation}
-
-This uncoupled system, has, therefore, a set of $n$ characteristics.
-These magnitudes $\Re_i$ which propagate along characteristics are
-known as ``Riemann invariants'' of the problem. Here we have a 1D
-configuration, so the domain is $\Omega : \left(0, L\right) x \left(0,
-  T\right)$. For the closure of the problem we require:
-\begin{itemize}
-\item ``n'' initial conditions of the form $\Re_i (x,t=0) = h_i(x)$,
-  where $i = {0, \ldots, n}$, and $h_i(x)$ is a vectorial function
-  given by the physical variables of the problem.
-\item ``n'' boundary conditions.
-\end{itemize}
-
-Now particularizing the previous equations for the 1D elastic bar
-described in \cite{Dyka1995}, we get that the matrix $\Matrix{P}$
-is the following:
-\begin{equation*}
-    \Matrix{P} =  \left[
-    \begin{array}{cc}
-      -\sqrt{E\rho} & \sqrt{E\rho}\\
-       1 & 1 
-    \end{array} \right]
-\end{equation*}
-and its inverse is:
-\begin{equation*}
-    \Matrix{P}^{-1} = \frac{1}{2\ \sqrt{E\rho}} \left[
-    \begin{array}{cc}
-      -1 & \frac{1}{\sqrt{E\rho}}\\
-      1 & \frac{1}{\sqrt{E\rho}} 
-    \end{array} \right]
-\end{equation*}
-
-And introducing the value of the inverse matrix $\Matrix{P}^1$ in the
-Riemann definition \eqref{eq:Riemann-definition} we get the following
-system of equations,
-\begin{align}
-  \label{eq:Riemann-I-1D-elastic-bar}
-  &\Re^{I} = \frac{1}{2\sqrt{\rho E}}\left(-\sigma + v\ \sqrt{\rho E}
-    \right)\\
-  \label{eq:Riemann-II-1D-elastic-bar}
-  &\Re^{II} = \frac{1}{2\sqrt{\rho E}}\left(\sigma + v\ \sqrt{\rho E} \right)
-\end{align}
-
-From \eqref{eq:Riemann-I-1D-elastic-bar} and
-\eqref{eq:Riemann-II-1D-elastic-bar} we can obtain the values of the
-stress and the velocity as:
-\begin{equation}
-  \label{eq:Riemann-stress-velocity}
-  v = \Re^{I} + \Re^{II} \quad , \quad \sigma = \sqrt{E \rho}\left(\Re^{II} - \Re^{I} \right)
-\end{equation}
-
-The boundary conditions are in both cases of radiation as there is not
-wave in-going from the exterior. So for the right side (fixed
-boundary) we get the following conditions:
-\begin{equation*}
-  \Re^{II} = 0 \quad and \quad v_{x=L} = 0
-\end{equation*}
-Therefore $\sigma_{x=L} = -2\sqrt{\rho E}\ \Re^{I}$. And in the left side
-(free boundary) we get the following conditions:
-\begin{equation*}
-  \Re^{I} = 0 \quad and \quad \sigma_{x=0} = 0
-\end{equation*}
-Therefore $v_{x=0} = 2\Re^{II}$. Finally, applying this conditions in
-the elastic bar sketched in \ref{fig:Dyka_Bar}, is possible to obtain
-the velocity history in the right side of the bar
-\ref{fig:vel_analytics_dyka} and the stress in the last quarter side of the Dyka
-bar \ref{fig:stress_analytics_dyka} as is demanded in \cite{Dyka1995}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% BibTeX users please use one of
-%\bibliographystyle{spbasic}      % basic style, author-year citations
-\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-\bibliography{Biblio.bib}   % name your BibTeX data base
-
 \end{document}
-% end of file template.tex
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2020-03-15 ListaFiguras.tex
Cambios 14-3-2020

@@
   \centering
-  \resizebox{\hsize}{!}{
+  \resizebox{0.85\hsize}{!}{
     \input{Figures/Dyka_bar.tex}}
@@
   \centering
-  \resizebox{\hsize}{!}{
+  \resizebox{0.85\hsize}{!}{
     \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_05}
@@
   \caption{Velocity evolution in the bar left side. This picture
-    shows a comparison of both time integration algorithms,
+    shows a comparison between both time integration algorithms,
     the Forward-Euler (FE) and the Predictor-Corrector explicit (PCE).}
@@
   \centering
-  \resizebox{\hsize}{!}{
+  \resizebox{0.85\hsize}{!}{
     \includegraphics[width=\textwidth]{./Figures/Stress_FE_vs_PCE_CFL_05}
@@
   \caption{Stress evolution in the bar left side. This picture
-    shows a comparison of both time integration algorithms,
+    shows a comparison between both time integration algorithms,
     the Forward-Euler (FE) and the Predictor-Corrector explicit (PCE).}
@@
   \centering
-  \resizebox{\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_LME_gamma_comparative}
+  \resizebox{0.85\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_LME_gamma_comparative}
   }
-  \caption{Velocity evolution at the point in the bar left side.}
+  \caption{Velocity evolution in the bar left side. This picture
+    shows how variation of $\gammma$ affect in a simulation
+    with no grid grossing.}
   \label{fig:Velocity-Dyka-LME-gamma-comparative}
@@
   \centering
-  \resizebox{\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
+  \resizebox{0.85\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
   }
-  \caption{Velocity evolution at the point in the bar left side.}
+  \caption{Velocity evolution in the bar left side. This picture
+    shows a comparison between the optimal transportation mesh-free
+    (OTM) method and the material point method (MPM) using the same
+    time integration scheme and and spacial discretization.}
   \label{fig:Velocity-Dyka-MPM-vs-OTM}
@@
   \centering
-  \resizebox{\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_Q4_vs_uGIMP_LME_Dyka}
+  \resizebox{0.85\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_Q4_vs_uGIMP_LME_Dyka}
   }
-  \caption{Velocity evolution at the point in the bar left side.}
+  \caption{Velocity evolution in the bar left side. This picture
+    shows a comparison between the three different interpolation
+    techniques using the explicit predictor corrector to perform the
+    simulations.}
   \label{fig:Velocity-Dyka-Q4-uGIMP-LME}
@@
   \centering
-  \resizebox{\hsize}{!}{
+  \resizebox{0.8\hsize}{!}{
     \input{Figures/Block.tex}}
-  \caption{Geometrical description of a soil block }.}
+  \caption{Initial setting of material points and grid nodes in the
+    soil block. The soil is fixed horizontally along the vertical
+    walls and vertically along the bottom. The units of the axis are meters.}}
   \label{fig:block}
@@
   \centering
-  \resizebox{\hsize}{!}{
+  \resizebox{0.9\hsize}{!}{
     \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
@@
   \centering
-  \resizebox{\hsize}{!}{
+  \resizebox{0.9\hsize}{!}{
     \includegraphics[width=\columnwidth]{Figures/1D_right_Velocity.png}
@@
   \centering
-  \resizebox{\hsize}{!}{
+  \resizebox{0.9\hsize}{!}{
     \includegraphics[width=\columnwidth]{Figures/1D_left_Stress.png}

### 2020-03-15 Figures/Timoshenko_Analytical.py
Solución Analítica barra Timoshenko

@@ -1,0 +1,36 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+L = 8
+c = 0.5
+D= 2*c
+# c = np.sqrt(3)/2
+nu = 0.3
+E = 3E5
+P = 100
+I = (1/12)*(2*c)**3
+
+DeltaX = 0.1
+Nx = int(L/DeltaX)
+Ny = int(2*c/DeltaX)
+x0 = np.linspace(0,L,Nx)
+y0 = np.linspace(-c,c,Ny)
+X0, Y0 = np.meshgrid(x0, y0, indexing='ij', sparse=False)
+
+Xf = np.zeros([Nx,Ny])
+Yf = np.zeros([Nx,Ny])
+
+for i in range(0,Nx):
+    for j in range(0,Ny):
+
+        Xf[i][j] = X0[i][j] + P*Y0[i][j]/(6*E*I)*((6*L-3*X0[i][j])*X0[i][j] + (2+nu)*(Y0[i][j]**2 - (D**2)/4 ))
+        Yf[i][j] = Y0[i][j] - P/(6*E*I)*(3*nu*Y0[i][j]**2*(L-X0[i][j]) + (4+5*nu)*X0[i][j]*(D**2)/4 + (3*L-X0[i][j])*X0[i][j]**2)
+
+
+fig, ax = plt.subplots()
+# ax.scatter(X0,Y0)
+ax.scatter(Xf,Yf)
+ax.axis('equal')
+fig.tight_layout()
+plt.grid()
+plt.show()

### 2020-03-20 main.tex
Cambios 14-3-2020
Cambios 20-3-2020

@@
 %%EndComments
+
 gsave
@@
 }
-\subtitle{Local-maximum entropy approximation and an explicit
+\subtitle{Local-maximum entropy approximation and explicit
   predictor-corrector scheme}
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
-    \STATE \textbf{Explicit Newmark Predictor} ($\gamma = 0.5$):
+    \STATE \textbf{Explicit Newmark Predictor} ($\gamma = 0.5$):\\
+    Only in those active nodes:
     \begin{equation*}
@@
 
-The previous lines describe the main algorithm without defining an
-interpolation technique. A direct consequence of this, is that it is
-possible to adopt a width range of them. The MPM has been
-successfully applied to a wide range of problems due to its ability to
-deal with large strain problems without mesh distorsion issues inherent to
-mesh based methods like FE. However, in the simulations made with the
-original MPM, there are numerical noises when particles crossing
-the cell boundaries. Recently the local maximum-entropy (or local
-\textit{max-ent}) shape function first introduced by Arroyo \& Ortiz
-(2006)\cite{Arroyo2006} has been tested under the MPM framework by
-Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
+% The previous lines describe the main algorithm without defining an
+% interpolation technique, so we are free to apply a wide range of the
+% existing.
+
+The popularity of the MPM has increase notoriously during
+the recent years due to its ability to deal with large strain problems
+without mesh distorsion issues inherent to mesh based methods like
+FE, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations made with the original MPM, there are
+numerical noises when particles crossing the cell boundaries. Recently
+the local maximum-entropy (or local \textit{max-ent}) shape function
+first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} has been
+tested under the MPM framework by Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
 simulations performed with the maxent basis functions show
 considerably more accurate stress approximations for MPM. Although, in
-\cite{Wobbes2020} authors does not deep in $\beta$ parameter
-benefits. In this publication a parametric analysis of $\Beta$ will be
-performed in order to reach a compromise value that minimize the
-presence of wiggle without introducing an additional spurious behaviour.
-
-The maximum-entropy estimate is defined as the type of statistical
-inference, which is the least biased possible on the given information
-\cite{Jaynes1957}. The basic idea of the shape functions based on such
+\cite{Wobbes2020} authors does not deep in how $\beta$ affects to the
+accuracy and stability of the solution.
+
+The basic idea of the shape functions based on such
 an estimate is to interpret the shape function $N_I(\vec{x})$ as the
@@
 \dots, n$. Here $n$ is the number of nodes in the domain.
+
+Taking the definition of entropy as a measure of how uncertainty a
+random variable is averaged on all its possible outcomes.
+
+Therefore following the principle of \textit{maximum-entropy}
+stated by Jaynes \cite{Jaynes1957}, the least biased shape functions
+are those that maximizes the entropy of the scheme
+
+estimate is defined as the type of statistical
+inference, which is the least biased possible on the given information.
+
 Taking Shannon's entropy as the starting point:
@@
 shape function $N_I(\vec{x})$,  satisfying both the zeroth and
-first-order consistency. The least-biased approximation scheme is given by
+first-order consistency.
+
+The least-biased approximation scheme is given by
 \begin{align*}
@@
 \end{align*}
+
 The local max-ent approximation schemes (LME) as a Pareto set,
@@
 Newton-Raphson approach.
+
 Similar to alternative non-polynomial meshfree basis functions, the
@@
 the limit values of the influence radius and is used thereafter to
-find the neighbour nodes of a given integration point.
+find the neighbour nodes of a given integration point. Regarding this
+aspect an important note in the implementation of this interpolation
+technique in the MPM is
+
 In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
@@
 present document but will be incorporated in future research.
-
-% \subsection{Error analysis MPM vs uGIMP vs MPM-\textit{max-ent}}
-% \label{sec:study-error}
-
-% For the convergence analysis, the root-mean-square (RMS) error in the
-% displacement is computed. RMS error is defined as follows
-
-% \begin{equation}
-%   \label{eq:RMS}
-%   RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)^2},
-% \end{equation}
-
-% where $\phi_p$ and $\hat{\phi}_p$ are respectively the analytical and
-% numerical solutions evaluated in the final time step in the position
-% of each particle.
 
@@
   \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/FE_vs_PCE_CFL_05}
+    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_05}
   }
@@
 \end{figure}
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_LME_gamma_comparative}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-LME-gamma}
+\end{figure}
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-OTM-MPM}
+\end{figure}
+
+For the convergence analysis, the root-mean-square (RMS) error in the
+velocity field is computed. RMS error is defined as follows
+
+\begin{equation}
+  \label{eq:RMS}
+  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
+\end{equation}
+
+where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
+numerical solutions evaluated in the final time step in the position
+of each particle.
+
+\begin{figure*}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Error_evol}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-error-evol}
+\end{figure*}
 
@@
   \subfloat[t = 0 seconds.]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_t0}
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_a_t0}
     \label{fig:Block-LME3-PCE-t0}
@@
   \subfloat[t = 5 seconds.]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_t025}
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_b_t025}
     \label{fig:Block-LME3-PCE-t025}
@@
   \subfloat[t = 20 seconds]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_t1}
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_c_t1}
     \label{fig:Block-LME3-PCE-t1}
@@
 \label{sec:conclusions}
-
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
+We have developed a new time integration scheme for the MPM, and
+proved how local \textit{max-ent} arise as a promising tool to
+overcome the grid-crossing error.
+
+adapt the value of $\beta$ to solve the equations fem-like of
+meshfree-like depending of how behaves the region
+
+This alternative technique overcome the constriction of the GIMP to
+regular mesh.
+
+The time integration here proposed mitigates the presence of wiggles
+and overshot
+
+future research :
+localization of the local max ent
+
+predictor-corrector for high dynamic problems like impact or
+collisions
+
+\begin{acknowledgements}
+If you'd like to thank anyone, place your comments here
+and remove the percent signs.
+\end{acknowledgements}
+
 %

### 2020-03-23 main.tex
Mejora figuras
Cambios text 23-03-2020

@@
 \usetikzlibrary{plotmarks}
+
+\usetikzlibrary{%
+    decorations.pathreplacing,%
+    decorations.pathmorphing%
+}
 
@@
 of each $\Omega_p$, figure \ref{fig:MPM-discretization}.
+
 \begin{figure}\sidecaption
   \centering
-  \resizebox{0.9\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Discretization_MPM}
-  }
+  \resizebox{\hsize}{!}{
+    \input{Figures/Discretization_MPM.tex}}
   \caption{MPM discretization.}
@@
 \end{figure}
+
+% \begin{figure}\sidecaption
+%   \centering
+%   \resizebox{0.9\hsize}{!}{
+%     \includegraphics[width=\textwidth]{./Figures/Discretization_MPM}
+%   }
+%   \caption{MPM discretization.}
+%   \label{fig:MPM-discretization}
+% \end{figure}
 
@@
   \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_05}
+    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_01}
   }
@@
   \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_LME_gamma_comparative}
+    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_LME_gamma_comparative}
   }
@@
   \label{fig:Dyka-LME-gamma}
+\end{figure}
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_uGIMP_vs_LME_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-uGIMP-LME}
 \end{figure}

### 2020-03-25 main.tex
Versión día 25-3-2020

@@
 \usepackage[lofdepth,lotdepth]{subfig}
-% \usepackage{graphicx}
+\usepackage{graphicx}
+\usepackage{subcaption}
+\usepackage{subfigure} % subfiguras
 %
@@
 \begin{abstract}
-  This document is devoted to describe the suitability of the Local
-  \textit{maximum-entropy} (LME) meshfree approximation technique under the framework of the
-  Material Point Method for dynamic problems. 
-  \keywords{LME \and MPM \and Dynamic problems}
+  Material Point Method (MPM) has arise in the recent years as an
+  alternative to Finite Element Method (FEM) under the large
+  deformation regime. However, the simulation of shock waves
+  propagation and other high frequency problems is still challenging
+  under this approach due the incapability of the standard MPM time
+  integration scheme to filter spurious noises. To overcome this
+  limitation in this paper a explicit predictor-corrector integration
+  method has been proposed. Its superior performance mitigates the
+  presence of spurious oscillations with minimal dissipation in high
+  frequency problems. Other source of numerical noise in the MPM is
+  due to the lack of smoothness of the interpolation functions, and
+  occurs due to material points crossing computational grid
+  boundaries. This noise results in spurious local variations at the material
+  points, where strain-stress fields are computed. This could invalidate
+  the solution in one case, or damage it in another. To overcome it,
+  this document adopts the \textit{local maximum-entropy approximation
+    schemes} (LME) a robust substitute for the wide range of shape
+  function in the MPM. Local \textit{max-ent} approximation may be regarded as a
+  \textit{thermalization} of Delaunay triangulation which resolves the
+  degenerate cases resulting from the lack or uniqueness of the
+  triangulation. Furthermore, by modifying one user-defined parameter they
+  are able to behave like finite elements or as a mesh-free
+  method. This capability allows to face a wide range of physics
+  with a single the shape function. Finally this paper demonstrates
+  the performance of both improvements thorough numerical examples.    
+  \keywords{LME \and MPM \and Explicit predictor-corrector \and Dynamic problems}
   % \PACS{PACS code1 \and PACS code2 \and more}
@@
 \label{intro}
-Since the proposal of the Material Point Method (\textbf{MPM}) by
-Sulsky {\it  et al.} (1994)\cite{Sulsky1994} as a generalization to
-solids of the fluid implicit particle (FLIP) method
-\cite{Brackbill1986}. It popularity has increased due to its ability
-to deal with large strain regime without suffer mesh distortion
-inaccuracies. However, this method suffers other kind of
-instabilities, such those when material points crossing cell
-boundaries. This give rise to the development of other interpolation
-techniques to overcome this limitation such as the generalized
-interpolation material point method (GIMP) Bardenhagen \& Kober
-(2004)\cite{Bardenhagen2004}, the dual
-domain material point method (DDMP) Zhang {\it et al.}
-(2011)\cite{Zhang2011a}, the B-Spline MPM Tran {\it et al.}
-(2019)\cite{Tran2019a} or the Conservative Taylor
-Least Squares reconstruction Wobbes {\it et al.}
-(2018)\cite{E_Wobbes_2018}. This techniques are devoted to mitigate the
-``grid crossing'' error.
-Nevertheless, in the presence of shock waves spurious
-numerical noises appears despite of this using techniques \cite{Tran2019e}. These numerical
-inaccuracies also known as wiggles are due to the time discretization
-technique. A simple approach to face those spurious noises is to add a
-damping source to the equilibrium equations. To overcome this
-limitation, many researchers has proposed alternative time integration
-schemes which reduce them by filtering high-frequencies. Some of these
-attempts are the implicit GIMP (iGIMP) Charlton {\it et al.}
-(2017)\nocite{Charlton2017} or the generalised-$\alpha$ scheme for the
-MPM proposed by Tran \& Solowski (2019)\nocite{Tran2019e}.
-
-The aim of this paper is to mitigate this spurious oscillations by the
-employ of a suitable combination of the maximum-entropy (or local
-\textit{max-ent}) $\gamma$ family shape functions, and the proposal of a explicit 
-predictor-corrector scheme. Local \textit{max-ent} shape functions was
-first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006}, it belongs to the class of convex 
+Since the proposal of the MPM by Sulsky {\it  et al.}
+(1994)\cite{Sulsky1994} as a generalization to solids of the Fluid
+Implicit Particle (FLIP) method \cite{Brackbill1986}. It popularity
+has increased due to its ability to deal with large strain regime
+without suffer mesh distortion inaccuracies.
+
+However, this method suffers other kind of instabilities, such those
+when material points crossing cell boundaries. This give rise to the
+development of other interpolation techniques to overcome this
+limitation such as the generalized interpolation material point method
+(GIMP) Bardenhagen \& Kober (2004)\cite{Bardenhagen2004}, which has
+demonstrate to have a good performance in the finite deformation
+regime. However, in the absence of a regular grid, construction of the
+weighting functions is only achieved at considerable effort and
+computational cost. Furthermore, as it is based in a voxel
+discretization, it is prone to suffer voxel domains overlap or gaps when the
+material point mesh becomes irregular, which can introduce severe
+inaccuracies. This is similar to the difficulty encountered by the
+finite element methods due to element distortion.
+A more robust alternative is the dual domain material point method
+(DDMP) proposed by Zhang {\it et al.}
+(2011)\cite{Zhang2011a}. Unfortunately this method shows an
+unsatisfactory behaviour when particle/cell ratio
+decreases~\cite{DHAKAL2016301}, therefore DDMP requires a large number
+of particles needed for convergence, this
+makes the method very expensive.
+
+the B-Spline MPM
+Tran {\it et al.} (2019)\cite{Tran2019a}
+
+the Conservative Taylor Least Squares \textbf{CTLS} reconstruction Wobbes {\it et al.}
+(2018)\cite{E_Wobbes_2018}.
+
+Local \textit{max-ent} shape functions was first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006}, it belongs to the class of convex 
 approximation schemes and provides a seamless transition between
@@
 Delaunay triangulation which effectively resolves the degenerate cases
-resulting from the lack of uniqueness of the triangulation. Local
+resulting from the lack of uniqueness or the triangulation. Local
 \textit{max-ent} basis functions possess many desirable properties for
@@
 satisfy the partition of unity property, and provide an exact
-approximation for affine functions \cite{Arroyo2006}. Furthermore, as
-it is not based in a voxel discretization as the GIMP, it is no prone to suffer
-voxel domains overlap, which can introduce severe inaccuracies. This
+approximation for affine functions \cite{Arroyo2006}. This
 approximation scheme has been proof to have a good performance under
@@
   al.}(2020)\cite{Wobbes2020} but limiting the $\gamma$ parameter to
-zero. On the other hand, the time integration scheme here proposed is an accommodation of
+zero.
+
+This techniques are devoted to mitigate the
+``grid crossing'' error. Nevertheless, in the presence of shock waves spurious
+numerical noises appears despite of this using techniques
+\cite{Tran2019e}.
+
+These numerical inaccuracies also known as wiggles
+are due to the time discretization technique. A simple approach to
+face those spurious noises is to add a non-physical damping source to the
+equilibrium equations. To avoid this, many researchers
+has proposed alternative time integration schemes which reduce the
+presence of high-frequency noises by filtering them. Some of these
+attempts are the implicit GIMP (iGIMP) Charlton {\it et al.}
+(2017)\nocite{Charlton2017} or the generalised-$\alpha$ scheme for the
+MPM proposed by Tran \& Solowski (2019)\nocite{Tran2019e}.
+
+On the other hand, the time integration scheme here proposed is an accommodation of
 the Newmark a-form ($\gamma = 0.5$ and $\beta = 0$)\footnote{Notice
@@
 presented in \cite{Navas2018a}.
+
+The aim of this paper is to mitigate this spurious oscillations by the
+employ of a suitable combination of the maximum-entropy (or local
+\textit{max-ent}) $\gamma$ family shape functions, and the proposal of a explicit 
+predictor-corrector scheme.
 
@@
 material integral, where we recover the Riemann integral definition as
-an addition  of a finite set of points. Therefore individual terms in
+an addition of a finite set of points, and their volumes are
+interpreted as quadrature weights. Therefore individual terms in
 \eqref{eq:BalanceMomentum_wf} are solved as follows. 
@@
   \label{eq:Approx-velocity-mesh}
-  \vec{v}_{p} = N_I(\vec{x}_p) \vect{v}_I
-  \quad \text{and} \quad \vec{v}^{\psi}_{p} = N_I(\vec{x}_p) \vect{v}_I^{\psi},
+  \vec{v}_{p} = N_{Ip} \vect{v}_I
+  \quad \text{and} \quad \vec{v}^{\psi}_{p} = N_{Ip} \vect{v}_I^{\psi},
 \end{equation}
@@
   \label{eq:Approx-gradvelocity-mesh}
-  \Grad{\vect{v}}_p = \vect{v}_I N_I(\vec{x}_p)
-  \quad \text{and} \quad \vec{v}^{\psi}_{p} = \sum^{Nn}_I N_I(\vec{x}_p) \vect{v}_I^{\psi},
+  \tens{\dot{\varepsilon}}_p = (\vect{v}_I \otimes \Grad{N_{Ip}})^s
+  \quad \text{and} \quad  \tens{\dot{\varepsilon}}_p^{\psi}=
+  (\vect{v}_I^{\psi} \otimes \Grad{N_{Ip}})^s ,
 \end{equation}
@@
   \label{eq:particle_nod_mass}
-  \tens{m}_{IJ} =
-  \sum^{Np}_{p} N_{Ip} m_p N_{Jp}.
+  \tens{m}_{IJ} = N_{Ip} m_p N_{Jp}.
 \end{equation}
@@
   \label{eq:nodal_internal_forces}
-  \vec{f}_{I}^{int} = - \sum^{N_p}_{p} \tens{\sigma}_{p} \cdot \Grad{N_{Ip}} \frac{m_p}{\rho_p}
+  \vec{f}_{I}^{int} = - \tens{\sigma}_{p} \cdot \Grad{N_{Ip}} \frac{m_p}{\rho_p}
 \end{equation}
@@
   \label{eq:nodal_external_forces}
-  \vec{f}_{I}^{ext} = \sum^{N_p}_{p} N_{Ip} \vec{b}_{p} m_p  + \sum^{N_p}_{p}
-  N_{Ip} \vec{t}^s_{p} m_p h^{-1} 
+  \vec{f}_{I}^{ext} = N_{Ip}\ \vec{b}_{p}\ m_p  + N_{Ip}\ \vec{t}^s_{p}\ m_p h^{-1} 
 \end{equation}
@@
     \tens{\varepsilon}_{p}}{\Delta t} =
-  \frac{1}{2} \sum^{Nn}_I \left[\Grad{N_{Ip}}\ \otimes \vec{v}_{I} + \vec{v}_{I} \otimes
+  \frac{1}{2} \left[\Grad{N_{Ip}}\ \otimes \vec{v}_{I} + \vec{v}_{I} \otimes
     \Grad{N_{Ip}}\ \right].
@@
   \label{eq:Updated_Lagrangian}
-  \dot{\vec{v}}_p = \sum^{N_n}_{I}N_{Ip}\ \vec{a}_{I},\quad and\quad
-  \dot{\vec{x}}_{p} = \sum^{N_n}_{I}N_{Ip}\ \vec{v}_{I}  
+  \dot{\vec{v}}_p = N_{Ip}\ \vec{a}_{I},\quad and\quad
+  \dot{\vec{x}}_{p} = N_{Ip}\ \vec{v}_{I}  
 \end{equation}
@@
   \centering
-  \resizebox{0.55\hsize}{!}{
+  \resizebox{0.8\hsize}{!}{
     \includegraphics[width=\textwidth]{./Figures/MPM_scheme}
@@
   \label{eq:Sulsky-1994-UL-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
-  \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{a}_{I}^{k}
+  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\ N_{Ip}^{k}\ \vec{a}_{I}^{k}
 \end{equation}
@@
   \label{eq:Sulsky-1994-UL-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{v}_{I}^{k}.
+  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ N_{Ip}^{k}\ \vec{v}_{I}^{k}.
 \end{equation}
@@
   \label{eq:Zhang-2016-UL-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \sum^{N_n}_{I} \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}.  
+  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}.  
 \end{equation}
@@
   \label{eq:Zhang-2016-UL-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
-  \sum^{N_n}_{I}\frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I},
+  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\ \frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I},
 \end{equation}
@@
   \label{eq:Tran-2019-GA-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
-  \sum^{N_n}_{I} N_{Ip}^{k}\ \left[(1 - \gamma)\ \vect{a}_I^{k} +
+  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\  N_{Ip}^{k}\ \left[(1 - \gamma)\ \vect{a}_I^{k} +
     \gamma\ \vect{a}_I^{k+1} \right],\\
@@
 \label{eq:Tran-2019-GA-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + 
-  \sum^{N_n}_{I}N_{Ip}^{k} \left[ \Delta t\ \vec{v}_{I}^{k}+ \Delta t^2\left( (\frac{1}{2} - \beta)\
+  \vect{x}_p^{k+1} = \vect{x}_p^{k} + N_{Ip}^{k} \left[ \Delta t\ \vec{v}_{I}^{k}+ \Delta t^2\left( (\frac{1}{2} - \beta)\
     \vec{a}_{I}^{k} + \beta\ \vec{a}_{I}^{k+1} \right) \right]
@@
   \label{eq:Tran-2019-GA-a}
-  \vect{a}_p^{k+1} = \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{a}_{I}^{k+1}.
+  \vect{a}_p^{k+1} = N_{Ip}^{k}\ \vec{a}_{I}^{k+1}.
 \end{equation}
@@
 as in \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v} when
-nodal masses become infinitesimal.
+nodal masses become infinitesimal, and requires extra storage for
+nodal values of acceleration and previous steps.
 
@@
 
-In this section, an explicit predictor-corrector time integration
+In this section, a explicit predictor-corrector time integration
 scheme is presented. It is based in the Newmark a-form 
 $\gamma = 0.5$ and $\beta = 0$ which is the central difference
-explicit. This method is devoted to solve a system of equations of type
+explicit. This method is devoted to solve a system of equations of the type
 \begin{equation*}
@@
 successfully in the MPM framework as was proved by
-\cite{Tran2019e}. Taking the predictor definition from the classic
-literature \cite{Hughes2000} and calculating nodal velocity, and
-updating particles position employing nodal values of velocity and
-acceleration. Therefore we get the following expression for the
-\textbf{predictor} stage for both velocity and displacement.
-\begin{equation}
-  \label{eq:5}
-  \vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
-  \underbrace{\sum^{N_n}_{I}N_{Ip}^k\ \vec{v}_{I}^{k}}_{\vec{v}_p^{k}} + \frac{1}{2}\Delta
-  t^2\ \underbrace{\sum^{N_n}_{I}\frac{N_{Ip}^k\ \vec{f}_{I}^{k}}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
-\end{equation}
-\begin{equation}
-  \label{eq:Predictor-velocity}
-  \vec{v}_I^{k+1} = \vec{v}_I^n + (1 - \gamma)\ \Delta t\ \vec{a}_I^k
-  \quad , \quad \vec{a}_I^k = \frac{\vec{f}_{I}^{k}}{\tens{m}_I^k}
-\end{equation}
-
-Consequently, the \textbf{corrector} stage for the nodal velocity is in the
-following way
-\begin{equation}
-  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{k+1} + \gamma\ \Delta t\
-  \vec{a}_I^{k+1} \quad , \quad  \vec{a}_I^{k+1} = \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}} 
-\end{equation}
-
-Notice that the predictor of the particle displacement is
-computed using information only from the predictor of the
-previous step. However, velocities are computed using half information
-of the past corrector and half of the past predictor. Therefore here we share
-similarities with the \textbf{leapfrog integration} which updates the
-position at full time step, but updates the velocity at half time
-steps. Notice also that with this approach the calculation of nodal
-momentum vales in not required, and particles velocities is just a
-post-process. So during the lagrangian step only the particles
-position is truly computed. This minimizes the information
-transference between the particles and nodes, and in consequence
-minimizes the associated error to this process.
-
-Due to its simplicity allows be implemented with minor modifications
+\cite{Tran2019e}.
+
+Taking the predictor definition from and calculating nodal velocity, and updating
+particles position employing nodal values of velocity and acceleration.
+
+The predictor-corrector algorithm has been described in the classic literature
+\cite{Hughes2000}, and its computational advantages and stability were widely
+proof by Liu \cite{Xiaojian94}. The ``classic'' PCE algorithm starts
+with a predicted value of the nodal velocity at the $(k+1)$th time step denoted by $\vec{\tilde{v}}_I^{k+1}$ given as,
+\begin{equation}
+  \label{eq:Predictor-velocity-I}
+  \vec{\tilde{v}}_I^{k+1} = \vec{v}_I^k + (1 - \gamma)\ \Delta t\ \vec{a}_I^k
+\end{equation}
+
+In \eqref{eq:Predictor-velocity-I} arise a \textit{user-defined}
+parameter $\gamma \geq 0$. This parameter influences both the predictor accuracy
+and the stability of the algorithm. As point out Liu
+\cite{Xiaojian94}, the truncation error of the predictor formula is
+$O(\Delta t^3)$ when $\gamma = 0.5$, and is unconditionally stable if
+$ 0 < \gamma \leq 0.25$.
+
+To accommodate this step to the MPM framework, it is necessary to get the
+nodal values of the velocity and acceleration throughout a variational
+recovery process where particles quantities are transferred to the
+mesh nodes. This technique arise as a generalization of the super-convergent recovery
+procedures described by Zienkiewicz \& Zhu \cite{ZZ1992_I} (\textit{ZZ})
+in the context of FEM. In the MPM Gauss quadrature is not employed as
+integrals are computed following the Riemann integral definition,
+where each component of the summation correspond to a particle of the
+discretization. Also Bardenhagen \& Kober \cite{Bardenhagen2004}
+proved that thorough this information-transference technique mass and momentum are conserved. So for a general particle variable $\Phi_p$ employing the
+\textit{ZZ} technique is possible to get its nodal homologous $\Phi_I$  as,
+\begin{equation}
+  \label{eq:Variational-recovery}
+   \Phi_I = \frac{m_p N_{Ip} \Phi_p}{m_I}
+ \end{equation}
+
+ Therefore, to get a analogous expression for
+ \eqref{eq:Predictor-velocity-I} in the context of the MPM, the
+ procedure described in the equation \eqref{eq:Variational-recovery}
+ is employed reaching to,
+ \begin{equation}
+   \label{eq:Predictor-velocity-II}
+   \vec{\tilde{v}}_I^{k+1} = \underbrace{\frac{N_{Ip}^{k} m_p
+       \vec{v}_p^k}{m_I}}_{\vec{v}_I^{k}} + (1 - \gamma)\ \Delta t\  \underbrace{\frac{N_{Ip}^{k} m_p \vec{a}_p^k}{m_I}}_{\vec{a}_I^{k}}
+ \end{equation}
+
+Nonetheless this way of computing the predictor stage can introduce
+instabilities due to numerical cancellation likewise the original
+Sulky algorithm. Thankfully this can be avoided easily by the
+equivalent formulation \eqref{eq:Predictor-velocity-II}, 
+\begin{equation}
+  \label{eq:Predictor-velocity-II}
+  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
+\end{equation}
+
+This way of computing the nodal predictor is both numerically stable
+and minimize the computational effort. Once nodal velocity are
+obtained, the essential boundary conditions are imposed. And in the
+following, the ``classic'' MPM algorithm continues to reach to the
+equilibrium equation \eqref{eq:particle_balance_forces3}. Here we
+continue with the \textbf{predictor} stage, due to the fact that we
+already have nodal velocity, this step is computed in the same way as
+in FEM,
+\begin{equation}
+  \label{eq:Corrector-velocity}
+  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}
+\end{equation}
+
+Finally updated particle kinetics are computed using nodal values as,
+\begin{align}
+  \label{eq:Update-lagrangian-pce}
+        &\vec{a}_p^{k+1} = \vec{a}_p^n +
+        \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
+        \frac{N_{Ip}^k\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
+         N_{Ip}^k\ \vec{v}_{I}^{k} +
+        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k} 
+\end{align}
+Notice that particle displacement is computed using the corrected
+nodal velocities and the accelerations computed with the velocities
+of the predictor. However, particles velocities and accelerations
+are computed using the corrected velocities. Therefore here we share similarities
+with the \textbf{leapfrog integration} which updates the position at
+full time step, but updates the velocity at half time steps. Notice
+also that with this approach the calculation of nodal momentum values
+are not required. Due to its simplicity allows be implemented with minor modifications
 over a standard forward Euler. It is summarized in shape of
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
-    \STATE \textbf{Explicit Newmark Predictor} ($\gamma = 0.5$):\\
-    Only in those active nodes:
+    \STATE \textbf{Update mass matrix}:
     \begin{equation*}
-      \vec{v}_I^{k+1} = \vec{v}_I^n + (1 - \gamma)\ \Delta t\ \vec{a}_I^k
-      \quad , \quad \vec{a}_I^k = \frac{\vec{f}_{I}^{k}}{\tens{m}_I^k}
+      \tens{m}_{I} = N_{Ip}^{k}\ m_p,
+    \end{equation*}
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \STATE \textbf{Explicit Newmark Predictor}:\\
+    \begin{equation*}
+      \vec{v}_I^{pred} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
     \end{equation*}
@@
     \STATE \textbf{Impose essential boundary conditions}:\\
-    At the fixed boundary, set $\vec{v}_{I}^{k+1} = 0$. 
+    At the fixed boundary, set $\vec{v}_{I}^{pred} = 0$. 
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Update mass matrix}:
-    \begin{equation*}
-      \tens{m}_{I} = \sum_{p}^{N_p}N_{Ip}^{k+1}\ m_p,
-    \end{equation*}
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
     \STATE \textbf{Deformation tensor increment calculation}.
     \begin{align*}
-      &\dot{\tens{\varepsilon}_{p}}^{k+1} = \frac{1}{2}\ \sum_{I}^{N_n}
-        \Grad{N_{Ip}^{k+1}}\vec{v}_{I}^{k+1} +
-        (\Grad{N_{Ip}^{k+1}}\vec{v}_{I}^{k+1})^T \\
+      &\dot{\tens{\varepsilon}_{p}}^{k+1} = \left[ \vec{v}_{I}^{pred} \otimes
+        \Grad{N_{Ip}^{k+1}} \right]^s \\
       &\Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\ \dot{\tens{\varepsilon}_{p}}^{k+1}
@@
     \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
-    \eqref{eq:nodal_internal_forces} and \eqref{eq:nodal_external_forces} in the time step $k+1$. In the
-    grid node $I$ is fixed in one of the spatial dimensions, set it to
+    \eqref{eq:nodal_internal_forces} and
+    \eqref{eq:nodal_external_forces} in the time step $k+1$.
+    In the grid node $I$ is fixed in one of the spatial dimensions, set it to
     zero to make the grid nodal acceleration zero in that direction.\\
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Explicit Newmark Corrector} ($\gamma = 0.5$):
+    \STATE \textbf{Explicit Newmark Corrector}:
     \begin{equation*}
-      \vec{v}_{I}^{k+1} = \vec{v}_{I}^{k+1} + \gamma\ \Delta t\
-      \vec{a}_I^{k+1} \quad , \quad  \vec{a}_I^{k+1} = \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}  
+      \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}  
     \end{equation*}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \STATE \textbf{Update particles position and velocity}:
+    \STATE \textbf{Update particles lagrangian quantities}:
     \begin{align*}
+      &\vec{a}_p^{k+1} = \vec{a}_p^n +
+        \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
+        \frac{N_{Ip}^k\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
       &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
-        \sum^{N_n}_{I} N_{Ip}^k\ \vec{v}_{I}^{k} +
-        \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
-      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
-        \sum^{N_n}_{I}\frac{N_{Ip}^k\
+         N_{Ip}^k\ \vec{v}_{I}^{k} +
+        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
         \vec{f}_{I}^{k}}{\tens{m}_I^k}
     \end{align*}
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \STATE \textbf{Reset nodal values}
   \end{algorithmic}
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[Piecewise linear (Q4).]{
-    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun_dy}
-    \label{fig:MPM_Shape_Fun}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[Local \textit{max-ent} $\gamma=17$.]{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun_dy}
-    \label{fig:LME_17.3_Shape_Fun}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[Uniform generalized interpolated material point.]{
-    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun_dy}
-    \label{fig:GIMP_Shape_Fun}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \subfloat[Local \textit{max-ent} $\gamma=10$.]{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun_dy}
-    \label{fig:LME_10.0_Shape_Fun}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
-  \subfloat[Local \textit{max-ent} $\gamma=7$.]{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun_dy}
-    \label{fig:LME_7.0_Shape_Fun}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
-  \subfloat[Local \textit{max-ent} $\gamma=5$.]{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun_dx}
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun_dy}
-    \label{fig:LME_5.0_Shape_Fun}
+  \subfigure[Q4]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun} \\
+      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dx} \\
+      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dy}
+    \end{tabular}  
+  }
+  \subfigure[$\text{LME}_{17}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun} \\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dx} \\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \subfigure[uGIMP]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun} \\
+      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dx} \\
+      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \subfigure[$\text{LME}_{10}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun} \\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dx} \\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dy}    
+    \end{tabular}
+  }
+  \subfigure[$\text{LME}_{5}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun} \\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dx} \\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dy}
+    \end{tabular}
   }
@@
   \label{fig:LME_MPM}
-\end{figure}
+\end{figure*}
 
@@
 %\bibliographystyle{spphys}       % APS-like style for physics
-\bibliography{Biblio.bib}   % name your BibTeX data base
+\bibliography{Biblio}   % name your BibTeX data base
 

### 2020-03-25 Figures/Scene_Na.py

@@ -1,0 +1,264 @@
+# Recorded script from Mayavi2
+from numpy import array
+try:
+    engine = mayavi.engine
+except NameError:
+    from mayavi.api import Engine
+    engine = Engine()
+    engine.start()
+if len(engine.scenes) == 0:
+    engine.new_scene()
+# ------------------------------------------- 
+from mayavi.modules.outline import Outline
+outline = Outline()
+module_manager = engine.scenes[0].children[0].children[0].children[0]
+engine.add_filter(outline, module_manager)
+# outline.outline_filter.input_connection = <tvtk.tvtk_classes.algorithm_output.AlgorithmOutput object at 0x7f82116ed770>
+outline.manual_bounds = True
+outline.bounds = array([-1.9,  1. , -1. ,  1. , -1. ,  1. ])
+outline.bounds = array([-1.9,  1. , -1. ,  1. , -1. ,  1. ])
+outline.bounds = array([-1.9,  1.9, -1. ,  1. , -1. ,  1. ])
+outline.bounds = array([-1.9,  1.9, -1. ,  1. , -1. ,  1. ])
+outline.bounds = array([-1.9,  1.9, -1.9,  1. , -1. ,  1. ])
+outline.bounds = array([-1.9,  1.9, -1.9,  1. , -1. ,  1. ])
+outline.bounds = array([-1.9,  1.9, -1.9,  1.9, -1. ,  1. ])
+outline.bounds = array([-1.9,  1.9, -1.9,  1.9, -1. ,  1. ])
+outline.bounds = array([-1.9,  1.9, -1.9,  1.9,  0. ,  1. ])
+outline.bounds = array([-1.9,  1.9, -1.9,  1.9,  0. ,  1. ])
+outline.bounds = array([-1.9,  1.9, -1.9,  1.9,  0. ,  4. ])
+outline.bounds = array([-1.9,  1.9, -1.9,  1.9,  0. ,  4. ])
+scene = engine.scenes[0]
+scene.scene.camera.position = [7.734688192344844, 7.734688192344844, 8.19470485206996]
+scene.scene.camera.focal_point = [0.0, 0.0, 0.4600166597251145]
+scene.scene.camera.view_angle = 30.0
+scene.scene.camera.view_up = [0.0, 0.0, 1.0]
+scene.scene.camera.clipping_range = [5.48912328832708, 21.372954126716014]
+scene.scene.camera.compute_view_plane_normal()
+scene.scene.render()
[…]

### 2020-03-25 Figures/Scene_dxNa.py

@@ -1,0 +1,250 @@
+# Recorded script from Mayavi2
+from numpy import array
+try:
+    engine = mayavi.engine
+except NameError:
+    from mayavi.api import Engine
+    engine = Engine()
+    engine.start()
+if len(engine.scenes) == 0:
+    engine.new_scene()
+# ------------------------------------------- 
+scene = engine.scenes[0]
+scene.scene.camera.position = [12.405354476130022, 12.405354476130022, 12.405354476130022]
+scene.scene.camera.focal_point = [0.0, 0.0, 0.0]
+scene.scene.camera.view_angle = 30.0
+scene.scene.camera.view_up = [0.0, 0.0, 1.0]
+scene.scene.camera.clipping_range = [15.574096976424016, 28.98128583252587]
+scene.scene.camera.compute_view_plane_normal()
+scene.scene.render()
+scene.scene.camera.position = [10.252359071181836, 10.252359071181836, 10.252359071181836]
+scene.scene.camera.focal_point = [0.0, 0.0, 0.0]
+scene.scene.camera.view_angle = 30.0
+scene.scene.camera.view_up = [0.0, 0.0, 1.0]
+scene.scene.camera.clipping_range = [11.88229052088975, 25.19625194124579]
+scene.scene.camera.compute_view_plane_normal()
+scene.scene.render()
+scene.scene.camera.position = [9.945049557847135, 11.27617527668267, 9.448622121496244]
+scene.scene.camera.focal_point = [0.0, 0.0, 0.0]
+scene.scene.camera.view_angle = 30.0
+scene.scene.camera.view_up = [-0.3759940360636462, -0.37748496147533483, 0.8462467658458346]
+scene.scene.camera.clipping_range = [11.808094532000167, 25.289649404646994]
+scene.scene.camera.compute_view_plane_normal()
+scene.scene.render()
+scene.scene.camera.position = [8.219049221361265, 9.319153121225344, 7.808778612806812]
+scene.scene.camera.focal_point = [0.0, 0.0, 0.0]
+scene.scene.camera.view_angle = 30.0
+scene.scene.camera.view_up = [-0.3759940360636462, -0.37748496147533483, 0.8462467658458346]
+scene.scene.camera.clipping_range = [8.757014816682595, 22.161522221770895]
+scene.scene.camera.compute_view_plane_normal()
+scene.scene.render()
+scene.scene.camera.position = [6.792602662282036, 7.701779439029209, 6.453536043641991]
[…]

### 2020-03-25 Figures/Scene_dxNa_LME.py

@@ -1,0 +1,92 @@
+# Recorded script from Mayavi2
+from numpy import array
+try:
+    engine = mayavi.engine
+except NameError:
+    from mayavi.api import Engine
+    engine = Engine()
+    engine.start()
+if len(engine.scenes) == 0:
+    engine.new_scene()
+# ------------------------------------------- 
+module_manager = engine.scenes[0].children[0].children[0].children[0]
+module_manager.scalar_lut_manager.lut_mode = 'jet'
+module_manager.vector_lut_manager.lut_mode = 'jet'
+scene = engine.scenes[0]
+scene.scene.background = (1.0, 1.0, 1.0)
+module_manager.scalar_lut_manager.title_text_property.shadow_offset = array([ 1, -1])
+module_manager.scalar_lut_manager.title_text_property.shadow_offset = array([ 1, -1])
+module_manager.scalar_lut_manager.title_text_property.color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
+module_manager.scalar_lut_manager.label_text_property.shadow_offset = array([ 1, -1])
+module_manager.scalar_lut_manager.label_text_property.shadow_offset = array([ 1, -1])
+module_manager.scalar_lut_manager.label_text_property.color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
+module_manager.vector_lut_manager.title_text_property.shadow_offset = array([ 1, -1])
+module_manager.vector_lut_manager.title_text_property.shadow_offset = array([ 1, -1])
+module_manager.vector_lut_manager.title_text_property.color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
+module_manager.vector_lut_manager.label_text_property.shadow_offset = array([ 1, -1])
+module_manager.vector_lut_manager.label_text_property.shadow_offset = array([ 1, -1])
+module_manager.vector_lut_manager.label_text_property.color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
+surface = engine.scenes[0].children[0].children[0].children[0].children[0]
+surface.actor.property.ambient_color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
+surface.actor.property.color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
[…]

### 2020-03-25 Figures/Shape_Fun_GIMP.py

@@ -1,10 +1,7 @@
 #!/opt/anaconda3/bin/python3
 
+from mayavi import mlab
 import numpy as np
-import matplotlib.pyplot as plt
-from mpl_toolkits.mplot3d import Axes3D
-from matplotlib import cm
-from matplotlib.ticker import LinearLocator, FixedLocator, FormatStrFormatter
 
 def GIMP(L, lp, Xp, Xi):
     """"""
@@ -39,98 +36,51 @@ def d_GIMP(L, lp, Xp, Xi):
     return d_Sip
 
 
-def print_dx_GIMP():
+def print_dx_GIMP(Show_grafs):
     N = 50
     xp = yp = np.linspace(-2, 2, N)
     Xp, Yp = np.meshgrid(xp, yp, indexing='ij', sparse=False)
-    Sip_xDy = np.zeros([N,N])
+    Sip_dxdy = np.zeros([N,N])
     xi = yi = 0
     L = 1.
     lp = 1/4.
-    # Show
-    Show_grafs = False
+
     format_fig = 'png'
 
     for i in range(0,N):
         for j in range(0,N):
-            Sip_xDy[i][j] = d_GIMP(L,lp,xp[i],xi) * GIMP(L,lp,yp[j],yi) 
+            Sip_dxdy[i][j] = d_GIMP(L,lp,xp[i],xi) * GIMP(L,lp,yp[j],yi) 
             
-    fig = plt.figure()
-    ax = fig.gca(projection='3d')
-    ax.grid(False)
-    ax.xaxis.pane.set_edgecolor('black')
-    ax.yaxis.pane.set_edgecolor('black')
-    ax.zaxis.pane.set_edgecolor('black')
-    ax.xaxis.pane.fill = False
-    ax.yaxis.pane.fill = False
-    ax.zaxis.pane.fill = False
-    ax.axes.xaxis.set_ticklabels([])
-    ax.axes.yaxis.set_ticklabels([])
-    ax.axes.zaxis.set_ticklabels([])
-    for line in ax.xaxis.get_ticklines():
-        line.set_visible(False)
-    for line in ax.yaxis.get_ticklines():
-        line.set_visible(False)
-    for line in ax.zaxis.get_ticklines():
-        line.set_visible(False)
-        
-    surf = ax.plot_surface(Xp, Yp, Sip_xDy, rstride=1,
-                           cstride=1, cmap=cm.jet,
[…]

### 2020-03-25 Figures/Shape_Fun_LME.py

@@ -1,10 +1,7 @@
 #!/home/migmolper2/anaconda3/bin/python3
 
+from mayavi import mlab
 import numpy as np
-import matplotlib.pyplot as plt
-from mpl_toolkits.mplot3d import Axes3D
-from matplotlib import cm
-from matplotlib.ticker import LinearLocator, FixedLocator, FormatStrFormatter
 
 """
   Shape functions based in :
@@ -219,44 +216,43 @@ def LME_lambda_NR(l, lambda_GP, Beta):
     # return the lagrange multipliers value
     return lambda_GP
 
-N_gp = 35
-N_n = 5
-L = 2.
-DX = (2*L-0.2)/N_n
-Gamma = 17.3 # 17.3
-Gamma = ([17.3,10.0,7.0,5.0])
-Node = 12 # 12
-format_fig='png'
-# Show
-Show_grafs = False
 
-xp = yp = np.linspace(-L+0.1, L-0.1, N_gp)
-zp = np.zeros([1,N_gp])
-Xp, Yp = np.meshgrid(xp, yp, indexing='ij', sparse=False)
-Zp = np.zeros([N_gp,N_gp])
-N_I = np.zeros_like(Zp)
-dNdx_I = np.zeros_like(Zp)
-dNdy_I = np.zeros_like(Zp)
+def print_LME(Gamma):
+    N_gp = 35
+    N_n = 5
+    L = 2.
+    # Gamma = ([17.3,10.0,7.0,5.0])
+    Node = 12 # 12
+    format_fig='png'
+    # Show
+    Show_grafs = False
 
-xI = yI = np.linspace(-L, L, N_n)
-zI = np.zeros([1,N_n])
-XI, YI = np.meshgrid(xI, yI, indexing='ij', sparse=False)
-ZI = np.zeros([N_n,N_n])
+    xp = yp = np.linspace(-L+0.1, L-0.1, N_gp)
+    zp = np.zeros([1,N_gp])
+    Xp, Yp = np.meshgrid(xp, yp, indexing='ij', sparse=False)
+    Zp = np.zeros([N_gp,N_gp])
+    N_I = np.zeros_like(Zp)
+    dNdx_I = np.zeros_like(Zp)
+    dNdy_I = np.zeros_like(Zp)
 
-l = np.zeros([N_n*N_n,2])
+    xI = yI = np.linspace(-L, L, N_n)
+    zI = np.zeros([1,N_n])
[…]

### 2020-03-25 Figures/Shape_Fun_MPM.py

@@ -1,10 +1,7 @@
 #!/opt/anaconda3/bin/python3
 
+from mayavi import mlab
 import numpy as np
-import matplotlib.pyplot as plt
-from mpl_toolkits.mplot3d import Axes3D
-from matplotlib import cm
-from matplotlib.ticker import LinearLocator, FixedLocator, FormatStrFormatter
 
 def MPM(L, Xp, Xi):
     """"""
@@ -26,7 +23,7 @@ def d_MPM(L, Xp, Xi):
         Sip = -1/L
     return Sip
 
-def print_dx_MPM():
+def print_dx_MPM(Show_grafs):
     N = 50
     xp = yp = np.linspace(-2, 2, N)
     Xp, Yp = np.meshgrid(xp, yp, indexing='ij', sparse=False)
@@ -34,42 +31,20 @@ def print_dx_MPM():
     xi = yi = 0
     L = 1.
     format_fig = 'png'
-    Show_grafs = False
 
     for i in range(0,N):
         for j in range(0,N):
             Sip_dxdy[i][j] = d_MPM(L,xp[i],xi) * MPM(L,yp[j],yi)
            
-    fig = plt.figure()
-    ax = fig.gca(projection='3d')
-    ax.grid(False)
-    ax.xaxis.pane.set_edgecolor('black')
-    ax.yaxis.pane.set_edgecolor('black')
-    ax.zaxis.pane.set_edgecolor('black')
-    ax.xaxis.pane.fill = False
-    ax.yaxis.pane.fill = False
-    ax.zaxis.pane.fill = False
-    ax.axes.xaxis.set_ticklabels([])
-    ax.axes.yaxis.set_ticklabels([])
-    ax.axes.zaxis.set_ticklabels([])
-    for line in ax.xaxis.get_ticklines():
-        line.set_visible(False)
-    for line in ax.yaxis.get_ticklines():
-        line.set_visible(False)
-    for line in ax.zaxis.get_ticklines():
-        line.set_visible(False)
+           
+    surf = mlab.mesh(Xp, Yp, Sip_dxdy)
     
-    surf = ax.plot_surface(Xp, Yp, Sip_dxdy, rstride=1,
-                           cstride=1, cmap=cm.jet,
-                           linewidth=0, antialiased=False)
-    ax.set_zlim3d(-1.00, 1.00)
-    plt.tight_layout()
-    plt.savefig('MPM_Shape_Fun_dx.%s'%(format_fig))
[…]

### 2020-03-26 main.tex
Version dia 27-3-2020

@@
 \begin{abstract}
-  Material Point Method (MPM) has arise in the recent years as an
+  Material Point Method (MPM) has arisen in the recent years as an
   alternative to Finite Element Method (FEM) under the large
@@
   integration scheme to filter spurious noises. To overcome this
-  limitation in this paper a explicit predictor-corrector integration
-  method has been proposed. Its superior performance mitigates the
+  limitation in this paper, an explicit predictor-corrector time integration
+  scheme has been proposed. Its superior performance mitigates the
   presence of spurious oscillations with minimal dissipation in high
-  frequency problems. Other source of numerical noise in the MPM is
-  due to the lack of smoothness of the interpolation functions, and
-  occurs due to material points crossing computational grid
-  boundaries. This noise results in spurious local variations at the material
+  frequency problems. Other source of numerical noise in the MPM 
+  occurs when to material points cross computational grid
+  boundaries and motivated due to the lack of smoothness of the interpolation
+  functions. This noise results in spurious local variations at the material
   points, where strain-stress fields are computed. This could invalidate
@@
   degenerate cases resulting from the lack or uniqueness of the
-  triangulation. Furthermore, by modifying one user-defined parameter they
-  are able to behave like finite elements or as a mesh-free
+  triangulation. Furthermore, by modifying a regularization parameter they
+  are able to behave finite element like or as a mesh-free
   method. This capability allows to face a wide range of physics
-  with a single the shape function. Finally this paper demonstrates
+  with a single shape function family. Finally this paper demonstrates
   the performance of both improvements thorough numerical examples.    
@@
 Since the proposal of the MPM by Sulsky {\it  et al.}
-(1994)\cite{Sulsky1994} as a generalization to solids of the Fluid
-Implicit Particle (FLIP) method \cite{Brackbill1986}. It popularity
+(1994)~\cite{Sulsky1994} as a generalization to solids of the Fluid
+Implicit Particle (FLIP) method~\cite{Brackbill1986}. It popularity
 has increased due to its ability to deal with large strain regime
@@
 limitation such as the generalized interpolation material point method
-(GIMP) Bardenhagen \& Kober (2004)\cite{Bardenhagen2004}, which has
+(GIMP) Bardenhagen \& Kober (2004)~\cite{Bardenhagen2004}, which has
 demonstrate to have a good performance in the finite deformation
@@
 weighting functions is only achieved at considerable effort and
-computational cost. Furthermore, as it is based in a voxel
-discretization, it is prone to suffer voxel domains overlap or gaps when the
-material point mesh becomes irregular, which can introduce severe
-inaccuracies. This is similar to the difficulty encountered by the
-finite element methods due to element distortion.
+computational cost.  Furthermore, as it is  a voxel based
+discretization technique, it is prone to suffer voxel domains overlap
+or gaps when the material point mesh becomes irregular, which can
+introduce severe inaccuracies. This is similar to the difficulty
+encountered by the finite element methods due to element distortion.
 A more robust alternative is the dual domain material point method
 (DDMP) proposed by Zhang {\it et al.}
-(2011)\cite{Zhang2011a}. Unfortunately this method shows an
+(2011)~\cite{Zhang2011a}. Unfortunately this method shows an
 unsatisfactory behaviour when particle/cell ratio
@@
 of particles needed for convergence, this
-makes the method very expensive.
-
-the B-Spline MPM
-Tran {\it et al.} (2019)\cite{Tran2019a}
-
-the Conservative Taylor Least Squares \textbf{CTLS} reconstruction Wobbes {\it et al.}
-(2018)\cite{E_Wobbes_2018}.
-
-Local \textit{max-ent} shape functions was first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006}, it belongs to the class of convex 
+makes the method very expensive. In recent years the employ of
+spline-lines has gain popularity with the introduction of the B-Spline
+MPM proposed by Roel Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
+this technique allows the employ of unstructured set of notes and
+particles. More recently, approximants derived from minimization has
+been introduced in to the MPM framework with the Conservative Taylor
+Least Squares (CTLS) reconstruction proposed by Wobbes {\it et al.}
+(2018)~\cite{E_Wobbes_2018}, unfortunately when particles are spread in
+a challenging way, the quality of the CTLS approximation decrease
+locally.
+
+This document adopts the \textit{local maximum-entropy approximation
+    schemes} (LME) as a robust substitute for the wide range of shape
+  function in the MPM. First introduced by Arroyo \& Ortiz
+(2006)~\cite{Arroyo2006}, it belongs to the class of convex 
 approximation schemes and provides a seamless transition between
-finite elements (\textbf{FE}) and mesh-free interpolations. The
+finite element method (FEM) and mesh-free interpolations. The
 approximation scheme is based on a compromise between minimizing the
@@
 satisfy the partition of unity property, and provide an exact
-approximation for affine functions \cite{Arroyo2006}. This
+approximation for affine functions~\cite{Arroyo2006}. This
 approximation scheme has been proof to have a good performance under
 the dynamic regime by other researchers like Navas {\it et al.}
-(2018)\cite{Navas2018a} and Li {\it et al.} (2012)\cite{Li2012} for
-Optimal Transportation Meshfree (\textbf{OTM}) method. And more
+(2018)~\cite{Navas2018a} and Li {\it et al.} (2012)~\cite{Li2012} for
+Optimal Transportation Meshfree (OTM) method. And more
 recently under the MPM framework by Wobbes {\it et
-  al.}(2020)\cite{Wobbes2020} but limiting the $\gamma$ parameter to
-zero.
+  al.}(2020)~\cite{Wobbes2020} but without exploring the benefits of
+the regularization parameter $\beta$.
 
@@
 ``grid crossing'' error. Nevertheless, in the presence of shock waves spurious
-numerical noises appears despite of this using techniques
-\cite{Tran2019e}.
-
-These numerical inaccuracies also known as wiggles
-are due to the time discretization technique. A simple approach to
-face those spurious noises is to add a non-physical damping source to the
-equilibrium equations. To avoid this, many researchers
-has proposed alternative time integration schemes which reduce the
-presence of high-frequency noises by filtering them. Some of these
-attempts are the implicit GIMP (iGIMP) Charlton {\it et al.}
-(2017)\nocite{Charlton2017} or the generalised-$\alpha$ scheme for the
-MPM proposed by Tran \& Solowski (2019)\nocite{Tran2019e}.
-
-On the other hand, the time integration scheme here proposed is an accommodation of
-the Newmark a-form ($\gamma = 0.5$ and $\beta = 0$)\footnote{Notice
-that these $\gamma$ and $\beta$ parameters does not have the same
-meaning for the LME shape functions.} which is the central difference
-explicit (CD). We have choose this method among other suitable
-alternatives as Wilson {\it et al.} (1972)\nocite{Wilson1972} or Chung
-\& Hulbert (1993)\nocite{Geranlized_alpha_1993} because it simplicity
-and it good performance dealing with solids dynamics problems like those
-presented in \cite{Navas2018a}.
-
-The aim of this paper is to mitigate this spurious oscillations by the
-employ of a suitable combination of the maximum-entropy (or local
-\textit{max-ent}) $\gamma$ family shape functions, and the proposal of a explicit 
-predictor-corrector scheme.
+numerical noises appears despite of this using
+techniques~\cite{Tran2019e}. These numerical inaccuracies also known
+as wiggles are due to inaccuracies in the time discretization technique.
+A simple approach to face those spurious noises is to add a
+nonphysical damping source to the equilibrium equations, this
+approach has been widely employed in this and many other numerical
+techniques. To avoid introducing this nonphysical sources, many
+researchers has proposed alternative time integration
+schemes which reduce the presence of high frequency noises by
+filtering them or increasing the accuracy of the time integration
+scheme. One of the most popular is the implicit GIMP (iGIMP)
+Charlton {\it et al.} (2017)~\cite{Charlton2017}, more recently Tran \&
+Solowski (2019)~\cite{Tran2019e} proposed a generalised-$\alpha$ scheme
+for the MPM with promising results but at the expense of increasing
+the computational effort. In this paper a less time consuming and high
+efficient explicit predictor corrector integration method has been
+proposed. It consists in an accommodation of the Newmark
+predictor-corrector or central difference explicit (CD). We have
+choose this method among other suitable alternatives as those proposed
+by Wilson {\it et al.} (1972)~\cite{Wilson1972} or Chung \& Hulbert
+(1993)~\cite{Geranlized_alpha_1993} because it simplicity and it good
+performance dealing with solids dynamics problems under a mesh-free
+framework in~\cite{Navas2018a}.
+
+The aim of this document is to mitigate the spurious oscillations due
+inaccuracies in both space and time discretization by the employ of a
+suitable combination of the maximum-entropy (or local
+\textit{max-ent}) family shape functions, and the proposal of
+a explicit predictor-corrector scheme. We illustrate the advantages of
+this approach thorough to simple but challenging test cases, like the
+propagation of shock waves in a elastic bar or the response of a block of soil
+gradually loaded with gravitational forces.
 
@@
 \ref{sec:local-max-ent} briefly reviews the local \textit{max-ent}
-basis functions here employed. In Section \ref{sec:dynamic-benchmark}
-a comparison between both methods MPM and OTM employing \textit{max-ent} shape
-function is performed as well a parametric study for the $\gamma$
-parameter. Both techniques will face to solve a classic dynamic
-benchmark proposed by Dyka \& Ingel (1995)\cite{Dyka1995}. Finally,
+basis functions here employed. In Section
+\ref{sec:Application-linear-elasticity-dynamic-problems} applications
+to prove the numerical accuracy of the proposed approach are presented. Finally,
 conclusions and future research topics are exposed in Section \ref{sec:conclusions}.
@@
 physical variables involved in this problem are collected in Table
-\ref{tab:notation-table}.
+\ref{tab:notation-table}. Three kind of subscript or superscript are used within paper. The
+subscript $\qed_p$ is used to define a particle variable. While the
+subscript $\qed_I$ is reserved in this notation for denoting nodal
+variables. And finally, the superscript $\qed^{\psi}$ involves a
+virtual magnitude. For the operators, the convention is : $\dot{\qed}$ and
+$\ddot{\qed}$ for the first and second time derivative, $\qued \otimes
+\qued$ means the dyadic operator, $(\cdot)$ and $(\colon)$ means the first
+and second contraction of a tensor, $\Div{\qed}$ denotes the
+divergence operator, and finally $\Grad{\qed}$ and $\GradS{\qed}$
+denotes the gradient and its symmetric part. Einstain subscripts
+convention is adopted therefore repeated index means addition.
 
@@
     $\vect{v}$ & Velocity field & First order tensor \\
-    $\vect{u}$ & Displacement field & Second order tensor \\
+    $\vect{u}$ & Displacement field & First order tensor \\
+    $\vect{x}$ & Global coordinates & First order tensor \\
+    $\vect{\xi}$ & Local coordinates & First order tensor \\
     $\tens{\sigma}$ & Cauchy stress tensor & Second order tensor \\
@@
 
-Three kind of subscript or superscript are used within paper. The
-subscript $\qed_p$ is used to define a particle variable. While the
-subscript $\qed_I$ is reserved in this notation for denoting nodal
-variables. And finally, the superscript $\qed^{\psi}$ involves a virtual
-magnitude. For the operators, the convention is : $\dot{\qed}$ and
-$\ddot{\qed}$ for the first and second time derivative, $\qued \otimes
-\qued$ means the dyadic operator, $(\cdot)$ and $(\colon)$ means the first
-and second contraction of a tensor, $\Div{\qed}$
-denotes the divergence operator, and finally $\Grad{\qed}$ and
-$\GradS{\qed}$ denotes the gradient and its symmetric part. Einstain
-subscripts convention is adopted so repeated index means addition.
-
 \section{Derivation of the MPM}
 \label{sec:derivation-mpm}
-The aim of this section is to provide an overview of
-the standard explicit MPM algorithm \cite{Sulsky1994}. Therefore, it
-is structured in the following shape: we will first give a
-introduction to the governing equations \ref{sec:governing-equations},
-later the variational statement of the problem will be presented
-\ref{sec:variational-formulation}, and finally a discretization
-procedure thorough Galerkin is performed \ref{sec:Galerkin-procedure}.
-
-The method has three main steps: (i) a variational recovery process,
-where particle data is projected to the grid nodes, (ii) an Eulerian
-step, where balance of momentum equation is expressed as a nodal
-equilibrium equation thorough a FEM-like procedure, and finally (iii) a Lagrangian advection of the particles.
-
-\subsection{Governing equations }
-\label{sec:governing-equations}
-In the MPM approach a continuum is considered. Let define a
-$\varOmega$ domain occupied by an elastic body, and $\partial
-\varOmega$ the boundary of the domain, where $\partial
-\varOmega = \Gamma_d \bigcup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n =
-\emptyset$. Note that $\varGamma_d$ is reserved for Dirichlet boundary
-conditions, and  $\varGamma_n$ for the Neumann. In a inifinitesimal
-strain context, the behaviour of the continuum can be described by the
-following set of equations:
-(i) the balance of momentum equation
+The aim of this section is to provide an overview of the standard
+explicit MPM algorithm~\cite{Sulsky1994}. In consequence it
+is structured as follows: the governing equations will be introduced
+in \ref{sec:The boundary-value-problem}, later the variational statement of
+the problem will be presented \ref{sec:variational-formulation}, and
+finally a discretization procedure thorough Galerkin is performed in
+\ref{sec:Galerkin-procedure}. The method has three main steps: (i) a
+variational recovery process, where particle data is projected to the
+grid nodes, (ii) an Eulerian step, where balance of momentum equation
+is expressed as a nodal equilibrium equation thorough a FEM-like
+procedure, and finally (iii) a Lagrangian advection of the
+particles. In consequence the MPM can be regarded as a
+Lagrangian-Eulerian method where particles carries on all the physical
+information and a set of background nodes is employed to
+compute the equilibrium equation.
+
+\subsection{The boundary-value problem}
+\label{sec:The boundary-value-problem}
+In MPM the continuum mechanics approach is considered. So on, let
+define a continuum domain $\varOmega$ occupied by an elastic body like the sketched in
+\ref{fig:Continuum-solid}, and $\partial \varOmega$ the boundaries of
+the domain defined by $\partial \varOmega = \Gamma_d \bigcup
+\Gamma_n$ and $\Gamma_d \cap  \Gamma_n = \emptyset$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.8\hsize}{!}{
+    \includegraphics[width=\textwidth]{Figures/Continuum-solid}}
+  \caption{Description of the boundary-value-problem in a
+    continuum. Red lines represents the closure $\partial \varOmega$
+    of the domain $\varOmega$ represented in gray.}
+  \label{fig:Continuum-solid}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this context the field $\vect{u}$ allows to describe the \textit{global state}
+of the system. Now the variable $\phi =
+(\tens{\varepsilon},\tens{\sigma})$ is defined as the set of \textit{local
+  states} at any point of the continuum which can be derived from the
+field $\vect{u}$ through the following set of governing equations and
+restrictions that must be satisfied. First (i) the \textit{compatibility
+  equation} that extracts from $\vect{u}$ the strain field is,
+\begin{equation}
+  \label{eq:Compatibility-equation}
+  \tens{\varepsilon} = \GradS{\vect{u}},
+\end{equation}
+together with essential boundary conditions of Dirichlet type
+$\varGamma_d$. An additional consideration over the strain field is
+the assumption of inifinitesimal strain, therefore second order terms
+in the spatial derivatives can be neglected. The corresponding
+conjugate variable for the strain field if the stress field
+$\tens{\sigma}$, which satisfies (ii) the \textit{conservation of
+  momentum equation}
 \begin{equation}
   \label{eq:Balance-momentum}
-\rho \vect{a} = \Div{\tens{\sigma}} + \rho \vect{b},
-\end{equation}
-(ii) the compatibility equation with ensure that the velocity
-field is compatible with the Cauchy strain field,
-\begin{equation}
-  \label{eq:Compatibility-equation}
-  \dot{\tens{\varepsilon}} = \GradS{\vect{v}},
-\end{equation}
-(iii) the constitutive equation, which relates the rate of Cauchy strain
-tensor with the rate of Cauchy stress tensor,
+\rho \frac{D\vect{v}}{Dt} = \Div{\tens{\sigma}} + \rho \vect{b}
+\end{equation}
+together with the natural boundary conditions of the Neumann type
+$\varGamma_n$. Next (iii) the constitutive equation as a linear
+application from $\Re^n$ to  $\Re^n$, which relates the
+strain tensor with the stress tensor,
 \begin{equation}
   \label{eq:Constitutive-equation}
-\dot{\tens{\sigma}} = \tens{D} \colon \dot{\tens{\varepsilon}},
-\end{equation}
-and finally (iv) the mass conservation, which can be obtained by
+\tens{\sigma} = \tens{D} \colon \tens{\varepsilon}.
+\end{equation}
+The final restriction is (iv) the mass conservation, which can be obtained by
 setting to zero the total derivative of the density field,
@@
 To write the variational statement of the problem, let us define a
-virtual velocity field such that
+virtual displacement field such that
 \begin{equation}
   \label{eq:Hilbert-space}
-  \vect{v}^{\psi} \in \mathcal{H}^1_0(\Omega) = \{ \vect{v}^{\psi} \in
-  \mathcal{H}^1 \mid \vect{v}^{\psi} = \vect{0}\ \text{on}\ \Gamma_d \}.
+  \vect{u}^{\psi} \in \mathcal{H}^1_0(\Omega) = \{ \vect{u}^{\psi} \in
+  \mathcal{H}^1 \mid \vect{u}^{\psi} = \vect{0}\ \text{on}\ \Gamma_d \}.
 \end{equation}
@@
   \label{eq:cauchy-secuence}
-  \Integral{3}{\vect{v}^{\psi}} < \infty\ \quad\text{and}\quad \Integral{3}{\tens{\varepsilon}^{\psi}} < \infty
+  \Integral{3}{\vect{u}^{\psi}} < \infty\ \quad\text{and}\quad
+  \Integral{3}{\tens{\varepsilon}^{\psi}} < \infty
 \end{equation}
 The principle of virtual work states that the equilibrium solution to
-the boundary value problem of elasticity is the function $\vect{v} \in
-\mathcal{H}^1_0$ such that, for $\vect{v}^{\psi} \in
+the boundary-value problem of elasticity is the function $\vect{u} \in
+\mathcal{H}^1_0$ such that, for $\vect{u}^{\psi} \in
 \mathcal{H}^1_0$, the following holds:
@@
   \label{eq:BalanceMomentum_wf}
-  \Integral{3}{\rho\ \left( \Deriv{\vec{v}}{t}\ - \vec{b} \right) \cdot \vec{v}^{\psi}} =
-  \Integral{2}{\vec{t}\ \cdot \vec{v}^{\psi}} - \Integral{3}{\tens{\sigma} \colon
+  \Integral{3}{\rho\ \left( \frac{d\vec{v}}{dt}\ - \vec{b} \right) \cdot \vec{u}^{\psi}} =
+  \Integral{2}{\vec{t}\ \cdot \vec{u}^{\psi}} - \Integral{3}{\tens{\sigma} \colon
    \tens{\varepsilon}^{\psi}},
 \end{equation}\\
-therefore (\ref{eq:BalanceMomentum_wf}) is the balance of momentum formulated in
-its weak form.
+therefore (\ref{eq:BalanceMomentum_wf}) together with
+\eqref{eq:Constitutive-equation} and
+\eqref{eq:Rho-material-derivative} represents the weak form
+formulation of the problem.
 
@@
 of each $\Omega_p$, figure \ref{fig:MPM-discretization}.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \input{Figures/Discretization_MPM.tex}}
-  \caption{MPM discretization.}
-  \label{fig:MPM-discretization}
-\end{figure}
-
-% \begin{figure}\sidecaption
-%   \centering
-%   \resizebox{0.9\hsize}{!}{
-%     \includegraphics[width=\textwidth]{./Figures/Discretization_MPM}
-%   }
-%   \caption{MPM discretization.}
-%   \label{fig:MPM-discretization}
-% \end{figure}
-
 Each material point is assigned with initial values of position,
@@
 $\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$, but also the
-virtual field $\vect{v}^{\psi}_{p}$. So employing the definition of the
-material integral, where we recover the Riemann integral definition as
-an addition of a finite set of points, and their volumes are
-interpreted as quadrature weights. Therefore individual terms in
-\eqref{eq:BalanceMomentum_wf} are solved as follows. 
+virtual displacement field $\vect{u}^{\psi}_{p}$. Therefore, employing
+the definition of the material integral, where we recover the Riemann
+integral definition as an addition of a finite set of points, and
+their volumes are interpreted as quadrature weights. Consequently,
+individual terms in \eqref{eq:BalanceMomentum_wf} are solved as follows. 
 \begin{itemize}
@@
     \label{eq:particle_acceleration_forces}
-    \Integral{3}{\rho\ \vec{a} \cdot \vect{v}^{\psi}} =
-    \dot{\vec{v}}_{p} \cdot \vect{v}^{\psi}_{p}\ m_p.
+    \Integral{3}{\rho\ \frac{d\vec{v}}{dt} \cdot \vect{u}^{\psi}} =
+    \frac{d\vec{v}_{p}}{dt} \cdot \vect{u}^{\psi}_{p}\ m_p.
   \end{equation}\\
@@
   \label{eq:particle_body_forces}
-  \Integral{3}{\rho\ \vec{b} \cdot \vect{v}^{\psi} } = 
-  \vec{b}_{p} \cdot \vect{v}^{\psi}_p\ m_p.
+  \Integral{3}{\rho\ \vec{b} \cdot \vect{u}^{\psi} } = 
+  \vec{b}_{p} \cdot \vect{u}^{\psi}_p\ m_p.
 \end{equation}\\
@@
     \label{eq:particle_load_forces}
-    \Integral{2}{\vec{t}\ \vect{v}^{\psi}} = \Integral{2}{\rho\
-      \vec{t}^s \cdot \vect{v}^{\psi}} = \vec{t}^s_{p} \cdot \vect{v}^{\psi}_{p}\ h^{-1}\ m_p ,
+    \Integral{2}{\vec{t}\ \vect{u}^{\psi}} = \Integral{2}{\rho\
+      \vec{t}^s \cdot \vect{u}^{\psi}} = \vec{t}^s_{p} \cdot \vect{u}^{\psi}_{p}\ h^{-1}\ m_p ,
   \end{aligned} 
@@
 , I = 1,2\ldots ,N_n$, is generated. Where $N_n$ is the number of grid
-nodes. This mesh is employed as a support to compute gradients and divergences.
-
+nodes. This mesh is employed as a support to compute gradients and
+divergences.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.8\hsize}{!}{
+    \includegraphics[width=\textwidth]{Figures/Mesh-particles-back}}
+  \caption{Description of the spatial discretization for domain presented in the
+    figure \ref{fig:Continuum-solid}. Blue mesh represent the
+    background computational support, and the grid mesh conforms the
+    discretized continuum body.}
+  \label{fig:MPM-discretization}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Introducing \eqref{eq:particle_acceleration_forces},
@@
 and \eqref{eq:particle_load_forces} in \eqref{eq:BalanceMomentum_wf},
-and approximating the real and virtual velocity  field of the particle
-$p$ as
-\begin{equation}
-  \label{eq:Approx-velocity-mesh}
-  \vec{v}_{p} = N_{Ip} \vect{v}_I
-  \quad \text{and} \quad \vec{v}^{\psi}_{p} = N_{Ip} \vect{v}_I^{\psi},
-\end{equation}
-\begin{equation}
-  \label{eq:Approx-gradvelocity-mesh}
-  \tens{\dot{\varepsilon}}_p = (\vect{v}_I \otimes \Grad{N_{Ip}})^s
-  \quad \text{and} \quad  \tens{\dot{\varepsilon}}_p^{\psi}=
-  (\vect{v}_I^{\psi} \otimes \Grad{N_{Ip}})^s ,
-\end{equation}
-we reach to the particle balance of forces of the continuum,
+and approximating the displacement field of the particle
+$p$ as $\vec{u}_{p} = N_{Ip} \vect{u}_I$, $\vec{u}^{\psi}_{p} = N_{Ip} \vect{u}_I^{\psi}$,
+and its gradient as $\tens{\varepsilon}_p = (\vect{u}_I \otimes
+\Grad{N_{Ip}})^s$, $\tens{\varepsilon}_p^{\psi}= (\vect{u}_I^{\psi} \otimes \Grad{N_{Ip}})^s$.
+We reach to the nodal balance of forces of the continuum,
 \begin{equation}
@@
 in Figure \ref{fig:MPM_algorithm}.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}\sidecaption
@@
   }
-  \caption{MPM standard algorithm.}
+  \caption{Description of the MPM standard algorithm.}
   \label{fig:MPM_algorithm}
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Other authors have proposed many others time integration alternatives
@@
 \end{equation*}
-
 As the MPM has a nodal stage, it is possible to apply this methods
 successfully in the MPM framework as was proved by
-\cite{Tran2019e}.
-
-Taking the predictor definition from and calculating nodal velocity, and updating
-particles position employing nodal values of velocity and acceleration.
-
-The predictor-corrector algorithm has been described in the classic literature
-\cite{Hughes2000}, and its computational advantages and stability were widely
-proof by Liu \cite{Xiaojian94}. The ``classic'' PCE algorithm starts
-with a predicted value of the nodal velocity at the $(k+1)$th time step denoted by $\vec{\tilde{v}}_I^{k+1}$ given as,
+\cite{Tran2019e}. Taking the predictor definition from and calculating
+nodal velocity, and updating particles position employing nodal values
+of velocity and acceleration. The predictor-corrector algorithm has
+been described in the classic literature \cite{Hughes2000}, and its
+computational advantages and stability were widely proof by Liu
+\cite{Xiaojian94}. The ``classic'' PCE algorithm starts with a
+predicted value of the nodal velocity at the $(k+1)$th time step denoted by $\vec{\tilde{v}}_I^{k+1}$ given as,
 \begin{equation}
@@
 \end{equation}
-
 In \eqref{eq:Predictor-velocity-I} arise a \textit{user-defined}
@@
 
-To accommodate this step to the MPM framework, it is necessary to get the
-nodal values of the velocity and acceleration throughout a variational
+To accommodate this step to the MPM framework, it is necessary to get
+the nodal values of the velocity and acceleration throughout a variational
 recovery process where particles quantities are transferred to the
@@
  \end{equation}
-
  Therefore, to get a analogous expression for
@@
  \end{equation}
-
 Nonetheless this way of computing the predictor stage can introduce
@@
 \end{equation}
-
 This way of computing the nodal predictor is both numerically stable
@@
 equilibrium equation \eqref{eq:particle_balance_forces3}. Here we
-continue with the \textbf{predictor} stage, due to the fact that we
+continue with the \textit{corrector} stage, due to the fact that we
 already have nodal velocity, this step is computed in the same way as
@@
 \end{equation}
-
 Finally updated particle kinetics are computed using nodal values as,
@@
 are computed using the corrected velocities. Therefore here we share similarities
-with the \textbf{leapfrog integration} which updates the position at
+with the \textit{leapfrog integration} which updates the position at
 full time step, but updates the velocity at half time steps. Notice
@@
 over a standard forward Euler. It is summarized in shape of
-pseudo-algorithm \ref{alg:PCE-algorithm}.
+pseudo-algorithm \ref{app:explicit-predictor-algorithm}.
+
+\section{Local max-ent approximants}
+\label{sec:local-max-ent}
+The popularity of the MPM has increase notoriously during
+the recent years due to its ability to deal with large strain problems
+without mesh distorsion issues inherent to mesh based methods like
+FEM, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations
+made with the original MPM, there are numerical noises when particles
+crossing the cell boundaries. Local maximum-entropy (or
+local \textit{max-ent}) shape function first introduced by Arroyo \&
+Ortiz (2006)\cite{Arroyo2006} has been recently tested under the MPM framework
+by Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
+simulations performed with the \textit{max-ent} basis functions show
+considerably more accurate stress approximations for MPM. Although, in
+\cite{Wobbes2020} authors does not deep in how the regularization
+parameter $\beta$ affects to the accuracy and stability of the solution.
+
+The basic idea of the shape functions based on such
+an estimate is to interpret the shape function $N_I(\vec{x})$ as the
+probability of $\vec{x}$ to obtain the value $\vec{x}_I$,  $I=1,
+\dots, n$. Here $n$ is the number of nodes in the domain.
+This approximation scheme represents a optimal compromise, in the sense of
+Pareto, between the \textit{unbiased statistical inference} based on
+the nodal data which leads to the principle of \textit{maximum-entropy}
+stated by Jaynes \cite{Jaynes1957}, and the definition of local shape
+functions of \textit{least width} the least biased shape functions.
+
+Taking the definition of entropy as a measure of how uncertainty a
+random variable is averaged on all its possible outcomes. And adopting
+the Shannon's entropy as the starting point:
+\begin{equation}
+  \label{eq:Shannon-entropy}
+  H(p_1(\vec{x}),\ldots,p_n(\vec{x})) = -\sum^{N_n}_{I=1}{p_I(\vec{x})\log p_I }
+\end{equation}
+where $p_I(\vec{x})$ is the probability, equivalent to the mentioned
+shape function $N_I(\vec{x})$,  satisfying both the zeroth and
+first-order consistency. The least-biased approximation scheme is
+given by
+\begin{align*}
+  \label{eq:least-biased-approximation-scheme}
+  \text{(LME)} \hspace{0.15cm} &\text{Maximize} \hspace{0.15cm} H(p) =
+  -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I }\\
+  &\text{subject to}\
+  \begin{cases}
+    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
+  \end{cases}
+\end{align*}
+The local max-ent approximation schemes (LME) as a Pareto set,
+defined by \cite{Arroyo2006} is as follows
+\begin{align*}
+  \label{eq:LME-scheme-pareto-set}
+  \text{(LME)}_{\beta} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
+  \vec{x} \hspace{0.15cm} \text{minimise} \hspace{0.15cm} f_{\beta}(\vec{x}, p) = \beta H(\vec{x},p) - H(p) \\
+  &\text{subject to}\
+  \begin{cases}
+    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
+  \end{cases}
+\end{align*}
+for $\beta \in (0,\infty)$ is Pareto optimal. The unique solution of
+the local max-ent problem (LME)$_\beta$ is: 
+\begin{equation}
+  \label{eq:LME-p}
+p(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
+    \vec{\lambda} \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
+\end{equation}
+where
+\begin{equation}
+  \label{eq:LME-Z}
+Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \; |\vec{x}-\vec{x}_I|^2 + \vec{\lambda} \cdot (\vec{x}-\vec{x}_I)  \right]}
+\end{equation}
+being $\vec{\lambda}^*(\vec{x})$ the unique minimiser  for $\log
+Z(\vec{x}, \vec{\lambda})$. In order to obtain the first derivatives of the shape function, it is also necessary to compute~$\nabla p^*_I$ 
+\begin{equation}
+  \label{eq:LME-grad-p}
+\nabla p^*_I=p^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} p^*_J \, \nabla f^*_J\right)
+\end{equation}
+where
+\begin{equation}
+  \label{eq:LME-f}
+f^*_I(\vec{x},  \vec{\lambda},\beta)=-\beta \, |\vec{x}-\vec{x}_I|^2 + \vec{\lambda}   \,  (\vec{x}-\vec{x}_I)
+\end{equation}
+Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression:
+\begin{eqnarray}
+\nabla p^*_I &=& -p^*_I \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I) \label{eq26} 
+\end{eqnarray}
+%&&\mbox{
+where \tens{J} is the Hessian matrix, defined by:
+%} \nonumber \\&& \nonumber \\
+\begin{eqnarray}
+\tens{J}(\vec{x},  \vec{\lambda},\beta) &=& \frac{\partial \vec{r}}{\partial  \vec{\lambda}} \label{eq27} \\ 
+%&& \nonumber \\
+\vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \partial_{\vec{\lambda}}{\log{ Z( \vec{x},\vec{\lambda}})} 
+%\nonumber \\ &=&
+  =\sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I) \label{eq28} 
+\end{eqnarray}
+Note that, the objective of the above procedure is to find the
+$\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. The
+traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27})
+to calculate small increments of $\partial\vec{\lambda}$ in a
+Newton-Raphson approach. Similar to alternative non-polynomial meshfree basis functions, the
+LME approximation scheme requires more than $d+1$ nodes to determine
+the values of the shape functions as well as their derivatives at any
+point in the convex hull of the nodal set, where $d$ is the dimension
+of the problem. The support size of LME shape functions may be
+controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
+\cite{Arroyo2006} (e.g. two dimensional example shown in figure. \ref{fig:LME_MPM}).
+ Since  $p_I$  is defined in the entire domain, in practice, the
+function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
+10$^{-6}$, for example,  would ensure a reasonable range of
+neighbours, see \cite{Arroyo2006} for details. This tolerance defines
+the limit values of the influence radius and is used thereafter to
+find the neighbour nodes of a given integration point. Regarding this
+aspect, an crucial consideration for the implementation of the LME
+shape functions in the MPM is exposed. To avoid the transference of
+particle information to those nodes fare apart from the particle
+domain $\Omega_p$, a especial treatment of the neighbour nodes for
+those particles close to the boundary is required. Here we employ an
+algorithm inspired in the one proposed by Kumar {\it et al.}
+(2019)\cite{Kochmann2019} to deal with interfaces between two
+materials in the OTM framework. It consists in select only those nodes
+
+employed to compute the solution are those whose
+position are inside 
+In opposite to the OTM where
+this approximation technique has been widely.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.7\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Particle-discretization}
+  }
+  \caption{This tolerance defines the limit values of the influence
+    radius and is used thereafter to find the neighbour nodes of a given integration point.} 
+  \label{fig:Particle-discretization}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Due to the FE-compatibility, the LME shape function is degenerated to
+linear finite element shape function if $d+1$ neighbouring nodes are
+chosen as the support. Furthermore, with a conveniently adopted
+\textit{regularization} parameter it is possible to get a GIMP-like
+shape function. A proof of this statements is observed in \ref{fig:LME_MPM}.  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+  \centering
+  \subfigure[Q4]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun}\\
+      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dx}\\
+      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dy}
+    \end{tabular}  
+  }
+  \subfigure[$\text{LME}_{17}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dx}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \subfigure[uGIMP]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun}\\
+      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dx}\\
+      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \subfigure[$\text{LME}_{10}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dx}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dy}    
+    \end{tabular}
+  }
+  \subfigure[$\text{LME}_{5}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dx}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \caption{Comparative of linear piecewise shape functions (Q4) and
+    uniform GIMP shape functions (uGIMP) \textit{versus} Local max-ent
+    shape functions for a two-dimensional arrangement of nodes, and
+    spatial derivatives for several values of $\gamma = \beta/h^2$.}
+  \label{fig:LME_MPM}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
+influence area of the shape function is controlled by the Euclidean
+norm, therefore the search area is geometrically a circle in 2D, or a
+sphere in 3D. Building upon the idea of anisotropic shape functions,
+\cite{Kochmann2019} introduced an enhanced version of the original
+local max-ent scheme, which uses an anisotropic support to deal with
+tensile inestability. Nonetheless this is out of the scope of the
+present document but will be incorporated in future research.
+
+\section{Application to linear elasticity dynamic problems.}
+\label{sec:Application-linear-elasticity-dynamic-problems}
+
+This section is devoted to test the ability of both predictor-corrector
+time integration scheme and the local \textit{max-ent} approximants to
+overcome spurious oscillations due to the grid crossing and high
+frequency loads under the context of the MPM.
+
+\subsection{Dyka bar}
+\label{sec:dyka-bar}
+
+High frequency , the benchmark proposed by Dyka \& Ingel
+(1995)\cite{Dyka1995} is considered to illustrate the
+capacity of the proposed time integration algorithm to avoid velocity
+fields instabilities.
+
+In the one-dimensional bar sketched in the figure \ref{fig:Dyka_Bar},
+the left end of the bar is fixed and the right and an initial velocity
+$v_0 = 5\ m/s$ is given to the last quarter of it in the x positive
+direction. The length of it is 0.1333 meters with an unit section.
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \input{Figures/Dyka_bar.tex}}
+  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
+  \label{fig:Dyka_Bar}
+\end{figure}
+
+The elastic parameters consider for this test are:
+\begin{itemize} 
+\item  Density : $7833\ kg/m3$
+\item  Poisson ratio : $0$
+\item  Elastic modulus : $200 \cdot 10^9\ Pa$
+\end{itemize}
+
+The boundary conditions are:
+\begin{equation}
+  \label{eq:3}
+  \sigma \rvert_{x=L} = 0 \quad , \quad v \rvert_{x=0} = 0
+\end{equation}
+
+The total simulation time is 0.0002 seconds, a direct consequence of
+that is we let the elastic wave generated travel thorough the bar
+(from A to C and back to A) at least four times. For the spatial
+discretization we will set a mesh size of 3.3325 millimeters. The
+initial mesh will be composed by a single particle in the center of
+the element.
+
+Regarding this, here we give one consideration to properly modellize
+this benchmark under the MPM framework. Notice that the free border of
+the bar has a horizontal displacement of 0.033 millimeters, therefore
+a computational domain with an extra gap of 0.033 millimeters is
+required in order to accommodate the unconstrained displacement of the
+particles in the left border of the bar. Here below the time step is
+controlled by the courant number, in this case, we adopt a middle
+value of it (CFL=0.5) as a compromise between stability and numerical
+accuracy.
+
+The analytical solution in terms of velocity
+\ref{fig:vel_analytics_dyka}, and stress
+\ref{fig:stress_analytics_dyka} can be found in the appendix
+\ref{app:analytical_sol} given by the Method of characteristics.
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_01}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-PCE-FE}
+\end{figure}
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_LME_gamma_comparative}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-LME-gamma}
+\end{figure}
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_uGIMP_vs_LME_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-uGIMP-LME}
+\end{figure}
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-OTM-MPM}
+\end{figure}
+
+For the convergence analysis, the root-mean-square (RMS) error in the
+velocity field is computed. RMS error is defined as follows
+
+\begin{equation}
+  \label{eq:RMS}
+  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
+\end{equation}
+
+where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
+numerical solutions evaluated in the final time step in the position
+of each particle.
+
+\begin{figure*}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Error_evol}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-error-evol}
+\end{figure*}
+
+\subsection{Andersen block}
+\label{sec:andersen-block}
+
+In order to test the ability of this interpolation technique to deal
+with grid crossing instabilities we will simulate the vertical
+compression of a square block (10 by 10 meters) of soft soil sketched
+in figure \ref{fig:block} and loaded using an incremental gravitation scheme.
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \input{Figures/Block.tex}}
+  \caption{Geometrical description of a soil block }.}
+  \label{fig:block}
+\end{figure}
+
+This test was taken from Andersen (2009)\cite{thesis_Andersen_2009}. The
+elastic parameters consider for this test are: 
+\begin{itemize} 
+\item  Initial density : $6\cdot 10^3\ kg/m^3$
+\item  Poisson ratio : $0$
+\item  Elastic modulus : $5\ MPa$
+\end{itemize}
+The gravity force is a apply as an external force according to the
+equations \eqref{eq:particle_body_forces},
+\eqref{eq:nodal_external_forces}. Using a total time period of T (20
+seconds) to apply the gravity, it is increased from 0 to 9.81$m/s$
+with a sinus function until T/2 and then maintained constant until T
+in order to arrive to a state of equilibrium, 
+\begin{equation}
+  \label{eq:gravity-load-block}
+ \mathbf{g}(t) = \left\{
+    \begin{array}{ll}
+      0.5 \mathbf{g} (\sin(\frac{2t \pi}{T} - \frac{\pi}{2})+1)  & \mbox{if } t \leq T/2 \\
+      \mathbf{g} & \mbox{if } t > T/2
+    \end{array}
+  \right.
+\end{equation}
+
+In order to get a stable solution, we will adopt a time step conducted
+by a Courant number of 0.1. On the other hand, the explicit predictor-corrector
+scheme is here employed looking forward getting better results. For the
+initial spatial discretization we will employ four particles per cell
+($\Delta x = 2\ m$). The initial setting of particles inside of the
+cell changes according to the interpolation technique adopted. For the
+bi-linear shape functions (Q4) and the LME shape functions, the initial
+position corresponds to the location of the gauss-points in a standard
+quadratic finite element. For the uniform-GIMP (uGIMP) shape function
+the initial position of each particle is located in the center of each
+voxel, due to the fact that in the initial situation, the voxel domain
+should not overlap each others, Steffen {\it et al.}
+(2008)\cite{Steffen2008}. Figure \ref{fig:vertical-displacement-block}
+shows the vertical displacement evolution of a point in the free
+surface of the block.
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
+  }
+  \caption{Comparative of the vertical displacement evolution in a
+    point located in the free surface employing different
+    interpolation schemes and numerical techniques.} 
+  \label{fig:vertical-displacement-block}
+\end{figure}
+
+As we can see the simulation using the Q4 interpolation technique
+turns out to be unstable and in the second 15 it fails. The uGIMP
+simulation is more stable than the one performed by the Q4. Despite
+this is still unstable and could trigger severe oscillations if we
+pretend to simulate non-linear materials. The LME simulation was
+performed using two kinds of shape functions, one with a low value of
+the dimensionless parameter, $\gamma = 0.8$, and other with a larger
+value of it, $\gamma = 3.0$. Notice that the results are both
+stable, but the larger values of $\gamma$ give us a very stable
+solution. This is due to the fact that with larger value of $\gamma$,
+the shape functions behaves in a similar way to the FEM, which performs
+very accurate in those cases with a reasonable mesh distorsion, and
+with a lower value it behaves in a similar way to the uGIMP. This
+behaviour was noticed previously by \cite{Arroyo2006}, were authors
+highlight how by adjusting the spatial variation of $\beta(\vect{x})$,
+it is possible to select regions of the domain of analysis which are
+treated by finite elements and regions that are treated in the style
+of meshfree methods, with seamless transitions between those regions.
+
+Figure \ref{fig:Block-LME3} shows the evolution of the vertical stress
+during the loading process. The result is physically realistic as
+stress increments linearly from the top to the bottom of the specimen,
+and the value of the vertical stress in a material point located in
+the bottom of the specimen oscillates centered in $5.2 MPa$, which is
+the analytic value given by $\sigma_{yy} = \rho g h_y$.
+
+\begin{figure}
+  \centering
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[t = 0 seconds.]{
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_a_t0}
+    \label{fig:Block-LME3-PCE-t0}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \qquad
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[t = 5 seconds.]{
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_b_t025}
+    \label{fig:Block-LME3-PCE-t025}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \qquad
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[t = 20 seconds]{
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_c_t1}
+    \label{fig:Block-LME3-PCE-t1}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \caption{Vertical normal stress and position of material points
+    during the loading process for a soft soil ($E = 5\ MPa$, $\rho_0
+    = 6\cdot 10^3\ kg/m^3$). Numerical parameters considered for the
+    simulation are : Local \textit{max-ent} shape function $\gamma =3$
+    and explicit PC scheme with CFL 0.1.}
+  \label{fig:Block-LME3}
+\end{figure}
+
+% \subsection{MPM versus OTM}
+% \label{sec:mpm-versus-otm}
+
+% MPM \cite{Sulsky1994} and OTM
+% models to avoid tensile instabilities. Here we employ our in-house
+% codes for both MPM and OTM simulations.
+
+% The results are provided for the explicit predictor-corrector version
+% of the MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM
+% algorithms. For MPM, piecewise-linear, uGIMP and \textit{max-ent}
+% basis functions are employed. The OTM algorithm is used only with
+% \textit{max-ent} shape functions.
+
+% \begin{figure*}\sidecaption
+%   \centering
+%   \resizebox{0.7\hsize}{!}{
+%     \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
+%   }
+%   \caption{Velocity evolution at the point in the bar left side.}
+%   \label{fig:Dyka-MPM-uGIMP-LME}
+% \end{figure*}
+
+\section{Conclusions}
+\label{sec:conclusions}
+We have developed a new time integration scheme for the MPM, and
+proved how local \textit{max-ent} arise as a promising tool to
+overcome the grid-crossing error.
+
+adapt the value of $\beta$ to solve the equations fem-like of
+meshfree-like depending of how behaves the region
+
+This alternative technique overcome the constriction of the GIMP to
+regular mesh.
+
+The time integration here proposed mitigates the presence of wiggles
+and overshot
+
+future research :
+localization of the local max ent
+
+predictor-corrector for high dynamic problems like impact or
+collisions
+
+\begin{acknowledgements}
+If you'd like to thank anyone, place your comments here
+and remove the percent signs.
+\end{acknowledgements}
+
+%
+\section*{Conflict of interest}
+%
+The authors declare that they have no conflict of interest.
+
+\appendix
+
+\section{Explicit predictor-corrector algorithm}
+\label{app:explicit-predictor-algorithm}
 
 \begin{algorithm}
-  \label{alg:PCE-algorithm}
   \floatname{algorithm}{Algorithm}
@@
 
-\section{Local max-ent approximants}
-\label{sec:local-max-ent}
-
-% The previous lines describe the main algorithm without defining an
-% interpolation technique, so we are free to apply a wide range of the
-% existing.
-
-The popularity of the MPM has increase notoriously during
-the recent years due to its ability to deal with large strain problems
-without mesh distorsion issues inherent to mesh based methods like
-FE, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations made with the original MPM, there are
-numerical noises when particles crossing the cell boundaries. Recently
-the local maximum-entropy (or local \textit{max-ent}) shape function
-first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} has been
-tested under the MPM framework by Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
-simulations performed with the maxent basis functions show
-considerably more accurate stress approximations for MPM. Although, in
-\cite{Wobbes2020} authors does not deep in how $\beta$ affects to the
-accuracy and stability of the solution.
-
-The basic idea of the shape functions based on such
-an estimate is to interpret the shape function $N_I(\vec{x})$ as the
-probability of $\vec{x}$ to obtain the value $\vec{x}_I$,  $I=1,
-\dots, n$. Here $n$ is the number of nodes in the domain.
-
-Taking the definition of entropy as a measure of how uncertainty a
-random variable is averaged on all its possible outcomes.
-
-Therefore following the principle of \textit{maximum-entropy}
-stated by Jaynes \cite{Jaynes1957}, the least biased shape functions
-are those that maximizes the entropy of the scheme
-
-estimate is defined as the type of statistical
-inference, which is the least biased possible on the given information.
-
-Taking Shannon's entropy as the starting point:
-\begin{equation}
-  \label{eq:Shannon-entropy}
-  H(p_1(\vec{x}),\ldots,p_n(\vec{x})) = -\sum^{N_n}_{I=1}{p_I(\vec{x})\log p_I }
-\end{equation}
-where $p_I(\vec{x})$ is the probability, equivalent to the mentioned
-shape function $N_I(\vec{x})$,  satisfying both the zeroth and
-first-order consistency.
-
-The least-biased approximation scheme is given by
-\begin{align*}
-  \text{(LME)} \hspace{0.15cm} \text{Maximize} \hspace{0.15cm} &H(p) = -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I } \nonumber \\
-  \text{subject to} \hspace{0.15cm} &p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \nonumber \\
-  &\sum_{I=1}^{N_n}{p_I} = 1 \nonumber \\
-  &\sum_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \nonumber 
-\end{align*}
-
-The local max-ent approximation schemes (LME) as a Pareto set,
-defined by \cite{Arroyo2006} is as follows 
-\begin{align*}
-  \text{(LME)}_{\beta} \hspace{0.15cm} \text{For fixed} \hspace{0.15cm}
-  \vec{x} \hspace{0.15cm} \text{minimise}  \nonumber \hspace{0.15cm} &f_{\beta}(\vec{x}, p) = \beta H(\vec{x},p) - H(p) \\
-  \text{subject to} \hspace{0.15cm} &p_I \ge 0, \hspace{0.2cm} \text{I=1, ..., n}  \\
-                                                                   &\sum_{I=1}^{N_n}{p_I} = 1 \\
-                                                                   &\sum_{I=1}^{N_n}{p_I \, \vec{x}_I} = \vec{x}
-\end{align*}
-for $\beta \in (0,\infty)$ is Pareto optimal. The unique solution of
-the local max-ent problem (LME)$_\beta$ is: 
-\begin{equation}
-  \label{eq:LME-p}
-p(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +  \vec{\lambda}  \;  (\vec{x}-\vec{x}_I)         \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
-\end{equation}
-where
-\begin{equation}
-  \label{eq:LME-Z}
-Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \, | \vec{x}-\vec{x}_I|^2 + \vec{\lambda}  \,  (\vec{x}-\vec{x}_I)  \right]}
-\end{equation}
-being $\vec{\lambda}^*(\vec{x})$ the unique minimiser  for $\log Z(\vec{x}, \vec{\lambda})$
-
-In order to obtain the first derivatives of the shape function, it is  also necessary to compute~$\nabla p^*_I$ 
-\begin{equation}
-  \label{eq:LME-grad-p}
-\nabla p^*_I=p^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} p^*_J \, \nabla f^*_J\right)
-\end{equation}
-where
-\begin{equation}
-  \label{eq:LME-f}
-f^*_I(\vec{x},  \vec{\lambda},\beta)=-\beta \, |\vec{x}-\vec{x}_I|^2 + \vec{\lambda}   \,  (\vec{x}-\vec{x}_I)
-\end{equation}
-Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression:
-\begin{eqnarray}
-\nabla p^*_I &=& -p^*_I \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I) \label{eq26} 
-\end{eqnarray}
-%&&\mbox{
-where \tens{J} is the Hessian matrix, defined by:
-%} \nonumber \\&& \nonumber \\
-\begin{eqnarray}
-\tens{J}(\vec{x},  \vec{\lambda},\beta) &=& \frac{\partial \vec{r}}{\partial  \vec{\lambda}} \label{eq27} \\ 
-%&& \nonumber \\
-\vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \partial_{\vec{\lambda}}{\log{ Z( \vec{x},\vec{\lambda}})} 
-%\nonumber \\ &=&
-  =\sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I) \label{eq28} 
-\end{eqnarray}
-Note that, the objective of the above procedure is to find the
-$\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. The
-traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27})
-to calculate small increments of $\partial\vec{\lambda}$ in a
-Newton-Raphson approach.
-
-Similar to alternative non-polynomial meshfree basis functions, the
-LME approximation scheme requires more than $d+1$ nodes to determine
-the values of the shape functions as well as their derivatives at any
-point in the convex hull of the nodal set, where $d$ is the dimension
-of the problem. Due to the FE-compatibility, the LME shape function is
-degenerated to linear finite element shape function if $d+1$
-neighbouring nodes are chosen as the support. The support size of LME
-shape functions may be controlled by adjusting a dimensionless
-parameter, $\gamma=\beta h^2$ (e.g. two dimensional example shown in
-figure. \ref{fig:LME_MPM})\cite{Arroyo2006}.
-
-\begin{figure*}
-  \centering
-  \subfigure[Q4]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun} \\
-      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dx} \\
-      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dy}
-    \end{tabular}  
-  }
-  \subfigure[$\text{LME}_{17}$]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun} \\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dx} \\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dy}
-    \end{tabular}
-  }
-  \subfigure[uGIMP]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun} \\
-      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dx} \\
-      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dy}
-    \end{tabular}
-  }
-  \subfigure[$\text{LME}_{10}$]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun} \\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dx} \\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dy}    
-    \end{tabular}
-  }
-  \subfigure[$\text{LME}_{5}$]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun} \\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dx} \\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dy}
-    \end{tabular}
-  }
-  \caption{Local max-ent shape functions for a two-dimensional
-    arrangement of nodes, and spatial derivatives for several values
-    of $\gamma = \beta/h^2$.}
-  \label{fig:LME_MPM}
-\end{figure*}
-
-Since  $p_I$  is defined in the entire domain, in practice, the
-function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
-10$^{-6}$, for example,  would ensure a reasonable range of
-neighbours, see \cite{Arroyo2006} for details. This tolerance defines
-the limit values of the influence radius and is used thereafter to
-find the neighbour nodes of a given integration point. Regarding this
-aspect an important note in the implementation of this interpolation
-technique in the MPM is
-
-In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
-influence area of the shape function is controlled by the Euclidean
-norm, therefore the search area is geometrically a circle in 2D, or a
-sphere in 3D. Building upon the idea of anisotropic shape functions,
-\cite{Kochmann2019} introduced an enhanced version of the original
-local max-ent scheme, which uses an anisotropic support to deal with
-tensile inestability. Nonetheless this is out of the scope of the
-present document but will be incorporated in future research.
-
-\section{Application to linear elasticity dynamic problems.}
-\label{sec:Application-linear-elasticity-dynamic-problems}
-
-This section is devoted to test the ability of both predictor-corrector
-time integration scheme and the local \textit{max-ent} approximants to
-overcome spurious oscillations due to the grid crossing and high
-frequency loads under the context of the MPM.
-
-\subsection{Dyka bar}
-\label{sec:dyka-bar}
-
-High frequency , the benchmark proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995} is considered to illustrate the
-capacity of the proposed time integration algorithm to avoid velocity
-fields instabilities.
-
-In the one-dimensional bar sketched in the figure \ref{fig:Dyka_Bar},
-the left end of the bar is fixed and the right and an initial velocity
-$v_0 = 5\ m/s$ is given to the last quarter of it in the x positive
-direction. The length of it is 0.1333 meters with an unit section.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \input{Figures/Dyka_bar.tex}}
-  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
-  \label{fig:Dyka_Bar}
-\end{figure}
-
-The elastic parameters consider for this test are:
-\begin{itemize} 
-\item  Density : $7833\ kg/m3$
-\item  Poisson ratio : $0$
-\item  Elastic modulus : $200 \cdot 10^9\ Pa$
-\end{itemize}
-
-The boundary conditions are:
-\begin{equation}
-  \label{eq:3}
-  \sigma \rvert_{x=L} = 0 \quad , \quad v \rvert_{x=0} = 0
-\end{equation}
-
-The total simulation time is 0.0002 seconds, a direct consequence of
-that is we let the elastic wave generated travel thorough the bar
-(from A to C and back to A) at least four times. For the spatial
-discretization we will set a mesh size of 3.3325 millimeters. The
-initial mesh will be composed by a single particle in the center of
-the element.
-
-Regarding this, here we give one consideration to properly modellize
-this benchmark under the MPM framework. Notice that the free border of
-the bar has a horizontal displacement of 0.033 millimeters, therefore
-a computational domain with an extra gap of 0.033 millimeters is
-required in order to accommodate the unconstrained displacement of the
-particles in the left border of the bar. Here below the time step is
-controlled by the courant number, in this case, we adopt a middle
-value of it (CFL=0.5) as a compromise between stability and numerical
-accuracy.
-
-The analytical solution in terms of velocity
-\ref{fig:vel_analytics_dyka}, and stress
-\ref{fig:stress_analytics_dyka} can be found in the appendix
-\ref{app:analytical_sol} given by the Method of characteristics.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_01}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-PCE-FE}
-\end{figure}
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_LME_gamma_comparative}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-LME-gamma}
-\end{figure}
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_uGIMP_vs_LME_Dyka}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-uGIMP-LME}
-\end{figure}
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-OTM-MPM}
-\end{figure}
-
-For the convergence analysis, the root-mean-square (RMS) error in the
-velocity field is computed. RMS error is defined as follows
-
-\begin{equation}
-  \label{eq:RMS}
-  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
-\end{equation}
-
-where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
-numerical solutions evaluated in the final time step in the position
-of each particle.
-
-\begin{figure*}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Error_evol}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-error-evol}
-\end{figure*}
-
-\subsection{Andersen block}
-\label{sec:andersen-block}
-
-In order to test the ability of this interpolation technique to deal
-with grid crossing instabilities we will simulate the vertical
-compression of a square block (10 by 10 meters) of soft soil sketched
-in figure \ref{fig:block} and loaded using an incremental gravitation scheme.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \input{Figures/Block.tex}}
-  \caption{Geometrical description of a soil block }.}
-  \label{fig:block}
-\end{figure}
-
-This test was taken from Andersen (2009)\cite{thesis_Andersen_2009}. The
-elastic parameters consider for this test are: 
-\begin{itemize} 
-\item  Initial density : $6\cdot 10^3\ kg/m^3$
-\item  Poisson ratio : $0$
-\item  Elastic modulus : $5\ MPa$
-\end{itemize}
-The gravity force is a apply as an external force according to the
-equations \eqref{eq:particle_body_forces},
-\eqref{eq:nodal_external_forces}. Using a total time period of T (20
-seconds) to apply the gravity, it is increased from 0 to 9.81$m/s$
-with a sinus function until T/2 and then maintained constant until T
-in order to arrive to a state of equilibrium, 
-\begin{equation}
-  \label{eq:gravity-load-block}
- \mathbf{g}(t) = \left\{
-    \begin{array}{ll}
-      0.5 \mathbf{g} (\sin(\frac{2t \pi}{T} - \frac{\pi}{2})+1)  & \mbox{if } t \leq T/2 \\
-      \mathbf{g} & \mbox{if } t > T/2
-    \end{array}
-  \right.
-\end{equation}
-
-In order to get a stable solution, we will adopt a time step conducted
-by a Courant number of 0.1. On the other hand, the explicit predictor-corrector
-scheme is here employed looking forward getting better results. For the
-initial spatial discretization we will employ four particles per cell
-($\Delta x = 2\ m$). The initial setting of particles inside of the
-cell changes according to the interpolation technique adopted. For the
-bi-linear shape functions (Q4) and the LME shape functions, the initial
-position corresponds to the location of the gauss-points in a standard
-quadratic finite element. For the uniform-GIMP (uGIMP) shape function
-the initial position of each particle is located in the center of each
-voxel, due to the fact that in the initial situation, the voxel domain
-should not overlap each others, Steffen {\it et al.}
-(2008)\cite{Steffen2008}. Figure \ref{fig:vertical-displacement-block}
-shows the vertical displacement evolution of a point in the free
-surface of the block.
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
-  }
-  \caption{Comparative of the vertical displacement evolution in a
-    point located in the free surface employing different
-    interpolation schemes and numerical techniques.} 
-  \label{fig:vertical-displacement-block}
-\end{figure}
-
-As we can see the simulation using the Q4 interpolation technique
-turns out to be unstable and in the second 15 it fails. The uGIMP
-simulation is more stable than the one performed by the Q4. Despite
-this is still unstable and could trigger severe oscillations if we
-pretend to simulate non-linear materials. The LME simulation was
-performed using two kinds of shape functions, one with a low value of
-the dimensionless parameter, $\gamma = 0.8$, and other with a larger
-value of it, $\gamma = 3.0$. Notice that the results are both
-stable, but the larger values of $\gamma$ give us a very stable
-solution. This is due to the fact that with larger value of $\gamma$,
-the shape functions behaves in a similar way to the FEM, which performs
-very accurate in those cases with a reasonable mesh distorsion, and
-with a lower value it behaves in a similar way to the uGIMP. This
-behaviour was noticed previously by \cite{Arroyo2006}, were authors
-highlight how by adjusting the spatial variation of $\beta(\vect{x})$,
-it is possible to select regions of the domain of analysis which are
-treated by finite elements and regions that are treated in the style
-of meshfree methods, with seamless transitions between those regions.
-
-Figure \ref{fig:Block-LME3} shows the evolution of the vertical stress
-during the loading process. The result is physically realistic as
-stress increments linearly from the top to the bottom of the specimen,
-and the value of the vertical stress in a material point located in
-the bottom of the specimen oscillates centered in $5.2 MPa$, which is
-the analytic value given by $\sigma_{yy} = \rho g h_y$.
-
-\begin{figure}
-  \centering
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[t = 0 seconds.]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_a_t0}
-    \label{fig:Block-LME3-PCE-t0}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[t = 5 seconds.]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_b_t025}
-    \label{fig:Block-LME3-PCE-t025}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[t = 20 seconds]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_c_t1}
-    \label{fig:Block-LME3-PCE-t1}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \caption{Vertical normal stress and position of material points
-    during the loading process for a soft soil ($E = 5\ MPa$, $\rho_0
-    = 6\cdot 10^3\ kg/m^3$). Numerical parameters considered for the
-    simulation are : Local \textit{max-ent} shape function $\gamma =3$
-    and explicit PC scheme with CFL 0.1.}
-  \label{fig:Block-LME3}
-\end{figure}
-
-% \subsection{MPM versus OTM}
-% \label{sec:mpm-versus-otm}
-
-% MPM \cite{Sulsky1994} and OTM
-% models to avoid tensile instabilities. Here we employ our in-house
-% codes for both MPM and OTM simulations.
-
-% The results are provided for the explicit predictor-corrector version
-% of the MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM
-% algorithms. For MPM, piecewise-linear, uGIMP and \textit{max-ent}
-% basis functions are employed. The OTM algorithm is used only with
-% \textit{max-ent} shape functions.
-
-% \begin{figure*}\sidecaption
-%   \centering
-%   \resizebox{0.7\hsize}{!}{
-%     \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
-%   }
-%   \caption{Velocity evolution at the point in the bar left side.}
-%   \label{fig:Dyka-MPM-uGIMP-LME}
-% \end{figure*}
-
-\section{Conclusions}
-\label{sec:conclusions}
-We have developed a new time integration scheme for the MPM, and
-proved how local \textit{max-ent} arise as a promising tool to
-overcome the grid-crossing error.
-
-adapt the value of $\beta$ to solve the equations fem-like of
-meshfree-like depending of how behaves the region
-
-This alternative technique overcome the constriction of the GIMP to
-regular mesh.
-
-The time integration here proposed mitigates the presence of wiggles
-and overshot
-
-future research :
-localization of the local max ent
-
-predictor-corrector for high dynamic problems like impact or
-collisions
-
-\begin{acknowledgements}
-If you'd like to thank anyone, place your comments here
-and remove the percent signs.
-\end{acknowledgements}
-
-%
-\section*{Conflict of interest}
-%
-The authors declare that they have no conflict of interest.
-
-\appendix
 \section{The analytical solution of the 1D Dyka benchmark}

### 2020-03-27 _region_.tex
Versión II día 27-3-2020

@@
 \usepackage[ugly]{units}
+% \usetikzlibrary{decorations}
+% \usetikzlibrary{arrows}
+\usetikzlibrary{plotmarks}
+
+\usetikzlibrary{%
+    decorations.pathreplacing,%
+    decorations.pathmorphing%
+}
 
@@
 
-\title{Suitability of the local-maximum entropy approximation under
-  the Material Point Method framework for dynamic problems. \thanks{Funding: This
+% \title{Novel improvements in the Material Point Method to face
+%   dynamic problems: 
+%   Local-maximum entropy approximation and an explicit predictor-corrector scheme. \thanks{Funding: This
+%     study was funded by Agustín de Betancourt Foundation (grant number
+%     262390106114).}
+% }
+
+\title{Enhanced Material Point Method to face
+  dynamic problems:\thanks{Funding: This
     study was funded by Agustín de Betancourt Foundation (grant number
@@
 }
-% \subtitle{}
-
-\titlerunning{Suitability of the LME approximation under
-  the MPM framework for dynamic problems.}        % if too long for running head
+\subtitle{Local-maximum entropy approximation and explicit
+  predictor-corrector scheme}
+
+\titlerunning{Novel improvements in the Material Point Method to face
+  dynamic problems.} % if too long for running head
 
@@
 \begin{abstract}
-  This document is devoted to describe the suitability of the Local
-  \textit{maximum-entropy} (LME) meshfree approximation technique under the framework of the
-  Material Point Method for dynamic problems. 
-  \keywords{LME \and MPM \and Dynamic problems}
+  Material Point Method (MPM) has arisen in the recent years as an
+  alternative to Finite Element Method (FEM) under the large
+  deformation regime. However, the simulation of shock waves
+  propagation and other high frequency problems is still challenging
+  under this approach due the incapability of the standard MPM time
+  integration scheme to filter spurious noises. To overcome this
+  limitation in this paper, an explicit predictor-corrector time integration
+  scheme has been proposed. Its superior performance mitigates the
+  presence of spurious oscillations with minimal dissipation in high
+  frequency problems. Other source of numerical noise in MPM 
+  occurs when to material points cross computational grid
+  boundaries and motivated due to the lack of smoothness of the interpolation
+  functions. This noise results in spurious local variations at the material
+  points, where strain-stress fields are computed. This could invalidate
+  the solution in one case, or damage it in another. To overcome it,
+  this document adopts the \textit{local maximum-entropy approximation
+    schemes} (LME) a robust substitute for the wide range of shape
+  function in MPM. Local \textit{max-ent} approximation may be regarded as a
+  \textit{thermalization} of Delaunay triangulation which resolves the
+  degenerate cases resulting from the lack or uniqueness of the
+  triangulation. Furthermore, by modifying a regularization parameter they
+  are able to behave finite element like or as a mesh-free
+  method. This capability allows to face a wide range of physics
+  with a single shape function family. Finally this paper demonstrates
+  the performance of both improvements thorough numerical examples.    
+  \keywords{LME \and MPM \and Explicit predictor-corrector \and Dynamic problems}
   % \PACS{PACS code1 \and PACS code2 \and more}
@@
 \label{intro}
-Since the proposal of the Material Point Method (\textbf{MPM}) by Sulsky {\it
-  et al.} (1994)\cite{Sulsky1994}, as a generalization of
-a particle-in-cell method \cite{Harlow1956} and a fluid implicit
-particle (FLIP) method \cite{Brackbill1986}, MPM has been used to
-simulate dynamic problems. However, in the simulations made with the
-originalMPM, there are numerical noises \cite{Tran2019e} when it is faced to solve
-classic dynamic benchmarks like the one proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995}.
-
-The aim of this paper is to mitigate this spurious oscillations by the
-employ of the maximum-entropy (or local \textit{max-ent}) shape
-function under the MPM framework. First introduced by
-\cite{Arroyo2006}, it belongs to the class of convex 
+Since the proposal of MPM by Sulsky {\it  et al.}
+(1994)~\cite{Sulsky1994} as a generalization to solids of the Fluid
+Implicit Particle (FLIP) method~\cite{Brackbill1986}. It popularity
+has increased due to its ability to deal with large strain regime
+without suffer mesh distortion inaccuracies.
+
+However, this method suffers other kind of instabilities, such those
+when material points crossing cell boundaries. This give rise to the
+development of other interpolation techniques to overcome this
+limitation such as the generalized interpolation material point method
+(GIMP) Bardenhagen \& Kober (2004)~\cite{Bardenhagen2004}, which has
+demonstrate to have a good performance in the finite deformation
+regime. However, in the absence of a regular grid, construction of the
+weighting functions is only achieved at considerable effort and
+computational cost.  Furthermore, as it is  a voxel based
+discretization technique, it is prone to suffer voxel domains overlap
+or gaps when the material point mesh becomes irregular, which can
+introduce severe inaccuracies. This is similar to the difficulty
+encountered by the finite element methods due to element distortion.
+A more robust alternative is the dual domain material point method
+(DDMP) proposed by Zhang {\it et al.}
+(2011)~\cite{Zhang2011a}. Unfortunately this method shows an
+unsatisfactory behaviour when particle/cell ratio
+decreases~\cite{DHAKAL2016301}, therefore DDMP requires a large number
+of particles needed for convergence, this
+makes the method very expensive. In recent years the employ of
+spline-lines has gain popularity with the introduction of the B-Spline
+MPM proposed by Roel Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
+this technique allows the employ of unstructured set of notes and
+particles. More recently, approximants derived from minimization has
+been introduced in to MPM framework with the Conservative Taylor
+Least Squares (CTLS) reconstruction proposed by Wobbes {\it et al.}
+(2018)~\cite{E_Wobbes_2018}, unfortunately when particles are spread in
+a challenging way, the quality of the CTLS approximation decrease
+locally.
+
+This document adopts the \textit{local maximum-entropy approximation
+    schemes} (LME) as a robust substitute for the wide range of shape
+  function in MPM. First introduced by Arroyo \& Ortiz
+(2006)~\cite{Arroyo2006}, it belongs to the class of convex 
 approximation schemes and provides a seamless transition between
-finite elements (\textbf{FE}) and mesh-free interpolations. The
+finite element method (FEM) and mesh-free interpolations. The
 approximation scheme is based on a compromise between minimizing the
@@
 Delaunay triangulation which effectively resolves the degenerate cases
-resulting from the lack of uniqueness of the triangulation. Local
+resulting from the lack of uniqueness or the triangulation. Local
 \textit{max-ent} basis functions possess many desirable properties for
-meshfree algorithms. First of all, they are entirely defined by the
-nodal set and the domain of analysis. They are also non-negative, satisfy the partition of unity
-property, and provide an exact approximation for affine functions \cite{Arroyo2006}.
-
-This approximation scheme has been proof to have a good performance
-under the dynamic regime by other researchers like Navas {\it et al.}
-(2018)\cite{Navas2018a} and Li {\it et al.} (2012)\cite{Li2012} for
-Optimal Transportation Meshfree (\textbf{OTM}) method.
-
-a comparison between both methods employing \textit{max-ent}  shape
-function is performed in this paper
-
-as well a parametric study for the $\gamma$ parameter
-
-finally, conclusions and future research topics are exposed
-
-\section{Notation}
+mesh-free algorithms. First of all, they are entirely defined by the
+nodal set and the domain of analysis. They are also non-negative,
+satisfy the partition of unity property, and provide an exact
+approximation for affine functions~\cite{Arroyo2006}. This
+approximation scheme has been proof to have a good performance under
+the dynamic regime by other researchers like Navas {\it et al.}
+(2018)~\cite{Navas2018a} and Li {\it et al.} (2012)~\cite{Li2012} for
+Optimal Transportation Meshfree (OTM) method. And more
+recently under MPM framework by Wobbes {\it et
+  al.}(2020)~\cite{Wobbes2020} but without exploring the benefits of
+the regularization parameter $\beta$.
+
+This techniques are devoted to mitigate the
+``grid crossing'' error. Nevertheless, in the presence of shock waves spurious
+numerical noises appears despite of this using
+techniques~\cite{Tran2019e}. These numerical inaccuracies also known
+as wiggles are due to inaccuracies in the time discretization technique.
+A simple approach to face those spurious noises is to add a
+nonphysical damping source to the equilibrium equations, this
+approach has been widely employed in this and many other numerical
+techniques. To avoid introducing this nonphysical sources, many
+researchers has proposed alternative time integration
+schemes which reduce the presence of high frequency noises by
+filtering them or increasing the accuracy of the time integration
+scheme. One of the most popular is the implicit GIMP (iGIMP)
+Charlton {\it et al.} (2017)~\cite{Charlton2017}, more recently Tran \&
+Solowski (2019)~\cite{Tran2019e} proposed a generalised-$\alpha$ scheme
+for MPM with promising results but at the expense of increasing
+the computational effort. In this paper a less time consuming and high
+efficient explicit predictor corrector integration method has been
+proposed. It consists in an accommodation of the Newmark
+predictor-corrector or central difference explicit (CD). We have
+choose this method among other suitable alternatives as those proposed
+by Wilson {\it et al.} (1972)~\cite{Wilson1972} or Chung \& Hulbert
+(1993)~\cite{Geranlized_alpha_1993} because it simplicity and it good
+performance dealing with solids dynamics problems under a mesh-free
+framework in~\cite{Navas2018a}.
+
+The aim of this document is to mitigate the spurious oscillations due
+inaccuracies in both space and time discretization by the employ of a
+suitable combination of the maximum-entropy (or local
+\textit{max-ent}) family shape functions, and the proposal of
+a explicit predictor-corrector scheme. We illustrate the advantages of
+this approach thorough to simple but challenging test cases, like the
+propagation of shock waves in a elastic bar or the response of a block of soil
+gradually loaded with gravitational forces.
+
+The article is organized as follows. Section \ref{sec:Notation}
+briefly reviews the notation here employed. Next, Section \ref{sec:derivation-mpm}
+is devoted to present briefly the governing equations of the elastic
+problem, the variational formulation and the Galerkin procedure. In Section \ref{sec:epc-algor-mpm} an explicit predictor-corrector
+time integration scheme for MPM is proposed. Section
+\ref{sec:local-max-ent} briefly reviews the local \textit{max-ent}
+basis functions here employed. In Section
+\ref{sec:Application-linear-elasticity-dynamic-problems} applications
+to prove the numerical accuracy of the proposed approach are presented. Finally,
+conclusions and future research topics are exposed in Section \ref{sec:conclusions}.
+
+\section{Brief note concerning the notation}
 \label{sec:Notation}
-In what follows, we will adopt the following convention:
-\begin{table}[h]
+In what follows, we will adopt the following convention. All the
+physical variables involved in this problem are collected in Table
+\ref{tab:notation-table}. Three kind of subscript or superscript are used within paper. The
+subscript $\qed_p$ is used to define a particle variable. While the
+subscript $\qed_I$ is reserved in this notation for denoting nodal
+variables. And finally, the superscript $\qed^{\psi}$ involves a
+virtual magnitude. For the operators, the convention is : $\dot{\qed}$ and
+$\ddot{\qed}$ for the first and second time derivative, $\qued \otimes
+\qued$ means the dyadic operator, $(\cdot)$ and $(\colon)$ means the first
+and second contraction of a tensor, $\Div{\qed}$ denotes the
+divergence operator, and finally $\Grad{\qed}$ and $\GradS{\qed}$
+denotes the gradient and its symmetric part. Einstain subscripts
+convention is adopted therefore repeated index means addition.
+
+\begin{table}
   \centering
@@
   \label{tab:notation-table}
-  \begin{tabular}{c c}
-    $\rho$ & Density field \\
-    $\vect{a}$ & Acceleration field \\
-    $\vect{v}$ & Velocity field \\
-    $\vect{u}$ & Displacement field \\
-    $\tens{\sigma}$ & Cauchy stress tensor \\
-    $\tens{\varepsilon}$ & Cauchy strain tensor\\
-    $\tens{D}$ & Constitutive tensor \\
+  \begin{tabular}{c c c}
+    $\rho$ & Density field & Scalar \\
+    $\vect{a}$ & Acceleration field & First order tensor \\
+    $\vect{v}$ & Velocity field & First order tensor \\
+    $\vect{u}$ & Displacement field & First order tensor \\
+    $\vect{x}$ & Global coordinates & First order tensor \\
+    $\vect{\xi}$ & Local coordinates & First order tensor \\
+    $\tens{\sigma}$ & Cauchy stress tensor & Second order tensor \\
+    $\tens{\varepsilon}$ & Cauchy strain tensor & Second order tensor \\
+    $\tens{D}$ & Constitutive tensor & Fourth order tensor\\
   \end{tabular}
@@
 
-The subscript $p$ is used to define a particle variable. While the subscript $I$ is reserved in this
-notation for denoting nodal variables.
-
-\section{Derivation of the MPM}
+\section{Derivation of MPM procedure}
 \label{sec:derivation-mpm}
-In this section, we provide an overview of the standard explicit MPM
-algorithm as presented by \cite{Sulsky1994}. The method has three main
-steps: a variational recovery process to project particle data to the
-nodes of the grid, a Eulerian step where balance of momentum is
-compute by solving internal and external forces in the nodes, and
-finally the advection of the Lagrangian particles. We will first give
-a introduction to the governing equations and then follow by an
-algorithmic description of the process.
-
-\subsection{Governing equations }
-\label{sec:governing-equations}
-In the MPM approach a continuum is considered. The continuum behaviour
-can be described by a set of governing equations which are
-
-the balance of momentum equation
+The aim of this section is to provide an overview of the standard
+explicit MPM algorithm~\cite{Sulsky1994}. In consequence it
+is structured as follows: the governing equations will be introduced
+in \ref{sec:The boundary-value-problem}, later the variational statement of
+the problem will be presented \ref{sec:variational-formulation}, and
+finally a discretization procedure thorough Galerkin is performed in
+\ref{sec:Galerkin-procedure}. The method has three main steps: (i) a
+variational recovery process, where particle data is projected to the
+grid nodes, (ii) an Eulerian step, where balance of momentum equation
+is expressed as a nodal equilibrium equation thorough a FEM-like
+procedure, and finally (iii) a Lagrangian advection of the
+particles. In consequence MPM can be regarded as a
+Lagrangian-Eulerian method where particles carries on all the physical
+information and a set of background nodes is employed to
+compute the equilibrium equation.
+
+\subsection{The boundary-value problem}
+\label{sec:The boundary-value-problem}
+In MPM the continuum mechanics approach is considered. So on, let
+define a continuum domain $\varOmega$ occupied by an elastic body like
+the sketched in the figure~\ref{fig:Continuum-solid}, and $\partial
+\varOmega$ the boundaries of the domain defined by $\partial \varOmega
+= \Gamma_d \bigcup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n = \emptyset$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.8\hsize}{!}{
+    \includegraphics[width=\textwidth]{Figures/Continuum-solid}}
+  \caption{Description of the boundary-value-problem in a
+    continuum. Red lines represents the closure $\partial \varOmega$
+    of the domain $\varOmega$ represented in gray.}
+  \label{fig:Continuum-solid}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this context the field $\vect{u}$ allows to describe the \textit{global state}
+of the system. Now the variable $\phi =
+(\tens{\varepsilon},\tens{\sigma})$ is defined as the set of \textit{local
+  states} at any point of the continuum which can be derived from the
+field $\vect{u}$ through the following set of governing equations and
+restrictions that must be satisfied. First (i) the \textit{compatibility
+  equation} that extracts from $\vect{u}$ the strain field is,
+\begin{equation}
+  \label{eq:Compatibility-equation}
+  \tens{\varepsilon} = \GradS{\vect{u}},
+\end{equation}
+together with essential boundary conditions of Dirichlet type
+$\varGamma_d$. An additional consideration over the strain field is
+the assumption of inifinitesimal strain, therefore second order terms
+in the spatial derivatives can be neglected. The corresponding
+conjugate variable for the strain field if the stress field
+$\tens{\sigma}$, which satisfies (ii) the \textit{conservation of
+  momentum equation}
 \begin{equation}
   \label{eq:Balance-momentum}
-\rho \vect{a} = \Div{\tens{\sigma}} + \rho \vect{b},
-\end{equation}
-where $\Div{\qed}$ denotes the divergence operator. To ensure that the
-velocity field is compatible with the strain field is necessary that
-them satisfy the compatibility equation,
-\begin{equation}
-  \label{eq:Compatibility-equation}
-  \dot{\tens{\varepsilon}} = \GradS{\vect{v}} = \frac{1}{2}\left(
-    \Grad{\vect{v}} +  \GradT{\vect{v}} \right),
-\end{equation}
-where $\GradS{\qed}$ denotes the symmetric part of the gradient
-operation. Thorough the constitutive equation, the rate of the Cauchy stress
-tensor is defined to be
+\rho \frac{D\vect{v}}{Dt} = \Div{\tens{\sigma}} + \rho \vect{b}
+\end{equation}
+together with the natural boundary conditions of the Neumann type
+$\varGamma_n$. Next (iii) the constitutive equation as a linear
+application from $\Re^n$ to  $\Re^n$, which relates the
+strain tensor with the stress tensor,
 \begin{equation}
   \label{eq:Constitutive-equation}
-\dot{\tens{\sigma}} = \tens{D} \colon \dot{\tens{\varepsilon}},
-\end{equation}
-where $\tens{D}$ is the classical elasticity tensor. Finally we
-introduce the total derivative expression over the density field,
+\tens{\sigma} = \tens{D} \colon \tens{\varepsilon}.
+\end{equation}
+The final restriction is (iv) the mass conservation, which can be obtained by
+setting to zero the total derivative of the density field,
 \begin{equation}
   \label{eq:Rho-material-derivative}
-\frac{D \rho}{D t} = \dot{\rho} + \rho \Grad{\vect{v}}.
-\end{equation}
-Where if we impose $\frac{D \rho}{D t}$ to be zero, the conservation
-of mass is guarantee.
+  \frac{D \rho}{D t} = \dot{\rho} + \rho \Div{\vect{v}} = 0.
+\end{equation}
 
@@
   \label{eq:cauchy-secuence}
-  \Integral{3}{\vect{v}^{\psi}} < \infty\ \quad\text{and}\quad \Integral{3}{\Grad{\vect{v}^{\psi}}} < \infty
+  \Integral{3}{\vect{u}^{\psi}} < \infty\ \quad\text{and}\quad
+  \Integral{3}{\tens{\varepsilon}^{\psi}} < \infty
 \end{equation}
 The principle of virtual work states that the equilibrium solution to
-the boundary value problem of elasticity is the function $\vect{v} \in
-\mathcal{H}^1_0$ such that, for $\vect{v}^{\psi} \in
+the boundary-value problem of elasticity is the function $\vect{u} \in
+\mathcal{H}^1_0$ such that, for $\vect{u}^{\psi} \in
 \mathcal{H}^1_0$, the following holds:
@@
   \label{eq:BalanceMomentum_wf}
-  \Integral{3}{\rho\ \left( \Deriv{\vec{v}}{t}\ - \vec{b} \right) \cdot \vec{v}^{\psi}} =
-  \Integral{2}{\vec{t}\ \cdot \vec{v}^{\psi}} - \Integral{3}{\tens{\sigma} \cdot
+  \Integral{3}{\rho\ \left( \frac{d\vec{v}}{dt}\ - \vec{b} \right) \cdot \vec{u}^{\psi}} =
+  \Integral{2}{\vec{t}\ \cdot \vec{u}^{\psi}} - \Integral{3}{\tens{\sigma} \colon
    \tens{\varepsilon}^{\psi}},
 \end{equation}\\
-therefore (\ref{eq:BalanceMomentum_wf}) is the balance of momentum formulated in
-its weak form.
+therefore (\ref{eq:BalanceMomentum_wf}) together with
+\eqref{eq:Constitutive-equation} and
+\eqref{eq:Rho-material-derivative} represents the weak form
+formulation of the problem.
 
@@
 \label{sec:Galerkin-procedure}
-In order to arrive to a finite set of equations, the continuum domain
+In order to arrive to a finite set of equations, in contrast with the
+FEM, in MPM a double discretization procedure is performed as we will
+describe here below. First, the continuum domain
 $\Omega$ is discretized with a finite sum of material points (in the
-following particles), each one represent a part of the discretized domain $\Omega_p$ with $p = 1,2\ldots ,N_p$
-where $N_p$ is the number of particles. The material point $\vec{x}_p$ is
-defined at the centroid of each $\Omega_p$. Further, a computational grid
-is formed of a finite set of grid points with coordinates $\vec{x}_I\
-, I = 1,2\ldots ,N_n$, where $N_n$ is the number of grid nodes.
-
+following particles), each one
+represent a part of the discretized domain $\varOmega_p \subset
+\varOmega$ with $p = 1,2\ldots ,N_p$ where $N_p$ is the number of
+particles. The material point $\vec{x}_p$ is defined at the centroid
+of each $\Omega_p$, figure~\ref{fig:MPM-discretization}.
+Each material point is assigned with initial values of position,
+velocity, mass, volume and stress denoted by $\vec{x}_p$,
+$\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$, but also the
+virtual displacement field $\vect{u}^{\psi}_{p}$. Therefore, employing
+the definition of the material integral, where we recover the Riemann
+integral definition as an addition of a finite set of points, and
+their volumes are interpreted as quadrature weights. Consequently,
+individual terms in \eqref{eq:BalanceMomentum_wf} are solved as follows. 
+\begin{itemize}
+\item Acceleration forces :
+\begin{equation}
+    \label{eq:particle_acceleration_forces}
+    \Integral{3}{\rho\ \frac{d\vec{v}}{dt} \cdot \vect{u}^{\psi}} =
+    \frac{d\vec{v}_{p}}{dt} \cdot \vect{u}^{\psi}_{p}\ m_p.
+  \end{equation}\\
+\item Internal forces :
+  \begin{equation}
+    \label{eq:particle_internal_forces}
+    \Integral{3}{\tens{\sigma}\ \colon \tens{\varepsilon}^{\psi}} =
+   \tens{\sigma}_{p}\ \colon \tens{\varepsilon}^{\psi}_p \ V_p.
+  \end{equation}\\
+\item Body forces :
+\begin{equation}
+  \label{eq:particle_body_forces}
+  \Integral{3}{\rho\ \vec{b} \cdot \vect{u}^{\psi} } = 
+  \vec{b}_{p} \cdot \vect{u}^{\psi}_p\ m_p.
+\end{equation}\\
+\item Loads :
+\begin{equation}
+  \begin{aligned}
+    \label{eq:particle_load_forces}
+    \Integral{2}{\vec{t}\ \vect{u}^{\psi}} = \Integral{2}{\rho\
+      \vec{t}^s \cdot \vect{u}^{\psi}} = \vec{t}^s_{p} \cdot \vect{u}^{\psi}_{p}\ h^{-1}\ m_p ,
+  \end{aligned} 
+\end{equation}
+\end{itemize}
+where $h$ is the thickness of the continuum in a 2D case. Here is
+where the second discretization procedure appears. A background mesh
+composed by a finite set of grid points with coordinates $\vec{x}_I\
+, I = 1,2\ldots ,N_n$, is generated. Where $N_n$ is the number of grid
+nodes. This mesh is employed as a support to compute gradients and
+divergences.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}\sidecaption
   \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Discretization_MPM}
-  }
-  \caption{MPM discretization.}
+  \resizebox{0.8\hsize}{!}{
+    \includegraphics[width=\textwidth]{Figures/Mesh-particles-back}}
+  \caption{Description of the spatial discretization for domain presented in the
+    figure~\ref{fig:Continuum-solid}. Blue mesh represent the
+    background computational support, and the grid mesh conforms the
+    discretized continuum body.}
   \label{fig:MPM-discretization}
 \end{figure}
-
-Each material point is assigned with initial values of position,
-velocity, mass, volume and stress denoted by $\vec{x}_p$,  $\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$. The problem is then integrated using a discrete number of time
-steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
-is the total number of time steps.  So employing the definition of the
-material integral, individual terms of \eqref{eq:BalanceMomentum_wf}
-are solved as follows. 
-\begin{itemize}
-\item Acceleration forces :
-\begin{equation}
-    \label{eq:particle_acceleration_forces}
-    \Integral{3}{\rho\ \vec{a}\ \vect{v}^{\psi}} =& \sum^{N_p}_{p}
-   \dot{\vec{v}}_{p}\ \vect{v}^{\psi}_{p}\ m_p.
-  \end{equation}\\
-\item Internal forces :
-  \begin{equation}
-    \label{eq:particle_internal_forces}
-    \Integral{3}{\tens{\sigma}\ \colon \Grad{\vec{\psi}}} = \sum^{N_p}_{p}
-   \tens{\sigma}_{p}\ \Grad{\tens{\psi}_{p}}\ V_p.
-  \end{equation}\\
-\item Body forces :
-\begin{equation}
-  \label{eq:particle_body_forces}
-  \Integral{3}{\rho\ \vec{b}\ \vect{v}^{\psi} } = \sum^{N_p}_{p}
-  \vec{b}_{p}\ \vect{v}^{\psi}_p\ m_p.
-\end{equation}\\
-\item Loads :
-\begin{equation}
-  \begin{aligned}
-    \label{eq:particle_load_forces}
-    \Integral{2}{\vec{t}\ \vect{v}^{\psi}} = \Integral{2}{\rho\
-      \vec{t}^s\ \vect{v}^{\psi}} = \sum^{N_p}_{p} \vec{t}^s_{p}\ \vect{v}^{\psi}_{p}\ h^{-1}\ m_p ,
-  \end{aligned} 
-\end{equation}
-\end{itemize}
-where $h$ is the thickness of the continuum in a 2D case. Introducing \eqref{eq:particle_acceleration_forces},
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Introducing \eqref{eq:particle_acceleration_forces},
 \eqref{eq:particle_internal_forces}, \eqref{eq:particle_body_forces}, 
 and \eqref{eq:particle_load_forces} in \eqref{eq:BalanceMomentum_wf},
-and approximating the virtual displacement of the particle $p$ as
-$\vec{\psi}_{p} = N_I(\vec{x}_p)\cdot \vect{1} = N_{Ip}$. We reach to
-the particle balance of forces of the continuum,
+and approximating the displacement field of the particle
+$p$ as $\vec{u}_{p} = N_{Ip} \vect{u}_I$, $\vec{u}^{\psi}_{p} = N_{Ip} \vect{u}_I^{\psi}$,
+and its gradient as $\tens{\varepsilon}_p = (\vect{u}_I \otimes
+\Grad{N_{Ip}})^s$, $\tens{\varepsilon}_p^{\psi}= (\vect{u}_I^{\psi} \otimes \Grad{N_{Ip}})^s$.
+We reach to the nodal balance of forces of the continuum,
 \begin{equation}
@@
   \label{eq:particle_nod_mass}
-  \tens{m}_{IJ} =
-  \sum^{Np}_{p} N_{Ip} m_p N_{Jp},
-\end{equation}
-and internal and external forces are computed as follows,
+  \tens{m}_{IJ} = N_{Ip} m_p N_{Jp}.
+\end{equation}
+To improve the computational efficiency and stability, the nodal mass matrix
+\eqref{eq:particle_nod_mass} can be substituted by the lumped mass
+matrix $\tens{m}_{IJ}^{lumped}$.
+Later, internal and external forces are computed as follows,
 \begin{equation}
   \label{eq:nodal_internal_forces}
-  \vec{f}_{I}^{int} = - \sum^{N_p}_{p} \Grad{N_{Ip}}
-  \tens{\sigma}_{p} \frac{m_p}{\rho_p}
+  \vec{f}_{I}^{int} = - \tens{\sigma}_{p} \cdot \Grad{N_{Ip}} \frac{m_p}{\rho_p}
 \end{equation}
@@
   \label{eq:nodal_external_forces}
-  \vec{f}_{I}^{ext} = \sum^{N_p}_{p} N_{Ip} m_p \vec{b}_{p} + \sum^{N_p}_{p}
-  N_{Ip} m_p h^{-1} \vec{t}^s_{p}
+  \vec{f}_{I}^{ext} = N_{Ip}\ \vec{b}_{p}\ m_p  + N_{Ip}\ \vec{t}^s_{p}\ m_p h^{-1} 
 \end{equation}
@@
     \tens{\varepsilon}_{p}}{\Delta t} =
-  \frac{1}{2}\left[\Grad{N_{Ip}}\ \vec{v}_{I} + \Grad{N_{Ip}}^T\
-    \vec{v}_{I}\right].
-\end{equation}
-Later, imposing $\frac{D \rho}{D t} = 0$, we ensures the mass
+  \frac{1}{2} \left[\Grad{N_{Ip}}\ \otimes \vec{v}_{I} + \vec{v}_{I} \otimes
+    \Grad{N_{Ip}}\ \right].
+\end{equation}
+Next, imposing $\frac{D \rho}{D t} = 0$, we ensures the mass
 conservation and update the density field.
@@
 
-To improve the computational efficiency and stability, the nodal mass matrix
-\eqref{eq:particle_nod_mass} can be substituted by the lumped mass
-matrix $\tens{m}_I$. Therefore the nodal balance of momentum equation \eqref{eq:particle_balance_forces3} can be simplified to
-\begin{equation}
-  \label{eq:SimplyNodalMomentum}
-  \dot{\vec{p}}_{I} = \tens{m}_I\ \vec{a}_{I} = \vec{f}_{I}^{int} + \vec{f}_{I}^{ext}.
-\end{equation}
-To solve the equation \eqref{eq:SimplyNodalMomentum}, a second order
-temporal integration scheme is required. The next step is to advect
-the particles solving,
+Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order
+temporal integration scheme is required. Therefore, time is
+discretized in to a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
+is the total number of time steps. Once the nodal equilibrium equation it is solved, the values in the nodes are
+interpolated back in to the particles and each particle it is advected
+to the new position,
 \begin{equation}
   \label{eq:Updated_Lagrangian}
-  \dot{\vec{v}}_p = \sum^{N_n}_{I}\vec{a}_{I}\ N_{Ip},\quad and\quad \dot{\vec{x}}_{p} = \sum^{N_n}_{I}\vec{v}_{I}\ N_{Ip}  
-\end{equation}
-To solve this equations, the forward Euler algorithm is the common
-choose for this in the MPM literature. In next lines, a complete
-description of the standard MPM algorithm will be described.
-
-\section{Explicit predictor-corrector scheme for MPM.}
-\label{sec:epc-algor-mpm}
-
-To solve equations \eqref{eq:SimplyNodalMomentum} and
-\eqref{eq:Updated_Lagrangian}, a time integration scheme is
-required. It has been described in detail by many researchers
+  \dot{\vec{v}}_p = N_{Ip}\ \vec{a}_{I},\quad and\quad
+  \dot{\vec{x}}_{p} = N_{Ip}\ \vec{v}_{I}  
+\end{equation}
+In MPM literature, this equations
+(\ref{eq:particle_balance_forces3}) and (\ref{eq:Updated_Lagrangian}),
+are solved with an explicit forward Euler algorithm. The time integration scheme of MPM has been described in detail by many researchers
 \cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and summarized
-in Figure \ref{fig:MPM_algorithm}. Other authors have proposed many
-others time integration alternatives like
-\cite{Guilkey2003}, \cite{Tran2019e}, \cite{Charlton2017}. In the first publication on
-the MPM \cite{Sulsky1994}, the nodal acceleration in employed to
-update the particles as
+in figure~\ref{fig:MPM_algorithm}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.8\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/MPM_scheme}
+  }
+  \caption{Description of MPM standard algorithm.}
+  \label{fig:MPM_algorithm}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Other authors have proposed many others time integration alternatives
+like \cite{Guilkey2003}, \cite{Tran2019e}, \cite{Charlton2017}. In the
+first publication on MPM \cite{Sulsky1994}, the nodal acceleration
+was employed to update the particles as
 \begin{equation}
   \label{eq:Sulsky-1994-UL-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
-  \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{a}_{I}^{k}
+  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\ N_{Ip}^{k}\ \vec{a}_{I}^{k}
 \end{equation}
@@
   \label{eq:Sulsky-1994-UL-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \sum^{N_n}_{I}N_{Ip}^{k}\ \vec{v}_{I}^{k}.
-\end{equation}
-However, in Andersen (2009)\cite{thesis_Andersen_2009} this
-algorithm has been shown to be numerically unstable due to that
+  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ N_{Ip}^{k}\ \vec{v}_{I}^{k}.
+\end{equation}
+However, as Andersen (2009)\cite{thesis_Andersen_2009} point out, this algorithm has been shown to be numerically unstable due to that
 $\vect{f}_I^{int,k}$ can be finite for an infinitesimal nodal mass
@@
   \label{eq:Zhang-2016-UL-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\
-  \sum^{N_n}_{I}\frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I},
+  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\ \frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I},
 \end{equation}
 Later Tran \& Solowski (2019)\cite{Tran2019e} presented a
-generalized-$\alpha$ scheme for the MPM inspired in the explicit time
+generalized-$\alpha$ scheme for MPM inspired in the explicit time
 integration algorithm proposed by Chung \& Hulbert
@@
 \cite{Tran2019e}. But it can present the same numerical instabilities
-as in \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v} when nodal masses become infinitesimal.
-Here we propose a explicit predictor-corrector scheme for MPM based on the Newmark a-form with
+as in \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v} when
+nodal masses become infinitesimal, and requires extra storage for
+nodal values of acceleration and previous steps.
+
+\section{Explicit predictor-corrector scheme for MPM.}
+\label{sec:epc-algor-mpm}
+
+In this section, a explicit predictor-corrector time integration
+scheme is presented. It is based in the Newmark a-form 
 $\gamma = 0.5$ and $\beta = 0$ which is the central difference
-explicit. This method is devoted to solve a system of equations of type
+explicit. This method is devoted to solve a system of equations of the type
 \begin{equation*}
   \Matrix{M}_{IJ}\ddot{\Vector{d}}_{J} + \Matrix{C}_{IJ}\dot{\Vector{d}}_{J} +
-  \Matrix{K}_{IJ}\Vector{d}_{J} = \Vector{F}_{I}
+  \Matrix{K}_{IJ}\Vector{d}_{J} = \Vector{F}_{I}.
 \end{equation*}
-Nevertheless it can be applied for an isolated mass, therefore it is
-possible to apply this methods successfully in the MPM framework as
-was proved by \cite{Tran2019e}. Taking the predictor
-definition from the classic literature \cite{Hughes2000} and
-calculating particles velocity and acceleration as described in 
-\cite{Zhang_book_2016}, we get the following expression for the
-\textbf{predictor} stage for both velocity and displacement.
-\begin{equation}
-  \label{eq:5}
-  \vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
-  \underbrace{\sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\
-      N_{Ip}^k}{\tens{m}_I^k}}_{\vec{v}_p^{k}} + \frac{1}{2}\Delta
-  t^2\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\
-      N_{Ip}^k}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
-\end{equation}
-\begin{equation}
-  \label{eq:Predictor-velocity}
-  \vec{v}_p^{k+1} = \vec{v}_p^n + (1 - \gamma)\ \Delta t\
-  \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\
-      N_{Ip}^k}{\tens{m}_I^k}}_{\vec{a}_p^{k}}
-\end{equation}
-
-Consequently, the \textbf{corrector} stage for the particles velocity is in the
-following way
-\begin{equation}
-  \vec{v}_{p}^{k+1} = \vec{v}_{p}^{k+1} +
-  \gamma\ \Delta t\ \underbrace{\sum^{N_n}_{I}\frac{\vec{f}_{I}^{k+1}\ N_{Ip}^{k+1}}{\tens{m}_I^{k+1}}}_{\vec{a}_p^{k+1}}  
-\end{equation}
-
-Notice that the predictor of the particle displacement is
-computed using information only from the predictor of the
-previous step. However, velocities are computed using half information
-of the past corrector and half of the past predictor. Therefore here we share
-similarities with the \textbf{leapfrog integration} which updates the
-position at full time step, but updates the velocity at half time
-steps. Due to its simplicity allows be implemented with minor modifications
+As MPM has a nodal stage, it is possible to apply this methods
+successfully in MPM framework as was proved by
+\cite{Tran2019e}. Taking the predictor definition from and calculating
+nodal velocity, and updating particles position employing nodal values
+of velocity and acceleration. The predictor-corrector algorithm has
+been described in the classic literature \cite{Hughes2000}, and its
+computational advantages and stability were widely proof by Liu
+\cite{Xiaojian94}. The ``classic'' PCE algorithm starts with a
+predicted value of the nodal velocity at the $(k+1)$th time step denoted by $\vec{\tilde{v}}_I^{k+1}$ given as,
+\begin{equation}
+  \label{eq:Predictor-velocity-I}
+  \vec{\tilde{v}}_I^{k+1} = \vec{v}_I^k + (1 - \gamma)\ \Delta t\ \vec{a}_I^k
+\end{equation}
+In \eqref{eq:Predictor-velocity-I} arise a \textit{user-defined}
+parameter $\gamma \geq 0$. This parameter influences both the predictor accuracy
+and the stability of the algorithm. As point out Liu
+\cite{Xiaojian94}, the truncation error of the predictor formula is
+$O(\Delta t^3)$ when $\gamma = 0.5$, and is unconditionally stable if
+$ 0 < \gamma \leq 0.25$.
+
+To accommodate this step to MPM framework, it is necessary to get
+the nodal values of the velocity and acceleration throughout a variational
+recovery process where particles quantities are transferred to the
+mesh nodes. This technique arise as a generalization of the super-convergent recovery
+procedures described by Zienkiewicz \& Zhu \cite{ZZ1992_I} (\textit{ZZ})
+in the context of FEM. In MPM Gauss quadrature is not employed as
+integrals are computed following the Riemann integral definition,
+where each component of the summation correspond to a particle of the
+discretization. Also Bardenhagen \& Kober \cite{Bardenhagen2004}
+proved that thorough this information-transference technique mass and momentum are conserved. So for a general particle variable $\Phi_p$ employing the
+\textit{ZZ} technique is possible to get its nodal homologous $\Phi_I$  as,
+\begin{equation}
+  \label{eq:Variational-recovery}
+   \Phi_I = \frac{m_p N_{Ip} \Phi_p}{m_I}
+ \end{equation}
+ Therefore, to get a analogous expression for
+ \eqref{eq:Predictor-velocity-I} in the context of MPM, the
+ procedure described in the equation \eqref{eq:Variational-recovery}
+ is employed reaching to,
+ \begin{equation}
+   \label{eq:Predictor-velocity-II}
+   \vec{\tilde{v}}_I^{k+1} = \underbrace{\frac{N_{Ip}^{k} m_p
+       \vec{v}_p^k}{m_I}}_{\vec{v}_I^{k}} + (1 - \gamma)\ \Delta t\  \underbrace{\frac{N_{Ip}^{k} m_p \vec{a}_p^k}{m_I}}_{\vec{a}_I^{k}}
+ \end{equation}
+Nonetheless this way of computing the predictor stage can introduce
+instabilities due to numerical cancellation likewise the original
+Sulky algorithm. Thankfully this can be avoided easily by the
+equivalent formulation \eqref{eq:Predictor-velocity-II}, 
+\begin{equation}
+  \label{eq:Predictor-velocity-II}
+  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
+\end{equation}
+This way of computing the nodal predictor is both numerically stable
+and minimize the computational effort. Once nodal velocity are
+obtained, the essential boundary conditions are imposed. And in the
+following, the ``classic'' MPM algorithm continues to reach to the
+equilibrium equation \eqref{eq:particle_balance_forces3}. Here we
+continue with the \textit{corrector} stage, due to the fact that we
+already have nodal velocity, this step is computed in the same way as
+in FEM,
+\begin{equation}
+  \label{eq:Corrector-velocity}
+  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}
+\end{equation}
+Finally updated particle kinetics are computed using nodal values as,
+\begin{align}
+  \label{eq:Update-lagrangian-pce}
+        &\vec{a}_p^{k+1} = \vec{a}_p^n +
+        \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
+        \frac{N_{Ip}^k\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
+         N_{Ip}^k\ \vec{v}_{I}^{k} +
+        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k} 
+\end{align}
+Notice that particle displacement is computed using the corrected
+nodal velocities and the accelerations computed with the velocities
+of the predictor. However, particles velocities and accelerations
+are computed using the corrected velocities. Therefore here we share similarities
+with the \textit{leapfrog integration} which updates the position at
+full time step, but updates the velocity at half time steps. Notice
+also that with this approach the calculation of nodal momentum values
+are not required. Due to its simplicity allows be implemented with minor modifications
 over a standard forward Euler. It is summarized in shape of
-pseudo-algorithm \ref{alg:PCE-algorithm}.
-
-\begin{algorithm}
-\floatname{algorithm}{Algorithm}
-\renewcommand{\thealgorithm}{}
-\caption{Explicit scheme : Newmark central difference}
-\label{alg:Second_step_MPM_2STG}
-\begin{algorithmic}[1]
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
-  \STATE \textbf{Explicit Newmark Predictor} ($\gamma = 0.5$) :
-  \begin{align*}
-    &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\ \sum^{N_n}_{I}\frac{\vec{p}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k} + \frac{1}{2}\Delta t^2\ \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k}\\
-    &\vec{v}_p^{k+1} = \vec{v}_p^n + (1 - \gamma)\  \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k}\ N_{Ip}^k}{\tens{M}_I^k}\Delta t        
-  \end{align*}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \STATE \textbf{Discard the previous nodal values}.
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \STATE \textbf{Transference of particles kinetics information to the
-    mesh}:\\
-  Calculate the lumped mass matrix $\tens{M}_{I}$,
-  and the nodal momentum $\vec{p}_{I}$ with the predicted values.
-  \begin{equation*}
-    \tens{M}_{I} = \sum_{p}^{N_p} m_p\ N_{Ip}^{k+1},
-  \end{equation*}
-  \begin{equation*}
-    \vec{p}_{I}^{k+1} = \sum_{p}^{N_p} m_p\ \vec{v}_{p}^{k+1}\ N_{Ip}^{k+1},
-  \end{equation*}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \STATE \textbf{Impose essential boundary conditions over momentum nodal
-    values}:\\
-  At the fixed boundary, set $\vec{p}_{I}^{k+1} = 0$. Later, get the
-  nodal values of the velocity field $\vec{v}_{I}^{k+1} =
-  \frac{\vec{p}_{I}^{k+1}}{\tens{M}_{I}}$
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \STATE \textbf{Deformation tensor increment calculation}.
-  \begin{align*}
-    &\dot{\tens{\varepsilon}_{p}}^{k+1} = \frac{1}{2}\ \sum_{I}^{N_n}
-    \Grad{N_{Ip}^{k+1}}\vec{v}_{I}^{k+1} +
-      (\Grad{N_{Ip}^{k+1}}\vec{v}_{I}^{k+1})^T \\
-    &\Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\ \dot{\tens{\varepsilon}_{p}}^{k+1}
-  \end{align*}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \STATE \textbf{Update the density field}:\\
-  \begin{equation*}
-    \rho_p^{k+1} = \frac{\rho_p^k}{1 + \mathit{tra}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.
-  \end{equation*}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \STATE \textbf{Balance of forces calculation}:\\
-  Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
-  \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
-  \eqref{eq:nodal_internal_forces} and \eqref{eq:nodal_external_forces} in the time step $k+1$. In the
-  grid node $I$ is fixed in one of the spatial dimensions, set it to
-  zero to make the grid nodal acceleration zero in that direction.\\
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \STATE \textbf{Integrate the grid nodal momentum equation :}\\
-  Calculate the nodal momentum $\vec{p}_{I}$ in $k+1$. 
-  \begin{equation*}
-    \vec{p}_{I}^{k+1} = \vec{p}_{I}^{k} + \vec{f}_{I}^{k+1}\Delta t
-  \end{equation*}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \STATE \textbf{Explicit Newmark Predictor}:
-  \begin{equation*}
-    \vec{v}_{p}^{k+1} = \vec{v}_{p}^{k+1} +
-    \gamma \sum^{N_n}_{I}\frac{\vec{f}_{I}^{k+1}\ N_{Ip}^{k+1}}{\tens{m}_I^{k+1}}\Delta t  
-  \end{equation*}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\end{algorithmic}
-\end{algorithm}
-
-\begin{figure*}\sidecaption
-  \centering
-  \resizebox{0.6\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/MPM_scheme}
-  }
-  \caption{MPM standard algorithm.}
-  \label{fig:MPM_algorithm}
-\end{figure*}
+pseudo-algorithm \ref{app:explicit-predictor-algorithm}.
 
@@
 \label{sec:local-max-ent}
-
-The previous lines describe the main algorithm without defining an
-interpolation technique. A direct consequence of this, is that it is
-possible to adopt a width range of shape functions and interpolation techniques. The MPM has been
-successfully applied to a wide range of problems due to its ability to
-deal with large strain problems without mesh distorsion issues inherent to
-mesh based methods like FE. However, in the simulations made with the
-original MPM, there are numerical noises when particles crossing
-the cell boundaries. These numerical inaccuracies give rise to the
-development of other interpolation techniques. Some of this
-alternatives techniques are the generalized interpolation material
-point method (GIMP) Bardenhagen \& Kober (2004)\cite{Bardenhagen2004},
-the dual domain material point method (DDMP) Zhang {\it et al.}
-(2011)\cite{Zhang2011a}, the B-Spline MPM Tran {\it et al.}
-(2019)\cite{Tran2019a}, the Conservative Taylor Least
-Squares reconstruction Wobbes {\it et al.}
-(2018)\cite{E_Wobbes_2018} and more recently the local
-maximum-entropy (or local \textit{max-ent}) shape function first
-introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} has been tested
-under the MPM framework by Wobbes {\it et al.}
-(2020)\cite{Wobbes2020} where they prof that simulations performed with the maxent basis functions
-show considerably more accurate stress approximations for
-MPM. Although, in \cite{Wobbes2020} authors does not deep in $\beta$
-parameter benefits
-
-The maximum-entropy estimate is defined as the type of statistical
-inference, which is the least biased possible on the given information
-\cite{Jaynes1957}. The basic idea of the shape functions based on such
+The popularity of MPM has increase notoriously during
+the recent years due to its ability to deal with large strain problems
+without mesh distorsion issues inherent to mesh based methods like
+FEM, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations
+made with the original MPM, there are numerical noises when particles
+crossing the cell boundaries. Local maximum-entropy (or
+local \textit{max-ent}) shape function first introduced by Arroyo \&
+Ortiz (2006)\cite{Arroyo2006} has been recently tested under MPM framework
+by Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
+simulations performed with the \textit{max-ent} basis functions show
+considerably more accurate stress approximations for MPM. Although, in
+\cite{Wobbes2020} authors does not deep in how the regularization
+parameter $\beta$ affects to the accuracy and stability of the solution.
+
+The basic idea of the shape functions based on such
 an estimate is to interpret the shape function $N_I(\vec{x})$ as the
@@
 \dots, n$. Here $n$ is the number of nodes in the domain.
-Taking Shannon's entropy as the starting point:
+This approximation scheme represents a optimal compromise, in the sense of
+Pareto, between the \textit{unbiased statistical inference} based on
+the nodal data which leads to the principle of \textit{maximum-entropy}
+stated by Jaynes \cite{Jaynes1957}, and the definition of local shape
+functions of \textit{least width} the least biased shape functions.
+
+Taking the definition of entropy as a measure of how uncertainty a
+random variable is averaged on all its possible outcomes. And adopting
+the Shannon's entropy as the starting point:
 \begin{equation}
@@
 shape function $N_I(\vec{x})$,  satisfying both the zeroth and
-first-order consistency. The least-biased approximation scheme is given by
-\begin{eqnarray}
-  \text{(ME)} \hspace{0.2cm} \text{Maximize} \hspace{0.1cm}H(p) &=&  -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I } \nonumber \\
-  \text{subject to} \hspace{0.5cm} p_I &\ge& 0, \hspace{0.5cm} \text{I=1, ..., n} \nonumber \\
-  \sum_{I=1}^{N_n}{p_I} &=& 1 \nonumber \\
-  \sum_{I=1}^{N_n}{p_I \vec{x}_I} &=& \vec{x} \nonumber 
-\end{eqnarray}
+first-order consistency. The least-biased approximation scheme is
+given by
+\begin{align*}
+  \label{eq:least-biased-approximation-scheme}
+  \text{(LME)} \hspace{0.15cm} &\text{Maximize} \hspace{0.15cm} H(p) =
+  -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I }\\
+  &\text{subject to}\
+  \begin{cases}
+    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
+  \end{cases}
+\end{align*}
 The local max-ent approximation schemes (LME) as a Pareto set,
 defined by \cite{Arroyo2006} is as follows
-\begin{eqnarray}
-  \text{(LME)}_{\beta} \hspace{0.5cm} \text{For fixed} \hspace{0.2cm} \vec{x} \hspace{0.2cm} \text{minimise}  \nonumber \\
-  \hspace{0.5cm}f_{\beta}(\vec{x}, p) &=& \beta H(\vec{x},p) - H(p)  \nonumber  \\
-  \text{subject to} \hspace{0.5cm} p_I &\ge& 0, \hspace{0.2cm} \text{I=1, ..., n}  \nonumber \\
-  \sum_{I=1}^{N_n}{p_I} &=& 1  \nonumber \\
-  \sum_{I=1}^{N_n}{p_I \, \vec{x}_I} &=& \vec{x}    \nonumber 
-\end{eqnarray}
+\begin{align*}
+  \label{eq:LME-scheme-pareto-set}
+  \text{(LME)}_{\beta} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
+  \vec{x} \hspace{0.15cm} \text{minimise} \hspace{0.15cm} f_{\beta}(\vec{x}, p) = \beta H(\vec{x},p) - H(p) \\
+  &\text{subject to}\
+  \begin{cases}
+    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
+  \end{cases}
+\end{align*}
 for $\beta \in (0,\infty)$ is Pareto optimal. The unique solution of
@@
   \label{eq:LME-p}
-p(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +  \vec{\lambda}  \;  (\vec{x}-\vec{x}_I)         \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
+p(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
+    \vec{\lambda} \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
 \end{equation}
@@
   \label{eq:LME-Z}
-Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \, | \vec{x}-\vec{x}_I|^2 + \vec{\lambda}  \,  (\vec{x}-\vec{x}_I)  \right]}
-\end{equation}
-being $\vec{\lambda}^*(\vec{x})$ the unique minimiser  for $\log Z(\vec{x}, \vec{\lambda})$
-
-In order to obtain the first derivatives of the shape function, it is  also necessary to compute~$\nabla p^*_I$ 
+Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \; |\vec{x}-\vec{x}_I|^2 + \vec{\lambda} \cdot (\vec{x}-\vec{x}_I)  \right]}
+\end{equation}
+being $\vec{\lambda}^*(\vec{x})$ the unique minimiser  for $\log
+Z(\vec{x}, \vec{\lambda})$. In order to obtain the first derivatives of the shape function, it is also necessary to compute~$\nabla p^*_I$ 
 \begin{equation}
@@
 \end{eqnarray}
-Note that, the objective of the above procedure is to find the $\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. 
-The traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27}) to calculate small increments of $\partial\vec{\lambda}$ in a Newton-Raphson approach.
-
-Similar to alternative non-polynomial meshfree basis functions, the LME approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem.
-Due to the FE-compatibility, the LME shape function is degenerated to linear finite element shape function if $d+1$ neighbouring nodes are chosen as the support.
-The support size of LME shape functions may be controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$ (e.g.
-two dimensional example shown in Fig.
-\ref{fig:LME_MPM})\cite{Arroyo2006}.
-Since  $p_I$  is defined in  the entire domain, in practice,  the function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance, 10$^{-6}$, for example,  would ensure a reasonable range of neighbours, see \cite{Arroyo2006} for details.
-This  tolerance defines the limit values of the influence radius and   is used thereafter to find the neighbour nodes of a given integration point.
-
-\begin{figure}
+Note that, the objective of the above procedure is to find the
+$\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. The
+traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27})
+to calculate small increments of $\partial\vec{\lambda}$ in a
+Newton-Raphson approach. Similar to alternative non-polynomial meshfree basis functions, the
+LME approximation scheme requires more than $d+1$ nodes to determine
+the values of the shape functions as well as their derivatives at any
+point in the convex hull of the nodal set, where $d$ is the dimension
+of the problem. The support size of LME shape functions may be
+controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
+\cite{Arroyo2006} (e.g. two dimensional example shown in figure~\ref{fig:LME_MPM}).
+ Since  $p_I$  is defined in the entire domain, in practice, the
+function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
+10$^{-6}$, for example,  would ensure a reasonable range of
+neighbours, see \cite{Arroyo2006} for details. This tolerance defines
+the limit values of the influence radius and is used thereafter to
+find the neighbour nodes of a given integration point. Regarding this
+aspect, an crucial consideration for the implementation of the LME
+shape functions in MPM is exposed. To avoid the transference of
+particle information to those nodes fare apart from the particle
+domain $\Omega_p$, a especial treatment of the neighbour nodes for
+those particles close to the boundary is required. It consists in
+select only those nodes which position $\vect{x}_I$ lies inside of the
+domain $\Omega$. This can be performed by employing the nodal
+connectivity of the background mesh. And activating for computing only
+those nodes whose element has a particle inside of it as we can see in
+figure~\ref{fig:Particle-discretization}. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
   \centering
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun}
-    \label{fig:MPM_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun_dx}
-    \label{fig:MPM_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/MPM_Shape_Fun_dy}
-    \label{fig:MPM_Shape_Fun_dy}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun}
-    \label{fig:LME_17.3_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun_dx}
-    \label{fig:LME_17.3_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_17_3_Shape_Fun_dy}
-    \label{fig:LME_17.3_Shape_Fun_dy}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun}
-    \label{fig:GIMP_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun_dx}
-    \label{fig:GIMP_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/GIMP_Shape_Fun_dy}
-    \label{fig:GIMP_Shape_Fun_dy}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun}
-    \label{fig:LME_10.0_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun_dx}
-    \label{fig:LME_10.0_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_10_0_Shape_Fun_dy}
-    \label{fig:LME_10.0_Shape_Fun_dy}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun}
-    \label{fig:LME_7.0_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun_dx}
-    \label{fig:LME_7.0_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_7_0_Shape_Fun_dy}
-    \label{fig:LME_7.0_Shape_Fun_dy}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun}
-    \label{fig:LME_5.0_Shape_Fun}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun_dx}
-    \label{fig:LME_5.0_Shape_Fun_dx}
-  }
-  \subfloat{
-    \includegraphics[width=0.3\columnwidth]{Figures/LME_5_0_Shape_Fun_dy}
-    \label{fig:LME_5.0_Shape_Fun_dy}
-  }
-  \caption{Local max-ent shape functions for a two-dimensional
-    arrangement of nodes, and spatial derivatives for several values
-    of $\gamma = \beta/h^2$.}
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Particle-discretization}
+  }
+  \caption{This tolerance defines the limit values of the influence
+    radius and is used thereafter to find the neighbour nodes of a
+    given integration point. The picture also shows the neighbourhood
+    criterion to select those node inside of $\Omega$.} 
+  \label{fig:Particle-discretization}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Due to the FE-compatibility, the LME shape function is degenerated to
+linear finite element shape function if $d+1$ neighbouring nodes are
+chosen as the support. Furthermore, with a conveniently adopted
+\textit{regularization} parameter it is possible to get a GIMP-like
+shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}.  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+  \centering
+  \subfigure[Q4]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun}\\
+      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dx}\\
+      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dy}
+    \end{tabular}  
+  }
+  \subfigure[$\text{LME}_{17}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dx}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \subfigure[uGIMP]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun}\\
+      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dx}\\
+      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \subfigure[$\text{LME}_{10}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dx}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dy}    
+    \end{tabular}
+  }
+  \subfigure[$\text{LME}_{5}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dx}\\
+      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \caption{Comparative of linear piecewise shape functions (Q4) and
+    uniform GIMP shape functions (uGIMP) \textit{versus} Local max-ent
+    shape functions for a two-dimensional arrangement of nodes, and
+    spatial derivatives for several values of $\gamma = \beta/h^2$.}
   \label{fig:LME_MPM}
-\end{figure}
-
-\section{Numerical results : 1D Elastic bar}
-\label{sec:dynamic-benchmark}
-
-In this section, the benchmark proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995} is considered to illustrate the
-capacity of MPM \cite{Sulsky1994} and OTM
-models to avoid tensile instabilities.
-
-In the one-dimensional bar sketched in
-the figure \ref{fig:Dyka_Bar}, the left end of the bar is fixed and
-the right and an initial velocity $v_0 = 5\ m/s$ is given to the last
-quarter of it in the x positive direction. The length of it is 0.1333
-meters with an unit section. The elastic parameters consider for this
-test are:
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
+influence area of the shape function is controlled by the Euclidean
+norm, therefore the search area is geometrically a circle in 2D, or a
+sphere in 3D. Building upon the idea of anisotropic shape functions,
+\cite{Kochmann2019} introduced an enhanced version of the original
+local max-ent scheme, which uses an anisotropic support to deal with
+tensile inestability. Nonetheless this is out of the scope of the
+present document but will be incorporated in future research.
+
+\section{Application to linear elasticity dynamic problems.}
+\label{sec:Application-linear-elasticity-dynamic-problems}
+
+This section is devoted to test the ability of both predictor-corrector
+time integration scheme and the local \textit{max-ent} approximants to
+overcome spurious oscillations due to the grid crossing and high
+frequency loads under the context of MPM Two different test has
+been adopted for this purpose, the benchmark proposed by Dyka \& Ingel
+(1995)\cite{Dyka1995} and the test proposed in the PhD thesis of
+Andersen (2009)\cite{thesis_Andersen_2009}. In all calculations we confine out attention to
+uniformly distribute node and particle sets. The accuracy of the PCE
+scheme is compared to the standard FE. In addition \textit{max-ent} solutions
+are compared with those provided by uGIMP and Q4 shape functions, also
+we compare MPM performance with OTM and FEM. All simulations were
+performed with in-hose software.
+
+\subsection{Dyka bar}
+\label{sec:dyka-bar}
+
+This benchmark was proposed due to its ability to shows the capability
+of the proposed time integration algorithm to avoid velocity
+fields instabilities. It consists in a one-dimensional bar with a
+length of 0.1333 meters, sketched in the
+figure~\ref{fig:Dyka_Bar}. The boundary conditions are in the right
+border displacement are constrained ($\vect{v} \rvert_{x=L} = 0$) and
+in the left displacement are let free ($\tens{\sigma} \rvert_{x=0} =
+0$). And a initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
+last quarter of it. Finally, the elastic parameters consider for this test are:
 \begin{itemize} 
@@
 \end{itemize}
-
-The results are provided for the explicit predictor-corrector version of the
-MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM algorithms. For MPM, piecewise-
-linear, uGIMP and \textit{max-ent} basis functions are employed. The OTM
-algorithm is used only with \textit{max-ent} shape functions.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}\sidecaption
   \centering
-  \resizebox{0.8\hsize}{!}{
+  \resizebox{\hsize}{!}{
     \input{Figures/Dyka_bar.tex}}
-  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar. }
+  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
   \label{fig:Dyka_Bar}
 \end{figure}
-
-The boundary conditions are:
-\begin{equation}
-  \label{eq:3}
-  \sigma \rvert_{x=L} = 0 \quad , \quad v \rvert_{x=0} = 0
-\end{equation}
-
-The analytical solution in terms of velocity
-\ref{fig:vel_analytics_dyka}, and stress
-\ref{fig:stress_analytics_dyka} can be found in the appendix
-\ref{app:analytical_sol} given by the Method of characteristics. For
-the convergence analysis, the root-mean-square (RMS) error in the
-displacement is computed. RMS error is defined as follows
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this case a duration of 0.0001 seconds for the simulation is
+consider. Therefore, the elastic wave generated travel thorough the bar
+(from A to C and back to A) at least two times. For the spatial
+discretization we propose a set a seven nodal mesh sizes (0.1, 0.3325, 0.5,
+1.0, 3.3325, 6.665, 10.0) in millimeters. For each element a number of
+four particles was selected. In the initial layout, particles are
+occupying the exact quadrature points of a linear quadrilateral. With
+the exception of the uGIMP simulation where gaps or overlap between
+voxels of each particle are not allowed. In those cases, each particles
+occupy the center of each cell quarter. For all simulations, time step
+is controlled by a Courant-Friedrichs-Levy condition of 0.1, were the adopted
+celerity is computed as,
+\begin{equation}
+  \label{eq:Cel}
+  Cel = \max\{\max_{p \in \Omega_p}\{ \vect{v}_p \} , \max_{p \in \Omega_p}\{ \sqrt{\frac{E_p}{\rho_p}} \} \}
+\end{equation}
+A important consideration regarding modellization concerns to the
+background mesh. Notice that free border of the bar has a maximum
+horizontal displacement of 0.03 millimeters, therefore 
+a computational domain with an extra gap of 0.03 millimeters is
+required in order to accommodate the unconstrained displacement of the
+particles in the left border of the bar. Naturally this problem arise
+when the mesh size is small enough that relative displacement of the
+particles are larger then the distance to the border, so grid crossing
+phenomena could appear even in those cases with infinitesimal
+displacements. In this case, an analytical solution is possible
+thought the characteristics method described in the appendix
+\ref{app:analytical_sol}. To measure the convergence of the solutions
+for the different time integration and approximation schemes the
+root-mean-square (RMS) error in the velocity field is computed. RMS
+error is defined as
 \begin{equation}
   \label{eq:RMS}
-  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)}
-\end{equation}
-
-\subsection{Error analysis MPM vs uGIMP vs MPM-\textit{max-ent}}
-\label{sec:study-error}
-
-\subsection{MPM versus OTM}
-\label{sec:mpm-versus-otm}
+  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
+\end{equation}
+where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
+numerical solutions evaluated in the final time step in the position
+of each particle. A first comparative between both time integration
+scheme is plotted in figure \ref{fig:Dyka-PCE-FE}. It demonstrates the
+superior performance of the PCE \textit{versus} the FE. In the PCE the
+spurious oscillations are quickly mitigated in the first time steps,
+and does not propagate the error in time in opposite to FE where the
+simulation becomes unstable after $6E^{5}$ seconds. Figure
+\ref{fig:Dyka-error-evol} also remarks the remarkable difference
+between both schemes. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_01}
+  }
+  \caption{Comparative of the PCE \textit{versus} the FE. In the
+    picture the velocity evolution at the point in the bar left side
+    is plotted.}
+  \label{fig:Dyka-PCE-FE}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Figure \eqref{fig:Dyka-LME-gamma} shows the sensibility of the LME
+approximation scheme to variations in the a-dimensional parameter
+$\beta$ that controls the value of the regularization parameter
+$\gamma$ depending of the mesh size. As we can see lower values of
+gamma exhibits a behaviour with a soft decay in some parts of the
+simulation due to the increase of nodes adopted to regularize the
+solutions. This capability could be useful in simulations where
+extremely noise oscillations could damage the solutions like memory
+materials. On the other hand larger values of the parameter $\beta$
+makes the solution tend to the linear FEM solution as the athermal
+limit is reached \cite{Arroyo2006}. Intermediate values of the
+regularization parameters give us a compromise between the both
+scenarios here described. An additional observation concerning the
+solution sensibility to regularization parameters occurs when mesh
+size decreases. For larger mesh size where the relative particle displacement
+is negligible in comparison with the cell size, the global behaviour
+is FEM-like, therefore larger values of $\gamma$ has offers better
+results. On the other hand, when mesh size is small enough to produce
+grid-crossing and mesh-free behaviour is required to ensures the
+convergence of the solution, tiny values of $\gamma$ has a better
+performance. Convergence plot in figure \eqref{fig:Dyka-error-evol}
+shows how the slope for the larger values of $\gamma$ decreases
+monotonically with the value of the mesh size, in contrast to larger
+values of it, whose suffers a punishment of the performance when significant
+movement of the particles occurs as far we reduce the mesh size.  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_LME_gamma_comparative}
+  }
+  \caption{Sensitive of LME approximants performance to changes in the
+    adimensional regularization parameter $\gamma = \beta/h^2$. To
+    illustrate it, the velocity evolution at the point in the bar left side
+    is plotted.}
+  \label{fig:Dyka-LME-gamma}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Figure \ref{fig:Dyka-uGIMP-LME} compares the performance of the
+uGIMP shape function \textit{versus} the LME approximation scheme with
+a adimensional regularization parameter $\gamma$ of 4.0. Although it
+does not shows remarkable differences, LME approximats exhibits a more
+robust behaviour than the uGIMP shape functions. Regarding this, notice
+the absence of uGIMP values for a mesh size of 0.3325 and 0.5
+millimeters. During these simulation the uGIMP suffered an unstable
+increase of the error so we decided to no include this nodes in the
+plot. A feasible explanation for this phenomena could be the presence
+of numerical cancellation which could produce gaps between
+voxels. Further research should be done in this direction for getting
+a better comprehension of this phenomena. In opposite, LME
+approximation does not suffers this phenomena either with irregular
+nodal layout.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_uGIMP_vs_LME_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-uGIMP-LME}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Finally, figure \ref{fig:Dyka-OTM-MPM}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-OTM-MPM}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{figure*}\sidecaption
+  \centering
+  \resizebox{0.7\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Error_evol}
+  }
+  \caption{Velocity evolution at the point in the Dyka bar left side,
+    convergence plots for FE and PCE. The plot is subdivided with
+    colours, the darker part of the diagram shows coincides when the
+    relative movement of the particles is large enough to produce the
+    grid crossing phenomena. The lightest part of the diagram
+    coincides when the relative movement of the particles in
+    negligible in comparison with the mesh size. And in the middle
+    region a transition behaviour take place.}
+  \label{fig:Dyka-error-evol}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Andersen block}
+\label{sec:andersen-block}
+
+In order to test the ability of this interpolation technique to deal
+with grid crossing instabilities we will simulate the vertical
+compression of a square block (10 by 10 meters) of soft soil sketched
+in figure~\ref{fig:block} and loaded using an incremental gravitation scheme.
+
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \input{Figures/Block.tex}}
+  \caption{Geometrical description of a soil block }.}
+  \label{fig:block}
+\end{figure}
+
+This test was taken from Andersen (2009)\cite{thesis_Andersen_2009}. The
+elastic parameters consider for this test are: 
+\begin{itemize} 
+\item  Initial density : $6\cdot 10^3\ kg/m^3$
+\item  Poisson ratio : $0$
+\item  Elastic modulus : $5\ MPa$
+\end{itemize}
+The gravity force is a apply as an external force according to the
+equations \eqref{eq:particle_body_forces},
+\eqref{eq:nodal_external_forces}. Using a total time period of T (20
+seconds) to apply the gravity, it is increased from 0 to 9.81$m/s$
+with a sinus function until T/2 and then maintained constant until T
+in order to arrive to a state of equilibrium, 
+\begin{equation}
+  \label{eq:gravity-load-block}
+ \mathbf{g}(t) = \left\{
+    \begin{array}{ll}
+      0.5 \mathbf{g} (\sin(\frac{2t \pi}{T} - \frac{\pi}{2})+1)  & \mbox{if } t \leq T/2 \\
+      \mathbf{g} & \mbox{if } t > T/2
+    \end{array}
+  \right.
+\end{equation}
+
+In order to get a stable solution, we will adopt a time step conducted
+by a Courant number of 0.1. On the other hand, the explicit predictor-corrector
+scheme is here employed looking forward getting better results. For the
+initial spatial discretization we will employ four particles per cell
+($\Delta x = 2\ m$). The initial setting of particles inside of the
+cell changes according to the approximation technique adopted. For the
+bi-linear shape functions (Q4) and the LME shape functions, the initial
+position corresponds to the location of the gauss-points in a standard
+quadratic finite element. For the uniform-GIMP (uGIMP) shape function
+the initial position of each particle is located in the center of each
+voxel, due to the fact that in the initial situation, the voxel domain
+should not overlap each others, Steffen {\it et al.}
+(2008)\cite{Steffen2008}. Figure~\ref{fig:vertical-displacement-block}
+shows the vertical displacement evolution of a point in the free
+surface of the block.
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
+  }
+  \caption{Comparative of the vertical displacement evolution in a
+    point located in the free surface employing different
+    interpolation schemes and numerical techniques.} 
+  \label{fig:vertical-displacement-block}
+\end{figure}
+
+As we can see the simulation using the Q4 interpolation technique
+turns out to be unstable and in the second 15 it fails. The uGIMP
+simulation is more stable than the one performed by the Q4. Despite
+this is still unstable and could trigger severe oscillations if we
+pretend to simulate non-linear materials. The LME simulation was
+performed using two kinds of shape functions, one with a low value of
+the dimensionless parameter, $\gamma = 0.8$, and other with a larger
+value of it, $\gamma = 3.0$. Notice that the results are both
+stable, but the larger values of $\gamma$ give us a very stable
+solution. This is due to the fact that with larger value of $\gamma$,
+the shape functions behaves in a similar way to the FEM, which performs
+very accurate in those cases with a reasonable mesh distorsion, and
+with a lower value it behaves in a similar way to the uGIMP. This
+behaviour was noticed previously by \cite{Arroyo2006}, were authors
+highlight how by adjusting the spatial variation of $\beta(\vect{x})$,
+it is possible to select regions of the domain of analysis which are
+treated by finite elements and regions that are treated in the style
+of meshfree methods, with seamless transitions between those regions.
+
+Figure~\ref{fig:Block-LME3} shows the evolution of the vertical stress
+during the loading process. The result is physically realistic as
+stress increments linearly from the top to the bottom of the specimen,
+and the value of the vertical stress in a material point located in
+the bottom of the specimen oscillates centered in $5.2 MPa$, which is
+the analytic value given by $\sigma_{yy} = \rho g h_y$.
+
+\begin{figure}
+  \centering
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[t = 0 seconds.]{
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_a_t0}
+    \label{fig:Block-LME3-PCE-t0}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \qquad
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[t = 5 seconds.]{
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_b_t025}
+    \label{fig:Block-LME3-PCE-t025}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \qquad
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \subfloat[t = 20 seconds]{
+    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_c_t1}
+    \label{fig:Block-LME3-PCE-t1}
+  }
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+  \caption{Vertical normal stress and position of material points
+    during the loading process for a soft soil ($E = 5\ MPa$, $\rho_0
+    = 6\cdot 10^3\ kg/m^3$). Numerical parameters considered for the
+    simulation are : Local \textit{max-ent} shape function $\gamma =3$
+    and explicit PC scheme with CFL 0.1.}
+  \label{fig:Block-LME3}
+\end{figure}
 
@@
 \label{sec:conclusions}
-
-Building upon the idea of anisotropic shape functions
-\cite{Arroyo2006}, \cite{Kochmann2019} introduced an enhanced version of the
-original local max-ent scheme, which uses an anisotropic support to
-deal with tensile inestability.
-
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
+We have developed a new time integration scheme for MPM, and
+proved how local \textit{max-ent} arise as a promising tool to
+overcome the grid-crossing error.
+
+adapt the value of $\beta$ to solve the equations fem-like of
+meshfree-like depending of how behaves the region
+
+This alternative technique overcome the constriction of the GIMP to
+regular mesh.
+
+The time integration here proposed mitigates the presence of wiggles
+and overshot
+
+future research :
+localization of the local max ent
+
+predictor-corrector for high dynamic problems like impact or
+collisions
+
+\begin{acknowledgements}
+If you'd like to thank anyone, place your comments here
+and remove the percent signs.
+\end{acknowledgements}
+
 %
@@
 \appendix
+
+\section{Explicit predictor-corrector algorithm}
+\label{app:explicit-predictor-algorithm}
+
+\begin{algorithm}
+  \floatname{algorithm}{Algorithm}
+  \renewcommand{\thealgorithm}{}
+  \caption{Explicit Predictor-Corrector scheme}
+  \begin{algorithmic}[1]
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
+    \STATE \textbf{Update mass matrix}:
+    \begin{equation*}
+      \tens{m}_{I} = N_{Ip}^{k}\ m_p,
+    \end{equation*}
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \STATE \textbf{Explicit Newmark Predictor}:\\
+    \begin{equation*}
+      \vec{v}_I^{pred} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
+    \end{equation*}
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \STATE \textbf{Impose essential boundary conditions}:\\
+    At the fixed boundary, set $\vec{v}_{I}^{pred} = 0$. 
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    % \STATE \textbf{Discard the previous nodal values}.
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \STATE \textbf{Deformation tensor increment calculation}.
+    \begin{align*}
+      &\dot{\tens{\varepsilon}_{p}}^{k+1} = \left[ \vec{v}_{I}^{pred} \otimes
+        \Grad{N_{Ip}^{k+1}} \right]^s \\
+      &\Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\ \dot{\tens{\varepsilon}_{p}}^{k+1}
+    \end{align*}
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \STATE \textbf{Update the density field}:
+    \begin{equation*}
+      \rho_p^{k+1} = \frac{\rho_p^k}{1 + \mathit{tra}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.
+    \end{equation*}
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \STATE \textbf{Balance of forces calculation}:\\
+    Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
+    \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
+    \eqref{eq:nodal_internal_forces} and
+    \eqref{eq:nodal_external_forces} in the time step $k+1$.
+    In the grid node $I$ is fixed in one of the spatial dimensions, set it to
+    zero to make the grid nodal acceleration zero in that direction.\\
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \STATE \textbf{Explicit Newmark Corrector}:
+    \begin{equation*}
+      \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}  
+    \end{equation*}
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    \STATE \textbf{Update particles lagrangian quantities}:
+    \begin{align*}
+      &\vec{a}_p^{k+1} = \vec{a}_p^n +
+        \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
+        \frac{N_{Ip}^k\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
+         N_{Ip}^k\ \vec{v}_{I}^{k} +
+        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}
+    \end{align*}
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \STATE \textbf{Reset nodal values}
+  \end{algorithmic}
+\end{algorithm}
+
 \section{The analytical solution of the 1D Dyka benchmark}
@@
 The boundary conditions are in both cases of radiation as there is not
-wave in-going from the exterior. So for the left side (fixed
+wave in-going from the exterior. So for the right side (fixed
 boundary) we get the following conditions:
 \begin{equation*}
-  &\Re^{I} = 0 \quad and \quad v_{x=0} = 0
+  \Re^{II} = 0 \quad and \quad v_{x=L} = 0
 \end{equation*}
-Therefore $\sigma_{x=0} = \sqrt{\rho E}\Re^{II}$. And in the left side
+Therefore $\sigma_{x=L} = -2\sqrt{\rho E}\ \Re^{I}$. And in the left side
 (free boundary) we get the following conditions:
 \begin{equation*}
-  &\Re^{II} = 0 \quad and \quad \sigma_{x=L} = 0
+  \Re^{I} = 0 \quad and \quad \sigma_{x=0} = 0
 \end{equation*}
-Therefore $v_{x=L} = \Re^{I}$. Finally, applying this conditions in
-the elastic bar sketched in \ref{fig:Dyka_Bar}, is possible to obtain
-the velocity history in the right side of the bar
-\ref{fig:vel_analytics_dyka} and the stress in the last quarter side of the Dyka
-bar \ref{fig:stress_analytics_dyka} as is demanded in \cite{Dyka1995}.
+Therefore $v_{x=0} = 2\Re^{II}$. Finally, applying this conditions in
+the elastic bar sketched in figure~\ref{fig:Dyka_Bar}, is possible to obtain
+the velocity history in the right side of the bar plotted in the figure~\ref{fig:vel_analytics_dyka} and the stress in the last quarter side of the Dyka
+bar plotted in the figure~\ref{fig:stress_analytics_dyka} as is demanded in \cite{Dyka1995}.
 
@@
 
-\message{ !name(main.tex) !offset(-1152) }
+\message{ !name(main.tex) !offset(-1619) }

### 2020-03-29 main.tex
Cambios 28-3-2020

@@
   presence of spurious oscillations with minimal dissipation in high
-  frequency problems. Other source of numerical noise in the MPM 
+  frequency problems. Other source of numerical noise in MPM 
   occurs when to material points cross computational grid
@@
     schemes} (LME) a robust substitute for the wide range of shape
-  function in the MPM. Local \textit{max-ent} approximation may be regarded as a
+  function in MPM. Local \textit{max-ent} approximation may be regarded as a
   \textit{thermalization} of Delaunay triangulation which resolves the
@@
 \label{intro}
-Since the proposal of the MPM by Sulsky {\it  et al.}
+Since the proposal of MPM by Sulsky {\it  et al.}
 (1994)~\cite{Sulsky1994} as a generalization to solids of the Fluid
@@
 or gaps when the material point mesh becomes irregular, which can
-introduce severe inaccuracies. This is similar to the difficulty
+introduce severe inaccuracies as noticed Steffen {\it et al.}
+(2008)\cite{Steffen2008}. This is similar to the difficulty
 encountered by the finite element methods due to element distortion.
@@
 particles. More recently, approximants derived from minimization has
-been introduced in to the MPM framework with the Conservative Taylor
+been introduced in to MPM framework with the Conservative Taylor
 Least Squares (CTLS) reconstruction proposed by Wobbes {\it et al.}
@@
     schemes} (LME) as a robust substitute for the wide range of shape
-  function in the MPM. First introduced by Arroyo \& Ortiz
+  function in MPM. First introduced by Arroyo \& Ortiz
 (2006)~\cite{Arroyo2006}, it belongs to the class of convex 
@@
 Optimal Transportation Meshfree (OTM) method. And more
-recently under the MPM framework by Wobbes {\it et
+recently under MPM framework by Wobbes {\it et
   al.}(2020)~\cite{Wobbes2020} but without exploring the benefits of
@@
 Solowski (2019)~\cite{Tran2019e} proposed a generalised-$\alpha$ scheme
-for the MPM with promising results but at the expense of increasing
+for MPM with promising results but at the expense of increasing
 the computational effort. In this paper a less time consuming and high
@@
 problem, the variational formulation and the Galerkin procedure. In Section \ref{sec:epc-algor-mpm} an explicit predictor-corrector
-time integration scheme for the MPM is proposed. Section
+time integration scheme for MPM is proposed. Section
 \ref{sec:local-max-ent} briefly reviews the local \textit{max-ent}
@@
 
-\section{Derivation of the MPM}
+\section{Derivation of MPM procedure}
 \label{sec:derivation-mpm}
@@
 procedure, and finally (iii) a Lagrangian advection of the
-particles. In consequence the MPM can be regarded as a
+particles. In consequence MPM can be regarded as a
 Lagrangian-Eulerian method where particles carries on all the physical
@@
 In MPM the continuum mechanics approach is considered. So on, let
-define a continuum domain $\varOmega$ occupied by an elastic body like the sketched in
-\ref{fig:Continuum-solid}, and $\partial \varOmega$ the boundaries of
-the domain defined by $\partial \varOmega = \Gamma_d \bigcup
-\Gamma_n$ and $\Gamma_d \cap  \Gamma_n = \emptyset$.
+define a continuum domain $\varOmega$ occupied by an elastic body like
+the sketched in the figure~\ref{fig:Continuum-solid}, and $\partial
+\varOmega$ the boundaries of the domain defined by $\partial \varOmega
+= \Gamma_d \bigcup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n = \emptyset$.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \resizebox{0.8\hsize}{!}{
+  \resizebox{0.5\hsize}{!}{
     \includegraphics[width=\textwidth]{Figures/Continuum-solid}}
@@
 In order to arrive to a finite set of equations, in contrast with the
-FEM, in the MPM a double discretization procedure is performed as we will
+FEM, in MPM a double discretization procedure is performed as we will
 describe here below. First, the continuum domain
@@
 particles. The material point $\vec{x}_p$ is defined at the centroid
-of each $\Omega_p$, figure \ref{fig:MPM-discretization}.
+of each $\Omega_p$, figure~\ref{fig:MPM-discretization}.
 Each material point is assigned with initial values of position,
@@
   \centering
-  \resizebox{0.8\hsize}{!}{
+  \resizebox{0.5\hsize}{!}{
     \includegraphics[width=\textwidth]{Figures/Mesh-particles-back}}
   \caption{Description of the spatial discretization for domain presented in the
-    figure \ref{fig:Continuum-solid}. Blue mesh represent the
+    figure~\ref{fig:Continuum-solid}. Blue mesh represent the
     background computational support, and the grid mesh conforms the
@@
 \end{equation}
-In the MPM literature, this equations
+In MPM literature, this equations
 (\ref{eq:particle_balance_forces3}) and (\ref{eq:Updated_Lagrangian}),
-are solved with an explicit forward Euler algorithm. The time integration scheme of the MPM has been described in detail by many researchers
+are solved with an explicit forward Euler algorithm. The time integration scheme of MPM has been described in detail by many researchers
 \cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and summarized
-in Figure \ref{fig:MPM_algorithm}.
+in figure~\ref{fig:MPM_algorithm}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \resizebox{0.8\hsize}{!}{
+  \resizebox{0.5\hsize}{!}{
     \includegraphics[width=\textwidth]{./Figures/MPM_scheme}
   }
-  \caption{Description of the MPM standard algorithm.}
+  \caption{Description of the three steps in MPM standard algorithm.}
   \label{fig:MPM_algorithm}
@@
 like \cite{Guilkey2003}, \cite{Tran2019e}, \cite{Charlton2017}. In the
-first publication on the MPM \cite{Sulsky1994}, the nodal acceleration
+first publication on MPM \cite{Sulsky1994}, the nodal acceleration
 was employed to update the particles as
@@
 Later Tran \& Solowski (2019)\cite{Tran2019e} presented a
-generalized-$\alpha$ scheme for the MPM inspired in the explicit time
+generalized-$\alpha$ scheme for MPM inspired in the explicit time
 integration algorithm proposed by Chung \& Hulbert
@@
 \end{equation*}
-As the MPM has a nodal stage, it is possible to apply this methods
-successfully in the MPM framework as was proved by
+As MPM has a nodal stage, it is possible to apply this methods
+successfully in MPM framework as was proved by
 \cite{Tran2019e}. Taking the predictor definition from and calculating
@@
 
-To accommodate this step to the MPM framework, it is necessary to get
+To accommodate this step to MPM framework, it is necessary to get
 the nodal values of the velocity and acceleration throughout a variational
@@
 procedures described by Zienkiewicz \& Zhu \cite{ZZ1992_I} (\textit{ZZ})
-in the context of FEM. In the MPM Gauss quadrature is not employed as
+in the context of FEM. In MPM Gauss quadrature is not employed as
 integrals are computed following the Riemann integral definition,
@@
  Therefore, to get a analogous expression for
- \eqref{eq:Predictor-velocity-I} in the context of the MPM, the
+ \eqref{eq:Predictor-velocity-I} in the context of MPM, the
  procedure described in the equation \eqref{eq:Variational-recovery}
@@
 over a standard forward Euler. It is summarized in shape of
-pseudo-algorithm \ref{app:explicit-predictor-algorithm}.
-
-\section{Local max-ent approximants}
-\label{sec:local-max-ent}
-The popularity of the MPM has increase notoriously during
-the recent years due to its ability to deal with large strain problems
-without mesh distorsion issues inherent to mesh based methods like
-FEM, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations
-made with the original MPM, there are numerical noises when particles
-crossing the cell boundaries. Local maximum-entropy (or
-local \textit{max-ent}) shape function first introduced by Arroyo \&
-Ortiz (2006)\cite{Arroyo2006} has been recently tested under the MPM framework
-by Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
-simulations performed with the \textit{max-ent} basis functions show
-considerably more accurate stress approximations for MPM. Although, in
-\cite{Wobbes2020} authors does not deep in how the regularization
-parameter $\beta$ affects to the accuracy and stability of the solution.
-
-The basic idea of the shape functions based on such
-an estimate is to interpret the shape function $N_I(\vec{x})$ as the
-probability of $\vec{x}$ to obtain the value $\vec{x}_I$,  $I=1,
-\dots, n$. Here $n$ is the number of nodes in the domain.
-This approximation scheme represents a optimal compromise, in the sense of
-Pareto, between the \textit{unbiased statistical inference} based on
-the nodal data which leads to the principle of \textit{maximum-entropy}
-stated by Jaynes \cite{Jaynes1957}, and the definition of local shape
-functions of \textit{least width} the least biased shape functions.
-
-Taking the definition of entropy as a measure of how uncertainty a
-random variable is averaged on all its possible outcomes. And adopting
-the Shannon's entropy as the starting point:
-\begin{equation}
-  \label{eq:Shannon-entropy}
-  H(p_1(\vec{x}),\ldots,p_n(\vec{x})) = -\sum^{N_n}_{I=1}{p_I(\vec{x})\log p_I }
-\end{equation}
-where $p_I(\vec{x})$ is the probability, equivalent to the mentioned
-shape function $N_I(\vec{x})$,  satisfying both the zeroth and
-first-order consistency. The least-biased approximation scheme is
-given by
-\begin{align*}
-  \label{eq:least-biased-approximation-scheme}
-  \text{(LME)} \hspace{0.15cm} &\text{Maximize} \hspace{0.15cm} H(p) =
-  -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I }\\
-  &\text{subject to}\
-  \begin{cases}
-    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
-  \end{cases}
-\end{align*}
-The local max-ent approximation schemes (LME) as a Pareto set,
-defined by \cite{Arroyo2006} is as follows
-\begin{align*}
-  \label{eq:LME-scheme-pareto-set}
-  \text{(LME)}_{\beta} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
-  \vec{x} \hspace{0.15cm} \text{minimise} \hspace{0.15cm} f_{\beta}(\vec{x}, p) = \beta H(\vec{x},p) - H(p) \\
-  &\text{subject to}\
-  \begin{cases}
-    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
-  \end{cases}
-\end{align*}
-for $\beta \in (0,\infty)$ is Pareto optimal. The unique solution of
-the local max-ent problem (LME)$_\beta$ is: 
-\begin{equation}
-  \label{eq:LME-p}
-p(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
-    \vec{\lambda} \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
-\end{equation}
-where
-\begin{equation}
-  \label{eq:LME-Z}
-Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \; |\vec{x}-\vec{x}_I|^2 + \vec{\lambda} \cdot (\vec{x}-\vec{x}_I)  \right]}
-\end{equation}
-being $\vec{\lambda}^*(\vec{x})$ the unique minimiser  for $\log
-Z(\vec{x}, \vec{\lambda})$. In order to obtain the first derivatives of the shape function, it is also necessary to compute~$\nabla p^*_I$ 
-\begin{equation}
-  \label{eq:LME-grad-p}
-\nabla p^*_I=p^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} p^*_J \, \nabla f^*_J\right)
-\end{equation}
-where
-\begin{equation}
-  \label{eq:LME-f}
-f^*_I(\vec{x},  \vec{\lambda},\beta)=-\beta \, |\vec{x}-\vec{x}_I|^2 + \vec{\lambda}   \,  (\vec{x}-\vec{x}_I)
-\end{equation}
-Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression:
-\begin{eqnarray}
-\nabla p^*_I &=& -p^*_I \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I) \label{eq26} 
-\end{eqnarray}
-%&&\mbox{
-where \tens{J} is the Hessian matrix, defined by:
-%} \nonumber \\&& \nonumber \\
-\begin{eqnarray}
-\tens{J}(\vec{x},  \vec{\lambda},\beta) &=& \frac{\partial \vec{r}}{\partial  \vec{\lambda}} \label{eq27} \\ 
-%&& \nonumber \\
-\vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \partial_{\vec{\lambda}}{\log{ Z( \vec{x},\vec{\lambda}})} 
-%\nonumber \\ &=&
-  =\sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I) \label{eq28} 
-\end{eqnarray}
-Note that, the objective of the above procedure is to find the
-$\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. The
-traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27})
-to calculate small increments of $\partial\vec{\lambda}$ in a
-Newton-Raphson approach. Similar to alternative non-polynomial meshfree basis functions, the
-LME approximation scheme requires more than $d+1$ nodes to determine
-the values of the shape functions as well as their derivatives at any
-point in the convex hull of the nodal set, where $d$ is the dimension
-of the problem. The support size of LME shape functions may be
-controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
-\cite{Arroyo2006} (e.g. two dimensional example shown in figure. \ref{fig:LME_MPM}).
- Since  $p_I$  is defined in the entire domain, in practice, the
-function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
-10$^{-6}$, for example,  would ensure a reasonable range of
-neighbours, see \cite{Arroyo2006} for details. This tolerance defines
-the limit values of the influence radius and is used thereafter to
-find the neighbour nodes of a given integration point. Regarding this
-aspect, an crucial consideration for the implementation of the LME
-shape functions in the MPM is exposed. To avoid the transference of
-particle information to those nodes fare apart from the particle
-domain $\Omega_p$, a especial treatment of the neighbour nodes for
-those particles close to the boundary is required. Here we employ an
-algorithm inspired in the one proposed by Kumar {\it et al.}
-(2019)\cite{Kochmann2019} to deal with interfaces between two
-materials in the OTM framework. It consists in select only those nodes
-
-employed to compute the solution are those whose
-position are inside 
-In opposite to the OTM where
-this approximation technique has been widely.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{0.7\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Particle-discretization}
-  }
-  \caption{This tolerance defines the limit values of the influence
-    radius and is used thereafter to find the neighbour nodes of a given integration point.} 
-  \label{fig:Particle-discretization}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Due to the FE-compatibility, the LME shape function is degenerated to
-linear finite element shape function if $d+1$ neighbouring nodes are
-chosen as the support. Furthermore, with a conveniently adopted
-\textit{regularization} parameter it is possible to get a GIMP-like
-shape function. A proof of this statements is observed in \ref{fig:LME_MPM}.  
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-  \centering
-  \subfigure[Q4]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun}\\
-      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dx}\\
-      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dy}
-    \end{tabular}  
-  }
-  \subfigure[$\text{LME}_{17}$]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dx}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dy}
-    \end{tabular}
-  }
-  \subfigure[uGIMP]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun}\\
-      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dx}\\
-      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dy}
-    \end{tabular}
-  }
-  \subfigure[$\text{LME}_{10}$]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dx}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dy}    
-    \end{tabular}
-  }
-  \subfigure[$\text{LME}_{5}$]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dx}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dy}
-    \end{tabular}
-  }
-  \caption{Comparative of linear piecewise shape functions (Q4) and
-    uniform GIMP shape functions (uGIMP) \textit{versus} Local max-ent
-    shape functions for a two-dimensional arrangement of nodes, and
-    spatial derivatives for several values of $\gamma = \beta/h^2$.}
-  \label{fig:LME_MPM}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
-influence area of the shape function is controlled by the Euclidean
-norm, therefore the search area is geometrically a circle in 2D, or a
-sphere in 3D. Building upon the idea of anisotropic shape functions,
-\cite{Kochmann2019} introduced an enhanced version of the original
-local max-ent scheme, which uses an anisotropic support to deal with
-tensile inestability. Nonetheless this is out of the scope of the
-present document but will be incorporated in future research.
-
-\section{Application to linear elasticity dynamic problems.}
-\label{sec:Application-linear-elasticity-dynamic-problems}
-
-This section is devoted to test the ability of both predictor-corrector
-time integration scheme and the local \textit{max-ent} approximants to
-overcome spurious oscillations due to the grid crossing and high
-frequency loads under the context of the MPM.
-
-\subsection{Dyka bar}
-\label{sec:dyka-bar}
-
-High frequency , the benchmark proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995} is considered to illustrate the
-capacity of the proposed time integration algorithm to avoid velocity
-fields instabilities.
-
-In the one-dimensional bar sketched in the figure \ref{fig:Dyka_Bar},
-the left end of the bar is fixed and the right and an initial velocity
-$v_0 = 5\ m/s$ is given to the last quarter of it in the x positive
-direction. The length of it is 0.1333 meters with an unit section.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \input{Figures/Dyka_bar.tex}}
-  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
-  \label{fig:Dyka_Bar}
-\end{figure}
-
-The elastic parameters consider for this test are:
-\begin{itemize} 
-\item  Density : $7833\ kg/m3$
-\item  Poisson ratio : $0$
-\item  Elastic modulus : $200 \cdot 10^9\ Pa$
-\end{itemize}
-
-The boundary conditions are:
-\begin{equation}
-  \label{eq:3}
-  \sigma \rvert_{x=L} = 0 \quad , \quad v \rvert_{x=0} = 0
-\end{equation}
-
-The total simulation time is 0.0002 seconds, a direct consequence of
-that is we let the elastic wave generated travel thorough the bar
-(from A to C and back to A) at least four times. For the spatial
-discretization we will set a mesh size of 3.3325 millimeters. The
-initial mesh will be composed by a single particle in the center of
-the element.
-
-Regarding this, here we give one consideration to properly modellize
-this benchmark under the MPM framework. Notice that the free border of
-the bar has a horizontal displacement of 0.033 millimeters, therefore
-a computational domain with an extra gap of 0.033 millimeters is
-required in order to accommodate the unconstrained displacement of the
-particles in the left border of the bar. Here below the time step is
-controlled by the courant number, in this case, we adopt a middle
-value of it (CFL=0.5) as a compromise between stability and numerical
-accuracy.
-
-The analytical solution in terms of velocity
-\ref{fig:vel_analytics_dyka}, and stress
-\ref{fig:stress_analytics_dyka} can be found in the appendix
-\ref{app:analytical_sol} given by the Method of characteristics.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_01}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-PCE-FE}
-\end{figure}
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_LME_gamma_comparative}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-LME-gamma}
-\end{figure}
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_uGIMP_vs_LME_Dyka}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-uGIMP-LME}
-\end{figure}
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-OTM-MPM}
-\end{figure}
-
-For the convergence analysis, the root-mean-square (RMS) error in the
-velocity field is computed. RMS error is defined as follows
-
-\begin{equation}
-  \label{eq:RMS}
-  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
-\end{equation}
-
-where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
-numerical solutions evaluated in the final time step in the position
-of each particle.
-
-\begin{figure*}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Error_evol}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-error-evol}
-\end{figure*}
-
-\subsection{Andersen block}
-\label{sec:andersen-block}
-
-In order to test the ability of this interpolation technique to deal
-with grid crossing instabilities we will simulate the vertical
-compression of a square block (10 by 10 meters) of soft soil sketched
-in figure \ref{fig:block} and loaded using an incremental gravitation scheme.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \input{Figures/Block.tex}}
-  \caption{Geometrical description of a soil block }.}
-  \label{fig:block}
-\end{figure}
-
-This test was taken from Andersen (2009)\cite{thesis_Andersen_2009}. The
-elastic parameters consider for this test are: 
-\begin{itemize} 
-\item  Initial density : $6\cdot 10^3\ kg/m^3$
-\item  Poisson ratio : $0$
-\item  Elastic modulus : $5\ MPa$
-\end{itemize}
-The gravity force is a apply as an external force according to the
-equations \eqref{eq:particle_body_forces},
-\eqref{eq:nodal_external_forces}. Using a total time period of T (20
-seconds) to apply the gravity, it is increased from 0 to 9.81$m/s$
-with a sinus function until T/2 and then maintained constant until T
-in order to arrive to a state of equilibrium, 
-\begin{equation}
-  \label{eq:gravity-load-block}
- \mathbf{g}(t) = \left\{
-    \begin{array}{ll}
-      0.5 \mathbf{g} (\sin(\frac{2t \pi}{T} - \frac{\pi}{2})+1)  & \mbox{if } t \leq T/2 \\
-      \mathbf{g} & \mbox{if } t > T/2
-    \end{array}
-  \right.
-\end{equation}
-
-In order to get a stable solution, we will adopt a time step conducted
-by a Courant number of 0.1. On the other hand, the explicit predictor-corrector
-scheme is here employed looking forward getting better results. For the
-initial spatial discretization we will employ four particles per cell
-($\Delta x = 2\ m$). The initial setting of particles inside of the
-cell changes according to the interpolation technique adopted. For the
-bi-linear shape functions (Q4) and the LME shape functions, the initial
-position corresponds to the location of the gauss-points in a standard
-quadratic finite element. For the uniform-GIMP (uGIMP) shape function
-the initial position of each particle is located in the center of each
-voxel, due to the fact that in the initial situation, the voxel domain
-should not overlap each others, Steffen {\it et al.}
-(2008)\cite{Steffen2008}. Figure \ref{fig:vertical-displacement-block}
-shows the vertical displacement evolution of a point in the free
-surface of the block.
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
-  }
-  \caption{Comparative of the vertical displacement evolution in a
-    point located in the free surface employing different
-    interpolation schemes and numerical techniques.} 
-  \label{fig:vertical-displacement-block}
-\end{figure}
-
-As we can see the simulation using the Q4 interpolation technique
-turns out to be unstable and in the second 15 it fails. The uGIMP
-simulation is more stable than the one performed by the Q4. Despite
-this is still unstable and could trigger severe oscillations if we
-pretend to simulate non-linear materials. The LME simulation was
-performed using two kinds of shape functions, one with a low value of
-the dimensionless parameter, $\gamma = 0.8$, and other with a larger
-value of it, $\gamma = 3.0$. Notice that the results are both
-stable, but the larger values of $\gamma$ give us a very stable
-solution. This is due to the fact that with larger value of $\gamma$,
-the shape functions behaves in a similar way to the FEM, which performs
-very accurate in those cases with a reasonable mesh distorsion, and
-with a lower value it behaves in a similar way to the uGIMP. This
-behaviour was noticed previously by \cite{Arroyo2006}, were authors
-highlight how by adjusting the spatial variation of $\beta(\vect{x})$,
-it is possible to select regions of the domain of analysis which are
-treated by finite elements and regions that are treated in the style
-of meshfree methods, with seamless transitions between those regions.
-
-Figure \ref{fig:Block-LME3} shows the evolution of the vertical stress
-during the loading process. The result is physically realistic as
-stress increments linearly from the top to the bottom of the specimen,
-and the value of the vertical stress in a material point located in
-the bottom of the specimen oscillates centered in $5.2 MPa$, which is
-the analytic value given by $\sigma_{yy} = \rho g h_y$.
-
-\begin{figure}
-  \centering
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[t = 0 seconds.]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_a_t0}
-    \label{fig:Block-LME3-PCE-t0}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[t = 5 seconds.]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_b_t025}
-    \label{fig:Block-LME3-PCE-t025}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[t = 20 seconds]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_c_t1}
-    \label{fig:Block-LME3-PCE-t1}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \caption{Vertical normal stress and position of material points
-    during the loading process for a soft soil ($E = 5\ MPa$, $\rho_0
-    = 6\cdot 10^3\ kg/m^3$). Numerical parameters considered for the
-    simulation are : Local \textit{max-ent} shape function $\gamma =3$
-    and explicit PC scheme with CFL 0.1.}
-  \label{fig:Block-LME3}
-\end{figure}
-
-% \subsection{MPM versus OTM}
-% \label{sec:mpm-versus-otm}
-
-% MPM \cite{Sulsky1994} and OTM
-% models to avoid tensile instabilities. Here we employ our in-house
-% codes for both MPM and OTM simulations.
-
-% The results are provided for the explicit predictor-corrector version
-% of the MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM
-% algorithms. For MPM, piecewise-linear, uGIMP and \textit{max-ent}
-% basis functions are employed. The OTM algorithm is used only with
-% \textit{max-ent} shape functions.
-
-% \begin{figure*}\sidecaption
-%   \centering
-%   \resizebox{0.7\hsize}{!}{
-%     \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
-%   }
-%   \caption{Velocity evolution at the point in the bar left side.}
-%   \label{fig:Dyka-MPM-uGIMP-LME}
-% \end{figure*}
-
-\section{Conclusions}
-\label{sec:conclusions}
-We have developed a new time integration scheme for the MPM, and
-proved how local \textit{max-ent} arise as a promising tool to
-overcome the grid-crossing error.
-
-adapt the value of $\beta$ to solve the equations fem-like of
-meshfree-like depending of how behaves the region
-
-This alternative technique overcome the constriction of the GIMP to
-regular mesh.
-
-The time integration here proposed mitigates the presence of wiggles
-and overshot
-
-future research :
-localization of the local max ent
-
-predictor-corrector for high dynamic problems like impact or
-collisions
-
-\begin{acknowledgements}
-If you'd like to thank anyone, place your comments here
-and remove the percent signs.
-\end{acknowledgements}
-
-%
-\section*{Conflict of interest}
-%
-The authors declare that they have no conflict of interest.
-
-\appendix
-
-\section{Explicit predictor-corrector algorithm}
-\label{app:explicit-predictor-algorithm}
+pseudo-algorithm.
 
@@
 
+\section{Local max-ent approximants}
+\label{sec:local-max-ent}
+The popularity of MPM has increase notoriously during
+the recent years due to its ability to deal with large strain problems
+without mesh distorsion issues inherent to mesh based methods like
+FEM, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations
+made with the original MPM, there are numerical noises when particles
+crossing the cell boundaries. Local maximum-entropy (or
+local \textit{max-ent}) shape function first introduced by Arroyo \&
+Ortiz (2006)\cite{Arroyo2006} has been recently tested under MPM framework
+by Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
+simulations performed with the \textit{max-ent} basis functions show
+considerably more accurate stress approximations for MPM. Although, in
+\cite{Wobbes2020} authors does not deep in how the regularization
+parameter $\beta$ affects to the accuracy and stability of the solution.
+
+The basic idea of the shape functions based on such
+an estimate is to interpret the shape function $N_I(\vec{x})$ as the
+probability of $\vec{x}$ to obtain the value $\vec{x}_I$,  $I=1,
+\dots, n$. Here $n$ is the number of nodes in the domain.
+This approximation scheme represents a optimal compromise, in the sense of
+Pareto, between the \textit{unbiased statistical inference} based on
+the nodal data which leads to the principle of \textit{maximum-entropy}
+stated by Jaynes \cite{Jaynes1957}, and the definition of local shape
+functions of \textit{least width} the least biased shape functions.
+
+Taking the definition of entropy as a measure of how uncertainty a
+random variable is averaged on all its possible outcomes. And adopting
+the Shannon's entropy as the starting point:
+\begin{equation}
+  \label{eq:Shannon-entropy}
+  H(p_1(\vec{x}),\ldots,p_n(\vec{x})) = -\sum^{N_n}_{I=1}{p_I(\vec{x})\log p_I }
+\end{equation}
+where $p_I(\vec{x})$ is the probability, equivalent to the mentioned
+shape function $N_I(\vec{x})$,  satisfying both the zeroth and
+first-order consistency. The least-biased approximation scheme is
+given by
+\begin{align*}
+  \label{eq:least-biased-approximation-scheme}
+  \text{(LME)} \hspace{0.15cm} &\text{Maximize} \hspace{0.15cm} H(p) =
+  -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I }\\
+  &\text{subject to}\
+  \begin{cases}
+    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
+  \end{cases}
+\end{align*}
+The local max-ent approximation schemes (LME) as a Pareto set,
+defined by \cite{Arroyo2006} is as follows
+\begin{align*}
+  \label{eq:LME-scheme-pareto-set}
+  \text{(LME)}_{\beta} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
+  \vec{x} \hspace{0.15cm} \text{minimise} \hspace{0.15cm} f_{\beta}(\vec{x}, p) = \beta H(\vec{x},p) - H(p) \\
+  &\text{subject to}\
+  \begin{cases}
+    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
+  \end{cases}
+\end{align*}
+for $\beta \in (0,\infty)$ is Pareto optimal. The unique solution of
+the local max-ent problem (LME)$_\beta$ is: 
+\begin{equation}
+  \label{eq:LME-p}
+p(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
+    \vec{\lambda} \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
+\end{equation}
+where
+\begin{equation}
+  \label{eq:LME-Z}
+Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \; |\vec{x}-\vec{x}_I|^2 + \vec{\lambda} \cdot (\vec{x}-\vec{x}_I)  \right]}
+\end{equation}
+being $\vec{\lambda}^*(\vec{x})$ the unique minimiser  for $\log
+Z(\vec{x}, \vec{\lambda})$. In order to obtain the first derivatives of the shape function, it is also necessary to compute~$\nabla p^*_I$ 
+\begin{equation}
+  \label{eq:LME-grad-p}
+\nabla p^*_I=p^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} p^*_J \, \nabla f^*_J\right)
+\end{equation}
+where
+\begin{equation}
+  \label{eq:LME-f}
+f^*_I(\vec{x},  \vec{\lambda},\beta)=-\beta \, |\vec{x}-\vec{x}_I|^2 + \vec{\lambda}   \,  (\vec{x}-\vec{x}_I)
+\end{equation}
+Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression:
+\begin{eqnarray}
+\nabla p^*_I &=& -p^*_I \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I) \label{eq26} 
+\end{eqnarray}
+%&&\mbox{
+where \tens{J} is the Hessian matrix, defined by:
+%} \nonumber \\&& \nonumber \\
+\begin{eqnarray}
+\tens{J}(\vec{x},  \vec{\lambda},\beta) &=& \frac{\partial \vec{r}}{\partial  \vec{\lambda}} \label{eq27} \\ 
+%&& \nonumber \\
+\vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \partial_{\vec{\lambda}}{\log{ Z( \vec{x},\vec{\lambda}})} 
+%\nonumber \\ &=&
+  =\sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I) \label{eq28} 
+\end{eqnarray}
+Note that, the objective of the above procedure is to find the
+$\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. The
+traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27})
+to calculate small increments of $\partial\vec{\lambda}$ in a
+Newton-Raphson approach. Similar to alternative non-polynomial meshfree basis functions, the
+LME approximation scheme requires more than $d+1$ nodes to determine
+the values of the shape functions as well as their derivatives at any
+point in the convex hull of the nodal set, where $d$ is the dimension
+of the problem. The support size of LME shape functions may be
+controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
+\cite{Arroyo2006} (e.g. two dimensional example shown in figure~\ref{fig:LME_MPM}).
+ Since  $p_I$  is defined in the entire domain, in practice, the
+function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
+10$^{-6}$, for example,  would ensure a reasonable range of
+neighbours, see \cite{Arroyo2006} for details. This tolerance defines
+the limit values of the influence radius and is used thereafter to
+find the neighbour nodes of a given integration point. Regarding this
+aspect, an crucial consideration for the implementation of the LME
+shape functions in MPM is exposed. To avoid the transference of
+particle information to those nodes fare apart from the particle
+domain $\Omega_p$, a especial treatment of the neighbour nodes for
+those particles close to the boundary is required. It consists in
+select only those nodes which position $\vect{x}_I$ lies inside of the
+domain $\Omega$. This can be performed by employing the nodal
+connectivity of the background mesh. And activating for computing only
+those nodes whose element has a particle inside of it as we can see in
+figure~\ref{fig:Particle-discretization}. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.5\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Particle-discretization}
+  }
+  \caption{This tolerance defines the limit values of the influence
+    radius and is used thereafter to find the neighbour nodes of a
+    given integration point. The picture also shows the neighbourhood
+    criterion to select those node inside of $\Omega$.} 
+  \label{fig:Particle-discretization}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Due to the FE-compatibility, the LME shape function is degenerated to
+linear finite element shape function if $d+1$ neighbouring nodes are
+chosen as the support. Furthermore, with a conveniently adopted
+\textit{regularization} parameter it is possible to get a GIMP-like
+shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}.  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+  \centering
+  \subfigure[Q4]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.14\textwidth]{Figures/MPM_Shape_Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures/MPM_Shape_Fun_dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures/MPM_Shape_Fun_dy}
+    \end{tabular}  
+  }
+  \subfigure[$\text{LME}_{17}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun_dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \subfigure[uGIMP]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.14\textwidth]{Figures/GIMP_Shape_Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures/GIMP_Shape_Fun_dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures/GIMP_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \subfigure[$\text{LME}_{10}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun_dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun_dy}    
+    \end{tabular}
+  }
+  \subfigure[$\text{LME}_{5}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.14\textwidth]{Figures/LME_5_0_Shape_Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_5_0_Shape_Fun_dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_5_0_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \caption{Comparative of linear piecewise shape functions (Q4) and
+    uniform GIMP shape functions (uGIMP) \textit{versus} Local max-ent
+    shape functions for a two-dimensional arrangement of nodes, and
+    spatial derivatives for several values of $\gamma = \beta/h^2$.}
+  \label{fig:LME_MPM}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
+influence area of the shape function is controlled by the Euclidean
+norm, therefore the search area is geometrically a circle in 2D, or a
+sphere in 3D. Building upon the idea of anisotropic shape functions,
+\cite{Kochmann2019} introduced an enhanced version of the original
+local max-ent scheme, which uses an anisotropic support to deal with
+tensile inestability. Nonetheless this is out of the scope of the
+present document but will be incorporated in future research.
+
+\section{Application to linear elasticity dynamic problems.}
+\label{sec:Application-linear-elasticity-dynamic-problems}
+
+This section is devoted to test the ability of both predictor-corrector
+time integration scheme and the local \textit{max-ent} approximants to
+overcome spurious oscillations due to the grid crossing and high
+frequency loads under the context of MPM Two different test has
+been adopted for this purpose, the benchmark proposed by Dyka \& Ingel
+(1995)\cite{Dyka1995} and the test proposed in the PhD thesis of
+Andersen (2009)\cite{thesis_Andersen_2009}. In all calculations we confine out attention to
+uniformly distribute node and particle sets. The accuracy of the PCE
+scheme is compared to the standard FE. In addition \textit{max-ent} solutions
+are compared with those provided by uGIMP and Q4 shape functions, also
+we compare MPM performance with OTM and FEM. All simulations were
+performed with in-hose software.
+
+\subsection{Dyka bar}
+\label{sec:dyka-bar}
+
+This benchmark was proposed due to its ability to shows the capability
+of the proposed time integration algorithm to avoid velocity
+fields instabilities. It consists in a one-dimensional bar with a
+length of 0.1333 meters, sketched in the
+figure~\ref{fig:Dyka_Bar}. The boundary conditions are in the right
+border displacement are constrained ($\vect{v} \rvert_{x=L} = 0$) and
+in the left displacement are let free ($\tens{\sigma} \rvert_{x=0} =
+0$). And a initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
+last quarter of it. Finally, the elastic parameters consider for this test are:
+\begin{itemize} 
+\item  Density : $7833\ kg/m3$
+\item  Poisson ratio : $0$
+\item  Elastic modulus : $200 \cdot 10^9\ Pa$
+\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \input{Figures/Dyka_bar.tex}}
+  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
+  \label{fig:Dyka_Bar}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this case a duration of 0.0001 seconds for the simulation is
+consider. Therefore, the elastic wave generated travel thorough the bar
+(from A to C and back to A) at least two times. For the spatial
+discretization we propose a set a seven nodal mesh sizes (0.1, 0.3325, 0.5,
+1.0, 3.3325, 6.665, 10.0) in millimeters. For each element a number of
+four particles was selected. In the initial layout, particles are
+occupying the exact quadrature points of a linear quadrilateral. With
+the exception of the uGIMP simulation where gaps or overlap between
+voxels of each particle are not allowed. In those cases, each particles
+occupy the center of each cell quarter. For all simulations, time step
+is controlled by a Courant-Friedrichs-Levy condition of 0.1, were the adopted
+celerity is computed as,
+\begin{equation}
+  \label{eq:Cel}
+  Cel = \max\{\max_{p \in \Omega_p}\{ \vect{v}_p \} , \max_{p \in \Omega_p}\{ \sqrt{\frac{E_p}{\rho_p}} \} \}
+\end{equation}
+A important consideration regarding modellization concerns to the
+background mesh. Notice that free border of the bar has a maximum
+horizontal displacement of 0.03 millimeters, therefore 
+a computational domain with an extra gap of 0.03 millimeters is
+required in order to accommodate the unconstrained displacement of the
+particles in the left border of the bar. Naturally this problem arise
+when the mesh size is small enough that relative displacement of the
+particles are larger then the distance to the border, so grid crossing
+phenomena could appear even in those cases with infinitesimal
+displacements.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{figure*}\sidecaption
+  \centering
+  \resizebox{0.7\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Error_evol}
+  }
+  \caption{Velocity evolution at the point in the Dyka bar left side,
+    convergence plots for FE and PCE. The plot is subdivided with
+    colours, the darker part of the diagram shows coincides when the
+    relative movement of the particles is large enough to produce the
+    grid crossing phenomena. The lightest part of the diagram
+    coincides when the relative movement of the particles in
+    negligible in comparison with the mesh size. And in the middle
+    region a transition behaviour take place.}
+  \label{fig:Dyka-error-evol}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this case, an analytical solution is possible
+thought the characteristics method described in the appendix
+\ref{app:analytical_sol}. To measure the convergence of the solutions
+for the different time integration and approximation schemes the
+root-mean-square (RMS) error in the velocity field is computed. RMS
+error is defined as
+\begin{equation}
+  \label{eq:RMS}
+  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
+\end{equation}
+where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
+numerical solutions evaluated in the final time step in the position
+of each particle. A first comparative between both time integration
+scheme is plotted in figure \ref{fig:Dyka-PCE-FE}. It demonstrates the
+superior performance of the PCE \textit{versus} the FE. In the PCE the
+spurious oscillations are quickly mitigated in the first time steps,
+and does not propagate the error in time in opposite to FE where the
+simulation becomes unstable after $6E^{5}$ seconds. Figure
+\ref{fig:Dyka-error-evol} also remarks the remarkable difference
+between both schemes. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.9\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_01}
+  }
+  \caption{Comparative of the PCE \textit{versus} the FE. In the
+    picture the velocity evolution at the point in the bar left side
+    is plotted.}
+  \label{fig:Dyka-PCE-FE}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Figure \eqref{fig:Dyka-LME-gamma} shows the sensibility of the LME
+approximation scheme to variations in the a-dimensional parameter
+$\beta$ that controls the value of the regularization parameter
+$\gamma$ depending of the mesh size. As we can see lower values of
+gamma exhibits a behaviour with a soft decay in some parts of the
+simulation due to the increase of nodes adopted to regularize the
+solutions. This capability could be useful in simulations where
+extremely noise oscillations could damage the solutions like memory
+materials. On the other hand larger values of the parameter $\beta$
+makes the solution tend to the linear FEM solution as the athermal
+limit is reached \cite{Arroyo2006}. Intermediate values of the
+regularization parameters give us a compromise between the both
+scenarios here described. An additional observation concerning the
+solution sensibility to regularization parameters occurs when mesh
+size decreases. For larger mesh size where the relative particle displacement
+is negligible in comparison with the cell size, the global behaviour
+is FEM-like, therefore larger values of $\gamma$ has offers better
+results. On the other hand, when mesh size is small enough to produce
+grid-crossing and mesh-free behaviour is required to ensures the
+convergence of the solution, tiny values of $\gamma$ has a better
+performance. Convergence plot in figure \eqref{fig:Dyka-error-evol}
+shows how the slope for the larger values of $\gamma$ decreases
+monotonically with the value of the mesh size, in contrast to larger
+values of it, whose suffers a punishment of the performance when significant
+movement of the particles occurs as far we reduce the mesh size.  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.9\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_LME_gamma_comparative}
+  }
+  \caption{Sensitive of LME approximants performance to changes in the
+    adimensional regularization parameter $\gamma = \beta/h^2$. To
+    illustrate it, the velocity evolution at the point in the bar left side
+    is plotted.}
+  \label{fig:Dyka-LME-gamma}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Figure \ref{fig:Dyka-uGIMP-LME} compares the performance of the
+uGIMP~\cite{Bardenhagen2004} shape function \textit{versus} the LME approximation scheme with
+a adimensional regularization parameter $\gamma$ of 4.0. Although it
+does not shows remarkable differences, LME approximats exhibits a more
+robust behaviour than the uGIMP shape functions. Regarding this, notice
+the absence of uGIMP values for a mesh size of 0.3325 and 0.5
+millimeters. During these simulation the uGIMP suffered an unstable
+increase of the error so we decided to no include this nodes in the
+plot. A feasible explanation for this phenomena could be the presence
+of numerical cancellation which could produce gaps between
+voxels. Further research should be done in this direction for getting
+a better comprehension of this phenomena. In opposite, LME
+approximation does not suffers this phenomena either with irregular
+nodal layout.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.9\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_uGIMP_vs_LME_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-uGIMP-LME}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Finally, figure \ref{fig:Dyka-OTM-MPM} compares the solution obtained
+with OTM~\cite{Li2010} \textit{versus} the solution obtained with MPM,
+both with same time integration scheme and spatial discretization. For
+this case the performance of MPM is robust and stable than OTM. As we
+can appreciate, during the first half of the simulation both method
+seem to perform in a similar way, but during the second half of the
+simulation after the elastic wave has travel from the free border to
+the fixed one and back, in OTM the solution becomes noisy than the
+one performed by MPM.  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.9\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-OTM-MPM}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Andersen block}
+\label{sec:andersen-block}
+
+In order to test the ability of this interpolation technique to deal
+with grid crossing instabilities we will simulate the vertical
+compression of a square block (10 by 10 meters) of soft soil sketched
+in figure~\ref{fig:block} and loaded using an incremental gravitation
+scheme.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.7\hsize}{!}{
+    \input{Figures/Block.tex}}
+  \caption{Geometrical description of a soil block }.}
+  \label{fig:block}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+This test was taken from PhD thesis of Andersen (2009)\cite{thesis_Andersen_2009}. The
+elastic parameters consider for this test are: 
+\begin{itemize} 
+\item  Initial density : $6\cdot 10^3\ kg/m^3$
+\item  Poisson ratio : $0$
+\item  Elastic modulus : $5\ MPa$
+\end{itemize}
+The gravity force is a apply as an external force according to the
+equations \eqref{eq:particle_body_forces},
+\eqref{eq:nodal_external_forces}. Using a total time period of T (20
+seconds) to apply the gravity, it is increased from 0 to 9.81$m/s$
+with a sinus function until T/2 and then maintained constant until T
+in order to arrive to a state of equilibrium, 
+\begin{equation}
+  \label{eq:gravity-load-block}
+ \mathbf{g}(t) = \left\{
+    \begin{array}{ll}
+      0.5 \mathbf{g} (\sin(\frac{2t \pi}{T} - \frac{\pi}{2})+1)  & \mbox{if } t \leq T/2 \\
+      \mathbf{g} & \mbox{if } t > T/2
+    \end{array}
+  \right.
+\end{equation}
+In order to get a stable solution, we will adopt a time step conducted
+by a Courant number of 0.1. On the other hand, the explicit predictor-corrector
+scheme is here employed looking forward getting better results. For the
+initial spatial discretization we will employ four particles per cell
+($\Delta x = 2\ m$). The initial setting of particles inside of the
+cell changes according to the approximation technique adopted. For the
+bi-linear shape functions and the LME approximants, the initial
+position corresponds to the location of the gauss-points in a standard
+quadratic finite element. For the uGIMP shape function the initial
+position of each particle is located in the center of each voxel, due
+to the fact that in the initial situation, the voxel domain should not
+overlap each others.
+
+Figure~\ref{fig:Block-LME3} shows the evolution of the vertical stress
+during the loading process. The result is physically realistic as
+stress increments linearly from the top to the bottom of the specimen,
+and the value of the vertical stress in a material point located in
+the bottom of the specimen oscillates centered in $5.2 MPa$, which is
+the analytic value given by $\sigma_{yy} = \rho g h_y$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+  \centering
+  \subfigure[t = 0 seconds.]{
+    \includegraphics[width=0.32\textwidth]{Figures/Block_LME3_PCE_a_t0}
+  }
+  \subfigure[t = 5 seconds.]{
+    \includegraphics[width=0.32\textwidth]{Figures/Block_LME3_PCE_b_t025}
+  }
+  \subfigure[t = 20 seconds]{
+    \includegraphics[width=0.32\textwidth]{Figures/Block_LME3_PCE_c_t1}
+  }
+  \caption{Vertical normal stress and position of material points
+    during the loading process for a soft soil ($E = 5\ MPa$, $\rho_0
+    = 6\cdot 10^3\ kg/m^3$). Numerical parameters considered for the
+    simulation are : Local \textit{max-ent} shape function $\gamma =3$
+    and explicit PC scheme with CFL 0.1.}
+  \label{fig:Block-LME3}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Figure~\ref{fig:vertical-displacement-block} shows the vertical
+displacement evolution of a point in the free surface of the block. As
+we can see the simulation using the Q4 interpolation technique turns
+out to be unstable and in the second 15 it fails. The uGIMP simulation
+is more stable than the one performed by the Q4. Despite this is still
+unstable and could trigger severe oscillations if we pretend to
+simulate non-linear materials. The LME simulation was performed using
+two kinds of shape functions, one with a low value of the
+dimensionless parameter, $\gamma = 0.8$, and other with a larger value
+of it, $\gamma = 3.0$. Notice that the results are both stable, but
+the larger values of $\gamma$ give us a very stable solution. This is
+due to the fact that with larger value of $\gamma$, the shape
+functions behaves in a similar way to the FEM, which performs very
+accurate in those cases with a reasonable mesh distorsion, and with a
+lower value it behaves in a similar way to the uGIMP. This behaviour
+was noticed previously by \cite{Arroyo2006}, were authors highlight
+how by adjusting the spatial variation of $\beta(\vect{x})$, it is
+possible to select regions of the domain of analysis which are treated
+by finite elements and regions that are treated in the style of
+meshfree methods, with seamless transitions between those regions. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
+  }
+  \caption{Comparative of the vertical displacement evolution in a
+    point located in the free surface employing different
+    interpolation schemes and numerical techniques.} 
+  \label{fig:vertical-displacement-block}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusions}
+\label{sec:conclusions}
+We have developed a novel time integration scheme for MPM, and
+proved how local \textit{max-ent} approximation scheme could be
+employed as an useful technique in MPM. The PCE arise as a highly
+efficient alternative for challenging dynamic problems like coupled
+$u-p_w$ without appeal to expensive implicit time integration
+algorithms. Also the procedure employed to design the PCE algorithm open
+the door to revisit a huge variety of time integration schemes
+developed originally for FEM, which can be rearranged to MPM framework
+with some modifications. Anyway, further research should be done to improve the
+formal comprehension of the algorithm good performance. This paper
+also enhances the suitability of the local \textit{max-ent} as a
+general promising alternative to the wide range of approximation.
+techniques developed for the MPM to overcome grid crossing
+limitations and to avoid the constriction of the uGIMP of a regular mesh
+or a high density of particles per cell. Future research of the
+group will be on the employ of this scheme to improve the localization
+capabilities of MPM for viscoplastic materials. Finally we remark on
+the possibility of adapting the function $\beta(\vect{x})$ as a second
+order tensor with the aim of adapt the shape function with the strain field which improves the
+performance of it in the aforementioned localization
+capabilities. Other possibility is to adapt the value of $\beta$ to
+solve the equations fem-like of meshfree-like depending of how behaves
+the region, this could be extremely useful in simulating all together
+initialization and propagation of fast landslides.
+
+\begin{acknowledgements}
+If you'd like to thank anyone, place your comments here
+and remove the percent signs.
+\end{acknowledgements}
+
+%
+\section*{Conflict of interest}
+%
+The authors declare that they have no conflict of interest.
+
+\appendix
+
 \section{The analytical solution of the 1D Dyka benchmark}
@@
 Therefore $v_{x=0} = 2\Re^{II}$. Finally, applying this conditions in
-the elastic bar sketched in \ref{fig:Dyka_Bar}, is possible to obtain
-the velocity history in the right side of the bar
-\ref{fig:vel_analytics_dyka} and the stress in the last quarter side of the Dyka
-bar \ref{fig:stress_analytics_dyka} as is demanded in \cite{Dyka1995}.
+the elastic bar sketched in figure~\ref{fig:Dyka_Bar}, is possible to obtain
+the velocity history in the right side of the bar plotted in the figure~\ref{fig:vel_analytics_dyka} and the stress in the last quarter side of the Dyka
+bar plotted in the figure~\ref{fig:stress_analytics_dyka} as is demanded in \cite{Dyka1995}.
 

### 2020-04-21 2020_EFM_MPM_Eigensoftening.tex
Cambios 22-4-2020

\documentclass[preprint,12pt,a4paper]{elsarticle}

% \usepackage{lineno,hyperref}
\usepackage{float}
\usepackage{subfig}
\usepackage{color}
\usepackage{soul}

\usepackage{algcompatible}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{algpseudocode}

\usepackage{cancel}

\usepackage{amsmath,amsthm,amssymb}

\newcommand{\vec}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\tens}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\Matrix}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\Vector}[1]{
  \ensuremath{\mathbf{{#1}}}
}
% Divergence
\newcommand{\Div}[1]{
  \ensuremath{div({#1})}
}
% Gradient
\newcommand\Grad[1]{grad({#1})}
\newcommand\GradS[1]{grad^s({#1})}
\newcommand\GradT[1]{grad^T({#1})}
% Partial derivative
\newcommand{\Deriv}[3][]{
  \ensuremath{\frac{\partial^{#1}{#2}}{ \partial {#3}^{#1} }}
}
% Integral
\newcommand{\Integral}[2]{
  \IfStrEqCase{#1}{
    {2}{\ensuremath{\int_{\varGamma_d}{#2}\ d\varGamma}}
    {3}{\ensuremath{\int_{\varOmega}{#2}\ d\varOmega}}
  }
}

\modulolinenumbers[5]

\journal{Engineering Fracture Mechanics}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{LME-MPM applied to quasi-brittle fracture.}

%% Group authors per affiliation:
\author{
Miguel Molinos$^a$\footnote{Corresponding author: m.molinos@outlook.es},
and Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es}
 }
 \address{
 $^a$ ETSI Caminos, Canales y Puertos, Universidad Polit\'ectnica de Madrid.\\ c. Prof. Aranguren 3, 28040 Madrid, Spain
}

\begin{abstract}

  The objective of this work is to introduce an alternative
  technique to address the fracture process of brittle and
  quasi-brittle materials under the material point method (MPM)
  framework. With this purpose the eigensoftening algorithm, developed
  originally for the optimal transportation meshfree (OTM)
  approximation scheme, is extended to the MPM with the aim of present
  a suitable alternative to the existing fracture algorithms developed
  for the MPM. The good fitting in the predictions made by the
  eigensoftening algorithm against both analytical and experimental
  results proofs the well performance of the method under challenging loads.

\end{abstract}

\begin{keyword}
Quasi brittle fracture \sep Local-\textit{max-ent} approximation \sep
Material Point Method \sep Solid Dynamics
\end{keyword}

\end{frontmatter}

\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:1}

The simulation of fracture propagation in a more accurate and
effective way can be considered as one of the original drivers for
developing novel spatial discretization methods such as meshfree
methods like the material point method (MPM). Presence of cracks are a
violation of the continuity requirement of the finite element method
(FEM).

By contrast, MPM does not suffer from the above difficulty since the
continuity requirement is less restrictive. Regarding fracture, it can
be described in two ways. One is to remove the restriction of the single-valued velocity field close to the crack by using two or
more sets of nodes \cite{Nairn_2006}. This method is based in to
assign different labels to distinguish if the material points and
nodes are in the same side of the crack or not. Under this approach
the crack surface is described with line segments in 2D and triangle
patches in 3D cases. This method was named as ``CRAcks with Material
Points (CRAMP)'' \cite{Nairn_2003}. In this method, the criteria for
crack propagation is based on such parameters as energy release rate
analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
intensity factor or the J-integral discussed by Guo \& Nairn
(2004)\cite{Nairn_2004}.

and the other is to use failed material points to
describe the crack evolution.

The erosion of the material point means that each material point can
be either intact or be completely failed or eroded and has no load
bearing capacity, Even thought the method has been successfully
applied to dynamic fragmentation of metals, quantitative validations,
such as stress or strain levels near or at the crack set compared to
experimental measures are still lacking. Having in mind that the
eigenerosion approach was intended for perfectly brittle fracture, an
eigensoftening concept is developed for quasi-brittle materials

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The meshfree methodology}
\label{sec:2}

The aim of this section is to provide an overview of the special
techniques employed to face the fracture problem under the MPM
framework. In consequence it is structured as follows: first in
\ref{sec:2.1} we summarize the explicit-predictor algorithm for the
MPM, next the local \textit{max-ent} approximants are introduced in
\ref{sec:2.2} as an accurate alternative technique to interpolate data
between particles and nodes, and finally the fracture algorithms based
in the eigendeformations are presented in \ref{sec:2.3}.

\subsection{The Material Point Method}
\label{sec:2.1}

The MPM~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian method
where particles carries on all the physical information and a set of
background nodes is employed to compute the equilibrium
equation. Since the MPM possesses the advantages of both Lagrangian
and Eulerian descriptions, no element distortion exists in the MPM,
therefore it is an appropriate and efficient method in solving
problems involving extremely large deformation and moving
discontinuities such fracture evolution. For the spatial
discretization, two sets of points are introduced in 
the MPM. First, the nodes. This points are considered fixed in the
space and are in charge of computing all the kinematic fields such
forces $f_I$, accelerations $a_I$ and velocities $v_I$. And second the
material points or particles. They are in charge of the discretization
of the continuum, and store the local state ($\sigma_p,
\varepsilon_p$). Without loosing generality, the MPM algorithm can be
described with three main steps: (i) a
variational recovery process, where particle data is projected to the
grid nodes, (ii) an Eulerian step, where balance of momentum equation
is expressed as a nodal equilibrium equation thorough a FEM-like
procedure, and finally (iii) a Lagrangian advection of the
particles. In the present research we will adopt a explicit
predictor-corrector time integration scheme. The purpose of this
choice is motivated due its proved robustness and stability in
numerical calculations. In the first stage (i), the nodal velocity
predictor is computed following \eqref{eq:Predictor-velocity}, 
\begin{equation}
  \label{eq:Predictor-velocity}
  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
\end{equation}
This way of computing the nodal predictor is both numerically stable
and minimize the computational effort. Once nodal velocity are
obtained, the essential boundary conditions are imposed. And in the
following, a Eulerian phase (ii) is computed in the set of nodes in a
FEM-like way, where nodal forces $\vec{f}_{I}^{k+1}$ are computed thorough the
equilibrium equation. Next the nodal velocities are corrected in a
\textit{corrector} stage,
\begin{equation}
  \label{eq:Corrector-velocity}
  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}
\end{equation}
Finally updated the particles are advected in the Lagrangian stage (iii) using nodal values as,
\begin{align}
  \label{eq:Update-lagrangian-pce}
        &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
        \frac{N_{Ip}^k\
        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
         N_{Ip}^k\ \vec{v}_{I}^{k} +
        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
        \vec{f}_{I}^{k}}{\tens{m}_I^k} 
\end{align}
The complete pseudo-algorithm it is summarized in \ref{sec:expl-pred-corr}.

\subsection{Spatial discretization : Local-\textit{max-ent} approximants}
\label{sec:2.2}

Local maximum-entropy (or local \textit{max-ent}) approximation scheme
was introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} as a bridge between finite elements and meshfree methods. The key idea of the  shape functions is to interpret the nodal of a shape function $N_I$ as
a probability. This allow us to introduce two important limits:
the principle of maximum-entropy (\textit{max-ent}) statistical
inference stated by \cite{Jaynes1957}, and the Delaunay triangulation
which ensures the minimal width of the shape function. To reach to a compromise between two competing objectives, a Pareto set is defined as, 
\begin{align*}
  \label{eq:LME-scheme-pareto-set}
  \text{(LME)}_{\beta} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
  \vec{x} \hspace{0.15cm} \text{minimise} \hspace{0.15cm} f_{\beta}(\vec{x}_p, N_I) = \beta U(\vec{x}_p,N_I) - H(N_I) \\
  &\text{subject to}\
  \begin{cases}
    N_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
    \sum\limits_{I=1}^{N_n}{N_I} = 1 \\[1em]   
    \sum\limits_{I=1}^{N_n}{N_I \vec{x}_I} = \vec{x} \\
  \end{cases}
\end{align*}
where $H(N_I)$ is the entropy of the system of nodes following the
definition given by Shannon (1948) \cite{Shannon1948}, and $U(\vec{x}_p,N_I) =
\sum_I N_I |\vec{x}_p - \vec{x}_I |^2$ a magnitude of the shape
function width. The regularization o \textit{thermalization} parameter
between the two criterion $\beta$ has Pareto optimal values in the range
$(0,\infty)$. The unique solution of the local max-ent problem
(LME)$_\beta$ is:
\begin{equation}
  \label{eq:LME-p}
N_I^*(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
    \vec{\lambda}^* \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
\end{equation}
where $Z(\vec{x},\vec{\lambda}^*(\vec{x}))$ is the \textit{partition
  function} defined as,
\begin{equation}
  \label{eq:LME-Z}
Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \; |\vec{x}-\vec{x}_I|^2 + \vec{\lambda} \cdot (\vec{x}-\vec{x}_I)  \right]}
\end{equation}
and evaluated in the unique minimiser $\vec{\lambda}^*(\vec{x})$ for
the function $\log
Z(\vec{x}, \vec{\lambda})$. The traditional way to obtain such a
minimiser is using (\ref{eq:LME-J}) to calculate small increments of $\partial\vec{\lambda}$ in a
Newton-Raphson approach. Where $\tens{J}$ is the Hessian matrix, defined by:
\begin{eqnarray}
  \label{eq:LME-J} 
  \tens{J}(\vec{x}, \vec{\lambda},\beta) &\equiv& \frac{\partial
                                                  \vec{r}}{\partial \vec{\lambda}}\\
  \label{eq:LME-r}
  \vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \frac{\partial \log{ Z(   \vec{x},\vec{\lambda}})}{\partial \vec{\lambda}}  = \sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I)
\end{eqnarray}
In order to obtain the first derivatives of the shape function~$\nabla
N^*_I$, can be computed as,
\begin{equation}
  \label{eq:LME-grad-p}
\nabla N^*_I = N^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} N^*_J \, \nabla f^*_J\right)
\end{equation}
where
\begin{equation}
  \label{eq:LME-f}
f^*_I(\vec{x},  \vec{\lambda},\beta)=-\beta \, |\vec{x}-\vec{x}_I|^2 + \vec{\lambda}^*  \,  (\vec{x}-\vec{x}_I)
\end{equation}
Employing the chain rule over \eqref{eq:LME-grad-p}, rearranging and considering $\beta$ as a
constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following
expression for the gradient of the shape function.
\begin{eqnarray}
  \label{eq:LME-gradp} 
\nabla N^*_I &=& -N^*_I \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I)
\end{eqnarray}

The regularization parameter $\beta$ of LME shape functions may be
controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
\cite{Arroyo2006}, where $h$ is defined as a measure of the nodal
spacing. Since  $N_I$ is defined in the entire domain, in practice,
the shape function decay $\exp(-\beta \vec{r} )$ is truncated  by  a
given tolerance, 10$^{-6}$, for example,  would ensure a reasonable range of
neighbours, see \cite{Arroyo2006} for details. This tolerance defines
the limit values of the influence radius and is used thereafter to
find the neighbour nodes of a given integration point.

\subsection{Fracture modelling approach}
\label{sec:2.3}

Within the context of MPM formulation, fracture can be modelled by
failing particles according to a suitable criterion. When material
points are failed, they are assumed to have a null stress
tensor. Navas {\it et al.} (2017)\cite{Navas_2017_ES} developed a
eigensoftening algorithm as an extension for quasi-brittle materials
of the eigenerosion proposed by Pandolfi \& Ortiz
(2012)\cite{Pandolfi_2012} for fracture of brittle materials. A
comparison between both in \cite{Navas_2017_ES} shows that
the eigenerosion algorithm significantly overestimates the tensile
stress and the strain peaks, while it captures the forces and crack
patterns accurately. On the other hand eigensoftening algorithm agree
very well with experimental results in all the aspects. Furthermore,
this algorithm has also proof its accuracy for complex fracture
patters such the present in fiber reinforces concrete (FRC),
\cite{Navas_2018_ES}.\\

\begin{align}
  \label{eq:energy-release-EE}
&G_p^{k+1} = \frac{C_{\epsilon}}{m_p^{k+1}}  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q W_q^{k+1}\\
&m_p^{k+1} =  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q  
\end{align}
where $B_{\epsilon}(x_p^{k+1})$ is the sphere of radius $\epsilon$
centered at $x_p^{k+1}$ known as the $\epsilon$-neighborhood of the
material point, $m_p^{k+1}$ is the mass of the neighborhood at step
$k+1$, $W_q^{k+1}$ is the current free-energy density per unit mass as
the material point $x_q^{k+1}$ of the neighborhood, finally
$C_{\epsilon}$ is a normalizing constant. This configuration
conveniently is sketched in Figure \ref{fig:Failed-particles}.
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Figures/Particle-failed}
  \caption{Scheme of a linear cohesive law, where the shaded area is
    $G_f$, $f_t$ is the tensile strength, and $w_c$ is the critical
    opening displacement.}
  \label{fig:Failed-particles}
\end{figure}
%%%%%%%%%%%
The material point fails when $G_p^{k+1}$ surpasses a critical energy
release rate that measures the material-specific energy, $G_F$. The
convergence of this approach has been analyzed by Schmidt {\it et al.}
(2009)\cite{Schmidt_2009}, who proof that it converges to the Griffith
fracture when discretization size tends to zero. It is necessary to
point out that when a material point overpass the critical energy, its
contribution to the internal forces vector  is set to zero, but its
contribution to the mass matrix is maintained. The mass of a material
point is discarded only when an eroded material point is not connected
to any nodes.\\

As can be noticed, in the eigenerosion algorithm an energetic
criterion is adopted. Due to that fact, unrealistic stress
concentration (higher than tensile strength) in quasi-brittle materials, see
\cite{Navas_2017_ES}. To overcome this limitation, the aforementioned
authors proposed the concept of eigensoftening to take in to account
the gradual failure in quasi-brittle materials. The concept is
inspired in the cohesive fracture widely employed in the context of
FEM \cite{Ortiz_1999}. This gradual failure criterion is plotted in
figure \label{fig:Damage-ft-wc}, where a linear decreasing cohesive
law is presented to illustrate the concept here described. In the
picture, the shaded area represents the static fracture energy per
unit of area, $G_F$. As we can see, a cohesive crack appears when the
maximum tensile strength, $f_t$ is reached. Once the opening
displacement $w$ takes the value of the critical crack displacement
$w_c$, a stress-free crack is attained. For intermediate values,
$w_n$, a damage value between zero and one represents the extension to
which the material has failed.
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Figures/Damage}
  \caption{Scheme of a linear cohesive law, where the shaded area is
    $G_f$, $f_t$ is the tensile strength, and $w_c$ is the critical
    opening displacement.}
  \label{fig:Damage-ft-wc}
\end{figure}
%%%%%%%%%%%
For the eigensoftening algorithm,

a strength criterion for crack initialization was adopted

\begin{equation}
  \label{eq:variation-averaged-strain-energy-density}
  \delta W_{p,\epsilon} = \frac{\partial G_p}{C_{\epsilon}} =
  \frac{1}{m_p} \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} \delta \tens{\epsilon}_q
\end{equation}

\begin{equation}
  \label{eq:variation-averaged-strain-energy-density-simpli}
  \delta W_{p,\epsilon} =
  \frac{\delta \tens{\epsilon}_p}{m_p} \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} 
\end{equation}

\begin{equation}
  \label{eq:equivalent-critical-stress}
  \delta \tens{\sigma}_{p,c} =
  \frac{1}{m_p} \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} 
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cases of study and discussion}
\label{sec:3}

\subsection{Comparison with analytical solution}
\label{sec:3.1}

\subsection{Brazilian test}
\label{sec:3.2}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Figures/Brazilian}
  \caption{Geometry and boundary condition of the Brazilian test.}
  \label{fig:geometry-brazilian-test}
\end{figure}

\subsection{Drop-weight impact test}
\label{sec:3.3}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/Drop_weight}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-drop-weight-impact-test}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:6}

\section*{Acknowledgements}
The first author acknowledges the fellowship Agustín de Betancourt 262390106114.

\appendix
%\addappheadtotoc
%\appendixpage
%\renewcommand{\theequation}{\Alph{section}.\arabic{equation}}

\clearpage

\section{Explicit Predictor-Corrector algorithm}
\label{sec:expl-pred-corr}

\begin{algorithm}
  \floatname{algorithm}{Algorithm}
  \renewcommand{\thealgorithm}{}
  \caption{Explicit Predictor-Corrector scheme}
  \begin{algorithmic}[1]
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
    \STATE \textbf{Update mass matrix}:
    \begin{equation*}
      \tens{m}_{I} = N_{Ip}^{k}\ m_p,
    \end{equation*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Explicit Newmark Predictor}:\\
    \begin{equation*}
      \vec{v}_I^{pred} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
    \end{equation*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Impose essential boundary conditions}:\\
    At the fixed boundary, set $\vec{v}_{I}^{pred} = 0$. 
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    % \STATE \textbf{Discard the previous nodal values}.
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Deformation tensor increment calculation}.
    \begin{align*}
      &\dot{\tens{\varepsilon}_{p}}^{k+1} = \left[ \vec{v}_{I}^{pred} \otimes
        \Grad{N_{Ip}^{k+1}} \right]^s \\
      &\Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\ \dot{\tens{\varepsilon}_{p}}^{k+1}
    \end{align*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Update the density field}:
    \begin{equation*}
      \rho_p^{k+1} = \frac{\rho_p^k}{1 + \mathit{tra}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.
    \end{equation*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Compute damage parameter}:
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Balance of forces calculation}:\\
    Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
    (1-\chi)\vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
    \eqref{eq:nodal_internal_forces} and
    \eqref{eq:nodal_external_forces} in the time step $k+1$.
    In the grid node $I$ is fixed in one of the spatial dimensions, set it to
    zero to make the grid nodal acceleration zero in that direction.\\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Explicit Newmark Corrector}:
    \begin{equation*}
      \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}  
    \end{equation*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \STATE \textbf{Update particles lagrangian quantities}:
    \begin{align*}
      &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
        \frac{N_{Ip}^k\
        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
         N_{Ip}^k\ \vec{v}_{I}^{k} +
        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
        \vec{f}_{I}^{k}}{\tens{m}_I^k}
    \end{align*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Reset nodal values}
  \end{algorithmic}
\end{algorithm}

\section{Eigensoftening Algorithm}
\label{sec:eigens-algor-1}

\begin{algorithm}\caption{Compute damage parameter $\chi_P^{k+1}$}\label{alg-eigens}
  \begin{algorithmic}
    \REQUIRE Particle status\\
    Number of particles: $N_p$\\
    $\epsilon$-neighbourhood of each particle $p$ : $B_{\epsilon,p}$\\
    \REQUIRE Material data\\
    Tensile strength: $f_{t,p}$\\
    Bandwidth of the cohesive fracture: $h_{\epsilon,p}$ \\
    Critical opening displacement: $w_c$\\ 
    \ENSURE Return damage parameter $\chi := \{\chi_p\}$
    \STATE $\chi_p \leftarrow \chi_p^{k}$
    \FOR{$p$ to $N_p$}
    \IF{$\chi_p = 0$ \AND $\epsilon_{f,p} = 0$}
    \FOR{$q \in B_{\epsilon,p}$}
    \IF{$\chi_q < 1$}    
    \STATE $\sum m_p\sigma_{p,I} \leftarrow \sum m_p\sigma_{p,I} + m_q\sigma_{q,I}$
    \ENDIF    
    \STATE $m_p \leftarrow m_p + m_q$
    \ENDFOR
    \STATE $\sigma_{p,\epsilon} \leftarrow \frac{1}{m_p} \sum m_p\sigma_{p,I}$
    \IF{$\sigma_{p,\epsilon} > f_{t,p}$}
    \STATE $\epsilon_{f,p} = \epsilon_{I,p}$   
    \ENDIF        
    \ELSE[$\chi_p \neq 1$ \AND $\epsilon_{f,p} > 0$]
    \STATE $\chi_p^{k+1} \leftarrow \min\Big \{1 , \max \{\chi_p^{k},
    \frac{(\epsilon_{I,p}- \epsilon_{f,p})\ h_{\epsilon,p}}{w_c} \} \Big \}$    
    \ENDIF    
    \ENDFOR
  \end{algorithmic}
\end{algorithm}

% name your BibTeX data base
\bibliography{Biblio/Biblio}

\end{document}

### 2020-04-21 Figures/Damage_graph.py

@@ -1,0 +1,13 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+xi = np.linspace(0,1)
+f = 1 - xi
+
+fig, ax = plt.subplots()
+ax.set_xlim(0,1.2)
+ax.set_ylim(0,1.2)
+ax.plot(xi,f)
+
+plt.show()
+

### 2020-04-22 LME-MPM.tex
Arreglando liadas

--- 2020-03-29 main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is a general template file for the LaTeX package SVJour
-% for Springer journals.          Springer Heidelberg 2010/09/16
-%
-% Copy it to a new file with a new name and use it as the basis
-% for your article. Delete % signs as needed.
-%
-% This template includes a few options for different layouts and
-% content for various journals. Please consult a previous issue of
-% your journal as needed.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% First comes an example EPS file -- just ignore it and
-% proceed on the \documentclass line
-% your LaTeX will extract the file if required
-\begin{filecontents*}{example.eps}
-%!PS-Adobe-3.0 EPSF-3.0
-%%BoundingBox: 19 19 221 221
-%%CreationDate: Mon Sep 29 1997
-%%Creator: programmed by hand (JK)
-%%EndComments
-
-gsave
-newpath
-  20 20 moveto
-  20 220 lineto
-  220 220 lineto
-  220 20 lineto
-closepath
-2 setlinewidth
-gsave
-  .4 setgray fill
-grestore
-stroke
-grestore
-\end{filecontents*}
-%
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-% flush right qed marks, e.g. at end of proof
-\smartqed
-
-\usepackage[lofdepth,lotdepth]{subfig}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{subfigure} % subfiguras
-%
-\usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{epstopdf}
-\usepackage{mathrsfs} % para formato de letra
-\usepackage{hyperref}
-\usepackage{enumitem}
-\usepackage{array}
-\usepackage{tabularx}
-\usepackage{supertabular}
-\usepackage{fancyhdr}
-\usepackage{multirow}
+% %%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+% %
+% % This is a general template file for the LaTeX package SVJour
+% % for Springer journals.          Springer Heidelberg 2010/09/16
+% %
+% % Copy it to a new file with a new name and use it as the basis
+% % for your article. Delete % signs as needed.
+% %
+% % This template includes a few options for different layouts and
+% % content for various journals. Please consult a previous issue of
+% % your journal as needed.
+% %
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %
+% % First comes an example EPS file -- just ignore it and
+% % proceed on the \documentclass line
+% % your LaTeX will extract the file if required
+% \begin{filecontents*}{example.eps}
+% %!PS-Adobe-3.0 EPSF-3.0
+% %%BoundingBox: 19 19 221 221
+% %%CreationDate: Mon Sep 29 1997
+% %%Creator: programmed by hand (JK)
+% %%EndComments
+
+% gsave
+% newpath
+%   20 20 moveto
+%   20 220 lineto
+%   220 220 lineto
+%   220 20 lineto
+% closepath
+% 2 setlinewidth
+% gsave
+%   .4 setgray fill
+% grestore
+% stroke
+% grestore
+% \end{filecontents*}
+% %
+% \RequirePackage{fix-cm}
+% %
+% %\documentclass{svjour3}                     % onecolumn (standard format)
+% %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+% %\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+% \documentclass[twocolumn]{svjour3}          % twocolumn
+% %
+% % flush right qed marks, e.g. at end of proof
+% \smartqed
+
+% \usepackage[lofdepth,lotdepth]{subfig}
+% \usepackage{graphicx}
+% \usepackage{subcaption}
+
+% \usepackage{amsmath,amsthm,amssymb}
+
+% \usepackage{amsfonts}
+% \usepackage{epstopdf}
+% \usepackage{mathrsfs} % para formato de letra
+% \usepackage{hyperref}
+% \usepackage{enumitem}
+% \usepackage{array}
+% \usepackage{tabularx}
+% \usepackage{supertabular}
+% \usepackage{fancyhdr}
+% \usepackage{multirow}
+% \usepackage{color}
+% \usepackage{makeidx}
+% \usepackage{setspace}
+% \usepackage{epsfig}
+
+% \usepackage{pgf}
+% % \usepgfplotslibrary{external} 
+% % \tikzexternalize
+
+% %\usepackage{latexsym}
+
+\documentclass[preprint,12pt,a4paper]{elsarticle}
+
+\usepackage{lineno,hyperref}
+\usepackage{float}
+\usepackage{subfig}
 \usepackage{color}
-\usepackage{makeidx}
-\usepackage{xstring}
-\usepackage{setspace}
-\usepackage{epsfig}
-
-\usepackage{pgf}
-% \usepgfplotslibrary{external} 
-% \tikzexternalize
-
-%\usepackage{subfigure}
-\usepackage{preview}
+\usepackage{soul}
+
 % Packages to write pseudo-algorithms %
@@
 \usepackage{algorithmic}
+
+\usepackage{cancel}
+
+\usepackage{subfigure} % subfiguras
+
+\usepackage{amsmath,amsthm,amssymb}
+\usepackage{xstring}
 
@@
 
-%\usepackage{latexsym}
-% etc.
-
-%
-
-% Matrix and vector nodes
+\newcommand{\vec}[1]{
+  \ensuremath{\mathbf{{#1}}}
+}
+\newcommand{\tens}[1]{
+  \ensuremath{\mathbf{{#1}}}
+}
 \newcommand{\Matrix}[1]{
@@
 }
-
 % Divergence
@@
 \newcommand\GradT[1]{grad^T({#1})}
-
 % Partial derivative
@@
 }
-
 % Integral
@@
 
-%
-% Insert the name of "your journal" with
-\journalname{Computational Particle Mechanics}
-%
+\modulolinenumbers[5]
+
+\journalname{Computer Methods in Applied Mechanics and Engineering}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Elsevier bibliography styles
+%%%%%%%%%%%%%%%%%%%%%%%
+%% To change the style, put a % in front of the second line of the current style and
+%% remove the % from the second line of the style you would like to use.
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Numbered
+%\bibliographystyle{model1-num-names}
+
+%% Numbered without titles
+%\bibliographystyle{model1a-num-names}
+
+%% Harvard
+%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
+%% Vancouver numbered
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+
+%% Vancouver name/year
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+
+%% APA style
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+
+%% AMA style
+%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
-% \title{Novel improvements in the Material Point Method to face
-%   dynamic problems: 
-%   Local-maximum entropy approximation and an explicit predictor-corrector scheme. \thanks{Funding: This
-%     study was funded by Agustín de Betancourt Foundation (grant number
-%     262390106114).}
-% }
+\begin{frontmatter}
 
 \title{Enhanced Material Point Method to face
-  dynamic problems:\thanks{Funding: This
-    study was funded by Agustín de Betancourt Foundation (grant number
-    262390106114).}
-}
-\subtitle{Local-maximum entropy approximation and explicit
+  dynamic problems: Local-maximum entropy approximation and explicit
   predictor-corrector scheme}
 
-\titlerunning{Novel improvements in the Material Point Method to face
-  dynamic problems.} % if too long for running head
-
-\author{Miguel Molinos \and
-  Pedro Navas \and
-  Manuel Pastor \and
-  Miguel Martín Stickle
-}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-% \institute{Miguel Molinos \at
-%   E.T.S de Ingenieros de Caminos, Canales y Puertos. \\
-%   Universidad Politéctnica de Madrid, 28040 Madrid, Spain \\
-%   \email{m.molinos@alumnos.upm.es}
-%   % \emph{Present address:} of F. Author  %  if needed
-%   \and
-%   Pedro Navas 
-%   \and
-%   Manuel Pastor
-%   \and
-%   Miguel Martín Stickle
-% }
-% \institute{Miguel Molinos, Pedro Navas and Manuel Pastor \at E.T.S
-%   de Ingenieros de Caminos, Canales y Puertos, Universidad Politéctnica de Madrid, 28040 Madrid, Spain, \; \email{m.molinos@outlook.es, pedro.navas@upm.es, manuel.pastor@upm.es}
-% }
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
+%% Group authors per affiliation:
+\author{
+Miguel Molinos$^a$
+Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es},
+Manuel Pastor$^a$
+and Miguel Martín Stickle$^a$ 
+}
+\address{
+  $^a$ ETSI Caminos, Canales y Puertos, Universidad Polit\'ectnica de Madrid.\\ c. Prof. Aranguren 3, 28040 Madrid, Spain
+}
+
 \begin{abstract}
@@
   integration scheme to filter spurious noises. To overcome this
-  limitation in this paper, an explicit predictor-corrector time integration
-  scheme has been proposed. Its superior performance mitigates the
+  limitation in this paper, an explicit predictor-corrector time integration scheme has been proposed. Its superior performance mitigates the 
   presence of spurious oscillations with minimal dissipation in high
@@
   the performance of both improvements thorough numerical examples.    
-  \keywords{LME \and MPM \and Explicit predictor-corrector \and Dynamic problems}
-  % \PACS{PACS code1 \and PACS code2 \and more}
-  % \subclass{MSC code1 \and MSC code2 \and more}
 \end{abstract}
+
+\begin{keyword}
+  LME \sep MPM \sep Explicit predictor-corrector \sep Dynamic problems}
+\end{keyword}
+
+\end{frontmatter}
+
+\linenumbers
 
@@
 physical variables involved in this problem are collected in Table
-\ref{tab:notation-table}. Three kind of subscript or superscript are used within paper. The
-subscript $\qed_p$ is used to define a particle variable. While the
-subscript $\qed_I$ is reserved in this notation for denoting nodal
+\ref{tab:notation-table}. Three kind of subscript or superscript are used within paper. The subscript$\qed_p$ is used to define a particle variable. While the
+subscript$\qed_I$ is reserved in this notation for denoting nodal
 variables. And finally, the superscript $\qed^{\psi}$ involves a
@@
 $\ddot{\qed}$ for the first and second time derivative, $\qued \otimes
-\qued$ means the dyadic operator, $(\cdot)$ and $(\colon)$ means the first
-and second contraction of a tensor, $\Div{\qed}$ denotes the
+\qued$ means the dyadic operator, $(\cdot)$ and $(\colon)$ means the first and second contraction of a tensor, $\Div{\qed}$ denotes the
 divergence operator, and finally $\Grad{\qed}$ and $\GradS{\qed}$
@@
 convention is adopted therefore repeated index means addition. 
-
 \begin{table}
@@
   \centering
-  \resizebox{0.5\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/MPM_scheme}
+  \resizebox{0.8\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/MPM_scheme_horizontal}
   }
@@
   \label{eq:Update-lagrangian-pce}
-        &\vec{a}_p^{k+1} = \vec{a}_p^n +
-        \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+        &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
       &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
@@
     \begin{align*}
-      &\vec{a}_p^{k+1} = \vec{a}_p^n +
-        \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
       &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
@@
 
-\section{Local max-ent approximants}
+\section{Local \textit{max-ent} approximants}
 \label{sec:local-max-ent}
@@
 parameter $\beta$ affects to the accuracy and stability of the solution.
-
 The basic idea of the shape functions based on such
-an estimate is to interpret the shape function $N_I(\vec{x})$ as the
-probability of $\vec{x}$ to obtain the value $\vec{x}_I$,  $I=1,
-\dots, n$. Here $n$ is the number of nodes in the domain.
+an estimate is to interpret the shape function $N_I(\vec{x})$ as a probability. This allow us to introduce two important limits:
+the principle of maximum-entropy (\textit{max-ent}) statistical
+inference stated by \cite{Jaynes1957}, and the Delaunay triangulation
+which ensures the minimal width of the shape function.
+
 This approximation scheme represents a optimal compromise, in the sense of
@@
   \label{eq:least-biased-approximation-scheme}
-  \text{(LME)} \hspace{0.15cm} &\text{Maximize} \hspace{0.15cm} H(p) =
-  -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I }\\
+  \text{(LME)} \hspace{0.15cm} &\text{Maximize} \hspace{0.15cm} H(N_I) \equiv
+  -\sum_{I}^{N_n}{N_I(\vec{x})\log N_I }\\
   &\text{subject to}\
   \begin{cases}
-    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
+    N_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I \vec{x}_I} = \vec{x} \\
   \end{cases}
 \end{align*}
-The local max-ent approximation schemes (LME) as a Pareto set,
-defined by \cite{Arroyo2006} is as follows
+On the other hand, we wish to control the width of the shape function and it dacay with distance away from the corresponding nodes.
+To reach to this objective \cite{Arroyo2006} propose the following linear program,
+\begin{align*}
+  \label{eq:RAJAN}
+  \text{(RAJ)} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
+  \vec{x} \hspace{0.15cm} \text{minimize} \hspace{0.15cm} U(\vec{x}_p,N_I) \equiv
+\sum_I N_I |\vec{x}_p - \vec{x}_I |^2\\
+  &\text{subject to}\
+  \begin{cases}
+    N_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I \vec{x}_I} = \vec{x} \\
+  \end{cases}
+\end{align*}
+To reach to a compromise between two competing objectives, a Pareto set is defined by \cite{Arroyo2006} as,
 \begin{align*}
@@
   \text{(LME)}_{\beta} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
-  \vec{x} \hspace{0.15cm} \text{minimise} \hspace{0.15cm} f_{\beta}(\vec{x}, p) = \beta H(\vec{x},p) - H(p) \\
+  \vec{x} \hspace{0.15cm} \text{minimize} \hspace{0.15cm} f_{\beta}(\vec{x}, N_I) \equiv \beta U(\vec{x},N_I) - H(N_I) \\
   &\text{subject to}\
   \begin{cases}
-    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
+    N_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I \vec{x}_I} = \vec{x} \\
   \end{cases}
 \end{align*}
-for $\beta \in (0,\infty)$ is Pareto optimal. The unique solution of
+The regularization o \textit{thermalization} parameter
+between the two criterion $\beta$ has Pareto optimal values in the range
+$\beta \in (0,\infty)$. The unique solution of
 the local max-ent problem (LME)$_\beta$ is:
@@
   \label{eq:LME-p}
-p(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
-    \vec{\lambda} \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
+N_I^*(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
+    \vec{\lambda}^* \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*)}
 \end{equation}
@@
 \end{equation}
-being $\vec{\lambda}^*(\vec{x})$ the unique minimiser  for $\log
-Z(\vec{x}, \vec{\lambda})$. In order to obtain the first derivatives of the shape function, it is also necessary to compute~$\nabla p^*_I$ 
+being $\vec{\lambda}^*(\vec{x})$ the unique minimiser for the function $\log
+Z(\vec{x}, \vec{\lambda})$.
+The traditional way to obtain such a minimiser is using Eq.~(\ref{eq:LME-J}) to calculate small increments of $\partial\vec{\lambda}$ in a Newton-Raphson approach.
+Where $\tens{J}$ is the Hessian matrix, defined by:
+\begin{eqnarray}
+  \label{eq:LME-J} 
+  \tens{J}(\vec{x}, \vec{\lambda},\beta) &\equiv& \frac{\partial
+                                                  \vec{r}}{\partial \vec{\lambda}}\\
+  \label{eq:LME-r}
+  \vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \frac{\partial \log{ Z(   \vec{x},\vec{\lambda}})}{\partial \vec{\lambda}}  = \sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I)
+\end{eqnarray}
+In order to obtain the first derivatives of the shape function, it is also necessary to compute~$\nabla N_I^*$
 \begin{equation}
   \label{eq:LME-grad-p}
-\nabla p^*_I=p^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} p^*_J \, \nabla f^*_J\right)
+\nabla N_I^* &=& N^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} N^*_J \, \nabla f^*_J\right)
 \end{equation}
@@
 \end{equation}
-Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression:
+Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression for the gradient of the sahep function.
 \begin{eqnarray}
-\nabla p^*_I &=& -p^*_I \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I) \label{eq26} 
+\nabla N_I^* &=& -N_I^* \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I) \label{eq26} 
 \end{eqnarray}
-%&&\mbox{
-where \tens{J} is the Hessian matrix, defined by:
-%} \nonumber \\&& \nonumber \\
-\begin{eqnarray}
-\tens{J}(\vec{x},  \vec{\lambda},\beta) &=& \frac{\partial \vec{r}}{\partial  \vec{\lambda}} \label{eq27} \\ 
-%&& \nonumber \\
-\vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \partial_{\vec{\lambda}}{\log{ Z( \vec{x},\vec{\lambda}})} 
-%\nonumber \\ &=&
-  =\sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I) \label{eq28} 
-\end{eqnarray}
-Note that, the objective of the above procedure is to find the
-$\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. The
-traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27})
-to calculate small increments of $\partial\vec{\lambda}$ in a
-Newton-Raphson approach. Similar to alternative non-polynomial meshfree basis functions, the
-LME approximation scheme requires more than $d+1$ nodes to determine
-the values of the shape functions as well as their derivatives at any
-point in the convex hull of the nodal set, where $d$ is the dimension
-of the problem. The support size of LME shape functions may be
+The regularization parameter $\beta$ of LME shape functions may be
 controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
-\cite{Arroyo2006} (e.g. two dimensional example shown in figure~\ref{fig:LME_MPM}).
- Since  $p_I$  is defined in the entire domain, in practice, the
+\cite{Arroyo2006}, where $h$ is defined as a measure of the nodal
+spacing. 
+Since $N_I$ is defined in the entire domain, in practice, the
 function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
 10$^{-6}$, for example,  would ensure a reasonable range of
-neighbours, see \cite{Arroyo2006} for details. This tolerance defines
-the limit values of the influence radius and is used thereafter to
-find the neighbour nodes of a given integration point. Regarding this
-aspect, an crucial consideration for the implementation of the LME
-shape functions in MPM is exposed. To avoid the transference of
-particle information to those nodes fare apart from the particle
-domain $\Omega_p$, a especial treatment of the neighbour nodes for
-those particles close to the boundary is required. It consists in
-select only those nodes which position $\vect{x}_I$ lies inside of the
-domain $\Omega$. This can be performed by employing the nodal
-connectivity of the background mesh. And activating for computing only
-those nodes whose element has a particle inside of it as we can see in
-figure~\ref{fig:Particle-discretization}. 
+neighbours, see \cite{Arroyo2006} for details.
+This tolerance defines the limit values of the influence radius and is used thereafter to
+find the neighbour nodes of a given integration point.
+An aditional remark is that in similariti  to alternative non-polynomial meshfree basis functions, the LME approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem.
+
+This interpolation technique avoid one important shortcoming when using
+GIMP or B-Spline MPM regarding the computational domain boundaries
+Steffen {\it et al.} (2008)\cite{Steffen2008b}. Which is the
+additional considerations in the applications of the boundary
+conditions. This is motivated because of their increased extents, it
+is possible for particles to influence, and be influenced by, nodes
+that lie outside of the simulation domain. Some researchers have solve
+this problems with ``extra'', or the called ``ghost'' nodes by other investigators. Anyway this nodes requires especial treatments similar
+to those employed in the smoothed particle hydrodynamics (SPH), for
+further details see Liu \& Liu (2003)\cite{Liu2003}. The approach here
+described does not requires the employ of this artifacts.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \resizebox{0.7\hsize}{!}{
+  \resizebox{\hsize}{!}{
     \includegraphics[width=\textwidth]{./Figures/Error_evol}
@@
   \subfigure[t = 0 seconds.]{
-    \includegraphics[width=0.32\textwidth]{Figures/Block_LME3_PCE_a_t0}
+    \includegraphics[width=0.3\textwidth]{Figures/Block_LME3_PCE_a_t0}
   }
   \subfigure[t = 5 seconds.]{
-    \includegraphics[width=0.32\textwidth]{Figures/Block_LME3_PCE_b_t025}
+    \includegraphics[width=0.3\textwidth]{Figures/Block_LME3_PCE_b_t025}
   }
   \subfigure[t = 20 seconds]{
-    \includegraphics[width=0.32\textwidth]{Figures/Block_LME3_PCE_c_t1}
+    \includegraphics[width=0.3\textwidth]{Figures/Block_LME3_PCE_c_t1}
   }
@@
 
-% BibTeX users please use one of
-%\bibliographystyle{spbasic}      % basic style, author-year citations
-\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-\bibliography{Biblio}   % name your BibTeX data base
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% name your BibTeX data base
+\bibliography{Biblio/Biblio}
 \end{document}
-% end of file template.tex
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-04-22 _region_.tex
Arreglando liadas

@@
-\message{ !name(main.tex)}%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is a general template file for the LaTeX package SVJour
-% for Springer journals.          Springer Heidelberg 2010/09/16
-%
-% Copy it to a new file with a new name and use it as the basis
-% for your article. Delete % signs as needed.
-%
-% This template includes a few options for different layouts and
-% content for various journals. Please consult a previous issue of
-% your journal as needed.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% First comes an example EPS file -- just ignore it and
-% proceed on the \documentclass line
-% your LaTeX will extract the file if required
-\begin{filecontents*}{example.eps}
-%!PS-Adobe-3.0 EPSF-3.0
-%%BoundingBox: 19 19 221 221
-%%CreationDate: Mon Sep 29 1997
-%%Creator: programmed by hand (JK)
-%%EndComments
-
-gsave
-newpath
-  20 20 moveto
-  20 220 lineto
-  220 220 lineto
-  220 20 lineto
-closepath
-2 setlinewidth
-gsave
-  .4 setgray fill
-grestore
-stroke
-grestore
-\end{filecontents*}
-%
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-% flush right qed marks, e.g. at end of proof
-\smartqed
-
-\usepackage[lofdepth,lotdepth]{subfig}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{subfigure} % subfiguras
-%
-\usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{epstopdf}
-\usepackage{mathrsfs} % para formato de letra
-\usepackage{hyperref}
-\usepackage{enumitem}
-\usepackage{array}
-\usepackage{tabularx}
-\usepackage{supertabular}
-\usepackage{fancyhdr}
-\usepackage{multirow}
+\message{ !name(LME-MPM.tex)}% %%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+% %
+% % This is a general template file for the LaTeX package SVJour
+% % for Springer journals.          Springer Heidelberg 2010/09/16
+% %
+% % Copy it to a new file with a new name and use it as the basis
+% % for your article. Delete % signs as needed.
+% %
+% % This template includes a few options for different layouts and
+% % content for various journals. Please consult a previous issue of
+% % your journal as needed.
+% %
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %
+% % First comes an example EPS file -- just ignore it and
+% % proceed on the \documentclass line
+% % your LaTeX will extract the file if required
+% \begin{filecontents*}{example.eps}
+% %!PS-Adobe-3.0 EPSF-3.0
+% %%BoundingBox: 19 19 221 221
+% %%CreationDate: Mon Sep 29 1997
+% %%Creator: programmed by hand (JK)
+% %%EndComments
+
+% gsave
+% newpath
+%   20 20 moveto
+%   20 220 lineto
+%   220 220 lineto
+%   220 20 lineto
+% closepath
+% 2 setlinewidth
+% gsave
+%   .4 setgray fill
+% grestore
+% stroke
+% grestore
+% \end{filecontents*}
+% %
+% \RequirePackage{fix-cm}
+% %
+% %\documentclass{svjour3}                     % onecolumn (standard format)
+% %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+% %\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+% \documentclass[twocolumn]{svjour3}          % twocolumn
+% %
+% % flush right qed marks, e.g. at end of proof
+% \smartqed
+
+% \usepackage[lofdepth,lotdepth]{subfig}
+% \usepackage{graphicx}
+% \usepackage{subcaption}
+
+% \usepackage{amsmath,amsthm,amssymb}
+
+% \usepackage{amsfonts}
+% \usepackage{epstopdf}
+% \usepackage{mathrsfs} % para formato de letra
+% \usepackage{hyperref}
+% \usepackage{enumitem}
+% \usepackage{array}
+% \usepackage{tabularx}
+% \usepackage{supertabular}
+% \usepackage{fancyhdr}
+% \usepackage{multirow}
+% \usepackage{color}
+% \usepackage{makeidx}
+% \usepackage{setspace}
+% \usepackage{epsfig}
+
+% \usepackage{pgf}
+% % \usepgfplotslibrary{external} 
+% % \tikzexternalize
+
+% %\usepackage{latexsym}
+
+\documentclass[preprint,12pt,a4paper]{elsarticle}
+
+\usepackage{lineno,hyperref}
+\usepackage{float}
+\usepackage{subfig}
 \usepackage{color}
-\usepackage{makeidx}
-\usepackage{xstring}
-\usepackage{setspace}
-\usepackage{epsfig}
-
-\usepackage{pgf}
-% \usepgfplotslibrary{external} 
-% \tikzexternalize
-
-%\usepackage{subfigure}
-\usepackage{preview}
+\usepackage{soul}
+
 % Packages to write pseudo-algorithms %
@@
 
-%
-% Insert the name of "your journal" with
-\journalname{Computational Particle Mechanics}
-%
+\modulolinenumbers[5]
+
+\journalname{Computer Methods in Applied Mechanics and Engineering}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Elsevier bibliography styles
+%%%%%%%%%%%%%%%%%%%%%%%
+%% To change the style, put a % in front of the second line of the current style and
+%% remove the % from the second line of the style you would like to use.
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Numbered
+%\bibliographystyle{model1-num-names}
+
+%% Numbered without titles
+%\bibliographystyle{model1a-num-names}
+
+%% Harvard
+%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
+%% Vancouver numbered
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+
+%% Vancouver name/year
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+
+%% APA style
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+
+%% AMA style
+%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
-\message{ !name(main.tex) !offset(-3) }
-
-% \title{Novel improvements in the Material Point Method to face
-%   dynamic problems: 
-%   Local-maximum entropy approximation and an explicit predictor-corrector scheme. \thanks{Funding: This
-%     study was funded by Agustín de Betancourt Foundation (grant number
-%     262390106114).}
-% }
+\message{ !name(LME-MPM.tex) !offset(-3) }
+
+\begin{frontmatter}
 
 \title{Enhanced Material Point Method to face
-  dynamic problems:\thanks{Funding: This
-    study was funded by Agustín de Betancourt Foundation (grant number
-    262390106114).}
-}
-\subtitle{Local-maximum entropy approximation and explicit
+  dynamic problems: Local-maximum entropy approximation and explicit
   predictor-corrector scheme}
 
-\titlerunning{Novel improvements in the Material Point Method to face
-  dynamic problems.} % if too long for running head
-
-\author{Miguel Molinos \and
-  Pedro Navas \and
-  Manuel Pastor \and
-  Miguel Martín Stickle
-}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-% \institute{Miguel Molinos \at
-%   E.T.S de Ingenieros de Caminos, Canales y Puertos. \\
-%   Universidad Politéctnica de Madrid, 28040 Madrid, Spain \\
-%   \email{m.molinos@alumnos.upm.es}
-%   % \emph{Present address:} of F. Author  %  if needed
-%   \and
-%   Pedro Navas 
-%   \and
-%   Manuel Pastor
-%   \and
-%   Miguel Martín Stickle
-% }
-% \institute{Miguel Molinos, Pedro Navas and Manuel Pastor \at E.T.S
-%   de Ingenieros de Caminos, Canales y Puertos, Universidad Politéctnica de Madrid, 28040 Madrid, Spain, \; \email{m.molinos@outlook.es, pedro.navas@upm.es, manuel.pastor@upm.es}
-% }
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
+%% Group authors per affiliation:
+\author{
+Miguel Molinos$^a$
+Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es},
+Manuel Pastor$^a$
+and Miguel Martín Stickle$^a$ 
+}
+\address{
+  $^a$ ETSI Caminos, Canales y Puertos, Universidad Polit\'ectnica de Madrid.\\ c. Prof. Aranguren 3, 28040 Madrid, Spain
+}
+
 \begin{abstract}
@@
   \centering
-  \resizebox{0.8\hsize}{!}{
+  \resizebox{0.5\hsize}{!}{
     \includegraphics[width=\textwidth]{Figures/Mesh-particles-back}}
@@
   \centering
-  \resizebox{0.8\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/MPM_scheme}
-  }
-  \caption{Description of MPM standard algorithm.}
+  \resizebox{0.5\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/MPM_scheme_horizontal}
+  }
+  \caption{Description of the three steps in MPM standard algorithm.}
   \label{fig:MPM_algorithm}
@@
 over a standard forward Euler. It is summarized in shape of
-pseudo-algorithm \ref{app:explicit-predictor-algorithm}.
-
-\section{Local max-ent approximants}
-\label{sec:local-max-ent}
-The popularity of MPM has increase notoriously during
-the recent years due to its ability to deal with large strain problems
-without mesh distorsion issues inherent to mesh based methods like
-FEM, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations
-made with the original MPM, there are numerical noises when particles
-crossing the cell boundaries. Local maximum-entropy (or
-local \textit{max-ent}) shape function first introduced by Arroyo \&
-Ortiz (2006)\cite{Arroyo2006} has been recently tested under MPM framework
-by Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
-simulations performed with the \textit{max-ent} basis functions show
-considerably more accurate stress approximations for MPM. Although, in
-\cite{Wobbes2020} authors does not deep in how the regularization
-parameter $\beta$ affects to the accuracy and stability of the solution.
-
-The basic idea of the shape functions based on such
-an estimate is to interpret the shape function $N_I(\vec{x})$ as the
-probability of $\vec{x}$ to obtain the value $\vec{x}_I$,  $I=1,
-\dots, n$. Here $n$ is the number of nodes in the domain.
-This approximation scheme represents a optimal compromise, in the sense of
-Pareto, between the \textit{unbiased statistical inference} based on
-the nodal data which leads to the principle of \textit{maximum-entropy}
-stated by Jaynes \cite{Jaynes1957}, and the definition of local shape
-functions of \textit{least width} the least biased shape functions.
-
-Taking the definition of entropy as a measure of how uncertainty a
-random variable is averaged on all its possible outcomes. And adopting
-the Shannon's entropy as the starting point:
-\begin{equation}
-  \label{eq:Shannon-entropy}
-  H(p_1(\vec{x}),\ldots,p_n(\vec{x})) = -\sum^{N_n}_{I=1}{p_I(\vec{x})\log p_I }
-\end{equation}
-where $p_I(\vec{x})$ is the probability, equivalent to the mentioned
-shape function $N_I(\vec{x})$,  satisfying both the zeroth and
-first-order consistency. The least-biased approximation scheme is
-given by
-\begin{align*}
-  \label{eq:least-biased-approximation-scheme}
-  \text{(LME)} \hspace{0.15cm} &\text{Maximize} \hspace{0.15cm} H(p) =
-  -\sum_{I}^{N_n}{p_I(\vec{x})\log p_I }\\
-  &\text{subject to}\
-  \begin{cases}
-    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
-  \end{cases}
-\end{align*}
-The local max-ent approximation schemes (LME) as a Pareto set,
-defined by \cite{Arroyo2006} is as follows
-\begin{align*}
-  \label{eq:LME-scheme-pareto-set}
-  \text{(LME)}_{\beta} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
-  \vec{x} \hspace{0.15cm} \text{minimise} \hspace{0.15cm} f_{\beta}(\vec{x}, p) = \beta H(\vec{x},p) - H(p) \\
-  &\text{subject to}\
-  \begin{cases}
-    p_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I} = 1 \\[1em]   
-    \sum\limits_{I=1}^{N_n}{p_I \vec{x}_I} = \vec{x} \\
-  \end{cases}
-\end{align*}
-for $\beta \in (0,\infty)$ is Pareto optimal. The unique solution of
-the local max-ent problem (LME)$_\beta$ is: 
-\begin{equation}
-  \label{eq:LME-p}
-p(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
-    \vec{\lambda} \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
-\end{equation}
-where
-\begin{equation}
-  \label{eq:LME-Z}
-Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \; |\vec{x}-\vec{x}_I|^2 + \vec{\lambda} \cdot (\vec{x}-\vec{x}_I)  \right]}
-\end{equation}
-being $\vec{\lambda}^*(\vec{x})$ the unique minimiser  for $\log
-Z(\vec{x}, \vec{\lambda})$. In order to obtain the first derivatives of the shape function, it is also necessary to compute~$\nabla p^*_I$ 
-\begin{equation}
-  \label{eq:LME-grad-p}
-\nabla p^*_I=p^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} p^*_J \, \nabla f^*_J\right)
-\end{equation}
-where
-\begin{equation}
-  \label{eq:LME-f}
-f^*_I(\vec{x},  \vec{\lambda},\beta)=-\beta \, |\vec{x}-\vec{x}_I|^2 + \vec{\lambda}   \,  (\vec{x}-\vec{x}_I)
-\end{equation}
-Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression:
-\begin{eqnarray}
-\nabla p^*_I &=& -p^*_I \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I) \label{eq26} 
-\end{eqnarray}
-%&&\mbox{
-where \tens{J} is the Hessian matrix, defined by:
-%} \nonumber \\&& \nonumber \\
-\begin{eqnarray}
-\tens{J}(\vec{x},  \vec{\lambda},\beta) &=& \frac{\partial \vec{r}}{\partial  \vec{\lambda}} \label{eq27} \\ 
-%&& \nonumber \\
-\vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \partial_{\vec{\lambda}}{\log{ Z( \vec{x},\vec{\lambda}})} 
-%\nonumber \\ &=&
-  =\sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I) \label{eq28} 
-\end{eqnarray}
-Note that, the objective of the above procedure is to find the
-$\vec{\lambda}$ which minimises  $\log Z(\vec{x}, \vec{\lambda})$. The
-traditional way to obtain such a minimiser  is using Eq.~(\ref{eq27})
-to calculate small increments of $\partial\vec{\lambda}$ in a
-Newton-Raphson approach. Similar to alternative non-polynomial meshfree basis functions, the
-LME approximation scheme requires more than $d+1$ nodes to determine
-the values of the shape functions as well as their derivatives at any
-point in the convex hull of the nodal set, where $d$ is the dimension
-of the problem. The support size of LME shape functions may be
-controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
-\cite{Arroyo2006} (e.g. two dimensional example shown in figure~\ref{fig:LME_MPM}).
- Since  $p_I$  is defined in the entire domain, in practice, the
-function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
-10$^{-6}$, for example,  would ensure a reasonable range of
-neighbours, see \cite{Arroyo2006} for details. This tolerance defines
-the limit values of the influence radius and is used thereafter to
-find the neighbour nodes of a given integration point. Regarding this
-aspect, an crucial consideration for the implementation of the LME
-shape functions in MPM is exposed. To avoid the transference of
-particle information to those nodes fare apart from the particle
-domain $\Omega_p$, a especial treatment of the neighbour nodes for
-those particles close to the boundary is required. It consists in
-select only those nodes which position $\vect{x}_I$ lies inside of the
-domain $\Omega$. This can be performed by employing the nodal
-connectivity of the background mesh. And activating for computing only
-those nodes whose element has a particle inside of it as we can see in
-figure~\ref{fig:Particle-discretization}. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Particle-discretization}
-  }
-  \caption{This tolerance defines the limit values of the influence
-    radius and is used thereafter to find the neighbour nodes of a
-    given integration point. The picture also shows the neighbourhood
-    criterion to select those node inside of $\Omega$.} 
-  \label{fig:Particle-discretization}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Due to the FE-compatibility, the LME shape function is degenerated to
-linear finite element shape function if $d+1$ neighbouring nodes are
-chosen as the support. Furthermore, with a conveniently adopted
-\textit{regularization} parameter it is possible to get a GIMP-like
-shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}.  
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-  \centering
-  \subfigure[Q4]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun}\\
-      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dx}\\
-      \includegraphics[width=0.16\textwidth]{Figures/MPM_Shape_Fun_dy}
-    \end{tabular}  
-  }
-  \subfigure[$\text{LME}_{17}$]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dx}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_17_3_Shape_Fun_dy}
-    \end{tabular}
-  }
-  \subfigure[uGIMP]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun}\\
-      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dx}\\
-      \includegraphics[width=0.16\textwidth]{Figures/GIMP_Shape_Fun_dy}
-    \end{tabular}
-  }
-  \subfigure[$\text{LME}_{10}$]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dx}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_10_0_Shape_Fun_dy}    
-    \end{tabular}
-  }
-  \subfigure[$\text{LME}_{5}$]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dx}\\
-      \includegraphics[width=0.16\textwidth]{Figures/LME_5_0_Shape_Fun_dy}
-    \end{tabular}
-  }
-  \caption{Comparative of linear piecewise shape functions (Q4) and
-    uniform GIMP shape functions (uGIMP) \textit{versus} Local max-ent
-    shape functions for a two-dimensional arrangement of nodes, and
-    spatial derivatives for several values of $\gamma = \beta/h^2$.}
-  \label{fig:LME_MPM}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
-influence area of the shape function is controlled by the Euclidean
-norm, therefore the search area is geometrically a circle in 2D, or a
-sphere in 3D. Building upon the idea of anisotropic shape functions,
-\cite{Kochmann2019} introduced an enhanced version of the original
-local max-ent scheme, which uses an anisotropic support to deal with
-tensile inestability. Nonetheless this is out of the scope of the
-present document but will be incorporated in future research.
-
-\section{Application to linear elasticity dynamic problems.}
-\label{sec:Application-linear-elasticity-dynamic-problems}
-
-This section is devoted to test the ability of both predictor-corrector
-time integration scheme and the local \textit{max-ent} approximants to
-overcome spurious oscillations due to the grid crossing and high
-frequency loads under the context of MPM Two different test has
-been adopted for this purpose, the benchmark proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995} and the test proposed in the PhD thesis of
-Andersen (2009)\cite{thesis_Andersen_2009}. In all calculations we confine out attention to
-uniformly distribute node and particle sets. The accuracy of the PCE
-scheme is compared to the standard FE. In addition \textit{max-ent} solutions
-are compared with those provided by uGIMP and Q4 shape functions, also
-we compare MPM performance with OTM and FEM. All simulations were
-performed with in-hose software.
-
-\subsection{Dyka bar}
-\label{sec:dyka-bar}
-
-This benchmark was proposed due to its ability to shows the capability
-of the proposed time integration algorithm to avoid velocity
-fields instabilities. It consists in a one-dimensional bar with a
-length of 0.1333 meters, sketched in the
-figure~\ref{fig:Dyka_Bar}. The boundary conditions are in the right
-border displacement are constrained ($\vect{v} \rvert_{x=L} = 0$) and
-in the left displacement are let free ($\tens{\sigma} \rvert_{x=0} =
-0$). And a initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
-last quarter of it. Finally, the elastic parameters consider for this test are:
-\begin{itemize} 
-\item  Density : $7833\ kg/m3$
-\item  Poisson ratio : $0$
-\item  Elastic modulus : $200 \cdot 10^9\ Pa$
-\end{itemize}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \input{Figures/Dyka_bar.tex}}
-  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
-  \label{fig:Dyka_Bar}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this case a duration of 0.0001 seconds for the simulation is
-consider. Therefore, the elastic wave generated travel thorough the bar
-(from A to C and back to A) at least two times. For the spatial
-discretization we propose a set a seven nodal mesh sizes (0.1, 0.3325, 0.5,
-1.0, 3.3325, 6.665, 10.0) in millimeters. For each element a number of
-four particles was selected. In the initial layout, particles are
-occupying the exact quadrature points of a linear quadrilateral. With
-the exception of the uGIMP simulation where gaps or overlap between
-voxels of each particle are not allowed. In those cases, each particles
-occupy the center of each cell quarter. For all simulations, time step
-is controlled by a Courant-Friedrichs-Levy condition of 0.1, were the adopted
-celerity is computed as,
-\begin{equation}
-  \label{eq:Cel}
-  Cel = \max\{\max_{p \in \Omega_p}\{ \vect{v}_p \} , \max_{p \in \Omega_p}\{ \sqrt{\frac{E_p}{\rho_p}} \} \}
-\end{equation}
-A important consideration regarding modellization concerns to the
-background mesh. Notice that free border of the bar has a maximum
-horizontal displacement of 0.03 millimeters, therefore 
-a computational domain with an extra gap of 0.03 millimeters is
-required in order to accommodate the unconstrained displacement of the
-particles in the left border of the bar. Naturally this problem arise
-when the mesh size is small enough that relative displacement of the
-particles are larger then the distance to the border, so grid crossing
-phenomena could appear even in those cases with infinitesimal
-displacements. In this case, an analytical solution is possible
-thought the characteristics method described in the appendix
-\ref{app:analytical_sol}. To measure the convergence of the solutions
-for the different time integration and approximation schemes the
-root-mean-square (RMS) error in the velocity field is computed. RMS
-error is defined as
-\begin{equation}
-  \label{eq:RMS}
-  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
-\end{equation}
-where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
-numerical solutions evaluated in the final time step in the position
-of each particle. A first comparative between both time integration
-scheme is plotted in figure \ref{fig:Dyka-PCE-FE}. It demonstrates the
-superior performance of the PCE \textit{versus} the FE. In the PCE the
-spurious oscillations are quickly mitigated in the first time steps,
-and does not propagate the error in time in opposite to FE where the
-simulation becomes unstable after $6E^{5}$ seconds. Figure
-\ref{fig:Dyka-error-evol} also remarks the remarkable difference
-between both schemes. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_01}
-  }
-  \caption{Comparative of the PCE \textit{versus} the FE. In the
-    picture the velocity evolution at the point in the bar left side
-    is plotted.}
-  \label{fig:Dyka-PCE-FE}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Figure \eqref{fig:Dyka-LME-gamma} shows the sensibility of the LME
-approximation scheme to variations in the a-dimensional parameter
-$\beta$ that controls the value of the regularization parameter
-$\gamma$ depending of the mesh size. As we can see lower values of
-gamma exhibits a behaviour with a soft decay in some parts of the
-simulation due to the increase of nodes adopted to regularize the
-solutions. This capability could be useful in simulations where
-extremely noise oscillations could damage the solutions like memory
-materials. On the other hand larger values of the parameter $\beta$
-makes the solution tend to the linear FEM solution as the athermal
-limit is reached \cite{Arroyo2006}. Intermediate values of the
-regularization parameters give us a compromise between the both
-scenarios here described. An additional observation concerning the
-solution sensibility to regularization parameters occurs when mesh
-size decreases. For larger mesh size where the relative particle displacement
-is negligible in comparison with the cell size, the global behaviour
-is FEM-like, therefore larger values of $\gamma$ has offers better
-results. On the other hand, when mesh size is small enough to produce
-grid-crossing and mesh-free behaviour is required to ensures the
-convergence of the solution, tiny values of $\gamma$ has a better
-performance. Convergence plot in figure \eqref{fig:Dyka-error-evol}
-shows how the slope for the larger values of $\gamma$ decreases
-monotonically with the value of the mesh size, in contrast to larger
-values of it, whose suffers a punishment of the performance when significant
-movement of the particles occurs as far we reduce the mesh size.  
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_LME_gamma_comparative}
-  }
-  \caption{Sensitive of LME approximants performance to changes in the
-    adimensional regularization parameter $\gamma = \beta/h^2$. To
-    illustrate it, the velocity evolution at the point in the bar left side
-    is plotted.}
-  \label{fig:Dyka-LME-gamma}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Figure \ref{fig:Dyka-uGIMP-LME} compares the performance of the
-uGIMP shape function \textit{versus} the LME approximation scheme with
-a adimensional regularization parameter $\gamma$ of 4.0. Although it
-does not shows remarkable differences, LME approximats exhibits a more
-robust behaviour than the uGIMP shape functions. Regarding this, notice
-the absence of uGIMP values for a mesh size of 0.3325 and 0.5
-millimeters. During these simulation the uGIMP suffered an unstable
-increase of the error so we decided to no include this nodes in the
-plot. A feasible explanation for this phenomena could be the presence
-of numerical cancellation which could produce gaps between
-voxels. Further research should be done in this direction for getting
-a better comprehension of this phenomena. In opposite, LME
-approximation does not suffers this phenomena either with irregular
-nodal layout.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_uGIMP_vs_LME_Dyka}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-uGIMP-LME}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Finally, figure \ref{fig:Dyka-OTM-MPM}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
-  }
-  \caption{Velocity evolution at the point in the bar left side.}
-  \label{fig:Dyka-OTM-MPM}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\begin{figure*}\sidecaption
-  \centering
-  \resizebox{0.7\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Error_evol}
-  }
-  \caption{Velocity evolution at the point in the Dyka bar left side,
-    convergence plots for FE and PCE. The plot is subdivided with
-    colours, the darker part of the diagram shows coincides when the
-    relative movement of the particles is large enough to produce the
-    grid crossing phenomena. The lightest part of the diagram
-    coincides when the relative movement of the particles in
-    negligible in comparison with the mesh size. And in the middle
-    region a transition behaviour take place.}
-  \label{fig:Dyka-error-evol}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Andersen block}
-\label{sec:andersen-block}
-
-In order to test the ability of this interpolation technique to deal
-with grid crossing instabilities we will simulate the vertical
-compression of a square block (10 by 10 meters) of soft soil sketched
-in figure~\ref{fig:block} and loaded using an incremental gravitation scheme.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \input{Figures/Block.tex}}
-  \caption{Geometrical description of a soil block }.}
-  \label{fig:block}
-\end{figure}
-
-This test was taken from Andersen (2009)\cite{thesis_Andersen_2009}. The
-elastic parameters consider for this test are: 
-\begin{itemize} 
-\item  Initial density : $6\cdot 10^3\ kg/m^3$
-\item  Poisson ratio : $0$
-\item  Elastic modulus : $5\ MPa$
-\end{itemize}
-The gravity force is a apply as an external force according to the
-equations \eqref{eq:particle_body_forces},
-\eqref{eq:nodal_external_forces}. Using a total time period of T (20
-seconds) to apply the gravity, it is increased from 0 to 9.81$m/s$
-with a sinus function until T/2 and then maintained constant until T
-in order to arrive to a state of equilibrium, 
-\begin{equation}
-  \label{eq:gravity-load-block}
- \mathbf{g}(t) = \left\{
-    \begin{array}{ll}
-      0.5 \mathbf{g} (\sin(\frac{2t \pi}{T} - \frac{\pi}{2})+1)  & \mbox{if } t \leq T/2 \\
-      \mathbf{g} & \mbox{if } t > T/2
-    \end{array}
-  \right.
-\end{equation}
-
-In order to get a stable solution, we will adopt a time step conducted
-by a Courant number of 0.1. On the other hand, the explicit predictor-corrector
-scheme is here employed looking forward getting better results. For the
-initial spatial discretization we will employ four particles per cell
-($\Delta x = 2\ m$). The initial setting of particles inside of the
-cell changes according to the approximation technique adopted. For the
-bi-linear shape functions (Q4) and the LME shape functions, the initial
-position corresponds to the location of the gauss-points in a standard
-quadratic finite element. For the uniform-GIMP (uGIMP) shape function
-the initial position of each particle is located in the center of each
-voxel, due to the fact that in the initial situation, the voxel domain
-should not overlap each others, Steffen {\it et al.}
-(2008)\cite{Steffen2008}. Figure~\ref{fig:vertical-displacement-block}
-shows the vertical displacement evolution of a point in the free
-surface of the block.
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
-  }
-  \caption{Comparative of the vertical displacement evolution in a
-    point located in the free surface employing different
-    interpolation schemes and numerical techniques.} 
-  \label{fig:vertical-displacement-block}
-\end{figure}
-
-As we can see the simulation using the Q4 interpolation technique
-turns out to be unstable and in the second 15 it fails. The uGIMP
-simulation is more stable than the one performed by the Q4. Despite
-this is still unstable and could trigger severe oscillations if we
-pretend to simulate non-linear materials. The LME simulation was
-performed using two kinds of shape functions, one with a low value of
-the dimensionless parameter, $\gamma = 0.8$, and other with a larger
-value of it, $\gamma = 3.0$. Notice that the results are both
-stable, but the larger values of $\gamma$ give us a very stable
-solution. This is due to the fact that with larger value of $\gamma$,
-the shape functions behaves in a similar way to the FEM, which performs
-very accurate in those cases with a reasonable mesh distorsion, and
-with a lower value it behaves in a similar way to the uGIMP. This
-behaviour was noticed previously by \cite{Arroyo2006}, were authors
-highlight how by adjusting the spatial variation of $\beta(\vect{x})$,
-it is possible to select regions of the domain of analysis which are
-treated by finite elements and regions that are treated in the style
-of meshfree methods, with seamless transitions between those regions.
-
-Figure~\ref{fig:Block-LME3} shows the evolution of the vertical stress
-during the loading process. The result is physically realistic as
-stress increments linearly from the top to the bottom of the specimen,
-and the value of the vertical stress in a material point located in
-the bottom of the specimen oscillates centered in $5.2 MPa$, which is
-the analytic value given by $\sigma_{yy} = \rho g h_y$.
-
-\begin{figure}
-  \centering
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[t = 0 seconds.]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_a_t0}
-    \label{fig:Block-LME3-PCE-t0}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[t = 5 seconds.]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_b_t025}
-    \label{fig:Block-LME3-PCE-t025}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \qquad
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \subfloat[t = 20 seconds]{
-    \includegraphics[width=0.8\columnwidth]{Figures/Block_LME3_PCE_c_t1}
-    \label{fig:Block-LME3-PCE-t1}
-  }
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \caption{Vertical normal stress and position of material points
-    during the loading process for a soft soil ($E = 5\ MPa$, $\rho_0
-    = 6\cdot 10^3\ kg/m^3$). Numerical parameters considered for the
-    simulation are : Local \textit{max-ent} shape function $\gamma =3$
-    and explicit PC scheme with CFL 0.1.}
-  \label{fig:Block-LME3}
-\end{figure}
-
-\section{Conclusions}
-\label{sec:conclusions}
-We have developed a new time integration scheme for MPM, and
-proved how local \textit{max-ent} arise as a promising tool to
-overcome the grid-crossing error.
-
-adapt the value of $\beta$ to solve the equations fem-like of
-meshfree-like depending of how behaves the region
-
-This alternative technique overcome the constriction of the GIMP to
-regular mesh.
-
-The time integration here proposed mitigates the presence of wiggles
-and overshot
-
-future research :
-localization of the local max ent
-
-predictor-corrector for high dynamic problems like impact or
-collisions
-
-\begin{acknowledgements}
-If you'd like to thank anyone, place your comments here
-and remove the percent signs.
-\end{acknowledgements}
-
-%
-\section*{Conflict of interest}
-%
-The authors declare that they have no conflict of interest.
-
-\appendix
-
-\section{Explicit predictor-corrector algorithm}
-\label{app:explicit-predictor-algorithm}
+pseudo-algorithm.
 
@@
 \end{algorithm}
+
+\section{Local \textit{max-ent} approximants}
+\label{sec:local-max-ent}
+The popularity of MPM has increase notoriously during
+the recent years due to its ability to deal with large strain problems
+without mesh distorsion issues inherent to mesh based methods like
+FEM, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations
+made with the original MPM, there are numerical noises when particles
+crossing the cell boundaries. Local maximum-entropy (or
+local \textit{max-ent}) shape function first introduced by Arroyo \&
+Ortiz (2006)\cite{Arroyo2006} has been recently tested under MPM framework
+by Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
+simulations performed with the \textit{max-ent} basis functions show
+considerably more accurate stress approximations for MPM. Although, in
+\cite{Wobbes2020} authors does not deep in how the regularization
+parameter $\beta$ affects to the accuracy and stability of the solution.
+The basic idea of the shape functions based on such
+an estimate is to interpret the shape function $N_I(\vec{x})$ as a probability. This allow us to introduce two important limits:
+the principle of maximum-entropy (\textit{max-ent}) statistical
+inference stated by \cite{Jaynes1957}, and the Delaunay triangulation
+which ensures the minimal width of the shape function.
+
+This approximation scheme represents a optimal compromise, in the sense of
+Pareto, between the \textit{unbiased statistical inference} based on
+the nodal data which leads to the principle of \textit{maximum-entropy}
+stated by Jaynes \cite{Jaynes1957}, and the definition of local shape
+functions of \textit{least width} the least biased shape functions.
+
+Taking the definition of entropy as a measure of how uncertainty a
+random variable is averaged on all its possible outcomes. And adopting
+the Shannon's entropy as the starting point:
+\begin{equation}
+  \label{eq:Shannon-entropy}
+  H(p_1(\vec{x}),\ldots,p_n(\vec{x})) = -\sum^{N_n}_{I=1}{p_I(\vec{x})\log p_I }
+\end{equation}
+where $p_I(\vec{x})$ is the probability, equivalent to the mentioned
+shape function $N_I(\vec{x})$, satisfying both the zeroth and
+first-order consistency. The least-biased approximation scheme is
+given by
+\begin{align*}
+  \label{eq:least-biased-approximation-scheme}
+  \text{(LME)} \hspace{0.15cm} &\text{Maximize} \hspace{0.15cm} H(N_I) \equiv
+  -\sum_{I}^{N_n}{N_I(\vec{x})\log N_I }\\
+  &\text{subject to}\
+  \begin{cases}
+    N_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I \vec{x}_I} = \vec{x} \\
+  \end{cases}
+\end{align*}
+On the other hand, we wish to control the width of the shape function and it dacay with distance away from the corresponding nodes.
+To reach to this objective \cite{Arroyo2006} propose the following linear program,
+\begin{align*}
+  \label{eq:RAJAN}
+  \text{(RAJ)} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
+  \vec{x} \hspace{0.15cm} \text{minimize} \hspace{0.15cm} U(\vec{x}_p,N_I) \equiv
+\sum_I N_I |\vec{x}_p - \vec{x}_I |^2\\
+  &\text{subject to}\
+  \begin{cases}
+    N_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I \vec{x}_I} = \vec{x} \\
+  \end{cases}
+\end{align*}
+To reach to a compromise between two competing objectives, a Pareto set is defined by \cite{Arroyo2006} as,
+\begin{align*}
+  \label{eq:LME-scheme-pareto-set}
+  \text{(LME)}_{\beta} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
+  \vec{x} \hspace{0.15cm} \text{minimize} \hspace{0.15cm} f_{\beta}(\vec{x}, N_I) \equiv \beta U(\vec{x},N_I) - H(N_I) \\
+  &\text{subject to}\
+  \begin{cases}
+    N_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I} = 1 \\[1em]   
+    \sum\limits_{I=1}^{N_n}{N_I \vec{x}_I} = \vec{x} \\
+  \end{cases}
+\end{align*}
+The regularization o \textit{thermalization} parameter
+between the two criterion $\beta$ has Pareto optimal values in the range
+$\beta \in (0,\infty)$. The unique solution of
+the local max-ent problem (LME)$_\beta$ is:
+\begin{equation}
+  \label{eq:LME-p}
+N_I^*(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
+    \vec{\lambda}^* \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*)}
+\end{equation}
+where
+\begin{equation}
+  \label{eq:LME-Z}
+Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \; |\vec{x}-\vec{x}_I|^2 + \vec{\lambda} \cdot (\vec{x}-\vec{x}_I)  \right]}
+\end{equation}
+being $\vec{\lambda}^*(\vec{x})$ the unique minimiser for the function $\log
+Z(\vec{x}, \vec{\lambda})$.
+The traditional way to obtain such a minimiser is using Eq.~(\ref{eq:LME-J}) to calculate small increments of $\partial\vec{\lambda}$ in a Newton-Raphson approach.
+Where $\tens{J}$ is the Hessian matrix, defined by:
+\begin{eqnarray}
+  \label{eq:LME-J} 
+  \tens{J}(\vec{x}, \vec{\lambda},\beta) &\equiv& \frac{\partial
+                                                  \vec{r}}{\partial \vec{\lambda}}\\
+  \label{eq:LME-r}
+  \vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \frac{\partial \log{ Z(   \vec{x},\vec{\lambda}})}{\partial \vec{\lambda}}  = \sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I)
+\end{eqnarray}
+In order to obtain the first derivatives of the shape function, it is also necessary to compute~$\nabla N_I^*$
+\begin{equation}
+  \label{eq:LME-grad-p}
+\nabla N_I^* &=& N^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} N^*_J \, \nabla f^*_J\right)
+\end{equation}
+where
+\begin{equation}
+  \label{eq:LME-f}
+f^*_I(\vec{x},  \vec{\lambda},\beta)=-\beta \, |\vec{x}-\vec{x}_I|^2 + \vec{\lambda}   \,  (\vec{x}-\vec{x}_I)
+\end{equation}
+Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression for the gradient of the sahep function.
+\begin{eqnarray}
+\nabla N_I^* &=& -N_I^* \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I) \label{eq26} 
+\end{eqnarray}
+The regularization parameter $\beta$ of LME shape functions may be
+controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
+\cite{Arroyo2006}, where $h$ is defined as a measure of the nodal
+spacing. 
+Since $N_I$ is defined in the entire domain, in practice, the
+function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
+10$^{-6}$, for example,  would ensure a reasonable range of
+neighbours, see \cite{Arroyo2006} for details.
+This tolerance defines the limit values of the influence radius and is used thereafter to
+find the neighbour nodes of a given integration point.
+An aditional remark is that in similariti  to alternative non-polynomial meshfree basis functions, the LME approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem.
+
+This interpolation technique avoid one important shortcoming when using
+GIMP or B-Spline MPM regarding the computational domain boundaries
+Steffen {\it et al.} (2008)\cite{Steffen2008b}. Which is the
+additional considerations in the applications of the boundary
+conditions. This is motivated because of their increased extents, it
+is possible for particles to influence, and be influenced by, nodes
+that lie outside of the simulation domain. Some researchers have solve
+this problems with ``extra'', or the called ``ghost'' nodes by other investigators. Anyway this nodes requires especial treatments similar
+to those employed in the smoothed particle hydrodynamics (SPH), for
+further details see Liu \& Liu (2003)\cite{Liu2003}. The approach here
+described does not requires the employ of this artifacts.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.5\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Particle-discretization}
+  }
+  \caption{This tolerance defines the limit values of the influence
+    radius and is used thereafter to find the neighbour nodes of a
+    given integration point. The picture also shows the neighbourhood
+    criterion to select those node inside of $\Omega$.} 
+  \label{fig:Particle-discretization}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Due to the FE-compatibility, the LME shape function is degenerated to
+linear finite element shape function if $d+1$ neighbouring nodes are
+chosen as the support. Furthermore, with a conveniently adopted
+\textit{regularization} parameter it is possible to get a GIMP-like
+shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}.  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+  \centering
+  \subfigure[Q4]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.14\textwidth]{Figures/MPM_Shape_Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures/MPM_Shape_Fun_dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures/MPM_Shape_Fun_dy}
+    \end{tabular}  
+  }
+  \subfigure[$\text{LME}_{17}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun_dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \subfigure[uGIMP]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.14\textwidth]{Figures/GIMP_Shape_Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures/GIMP_Shape_Fun_dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures/GIMP_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \subfigure[$\text{LME}_{10}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun_dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun_dy}    
+    \end{tabular}
+  }
+  \subfigure[$\text{LME}_{5}$]{
+    \begin{tabular}{c}
+      \includegraphics[width=0.14\textwidth]{Figures/LME_5_0_Shape_Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_5_0_Shape_Fun_dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures/LME_5_0_Shape_Fun_dy}
+    \end{tabular}
+  }
+  \caption{Comparative of linear piecewise shape functions (Q4) and
+    uniform GIMP shape functions (uGIMP) \textit{versus} Local max-ent
+    shape functions for a two-dimensional arrangement of nodes, and
+    spatial derivatives for several values of $\gamma = \beta/h^2$.}
+  \label{fig:LME_MPM}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
+influence area of the shape function is controlled by the Euclidean
+norm, therefore the search area is geometrically a circle in 2D, or a
+sphere in 3D. Building upon the idea of anisotropic shape functions,
+\cite{Kochmann2019} introduced an enhanced version of the original
+local max-ent scheme, which uses an anisotropic support to deal with
+tensile inestability. Nonetheless this is out of the scope of the
+present document but will be incorporated in future research.
+
+\section{Application to linear elasticity dynamic problems.}
+\label{sec:Application-linear-elasticity-dynamic-problems}
+
+This section is devoted to test the ability of both predictor-corrector
+time integration scheme and the local \textit{max-ent} approximants to
+overcome spurious oscillations due to the grid crossing and high
+frequency loads under the context of MPM Two different test has
+been adopted for this purpose, the benchmark proposed by Dyka \& Ingel
+(1995)\cite{Dyka1995} and the test proposed in the PhD thesis of
+Andersen (2009)\cite{thesis_Andersen_2009}. In all calculations we confine out attention to
+uniformly distribute node and particle sets. The accuracy of the PCE
+scheme is compared to the standard FE. In addition \textit{max-ent} solutions
+are compared with those provided by uGIMP and Q4 shape functions, also
+we compare MPM performance with OTM and FEM. All simulations were
+performed with in-hose software.
+
+\subsection{Dyka bar}
+\label{sec:dyka-bar}
+
+This benchmark was proposed due to its ability to shows the capability
+of the proposed time integration algorithm to avoid velocity
+fields instabilities. It consists in a one-dimensional bar with a
+length of 0.1333 meters, sketched in the
+figure~\ref{fig:Dyka_Bar}. The boundary conditions are in the right
+border displacement are constrained ($\vect{v} \rvert_{x=L} = 0$) and
+in the left displacement are let free ($\tens{\sigma} \rvert_{x=0} =
+0$). And a initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
+last quarter of it. Finally, the elastic parameters consider for this test are:
+\begin{itemize} 
+\item  Density : $7833\ kg/m3$
+\item  Poisson ratio : $0$
+\item  Elastic modulus : $200 \cdot 10^9\ Pa$
+\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \input{Figures/Dyka_bar.tex}}
+  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
+  \label{fig:Dyka_Bar}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this case a duration of 0.0001 seconds for the simulation is
+consider. Therefore, the elastic wave generated travel thorough the bar
+(from A to C and back to A) at least two times. For the spatial
+discretization we propose a set a seven nodal mesh sizes (0.1, 0.3325, 0.5,
+1.0, 3.3325, 6.665, 10.0) in millimeters. For each element a number of
+four particles was selected. In the initial layout, particles are
+occupying the exact quadrature points of a linear quadrilateral. With
+the exception of the uGIMP simulation where gaps or overlap between
+voxels of each particle are not allowed. In those cases, each particles
+occupy the center of each cell quarter. For all simulations, time step
+is controlled by a Courant-Friedrichs-Levy condition of 0.1, were the adopted
+celerity is computed as,
+\begin{equation}
+  \label{eq:Cel}
+  Cel = \max\{\max_{p \in \Omega_p}\{ \vect{v}_p \} , \max_{p \in \Omega_p}\{ \sqrt{\frac{E_p}{\rho_p}} \} \}
+\end{equation}
+A important consideration regarding modellization concerns to the
+background mesh. Notice that free border of the bar has a maximum
+horizontal displacement of 0.03 millimeters, therefore 
+a computational domain with an extra gap of 0.03 millimeters is
+required in order to accommodate the unconstrained displacement of the
+particles in the left border of the bar. Naturally this problem arise
+when the mesh size is small enough that relative displacement of the
+particles are larger then the distance to the border, so grid crossing
+phenomena could appear even in those cases with infinitesimal
+displacements.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{figure*}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Error_evol}
+  }
+  \caption{Velocity evolution at the point in the Dyka bar left side,
+    convergence plots for FE and PCE. The plot is subdivided with
+    colours, the darker part of the diagram shows coincides when the
+    relative movement of the particles is large enough to produce the
+    grid crossing phenomena. The lightest part of the diagram
+    coincides when the relative movement of the particles in
+    negligible in comparison with the mesh size. And in the middle
+    region a transition behaviour take place.}
+  \label{fig:Dyka-error-evol}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this case, an analytical solution is possible
+thought the characteristics method described in the appendix
+\ref{app:analytical_sol}. To measure the convergence of the solutions
+for the different time integration and approximation schemes the
+root-mean-square (RMS) error in the velocity field is computed. RMS
+error is defined as
+\begin{equation}
+  \label{eq:RMS}
+  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
+\end{equation}
+where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
+numerical solutions evaluated in the final time step in the position
+of each particle. A first comparative between both time integration
+scheme is plotted in figure \ref{fig:Dyka-PCE-FE}. It demonstrates the
+superior performance of the PCE \textit{versus} the FE. In the PCE the
+spurious oscillations are quickly mitigated in the first time steps,
+and does not propagate the error in time in opposite to FE where the
+simulation becomes unstable after $6E^{5}$ seconds. Figure
+\ref{fig:Dyka-error-evol} also remarks the remarkable difference
+between both schemes. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.9\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_01}
+  }
+  \caption{Comparative of the PCE \textit{versus} the FE. In the
+    picture the velocity evolution at the point in the bar left side
+    is plotted.}
+  \label{fig:Dyka-PCE-FE}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Figure \eqref{fig:Dyka-LME-gamma} shows the sensibility of the LME
+approximation scheme to variations in the a-dimensional parameter
+$\beta$ that controls the value of the regularization parameter
+$\gamma$ depending of the mesh size. As we can see lower values of
+gamma exhibits a behaviour with a soft decay in some parts of the
+simulation due to the increase of nodes adopted to regularize the
+solutions. This capability could be useful in simulations where
+extremely noise oscillations could damage the solutions like memory
+materials. On the other hand larger values of the parameter $\beta$
+makes the solution tend to the linear FEM solution as the athermal
+limit is reached \cite{Arroyo2006}. Intermediate values of the
+regularization parameters give us a compromise between the both
+scenarios here described. An additional observation concerning the
+solution sensibility to regularization parameters occurs when mesh
+size decreases. For larger mesh size where the relative particle displacement
+is negligible in comparison with the cell size, the global behaviour
+is FEM-like, therefore larger values of $\gamma$ has offers better
+results. On the other hand, when mesh size is small enough to produce
+grid-crossing and mesh-free behaviour is required to ensures the
+convergence of the solution, tiny values of $\gamma$ has a better
+performance. Convergence plot in figure \eqref{fig:Dyka-error-evol}
+shows how the slope for the larger values of $\gamma$ decreases
+monotonically with the value of the mesh size, in contrast to larger
+values of it, whose suffers a punishment of the performance when significant
+movement of the particles occurs as far we reduce the mesh size.  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.9\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_LME_gamma_comparative}
+  }
+  \caption{Sensitive of LME approximants performance to changes in the
+    adimensional regularization parameter $\gamma = \beta/h^2$. To
+    illustrate it, the velocity evolution at the point in the bar left side
+    is plotted.}
+  \label{fig:Dyka-LME-gamma}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Figure \ref{fig:Dyka-uGIMP-LME} compares the performance of the
+uGIMP~\cite{Bardenhagen2004} shape function \textit{versus} the LME approximation scheme with
+a adimensional regularization parameter $\gamma$ of 4.0. Although it
+does not shows remarkable differences, LME approximats exhibits a more
+robust behaviour than the uGIMP shape functions. Regarding this, notice
+the absence of uGIMP values for a mesh size of 0.3325 and 0.5
+millimeters. During these simulation the uGIMP suffered an unstable
+increase of the error so we decided to no include this nodes in the
+plot. A feasible explanation for this phenomena could be the presence
+of numerical cancellation which could produce gaps between
+voxels. Further research should be done in this direction for getting
+a better comprehension of this phenomena. In opposite, LME
+approximation does not suffers this phenomena either with irregular
+nodal layout.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.9\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_uGIMP_vs_LME_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-uGIMP-LME}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Finally, figure \ref{fig:Dyka-OTM-MPM} compares the solution obtained
+with OTM~\cite{Li2010} \textit{versus} the solution obtained with MPM,
+both with same time integration scheme and spatial discretization. For
+this case the performance of MPM is robust and stable than OTM. As we
+can appreciate, during the first half of the simulation both method
+seem to perform in a similar way, but during the second half of the
+simulation after the elastic wave has travel from the free border to
+the fixed one and back, in OTM the solution becomes noisy than the
+one performed by MPM.  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.9\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
+  }
+  \caption{Velocity evolution at the point in the bar left side.}
+  \label{fig:Dyka-OTM-MPM}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Andersen block}
+\label{sec:andersen-block}
+
+In order to test the ability of this interpolation technique to deal
+with grid crossing instabilities we will simulate the vertical
+compression of a square block (10 by 10 meters) of soft soil sketched
+in figure~\ref{fig:block} and loaded using an incremental gravitation
+scheme.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{0.7\hsize}{!}{
+    \input{Figures/Block.tex}}
+  \caption{Geometrical description of a soil block }.}
+  \label{fig:block}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+This test was taken from PhD thesis of Andersen (2009)\cite{thesis_Andersen_2009}. The
+elastic parameters consider for this test are: 
+\begin{itemize} 
+\item  Initial density : $6\cdot 10^3\ kg/m^3$
+\item  Poisson ratio : $0$
+\item  Elastic modulus : $5\ MPa$
+\end{itemize}
+The gravity force is a apply as an external force according to the
+equations \eqref{eq:particle_body_forces},
+\eqref{eq:nodal_external_forces}. Using a total time period of T (20
+seconds) to apply the gravity, it is increased from 0 to 9.81$m/s$
+with a sinus function until T/2 and then maintained constant until T
+in order to arrive to a state of equilibrium, 
+\begin{equation}
+  \label{eq:gravity-load-block}
+ \mathbf{g}(t) = \left\{
+    \begin{array}{ll}
+      0.5 \mathbf{g} (\sin(\frac{2t \pi}{T} - \frac{\pi}{2})+1)  & \mbox{if } t \leq T/2 \\
+      \mathbf{g} & \mbox{if } t > T/2
+    \end{array}
+  \right.
+\end{equation}
+In order to get a stable solution, we will adopt a time step conducted
+by a Courant number of 0.1. On the other hand, the explicit predictor-corrector
+scheme is here employed looking forward getting better results. For the
+initial spatial discretization we will employ four particles per cell
+($\Delta x = 2\ m$). The initial setting of particles inside of the
+cell changes according to the approximation technique adopted. For the
+bi-linear shape functions and the LME approximants, the initial
+position corresponds to the location of the gauss-points in a standard
+quadratic finite element. For the uGIMP shape function the initial
+position of each particle is located in the center of each voxel, due
+to the fact that in the initial situation, the voxel domain should not
+overlap each others.
+
+Figure~\ref{fig:Block-LME3} shows the evolution of the vertical stress
+during the loading process. The result is physically realistic as
+stress increments linearly from the top to the bottom of the specimen,
+and the value of the vertical stress in a material point located in
+the bottom of the specimen oscillates centered in $5.2 MPa$, which is
+the analytic value given by $\sigma_{yy} = \rho g h_y$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+  \centering
+  \subfigure[t = 0 seconds.]{
+    \includegraphics[width=0.3\textwidth]{Figures/Block_LME3_PCE_a_t0}
+  }
+  \subfigure[t = 5 seconds.]{
+    \includegraphics[width=0.3\textwidth]{Figures/Block_LME3_PCE_b_t025}
+  }
+  \subfigure[t = 20 seconds]{
+    \includegraphics[width=0.3\textwidth]{Figures/Block_LME3_PCE_c_t1}
+  }
+  \caption{Vertical normal stress and position of material points
+    during the loading process for a soft soil ($E = 5\ MPa$, $\rho_0
+    = 6\cdot 10^3\ kg/m^3$). Numerical parameters considered for the
+    simulation are : Local \textit{max-ent} shape function $\gamma =3$
+    and explicit PC scheme with CFL 0.1.}
+  \label{fig:Block-LME3}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Figure~\ref{fig:vertical-displacement-block} shows the vertical
+displacement evolution of a point in the free surface of the block. As
+we can see the simulation using the Q4 interpolation technique turns
+out to be unstable and in the second 15 it fails. The uGIMP simulation
+is more stable than the one performed by the Q4. Despite this is still
+unstable and could trigger severe oscillations if we pretend to
+simulate non-linear materials. The LME simulation was performed using
+two kinds of shape functions, one with a low value of the
+dimensionless parameter, $\gamma = 0.8$, and other with a larger value
+of it, $\gamma = 3.0$. Notice that the results are both stable, but
+the larger values of $\gamma$ give us a very stable solution. This is
+due to the fact that with larger value of $\gamma$, the shape
+functions behaves in a similar way to the FEM, which performs very
+accurate in those cases with a reasonable mesh distorsion, and with a
+lower value it behaves in a similar way to the uGIMP. This behaviour
+was noticed previously by \cite{Arroyo2006}, were authors highlight
+how by adjusting the spatial variation of $\beta(\vect{x})$, it is
+possible to select regions of the domain of analysis which are treated
+by finite elements and regions that are treated in the style of
+meshfree methods, with seamless transitions between those regions. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
+  }
+  \caption{Comparative of the vertical displacement evolution in a
+    point located in the free surface employing different
+    interpolation schemes and numerical techniques.} 
+  \label{fig:vertical-displacement-block}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusions}
+\label{sec:conclusions}
+We have developed a novel time integration scheme for MPM, and
+proved how local \textit{max-ent} approximation scheme could be
+employed as an useful technique in MPM. The PCE arise as a highly
+efficient alternative for challenging dynamic problems like coupled
+$u-p_w$ without appeal to expensive implicit time integration
+algorithms. Also the procedure employed to design the PCE algorithm open
+the door to revisit a huge variety of time integration schemes
+developed originally for FEM, which can be rearranged to MPM framework
+with some modifications. Anyway, further research should be done to improve the
+formal comprehension of the algorithm good performance. This paper
+also enhances the suitability of the local \textit{max-ent} as a
+general promising alternative to the wide range of approximation.
+techniques developed for the MPM to overcome grid crossing
+limitations and to avoid the constriction of the uGIMP of a regular mesh
+or a high density of particles per cell. Future research of the
+group will be on the employ of this scheme to improve the localization
+capabilities of MPM for viscoplastic materials. Finally we remark on
+the possibility of adapting the function $\beta(\vect{x})$ as a second
+order tensor with the aim of adapt the shape function with the strain field which improves the
+performance of it in the aforementioned localization
+capabilities. Other possibility is to adapt the value of $\beta$ to
+solve the equations fem-like of meshfree-like depending of how behaves
+the region, this could be extremely useful in simulating all together
+initialization and propagation of fast landslides.
+
+\begin{acknowledgements}
+If you'd like to thank anyone, place your comments here
+and remove the percent signs.
+\end{acknowledgements}
+
+% 
+\section*{Conflict of interest}
+%
+The authors declare that they have no conflict of interest.
+
+\appendix
 
@@
 %%% End:
-
-\message{ !name(main.tex) !offset(-1619) }
+\message{ !name(LME-MPM.tex) !offset(-1635) }

### 2020-04-22 Figures/Damage_graph.py

@@ -1,13 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-xi = np.linspace(0,1)
-f = 1 - xi
-
-fig, ax = plt.subplots()
-ax.set_xlim(0,1.2)
-ax.set_ylim(0,1.2)
-ax.plot(xi,f)
-
-plt.show()
-

### 2020-04-25 LME-MPM.tex
Cambios 24-4-2020

@@
-% %%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-% %
-% % This is a general template file for the LaTeX package SVJour
-% % for Springer journals.          Springer Heidelberg 2010/09/16
-% %
-% % Copy it to a new file with a new name and use it as the basis
-% % for your article. Delete % signs as needed.
-% %
-% % This template includes a few options for different layouts and
-% % content for various journals. Please consult a previous issue of
-% % your journal as needed.
-% %
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %
-% % First comes an example EPS file -- just ignore it and
-% % proceed on the \documentclass line
-% % your LaTeX will extract the file if required
-% \begin{filecontents*}{example.eps}
-% %!PS-Adobe-3.0 EPSF-3.0
-% %%BoundingBox: 19 19 221 221
-% %%CreationDate: Mon Sep 29 1997
-% %%Creator: programmed by hand (JK)
-% %%EndComments
-
-% gsave
-% newpath
-%   20 20 moveto
-%   20 220 lineto
-%   220 220 lineto
-%   220 20 lineto
-% closepath
-% 2 setlinewidth
-% gsave
-%   .4 setgray fill
-% grestore
-% stroke
-% grestore
-% \end{filecontents*}
-% %
-% \RequirePackage{fix-cm}
-% %
-% %\documentclass{svjour3}                     % onecolumn (standard format)
-% %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-% %\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-% \documentclass[twocolumn]{svjour3}          % twocolumn
-% %
-% % flush right qed marks, e.g. at end of proof
-% \smartqed
-
-% \usepackage[lofdepth,lotdepth]{subfig}
-% \usepackage{graphicx}
-% \usepackage{subcaption}
-
-% \usepackage{amsmath,amsthm,amssymb}
-
-% \usepackage{amsfonts}
-% \usepackage{epstopdf}
-% \usepackage{mathrsfs} % para formato de letra
-% \usepackage{hyperref}
-% \usepackage{enumitem}
-% \usepackage{array}
-% \usepackage{tabularx}
-% \usepackage{supertabular}
-% \usepackage{fancyhdr}
-% \usepackage{multirow}
-% \usepackage{color}
-% \usepackage{makeidx}
-% \usepackage{setspace}
-% \usepackage{epsfig}
-
-% \usepackage{pgf}
-% % \usepgfplotslibrary{external} 
-% % \tikzexternalize
-
-% %\usepackage{latexsym}
-
 \documentclass[preprint,12pt,a4paper]{elsarticle}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Init glossaries
+\usepackage[acronym]{glossaries}
+
+\makeglossaries
+
+\newglossaryentry{domain}
+{
+  name=$\varOmega$,
+  description={Continuum domain}
+}
+
+\newglossaryentry{contour}
+{
+  name=$\partial\varOmega$,
+  description={Boundary of the continuum domain $\varOmega$. Also
+    defined as $\Gamma$}
+}
+
+\newglossaryentry{dirichlet-boundary}
+{
+  name=$ \Gamma_d$,
+  description={Essential or Dirichlet boundary conditions over $\partial\varOmega$}
+}
+
+\newglossaryentry{neumann-boundary}
+{
+  name=$ \Gamma_n$,
+  description={Natural or Nemann boundary conditions over $\partial\varOmega$}
+}
+
+\newglossaryentry{rho}
+{
+  name=$\rho$,
+  description={Describes the scalar density field}
+}
+
+\newglossaryentry{a}
+{
+  name=$\vect{a}$,
+  description={First order tensor which describes the acceleration field}
+}
+
+\newglossaryentry{v}
+{
+  name=$\vect{v}$,
+  description={First order tensor which describes the velocity field}
+}
+
+\newglossaryentry{u}
+{
+  name=$\vect{u}$,
+  description={First order tensor which describes the displacement field}
+}
+
+\newglossaryentry{x}
+{
+  name=$\vect{x}$,
+  description={First order tensor which describes the global coordinates field}
+}
+
+\newglossaryentry{xi}
+{
+  name=$\vect{\xi}$,
+  description={First order tensor which describes the local coordinates field}
+}
+
+\newglossaryentry{stress}
+{
+  name=$\tens{\sigma}$,
+  description={Second order tensor which means the Cauchy stress tensor}
+}
+
+\newglossaryentry{strain}
+{
+  name=$\tens{\varepsilon}$,
+  description={Second order tensor which means the Cauchy strain tensor}
+}
+
+\newglossaryentry{Constitutive}
+{
+  name=$\tens{D}$,
+  description={Four order tensor which means the constitutive response
+    of the material}
+}
+
+\newglossaryentry{LME-beta}
+{
+  name=$\beta$,
+  description={Regularization or thermalization parameter of the
+    LME$_{\beta}$ Pareto set}
+}
+
+\newacronym{mpm}{MPM}{Material Point Method}
+\newacronym{otm}{OTM}{Optimal Transportation Meshfree}
+\newacronym{sph}{SPH}{Smoothed Particle Hydrodynamics}
+\newacronym{fem}{FEM}{Finite Element Method}
+\newacronym{lme}{LME}{Local Maximum-Entropy}
+\newacronym{flip}{FLIP}{Fluid Implicit Particle}
+\newacronym{gimp}{GIMP}{Generalized Interpolation Material Point}
+\newacronym{igimp}{iGIMP}{Implicit GIMP}
+\newacronym{ugimp}{uGIMP}{Uniform GIMP}
+\newacronym{ddmp}{DDMP}{Dual Domain Material Point}
+\newacronym{ctls}{CTLS}{Conservative Taylor Least Squares}
+\newacronym{npc}{NPC}{Newmark Predictor-Corrector}
+\newacronym{fe}{FE}{Forward Euler}
+
+% End glossaries
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \modulolinenumbers[5]
@@
 \begin{abstract}
-  Material Point Method (MPM) has arisen in the recent years as an
-  alternative to Finite Element Method (FEM) under the large
+  \acrfull{mpm} has arisen in the recent years as an
+  alternative to \acrfull{fem} under the large
   deformation regime. However, the simulation of shock waves
   propagation and other high frequency problems is still challenging
-  under this approach due the incapability of the standard MPM time
+  under this approach due the incapability of the standard \acrshort{mpm} time
   integration scheme to filter spurious noises. To overcome this
-  limitation in this paper, an explicit predictor-corrector time integration scheme has been proposed. Its superior performance mitigates the 
-  presence of spurious oscillations with minimal dissipation in high
-  frequency problems. Other source of numerical noise in MPM 
+  limitation in this paper, an explicit predictor-corrector time
+  integration scheme has been proposed. Its superior performance
+  mitigates the presence of spurious oscillations with minimal dissipation in high
+  frequency problems. Other source of numerical noise in \acrshort{mpm} 
   occurs when to material points cross computational grid
@@
   the solution in one case, or damage it in another. To overcome it,
-  this document adopts the \textit{local maximum-entropy approximation
-    schemes} (LME) a robust substitute for the wide range of shape
-  function in MPM. Local \textit{max-ent} approximation may be regarded as a
-  \textit{thermalization} of Delaunay triangulation which resolves the
+  this document adopts the \acrfull{lme} approximation schemes a
+  robust substitute for the wide range of shape function in
+  \acrshort{mpm}. \acrshort{lme} approximation may be regarded
+  as a \textit{thermalization} of Delaunay triangulation which resolves the
   degenerate cases resulting from the lack or uniqueness of the
@@
 \begin{keyword}
-  LME \sep MPM \sep Explicit predictor-corrector \sep Dynamic problems}
+  \acrshort{lme} \sep \acrshort{mpm} \sep Explicit predictor-corrector \sep Dynamic problems}
 \end{keyword}
@@
 \label{intro}
-Since the proposal of MPM by Sulsky {\it  et al.}
-(1994)~\cite{Sulsky1994} as a generalization to solids of the Fluid
-Implicit Particle (FLIP) method~\cite{Brackbill1986}. It popularity
+Since the proposal of \acrshort{mpm} by Sulsky {\it  et al.}
+(1994)~\cite{Sulsky1994} as a generalization to solids of the \acrfull{flip} method~\cite{Brackbill1986}. It popularity
 has increased due to its ability to deal with large strain regime
@@
 development of other interpolation techniques to overcome this
-limitation such as the generalized interpolation material point method
-(GIMP) Bardenhagen \& Kober (2004)~\cite{Bardenhagen2004}, which has
+limitation such as the \acrfull{gimp} method Bardenhagen \& Kober
+(2004)~\cite{Bardenhagen2004}, which has
 demonstrate to have a good performance in the finite deformation
@@
 encountered by the finite element methods due to element distortion.
-A more robust alternative is the dual domain material point method
-(DDMP) proposed by Zhang {\it et al.}
+A more robust alternative is the \acrfull{ddmp} method proposed by Zhang {\it et al.}
 (2011)~\cite{Zhang2011a}. Unfortunately this method shows an
 unsatisfactory behaviour when particle/cell ratio
-decreases~\cite{DHAKAL2016301}, therefore DDMP requires a large number
+decreases~\cite{DHAKAL2016301}, therefore \acrshort{ddmp} requires a large number
 of particles needed for convergence, this
@@
 spline-lines has gain popularity with the introduction of the B-Spline
-MPM proposed by Roel Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
+\acrshort{mpm} proposed by Roel Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
 this technique allows the employ of unstructured set of notes and
 particles. More recently, approximants derived from minimization has
-been introduced in to MPM framework with the Conservative Taylor
-Least Squares (CTLS) reconstruction proposed by Wobbes {\it et al.}
+been introduced in to \acrshort{mpm} framework with the \acrfull{ctls}
+reconstruction proposed by Wobbes {\it et al.}
 (2018)~\cite{E_Wobbes_2018}, unfortunately when particles are spread in
-a challenging way, the quality of the CTLS approximation decrease
+a challenging way, the quality of the \acrshort{ctls} approximation decrease
 locally.
 
-This document adopts the \textit{local maximum-entropy approximation
-    schemes} (LME) as a robust substitute for the wide range of shape
-  function in MPM. First introduced by Arroyo \& Ortiz
+This document adopts the \acrshort{lme} or local \textit{max-ent} as a robust substitute for the
+wide range of shape function in \acrshort{mpm}. First introduced by Arroyo \& Ortiz
 (2006)~\cite{Arroyo2006}, it belongs to the class of convex 
 approximation schemes and provides a seamless transition between
-finite element method (FEM) and mesh-free interpolations. The
+\acrshort{fem} and mesh-free interpolations. The
 approximation scheme is based on a compromise between minimizing the
@@
 (2018)~\cite{Navas2018a} and Li {\it et al.} (2012)~\cite{Li2012} for
-Optimal Transportation Meshfree (OTM) method. And more
-recently under MPM framework by Wobbes {\it et
+\acrfull{otm} method. And more
+recently under \acrshort{mpm} framework by Wobbes {\it et
   al.}(2020)~\cite{Wobbes2020} but without exploring the benefits of
-the regularization parameter $\beta$.
+the regularization parameter \gls{LME-beta}.
 
@@
 filtering them or increasing the accuracy of the time integration
-scheme. One of the most popular is the implicit GIMP (iGIMP)
+scheme. One of the most popular is the \acrfull{igimp}
 Charlton {\it et al.} (2017)~\cite{Charlton2017}, more recently Tran \&
 Solowski (2019)~\cite{Tran2019e} proposed a generalised-$\alpha$ scheme
-for MPM with promising results but at the expense of increasing
+for \acrshort{mpm} with promising results but at the expense of increasing
 the computational effort. In this paper a less time consuming and high
 efficient explicit predictor corrector integration method has been
-proposed. It consists in an accommodation of the Newmark
-predictor-corrector or central difference explicit (CD). We have
-choose this method among other suitable alternatives as those proposed
+proposed. It consists in an accommodation of the \acrsull{npc}. This method
+has been chosen among other suitable alternatives as those proposed
 by Wilson {\it et al.} (1972)~\cite{Wilson1972} or Chung \& Hulbert
@@
 inaccuracies in both space and time discretization by the employ of a
-suitable combination of the maximum-entropy (or local
-\textit{max-ent}) family shape functions, and the proposal of
-a explicit predictor-corrector scheme. We illustrate the advantages of
-this approach thorough to simple but challenging test cases, like the
+suitable combination of the \acrshort{lme} family shape functions, and the proposal of
+a explicit predictor-corrector scheme. The advantages of
+this approach will be illustrated thorough to simple but challenging test cases, like the
 propagation of shock waves in a elastic bar or the response of a block of soil
@@
 
-The article is organized as follows. Section \ref{sec:Notation}
-briefly reviews the notation here employed. Next, Section \ref{sec:derivation-mpm}
-is devoted to present briefly the governing equations of the elastic
-problem, the variational formulation and the Galerkin procedure. In Section \ref{sec:epc-algor-mpm} an explicit predictor-corrector
-time integration scheme for MPM is proposed. Section
-\ref{sec:local-max-ent} briefly reviews the local \textit{max-ent}
-basis functions here employed. In Section
+The article is organized as follows. Section \ref{sec:meshfree-methodology}
+is devoted to describe the meshfree methodology adopted in this
+research, first \acrshort{mpm} procedure is introduced in
+\ref{sec:derivation-mpm}, second the explicit predictor-corrector
+time integration scheme is presented in \ref{sec:epc-algor-mpm}, and
+third \acrshort{lme} approximation scheme will be introduced in
+\ref{sec:local-max-ent}. In Section
 \ref{sec:Application-linear-elasticity-dynamic-problems} applications
-to prove the numerical accuracy of the proposed approach are presented. Finally,
-conclusions and future research topics are exposed in Section \ref{sec:conclusions}.
-
-\section{Brief note concerning the notation}
-\label{sec:Notation}
-In what follows, we will adopt the following convention. All the
-physical variables involved in this problem are collected in Table
-\ref{tab:notation-table}. Three kind of subscript or superscript are used within paper. The subscript$\qed_p$ is used to define a particle variable. While the
-subscript$\qed_I$ is reserved in this notation for denoting nodal
-variables. And finally, the superscript $\qed^{\psi}$ involves a
-virtual magnitude. For the operators, the convention is : $\dot{\qed}$ and
-$\ddot{\qed}$ for the first and second time derivative, $\qued \otimes
-\qued$ means the dyadic operator, $(\cdot)$ and $(\colon)$ means the first and second contraction of a tensor, $\Div{\qed}$ denotes the
-divergence operator, and finally $\Grad{\qed}$ and $\GradS{\qed}$
+to prove the numerical accuracy of the proposed approach are
+presented. Finally, conclusions and future research topics are exposed in Section \ref{sec:conclusions}.
+
+\section{The meshfree methodology}
+\label{sec:meshfree-methodology}
+
+The aim of this section is to provide an overview of the standard
+explicit \acrshort{mpm} algorithm~\cite{Sulsky1994}. Without loosing
+generality, the method has three main steps: (i) a
+variational recovery process, where particle data is projected to the
+grid nodes, (ii) an Eulerian step, where balance of momentum equation
+is expressed as a nodal equilibrium equation thorough a \acrshort{fem}-like
+procedure, and finally (iii) a Lagrangian advection of the
+particles. In consequence \acrshort{mpm} can be regarded as a
+Lagrangian-Eulerian method where particles carries on all the physical
+information and a set of background nodes is employed to
+compute the equilibrium equation. In what follows, we will adopt the
+following convention. Three kind of subscript or superscript are used
+within paper. The subscript $\Box_p$ is used to define a particle
+variable. While the subscript $\Box_I$ is reserved in this notation for denoting nodal
+variables. And finally, the superscript $\Box^{\psi}$ involves a
+virtual magnitude. For the operators, the convention is : $\dot{\Box}$ and
+$\ddot{\Box}$ for the first and second time derivative, $\qued \otimes
+\qued$ means the dyadic operator, $\Box \cdot \Box$ and $\Box \colon \Box$ means the
+first and second contraction of a tensor, $\Div{\Box}$ denotes the
+divergence operator, and finally $\Grad{\Box}$ and $\GradS{\Box}$
 denotes the gradient and its symmetric part. Einstain subscripts
 convention is adopted therefore repeated index means addition.
-\begin{table}
-  \centering
-  \caption{Physical variables involved in the problem}
-  \label{tab:notation-table}
-  \begin{tabular}{c c c}
-    $\rho$ & Density field & Scalar \\
-    $\vect{a}$ & Acceleration field & First order tensor \\
-    $\vect{v}$ & Velocity field & First order tensor \\
-    $\vect{u}$ & Displacement field & First order tensor \\
-    $\vect{x}$ & Global coordinates & First order tensor \\
-    $\vect{\xi}$ & Local coordinates & First order tensor \\
-    $\tens{\sigma}$ & Cauchy stress tensor & Second order tensor \\
-    $\tens{\varepsilon}$ & Cauchy strain tensor & Second order tensor \\
-    $\tens{D}$ & Constitutive tensor & Fourth order tensor\\
-  \end{tabular}
-\end{table}
-
-\section{Derivation of MPM procedure}
+
+\subsection{Derivation of MPM procedure}
 \label{sec:derivation-mpm}
-The aim of this section is to provide an overview of the standard
-explicit MPM algorithm~\cite{Sulsky1994}. In consequence it
-is structured as follows: the governing equations will be introduced
-in \ref{sec:The boundary-value-problem}, later the variational statement of
-the problem will be presented \ref{sec:variational-formulation}, and
-finally a discretization procedure thorough Galerkin is performed in
-\ref{sec:Galerkin-procedure}. The method has three main steps: (i) a
-variational recovery process, where particle data is projected to the
-grid nodes, (ii) an Eulerian step, where balance of momentum equation
-is expressed as a nodal equilibrium equation thorough a FEM-like
-procedure, and finally (iii) a Lagrangian advection of the
-particles. In consequence MPM can be regarded as a
-Lagrangian-Eulerian method where particles carries on all the physical
-information and a set of background nodes is employed to
-compute the equilibrium equation.
-
-\subsection{The boundary-value problem}
-\label{sec:The boundary-value-problem}
-In MPM the continuum mechanics approach is considered. So on, let
-define a continuum domain $\varOmega$ occupied by an elastic body like
-the sketched in the figure~\ref{fig:Continuum-solid}, and $\partial
-\varOmega$ the boundaries of the domain defined by $\partial \varOmega
+
+In \acrshort{mpm} the continuum mechanics approach is considered. So on, let
+define a continuum \gls{domain}  occupied by an elastic body like
+the sketched in the figure~\ref{fig:Continuum-solid}, and \gls{contour} the boundaries of the domain defined by $\partial \varOmega
 = \Gamma_d \bigcup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n = \emptyset$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this context the field $\vect{u}$ allows to describe the \textit{global state}
+In this context the field \gls{u} allows to describe the \textit{global state}
 of the system. Now the variable $\phi =
@@
   states} at any point of the continuum which can be derived from the
-field $\vect{u}$ through the following set of governing equations and
+field \gls{u} through the following set of governing equations and
 restrictions that must be satisfied. First (i) the \textit{compatibility
-  equation} that extracts from $\vect{u}$ the strain field is,
+  equation} that extracts from \gls{u} the strain field \gls{strain} is,
 \begin{equation}
@@
 \end{equation}
-together with essential boundary conditions of Dirichlet type
-$\varGamma_d$. An additional consideration over the strain field is
+together with essential boundary conditions of Dirichlet type \gls{dirichlet-boundary}. An additional consideration over the strain field is
 the assumption of inifinitesimal strain, therefore second order terms
@@
 conjugate variable for the strain field if the stress field
-$\tens{\sigma}$, which satisfies (ii) the \textit{conservation of
+\gls{stress}, which satisfies (ii) the \textit{conservation of
   momentum equation}
@@
 \end{equation}
-together with the natural boundary conditions of the Neumann type
-$\varGamma_n$. Next (iii) the constitutive equation as a linear
+together with the natural boundary conditions of the Neumann type \gls{neumann-boundary}. Next (iii) the constitutive equation as a linear
 application from $\Re^n$ to $\Re^n$, which relates the
@@
 
-\subsection{Variational formulation}
-\label{sec:variational-formulation}
 To write the variational statement of the problem, let us define a
@@
 \end{equation}
-And which satisfies that the Cauchy sequences are convergent in $\varOmega$
+And which satisfies that the Cauchy sequences are convergent in \gls{domain}
 \begin{equation}
@@
 
-\subsection{Galerkin procedure}
-\label{sec:Galerkin-procedure}
 In order to arrive to a finite set of equations, in contrast with the
-FEM, in MPM a double discretization procedure is performed as we will
-describe here below. First, the continuum domain
-$\Omega$ is discretized with a finite sum of material points (in the
+\acrshort{fem}, in \acrshort{mpm} a double discretization procedure is
+performed. First, the continuum \gls{domain} is discretized with a finite sum of material points (in the
 following particles), each one
@@
 virtual displacement field $\vect{u}^{\psi}_{p}$. Therefore, employing
-the definition of the material integral, where we recover the Riemann
-integral definition as an addition of a finite set of points, and
+the definition of the material integral, where Riemann
+integral definition is recovered as an addition of a finite set of points, and
 their volumes are interpreted as quadrature weights. Consequently,
@@
 Introducing \eqref{eq:particle_acceleration_forces},
-\eqref{eq:particle_internal_forces}, \eqref{eq:particle_body_forces}, 
-and \eqref{eq:particle_load_forces} in \eqref{eq:BalanceMomentum_wf},
-and approximating the displacement field of the particle
+\eqref{eq:particle_internal_forces}, \eqref{eq:particle_body_forces},  \eqref{eq:particle_load_forces} in \eqref{eq:BalanceMomentum_wf},
+approximating the displacement field of the particle
 $p$ as $\vec{u}_{p} = N_{Ip} \vect{u}_I$, $\vec{u}^{\psi}_{p} = N_{Ip} \vect{u}_I^{\psi}$,
@@
 \Grad{N_{Ip}})^s$, $\tens{\varepsilon}_p^{\psi}= (\vect{u}_I^{\psi} \otimes \Grad{N_{Ip}})^s$.
-We reach to the nodal balance of forces of the continuum,
+nodal balance of forces of the continuum is obtained,
 \begin{equation}
@@
 \end{equation}
-Next, imposing $\frac{D \rho}{D t} = 0$, we ensures the mass
-conservation and update the density field.
+Next, mass conservation is guaranteed by enforcing the null value of
+the material derivative of the density field $\frac{D \rho}{D t} = 0$.
+This leads a suitable equation to update the density field.
 \begin{equation}
   \label{eq:MassConservation}
-\dot{\rho} = - \rho\ \mathit{tra} \left( \dot{\tens{\varepsilon}} \right)
-\end{equation}
-
+\dot{\rho} = - \rho\ \mathit{trace} \left( \dot{\tens{\varepsilon}} \right)
+\end{equation}
 Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order
@@
 \end{equation}
-In MPM literature, this equations
+In \acrshort{mpm} literature, this equations
 (\ref{eq:particle_balance_forces3}) and (\ref{eq:Updated_Lagrangian}),
-are solved with an explicit forward Euler algorithm. The time integration scheme of MPM has been described in detail by many researchers
+is solved with an explicit forward Euler algorithm. The time integration scheme of \acrshort{mpm} has been described in detail by many researchers
 \cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and summarized
@@
   }
-  \caption{Description of the three steps in MPM standard algorithm.}
+  \caption{Description of the three steps in \acrshort{mpm} standard algorithm.}
   \label{fig:MPM_algorithm}
@@
 like \cite{Guilkey2003}, \cite{Tran2019e}, \cite{Charlton2017}. In the
-first publication on MPM \cite{Sulsky1994}, the nodal acceleration
+first publication on \acrshort{mpm} \cite{Sulsky1994}, the nodal acceleration
 was employed to update the particles as
@@
 Later Tran \& Solowski (2019)\cite{Tran2019e} presented a
-generalized-$\alpha$ scheme for MPM inspired in the explicit time
+generalized-$\alpha$ scheme for \acrshort{mpm} inspired in the explicit time
 integration algorithm proposed by Chung \& Hulbert
@@
 
-\section{Explicit predictor-corrector scheme for MPM.}
+\subsection{Explicit predictor-corrector scheme for \acrshort{mpm}.}
 \label{sec:epc-algor-mpm}
@@
 \end{equation*}
-As MPM has a nodal stage, it is possible to apply this methods
-successfully in MPM framework as was proved by
+As \acrshort{mpm} has a nodal stage, it is possible to apply this methods
+successfully in \acrshort{mpm} framework as were proved by
 \cite{Tran2019e}. Taking the predictor definition from and calculating
-nodal velocity, and updating particles position employing nodal values
+nodal velocities, and updating particles position employing nodal values
 of velocity and acceleration. The predictor-corrector algorithm has
@@
 computational advantages and stability were widely proof by Liu
-\cite{Xiaojian94}. The ``classic'' PCE algorithm starts with a
-predicted value of the nodal velocity at the $(k+1)$th time step denoted by $\vec{\tilde{v}}_I^{k+1}$ given as,
+\cite{Xiaojian94}. The ``classic'' \acrfull{npc} algorithm starts with a
+predicted value of the nodal velocities at the $(k+1)$th time step denoted by $\vec{\tilde{v}}_I^{k+1}$ given as,
 \begin{equation}
@@
 
-To accommodate this step to MPM framework, it is necessary to get
+To accommodate this step to \acrshort{mpm} framework, it is necessary to get
 the nodal values of the velocity and acceleration throughout a variational
@@
 procedures described by Zienkiewicz \& Zhu \cite{ZZ1992_I} (\textit{ZZ})
-in the context of FEM. In MPM Gauss quadrature is not employed as
+in the context of \acrshort{fem}. In \acrshort{mpm} Gauss quadrature is not employed as
 integrals are computed following the Riemann integral definition,
@@
  Therefore, to get a analogous expression for
- \eqref{eq:Predictor-velocity-I} in the context of MPM, the
+ \eqref{eq:Predictor-velocity-I} in the context of \acrshort{mpm}, the
  procedure described in the equation \eqref{eq:Variational-recovery}
@@
 This way of computing the nodal predictor is both numerically stable
-and minimize the computational effort. Once nodal velocity are
-obtained, the essential boundary conditions are imposed. And in the
-following, the ``classic'' MPM algorithm continues to reach to the
-equilibrium equation \eqref{eq:particle_balance_forces3}. Here we
-continue with the \textit{corrector} stage, due to the fact that we
-already have nodal velocity, this step is computed in the same way as
-in FEM,
+and minimize the computational effort. Once nodal velocities are
+obtained, the essential boundary conditions are imposed over \gls{dirichlet-boundary}. And in the
+following, the ``classic'' \acrshort{mpm} algorithm continues to reach to the
+equilibrium equation \eqref{eq:particle_balance_forces3}. Now the
+\textit{corrector} stage is introduced. Due to the fact that nodal
+velocities were obtained earlier, this step is computed in the same way as
+in \acrshort{fem},
 \begin{equation}
@@
   \renewcommand{\thealgorithm}{}
-  \caption{Explicit Predictor-Corrector scheme}
+  \caption{\acrfull{npc} scheme}
   \begin{algorithmic}[1]
@@
 
-\section{Local \textit{max-ent} approximants}
+\subsection{Local \textit{max-ent} approximants}
 \label{sec:local-max-ent}
-The popularity of MPM has increase notoriously during
+The popularity of \acrshort{mpm} has increase notoriously during
 the recent years due to its ability to deal with large strain problems
 without mesh distorsion issues inherent to mesh based methods like
-FEM, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations
-made with the original MPM, there are numerical noises when particles
-crossing the cell boundaries. Local maximum-entropy (or
-local \textit{max-ent}) shape function first introduced by Arroyo \&
-Ortiz (2006)\cite{Arroyo2006} has been recently tested under MPM framework
-by Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
-simulations performed with the \textit{max-ent} basis functions show
-considerably more accurate stress approximations for MPM. Although, in
-\cite{Wobbes2020} authors does not deep in how the regularization
-parameter $\beta$ affects to the accuracy and stability of the solution.
-The basic idea of the shape functions based on such
-an estimate is to interpret the shape function $N_I(\vec{x})$ as a probability. This allow us to introduce two important limits:
+\acrshort{fem}, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations
+made with the original \acrshort{mpm}, there are numerical noises when particles
+crossing the cell boundaries. \acrfull{lme} approximation schemes were
+first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} has been
+recently tested under \acrshort{mpm} framework by Wobbes {\it et al.}
+(2020)\cite{Wobbes2020} where they prof that simulations performed
+with \acrshort{lme}, shows considerably more accurate stress
+approximations for \acrshort{mpm}. Although, in \cite{Wobbes2020}
+authors does not deep in how the regularization parameter $\beta$
+affects to the accuracy and stability of the solution. The basic idea
+of the shape functions based on such an estimate is to interpret the shape function $N_I(\vec{x})$ as a probability. This allow us to introduce two important limits:
 the principle of maximum-entropy (\textit{max-ent}) statistical
@@
 \end{align*}
-On the other hand, we wish to control the width of the shape function and it dacay with distance away from the corresponding nodes.
-To reach to this objective \cite{Arroyo2006} propose the following linear program,
+On the other hand, the control of the shape function width and its
+dacay with distance away from the corresponding nodes is a desirable property. To reach to this objective \cite{Arroyo2006} propose the following linear program,
 \begin{align*}
@@
 $\beta \in (0,\infty)$. The unique solution of
-the local max-ent problem (LME)$_\beta$ is:
+the local \textit{max-ent} problem \acrshort{lme}$_\beta$ is:
 \begin{equation}
@@
 \end{eqnarray}
-The regularization parameter $\beta$ of LME shape functions may be
+The regularization parameter $\beta$ of \acrshort{lme} shape functions may be
 controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
@@
 find the neighbour nodes of a given integration point.
-An aditional remark is that in similariti  to alternative non-polynomial meshfree basis functions, the LME approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem.
+An aditional remark is that in similariti  to alternative non-polynomial meshfree basis functions, the \acrshort{lme} approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem.
 
 This interpolation technique avoid one important shortcoming when using
-GIMP or B-Spline MPM regarding the computational domain boundaries
+\acrshort{gimp} or B-Spline \acrshort{mpm} regarding the computational domain boundaries
 Steffen {\it et al.} (2008)\cite{Steffen2008b}. Which is the
@@
 this problems with ``extra'', or the called ``ghost'' nodes by other investigators. Anyway this nodes requires especial treatments similar
-to those employed in the smoothed particle hydrodynamics (SPH), for
+to those employed in the \acrfull{sph}, for
 further details see Liu \& Liu (2003)\cite{Liu2003}. The approach here
@@
     given integration point. The picture also shows the neighbourhood
-    criterion to select those node inside of $\Omega$.} 
+    criterion to select those node inside of \gls{domain}.} 
   \label{fig:Particle-discretization}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Due to the FE-compatibility, the LME shape function is degenerated to
+Due to the \short{fem}-compatibility, the \acrshort{lme} shape function is degenerated to
 linear finite element shape function if $d+1$ neighbouring nodes are
 chosen as the support. Furthermore, with a conveniently adopted
-\textit{regularization} parameter it is possible to get a GIMP-like
+\textit{regularization} parameter it is possible to get a \acrshort{gimp}-like
 shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}.  
@@
   \caption{Comparative of linear piecewise shape functions (Q4) and
-    uniform GIMP shape functions (uGIMP) \textit{versus} Local max-ent
-    shape functions for a two-dimensional arrangement of nodes, and
+    \acrshort{ugimp} shape functions \textit{versus}  \acrshort{lme}
+    approximation for a two-dimensional arrangement of nodes, and
     spatial derivatives for several values of $\gamma = \beta/h^2$.}
@@
 \cite{Kochmann2019} introduced an enhanced version of the original
-local max-ent scheme, which uses an anisotropic support to deal with
+\acrshort{lme} scheme, which uses an anisotropic support to deal with 
 tensile inestability. Nonetheless this is out of the scope of the
@@
 overcome spurious oscillations due to the grid crossing and high
-frequency loads under the context of MPM Two different test has
+frequency loads under the context of \acrshort{mpm} Two different test has
 been adopted for this purpose, the benchmark proposed by Dyka \& Ingel
 (1995)\cite{Dyka1995} and the test proposed in the PhD thesis of
-Andersen (2009)\cite{thesis_Andersen_2009}. In all calculations we confine out attention to
-uniformly distribute node and particle sets. The accuracy of the PCE
-scheme is compared to the standard FE. In addition \textit{max-ent} solutions
-are compared with those provided by uGIMP and Q4 shape functions, also
-we compare MPM performance with OTM and FEM. All simulations were
-performed with in-hose software.
-
-\subsection{Dyka bar}
+Andersen (2009)\cite{thesis_Andersen_2009}. Thought them, the accuracy of the \acrshort{npc}
+scheme is compared to the standard \acrshort{fe}. In addition \acrshort{lme} solutions
+are compared with those provided by \acrfull{ugimp} and Q4 shape
+functions. To avoid some mesh-dependent issues, in all
+calculations a regular background mesh was setted. All simulations were performed with in-hose software.
+
+\subsection{Dyka bar \cite{Dyka1995}}
 \label{sec:dyka-bar}
@@
 length of 0.1333 meters, sketched in the
-figure~\ref{fig:Dyka_Bar}. The boundary conditions are in the right
+figure~\ref{fig:Dyka_Bar}. The boundary conditions are: in the right
 border displacement are constrained ($\vect{v} \rvert_{x=L} = 0$) and
@@
 (from A to C and back to A) at least two times. For the spatial
-discretization we propose a set a seven nodal mesh sizes (0.1, 0.3325, 0.5,
+discretization we adopt a set of seven nodal mesh sizes (0.1, 0.3325, 0.5,
 1.0, 3.3325, 6.665, 10.0) in millimeters. For each element a number of
@@
 occupying the exact quadrature points of a linear quadrilateral. With
-the exception of the uGIMP simulation where gaps or overlap between
+the exception of the \acrshort{ugimp} simulation where gaps or overlap between
 voxels of each particle are not allowed. In those cases, each particles
@@
   \caption{Velocity evolution at the point in the Dyka bar left side,
-    convergence plots for FE and PCE. The plot is subdivided with
+    convergence plots for \acrshort{fe} and \acrshort{npc}. The plot is subdivided with
     colours, the darker part of the diagram shows coincides when the
@@
 of each particle. A first comparative between both time integration
-scheme is plotted in figure \ref{fig:Dyka-PCE-FE}. It demonstrates the
-superior performance of the PCE \textit{versus} the FE. In the PCE the
+scheme is plotted in figure \ref{fig:Dyka-NPC-FE}. It demonstrates the
+superior performance of the \acrshort{npc} \textit{versus} the \acrshort{fe}. In the \acrshort{npc} the
 spurious oscillations are quickly mitigated in the first time steps,
-and does not propagate the error in time in opposite to FE where the
+and does not propagate the error in time in opposite to \acrshort{fe} where the
 simulation becomes unstable after $6E^{5}$ seconds. Figure
@@
   }
-  \caption{Comparative of the PCE \textit{versus} the FE. In the
+  \caption{Comparative of the \acrshort{npc} \textit{versus} the \acrshort{fe}. In the
     picture the velocity evolution at the point in the bar left side
     is plotted.}
-  \label{fig:Dyka-PCE-FE}
+  \label{fig:Dyka-NPC-FE}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Figure \eqref{fig:Dyka-LME-gamma} shows the sensibility of the LME
+Figure \eqref{fig:Dyka-LME-gamma} shows the sensibility of the \acrshort{lme}
 approximation scheme to variations in the a-dimensional parameter
 $\beta$ that controls the value of the regularization parameter
-$\gamma$ depending of the mesh size. As we can see lower values of
+$\gamma$ depending of the mesh size. Notice how lower values of
 gamma exhibits a behaviour with a soft decay in some parts of the
@@
 materials. On the other hand larger values of the parameter $\beta$
-makes the solution tend to the linear FEM solution as the athermal
+makes the solution tend to the linear \acrshort{fem} solution as the athermal
 limit is reached \cite{Arroyo2006}. Intermediate values of the
@@
 is negligible in comparison with the cell size, the global behaviour
-is FEM-like, therefore larger values of $\gamma$ has offers better
+is \acrshort{fem}-like, therefore larger values of $\gamma$ has offers better
 results. On the other hand, when mesh size is small enough to produce
@@
 values of it, whose suffers a punishment of the performance when significant
-movement of the particles occurs as far we reduce the mesh size.  
+movement of the particles occurs as far mesh size is reduced.  
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Figure \ref{fig:Dyka-uGIMP-LME} compares the performance of the
-uGIMP~\cite{Bardenhagen2004} shape function \textit{versus} the LME approximation scheme with
+\acrshort{ugimp}~\cite{Bardenhagen2004} shape function \textit{versus} the \acrshort{lme} approximation scheme with
 a adimensional regularization parameter $\gamma$ of 4.0. Although it
-does not shows remarkable differences, LME approximats exhibits a more
-robust behaviour than the uGIMP shape functions. Regarding this, notice
-the absence of uGIMP values for a mesh size of 0.3325 and 0.5
-millimeters. During these simulation the uGIMP suffered an unstable
-increase of the error so we decided to no include this nodes in the
-plot. A feasible explanation for this phenomena could be the presence
-of numerical cancellation which could produce gaps between
-voxels. Further research should be done in this direction for getting
-a better comprehension of this phenomena. In opposite, LME
-approximation does not suffers this phenomena either with irregular
-nodal layout.
+does not shows remarkable differences, \acrshort{lme} approximats exhibits a more
+robust behaviour than the \acrshort{ugimp} shape functions. Regarding this, notice
+the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5
+millimeters. This is because during these simulation the \acrshort{ugimp} suffered an unstable
+increase of the error which yield unacceptable results. A feasible
+explanation for this phenomena could be the presence of numerical
+cancellation which could produce gaps between voxels. Further research
+should be done in this direction for getting a better comprehension of
+this phenomena. In opposite, \acrshort{lme} approximation does not
+suffers this phenomena either with irregular nodal layout.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Finally, figure \ref{fig:Dyka-OTM-MPM} compares the solution obtained
-with OTM~\cite{Li2010} \textit{versus} the solution obtained with MPM,
+with \acrshort{otm}~\cite{Li2010} \textit{versus} the solution obtained with \acrshort{mpm},
 both with same time integration scheme and spatial discretization. For
-this case the performance of MPM is robust and stable than OTM. As we
-can appreciate, during the first half of the simulation both method
+this case the performance of \acrshort{mpm} is robust and stable than
+\acrshort{otm}. During the first half of the simulation both method 
 seem to perform in a similar way, but during the second half of the
 simulation after the elastic wave has travel from the free border to
-the fixed one and back, in OTM the solution becomes noisy than the
-one performed by MPM.  
+the fixed one and back, in \acrshort{otm} the solution becomes noisy than the
+one performed by \acrshort{mpm}.  
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In order to test the ability of this interpolation technique to deal
-with grid crossing instabilities we will simulate the vertical
-compression of a square block (10 by 10 meters) of soft soil sketched
-in figure~\ref{fig:block} and loaded using an incremental gravitation
-scheme.
+The following test was proposed to measure proof the ability of this
+interpolation technique to deal with grid crossing instabilities. It
+consists in the simulation of a square block of soil incrementally
+loaded by a body force. Details of the problem are sketched in figure~\ref{fig:block}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
-In order to get a stable solution, we will adopt a time step conducted
-by a Courant number of 0.1. On the other hand, the explicit predictor-corrector
-scheme is here employed looking forward getting better results. For the
-initial spatial discretization we will employ four particles per cell
-($\Delta x = 2\ m$). The initial setting of particles inside of the
+In order to get a stable solution, time step was conducted by a
+Courant number of 0.1. On the other hand, the explicit
+predictor-corrector scheme is here employed looking forward getting better results. For the
+initial spatial discretization four particles per cell
+($\Delta x = 2\ m$) were adopted. The initial layout of particles inside of the
 cell changes according to the approximation technique adopted. For the
-bi-linear shape functions and the LME approximants, the initial
+bi-linear shape functions and the \acrshort{lme} approximants, the initial
 position corresponds to the location of the gauss-points in a standard
-quadratic finite element. For the uGIMP shape function the initial
+quadratic finite element. For the \acrshort{ugimp} shape function the initial
 position of each particle is located in the center of each voxel, due
@@
 Figure~\ref{fig:vertical-displacement-block} shows the vertical
-displacement evolution of a point in the free surface of the block. As
-we can see the simulation using the Q4 interpolation technique turns
-out to be unstable and in the second 15 it fails. The uGIMP simulation
+displacement evolution of a point in the free surface of the
+block. This figure shows how simulations performed with a bi-linear
+interpolation technique (Q4) turns out to be unstable during
+cell-crossing and consequently fails. The \acrshort{ugimp} simulation
 is more stable than the one performed by the Q4. Despite this is still
-unstable and could trigger severe oscillations if we pretend to
-simulate non-linear materials. The LME simulation was performed using
-two kinds of shape functions, one with a low value of the
+unstable and could trigger severe oscillations in simulation with
+non-linear  materials. The \acrshort{lme} simulation was performed
+using two kinds of shape functions, one with a low value of the
 dimensionless parameter, $\gamma = 0.8$, and other with a larger value
@@
 due to the fact that with larger value of $\gamma$, the shape
-functions behaves in a similar way to the FEM, which performs very
+functions behaves in a similar way to the \acrshort{fem}, which performs very
 accurate in those cases with a reasonable mesh distorsion, and with a
-lower value it behaves in a similar way to the uGIMP. This behaviour
+lower value it behaves in a similar way to the \acrshort{ugimp}. This behaviour
 was noticed previously by \cite{Arroyo2006}, were authors highlight
@@
 \label{sec:conclusions}
-We have developed a novel time integration scheme for MPM, and
+We have developed a novel time integration scheme for \acrshort{mpm}, and
 proved how local \textit{max-ent} approximation scheme could be
-employed as an useful technique in MPM. The PCE arise as a highly
+employed as an useful technique in \acrshort{mpm}. The \acrshort{npc} arise as a highly
 efficient alternative for challenging dynamic problems like coupled
 $u-p_w$ without appeal to expensive implicit time integration
-algorithms. Also the procedure employed to design the PCE algorithm open
+algorithms. Also the procedure employed to design the \acrshort{npc} algorithm open
 the door to revisit a huge variety of time integration schemes
-developed originally for FEM, which can be rearranged to MPM framework
+developed originally for \acrshort{fem}, which can be rearranged to \acrshort{mpm} framework
 with some modifications. Anyway, further research should be done to improve the
 formal comprehension of the algorithm good performance. This paper
-also enhances the suitability of the local \textit{max-ent} as a
+also enhances the suitability of the \acrshort{lme} approximation as a
 general promising alternative to the wide range of approximation.
-techniques developed for the MPM to overcome grid crossing
-limitations and to avoid the constriction of the uGIMP of a regular mesh
+techniques developed for the \acrshort{mpm} to overcome grid crossing
+limitations and to avoid the constriction of the \acrshort{ugimp} of a regular mesh
 or a high density of particles per cell. Future research of the
 group will be on the employ of this scheme to improve the localization
-capabilities of MPM for viscoplastic materials. Finally we remark on
+capabilities of \acrshort{mpm} for viscoplastic materials. Finally we remark on
 the possibility of adapting the function $\beta(\vect{x})$ as a second
@@
 capabilities. Other possibility is to adapt the value of $\beta$ to
-solve the equations fem-like of meshfree-like depending of how behaves
+solve the equations \acrshort{fem}-like of meshfree-like depending of how behaves
 the region, this could be extremely useful in simulating all together
@@
 
+% \printglossary[type=\acronymtype]
+\printglossaries
+
 \appendix
@@
 
-For the derivation of this analytical solution we will consider  the
+For the derivation of this analytical solution we will considered  the
 dynamic behaviour of a 1D elastic bar. The governing equations are the

### 2020-04-25 _region_.tex
Cambios 24-4-2020

@@
-\message{ !name(LME-MPM.tex)}% %%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-% %
-% % This is a general template file for the LaTeX package SVJour
-% % for Springer journals.          Springer Heidelberg 2010/09/16
-% %
-% % Copy it to a new file with a new name and use it as the basis
-% % for your article. Delete % signs as needed.
-% %
-% % This template includes a few options for different layouts and
-% % content for various journals. Please consult a previous issue of
-% % your journal as needed.
-% %
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %
-% % First comes an example EPS file -- just ignore it and
-% % proceed on the \documentclass line
-% % your LaTeX will extract the file if required
-% \begin{filecontents*}{example.eps}
-% %!PS-Adobe-3.0 EPSF-3.0
-% %%BoundingBox: 19 19 221 221
-% %%CreationDate: Mon Sep 29 1997
-% %%Creator: programmed by hand (JK)
-% %%EndComments
-
-% gsave
-% newpath
-%   20 20 moveto
-%   20 220 lineto
-%   220 220 lineto
-%   220 20 lineto
-% closepath
-% 2 setlinewidth
-% gsave
-%   .4 setgray fill
-% grestore
-% stroke
-% grestore
-% \end{filecontents*}
-% %
-% \RequirePackage{fix-cm}
-% %
-% %\documentclass{svjour3}                     % onecolumn (standard format)
-% %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-% %\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-% \documentclass[twocolumn]{svjour3}          % twocolumn
-% %
-% % flush right qed marks, e.g. at end of proof
-% \smartqed
-
-% \usepackage[lofdepth,lotdepth]{subfig}
-% \usepackage{graphicx}
-% \usepackage{subcaption}
-
-% \usepackage{amsmath,amsthm,amssymb}
-
-% \usepackage{amsfonts}
-% \usepackage{epstopdf}
-% \usepackage{mathrsfs} % para formato de letra
-% \usepackage{hyperref}
-% \usepackage{enumitem}
-% \usepackage{array}
-% \usepackage{tabularx}
-% \usepackage{supertabular}
-% \usepackage{fancyhdr}
-% \usepackage{multirow}
-% \usepackage{color}
-% \usepackage{makeidx}
-% \usepackage{setspace}
-% \usepackage{epsfig}
-
-% \usepackage{pgf}
-% % \usepgfplotslibrary{external} 
-% % \tikzexternalize
-
-% %\usepackage{latexsym}
-
+\message{ !name(LME-MPM.tex)}
 \documentclass[preprint,12pt,a4paper]{elsarticle}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Init glossaries
+\usepackage[acronym]{glossaries}
+
+\makeglossaries
+
+\newglossaryentry{domain}
+{
+  name=$\varOmega$,
+  description={Continuum domain}
+}
+
+\newglossaryentry{contour}
+{
+  name=$\partial\varOmega$,
+  description={Boundary of the continuum domain $\varOmega$. Also
+    defined as $\Gamma$}
+}
+
+\newglossaryentry{dirichlet-boundary}
+{
+  name=$ \Gamma_d$,
+  description={Essential or Dirichlet boundary conditions over $\partial\varOmega$}
+}
+
+\newglossaryentry{neumann-boundary}
+{
+  name=$ \Gamma_n$,
+  description={Natural or Nemann boundary conditions over $\partial\varOmega$}
+}
+
+\newglossaryentry{rho}
+{
+  name=$\rho$,
+  description={Describes the scalar density field}
+}
+
+\newglossaryentry{a}
+{
+  name=$\vect{a}$,
+  description={First order tensor which describes the acceleration field}
+}
+
+\newglossaryentry{v}
+{
+  name=$\vect{v}$,
+  description={First order tensor which describes the velocity field}
+}
+
+\newglossaryentry{u}
+{
+  name=$\vect{u}$,
+  description={First order tensor which describes the displacement field}
+}
+
+\newglossaryentry{x}
+{
+  name=$\vect{x}$,
+  description={First order tensor which describes the global coordinates field}
+}
+
+\newglossaryentry{xi}
+{
+  name=$\vect{\xi}$,
+  description={First order tensor which describes the local coordinates field}
+}
+
+\newglossaryentry{stress}
+{
+  name=$\tens{\sigma}$,
+  description={Second order tensor which means the Cauchy stress tensor}
+}
+
+\newglossaryentry{strain}
+{
+  name=$\tens{\varepsilon}$,
+  description={Second order tensor which means the Cauchy strain tensor}
+}
+
+\newglossaryentry{Constitutive}
+{
+  name=$\tens{D}$,
+  description={Four order tensor which means the constitutive response
+    of the material}
+}
+
+\newglossaryentry{LME-beta}
+{
+  name=$\beta$,
+  description={Regularization or thermalization parameter of the
+    LME$_{\beta}$ Pareto set}
+}
+
+\newacronym{mpm}{MPM}{Material Point Method}
+\newacronym{otm}{OTM}{Optimal Transportation Meshfree}
+\newacronym{sph}{SPH}{Smoothed Particle Hydrodynamics}
+\newacronym{fem}{FEM}{Finite Element Method}
+\newacronym{lme}{LME}{Local Maximum-Entropy}
+\newacronym{flip}{FLIP}{Fluid Implicit Particle}
+\newacronym{gimp}{GIMP}{Generalized Interpolation Material Point}
+\newacronym{igimp}{iGIMP}{Implicit GIMP}
+\newacronym{ugimp}{uGIMP}{Uniform GIMP}
+\newacronym{ddmp}{DDMP}{Dual Domain Material Point}
+\newacronym{ctls}{CTLS}{Conservative Taylor Least Squares}
+
+% End glossaries
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \modulolinenumbers[5]
@@
 \begin{abstract}
-  Material Point Method (MPM) has arisen in the recent years as an
-  alternative to Finite Element Method (FEM) under the large
+  \acrfull{mpm} has arisen in the recent years as an
+  alternative to \acrfull{fem} under the large
   deformation regime. However, the simulation of shock waves
   propagation and other high frequency problems is still challenging
-  under this approach due the incapability of the standard MPM time
+  under this approach due the incapability of the standard \acrshort{MPM} time
   integration scheme to filter spurious noises. To overcome this
-  limitation in this paper, an explicit predictor-corrector time integration scheme has been proposed. Its superior performance mitigates the 
-  presence of spurious oscillations with minimal dissipation in high
-  frequency problems. Other source of numerical noise in MPM 
+  limitation in this paper, an explicit predictor-corrector time
+  integration scheme has been proposed. Its superior performance
+  mitigates the presence of spurious oscillations with minimal dissipation in high
+  frequency problems. Other source of numerical noise in \acrshort{MPM} 
   occurs when to material points cross computational grid
@@
   the solution in one case, or damage it in another. To overcome it,
-  this document adopts the \textit{local maximum-entropy approximation
-    schemes} (LME) a robust substitute for the wide range of shape
-  function in MPM. Local \textit{max-ent} approximation may be regarded as a
-  \textit{thermalization} of Delaunay triangulation which resolves the
+  this document adopts the \acrfull{lme} approximation schemes a
+  robust substitute for the wide range of shape function in
+  \acrshort{MPM}. Local \textit{max-ent} approximation may be regarded
+  as a \textit{thermalization} of Delaunay triangulation which resolves the
   degenerate cases resulting from the lack or uniqueness of the
@@
 development of other interpolation techniques to overcome this
-limitation such as the generalized interpolation material point method
-(GIMP) Bardenhagen \& Kober (2004)~\cite{Bardenhagen2004}, which has
+limitation such as the \acrfull{gimp} method Bardenhagen \& Kober (2004)~\cite{Bardenhagen2004}, which has
 demonstrate to have a good performance in the finite deformation
@@
 spline-lines has gain popularity with the introduction of the B-Spline
-MPM proposed by Roel Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
+\acrshort{mpm} proposed by Roel Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
 this technique allows the employ of unstructured set of notes and
 particles. More recently, approximants derived from minimization has
-been introduced in to MPM framework with the Conservative Taylor
+been introduced in to \acrshort{mpm} framework with the Conservative Taylor
 Least Squares (CTLS) reconstruction proposed by Wobbes {\it et al.}
@@
     schemes} (LME) as a robust substitute for the wide range of shape
-  function in MPM. First introduced by Arroyo \& Ortiz
+  function in \acrshort{mpm}. First introduced by Arroyo \& Ortiz
 (2006)~\cite{Arroyo2006}, it belongs to the class of convex 
@@
 Optimal Transportation Meshfree (OTM) method. And more
-recently under MPM framework by Wobbes {\it et
+recently under \acrshort{mpm} framework by Wobbes {\it et
   al.}(2020)~\cite{Wobbes2020} but without exploring the benefits of
-the regularization parameter $\beta$.
+the regularization parameter \gls{LME-beta}.
 
@@
 filtering them or increasing the accuracy of the time integration
-scheme. One of the most popular is the implicit GIMP (iGIMP)
+scheme. One of the most popular is the \acrfull{igimp}
 Charlton {\it et al.} (2017)~\cite{Charlton2017}, more recently Tran \&
 Solowski (2019)~\cite{Tran2019e} proposed a generalised-$\alpha$ scheme
-for MPM with promising results but at the expense of increasing
+for \acrshort{mpm} with promising results but at the expense of increasing
 the computational effort. In this paper a less time consuming and high
@@
 problem, the variational formulation and the Galerkin procedure. In Section \ref{sec:epc-algor-mpm} an explicit predictor-corrector
-time integration scheme for MPM is proposed. Section
+time integration scheme for \acrshort{mpm} is proposed. Section
 \ref{sec:local-max-ent} briefly reviews the local \textit{max-ent}
@@
 
-\section{Brief note concerning the notation}
-\label{sec:Notation}
-In what follows, we will adopt the following convention. All the
-physical variables involved in this problem are collected in Table
-\ref{tab:notation-table}. Three kind of subscript or superscript are used within paper. The subscript$\qed_p$ is used to define a particle variable. While the
-subscript$\qed_I$ is reserved in this notation for denoting nodal
-variables. And finally, the superscript $\qed^{\psi}$ involves a
-virtual magnitude. For the operators, the convention is : $\dot{\qed}$ and
-$\ddot{\qed}$ for the first and second time derivative, $\qued \otimes
-\qued$ means the dyadic operator, $(\cdot)$ and $(\colon)$ means the first and second contraction of a tensor, $\Div{\qed}$ denotes the
-divergence operator, and finally $\Grad{\qed}$ and $\GradS{\qed}$
-denotes the gradient and its symmetric part. Einstain subscripts
-convention is adopted therefore repeated index means addition. 
-\begin{table}
-  \centering
-  \caption{Physical variables involved in the problem}
-  \label{tab:notation-table}
-  \begin{tabular}{c c c}
-    $\rho$ & Density field & Scalar \\
-    $\vect{a}$ & Acceleration field & First order tensor \\
-    $\vect{v}$ & Velocity field & First order tensor \\
-    $\vect{u}$ & Displacement field & First order tensor \\
-    $\vect{x}$ & Global coordinates & First order tensor \\
-    $\vect{\xi}$ & Local coordinates & First order tensor \\
-    $\tens{\sigma}$ & Cauchy stress tensor & Second order tensor \\
-    $\tens{\varepsilon}$ & Cauchy strain tensor & Second order tensor \\
-    $\tens{D}$ & Constitutive tensor & Fourth order tensor\\
-  \end{tabular}
-\end{table}
-
-\section{Derivation of MPM procedure}
+\section{The meshfreesubsection procedure}
 \label{sec:derivation-mpm}
+
 The aim of this section is to provide an overview of the standard
-explicit MPM algorithm~\cite{Sulsky1994}. In consequence it
+explicit \acrshort{mpm} algorithm~\cite{Sulsky1994}. In consequence it
 is structured as follows: the governing equations will be introduced
@@
 procedure, and finally (iii) a Lagrangian advection of the
-particles. In consequence MPM can be regarded as a
+particles. In consequence \acrshort{mpm} can be regarded as a
 Lagrangian-Eulerian method where particles carries on all the physical
 information and a set of background nodes is employed to
-compute the equilibrium equation.
-
-\subsection{The boundary-value problem}
-\label{sec:The boundary-value-problem}
-In MPM the continuum mechanics approach is considered. So on, let
-define a continuum domain $\varOmega$ occupied by an elastic body like
-the sketched in the figure~\ref{fig:Continuum-solid}, and $\partial
-\varOmega$ the boundaries of the domain defined by $\partial \varOmega
+compute the equilibrium equation. In what follows, we will adopt the
+following convention. Three kind of subscript or superscript are used
+within paper. The subscript $\Box_p$ is used to define a particle
+variable. While the subscript $\Box_I$ is reserved in this notation for denoting nodal
+variables. And finally, the superscript $\Box^{\psi}$ involves a
+virtual magnitude. For the operators, the convention is : $\dot{\Box}$ and
+$\ddot{\Box}$ for the first and second time derivative, $\qued \otimes
+\qued$ means the dyadic operator, $\Box \cdot \Box$ and $\Box \colon \Box$ means the
+first and second contraction of a tensor, $\Div{\Box}$ denotes the
+divergence operator, and finally $\Grad{\Box}$ and $\GradS{\Box}$
+denotes the gradient and its symmetric part. Einstain subscripts
+convention is adopted therefore repeated index means addition.
+
+\subsection{Derivation of MPM procedure}
+\label{sec:derivation-mpm}
+
+In \acrshort{mpm} the continuum mechanics approach is considered. So on, let
+define a continuum \gls{domain}  occupied by an elastic body like
+the sketched in the figure~\ref{fig:Continuum-solid}, and \gls{contour} the boundaries of the domain defined by $\partial \varOmega
 = \Gamma_d \bigcup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n = \emptyset$.
@@
 
-\subsection{Galerkin procedure}
-\label{sec:Galerkin-procedure}
 In order to arrive to a finite set of equations, in contrast with the
-FEM, in MPM a double discretization procedure is performed as we will
+FEM, in \acrshort{mpm} a double discretization procedure is performed as we will
 describe here below. First, the continuum domain
@@
 \end{equation}
-In MPM literature, this equations
+In \acrshort{mpm} literature, this equations
 (\ref{eq:particle_balance_forces3}) and (\ref{eq:Updated_Lagrangian}),
-are solved with an explicit forward Euler algorithm. The time integration scheme of MPM has been described in detail by many researchers
+are solved with an explicit forward Euler algorithm. The time integration scheme of \acrshort{mpm} has been described in detail by many researchers
 \cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and summarized
@@
   \centering
-  \resizebox{0.5\hsize}{!}{
+  \resizebox{0.8\hsize}{!}{
     \includegraphics[width=\textwidth]{./Figures/MPM_scheme_horizontal}
   }
-  \caption{Description of the three steps in MPM standard algorithm.}
+  \caption{Description of the three steps in \acrshort{mpm} standard algorithm.}
   \label{fig:MPM_algorithm}
@@
 \end{equation*}
-As MPM has a nodal stage, it is possible to apply this methods
-successfully in MPM framework as was proved by
+As \acrshort{mpm} has a nodal stage, it is possible to apply this methods
+successfully in \acrshort{mpm} framework as was proved by
 \cite{Tran2019e}. Taking the predictor definition from and calculating
@@
 procedures described by Zienkiewicz \& Zhu \cite{ZZ1992_I} (\textit{ZZ})
-in the context of FEM. In MPM Gauss quadrature is not employed as
+in the context of FEM. In \acrshort{mpm} Gauss quadrature is not employed as
 integrals are computed following the Riemann integral definition,
@@
 obtained, the essential boundary conditions are imposed. And in the
-following, the ``classic'' MPM algorithm continues to reach to the
+following, the ``classic'' \acrshort{mpm} algorithm continues to reach to the
 equilibrium equation \eqref{eq:particle_balance_forces3}. Here we
@@
 
-\section{Local \textit{max-ent} approximants}
+\subsection{Local \textit{max-ent} approximants}
 \label{sec:local-max-ent}
-The popularity of MPM has increase notoriously during
+The popularity of \acrshort{mpm} has increase notoriously during
 the recent years due to its ability to deal with large strain problems
@@
 FEM, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations
-made with the original MPM, there are numerical noises when particles
+made with the original \acrshort{mpm}, there are numerical noises when particles
 crossing the cell boundaries. Local maximum-entropy (or
 local \textit{max-ent}) shape function first introduced by Arroyo \&
-Ortiz (2006)\cite{Arroyo2006} has been recently tested under MPM framework
+Ortiz (2006)\cite{Arroyo2006} has been recently tested under \acrshort{mpm} framework
 by Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
 simulations performed with the \textit{max-ent} basis functions show
-considerably more accurate stress approximations for MPM. Although, in
+considerably more accurate stress approximations for \acrshort{mpm}. Although, in
 \cite{Wobbes2020} authors does not deep in how the regularization
@@
 This interpolation technique avoid one important shortcoming when using
-GIMP or B-Spline MPM regarding the computational domain boundaries
+\acrshort{gimp} or B-Spline \acrshort{mpm} regarding the computational domain boundaries
 Steffen {\it et al.} (2008)\cite{Steffen2008b}. Which is the
@@
 chosen as the support. Furthermore, with a conveniently adopted
-\textit{regularization} parameter it is possible to get a GIMP-like
+\textit{regularization} parameter it is possible to get a \acrshort{gimp}-like
 shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}.  
@@
 overcome spurious oscillations due to the grid crossing and high
-frequency loads under the context of MPM Two different test has
+frequency loads under the context of \acrshort{mpm} Two different test has
 been adopted for this purpose, the benchmark proposed by Dyka \& Ingel
@@
 scheme is compared to the standard FE. In addition \textit{max-ent} solutions
-are compared with those provided by uGIMP and Q4 shape functions, also
-we compare MPM performance with OTM and FEM. All simulations were
+are compared with those provided by \acrfull{ugimp} and Q4 shape functions, also
+we compare \acrshort{mpm} performance with OTM and FEM. All simulations were
 performed with in-hose software.
 
-\subsection{Dyka bar}
+\subsection{Dyka bar \cite{Dyka1995}}
 \label{sec:dyka-bar}
@@
 Figure \ref{fig:Dyka-uGIMP-LME} compares the performance of the
-uGIMP~\cite{Bardenhagen2004} shape function \textit{versus} the LME approximation scheme with
+\acrshort{ugimp}~\cite{Bardenhagen2004} shape function \textit{versus} the LME approximation scheme with
 a adimensional regularization parameter $\gamma$ of 4.0. Although it
 does not shows remarkable differences, LME approximats exhibits a more
-robust behaviour than the uGIMP shape functions. Regarding this, notice
-the absence of uGIMP values for a mesh size of 0.3325 and 0.5
-millimeters. During these simulation the uGIMP suffered an unstable
+robust behaviour than the \acrshort{ugimp} shape functions. Regarding this, notice
+the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5
+millimeters. During these simulation the \acrshort{ugimp} suffered an unstable
 increase of the error so we decided to no include this nodes in the
@@
 Finally, figure \ref{fig:Dyka-OTM-MPM} compares the solution obtained
-with OTM~\cite{Li2010} \textit{versus} the solution obtained with MPM,
+with OTM~\cite{Li2010} \textit{versus} the solution obtained with \acrshort{mpm},
 both with same time integration scheme and spatial discretization. For
-this case the performance of MPM is robust and stable than OTM. As we
+this case the performance of \acrshort{mpm} is robust and stable than OTM. As we
 can appreciate, during the first half of the simulation both method
@@
 the fixed one and back, in OTM the solution becomes noisy than the
-one performed by MPM.  
+one performed by \acrshort{mpm}.  
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 position corresponds to the location of the gauss-points in a standard
-quadratic finite element. For the uGIMP shape function the initial
+quadratic finite element. For the \acrshort{ugimp} shape function the initial
 position of each particle is located in the center of each voxel, due
@@
 we can see the simulation using the Q4 interpolation technique turns
-out to be unstable and in the second 15 it fails. The uGIMP simulation
+out to be unstable and in the second 15 it fails. The \acrshort{ugimp} simulation
 is more stable than the one performed by the Q4. Despite this is still
@@
 accurate in those cases with a reasonable mesh distorsion, and with a
-lower value it behaves in a similar way to the uGIMP. This behaviour
+lower value it behaves in a similar way to the \acrshort{ugimp}. This behaviour
 was noticed previously by \cite{Arroyo2006}, were authors highlight
@@
 \label{sec:conclusions}
-We have developed a novel time integration scheme for MPM, and
+We have developed a novel time integration scheme for \acrshort{mpm}, and
 proved how local \textit{max-ent} approximation scheme could be
-employed as an useful technique in MPM. The PCE arise as a highly
+employed as an useful technique in \acrshort{mpm}. The PCE arise as a highly
 efficient alternative for challenging dynamic problems like coupled
@@
 the door to revisit a huge variety of time integration schemes
-developed originally for FEM, which can be rearranged to MPM framework
+developed originally for FEM, which can be rearranged to \acrshort{mpm} framework
 with some modifications. Anyway, further research should be done to improve the
@@
 general promising alternative to the wide range of approximation.
-techniques developed for the MPM to overcome grid crossing
-limitations and to avoid the constriction of the uGIMP of a regular mesh
+techniques developed for the \acrshort{mpm} to overcome grid crossing
+limitations and to avoid the constriction of the \acrshort{ugimp} of a regular mesh
 or a high density of particles per cell. Future research of the
 group will be on the employ of this scheme to improve the localization
-capabilities of MPM for viscoplastic materials. Finally we remark on
+capabilities of \acrshort{mpm} for viscoplastic materials. Finally we remark on
 the possibility of adapting the function $\beta(\vect{x})$ as a second
@@
 The authors declare that they have no conflict of interest.
+
+% \printglossary[type=\acronymtype]
+\printglossaries
 
@@
 %%% End:
-\message{ !name(LME-MPM.tex) !offset(-1635) }
+\message{ !name(LME-MPM.tex) !offset(-1652) }

### 2020-04-26 LME-MPM.tex
Hasta integracion temporal

@@
 \usepackage{soul}
+\usepackage{cancel}
 
@@
 
-\newcommand{\vec}[1]{
+\newcommand{\vect}[1]{
   \ensuremath{\mathbf{{#1}}}
@@
   \ensuremath{\mathbf{{#1}}}
+}
+\newcommand{\red}[1]{
+  \textcolor{red}{{#1}}
 }
@@
   dynamic problems: Local-maximum entropy approximation and explicit
-  predictor-corrector scheme}
+  predictor-corrector scheme\\
+  \red{On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme}}
 
@@
   integration scheme to filter spurious noises. To overcome this
-  limitation in this paper, an explicit predictor-corrector time
-  integration scheme has been proposed. Its superior performance
+  limitation in this paper, an Explicit Predictor-Corrector time
+  integration scheme has been proposed. Its \textcolor{red}{powerful} \cancel{superior} performance
   mitigates the presence of spurious oscillations with minimal dissipation in high
   frequency problems. Other source of numerical noise in \acrshort{mpm} 
-  occurs when to material points cross computational grid
-  boundaries and motivated due to the lack of smoothness of the interpolation
+  occurs when the material points cross computational grid
+  boundaries, being this issue motivated by the lack of smoothness of the interpolation
   functions. This noise results in spurious local variations at the material
-  points, where strain-stress fields are computed. This could invalidate
-  the solution in one case, or damage it in another. To overcome it,
-  this document adopts the \acrfull{lme} approximation schemes a
-  robust substitute for the wide range of shape function in
+  points, where strain-stress fields are computed. This could lead to inaccurate solutions as well as aborted simulations in the worst cases. To overcome it,
+  this document adopts the \acrfull{lme} approximation schemes as a
+  robust substitute of the traditional shape function in
   \acrshort{mpm}. \acrshort{lme} approximation may be regarded
@@
   triangulation. Furthermore, by modifying a regularization parameter they
-  are able to behave finite element like or as a mesh-free
+  are able to behave finite element like or as a meshfree
   method. This capability allows to face a wide range of physics
@@
 \begin{keyword}
-  \acrshort{lme} \sep \acrshort{mpm} \sep Explicit predictor-corrector \sep Dynamic problems}
+  \acrshort{lme} \sep \acrshort{mpm} \sep Explicit predictor-corrector \sep Dynamic problems
 \end{keyword}
@@
 Since the proposal of \acrshort{mpm} by Sulsky {\it  et al.}
-(1994)~\cite{Sulsky1994} as a generalization to solids of the \acrfull{flip} method~\cite{Brackbill1986}. It popularity
+(1994)~\cite{Sulsky1994} as a generalization to solids of the \acrfull{flip} method~\cite{Brackbill1986}, its popularity
 has increased due to its ability to deal with large strain regime
 without suffer mesh distortion inaccuracies.
-
-However, this method suffers other kind of instabilities, such those
-when material points crossing cell boundaries. This give rise to the
+\red{One of the main fields where this method is strong is the dynamic one since the original time integration scheme proposed was the \acrfull{fe}~\cite{Sulsky1994}, carried out in a explicit manner.
+However, in this type or problems, the main instabilities of the original \acrshort{mpm} are even marked.}
+
+\cancel{However, this method suffers other kind of instabilities, such those} \red{On the one hand, the main source of instability occurs}
+when material points cross cell boundaries. This \cancel{give rise to} provoked the
 development of other interpolation techniques to overcome this
@@
 (2004)~\cite{Bardenhagen2004}, which has
-demonstrate to have a good performance in the finite deformation
+demonstrated to have a good performance in the finite deformation
 regime. However, in the absence of a regular grid, construction of the
 weighting functions is only achieved at considerable effort and
-computational cost.  Furthermore, as it is  a voxel based
+computational cost.  Furthermore, as it is a voxel-based
 discretization technique, it is prone to suffer voxel domains overlap
@@
 unsatisfactory behaviour when particle/cell ratio
-decreases~\cite{DHAKAL2016301}, therefore \acrshort{ddmp} requires a large number
-of particles needed for convergence, this
-makes the method very expensive. In recent years the employ of
-spline-lines has gain popularity with the introduction of the B-Spline
+decreases~\cite{DHAKAL2016301}. Therefore \acrshort{ddmp} a large number of particles is needed for convergence, what
+makes the method very expensive. In recent years the employment of
+spline-lines as shape functions has gain popularity with the introduction of the B-Spline 
 \acrshort{mpm} proposed by Roel Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
-this technique allows the employ of unstructured set of notes and
+this technique allows the employment of unstructured set of notes and
 particles. More recently, approximants derived from minimization has
-been introduced in to \acrshort{mpm} framework with the \acrfull{ctls}
+been introduced in to the \acrshort{mpm} framework with the \acrfull{ctls}
 reconstruction proposed by Wobbes {\it et al.}
-(2018)~\cite{E_Wobbes_2018}, unfortunately when particles are spread in
-a challenging way, the quality of the \acrshort{ctls} approximation decrease
-locally.
-
-This document adopts the \acrshort{lme} or local \textit{max-ent} as a robust substitute for the
-wide range of shape function in \acrshort{mpm}. First introduced by Arroyo \& Ortiz
+(2018)~\cite{E_Wobbes_2018}. Unfortunately, when particles are spread in
+a challenging way, the quality of the \acrshort{ctls} approximation decreases locally.
+
+This document adopts the \acrfull{lme}, or Local \textit{Max-Ent} approximates, as a robust substitute \cancel{for the
+wide range of} \red{of the aforementioned} shape functions in \acrshort{mpm}. First introduced by Arroyo \& Ortiz
 (2006)~\cite{Arroyo2006}, it belongs to the class of convex 
 approximation schemes and provides a seamless transition between
-\acrshort{fem} and mesh-free interpolations. The
+\acrshort{fem} and meshfree interpolations. The
 approximation scheme is based on a compromise between minimizing the
 width of the shape function support and maximizing the information
-entropy of the approximation. The local \textit{max-ent} approximation
+entropy of the approximation. The \acrshort{lme} approximation
 may be regarded as a regularization, or \textit{thermalization}, of
 Delaunay triangulation which effectively resolves the degenerate cases
-resulting from the lack of uniqueness or the triangulation. Local
-\textit{max-ent} basis functions possess many desirable properties for
-mesh-free algorithms. First of all, they are entirely defined by the
+resulting from the lack of uniqueness or the triangulation. \acrshort{lme} basis functions possess many desirable properties for
+meshfree algorithms. First of all, they are entirely defined by the
 nodal set and the domain of analysis. They are also non-negative,
 satisfy the partition of unity property, and provide an exact
-approximation for affine functions~\cite{Arroyo2006}. This
-approximation scheme has been proof to have a good performance under
-the dynamic regime by other researchers like Navas {\it et al.}
-(2018)~\cite{Navas2018a} and Li {\it et al.} (2012)~\cite{Li2012} for
-\acrfull{otm} method. And more
-recently under \acrshort{mpm} framework by Wobbes {\it et
-  al.}(2020)~\cite{Wobbes2020} but without exploring the benefits of
-the regularization parameter \gls{LME-beta}.
-
-This techniques are devoted to mitigate the
-``grid crossing'' error. Nevertheless, in the presence of shock waves spurious
-numerical noises appears despite of this using
-techniques~\cite{Tran2019e}. These numerical inaccuracies also known
-as wiggles are due to inaccuracies in the time discretization technique.
-A simple approach to face those spurious noises is to add a
-nonphysical damping source to the equilibrium equations, this
+approximation for related functions~\cite{Arroyo2006}.
+Important contributions on the Maximum-Entropy have been made by Sukumar and coworkers~\cite{Sukumar15} with Cell-based techniques and the ones carried within the \acrfull{otm} method.
+The latter methodology has been proven to have a good performance under
+the dynamic regime by other researchers, being important the contributions of Li {\it et al.} (2012)~\cite{Li2012} and Navas {\it et al.}
+(2018)~\cite{Navas:17b,Navas2018a} in the explicit regime and Navas {\it et al.}~\cite{Navas2016,Navas2016b,Navas:17c} and Wriggers and coworkers~\cite{Wriggers18} with implicit schemes. And more
+recently, under \acrshort{mpm} framework, the work made by Wobbes {\it et
+  al.}(2020)~\cite{Wobbes2020}. \cancel{but without exploring} \red{The proposed research delves into the benefits of
+the regularization parameter, \gls{LME-beta}, and the analogy of the different obtained shape functions derive by the tuning of this parameter and the traditional \acrshort{mpm} ones.}
+
+The aforementioned techniques are devoted to mitigate the
+``grid crossing'' error. Nevertheless, in the presence of shock waves spurious,
+numerical noises appear despite of the employment of these
+techniques~\cite{Tran2019e}. These numerical inaccuracies, also known
+as wiggles, arise due to inaccuracies in the time discretization technique.
+A simple approach to face those spurious noises lies on the addition of nonphysical damping sources to the equilibrium equations. This
 approach has been widely employed in this and many other numerical
@@
 schemes which reduce the presence of high frequency noises by
-filtering them or increasing the accuracy of the time integration
-scheme. One of the most popular is the \acrfull{igimp}
-Charlton {\it et al.} (2017)~\cite{Charlton2017}, more recently Tran \&
+filtering them or increasing \red{somehow} the accuracy. \cancel{of the time integration
+scheme.} One of the most popular is the \acrfull{igimp}
+Charlton {\it et al.} (2017)~\cite{Charlton2017} \red{DECIR MAS DE ESTO}. More recently Tran \&
 Solowski (2019)~\cite{Tran2019e} proposed a generalised-$\alpha$ scheme
@@
 the computational effort. In this paper a less time consuming and high
-efficient explicit predictor corrector integration method has been
-proposed. It consists in an accommodation of the \acrsull{npc}. This method
+efficient explicit predictor-corrector integration method has been
+proposed. It consists in an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
 has been chosen among other suitable alternatives as those proposed
 by Wilson {\it et al.} (1972)~\cite{Wilson1972} or Chung \& Hulbert
-(1993)~\cite{Geranlized_alpha_1993} because it simplicity and it good
-performance dealing with solids dynamics problems under a mesh-free
+(1993)~\cite{Geranlized_alpha_1993} because its simplicity and its good
+performance dealing with solid dynamic problems under a meshfree
 framework in~\cite{Navas2018a}.
@@
 The aim of this document is to mitigate the spurious oscillations due
-inaccuracies in both space and time discretization by the employ of a
-suitable combination of the \acrshort{lme} family shape functions, and the proposal of
-a explicit predictor-corrector scheme. The advantages of
-this approach will be illustrated thorough to simple but challenging test cases, like the
-propagation of shock waves in a elastic bar or the response of a block of soil
-gradually loaded with gravitational forces.
-
-The article is organized as follows. Section \ref{sec:meshfree-methodology}
+inaccuracies in both space and time discretization by the employment of a
+suitable combination of the \acrshort{lme} family shape functions, and the proposal of an explicit predictor-corrector scheme. The advantages of
+this approach will be illustrated through several \cancel{simple but} challenging test cases \red{on the elastic regime}: the
+propagation of shock waves in a elastic bar and the response of a block of soil gradually loaded with gravitational forces.
+
+The article is organised as follows. Section \ref{sec:meshfree-methodology}
 is devoted to describe the meshfree methodology adopted in this
@@
 explicit \acrshort{mpm} algorithm~\cite{Sulsky1994}. Without loosing
-generality, the method has three main steps: (i) a
+generality, the method is composed by three main steps: (i) a
 variational recovery process, where particle data is projected to the
 grid nodes, (ii) an Eulerian step, where balance of momentum equation
-is expressed as a nodal equilibrium equation thorough a \acrshort{fem}-like
+is expressed as a nodal equilibrium equation through a \acrshort{fem}-like
 procedure, and finally (iii) a Lagrangian advection of the
-particles. In consequence \acrshort{mpm} can be regarded as a
-Lagrangian-Eulerian method where particles carries on all the physical
+particles. In consequence, \acrshort{mpm} can be regarded as a
+Lagrangian-Eulerian method where particles carry on all the physical
 information and a set of background nodes is employed to
@@
 divergence operator, and finally $\Grad{\Box}$ and $\GradS{\Box}$
-denotes the gradient and its symmetric part. Einstain subscripts
+denotes the gradient and its symmetric part. Einstein subscripts
 convention is adopted therefore repeated index means addition.
+
+\red{Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are describe in subsection \ref{sec:derivation-mpm},\ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.}
 
@@
 field \gls{u} through the following set of governing equations and
-restrictions that must be satisfied. First (i) the \textit{compatibility
-  equation} that extracts from \gls{u} the strain field \gls{strain} is,
+restrictions that must be satisfied. \red{First (i) the \textit{compatibility
+  equation}, where the the strain field \gls{strain} is extracted from \gls{u} is defined as:}
 \begin{equation}
@@
 the assumption of inifinitesimal strain, therefore second order terms
-in the spatial derivatives can be neglected. The corresponding
-conjugate variable for the strain field if the stress field
-\gls{stress}, which satisfies (ii) the \textit{conservation of
-  momentum equation}
+in the spatial derivatives can be neglected.
+\red{Therefore, the stress field \gls{stress} will be considered the corresponding conjugate variable for the strain field, being the one} which satisfies (ii) the \textit{conservation of
+  momentum equation}:
 \begin{equation}
@@
 \end{equation}
-together with the natural boundary conditions of the Neumann type \gls{neumann-boundary}. Next (iii) the constitutive equation as a linear
+together with the natural boundary conditions of the Neumann type \gls{neumann-boundary}.  An aditional component will be (iii) the constitutive equation as a linear
 application from $\Re^n$ to $\Re^n$, which relates the
-strain tensor with the stress tensor,
+strain tensor with the stress tensor:
 \begin{equation}
@@
 \end{equation}
-The final restriction is (iv) the mass conservation, which can be obtained by
+\red{In this research, plane strain Linear Elasticity has been considered.
+Thus the constitutive tensor, \tens{D}, is the well known linear elastic one.} The final restriction is (iv) the mass conservation, which can be obtained by
 setting to zero the total derivative of the density field,
@@
 
-To write the variational statement of the problem, let us define a
+In order to obtain the variational statement of the problem, let us define a
 virtual displacement field such that
@@
   \vect{u}^{\psi} \in \mathcal{H}^1_0(\Omega) = \{ \vect{u}^{\psi} \in
-  \mathcal{H}^1 \mid \vect{u}^{\psi} = \vect{0}\ \text{on}\ \Gamma_d \}.
-\end{equation}
-And which satisfies that the Cauchy sequences are convergent in \gls{domain}
+  \mathcal{H}^1 \mid \vect{u}^{\psi} = \vect{0}\ \text{on}\ \Gamma_d \};
+\end{equation}
+satisfying that the Cauchy sequences are convergent in \gls{domain} as well:
 \begin{equation}
@@
   \Integral{3}{\vect{u}^{\psi}} < \infty\ \quad\text{and}\quad
-  \Integral{3}{\tens{\varepsilon}^{\psi}} < \infty
+  \Integral{3}{\tens{\varepsilon}^{\psi}} < \infty.
 \end{equation}
@@
   \Integral{2}{\vec{t}\ \cdot \vec{u}^{\psi}} - \Integral{3}{\tens{\sigma} \colon
-   \tens{\varepsilon}^{\psi}},
+   \tens{\varepsilon}^{\psi}}.
 \end{equation}\\
-therefore (\ref{eq:BalanceMomentum_wf}) together with
+Thus, equation~\eqref{eq:BalanceMomentum_wf}, together with
 \eqref{eq:Constitutive-equation} and
-\eqref{eq:Rho-material-derivative} represents the weak form
+\eqref{eq:Rho-material-derivative}, represents the weak form
 formulation of the problem.
 
-In order to arrive to a finite set of equations, in contrast with the
+In order to obtain a finite set of equations, in contrast with the
 \acrshort{fem}, in \acrshort{mpm} a double discretization procedure is
-performed. First, the continuum \gls{domain} is discretized with a finite sum of material points (in the
-following particles), each one
-represent a part of the discretized domain $\varOmega_p \subset
+performed. First, the continuum \gls{domain} is discretized with a finite sum of material points (also denominated particles the manuscript). Each material point
+represents a part of the discretized domain $\varOmega_p \subset
 \varOmega$ with $p = 1,2\ldots ,N_p$ where $N_p$ is the number of
-particles. The material point $\vec{x}_p$ is defined at the centroid
-of each $\Omega_p$, figure~\ref{fig:MPM-discretization}.
-Each material point is assigned with initial values of position,
+particles. The material point location, $\vec{x}_p$, is defined at the centroid
+of each $\Omega_p$ (see figure~\ref{fig:MPM-discretization} for details).
+Initial values of position,
 velocity, mass, volume and stress denoted by $\vec{x}_p$,
-$\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$, but also the
+$\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$ respectively are assigned to each material point, which also owns the
 virtual displacement field $\vect{u}^{\psi}_{p}$. Therefore, employing
-the definition of the material integral, where Riemann
+the definition of the material integral, where Riemann \red{ALGUNA CITA AQUI}
 integral definition is recovered as an addition of a finite set of points, and
@@
 \end{itemize}
-where $h$ is the thickness of the continuum in a 2D case. Here is
-where the second discretization procedure appears. A background mesh
+where $h$ is the thickness of the continuum in a 2D case. Following, the aforementioned second discretization procedure appears. A background mesh
 composed by a finite set of grid points with coordinates $\vec{x}_I\
-, I = 1,2\ldots ,N_n$, is generated. Where $N_n$ is the number of grid
-nodes. This mesh is employed as a support to compute gradients and
-divergences.
+, I = 1,2\ldots ,N_n$, is generated, being $N_n$ the number of grid
+nodes. \red{Spatial derivatives, such as gradients and
+divergences, are computed through the support of the background mesh.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     figure~\ref{fig:Continuum-solid}. Blue mesh represent the
-    background computational support, and the grid mesh conforms the
+    background computational support, and the red mesh conforms the
     discretized continuum body.}
@@
 \Grad{N_{Ip}})^s$, $\tens{\varepsilon}_p^{\psi}= (\vect{u}_I^{\psi} \otimes \Grad{N_{Ip}})^s$.
-nodal balance of forces of the continuum is obtained,
+nodal balance of forces of the continuum yields:
 \begin{equation}
@@
 \end{equation}
-where $\dot{\vec{p}}_{I}$ is the rate of momentum at grid node $I$, the nodal mass matrix $\tens{m}_{IJ}$ is,
+where $\dot{\vec{p}}_{I}$ is the rate of momentum at grid node $I$ and $\tens{m}_{IJ}$, the nodal mass matrix, is obtained through:
 \begin{equation}
@@
 \end{equation}
-To improve the computational efficiency and stability, the nodal mass matrix
+In order to improve the computational efficiency and stability, the nodal mass matrix
 \eqref{eq:particle_nod_mass} can be substituted by the lumped mass
 matrix $\tens{m}_{IJ}^{lumped}$.
-Later, internal and external forces are computed as follows,
+Following, internal and external forces are computed as follows,
 \begin{equation}
@@
 is the particle $p$ stress field, which can be integrated employing
-the suitable constitutive model. The strain tensor is updated employing the rate of stress tensor $\dot{ \tens{\varepsilon}}_{p}$ used to update the
-strain tensor is as follows \eqref{eq:IncrStrainPoint}.
+the suitable constitutive model.
+The strain tensor rate, $\dot{ \tens{\varepsilon}}_{p}$, as a measure of the time derivative of the strain tensor, is updated employing the velocity at the background mesh by the equation:
 \begin{equation}
@@
 the material derivative of the density field $\frac{D \rho}{D t} = 0$.
-This leads a suitable equation to update the density field.
+This leads to a suitable equation to update the density field:
 \begin{equation}
   \label{eq:MassConservation}
-\dot{\rho} = - \rho\ \mathit{trace} \left( \dot{\tens{\varepsilon}} \right)
+\dot{\rho} = - \rho\ \mathit{trace} \left( \dot{\tens{\varepsilon}} \right).
 \end{equation}
 Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order
-temporal integration scheme is required. Therefore, time is
-discretized in to a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
-is the total number of time steps. Once the nodal equilibrium equation it is solved, the values in the nodes are
-interpolated back in to the particles and each particle it is advected
-to the new position,
+\cancel{temporal} \red{time} integration scheme is required. Therefore, time is
+discretized into a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
+is the total number of time steps. Once the nodal equilibrium equation is solved, the values at the nodes are
+interpolated back into the particles, which are advected
+to the new position through:
 \begin{equation}
@@
 \end{equation}
-In \acrshort{mpm} literature, this equations
-(\ref{eq:particle_balance_forces3}) and (\ref{eq:Updated_Lagrangian}),
-is solved with an explicit forward Euler algorithm. The time integration scheme of \acrshort{mpm} has been described in detail by many researchers
-\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and summarized
-in figure~\ref{fig:MPM_algorithm}.
+\red{Traditionally, Eqs.
+\eqref{eq:particle_balance_forces3} and ~\eqref{eq:Updated_Lagrangian},
+are solved with an explicit forward Euler algorithm. In the following subsection, this and the proposed schemes are described}.
+
+\subsection{\acrshort{mpm} time integration scheme: the Explicit Predictor-Corrector proposal}
+%\subsection{Explicit predictor-corrector scheme for \acrshort{mpm}.}
+\label{sec:epc-algor-mpm}
+
+\red{As was stated previosuly, an explicit forward Euler algorithm has been utilized widely within the \acrshort{MPM} methodology. This scheme has been described in detail by many researchers
+\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and can be sketched by the scheme of the figure~\ref{fig:MPM_algorithm}.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
-However, as Andersen (2009)\cite{thesis_Andersen_2009} point out, this algorithm has been shown to be numerically unstable due to that
+However, as Andersen (2009)\cite{thesis_Andersen_2009} pointed out, this algorithm has been shown to be numerically unstable due to that
 $\vect{f}_I^{int,k}$ can be finite for an infinitesimal nodal mass
-$\tens{m}$. This can lead to numerical issues when nodal acceleration
-is obtained for evaluating \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v}. Hence, a
-corrected version of this algorithm in shown in Zhang {\it et al.}
-(2016)\cite{Zhang_book_2016}
+$\tens{m}$\red{NO ENTIENDO??}. This issue may lead to numerical issues when nodal acceleration
+is obtained in the evaluation of the Eqs. \eqref{eq:Sulsky-1994-UL-x} and \eqref{eq:Sulsky-1994-UL-v}. Hence, a
+corrected version of this algorithm was proposed by Zhang {\it et al.}
+(2016)\cite{Zhang_book_2016}:
 \begin{equation}
   \label{eq:Zhang-2016-UL-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}.  
+  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}, 
 \end{equation}
@@
   \label{eq:Zhang-2016-UL-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\ \frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I},
-\end{equation}
-Later Tran \& Solowski (2019)\cite{Tran2019e} presented a
+  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\ \frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I}.
+\end{equation}
+Delving into the improvement of the accuracy of the \acrshort{mpm} explicit schemes, Tran \& Solowski (2019)\cite{Tran2019e} presented a
 generalized-$\alpha$ scheme for \acrshort{mpm} inspired in the explicit time
@@
   \vect{x}_p^{k+1} = \vect{x}_p^{k} + N_{Ip}^{k} \left[ \Delta t\ \vec{v}_{I}^{k}+ \Delta t^2\left( (\frac{1}{2} - \beta)\
-    \vec{a}_{I}^{k} + \beta\ \vec{a}_{I}^{k+1} \right) \right]
+    \vec{a}_{I}^{k} + \beta\ \vec{a}_{I}^{k+1} \right) \right],
 \end{equation}
@@
 
-This scheme has prof to damps out the higher frequency noises
-\cite{Tran2019e}. But it can present the same numerical instabilities
+This scheme has been proven to damps out the highest frequency noises
+\cite{Tran2019e}. However, it can present the same numerical instabilities
 as in \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v} when
@@
 
-\subsection{Explicit predictor-corrector scheme for \acrshort{mpm}.}
-\label{sec:epc-algor-mpm}
-
-In this section, a explicit predictor-corrector time integration
-scheme is presented. It is based in the Newmark a-form 
-$\gamma = 0.5$ and $\beta = 0$ which is the central difference
-explicit. This method is devoted to solve a system of equations of the type
+In this section, an explicit predictor-corrector time integration
+scheme is proposed. It is based on the Newmark central differences explicit scheme, which is also denominated a-form 
+$\gamma = 0.5$ and $\beta = 0$. This method is devoted to solve a system of equations of the type
 \begin{equation*}
@@
 \end{equation*}
-As \acrshort{mpm} has a nodal stage, it is possible to apply this methods
-successfully in \acrshort{mpm} framework as were proved by
-\cite{Tran2019e}. Taking the predictor definition from and calculating
-nodal velocities, and updating particles position employing nodal values
-of velocity and acceleration. The predictor-corrector algorithm has
+\red{The nodal \acrshort{mpm} stage allows to apply this method
+in the \acrshort{mpm} framework in a similar manner that the one
+proposed by Tran~\it{et al.}~\cite{Tran2019e}. Taking into account the predictor definition, it is possible to calculate
+nodal velocities and update particles position employing nodal values
+of velocity and acceleration.}
+
+The predictor-corrector algorithm has
 been described in the classic literature \cite{Hughes2000}, and its
-computational advantages and stability were widely proof by Liu
+stability and computational advantages were widely proven by Liu
 \cite{Xiaojian94}. The ``classic'' \acrfull{npc} algorithm starts with a
-predicted value of the nodal velocities at the $(k+1)$th time step denoted by $\vec{\tilde{v}}_I^{k+1}$ given as,
+predicted value of the nodal velocities at the $(k+1)$th time step, denoted by $\vec{\tilde{v}}_I^{k+1}$, which is calculated as follows:
 \begin{equation}
   \label{eq:Predictor-velocity-I}
-  \vec{\tilde{v}}_I^{k+1} = \vec{v}_I^k + (1 - \gamma)\ \Delta t\ \vec{a}_I^k
-\end{equation}
-In \eqref{eq:Predictor-velocity-I} arise a \textit{user-defined}
-parameter $\gamma \geq 0$. This parameter influences both the predictor accuracy
-and the stability of the algorithm. As point out Liu
+  \vec{\tilde{v}}_I^{k+1} = \vec{v}_I^k + (1 - \gamma)\ \Delta t\ \vec{a}_I^k.
+\end{equation}
+
+The \textit{user-defined}
+parameter $\gamma \geq 0$ that appears in In \eqref{eq:Predictor-velocity-I}, influences both the predictor accuracy
+and the stability of the algorithm. As pointed out Liu
 \cite{Xiaojian94}, the truncation error of the predictor formula is
@@
 recovery process where particles quantities are transferred to the
-mesh nodes. This technique arise as a generalization of the super-convergent recovery
+mesh nodes. This technique arises as a generalization of the super-convergent recovery
 procedures described by Zienkiewicz \& Zhu \cite{ZZ1992_I} (\textit{ZZ})
-in the context of \acrshort{fem}. In \acrshort{mpm} Gauss quadrature is not employed as
+in the context of \acrshort{fem}. In \acrshort{mpm}, Gauss quadratures are not employed. However, 
 integrals are computed following the Riemann integral definition,
-where each component of the summation correspond to a particle of the
+where each component of the summation corresponds to a particle of the
 discretization. Also Bardenhagen \& Kober \cite{Bardenhagen2004}
-proved that thorough this information-transference technique mass and momentum are conserved. So for a general particle variable $\Phi_p$ employing the
-\textit{ZZ} technique is possible to get its nodal homologous $\Phi_I$  as,
+proved that through this information-transference technique mass and momentum are conserved. So for a general particle variable $\Phi_p$, employing the
+\textit{ZZ} technique, it is possible to get its nodal homologous $\Phi_I$  as:
 \begin{equation}
   \label{eq:Variational-recovery}
-   \Phi_I = \frac{m_p N_{Ip} \Phi_p}{m_I}
- \end{equation}
- Therefore, to get a analogous expression for
+   \Phi_I = \frac{m_p N_{Ip} \Phi_p}{m_I}.
+ \end{equation}
+ Therefore, to get an analogous expression for
  \eqref{eq:Predictor-velocity-I} in the context of \acrshort{mpm}, the
  procedure described in the equation \eqref{eq:Variational-recovery}
- is employed reaching to,
+ is employed, obtainen the following expression:
  \begin{equation}
@@
    \vec{\tilde{v}}_I^{k+1} = \underbrace{\frac{N_{Ip}^{k} m_p
-       \vec{v}_p^k}{m_I}}_{\vec{v}_I^{k}} + (1 - \gamma)\ \Delta t\  \underbrace{\frac{N_{Ip}^{k} m_p \vec{a}_p^k}{m_I}}_{\vec{a}_I^{k}}
+       \vec{v}_p^k}{m_I}}_{\vec{v}_I^{k}} + (1 - \gamma)\ \Delta t\  \underbrace{\frac{N_{Ip}^{k} m_p \vec{a}_p^k}{m_I}}_{\vec{a}_I^{k}}.
  \end{equation}
@@
 instabilities due to numerical cancellation likewise the original
-Sulky algorithm. Thankfully this can be avoided easily by the
-equivalent formulation \eqref{eq:Predictor-velocity-II}, 
+Sulky algorithm. Thankfully, this can be avoided easily by the
+equivalent formulation proposed as follows: 
 \begin{equation}
   \label{eq:Predictor-velocity-II}
-  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
+  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}.
 \end{equation}
@@
 following, the ``classic'' \acrshort{mpm} algorithm continues to reach to the
-equilibrium equation \eqref{eq:particle_balance_forces3}. Now the
+equilibrium equation \eqref{eq:particle_balance_forces3}. Next, the
 \textit{corrector} stage is introduced. Due to the fact that nodal
@@
   \label{eq:Corrector-velocity}
-  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}
-\end{equation}
-Finally updated particle kinetics are computed using nodal values as,
+  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}.
+\end{equation}
+Finally updated particle kinetics are computed using nodal values as:
 \begin{align}
@@
         \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k} 
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}.
 \end{align}
-Notice that particle displacement is computed using the corrected
-nodal velocities and the accelerations computed with the velocities
-of the predictor. However, particles velocities and accelerations
+Notice that particle displacements are computed using the corrected
+nodal velocities as well as the accelerations with the velocities
+of the predictor. However, particle velocities and accelerations
 are computed using the corrected velocities. Therefore here we share similarities
-with the \textit{leapfrog integration} which updates the position at
-full time step, but updates the velocity at half time steps. Notice
-also that with this approach the calculation of nodal momentum values
-are not required. Due to its simplicity allows be implemented with minor modifications
-over a standard forward Euler. It is summarized in shape of
-pseudo-algorithm.
+with the \textit{leapfrog integration} where position is not updated at
+full time step, but the velocity is updated at half time steps. Notice
+also that, with this approach, the calculation of nodal momentum values
+are not required. Due to its simplicity, the proposed scheme can be implemented with minor modifications
+over the standard forward Euler. The full implementation is summarized in the algorithm~\ref{algo:1}.
 
 \begin{algorithm}
-  \floatname{algorithm}{Algorithm}
+  \floatname{algorithm}{Algorithm 1}
   \renewcommand{\thealgorithm}{}
-  \caption{\acrfull{npc} scheme}
+  \caption{\acrfull{npc} scheme} \label{algo:1}
   \begin{algorithmic}[1]
@@
     \begin{equation*}
-      \rho_p^{k+1} = \frac{\rho_p^k}{1 + \mathit{tra}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.
+      \rho_p^{k+1} = \frac{\rho_p^k}{1 + \mathit{trace}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.
     \end{equation*}
@@
     Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
-    \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
+    \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ by evaluating
     \eqref{eq:nodal_internal_forces} and
     \eqref{eq:nodal_external_forces} in the time step $k+1$.
-    In the grid node $I$ is fixed in one of the spatial dimensions, set it to
-    zero to make the grid nodal acceleration zero in that direction.\\
+    In the grid node, $I$ is fixed in one of the spatial dimensions, set it to
+    zero to make the grid nodal acceleration zero in that direction.\red{NO ENTIEND??}\\
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
 
+% 
+\section*{Acknowledgements}
+%
+The financial support to develop this research from the Ministerio de Ciencia e Innovación, under Grant No.
+BIA-2016-76253 is greatly appreciated.
+The first and the second authors also acknowledge the fellowship Fundaci\'on Agust\'in de Betancourt and Juan de la Cierva (FJCI-2017–31544) respectively.
+
 % \printglossary[type=\acronymtype]

### 2020-04-27 LME-MPM.tex
Hasta Rigid Block

@@
 been described in the classic literature \cite{Hughes2000}, and its
-stability and computational advantages were widely proven by Liu
+stability and computational advantages were widely validated by Liu
 \cite{Xiaojian94}. The ``classic'' \acrfull{npc} algorithm starts with a
@@
 
-\subsection{Local \textit{max-ent} approximants}
+\subsection{Local \textit{Max-Ent} approximants}
 \label{sec:local-max-ent}
-The popularity of \acrshort{mpm} has increase notoriously during
+The popularity of the \acrshort{mpm} has increased notoriously during
 the recent years due to its ability to deal with large strain problems
 without mesh distorsion issues inherent to mesh based methods like
-\acrshort{fem}, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations
-made with the original \acrshort{mpm}, there are numerical noises when particles
-crossing the cell boundaries. \acrfull{lme} approximation schemes were
-first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} has been
+\acrshort{fem}, see Wi{\c{e}}ckowski \cite{Wieckowski2004}. However, in the simulations
+made with the original \acrshort{mpm}, numerical noises appear when particles
+cross the cell boundaries. \red{Solving this issue is the main goal of the employment of the \acrshort{LME} shape functions}.
+
+\acrfull{lme} approximation schemes were
+first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} and has been
 recently tested under \acrshort{mpm} framework by Wobbes {\it et al.}
-(2020)\cite{Wobbes2020} where they prof that simulations performed
-with \acrshort{lme}, shows considerably more accurate stress
-approximations for \acrshort{mpm}. Although, in \cite{Wobbes2020}
-authors does not deep in how the regularization parameter $\beta$
-affects to the accuracy and stability of the solution. The basic idea
-of the shape functions based on such an estimate is to interpret the shape function $N_I(\vec{x})$ as a probability. This allow us to introduce two important limits:
+(2020)\cite{Wobbes2020}. \red{The performed simulations of \acrshort{mpm}
+within \acrshort{lme} in \cite{Wobbes2020} shows considerably more accurate stress
+approximations than traditional \acrshort{mpm} schemes. However, 
+how the regularization parameter $\beta$
+affects to the accuracy and stability of the solution is not assessed deeply in that research, which is considered interesting in the present manuscript; the tuning of this $\beta$ parameter allows to make the comparison of the accuracy against analogous traditional \acrshort{mpm} shape function.}
+
+The basic idea
+of the shape functions based on such an estimate is to interpret the shape function $N_I(\vec{x})$ as a probability. This allows us to introduce two important limits:
 the principle of maximum-entropy (\textit{max-ent}) statistical
@@
 
-This approximation scheme represents a optimal compromise, in the sense of
+This approximation scheme represents an optimal compromise, in the sense of
 Pareto, between the \textit{unbiased statistical inference} based on
-the nodal data which leads to the principle of \textit{maximum-entropy}
+the nodal data which leads to the principle of \textit{Maximum-Entropy}
 stated by Jaynes \cite{Jaynes1957}, and the definition of local shape
@@
 On the other hand, the control of the shape function width and its
-dacay with distance away from the corresponding nodes is a desirable property. To reach to this objective \cite{Arroyo2006} propose the following linear program,
+decay with distance away from the corresponding nodes is a desirable property. To reach to this objective \cite{Arroyo2006} propose the following linear program,
 \begin{align*}
@@
 \end{align*}
-The regularization o \textit{thermalization} parameter
-between the two criterion $\beta$ has Pareto optimal values in the range
+The regularization or \textit{thermalization} parameter
+between the two criterion, $\beta$, has Pareto optimal values in the range
 $\beta \in (0,\infty)$. The unique solution of
@@
 The traditional way to obtain such a minimiser is using Eq.~(\ref{eq:LME-J}) to calculate small increments of $\partial\vec{\lambda}$ in a Newton-Raphson approach.
-Where $\tens{J}$ is the Hessian matrix, defined by:
+$\tens{J}$ is defined as the Hessian matrix, obtained by:
 \begin{eqnarray}
@@
 \end{equation}
-Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression for the gradient of the sahep function.
+Employing the chain rule, rearranging and considering $\beta$ as a constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following expression for the gradient of the shape function.
 \begin{eqnarray}
@@
 function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
-10$^{-6}$, for example,  would ensure a reasonable range of
-neighbours, see \cite{Arroyo2006} for details.
+10$^{-6}$ \red{in this research} \cancel{for example},  would ensure a reasonable range of
+neighbours (see \cite{Arroyo2006} for details).
 This tolerance defines the limit values of the influence radius and is used thereafter to
 find the neighbour nodes of a given integration point.
-An aditional remark is that in similariti  to alternative non-polynomial meshfree basis functions, the \acrshort{lme} approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem.
-
-This interpolation technique avoid one important shortcoming when using
+An additional remark is that, analogous to alternative non-polynomial meshfree basis functions, the \acrshort{lme} approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem.
+
+This interpolation technique avoids important shortcomings when using
 \acrshort{gimp} or B-Spline \acrshort{mpm} regarding the computational domain boundaries
-Steffen {\it et al.} (2008)\cite{Steffen2008b}. Which is the
-additional considerations in the applications of the boundary
-conditions. This is motivated because of their increased extents, it
-is possible for particles to influence, and be influenced by, nodes
-that lie outside of the simulation domain. Some researchers have solve
-this problems with ``extra'', or the called ``ghost'' nodes by other investigators. Anyway this nodes requires especial treatments similar
+(see Steffen {\it et al.} (2008)\cite{Steffen2008b}), which are related to the
+additional considerations in the application of the boundary
+conditions.
+Motivated by their increased extents, particles may share an influence radius that lies outside of the simulation domain.
+Some researchers have solved this problem with the so called ``extra'' or ``ghost'' nodes \cancel{by other investigators}.
+These nodes require especial treatment, similar
 to those employed in the \acrfull{sph}, for
 further details see Liu \& Liu (2003)\cite{Liu2003}. The approach here
-described does not requires the employ of this artifacts.
+described does not requires the employment of this artifices.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \textit{regularization} parameter it is possible to get a \acrshort{gimp}-like
-shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}.  
+shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}\red{COMENTAR MAS; ES LA DIFERENCIA CON WOBBES}. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
@@
 \acrshort{lme} scheme, which uses an anisotropic support to deal with 
-tensile inestability. Nonetheless this is out of the scope of the
-present document but will be incorporated in future research.
+tensile instability. \red{This is another benefit of the proposed methodology, that, although is out of the scope of the
+present document, will be incorporated in future research.}
 
@@
 This section is devoted to test the ability of both predictor-corrector
-time integration scheme and the local \textit{max-ent} approximants to
+time integration scheme and the Local \textit{Max-Ent} approximants to
 overcome spurious oscillations due to the grid crossing and high
-frequency loads under the context of \acrshort{mpm} Two different test has
-been adopted for this purpose, the benchmark proposed by Dyka \& Ingel
+frequency loads under the context of \acrshort{mpm}. Two different test have
+been adopted for this purpose: the benchmark proposed by Dyka \& Ingel
 (1995)\cite{Dyka1995} and the test proposed in the PhD thesis of
-Andersen (2009)\cite{thesis_Andersen_2009}. Thought them, the accuracy of the \acrshort{npc}
-scheme is compared to the standard \acrshort{fe}. In addition \acrshort{lme} solutions
+Andersen (2009)\cite{thesis_Andersen_2009}. On the one hand, the accuracy of the \acrfull{npc}
+scheme is compared to the standard \acrfull{fe} in order to assess the performance of the time integration schemes. On the other hand,  \acrshort{lme} solutions
 are compared with those provided by \acrfull{ugimp} and Q4 shape
 functions. To avoid some mesh-dependent issues, in all
-calculations a regular background mesh was setted. All simulations were performed with in-hose software.
-
-\subsection{Dyka bar \cite{Dyka1995}}
+calculations a regular background mesh was set. All simulations were performed with in-hose software.
+
+\subsection{Dyka's bar \cite{Dyka1995}}
 \label{sec:dyka-bar}
 
-This benchmark was proposed due to its ability to shows the capability
+This benchmark was proposed \red{by Dyka~\cite{Dyka1995} since allows so study easily the capability}
 of the proposed time integration algorithm to avoid velocity
-fields instabilities. It consists in a one-dimensional bar with a
-length of 0.1333 meters, sketched in the
-figure~\ref{fig:Dyka_Bar}. The boundary conditions are: in the right
-border displacement are constrained ($\vect{v} \rvert_{x=L} = 0$) and
-in the left displacement are let free ($\tens{\sigma} \rvert_{x=0} =
-0$). And a initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
-last quarter of it. Finally, the elastic parameters consider for this test are:
+field instabilities. It consists of a one-dimensional bar of a length of 0.1333 meters, sketched in the
+figure~\ref{fig:Dyka_Bar}. The boundary conditions are: displacements are constrained ($\vect{v} \rvert_{x=L} = 0$) in the right
+border, letting free in the rest of the body and ($\tens{\sigma} \rvert_{x=0} =
+0$). An initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
+left quarter of the bar. Finally, the elastic parameters considered for this test are:
 \begin{itemize} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this case a duration of 0.0001 seconds for the simulation is
-consider. Therefore, the elastic wave generated travel thorough the bar
+In this case, \cancel{a duration of } 0.0001 seconds \red{are considered }in the simulation. Therefore, the elastic wave generated travel through the bar
 (from A to C and back to A) at least two times. For the spatial
-discretization we adopt a set of seven nodal mesh sizes (0.1, 0.3325, 0.5,
-1.0, 3.3325, 6.665, 10.0) in millimeters. For each element a number of
+discretization, a set of seven nodal mesh sizes (0.1, 0.3325, 0.5,
+1.0, 3.3325, 6.665, 10.0 millimeters) are considered. For each element a number of
 four particles was selected. In the initial layout, particles are
-occupying the exact quadrature points of a linear quadrilateral. With
-the exception of the \acrshort{ugimp} simulation where gaps or overlap between
-voxels of each particle are not allowed. In those cases, each particles
-occupy the center of each cell quarter. For all simulations, time step
+occupying the exact quadrature points of a linear quadrilateral, with
+the exception of the \acrshort{ugimp} simulation, where gaps or overlap between
+voxels of each particle are not allowed. In those cases, each particle
+occupies the center of each cell quarter. For all simulations, time step
 is controlled by a Courant-Friedrichs-Levy condition of 0.1, were the adopted
-celerity is computed as,
+celerity is computed as:
 \begin{equation}
   \label{eq:Cel}
-  Cel = \max\{\max_{p \in \Omega_p}\{ \vect{v}_p \} , \max_{p \in \Omega_p}\{ \sqrt{\frac{E_p}{\rho_p}} \} \}
-\end{equation}
-A important consideration regarding modellization concerns to the
+  Cel = \max\{\max_{p \in \Omega_p}\{ \vect{v}_p \} , \max_{p \in \Omega_p}\{ \sqrt{\frac{E_p}{\rho_p}} \} \}.
+\end{equation}
+An important consideration regarding modellization concerns to the
 background mesh. Notice that free border of the bar has a maximum
@@
 required in order to accommodate the unconstrained displacement of the
-particles in the left border of the bar. Naturally this problem arise
+particles in the left border of the bar. Naturally this problem arises
 when the mesh size is small enough that relative displacement of the
-particles are larger then the distance to the border, so grid crossing
+particles is larger then the distance to the border, so grid crossing
 phenomena could appear even in those cases with infinitesimal
 displacements.
+
+In this case, an analytical solution can be obtained
+through the characteristics method, described in the appendix
+\ref{app:analytical_sol}. To measure the convergence of the solutions
+for the different time integration and approximation schemes the
+root-mean-square (RMS) error in the velocity field is computed. RMS
+error is defined as
+\begin{equation}
+  \label{eq:RMS}
+  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
+\end{equation}
+where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
+numerical solutions evaluated in the final time step in the position
+of each particle.
+\red{In Fig.
+\ref{fig:Dyka-error-evol} the evolution of the RMS is obtained for both time integration schemes.
+The right figure, with the \acrshort{NPC} results, shows lower values of the estimated error, denoting the higher performance of this methodology.
+About the spatial discretization, the \acrshort{LME} schemes show an error comparable to the obtained with the \acrshort{uGIMP}, being even lower close to the grid-crossing region.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
   }
-  \caption{Velocity evolution at the point in the Dyka bar left side,
+  \caption{Velocity error evolution at the point A in the Dyka's bar ,
     convergence plots for \acrshort{fe} and \acrshort{npc}. The plot is subdivided with
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this case, an analytical solution is possible
-thought the characteristics method described in the appendix
-\ref{app:analytical_sol}. To measure the convergence of the solutions
-for the different time integration and approximation schemes the
-root-mean-square (RMS) error in the velocity field is computed. RMS
-error is defined as
-\begin{equation}
-  \label{eq:RMS}
-  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
-\end{equation}
-where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
-numerical solutions evaluated in the final time step in the position
-of each particle. A first comparative between both time integration
-scheme is plotted in figure \ref{fig:Dyka-NPC-FE}. It demonstrates the
+
+A first comparative between the velocity results of both time integration
+schemes is plotted in figure \ref{fig:Dyka-NPC-FE}. It demonstrates the
 superior performance of the \acrshort{npc} \textit{versus} the \acrshort{fe}. In the \acrshort{npc} the
 spurious oscillations are quickly mitigated in the first time steps,
-and does not propagate the error in time in opposite to \acrshort{fe} where the
-simulation becomes unstable after $6E^{5}$ seconds. Figure
+and the error is not propagated in time, opposite to the results of the \acrshort{fe} scheme, where the
+simulation becomes unstable after $6E^{5}$ seconds. \cancel{Figure
 \ref{fig:Dyka-error-evol} also remarks the remarkable difference
-between both schemes. 
+between both schemes.} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Figure \eqref{fig:Dyka-LME-gamma} shows the sensibility of the \acrshort{lme}
-approximation scheme to variations in the a-dimensional parameter
-$\beta$ that controls the value of the regularization parameter
-$\gamma$ depending of the mesh size. Notice how lower values of
+approximation scheme to variations in the parameter
+$\gamma$, which is the one that controls the value of the regularization parameter
+$\beta$ together with of the mesh size. Notice how lower values of
 gamma exhibits a behaviour with a soft decay in some parts of the
@@
 materials. On the other hand larger values of the parameter $\beta$
-makes the solution tend to the linear \acrshort{fem} solution as the athermal
-limit is reached \cite{Arroyo2006}. Intermediate values of the
+makes the solution tend to the linear \acrshort{fem} solution as the athermal limit is reached \cite{Arroyo2006}. Intermediate values of the
 regularization parameters give us a compromise between the both
-scenarios here described. An additional observation concerning the
-solution sensibility to regularization parameters occurs when mesh
-size decreases. For larger mesh size where the relative particle displacement
+scenarios here described. An additional observation, concerning to the
+solution sensibility depending on the regularization parameters, \red{is the behaviour of the solution depending on the decreasing of mesh
+size}. For larger mesh sizes, where the relative particle displacement
 is negligible in comparison with the cell size, the global behaviour
-is \acrshort{fem}-like, therefore larger values of $\gamma$ has offers better
-results. On the other hand, when mesh size is small enough to produce
-grid-crossing and mesh-free behaviour is required to ensures the
-convergence of the solution, tiny values of $\gamma$ has a better
-performance. Convergence plot in figure \eqref{fig:Dyka-error-evol}
-shows how the slope for the larger values of $\gamma$ decreases
-monotonically with the value of the mesh size, in contrast to larger
-values of it, whose suffers a punishment of the performance when significant
-movement of the particles occurs as far mesh size is reduced.  
+is \acrshort{fem}-like; therefore, larger values of $\gamma$ \red{may offer better results}. On the other hand, when mesh size is small enough to produce
+grid-crossing meshfree behaviour is required to ensure the
+convergence of the solution and tiny values of $\gamma$ \red{may lead to better
+performances}. Convergence plot in figure \eqref{fig:Dyka-error-evol}
+shows how the slope, for the larger values of $\gamma$, decreases
+monotonically with the value of the mesh size, in contrast with larger
+values of $\gamma$, \red{where the performance is punished with significant
+movement of the particles as far as the mesh size is reduced.} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \caption{Sensitive of LME approximants performance to changes in the
-    adimensional regularization parameter $\gamma = \beta/h^2$. To
+    dimensionless regularization parameter $\gamma = \beta/h^2$. To
     illustrate it, the velocity evolution at the point in the bar left side
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Figure \ref{fig:Dyka-uGIMP-LME} compares the performance of the
+
+\red{The performance of the
 \acrshort{ugimp}~\cite{Bardenhagen2004} shape function \textit{versus} the \acrshort{lme} approximation scheme with
-a adimensional regularization parameter $\gamma$ of 4.0. Although it
-does not shows remarkable differences, \acrshort{lme} approximats exhibits a more
-robust behaviour than the \acrshort{ugimp} shape functions. Regarding this, notice
+a dimensionless regularization parameter $\gamma$ of 4.0 is compared in Figure \ref{fig:Dyka-uGIMP-LME}. Although remarkable differences are not observed, more
+robust behaviour is exhibited by the \acrshort{lme} approximants than the \acrshort{ugimp} shape functions.} Regarding this, notice
 the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5
-millimeters. This is because during these simulation the \acrshort{ugimp} suffered an unstable
-increase of the error which yield unacceptable results. A feasible
+millimeters. \red{The reason is due to an unstable
+increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yield unacceptable results}. A feasible
 explanation for this phenomena could be the presence of numerical
@@
 should be done in this direction for getting a better comprehension of
-this phenomena. In opposite, \acrshort{lme} approximation does not
-suffers this phenomena either with irregular nodal layout.
+this phenomenon. \red{Conversely, this shortcoming is not suffered by \acrshort{lme}, independently of regular or with irregular nodal layout.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Finally, figure \ref{fig:Dyka-OTM-MPM} compares the solution obtained
-with \acrshort{otm}~\cite{Li2010} \textit{versus} the solution obtained with \acrshort{mpm},
-both with same time integration scheme and spatial discretization. For
-this case the performance of \acrshort{mpm} is robust and stable than
+
+Finally, the \acrshort{otm}~\cite{Li2010} \textit{versus} obtained solution is compared against the one obtained with \acrshort{mpm}, both with same time integration scheme and spatial discretization, and results are shown in figure \ref{fig:Dyka-OTM-MPM}.
+In
+this case, the performance of \acrshort{mpm} presents better robustness and stability than the
 \acrshort{otm}. During the first half of the simulation both method 
@@
 simulation after the elastic wave has travel from the free border to
-the fixed one and back, in \acrshort{otm} the solution becomes noisy than the
+the fixed one and back, in \acrshort{otm} the solution becomes more noisy than the
 one performed by \acrshort{mpm}.  
@@
 
-\subsection{Andersen block}
+\clearpage
+\subsection{Rigid block}
 \label{sec:andersen-block}
@@
     \input{Figures/Block.tex}}
-  \caption{Geometrical description of a soil block }.}
+  \caption{Geometrical description of a soil block }.
   \label{fig:block}
@@
 hyperbolic despite the fact it does not have a second order
-temporal derivative as \eqref{eq:1D-wave-elastic}. A proof of this can
+time derivative as \eqref{eq:1D-wave-elastic}. A proof of this can
 be easily obtained if we get the zeros of the hypersurface defined by

### 2020-04-27 LME-MPM.tex
Cambios Figuras e Introducción

--- 2020-04-26 LME-MPM.tex
@@
 
-\usepackage{lineno,hyperref}
+\usepackage{lineno}
+% \usepackage{hredyperref}
 \usepackage{float}
@@
   \ensuremath{\mathbf{{#1}}}
-}
-\newcommand{\red}[1]{
-  \textcolor{red}{{#1}}
 }
@@
 
+\newcommand{\red}[1]{
+  \textcolor{red}{{#1}}
+}
+
+\newcommand{\MMP}[1]{
+  \textcolor{blue}{{#1}}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \modulolinenumbers[5]
@@
   limitation in this paper, an Explicit Predictor-Corrector time
-  integration scheme has been proposed. Its \textcolor{red}{powerful} \cancel{superior} performance
-  mitigates the presence of spurious oscillations with minimal dissipation in high
-  frequency problems. Other source of numerical noise in \acrshort{mpm} 
-  occurs when the material points cross computational grid
-  boundaries, being this issue motivated by the lack of smoothness of the interpolation
-  functions. This noise results in spurious local variations at the material
-  points, where strain-stress fields are computed. This could lead to inaccurate solutions as well as aborted simulations in the worst cases. To overcome it,
-  this document adopts the \acrfull{lme} approximation schemes as a
-  robust substitute of the traditional shape function in
+  integration scheme has been proposed. Its \textcolor{red}{powerful}
+  \cancel{superior} performance mitigates the presence of spurious
+  oscillations with minimal dissipation in high frequency
+  problems. Other source of numerical noise in \acrshort{mpm} occurs
+  when the material points cross computational grid boundaries, being
+  this issue motivated by the lack of smoothness of the interpolation
+  functions. This noise results in spurious local variations at the
+  material points, where strain-stress fields are computed. This could
+  lead to inaccurate solutions as well as aborted simulations in the
+  worst cases. To overcome it, this document adopts the \acrfull{lme}
+  approximation schemes as a robust substitute of the traditional shape function in
   \acrshort{mpm}. \acrshort{lme} approximation may be regarded
@@
 schemes which reduce the presence of high frequency noises by
-filtering them or increasing \red{somehow} the accuracy. \cancel{of the time integration
-scheme.} One of the most popular is the \acrfull{igimp}
-Charlton {\it et al.} (2017)~\cite{Charlton2017} \red{DECIR MAS DE ESTO}. More recently Tran \&
-Solowski (2019)~\cite{Tran2019e} proposed a generalised-$\alpha$ scheme
-for \acrshort{mpm} with promising results but at the expense of increasing
-the computational effort. In this paper a less time consuming and high
-efficient explicit predictor-corrector integration method has been
+filtering them or increasing \red{somehow} the accuracy. \cancel{of
+  the time integration scheme.} \MMP{One of the first attempts of it was
+the proposal of an implicit time integration scheme by Guilkey \&
+Weiss \cite{Guilkey_2003}. More recently Wang {\it et al.}
+\cite{Wang_2016} to downsize this spurious noises add a nonvoiscous
+damping to the linear momentum balance equation, and later Charlton
+{\it et al.} \cite{Charlton_2017} extended this scheme to the
+\acrshort{gimp} approach, and introducing the well-know
+\acrfull{igimp} method. However, the local damping introduced by
+\cite{Wang_2016} can totally over-damp the solution in time-dependent
+simulations such as in consolidation process. Within the explicit
+time integration schemes, Lu {\it et al.}\cite{LU_2018} introduced the time-discontinuous Galerkin method to control the spurious noises
+propagation, and later Tran \& Solowski~\cite{Tran2019e}
+proposed a generalised-$\alpha$ scheme for \acrshort{mpm} with
+promising results but at the expense of increasing the computational
+effort.}
+In this paper a less time consuming and high efficient explicit predictor-corrector integration method has been
 proposed. It consists in an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method

### 2020-04-27 LME-MPM.tex
Nuevo pdf
Cambios comentarios PNA

@@
 
-\newcommand{\red}[1]{
+\newcommand{\PNA}[1]{
   \textcolor{red}{{#1}}
@@
   \textcolor{blue}{{#1}}
+}
+
+\newcommand{\MMS}[1]{
+  \textcolor{gree}{{#1}}
 }
@@
   predictor-corrector scheme\\
-  \red{On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme}}
+  \PNA{On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme}}
 
@@
   integration scheme has been proposed. Its \textcolor{red}{powerful}
-  \cancel{superior} performance mitigates the presence of spurious
-  oscillations with minimal dissipation in high frequency
-  problems. Other source of numerical noise in \acrshort{mpm} occurs
-  when the material points cross computational grid boundaries, being
-  this issue motivated by the lack of smoothness of the interpolation
-  functions. This noise results in spurious local variations at the
-  material points, where strain-stress fields are computed. This could
-  lead to inaccurate solutions as well as aborted simulations in the
-  worst cases. To overcome it, this document adopts the \acrfull{lme}
-  approximation schemes as a robust substitute of the traditional shape function in
-  \acrshort{mpm}. \acrshort{lme} approximation may be regarded
-  as a \textit{thermalization} of Delaunay triangulation which resolves the
+  performance mitigates the presence of spurious oscillations with
+  minimal dissipation in high frequency problems. Other source of
+  numerical noise in \acrshort{mpm} occurs when the material points
+  cross computational grid boundaries, being this issue motivated by
+  the lack of smoothness of the interpolation functions. This noise
+  results in spurious local variations at the material points, where
+  strain-stress fields are computed. This could lead to inaccurate
+  solutions as well as aborted simulations in the worst cases. To
+  overcome it, this document adopts the \acrfull{lme} approximation
+  schemes as a robust substitute of the traditional shape function in
+  \acrshort{mpm}. \acrshort{lme} approximation may be regarded as a
+  \textit{thermalization} of Delaunay triangulation which resolves the
   degenerate cases resulting from the lack or uniqueness of the
-  triangulation. Furthermore, by modifying a regularization parameter they
-  are able to behave finite element like or as a meshfree
+  triangulation. Furthermore, by modifying a regularization parameter
+  they are able to behave finite element like or as a meshfree
   method. This capability allows to face a wide range of physics
@@
 without suffer mesh distortion inaccuracies.
-\red{One of the main fields where this method is strong is the dynamic one since the original time integration scheme proposed was the \acrfull{fe}~\cite{Sulsky1994}, carried out in a explicit manner.
+\PNA{One of the main fields where this method is strong is the dynamic one since the original time integration scheme proposed was the \acrfull{fe}~\cite{Sulsky1994}, carried out in a explicit manner.
 However, in this type or problems, the main instabilities of the original \acrshort{mpm} are even marked.}
 
-\cancel{However, this method suffers other kind of instabilities, such those} \red{On the one hand, the main source of instability occurs}
-when material points cross cell boundaries. This \cancel{give rise to} provoked the
-development of other interpolation techniques to overcome this
-limitation such as the \acrfull{gimp} method Bardenhagen \& Kober
-(2004)~\cite{Bardenhagen2004}, which has
+\PNA{On the one hand, the main source of instability occurs} when
+material points cross cell boundaries. This provoked the development
+of other interpolation techniques to overcome this limitation such as
+the \acrfull{gimp} method Bardenhagen \& Kober (2004)~\cite{Bardenhagen2004}, which has
 demonstrated to have a good performance in the finite deformation
@@
 
-This document adopts the \acrfull{lme}, or Local \textit{Max-Ent} approximates, as a robust substitute \cancel{for the
-wide range of} \red{of the aforementioned} shape functions in \acrshort{mpm}. First introduced by Arroyo \& Ortiz
+This document adopts the \acrfull{lme}, or Local \textit{Max-Ent} approximates, as a robust substitute \PNA{of the aforementioned} shape functions in \acrshort{mpm}.
+First introduced by Arroyo \& Ortiz
 (2006)~\cite{Arroyo2006}, it belongs to the class of convex 
@@
 recently, under \acrshort{mpm} framework, the work made by Wobbes {\it et
-  al.}(2020)~\cite{Wobbes2020}. \cancel{but without exploring} \red{The proposed research delves into the benefits of
+  al.}(2020)~\cite{Wobbes2020}.\PNA{The proposed research delves into the benefits of
 the regularization parameter, \gls{LME-beta}, and the analogy of the different obtained shape functions derive by the tuning of this parameter and the traditional \acrshort{mpm} ones.}
@@
 schemes which reduce the presence of high frequency noises by
-filtering them or increasing \red{somehow} the accuracy. \cancel{of
-  the time integration scheme.} \MMP{One of the first attempts of it was
+filtering them or increasing \PNA{somehow} the accuracy. \MMP{One of the first attempts of it was
 the proposal of an implicit time integration scheme by Guilkey \&
@@
 {\it et al.} \cite{Charlton_2017} extended this scheme to the
-\acrshort{gimp} approach, and introducing the well-know
-\acrfull{igimp} method. However, the local damping introduced by
+\acrshort{gimp} approach introducing the \acrfull{igimp}
+method. However, the local damping introduced by 
 \cite{Wang_2016} can totally over-damp the solution in time-dependent
@@
 promising results but at the expense of increasing the computational
-effort.}
-In this paper a less time consuming and high efficient explicit predictor-corrector integration method has been
+effort.} In this paper a less time consuming and high efficient explicit predictor-corrector integration method has been
 proposed. It consists in an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
@@
 suitable combination of the \acrshort{lme} family shape functions, and the proposal of an explicit predictor-corrector scheme. The advantages of
-this approach will be illustrated through several \cancel{simple but} challenging test cases \red{on the elastic regime}: the
+this approach will be illustrated through several challenging test cases \PNA{on the elastic regime}: the
 propagation of shock waves in a elastic bar and the response of a block of soil gradually loaded with gravitational forces.
@@
 
-\red{Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are describe in subsection \ref{sec:derivation-mpm},\ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.}
+\PNA{Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are describe in subsection \ref{sec:derivation-mpm},\ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.}
 
@@
 field \gls{u} through the following set of governing equations and
-restrictions that must be satisfied. \red{First (i) the \textit{compatibility
+restrictions that must be satisfied. \PNA{First (i) the \textit{compatibility
   equation}, where the the strain field \gls{strain} is extracted from \gls{u} is defined as:}
@@
 in the spatial derivatives can be neglected.
-\red{Therefore, the stress field \gls{stress} will be considered the corresponding conjugate variable for the strain field, being the one} which satisfies (ii) the \textit{conservation of
+\PNA{Therefore, the stress field \gls{stress} will be considered the corresponding conjugate variable for the strain field, being the one} which satisfies (ii) the \textit{conservation of
   momentum equation}:
@@
 \end{equation}
-\red{In this research, plane strain Linear Elasticity has been considered.
+\PNA{In this research, plane strain Linear Elasticity has been considered.
 Thus the constitutive tensor, \tens{D}, is the well known linear elastic one.} The final restriction is (iv) the mass conservation, which can be obtained by
@@
 virtual displacement field $\vect{u}^{\psi}_{p}$. Therefore, employing
-the definition of the material integral, where Riemann \red{ALGUNA CITA AQUI}
+the definition of the material integral, where Riemann \PNA{ALGUNA CITA AQUI}
 integral definition is recovered as an addition of a finite set of points, and
@@
 , I = 1,2\ldots ,N_n$, is generated, being $N_n$ the number of grid
-nodes. \red{Spatial derivatives, such as gradients and
+nodes. \PNA{Spatial derivatives, such as gradients and
 divergences, are computed through the support of the background mesh.}
@@
 \end{equation}
-Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order
-\cancel{temporal} \red{time} integration scheme is required. Therefore, time is
+Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order \PNA{time} integration scheme is required. Therefore, time is
 discretized into a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
@@
 \end{equation}
-\red{Traditionally, Eqs.
+\PNA{Traditionally, Eqs.
 \eqref{eq:particle_balance_forces3} and ~\eqref{eq:Updated_Lagrangian},
@@
 
-\red{As was stated previosuly, an explicit forward Euler algorithm has been utilized widely within the \acrshort{MPM} methodology. This scheme has been described in detail by many researchers
+\PNA{As was stated previosuly, an explicit forward Euler algorithm has been utilized widely within the \acrshort{MPM} methodology. This scheme has been described in detail by many researchers
 \cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and can be sketched by the scheme of the figure~\ref{fig:MPM_algorithm}.}
@@
 However, as Andersen (2009)\cite{thesis_Andersen_2009} pointed out, this algorithm has been shown to be numerically unstable due to that
-$\vect{f}_I^{int,k}$ can be finite for an infinitesimal nodal mass
-$\tens{m}$\red{NO ENTIENDO??}. This issue may lead to numerical issues when nodal acceleration
+$\vect{f}_I^{int,k}$ can be infinite for an infinitesimal nodal mass
+$\tens{m}$. This issue may lead to numerical issues when nodal acceleration
 is obtained in the evaluation of the Eqs. \eqref{eq:Sulsky-1994-UL-x} and \eqref{eq:Sulsky-1994-UL-v}. Hence, a
@@
 \end{equation*}
-\red{The nodal \acrshort{mpm} stage allows to apply this method
+\PNA{The nodal \acrshort{mpm} stage allows to apply this method
 in the \acrshort{mpm} framework in a similar manner that the one
@@
     \eqref{eq:nodal_external_forces} in the time step $k+1$.
-    In the grid node, $I$ is fixed in one of the spatial dimensions, set it to
-    zero to make the grid nodal acceleration zero in that direction.\red{NO ENTIEND??}\\
+    \MMP{In those nodes where $\Deriv{\vect{v}_I^{k}}{t} \big\rvert_{\Gamma_d} = 0$,
+      the acceleration is fixed to zero and nodal forces are stored as
+      reactions.}\\
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
 made with the original \acrshort{mpm}, numerical noises appear when particles
-cross the cell boundaries. \red{Solving this issue is the main goal of the employment of the \acrshort{LME} shape functions}.
+cross the cell boundaries. \PNA{Solving this issue is the main goal of the employment of the \acrshort{LME} shape functions}.
 
@@
 recently tested under \acrshort{mpm} framework by Wobbes {\it et al.}
-(2020)\cite{Wobbes2020}. \red{The performed simulations of \acrshort{mpm}
+(2020)\cite{Wobbes2020}. \PNA{The performed simulations of \acrshort{mpm}
 within \acrshort{lme} in \cite{Wobbes2020} shows considerably more accurate stress
@@
 function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
-10$^{-6}$ \red{in this research} \cancel{for example},  would ensure a reasonable range of
+10$^{-6}$ \PNA{in this research},  would ensure a reasonable range of
 neighbours (see \cite{Arroyo2006} for details).
@@
 Motivated by their increased extents, particles may share an influence radius that lies outside of the simulation domain.
-Some researchers have solved this problem with the so called ``extra'' or ``ghost'' nodes \cancel{by other investigators}.
+Some researchers have solved this problem with the so called ``extra'' or ``ghost'' nodes.
 These nodes require especial treatment, similar
@@
 described does not requires the employment of this artifices.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{0.5\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Particle-discretization}
-  }
-  \caption{This tolerance defines the limit values of the influence
-    radius and is used thereafter to find the neighbour nodes of a
-    given integration point. The picture also shows the neighbourhood
-    criterion to select those node inside of \gls{domain}.} 
-  \label{fig:Particle-discretization}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Due to the \short{fem}-compatibility, the \acrshort{lme} shape function is degenerated to
@@
 \textit{regularization} parameter it is possible to get a \acrshort{gimp}-like
-shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}\red{COMENTAR MAS; ES LA DIFERENCIA CON WOBBES}. 
+shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}\PNA{COMENTAR MAS; ES LA DIFERENCIA CON WOBBES}. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \acrshort{lme} scheme, which uses an anisotropic support to deal with 
-tensile instability. \red{This is another benefit of the proposed methodology, that, although is out of the scope of the
+tensile instability. \PNA{This is another benefit of the proposed methodology, that, although is out of the scope of the
 present document, will be incorporated in future research.}
@@
 
-This benchmark was proposed \red{by Dyka~\cite{Dyka1995} since allows so study easily the capability}
+This benchmark was proposed \PNA{by Dyka~\cite{Dyka1995} since allows so study easily the capability}
 of the proposed time integration algorithm to avoid velocity
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this case, \cancel{a duration of } 0.0001 seconds \red{are considered }in the simulation. Therefore, the elastic wave generated travel through the bar
+In this case, 0.0001 seconds \PNA{are considered }in the simulation. Therefore, the elastic wave generated travel through the bar
 (from A to C and back to A) at least two times. For the spatial
@@
 of each particle.
-\red{In Fig.
+\PNA{In Fig.
 \ref{fig:Dyka-error-evol} the evolution of the RMS is obtained for both time integration schemes.
@@
 and the error is not propagated in time, opposite to the results of the \acrshort{fe} scheme, where the
-simulation becomes unstable after $6E^{5}$ seconds. \cancel{Figure
-\ref{fig:Dyka-error-evol} also remarks the remarkable difference
-between both schemes.} 
+simulation becomes unstable after $6E^{5}$ seconds.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 scenarios here described. An additional observation, concerning to the
-solution sensibility depending on the regularization parameters, \red{is the behaviour of the solution depending on the decreasing of mesh
+solution sensibility depending on the regularization parameters, \PNA{is the behaviour of the solution depending on the decreasing of mesh
 size}. For larger mesh sizes, where the relative particle displacement
 is negligible in comparison with the cell size, the global behaviour
-is \acrshort{fem}-like; therefore, larger values of $\gamma$ \red{may offer better results}. On the other hand, when mesh size is small enough to produce
+is \acrshort{fem}-like; therefore, larger values of $\gamma$ \PNA{may offer better results}. On the other hand, when mesh size is small enough to produce
 grid-crossing meshfree behaviour is required to ensure the
-convergence of the solution and tiny values of $\gamma$ \red{may lead to better
+convergence of the solution and tiny values of $\gamma$ \PNA{may lead to better
 performances}. Convergence plot in figure \eqref{fig:Dyka-error-evol}
@@
 monotonically with the value of the mesh size, in contrast with larger
-values of $\gamma$, \red{where the performance is punished with significant
+values of $\gamma$, \PNA{where the performance is punished with significant
 movement of the particles as far as the mesh size is reduced.} 
@@
 
-\red{The performance of the
+\PNA{The performance of the
 \acrshort{ugimp}~\cite{Bardenhagen2004} shape function \textit{versus} the \acrshort{lme} approximation scheme with
@@
 the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5
-millimeters. \red{The reason is due to an unstable
+millimeters. \PNA{The reason is due to an unstable
 increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yield unacceptable results}. A feasible
@@
 should be done in this direction for getting a better comprehension of
-this phenomenon. \red{Conversely, this shortcoming is not suffered by \acrshort{lme}, independently of regular or with irregular nodal layout.}
+this phenomenon. \PNA{Conversely, this shortcoming is not suffered by \acrshort{lme}, independently of regular or with irregular nodal layout.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-04-27 LME-MPM.tex
Quedan_conclusiones

@@
 
-The following test was proposed to measure proof the ability of this
+The following test was proposed to \PNA{validate} \cancel{measure proof} the ability of the proposed
 interpolation technique to deal with grid crossing instabilities. It
-consists in the simulation of a square block of soil incrementally
+consists of the simulation of a square block of soil incrementally
 loaded by a body force. Details of the problem are sketched in figure~\ref{fig:block}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-This test was taken from PhD thesis of Andersen (2009)\cite{thesis_Andersen_2009}. The
-elastic parameters consider for this test are: 
+This test was \cancel{taken from PhD thesis of Andersen} \PNA{previously proposed by Andersen} (2009)\cite{thesis_Andersen_2009}. The
+elastic parameters considered for this test are: 
 \begin{itemize} 
@@
 \end{itemize}
-The gravity force is a apply as an external force according to the
-equations \eqref{eq:particle_body_forces},
+The gravity force is applied as an external force according to the
+equations \eqref{eq:particle_body_forces} and
 \eqref{eq:nodal_external_forces}. Using a total time period of T (20
 seconds) to apply the gravity, it is increased from 0 to 9.81$m/s$
-with a sinus function until T/2 and then maintained constant until T
-in order to arrive to a state of equilibrium, 
+with a sinusoidal function until T/2 and then maintained constant until T
+in order to reach the equilibrium state:
 \begin{equation}
@@
 Courant number of 0.1. On the other hand, the explicit
-predictor-corrector scheme is here employed looking forward getting better results. For the
+predictor-corrector scheme is here employed looking forward to getting better results. For the
 initial spatial discretization four particles per cell
@@
 during the loading process. The result is physically realistic as
-stress increments linearly from the top to the bottom of the specimen,
+the stress increases linearly from the top to the bottom of the specimen,
 and the value of the vertical stress in a material point located in
-the bottom of the specimen oscillates centered in $5.2 MPa$, which is
+the bottom of the specimen oscillates around $5.2 MPa$, which is
 the analytic value given by $\sigma_{yy} = \rho g h_y$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Figure~\ref{fig:vertical-displacement-block} shows the vertical
@@
 interpolation technique (Q4) turns out to be unstable during
-cell-crossing and consequently fails. The \acrshort{ugimp} simulation
-is more stable than the one performed by the Q4. Despite this is still
+cell-crossing and consequently fail. The \acrshort{ugimp} simulation
+is more stable than the one performed by the Q4, \PNA{although} \cancel{Despite this} is still
 unstable and could trigger severe oscillations in simulation with
@@
 lower value it behaves in a similar way to the \acrshort{ugimp}. This behaviour
-was noticed previously by \cite{Arroyo2006}, were authors highlight
-how by adjusting the spatial variation of $\beta(\vect{x})$, it is
+was noticed previously by \cite{Arroyo2006}, were authors highlighted
+how, by adjusting the spatial variation of $\beta(\vect{x})$, it is
 possible to select regions of the domain of analysis which are treated

### 2020-04-27 _region_.tex
Cambios en apéndice y modificaciones a comentarios

@@
-\message{ !name(LME-MPM.tex)}
-\documentclass[preprint,12pt,a4paper]{elsarticle}
-
-\usepackage{lineno,hyperref}
+\message{ !name(LME-MPM.tex)}\documentclass[preprint,12pt,a4paper]{elsarticle}
+
+\usepackage{lineno}
+\usepackage{hyperref}
 \usepackage{float}
@@
 \newacronym{ctls}{CTLS}{Conservative Taylor Least Squares}
+\newacronym{npc}{NPC}{Newmark Predictor-Corrector}
+\newacronym{fe}{FE}{Forward Euler}
 
 % End glossaries
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\PNA}[1]{
+  \textcolor{red}{{#1}}
+}
+
+\newcommand{\MMP}[1]{
+  \textcolor{blue}{{#1}}
+}
+
+\newcommand{\MMS}[1]{
+  \textcolor{gree}{{#1}}
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   dynamic problems: Local-maximum entropy approximation and explicit
-  predictor-corrector scheme}
+  predictor-corrector scheme\\
+  \PNA{On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme}}
 
@@
   propagation and other high frequency problems is still challenging
-  under this approach due the incapability of the standard \acrshort{MPM} time
+  under this approach due the incapability of the standard \acrshort{mpm} time
   integration scheme to filter spurious noises. To overcome this
-  limitation in this paper, an explicit predictor-corrector time
-  integration scheme has been proposed. Its superior performance
-  mitigates the presence of spurious oscillations with minimal dissipation in high
-  frequency problems. Other source of numerical noise in \acrshort{MPM} 
-  occurs when to material points cross computational grid
-  boundaries and motivated due to the lack of smoothness of the interpolation
-  functions. This noise results in spurious local variations at the material
-  points, where strain-stress fields are computed. This could invalidate
-  the solution in one case, or damage it in another. To overcome it,
-  this document adopts the \acrfull{lme} approximation schemes a
-  robust substitute for the wide range of shape function in
-  \acrshort{MPM}. Local \textit{max-ent} approximation may be regarded
-  as a \textit{thermalization} of Delaunay triangulation which resolves the
+  limitation in this paper, an Explicit Predictor-Corrector time
+  integration scheme has been proposed. Its \textcolor{red}{powerful}
+  performance mitigates the presence of spurious oscillations with
+  minimal dissipation in high frequency problems. Other source of
+  numerical noise in \acrshort{mpm} occurs when the material points
+  cross computational grid boundaries, being this issue motivated by
+  the lack of smoothness of the interpolation functions. This noise
+  results in spurious local variations at the material points, where
+  strain-stress fields are computed. This could lead to inaccurate
+  solutions as well as aborted simulations in the worst cases. To
+  overcome it, this document adopts the \acrfull{lme} approximation
+  schemes as a robust substitute of the traditional shape function in
+  \acrshort{mpm}. \acrshort{lme} approximation may be regarded as a
+  \textit{thermalization} of Delaunay triangulation which resolves the
   degenerate cases resulting from the lack or uniqueness of the
-  triangulation. Furthermore, by modifying a regularization parameter they
-  are able to behave finite element like or as a mesh-free
+  triangulation. Furthermore, by modifying a regularization parameter
+  they are able to behave finite element like or as a meshfree
   method. This capability allows to face a wide range of physics
@@
 Since the proposal of \acrshort{mpm} by Sulsky {\it  et al.}
-(1994)~\cite{Sulsky1994} as a generalization to solids of the \acrfull{flip} method~\cite{Brackbill1986}. It popularity
+(1994)~\cite{Sulsky1994} as a generalization to solids of the \acrfull{flip} method~\cite{Brackbill1986}, its popularity
 has increased due to its ability to deal with large strain regime
-without suffer mesh distortion inaccuracies.
-
-However, this method suffers other kind of instabilities, such those
-when material points crossing cell boundaries. This give rise to the
-development of other interpolation techniques to overcome this
-limitation such as the \acrfull{gimp} method Bardenhagen \& Kober (2004)~\cite{Bardenhagen2004}, which has
-demonstrate to have a good performance in the finite deformation
+without suffer mesh distortion inaccuracies.\PNA{One of the main fields where this method is strong is the dynamic one since the original time integration scheme proposed was the \acrfull{fe}~\cite{Sulsky1994}, carried out in a explicit manner.
+However, in this type or problems, the main instabilities of the original \acrshort{mpm} are even marked.}
+
+\PNA{On the one hand, the main source of instability occurs} when
+material points cross cell boundaries. This provoked the development
+of other interpolation techniques to overcome this limitation such as
+the \acrfull{gimp} method Bardenhagen \& Kober (2004)~\cite{Bardenhagen2004}, which has
+demonstrated to have a good performance in the finite deformation
 regime. However, in the absence of a regular grid, construction of the
 weighting functions is only achieved at considerable effort and
-computational cost.  Furthermore, as it is  a voxel based
+computational cost.  Furthermore, as it is a voxel-based
 discretization technique, it is prone to suffer voxel domains overlap
@@
 encountered by the finite element methods due to element distortion.
-A more robust alternative is the dual domain material point method
-(DDMP) proposed by Zhang {\it et al.}
+A more robust alternative is the \acrfull{ddmp} method proposed by Zhang {\it et al.}
 (2011)~\cite{Zhang2011a}. Unfortunately this method shows an
 unsatisfactory behaviour when particle/cell ratio
-decreases~\cite{DHAKAL2016301}, therefore DDMP requires a large number
-of particles needed for convergence, this
-makes the method very expensive. In recent years the employ of
-spline-lines has gain popularity with the introduction of the B-Spline
+decreases~\cite{DHAKAL2016301}. Therefore \acrshort{ddmp} a large number of particles is needed for convergence, what
+makes the method very expensive. In recent years the employment of
+spline-lines as shape functions has gain popularity with the introduction of the B-Spline 
 \acrshort{mpm} proposed by Roel Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
-this technique allows the employ of unstructured set of notes and
+this technique allows the employment of unstructured set of notes and
 particles. More recently, approximants derived from minimization has
-been introduced in to \acrshort{mpm} framework with the Conservative Taylor
-Least Squares (CTLS) reconstruction proposed by Wobbes {\it et al.}
-(2018)~\cite{E_Wobbes_2018}, unfortunately when particles are spread in
-a challenging way, the quality of the CTLS approximation decrease
-locally.
-
-This document adopts the \textit{local maximum-entropy approximation
-    schemes} (LME) as a robust substitute for the wide range of shape
-  function in \acrshort{mpm}. First introduced by Arroyo \& Ortiz
+been introduced in to the \acrshort{mpm} framework with the \acrfull{ctls}
+reconstruction proposed by Wobbes {\it et al.}
+(2018)~\cite{E_Wobbes_2018}. Unfortunately, when particles are spread in
+a challenging way, the quality of the \acrshort{ctls} approximation decreases locally.
+
+This document adopts the \acrfull{lme}, or Local \textit{Max-Ent} approximates, as a robust substitute\PNA{of the aforementioned} shape functions in \acrshort{mpm}. First introduced by Arroyo \& Ortiz
 (2006)~\cite{Arroyo2006}, it belongs to the class of convex 
 approximation schemes and provides a seamless transition between
-finite element method (FEM) and mesh-free interpolations. The
+\acrshort{fem} and meshfree interpolations. The
 approximation scheme is based on a compromise between minimizing the
 width of the shape function support and maximizing the information
-entropy of the approximation. The local \textit{max-ent} approximation
+entropy of the approximation. The \acrshort{lme} approximation
 may be regarded as a regularization, or \textit{thermalization}, of
 Delaunay triangulation which effectively resolves the degenerate cases
-resulting from the lack of uniqueness or the triangulation. Local
-\textit{max-ent} basis functions possess many desirable properties for
-mesh-free algorithms. First of all, they are entirely defined by the
+resulting from the lack of uniqueness or the triangulation. \acrshort{lme} basis functions possess many desirable properties for
+meshfree algorithms. First of all, they are entirely defined by the
 nodal set and the domain of analysis. They are also non-negative,
 satisfy the partition of unity property, and provide an exact
-approximation for affine functions~\cite{Arroyo2006}. This
-approximation scheme has been proof to have a good performance under
-the dynamic regime by other researchers like Navas {\it et al.}
-(2018)~\cite{Navas2018a} and Li {\it et al.} (2012)~\cite{Li2012} for
-Optimal Transportation Meshfree (OTM) method. And more
-recently under \acrshort{mpm} framework by Wobbes {\it et
-  al.}(2020)~\cite{Wobbes2020} but without exploring the benefits of
-the regularization parameter \gls{LME-beta}.
-
-This techniques are devoted to mitigate the
-``grid crossing'' error. Nevertheless, in the presence of shock waves spurious
-numerical noises appears despite of this using
-techniques~\cite{Tran2019e}. These numerical inaccuracies also known
-as wiggles are due to inaccuracies in the time discretization technique.
-A simple approach to face those spurious noises is to add a
-nonphysical damping source to the equilibrium equations, this
+approximation for related functions~\cite{Arroyo2006}.
+Important contributions on the Maximum-Entropy have been made by Sukumar and coworkers~\cite{Sukumar15} with Cell-based techniques and the ones carried within the \acrfull{otm} method.
+The latter methodology has been proven to have a good performance under
+the dynamic regime by other researchers, being important the contributions of Li {\it et al.} (2012)~\cite{Li2012} and Navas {\it et al.}
+(2018)~\cite{Navas:17b,Navas2018a} in the explicit regime and Navas {\it et al.}~\cite{Navas2016,Navas2016b,Navas:17c} and Wriggers and coworkers~\cite{Wriggers18} with implicit schemes. And more
+recently, under \acrshort{mpm} framework, the work made by Wobbes {\it et
+  al.}(2020)~\cite{Wobbes2020}.\PNA{The proposed research delves into the benefits of
+the regularization parameter, \gls{LME-beta}, and the analogy of the different obtained shape functions derive by the tuning of this parameter and the traditional \acrshort{mpm} ones.}
+
+The aforementioned techniques are devoted to mitigate the
+``grid crossing'' error. Nevertheless, in the presence of shock waves spurious,
+numerical noises appear despite of the employment of these
+techniques~\cite{Tran2019e}. These numerical inaccuracies, also known
+as wiggles, arise due to inaccuracies in the time discretization technique.
+A simple approach to face those spurious noises lies on the addition of nonphysical damping sources to the equilibrium equations. This
 approach has been widely employed in this and many other numerical
@@
 schemes which reduce the presence of high frequency noises by
-filtering them or increasing the accuracy of the time integration
-scheme. One of the most popular is the \acrfull{igimp}
-Charlton {\it et al.} (2017)~\cite{Charlton2017}, more recently Tran \&
-Solowski (2019)~\cite{Tran2019e} proposed a generalised-$\alpha$ scheme
-for \acrshort{mpm} with promising results but at the expense of increasing
-the computational effort. In this paper a less time consuming and high
-efficient explicit predictor corrector integration method has been
-proposed. It consists in an accommodation of the Newmark
-predictor-corrector or central difference explicit (CD). We have
-choose this method among other suitable alternatives as those proposed
+filtering them or increasing\PNA{somehow} the accuracy.\MMP{One of the first attempts of it was
+the proposal of an implicit time integration scheme by Guilkey \&
+Weiss \cite{Guilkey_2003}. More recently Wang {\it et al.}
+\cite{Wang_2016} to downsize this spurious noises add a nonvoiscous
+damping to the linear momentum balance equation, and later Charlton
+{\it et al.} \cite{Charlton_2017} extended this scheme to the
+\acrshort{gimp} approach introducing the \acrfull{igimp}
+method. However, the local damping introduced by 
+\cite{Wang_2016} can totally over-damp the solution in time-dependent
+simulations such as in consolidation process. Within the explicit
+time integration schemes, Lu {\it et al.}\cite{LU_2018} introduced the time-discontinuous Galerkin method to control the spurious noises
+propagation, and later Tran \& Solowski~\cite{Tran2019e}
+proposed a generalised-$\alpha$ scheme for \acrshort{mpm} with
+promising results but at the expense of increasing the computational
+effort.} In this paper a less time consuming and high efficient explicit predictor-corrector integration method has been
+proposed. It consists in an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
+has been chosen among other suitable alternatives as those proposed
 by Wilson {\it et al.} (1972)~\cite{Wilson1972} or Chung \& Hulbert
-(1993)~\cite{Geranlized_alpha_1993} because it simplicity and it good
-performance dealing with solids dynamics problems under a mesh-free
+(1993)~\cite{Geranlized_alpha_1993} because its simplicity and its good
+performance dealing with solid dynamic problems under a meshfree
 framework in~\cite{Navas2018a}.
@@
 The aim of this document is to mitigate the spurious oscillations due
-inaccuracies in both space and time discretization by the employ of a
-suitable combination of the maximum-entropy (or local
-\textit{max-ent}) family shape functions, and the proposal of
-a explicit predictor-corrector scheme. We illustrate the advantages of
-this approach thorough to simple but challenging test cases, like the
-propagation of shock waves in a elastic bar or the response of a block of soil
-gradually loaded with gravitational forces.
-
-The article is organized as follows. Section \ref{sec:Notation}
-briefly reviews the notation here employed. Next, Section \ref{sec:derivation-mpm}
-is devoted to present briefly the governing equations of the elastic
-problem, the variational formulation and the Galerkin procedure. In Section \ref{sec:epc-algor-mpm} an explicit predictor-corrector
-time integration scheme for \acrshort{mpm} is proposed. Section
-\ref{sec:local-max-ent} briefly reviews the local \textit{max-ent}
-basis functions here employed. In Section
+inaccuracies in both space and time discretization by the employment of a
+suitable combination of the \acrshort{lme} family shape functions, and the proposal of an explicit predictor-corrector scheme. The advantages of
+this approach will be illustrated through several challenging test cases\PNA{on the elastic regime}: the
+propagation of shock waves in a elastic bar and the response of a block of soil gradually loaded with gravitational forces.
+
+The article is organised as follows. Section \ref{sec:meshfree-methodology}
+is devoted to describe the meshfree methodology adopted in this
+research, first \acrshort{mpm} procedure is introduced in
+\ref{sec:derivation-mpm}, second the explicit predictor-corrector
+time integration scheme is presented in \ref{sec:epc-algor-mpm}, and
+third \acrshort{lme} approximation scheme will be introduced in
+\ref{sec:local-max-ent}. In Section
 \ref{sec:Application-linear-elasticity-dynamic-problems} applications
-to prove the numerical accuracy of the proposed approach are presented. Finally,
-conclusions and future research topics are exposed in Section \ref{sec:conclusions}.
-
-\section{The meshfreesubsection procedure}
-\label{sec:derivation-mpm}
+to prove the numerical accuracy of the proposed approach are
+presented. Finally, conclusions and future research topics are exposed in Section \ref{sec:conclusions}.
+
+\section{The meshfree methodology}
+\label{sec:meshfree-methodology}
 
 The aim of this section is to provide an overview of the standard
-explicit \acrshort{mpm} algorithm~\cite{Sulsky1994}. In consequence it
-is structured as follows: the governing equations will be introduced
-in \ref{sec:The boundary-value-problem}, later the variational statement of
-the problem will be presented \ref{sec:variational-formulation}, and
-finally a discretization procedure thorough Galerkin is performed in
-\ref{sec:Galerkin-procedure}. The method has three main steps: (i) a
+explicit \acrshort{mpm} algorithm~\cite{Sulsky1994}. Without loosing
+generality, the method is composed by three main steps: (i) a
 variational recovery process, where particle data is projected to the
 grid nodes, (ii) an Eulerian step, where balance of momentum equation
-is expressed as a nodal equilibrium equation thorough a FEM-like
+is expressed as a nodal equilibrium equation through a \acrshort{fem}-like
 procedure, and finally (iii) a Lagrangian advection of the
-particles. In consequence \acrshort{mpm} can be regarded as a
-Lagrangian-Eulerian method where particles carries on all the physical
+particles. In consequence, \acrshort{mpm} can be regarded as a
+Lagrangian-Eulerian method where particles carry on all the physical
 information and a set of background nodes is employed to
@@
 divergence operator, and finally $\Grad{\Box}$ and $\GradS{\Box}$
-denotes the gradient and its symmetric part. Einstain subscripts
-convention is adopted therefore repeated index means addition.
+denotes the gradient and its symmetric part. Einstein subscripts
+convention is adopted therefore repeated index means addition.\PNA{Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are describe in subsection \ref{sec:derivation-mpm},\ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.}
 
@@
 field \gls{u} through the following set of governing equations and
-restrictions that must be satisfied. First (i) the \textit{compatibility
-  equation} that extracts from \gls{u} the strain field \gls{strain} is,
+restrictions that must be satisfied.\PNA{First (i) the \textit{compatibility
+  equation}, where the the strain field \gls{strain} is extracted from \gls{u} is defined as:}
 \begin{equation}
@@
 \end{equation}
-together with essential boundary conditions of Dirichlet type
-$\varGamma_d$. An additional consideration over the strain field is
+together with essential boundary conditions of Dirichlet type \gls{dirichlet-boundary}. An additional consideration over the strain field is
 the assumption of inifinitesimal strain, therefore second order terms
-in the spatial derivatives can be neglected. The corresponding
-conjugate variable for the strain field if the stress field
-\gls{stress}, which satisfies (ii) the \textit{conservation of
-  momentum equation}
+in the spatial derivatives can be neglected.\PNA{Therefore, the stress field \gls{stress} will be considered the corresponding conjugate variable for the strain field, being the one} which satisfies (ii) the \textit{conservation of
+  momentum equation}:
 \begin{equation}
@@
 \end{equation}
-together with the natural boundary conditions of the Neumann type
-$\varGamma_n$. Next (iii) the constitutive equation as a linear
+together with the natural boundary conditions of the Neumann type \gls{neumann-boundary}.  An aditional component will be (iii) the constitutive equation as a linear
 application from $\Re^n$ to $\Re^n$, which relates the
-strain tensor with the stress tensor,
+strain tensor with the stress tensor:
 \begin{equation}
@@
 \end{equation}
-The final restriction is (iv) the mass conservation, which can be obtained by
+\PNA{In this research, plane strain Linear Elasticity has been considered.
+Thus the constitutive tensor, \tens{D}, is the well known linear elastic one.} The final restriction is (iv) the mass conservation, which can be obtained by
 setting to zero the total derivative of the density field,
@@
   \vect{u}^{\psi} \in \mathcal{H}^1_0(\Omega) = \{ \vect{u}^{\psi} \in
-  \mathcal{H}^1 \mid \vect{u}^{\psi} = \vect{0}\ \text{on}\ \Gamma_d \}.
-\end{equation}
-And which satisfies that the Cauchy sequences are convergent in $\varOmega$
+  \mathcal{H}^1 \mid \vect{u}^{\psi} = \vect{0}\ \text{on}\ \Gamma_d \};
+\end{equation}
+satisfying that the Cauchy sequences are convergent in \gls{domain} as well:
 \begin{equation}
@@
   \Integral{2}{\vec{t}\ \cdot \vec{u}^{\psi}} - \Integral{3}{\tens{\sigma} \colon
-   \tens{\varepsilon}^{\psi}},
+   \tens{\varepsilon}^{\psi}}.
 \end{equation}\\
-therefore (\ref{eq:BalanceMomentum_wf}) together with
+Thus, equation~\eqref{eq:BalanceMomentum_wf}, together with
 \eqref{eq:Constitutive-equation} and
-\eqref{eq:Rho-material-derivative} represents the weak form
+\eqref{eq:Rho-material-derivative}, represents the weak form
 formulation of the problem.
 
-In order to arrive to a finite set of equations, in contrast with the
-FEM, in \acrshort{mpm} a double discretization procedure is performed as we will
-describe here below. First, the continuum domain
-$\Omega$ is discretized with a finite sum of material points (in the
-following particles), each one
-represent a part of the discretized domain $\varOmega_p \subset
+In order to obtain a finite set of equations, in contrast with the
+\acrshort{fem}, in \acrshort{mpm} a double discretization procedure is
+performed. First, the continuum \gls{domain} is discretized with a finite sum of material points (also denominated particles the manuscript). Each material point
+represents a part of the discretized domain $\varOmega_p \subset
 \varOmega$ with $p = 1,2\ldots ,N_p$ where $N_p$ is the number of
-particles. The material point $\vec{x}_p$ is defined at the centroid
-of each $\Omega_p$, figure~\ref{fig:MPM-discretization}.
-Each material point is assigned with initial values of position,
+particles. The material point location, $\vec{x}_p$, is defined at the centroid
+of each $\Omega_p$ (see figure~\ref{fig:MPM-discretization} for details).
+Initial values of position,
 velocity, mass, volume and stress denoted by $\vec{x}_p$,
-$\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$, but also the
+$\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$ respectively are assigned to each material point, which also owns the
 virtual displacement field $\vect{u}^{\psi}_{p}$. Therefore, employing
-the definition of the material integral, where we recover the Riemann
-integral definition as an addition of a finite set of points, and
-their volumes are interpreted as quadrature weights. Consequently,
+the definition of the material integral, where Riemann
+integral definition \cite{Riemann_1854} is recovered as an addition of
+a finite set of points, and their volumes are interpreted as quadrature weights. Consequently,
 individual terms in \eqref{eq:BalanceMomentum_wf} are solved as follows. 
@@
 \end{itemize}
-where $h$ is the thickness of the continuum in a 2D case. Here is
-where the second discretization procedure appears. A background mesh
+where $h$ is the thickness of the continuum in a 2D case. Following, the aforementioned second discretization procedure appears. A background mesh
 composed by a finite set of grid points with coordinates $\vec{x}_I\
-, I = 1,2\ldots ,N_n$, is generated. Where $N_n$ is the number of grid
-nodes. This mesh is employed as a support to compute gradients and
-divergences.
+, I = 1,2\ldots ,N_n$, is generated, being $N_n$ the number of grid
+nodes.\PNA{Spatial derivatives, such as gradients and
+divergences, are computed through the support of the background mesh.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \Grad{N_{Ip}})^s$, $\tens{\varepsilon}_p^{\psi}= (\vect{u}_I^{\psi} \otimes \Grad{N_{Ip}})^s$.
-We reach to the nodal balance of forces of the continuum,
+nodal balance of forces of the continuum yields:
 \begin{equation}
@@
 \end{equation}
-Next, imposing $\frac{D \rho}{D t} = 0$, we ensures the mass
-conservation and update the density field.
+Next, mass conservation is guaranteed by enforcing the null value of
+the material derivative of the density field $\frac{D \rho}{D t} = 0$.
+This leads to a suitable equation to update the density field:
 \begin{equation}
   \label{eq:MassConservation}
-\dot{\rho} = - \rho\ \mathit{tra} \left( \dot{\tens{\varepsilon}} \right)
-\end{equation}
-
-Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order
-temporal integration scheme is required. Therefore, time is
-discretized in to a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
-is the total number of time steps. Once the nodal equilibrium equation it is solved, the values in the nodes are
-interpolated back in to the particles and each particle it is advected
-to the new position,
+\dot{\rho} = - \rho\ \mathit{trace} \left( \dot{\tens{\varepsilon}} \right).
+\end{equation}
+Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order\PNA{time} integration scheme is required. Therefore, time is
+discretized into a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
+is the total number of time steps. Once the nodal equilibrium equation is solved, the values at the nodes are
+interpolated back into the particles, which are advected
+to the new position through:
 \begin{equation}
@@
 \end{equation}
-In \acrshort{mpm} literature, this equations
-(\ref{eq:particle_balance_forces3}) and (\ref{eq:Updated_Lagrangian}),
-are solved with an explicit forward Euler algorithm. The time integration scheme of \acrshort{mpm} has been described in detail by many researchers
-\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and summarized
-in figure~\ref{fig:MPM_algorithm}.
+\PNA{Traditionally, Eqs.
+\eqref{eq:particle_balance_forces3} and ~\eqref{eq:Updated_Lagrangian},
+are solved with an explicit forward Euler algorithm. In the following subsection, this and the proposed schemes are described}.
+
+\subsection{\acrshort{mpm} time integration scheme: the Explicit Predictor-Corrector proposal}
+%\subsection{Explicit predictor-corrector scheme for \acrshort{mpm}.}
+\label{sec:epc-algor-mpm}
+
+\PNA{As was stated previosuly, an explicit forward Euler algorithm has been utilized widely within the \acrshort{MPM} methodology. This scheme has been described in detail by many researchers
+\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and can be sketched by the scheme of the figure~\ref{fig:MPM_algorithm}.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Other authors have proposed many others time integration alternatives
-like \cite{Guilkey2003}, \cite{Tran2019e}, \cite{Charlton2017}. In the
+like \cite{Guilkey_2003,Charlton_2017,Tran2019e}. In the
 first publication on \acrshort{mpm} \cite{Sulsky1994}, the nodal acceleration
@@
 \end{equation}
-However, as Andersen (2009)\cite{thesis_Andersen_2009} point out, this algorithm has been shown to be numerically unstable due to that
-$\vect{f}_I^{int,k}$ can be finite for an infinitesimal nodal mass
-$\tens{m}$. This can lead to numerical issues when nodal acceleration
-is obtained for evaluating \eqref{eq:Sulsky-1994-UL-x},\eqref{eq:Sulsky-1994-UL-v}. Hence, a
-corrected version of this algorithm in shown in Zhang {\it et al.}
-(2016)\cite{Zhang_book_2016}
+However, as Andersen (2009)\cite{thesis_Andersen_2009} pointed out, this algorithm has been shown to be numerically unstable due to that
+$\vect{f}_I^{int,k}$ can be infinite for an infinitesimal nodal mass
+$\tens{m}$. This issue may lead to numerical issues when nodal acceleration
+is obtained in the evaluation of the Eqs. \eqref{eq:Sulsky-1994-UL-x} and \eqref{eq:Sulsky-1994-UL-v}. Hence, a
+corrected version of this algorithm was proposed by Zhang {\it et al.}
+(2016)\cite{Zhang_book_2016}:
 \begin{equation}
   \label{eq:Zhang-2016-UL-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}.  
+  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}, 
 \end{equation}
@@
 \end{equation*}
-As \acrshort{mpm} has a nodal stage, it is possible to apply this methods
-successfully in \acrshort{mpm} framework as was proved by
-\cite{Tran2019e}. Taking the predictor definition from and calculating
-nodal velocity, and updating particles position employing nodal values
-of velocity and acceleration. The predictor-corrector algorithm has
+\PNA{The nodal \acrshort{mpm} stage allows to apply this method
+in the \acrshort{mpm} framework in a similar manner that the one
+proposed by Tran~\it{et al.}~\cite{Tran2019e}. Taking into account the predictor definition, it is possible to calculate
+nodal velocities and update particles position employing nodal values
+of velocity and acceleration.}
+
+The predictor-corrector algorithm has
 been described in the classic literature \cite{Hughes2000}, and its
-computational advantages and stability were widely proof by Liu
-\cite{Xiaojian94}. The ``classic'' PCE algorithm starts with a
-predicted value of the nodal velocity at the $(k+1)$th time step denoted by $\vec{\tilde{v}}_I^{k+1}$ given as,
+stability and computational advantages were widely validated by Liu
+\cite{Xiaojian94}. The ``classic'' \acrfull{npc} algorithm starts with a
+predicted value of the nodal velocities at the $(k+1)$th time step, denoted by $\vec{\tilde{v}}_I^{k+1}$, which is calculated as follows:
 \begin{equation}
   \label{eq:Predictor-velocity-I}
-  \vec{\tilde{v}}_I^{k+1} = \vec{v}_I^k + (1 - \gamma)\ \Delta t\ \vec{a}_I^k
-\end{equation}
-In \eqref{eq:Predictor-velocity-I} arise a \textit{user-defined}
-parameter $\gamma \geq 0$. This parameter influences both the predictor accuracy
-and the stability of the algorithm. As point out Liu
+  \vec{\tilde{v}}_I^{k+1} = \vec{v}_I^k + (1 - \gamma)\ \Delta t\ \vec{a}_I^k.
+\end{equation}
+
+The \textit{user-defined}
+parameter $\gamma \geq 0$ that appears in In \eqref{eq:Predictor-velocity-I}, influences both the predictor accuracy
+and the stability of the algorithm. As pointed out Liu
 \cite{Xiaojian94}, the truncation error of the predictor formula is
@@
 recovery process where particles quantities are transferred to the
-mesh nodes. This technique arise as a generalization of the super-convergent recovery
+mesh nodes. This technique arises as a generalization of the super-convergent recovery
 procedures described by Zienkiewicz \& Zhu \cite{ZZ1992_I} (\textit{ZZ})
-in the context of FEM. In \acrshort{mpm} Gauss quadrature is not employed as
+in the context of \acrshort{fem}. In \acrshort{mpm}, Gauss quadratures are not employed. However, 
 integrals are computed following the Riemann integral definition,
-where each component of the summation correspond to a particle of the
+where each component of the summation corresponds to a particle of the
 discretization. Also Bardenhagen \& Kober \cite{Bardenhagen2004}
-proved that thorough this information-transference technique mass and momentum are conserved. So for a general particle variable $\Phi_p$ employing the
-\textit{ZZ} technique is possible to get its nodal homologous $\Phi_I$  as,
+proved that through this information-transference technique mass and momentum are conserved. So for a general particle variable $\Phi_p$, employing the
+\textit{ZZ} technique, it is possible to get its nodal homologous $\Phi_I$  as:
 \begin{equation}
   \label{eq:Variational-recovery}
-   \Phi_I = \frac{m_p N_{Ip} \Phi_p}{m_I}
- \end{equation}
- Therefore, to get a analogous expression for
+   \Phi_I = \frac{m_p N_{Ip} \Phi_p}{m_I}.
+ \end{equation}
+ Therefore, to get an analogous expression for
  \eqref{eq:Predictor-velocity-I} in the context of \acrshort{mpm}, the
  procedure described in the equation \eqref{eq:Variational-recovery}
- is employed reaching to,
+ is employed, obtainen the following expression:
  \begin{equation}
@@
 instabilities due to numerical cancellation likewise the original
-Sulky algorithm. Thankfully this can be avoided easily by the
-equivalent formulation \eqref{eq:Predictor-velocity-II}, 
+Sulky algorithm. Thankfully, this can be avoided easily by the
+equivalent formulation proposed as follows: 
 \begin{equation}
   \label{eq:Predictor-velocity-II}
-  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
+  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}.
 \end{equation}
 This way of computing the nodal predictor is both numerically stable
-and minimize the computational effort. Once nodal velocity are
-obtained, the essential boundary conditions are imposed. And in the
+and minimize the computational effort. Once nodal velocities are
+obtained, the essential boundary conditions are imposed over \gls{dirichlet-boundary}. And in the
 following, the ``classic'' \acrshort{mpm} algorithm continues to reach to the
-equilibrium equation \eqref{eq:particle_balance_forces3}. Here we
-continue with the \textit{corrector} stage, due to the fact that we
-already have nodal velocity, this step is computed in the same way as
-in FEM,
+equilibrium equation \eqref{eq:particle_balance_forces3}. Next, the
+\textit{corrector} stage is introduced. Due to the fact that nodal
+velocities were obtained earlier, this step is computed in the same way as
+in \acrshort{fem},
 \begin{equation}
   \label{eq:Corrector-velocity}
-  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}
-\end{equation}
-Finally updated particle kinetics are computed using nodal values as,
+  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}.
+\end{equation}
+Finally updated particle kinetics are computed using nodal values as:
 \begin{align}
@@
         \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k} 
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}.
 \end{align}
-Notice that particle displacement is computed using the corrected
-nodal velocities and the accelerations computed with the velocities
-of the predictor. However, particles velocities and accelerations
+Notice that particle displacements are computed using the corrected
+nodal velocities as well as the accelerations with the velocities
+of the predictor. However, particle velocities and accelerations
 are computed using the corrected velocities. Therefore here we share similarities
-with the \textit{leapfrog integration} which updates the position at
-full time step, but updates the velocity at half time steps. Notice
-also that with this approach the calculation of nodal momentum values
-are not required. Due to its simplicity allows be implemented with minor modifications
-over a standard forward Euler. It is summarized in shape of
-pseudo-algorithm.
+with the \textit{leapfrog integration} where position is not updated at
+full time step, but the velocity is updated at half time steps. Notice
+also that, with this approach, the calculation of nodal momentum values
+are not required. Due to its simplicity, the proposed scheme can be implemented with minor modifications
+over the standard forward Euler. The full implementation is summarized in the algorithm~\ref{algo:1}.
 
 \begin{algorithm}
-  \floatname{algorithm}{Algorithm}
+  \floatname{algorithm}{Algorithm 1}
   \renewcommand{\thealgorithm}{}
-  \caption{Explicit Predictor-Corrector scheme}
+  \caption{\acrfull{npc} scheme} \label{algo:1}
   \begin{algorithmic}[1]
@@
     Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
-    \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
+    \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ by evaluating
     \eqref{eq:nodal_internal_forces} and
     \eqref{eq:nodal_external_forces} in the time step $k+1$.
-    In the grid node $I$ is fixed in one of the spatial dimensions, set it to
-    zero to make the grid nodal acceleration zero in that direction.\\
+    \MMP{In those nodes where $\Deriv{\vect{v}_I^{k}}{t} \big\rvert_{\Gamma_d} = 0$,
+      the acceleration is fixed to zero and nodal forces are stored as
+      reactions.}\\
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
 
-\subsection{Local \textit{max-ent} approximants}
+\subsection{Local \textit{Max-Ent} approximants}
 \label{sec:local-max-ent}
-The popularity of \acrshort{mpm} has increase notoriously during
+The popularity of the \acrshort{mpm} has increased notoriously during
 the recent years due to its ability to deal with large strain problems
 without mesh distorsion issues inherent to mesh based methods like
-FEM, see Zdzislaw \cite{Wieckowski2004}. However, in the simulations
-made with the original \acrshort{mpm}, there are numerical noises when particles
-crossing the cell boundaries. Local maximum-entropy (or
-local \textit{max-ent}) shape function first introduced by Arroyo \&
-Ortiz (2006)\cite{Arroyo2006} has been recently tested under \acrshort{mpm} framework
-by Wobbes {\it et al.} (2020)\cite{Wobbes2020} where they prof that
-simulations performed with the \textit{max-ent} basis functions show
-considerably more accurate stress approximations for \acrshort{mpm}. Although, in
-\cite{Wobbes2020} authors does not deep in how the regularization
-parameter $\beta$ affects to the accuracy and stability of the solution.
-The basic idea of the shape functions based on such
-an estimate is to interpret the shape function $N_I(\vec{x})$ as a probability. This allow us to introduce two important limits:
+\acrshort{fem}, see Wi{\c{e}}ckowski \cite{Wieckowski2004}. However, in the simulations
+made with the original \acrshort{mpm}, numerical noises appear when particles
+cross the cell boundaries.\PNA{Solving this issue is the main goal of the employment of the \acrshort{LME} shape functions}.
+
+\acrfull{lme} approximation schemes were
+first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} and has been
+recently tested under \acrshort{mpm} framework by Wobbes {\it et al.}
+(2020)\cite{Wobbes2020}.\PNA{The performed simulations of \acrshort{mpm}
+within \acrshort{lme} in \cite{Wobbes2020} shows considerably more accurate stress
+approximations than traditional \acrshort{mpm} schemes. However, 
+how the regularization parameter $\beta$
+affects to the accuracy and stability of the solution is not assessed deeply in that research, which is considered interesting in the present manuscript; the tuning of this $\beta$ parameter allows to make the comparison of the accuracy against analogous traditional \acrshort{mpm} shape function.}
+
+The basic idea
+of the shape functions based on such an estimate is to interpret the shape function $N_I(\vec{x})$ as a probability. This allows us to introduce two important limits:
 the principle of maximum-entropy (\textit{max-ent}) statistical
@@
 \end{align*}
-On the other hand, we wish to control the width of the shape function and it dacay with distance away from the corresponding nodes.
-To reach to this objective \cite{Arroyo2006} propose the following linear program,
+On the other hand, the control of the shape function width and its
+decay with distance away from the corresponding nodes is a desirable property. To reach to this objective \cite{Arroyo2006} propose the following linear program,
 \begin{align*}
@@
 \end{align*}
-The regularization o \textit{thermalization} parameter
-between the two criterion $\beta$ has Pareto optimal values in the range
+The regularization or \textit{thermalization} parameter
+between the two criterion, $\beta$, has Pareto optimal values in the range
 $\beta \in (0,\infty)$. The unique solution of
-the local max-ent problem (LME)$_\beta$ is:
+the local \textit{max-ent} problem \acrshort{lme}$_\beta$ is:
 \begin{equation}
@@
 function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
-10$^{-6}$, for example,  would ensure a reasonable range of
-neighbours, see \cite{Arroyo2006} for details.
+10$^{-6}$\PNA{in this research},  would ensure a reasonable range of
+neighbours (see \cite{Arroyo2006} for details).
 This tolerance defines the limit values of the influence radius and is used thereafter to
 find the neighbour nodes of a given integration point.
-An aditional remark is that in similariti  to alternative non-polynomial meshfree basis functions, the LME approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem.
-
-This interpolation technique avoid one important shortcoming when using
+An additional remark is that, analogous to alternative non-polynomial meshfree basis functions, the \acrshort{lme} approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem.
+
+This interpolation technique avoids important shortcomings when using
 \acrshort{gimp} or B-Spline \acrshort{mpm} regarding the computational domain boundaries
-Steffen {\it et al.} (2008)\cite{Steffen2008b}. Which is the
-additional considerations in the applications of the boundary
-conditions. This is motivated because of their increased extents, it
-is possible for particles to influence, and be influenced by, nodes
-that lie outside of the simulation domain. Some researchers have solve
-this problems with ``extra'', or the called ``ghost'' nodes by other investigators. Anyway this nodes requires especial treatments similar
-to those employed in the smoothed particle hydrodynamics (SPH), for
+(see Steffen {\it et al.} (2008)\cite{Steffen2008b}), which are related to the
+additional considerations in the application of the boundary
+conditions.
+Motivated by their increased extents, particles may share an influence radius that lies outside of the simulation domain.
+Some researchers have solved this problem with the so called ``extra'' or ``ghost'' nodes.
+These nodes require especial treatment, similar
+to those employed in the \acrfull{sph}, for
 further details see Liu \& Liu (2003)\cite{Liu2003}. The approach here
-described does not requires the employ of this artifacts.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{0.5\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Particle-discretization}
-  }
-  \caption{This tolerance defines the limit values of the influence
-    radius and is used thereafter to find the neighbour nodes of a
-    given integration point. The picture also shows the neighbourhood
-    criterion to select those node inside of $\Omega$.} 
-  \label{fig:Particle-discretization}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Due to the FE-compatibility, the LME shape function is degenerated to
-linear finite element shape function if $d+1$ neighbouring nodes are
-chosen as the support. Furthermore, with a conveniently adopted
-\textit{regularization} parameter it is possible to get a \acrshort{gimp}-like
-shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}.  
+described does not requires the employment of this artifices.
+Due to the \short{fem}-compatibility, the \acrshort{lme} shape
+function is degenerated to linear finite element shape function if
+$d+1$ neighbouring nodes are chosen as the support, where $d$ is the
+number of dimensions in the problem. Furthermore, with a conveniently
+adopted \textit{regularization} parameter it is possible to get a 
+\acrshort{gimp}-like shape function.\MMP{Finally \short{sph}-like
+behaviour can be obtained for lower values of $\gamma$ since the
+support of the shape function is drastically increase, and therefore
+\textit{smoother} solutions are obtained. See \cite{Navas2016} for an
+application of this capability, in this publication authors smooth 
+oscillations due to excess of pore water pressure in consolidation
+problems.}A proof of this statements is observed in figure~\ref{fig:LME_MPM}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \subfigure[$\text{LME}_{17}$]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun}\\
+    \begin{tabular}{c}      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun}\\
       \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun_dx}\\
@@
   \subfigure[$\text{LME}_{10}$]{
-    \begin{tabular}{c}
-      \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun}\\
-      \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun_dx}\\
-      \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun_dy}    
+    \begin{tabular}{c} \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun}\\ \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun_dx}\\      \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun_dy}
     \end{tabular}
@@
 \cite{Kochmann2019} introduced an enhanced version of the original
-local max-ent scheme, which uses an anisotropic support to deal with
-tensile inestability. Nonetheless this is out of the scope of the
-present document but will be incorporated in future research.
+\acrshort{lme} scheme, which uses an anisotropic support to deal with 
+tensile instability.\PNA{This is another benefit of the proposed methodology, that, although is out of the scope of the
+present document, will be incorporated in future research.}
 
@@
 This section is devoted to test the ability of both predictor-corrector
-time integration scheme and the local \textit{max-ent} approximants to
+time integration scheme and the Local \textit{Max-Ent} approximants to
 overcome spurious oscillations due to the grid crossing and high
-frequency loads under the context of \acrshort{mpm} Two different test has
-been adopted for this purpose, the benchmark proposed by Dyka \& Ingel
+frequency loads under the context of \acrshort{mpm}. Two different test have
+been adopted for this purpose: the benchmark proposed by Dyka \& Ingel
 (1995)\cite{Dyka1995} and the test proposed in the PhD thesis of
-Andersen (2009)\cite{thesis_Andersen_2009}. In all calculations we confine out attention to
-uniformly distribute node and particle sets. The accuracy of the PCE
-scheme is compared to the standard FE. In addition \textit{max-ent} solutions
-are compared with those provided by \acrfull{ugimp} and Q4 shape functions, also
-we compare \acrshort{mpm} performance with OTM and FEM. All simulations were
-performed with in-hose software.
-
-\subsection{Dyka bar \cite{Dyka1995}}
+Andersen (2009)\cite{thesis_Andersen_2009}. On the one hand, the accuracy of the \acrfull{npc}
+scheme is compared to the standard \acrfull{fe} in order to assess the performance of the time integration schemes. On the other hand,  \acrshort{lme} solutions
+are compared with those provided by \acrfull{ugimp} and Q4 shape
+functions. To avoid some mesh-dependent issues, in all
+calculations a regular background mesh was set. All simulations were performed with in-hose software.
+
+\subsection{Dyka's bar \cite{Dyka1995}}
 \label{sec:dyka-bar}
 
-This benchmark was proposed due to its ability to shows the capability
+This benchmark was proposed\PNA{by Dyka~\cite{Dyka1995} since allows so study easily the capability}
 of the proposed time integration algorithm to avoid velocity
-fields instabilities. It consists in a one-dimensional bar with a
-length of 0.1333 meters, sketched in the
-figure~\ref{fig:Dyka_Bar}. The boundary conditions are in the right
-border displacement are constrained ($\vect{v} \rvert_{x=L} = 0$) and
-in the left displacement are let free ($\tens{\sigma} \rvert_{x=0} =
-0$). And a initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
-last quarter of it. Finally, the elastic parameters consider for this test are:
+field instabilities. It consists of a one-dimensional bar of a length of 0.1333 meters, sketched in the
+figure~\ref{fig:Dyka_Bar}. The boundary conditions are: displacements are constrained ($\vect{v} \rvert_{x=L} = 0$) in the right
+border, letting free in the rest of the body and ($\tens{\sigma} \rvert_{x=0} =
+0$). An initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
+left quarter of the bar. Finally, the elastic parameters considered for this test are:
 \begin{itemize} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this case a duration of 0.0001 seconds for the simulation is
-consider. Therefore, the elastic wave generated travel thorough the bar
+In this case, 0.0001 seconds\PNA{are considered }in the simulation. Therefore, the elastic wave generated travel through the bar
 (from A to C and back to A) at least two times. For the spatial
-discretization we propose a set a seven nodal mesh sizes (0.1, 0.3325, 0.5,
-1.0, 3.3325, 6.665, 10.0) in millimeters. For each element a number of
+discretization, a set of seven nodal mesh sizes (0.1, 0.3325, 0.5,
+1.0, 3.3325, 6.665, 10.0 millimeters) are considered. For each element a number of
 four particles was selected. In the initial layout, particles are
-occupying the exact quadrature points of a linear quadrilateral. With
-the exception of the \acrshort{ugimp} simulation where gaps or overlap between
-voxels of each particle are not allowed. In those cases, each particles
-occupy the center of each cell quarter. For all simulations, time step
+occupying the exact quadrature points of a linear quadrilateral, with
+the exception of the \acrshort{ugimp} simulation, where gaps or overlap between
+voxels of each particle are not allowed. In those cases, each particle
+occupies the center of each cell quarter. For all simulations, time step
 is controlled by a Courant-Friedrichs-Levy condition of 0.1, were the adopted
-celerity is computed as,
+celerity is computed as:
 \begin{equation}
   \label{eq:Cel}
-  Cel = \max\{\max_{p \in \Omega_p}\{ \vect{v}_p \} , \max_{p \in \Omega_p}\{ \sqrt{\frac{E_p}{\rho_p}} \} \}
-\end{equation}
-A important consideration regarding modellization concerns to the
+  Cel = \max\{\max_{p \in \Omega_p}\{ \vect{v}_p \} , \max_{p \in \Omega_p}\{ \sqrt{\frac{E_p}{\rho_p}} \} \}.
+\end{equation}
+An important consideration regarding modellization concerns to the
 background mesh. Notice that free border of the bar has a maximum
@@
 required in order to accommodate the unconstrained displacement of the
-particles in the left border of the bar. Naturally this problem arise
+particles in the left border of the bar. Naturally this problem arises
 when the mesh size is small enough that relative displacement of the
-particles are larger then the distance to the border, so grid crossing
+particles is larger then the distance to the border, so grid crossing
 phenomena could appear even in those cases with infinitesimal
 displacements.
+
+In this case, an analytical solution can be obtained
+through the characteristics method, described in the appendix
+\ref{app:analytical_sol}. To measure the convergence of the solutions
+for the different time integration and approximation schemes the
+root-mean-square (RMS) error in the velocity field is computed. RMS
+error is defined as
+\begin{equation}
+  \label{eq:RMS}
+  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
+\end{equation}
+where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
+numerical solutions evaluated in the final time step in the position
+of each particle.\PNA{In Fig.
+\ref{fig:Dyka-error-evol} the evolution of the RMS is obtained for both time integration schemes.
+The right figure, with the \acrshort{NPC} results, shows lower values of the estimated error, denoting the higher performance of this methodology.
+About the spatial discretization, the \acrshort{LME} schemes show an error comparable to the obtained with the \acrshort{uGIMP}, being even lower close to the grid-crossing region.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
   }
-  \caption{Velocity evolution at the point in the Dyka bar left side,
-    convergence plots for FE and PCE. The plot is subdivided with
+  \caption{Velocity error evolution at the point A in the Dyka's bar ,
+    convergence plots for \acrshort{fe} and \acrshort{npc}. The plot is subdivided with
     colours, the darker part of the diagram shows coincides when the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this case, an analytical solution is possible
-thought the characteristics method described in the appendix
-\ref{app:analytical_sol}. To measure the convergence of the solutions
-for the different time integration and approximation schemes the
-root-mean-square (RMS) error in the velocity field is computed. RMS
-error is defined as
-\begin{equation}
-  \label{eq:RMS}
-  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
-\end{equation}
-where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
-numerical solutions evaluated in the final time step in the position
-of each particle. A first comparative between both time integration
-scheme is plotted in figure \ref{fig:Dyka-PCE-FE}. It demonstrates the
-superior performance of the PCE \textit{versus} the FE. In the PCE the
+
+A first comparative between the velocity results of both time integration
+schemes is plotted in figure \ref{fig:Dyka-NPC-FE}. It demonstrates the
+superior performance of the \acrshort{npc} \textit{versus} the \acrshort{fe}. In the \acrshort{npc} the
 spurious oscillations are quickly mitigated in the first time steps,
-and does not propagate the error in time in opposite to FE where the
-simulation becomes unstable after $6E^{5}$ seconds. Figure
-\ref{fig:Dyka-error-evol} also remarks the remarkable difference
-between both schemes. 
+and the error is not propagated in time, opposite to the results of the \acrshort{fe} scheme, where the
+simulation becomes unstable after $6E^{5}$ seconds.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   }
-  \caption{Comparative of the PCE \textit{versus} the FE. In the
+  \caption{Comparative of the \acrshort{npc} \textit{versus} the \acrshort{fe}. In the
     picture the velocity evolution at the point in the bar left side
     is plotted.}
-  \label{fig:Dyka-PCE-FE}
+  \label{fig:Dyka-NPC-FE}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Figure \eqref{fig:Dyka-LME-gamma} shows the sensibility of the LME
-approximation scheme to variations in the a-dimensional parameter
-$\beta$ that controls the value of the regularization parameter
-$\gamma$ depending of the mesh size. As we can see lower values of
+
+Figure \eqref{fig:Dyka-LME-gamma} shows the sensibility of the \acrshort{lme}
+approximation scheme to variations in the parameter
+$\gamma$, which is the one that controls the value of the regularization parameter
+$\beta$ together with of the mesh size. Notice how lower values of
 gamma exhibits a behaviour with a soft decay in some parts of the
@@
 materials. On the other hand larger values of the parameter $\beta$
-makes the solution tend to the linear FEM solution as the athermal
-limit is reached \cite{Arroyo2006}. Intermediate values of the
+makes the solution tend to the linear \acrshort{fem} solution as the athermal limit is reached \cite{Arroyo2006}. Intermediate values of the
 regularization parameters give us a compromise between the both
-scenarios here described. An additional observation concerning the
-solution sensibility to regularization parameters occurs when mesh
-size decreases. For larger mesh size where the relative particle displacement
+scenarios here described. An additional observation, concerning to the
+solution sensibility depending on the regularization parameters, \PNA{is the behaviour of the solution depending on the decreasing of mesh
+size}. For larger mesh sizes, where the relative particle displacement
 is negligible in comparison with the cell size, the global behaviour
-is FEM-like, therefore larger values of $\gamma$ has offers better
-results. On the other hand, when mesh size is small enough to produce
-grid-crossing and mesh-free behaviour is required to ensures the
-convergence of the solution, tiny values of $\gamma$ has a better
-performance. Convergence plot in figure \eqref{fig:Dyka-error-evol}
-shows how the slope for the larger values of $\gamma$ decreases
-monotonically with the value of the mesh size, in contrast to larger
-values of it, whose suffers a punishment of the performance when significant
-movement of the particles occurs as far we reduce the mesh size.  
+is \acrshort{fem}-like; therefore, larger values of $\gamma$ \PNA{may offer better results}. On the other hand, when mesh size is small enough to produce
+grid-crossing meshfree behaviour is required to ensure the
+convergence of the solution and tiny values of $\gamma$\PNA{may lead to better
+performances}. Convergence plot in figure \eqref{fig:Dyka-error-evol}
+shows how the slope, for the larger values of $\gamma$, decreases
+monotonically with the value of the mesh size, in contrast with larger
+values of $\gamma$,\PNA{where the performance is punished with significant
+movement of the particles as far as the mesh size is reduced.} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Figure \ref{fig:Dyka-uGIMP-LME} compares the performance of the
-\acrshort{ugimp}~\cite{Bardenhagen2004} shape function \textit{versus} the LME approximation scheme with
-a adimensional regularization parameter $\gamma$ of 4.0. Although it
-does not shows remarkable differences, LME approximats exhibits a more
-robust behaviour than the \acrshort{ugimp} shape functions. Regarding this, notice
+\PNA{The performance of the
+\acrshort{ugimp}~\cite{Bardenhagen2004} shape function \textit{versus} the \acrshort{lme} approximation scheme with
+a dimensionless regularization parameter $\gamma$ of 4.0 is compared in Figure \ref{fig:Dyka-uGIMP-LME}. Although remarkable differences are not observed, more
+robust behaviour is exhibited by the \acrshort{lme} approximants than the \acrshort{ugimp} shape functions.} Regarding this, notice
 the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5
-millimeters. During these simulation the \acrshort{ugimp} suffered an unstable
-increase of the error so we decided to no include this nodes in the
-plot. A feasible explanation for this phenomena could be the presence
-of numerical cancellation which could produce gaps between
-voxels. Further research should be done in this direction for getting
-a better comprehension of this phenomena. In opposite, LME
-approximation does not suffers this phenomena either with irregular
-nodal layout.
+millimeters.\PNA{The reason is due to an unstable
+increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yield unacceptable results}. A feasible
+explanation for this phenomena could be the presence of numerical
+cancellation which could produce gaps between voxels. Further research
+should be done in this direction for getting a better comprehension of
+this phenomenon.\PNA{Conversely, this shortcoming is not suffered by \acrshort{lme}, independently of regular or with irregular nodal layout.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Finally, figure \ref{fig:Dyka-OTM-MPM} compares the solution obtained
-with OTM~\cite{Li2010} \textit{versus} the solution obtained with \acrshort{mpm},
-both with same time integration scheme and spatial discretization. For
-this case the performance of \acrshort{mpm} is robust and stable than OTM. As we
-can appreciate, during the first half of the simulation both method
+
+Finally, the \acrshort{otm}~\cite{Li2010} \textit{versus} obtained solution is compared against the one obtained with \acrshort{mpm}, both with same time integration scheme and spatial discretization, and results are shown in figure \ref{fig:Dyka-OTM-MPM}.
+In
+this case, the performance of \acrshort{mpm} presents better robustness and stability than the
+\acrshort{otm}. During the first half of the simulation both method 
 seem to perform in a similar way, but during the second half of the
 simulation after the elastic wave has travel from the free border to
-the fixed one and back, in OTM the solution becomes noisy than the
+the fixed one and back, in \acrshort{otm} the solution becomes more noisy than the
 one performed by \acrshort{mpm}.  
@@
 
-\subsection{Andersen block}
+\clearpage
+\subsection{Rigid block}
 \label{sec:andersen-block}
 
-In order to test the ability of this interpolation technique to deal
-with grid crossing instabilities we will simulate the vertical
-compression of a square block (10 by 10 meters) of soft soil sketched
-in figure~\ref{fig:block} and loaded using an incremental gravitation
-scheme.
+The following test was proposed to measure proof the ability of this
+interpolation technique to deal with grid crossing instabilities. It
+consists in the simulation of a square block of soil incrementally
+loaded by a body force. Details of the problem are sketched in figure~\ref{fig:block}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
-In order to get a stable solution, we will adopt a time step conducted
-by a Courant number of 0.1. On the other hand, the explicit predictor-corrector
-scheme is here employed looking forward getting better results. For the
-initial spatial discretization we will employ four particles per cell
-($\Delta x = 2\ m$). The initial setting of particles inside of the
+In order to get a stable solution, time step was conducted by a
+Courant number of 0.1. On the other hand, the explicit
+predictor-corrector scheme is here employed looking forward getting better results. For the
+initial spatial discretization four particles per cell
+($\Delta x = 2\ m$) were adopted. The initial layout of particles inside of the
 cell changes according to the approximation technique adopted. For the
-bi-linear shape functions and the LME approximants, the initial
+bi-linear shape functions and the \acrshort{lme} approximants, the initial
 position corresponds to the location of the gauss-points in a standard
@@
 Figure~\ref{fig:vertical-displacement-block} shows the vertical
-displacement evolution of a point in the free surface of the block. As
-we can see the simulation using the Q4 interpolation technique turns
-out to be unstable and in the second 15 it fails. The \acrshort{ugimp} simulation
+displacement evolution of a point in the free surface of the
+block. This figure shows how simulations performed with a bi-linear
+interpolation technique (Q4) turns out to be unstable during
+cell-crossing and consequently fails. The \acrshort{ugimp} simulation
 is more stable than the one performed by the Q4. Despite this is still
-unstable and could trigger severe oscillations if we pretend to
-simulate non-linear materials. The LME simulation was performed using
-two kinds of shape functions, one with a low value of the
+unstable and could trigger severe oscillations in simulation with
+non-linear  materials. The \acrshort{lme} simulation was performed
+using two kinds of shape functions, one with a low value of the
 dimensionless parameter, $\gamma = 0.8$, and other with a larger value
@@
 due to the fact that with larger value of $\gamma$, the shape
-functions behaves in a similar way to the FEM, which performs very
+functions behaves in a similar way to the \acrshort{fem}, which performs very
 accurate in those cases with a reasonable mesh distorsion, and with a
@@
 proved how local \textit{max-ent} approximation scheme could be
-employed as an useful technique in \acrshort{mpm}. The PCE arise as a highly
+employed as an useful technique in \acrshort{mpm}. The \acrshort{npc} arise as a highly
 efficient alternative for challenging dynamic problems like coupled
 $u-p_w$ without appeal to expensive implicit time integration
-algorithms. Also the procedure employed to design the PCE algorithm open
+algorithms. Also the procedure employed to design the \acrshort{npc} algorithm open
 the door to revisit a huge variety of time integration schemes
-developed originally for FEM, which can be rearranged to \acrshort{mpm} framework
+developed originally for \acrshort{fem}, which can be rearranged to \acrshort{mpm} framework
 with some modifications. Anyway, further research should be done to improve the
 formal comprehension of the algorithm good performance. This paper
-also enhances the suitability of the local \textit{max-ent} as a
+also enhances the suitability of the \acrshort{lme} approximation as a
 general promising alternative to the wide range of approximation.
@@
 
+% 
+\section*{Acknowledgements}
+%
+The financial support to develop this research from the Ministerio de Ciencia e Innovaci\'on, under Grant No.
+BIA-2016-76253 is greatly appreciated.
+The first and the second authors also acknowledge the fellowship Fundaci\'on Agust\'in de Betancourt and Juan de la Cierva (FJCI-2017–31544) respectively.
+
 % \printglossary[type=\acronymtype]
@@
 
-For the derivation of this analytical solution we will consider  the
-dynamic behaviour of a 1D elastic bar. The governing equations are the
-following: (i) The balance of linear momentum,
+For the derivation of this analytical solution, a 1D elastic bar is
+consider. Henceforth for convenience the governing equations will be written in terms of stress and velocity. The balance of linear momentum,
 \begin{equation}
@@
 \end{equation}
-where $\sigma$ is the stress value, $\rho$ is the density, and 
-$v$ is the velocity. (ii) The constitutive model, which for convenience of the
-following developments will be written in terms of displacement and
-velocities as, 
+Secondly the constitutive equation is the well known linear
+elastic one,
 \begin{equation}
@@
 \end{equation}
-where $E$ is the elastic modulus. (iii) The compatibility equation
-also in terms of the velocity field,
+where $E$ is the elastic modulus. And finally the compatibility
+equation,
 \begin{equation}
@@
 \end{equation}
-Next for simplicity, we will introduce \eqref{eq:CompatibilityEquation_e} in 
-\eqref{eq:1D-constitutive-equation}, so we get the following system of equations,
+Next for simplicity, we will introduce
+\eqref{eq:CompatibilityEquation_e} in
+\eqref{eq:1D-constitutive-equation}, it yield to,
 \begin{align}
@@
 \end{align}
-
 Introducing \eqref{eq:1D-constitutive-equation-II} in
-\eqref{eq:1D-balance-linear-momentum-II} and expressing the remaining
-equation in terms of the displacement, we reach the 1D wave
-equation for linear elastic materials,
+\eqref{eq:1D-balance-linear-momentum-II} and expressing the remaining equation in terms of the displacement, results the wave equation for linear elastic materials,
 \begin{equation}
@@
 \end{equation}
-where we have introduced the wave celerity $c$ as,
-\begin{equation}
-  \label{eq:1D-elastic-wave-celerity}
-  c = \sqrt{\frac{E}{\rho}}
-\end{equation}
-Alternative, rearranging both equations
-\eqref{eq:1D-balance-linear-momentum-II} and
-\eqref{eq:1D-constitutive-equation-II} it is possible to join them in a
-single system of equations as,
+where $c = \sqrt{\frac{E}{\rho}}$ is the material celerity. Alternative, rearranging both equations \eqref{eq:1D-balance-linear-momentum-II} and
+\eqref{eq:1D-constitutive-equation-II} it is possible to join them in a single system of equations as,
 \begin{equation}
@@
 \end{equation}
-This expression can be written in a more compact format as,
+Or in a more compact format,
 \begin{equation}
   \label{eq:System-stress-velocity-II}
-  \Deriv{\Vector{\phi}}{t} + \Matrix{A}\Deriv{\Vector{\phi}}{x} = \Vector{0}
-\end{equation}
-where both variables are joined in a single vectorial variable
-$\Vector{\phi}$ and $\Matrix{A}$ in coupling matrix between both equations,
+  \Deriv{\Vector{\phi}}{t} + \Matrix{A}\Deriv{\Vector{\phi}}{x} = \Vector{0}.
+\end{equation}
+In \eqref{eq:System-stress-velocity-II} stress and velocity are joined in to a single structure $\Vector{\phi}$ and $\Matrix{A}$ in coupling matrix between both equations,
 \begin{equation*}
@@
 \end{equation*}
-Note that the nature of \label{eq:eq:System-stress-velocity-II} is still
-hyperbolic despite the fact it does not have a second order
-temporal derivative as \eqref{eq:1D-wave-elastic}. A proof of this can
-be easily obtained if we get the zeros of the hypersurface defined by
-\eqref{eq:1D-wave-elastic}. And later the eigenvalues of $\Matrix{A}$
-in \eqref{eq:System-stress-velocity-II}. In both cases, eigenvalues
-are real and distinct ($\lambda = \pm \sqrt{\frac{E}{\rho}}$),
-therefore the system is called strictly hyperbolic.
-
-For a more general description in the following, we will assume that $\Matrix{A}$ has $n$
-different eigenvalues $\{ \lambda_1, \lambda_2, \ldots, \lambda_i, \ldots
-\lambda_n \}$ and $n$ eigenvectors $\{ \vec{x}^1, \vec{x}^2, \ldots,
+Despite of this manipulation, the nature
+of \label{eq:eq:System-stress-velocity-II} is still hyperbolic. A
+proof of this can be easily obtained computing the zeros of the
+hypersurface defined by \eqref{eq:1D-wave-elastic}. And later the
+eigenvalues of $\Matrix{A}$ in \eqref{eq:System-stress-velocity-II}. In both cases, eigenvalues are real and distinct ($\lambda = \pm \sqrt{\frac{E}{\rho}}$),
+therefore the system is called strictly hyperbolic. Assuming that  $\Matrix{A}$ has $n$ different eigenvalues $\{ \lambda_1, \ldots, \lambda_i, \ldots
+\lambda_n \}$ and $n$ eigenvectors $\{ \vec{x}^1, \ldots,
 \vec{x}^i, \ldots \vec{x}^n \}$ satisfying that $\tens{A} \vec{x} =
-\lambda \vec{x} $. Now we introduce the matrix $\Matrix{P}$ whose columns are the $n$
-eigenvalues $\Vector{x}$
+\lambda \vec{x} $. Now we introduce the matrix $\Matrix{P}$ whose columns are the $n$ eigenvalues $\Vector{x}$
 \begin{equation}
@@
 \end{equation}
-Diagonalizing $\Matrix{A}$ using $\Matrix{P}$ we get
+Diagonalizing $\Matrix{A}$ using $\Matrix{P}$ yields,
 \begin{equation}
@@
 \end{equation}
-where $ \Lambda_{ii} = \lambda_i$. Next we will define a vector $\Vector{\Re}$ such that:
+where $ \Lambda_{ii} = \lambda_i$. Now, lets define a vector $\Vector{\Re}$ as
 \begin{equation}
   \label{eq:Riemann-definition}
-  \Vector{\phi} = \Matrix{P}\ \Vector{\Re}
-\end{equation}
-we will assume to be integrable. Expanding the above expression with
-the chain rule and passing the matrix $\Matrix{P}$ to left hand side
-of the equality we get,
+  \Vector{\phi} = \Matrix{P}\ \Vector{\Re}.
+\end{equation}
+Expanding the above expression with the chain rule and passing the
+matrix $\Matrix{P}$ to left hand side of the equality we get,
 \begin{equation}
@@
 which consists of $n$ uncoupled equations as $\varLambda$ is
-diagonal matrix as we can see in \eqref{eq:Lambda-matrix}. Each of this
-equations are 1D scalar convective transport equations, with solutions
-of the form:
+diagonal matrix as we can see in \eqref{eq:Lambda-matrix}. Each of
+this equations are 1D scalar convective transport equations, with
+solutions of the form:
 \begin{equation}
@@
 \end{equation}
-
-This uncoupled system, has, therefore, a set of $n$ characteristics.
+This uncoupled system, has a set of $n$ characteristics.
 These magnitudes $\Re_i$ which propagate along characteristics are
-known as ``Riemann invariants'' of the problem. Here we have a 1D
-configuration, so the domain is $\Omega : \left(0, L\right) x \left(0,
-  T\right)$. For the closure of the problem we require:
-\begin{itemize}
-\item ``n'' initial conditions of the form $\Re_i (x,t=0) = h_i(x)$,
-  where $i = {0, \ldots, n}$, and $h_i(x)$ is a vectorial function
-  given by the physical variables of the problem.
-\item ``n'' boundary conditions.
-\end{itemize}
-
-Now particularizing the previous equations for the 1D elastic bar
-described in \cite{Dyka1995}, we get that the matrix $\Matrix{P}$
-is the following:
+known as \textit{Riemann invariants} of the problem. For the closure
+of the problem it is required ``n'' initial conditions of the form
+$\Re_i (x,t=0) = h_i(x)$, and ``n'' boundary
+conditions. Particularizing the previous equations for the 1D elastic
+bar described in \cite{Dyka1995}, $\Matrix{P}$ can computed as,
 \begin{equation*}
@@
 \end{equation*}
-and its inverse is:
-\begin{equation*}
-    \Matrix{P}^{-1} = \frac{1}{2\ \sqrt{E\rho}} \left[
-    \begin{array}{cc}
-      -1 & \frac{1}{\sqrt{E\rho}}\\
-      1 & \frac{1}{\sqrt{E\rho}} 
-    \end{array} \right]
-\end{equation*}
-
-And introducing the value of the inverse matrix $\Matrix{P}^1$ in the
-Riemann definition \eqref{eq:Riemann-definition} we get the following
-system of equations,
+With the value of the inverse matrix $\Matrix{P}^{-1}$ in the Riemann
+definition \eqref{eq:Riemann-definition}, a set of equations arise,
 \begin{align}
@@
 \end{align}
-
 From \eqref{eq:Riemann-I-1D-elastic-bar} and
-\eqref{eq:Riemann-II-1D-elastic-bar} we can obtain the values of the
-stress and the velocity as:
+\eqref{eq:Riemann-II-1D-elastic-bar} the values of the
+stress and the velocity can be computed in the following way,
 \begin{equation}
@@
 \end{equation}
-
 The boundary conditions are in both cases of radiation as there is not
-wave in-going from the exterior. So for the right side (fixed
-boundary) we get the following conditions:
+wave in-going from the exterior. So for the right side the conditions are,
 \begin{equation*}
-  \Re^{II} = 0 \quad and \quad v_{x=L} = 0
+  \Re^{II} = 0 \quad and \quad v_{x=L} = 0 \quad\Rightarrow \quad \sigma_{x=L} = -2\sqrt{\rho E}\ \Re^{I}
 \end{equation*}
-Therefore $\sigma_{x=L} = -2\sqrt{\rho E}\ \Re^{I}$. And in the left side
-(free boundary) we get the following conditions:
+
+And in the left side,
 \begin{equation*}
-  \Re^{I} = 0 \quad and \quad \sigma_{x=0} = 0
+  \Re^{I} = 0 \quad and \quad \sigma_{x=0} = 0  \quad \Rightarrow
+  \quad v_{x=0} = 2\Re^{II}
 \end{equation*}
-Therefore $v_{x=0} = 2\Re^{II}$. Finally, applying this conditions in
-the elastic bar sketched in figure~\ref{fig:Dyka_Bar}, is possible to obtain
-the velocity history in the right side of the bar plotted in the figure~\ref{fig:vel_analytics_dyka} and the stress in the last quarter side of the Dyka
-bar plotted in the figure~\ref{fig:stress_analytics_dyka} as is demanded in \cite{Dyka1995}.
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\columnwidth]{Figures/1D_right_Velocity.png}
-  }
-  \caption[Velocities values in the right side of the Dyka
-  bar]{Analytical solution for the velocity in the right side of the Dyka bar.}
-  \label{fig:vel_analytics_dyka}
-\end{figure}
-
-\begin{figure}\sidecaption
-  \centering
-  \resizebox{\hsize}{!}{
-    \includegraphics[width=\columnwidth]{Figures/1D_left_Stress.png}
-  }
-  \caption[Stress values in the last quarter side of the Dyka
-  bar]{Analytical solution for the stress in the last quarter of the Dyka bar.}
-  \label{fig:stress_analytics_dyka}
-\end{figure}
+By imposing this boundary conditions, the problem is fully defined as in \cite{Dyka1995}.
 
@@
 %%% End:
-\message{ !name(LME-MPM.tex) !offset(-1652) }
+\message{ !name(LME-MPM.tex) !offset(-1585) }

### 2020-04-27 LME-MPM.tex

@@
 \usepackage{lineno}
-% \usepackage{hredyperref}
+\usepackage{hyperref}
 \usepackage{float}
@@
 has increased due to its ability to deal with large strain regime
-without suffer mesh distortion inaccuracies.
-\PNA{One of the main fields where this method is strong is the dynamic one since the original time integration scheme proposed was the \acrfull{fe}~\cite{Sulsky1994}, carried out in a explicit manner.
+without suffer mesh distortion inaccuracies.\PNA{One of the main fields where this method is strong is the dynamic one since the original time integration scheme proposed was the \acrfull{fe}~\cite{Sulsky1994}, carried out in a explicit manner.
 However, in this type or problems, the main instabilities of the original \acrshort{mpm} are even marked.}
@@
 
-This document adopts the \acrfull{lme}, or Local \textit{Max-Ent} approximates, as a robust substitute \PNA{of the aforementioned} shape functions in \acrshort{mpm}.
-First introduced by Arroyo \& Ortiz
+This document adopts the \acrfull{lme}, or Local \textit{Max-Ent} approximates, as a robust substitute\PNA{of the aforementioned} shape functions in \acrshort{mpm}. First introduced by Arroyo \& Ortiz
 (2006)~\cite{Arroyo2006}, it belongs to the class of convex 
@@
 schemes which reduce the presence of high frequency noises by
-filtering them or increasing \PNA{somehow} the accuracy. \MMP{One of the first attempts of it was
+filtering them or increasing\PNA{somehow} the accuracy.\MMP{One of the first attempts of it was
 the proposal of an implicit time integration scheme by Guilkey \&
@@
 suitable combination of the \acrshort{lme} family shape functions, and the proposal of an explicit predictor-corrector scheme. The advantages of
-this approach will be illustrated through several challenging test cases \PNA{on the elastic regime}: the
+this approach will be illustrated through several challenging test cases\PNA{on the elastic regime}: the
 propagation of shock waves in a elastic bar and the response of a block of soil gradually loaded with gravitational forces.
@@
 denotes the gradient and its symmetric part. Einstein subscripts
-convention is adopted therefore repeated index means addition.
-
-\PNA{Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are describe in subsection \ref{sec:derivation-mpm},\ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.}
+convention is adopted therefore repeated index means addition.\PNA{Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are describe in subsection \ref{sec:derivation-mpm},\ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.}
 
@@
 field \gls{u} through the following set of governing equations and
-restrictions that must be satisfied. \PNA{First (i) the \textit{compatibility
+restrictions that must be satisfied.\PNA{First (i) the \textit{compatibility
   equation}, where the the strain field \gls{strain} is extracted from \gls{u} is defined as:}
@@
 the assumption of inifinitesimal strain, therefore second order terms
-in the spatial derivatives can be neglected.
-\PNA{Therefore, the stress field \gls{stress} will be considered the corresponding conjugate variable for the strain field, being the one} which satisfies (ii) the \textit{conservation of
+in the spatial derivatives can be neglected.\PNA{Therefore, the stress field \gls{stress} will be considered the corresponding conjugate variable for the strain field, being the one} which satisfies (ii) the \textit{conservation of
   momentum equation}:
@@
 virtual displacement field $\vect{u}^{\psi}_{p}$. Therefore, employing
-the definition of the material integral, where Riemann \PNA{ALGUNA CITA AQUI}
-integral definition is recovered as an addition of a finite set of points, and
-their volumes are interpreted as quadrature weights. Consequently,
+the definition of the material integral, where Riemann
+integral definition \cite{Riemann_1854} is recovered as an addition of
+a finite set of points, and their volumes are interpreted as quadrature weights. Consequently,
 individual terms in \eqref{eq:BalanceMomentum_wf} are solved as follows. 
@@
 , I = 1,2\ldots ,N_n$, is generated, being $N_n$ the number of grid
-nodes. \PNA{Spatial derivatives, such as gradients and
+nodes.\PNA{Spatial derivatives, such as gradients and
 divergences, are computed through the support of the background mesh.}
@@
 \end{equation}
-Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order \PNA{time} integration scheme is required. Therefore, time is
+Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order\PNA{time} integration scheme is required. Therefore, time is
 discretized into a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
@@
 made with the original \acrshort{mpm}, numerical noises appear when particles
-cross the cell boundaries. \PNA{Solving this issue is the main goal of the employment of the \acrshort{LME} shape functions}.
+cross the cell boundaries.\PNA{Solving this issue is the main goal of the employment of the \acrshort{LME} shape functions}.
 
@@
 recently tested under \acrshort{mpm} framework by Wobbes {\it et al.}
-(2020)\cite{Wobbes2020}. \PNA{The performed simulations of \acrshort{mpm}
+(2020)\cite{Wobbes2020}.\PNA{The performed simulations of \acrshort{mpm}
 within \acrshort{lme} in \cite{Wobbes2020} shows considerably more accurate stress
@@
 function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
-10$^{-6}$ \PNA{in this research},  would ensure a reasonable range of
+10$^{-6}$\PNA{in this research},  would ensure a reasonable range of
 neighbours (see \cite{Arroyo2006} for details).
@@
 described does not requires the employment of this artifices.
-Due to the \short{fem}-compatibility, the \acrshort{lme} shape function is degenerated to
-linear finite element shape function if $d+1$ neighbouring nodes are
-chosen as the support. Furthermore, with a conveniently adopted
-\textit{regularization} parameter it is possible to get a \acrshort{gimp}-like
-shape function. A proof of this statements is observed in figure~\ref{fig:LME_MPM}\PNA{COMENTAR MAS; ES LA DIFERENCIA CON WOBBES}. 
+Due to the \short{fem}-compatibility, the \acrshort{lme} shape
+function is degenerated to linear finite element shape function if
+$d+1$ neighbouring nodes are chosen as the support, where $d$ is the
+number of dimensions in the problem. Furthermore, with a conveniently
+adopted \textit{regularization} parameter it is possible to get a 
+\acrshort{gimp}-like shape function.\MMP{Finally \short{sph}-like
+behaviour can be obtained for lower values of $\gamma$ since the
+support of the shape function is drastically increase, and therefore
+\textit{smoother} solutions are obtained. See \cite{Navas2016} for an
+application of this capability, in this publication authors smooth 
+oscillations due to excess of pore water pressure in consolidation
+problems.}A proof of this statements is observed in figure~\ref{fig:LME_MPM}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-
 In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
@@
 \acrshort{lme} scheme, which uses an anisotropic support to deal with 
-tensile instability. \PNA{This is another benefit of the proposed methodology, that, although is out of the scope of the
+tensile instability.\PNA{This is another benefit of the proposed methodology, that, although is out of the scope of the
 present document, will be incorporated in future research.}
@@
 
-This benchmark was proposed \PNA{by Dyka~\cite{Dyka1995} since allows so study easily the capability}
+This benchmark was proposed\PNA{by Dyka~\cite{Dyka1995} since allows so study easily the capability}
 of the proposed time integration algorithm to avoid velocity
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this case, 0.0001 seconds \PNA{are considered }in the simulation. Therefore, the elastic wave generated travel through the bar
+In this case, 0.0001 seconds\PNA{are considered }in the simulation. Therefore, the elastic wave generated travel through the bar
 (from A to C and back to A) at least two times. For the spatial
@@
 numerical solutions evaluated in the final time step in the position
-of each particle.
-\PNA{In Fig.
+of each particle.\PNA{In Fig.
 \ref{fig:Dyka-error-evol} the evolution of the RMS is obtained for both time integration schemes.
@@
 grid-crossing meshfree behaviour is required to ensure the
-convergence of the solution and tiny values of $\gamma$ \PNA{may lead to better
+convergence of the solution and tiny values of $\gamma$\PNA{may lead to better
 performances}. Convergence plot in figure \eqref{fig:Dyka-error-evol}
@@
 monotonically with the value of the mesh size, in contrast with larger
-values of $\gamma$, \PNA{where the performance is punished with significant
+values of $\gamma$,\PNA{where the performance is punished with significant
 movement of the particles as far as the mesh size is reduced.} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \PNA{The performance of the
@@
 the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5
-millimeters. \PNA{The reason is due to an unstable
+millimeters.\PNA{The reason is due to an unstable
 increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yield unacceptable results}. A feasible
@@
 should be done in this direction for getting a better comprehension of
-this phenomenon. \PNA{Conversely, this shortcoming is not suffered by \acrshort{lme}, independently of regular or with irregular nodal layout.}
+this phenomenon.\PNA{Conversely, this shortcoming is not suffered by \acrshort{lme}, independently of regular or with irregular nodal layout.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-The financial support to develop this research from the Ministerio de Ciencia e Innovación, under Grant No.
+The financial support to develop this research from the Ministerio de Ciencia e Innovaci\'on, under Grant No.
 BIA-2016-76253 is greatly appreciated.
@@
 
-For the derivation of this analytical solution we will considered  the
-dynamic behaviour of a 1D elastic bar. The governing equations are the
-following: (i) The balance of linear momentum,
+For the derivation of this analytical solution, a 1D elastic bar is
+consider. Henceforth for convenience the governing equations will be written in terms of stress and velocity. The balance of linear momentum,
 \begin{equation}
@@
 \end{equation*}
-Note that the nature of \label{eq:eq:System-stress-velocity-II} is still
-hyperbolic despite the fact it does not have a second order
-time derivative as \eqref{eq:1D-wave-elastic}. A proof of this can
-be easily obtained if we get the zeros of the hypersurface defined by
-\eqref{eq:1D-wave-elastic}. And later the eigenvalues of $\Matrix{A}$
-in \eqref{eq:System-stress-velocity-II}. In both cases, eigenvalues
-are real and distinct ($\lambda = \pm \sqrt{\frac{E}{\rho}}$),
-therefore the system is called strictly hyperbolic.
-
-For a more general description in the following, we will assume that $\Matrix{A}$ has $n$
-different eigenvalues $\{ \lambda_1, \lambda_2, \ldots, \lambda_i, \ldots
-\lambda_n \}$ and $n$ eigenvectors $\{ \vec{x}^1, \vec{x}^2, \ldots,
+Despite of this manipulation, the nature
+of \label{eq:eq:System-stress-velocity-II} is still hyperbolic. A
+proof of this can be easily obtained computing the zeros of the
+hypersurface defined by \eqref{eq:1D-wave-elastic}. And later the
+eigenvalues of $\Matrix{A}$ in \eqref{eq:System-stress-velocity-II}. In both cases, eigenvalues are real and distinct ($\lambda = \pm \sqrt{\frac{E}{\rho}}$),
+therefore the system is called strictly hyperbolic. Assuming that  $\Matrix{A}$ has $n$ different eigenvalues $\{ \lambda_1, \ldots, \lambda_i, \ldots
+\lambda_n \}$ and $n$ eigenvectors $\{ \vec{x}^1, \ldots,
 \vec{x}^i, \ldots \vec{x}^n \}$ satisfying that $\tens{A} \vec{x} =
-\lambda \vec{x} $. Now we introduce the matrix $\Matrix{P}$ whose columns are the $n$
-eigenvalues $\Vector{x}$
+\lambda \vec{x} $. Now we introduce the matrix $\Matrix{P}$ whose columns are the $n$ eigenvalues $\Vector{x}$
 \begin{equation}

### 2020-04-27 LME-MPM.tex
Nuevo pdf (merge)

@@
 \textit{smoother} solutions are obtained. See \cite{Navas2016} for an
-application of this capability, in this publication authors smooth 
-oscillations due to excess of pore water pressure in consolidation
-problems.}A proof of this statements is observed in figure~\ref{fig:LME_MPM}.
+application of this capability, where publication oscillations due to
+excess of pore water pressure in consolidation problems are smoothed out by using this technique.}A proof of this statements is observed in figure~\ref{fig:LME_MPM}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:conclusions}
-We have developed a novel time integration scheme for \acrshort{mpm}, and
-proved how local \textit{max-ent} approximation scheme could be
-employed as an useful technique in \acrshort{mpm}. The \acrshort{npc} arise as a highly
-efficient alternative for challenging dynamic problems like coupled
-$u-p_w$ without appeal to expensive implicit time integration
-algorithms. Also the procedure employed to design the \acrshort{npc} algorithm open
-the door to revisit a huge variety of time integration schemes
-developed originally for \acrshort{fem}, which can be rearranged to \acrshort{mpm} framework
-with some modifications. Anyway, further research should be done to improve the
-formal comprehension of the algorithm good performance. This paper
-also enhances the suitability of the \acrshort{lme} approximation as a
-general promising alternative to the wide range of approximation.
-techniques developed for the \acrshort{mpm} to overcome grid crossing
-limitations and to avoid the constriction of the \acrshort{ugimp} of a regular mesh
-or a high density of particles per cell. Future research of the
-group will be on the employ of this scheme to improve the localization
-capabilities of \acrshort{mpm} for viscoplastic materials. Finally we remark on
-the possibility of adapting the function $\beta(\vect{x})$ as a second
-order tensor with the aim of adapt the shape function with the strain field which improves the
-performance of it in the aforementioned localization
-capabilities. Other possibility is to adapt the value of $\beta$ to
-solve the equations \acrshort{fem}-like of meshfree-like depending of how behaves
-the region, this could be extremely useful in simulating all together
-initialization and propagation of fast landslides.
-
-\begin{acknowledgements}
-If you'd like to thank anyone, place your comments here
-and remove the percent signs.
-\end{acknowledgements}
-
+We have developed a novel time integration scheme for
+\acrshort{mpm}. The \acrshort{npc} arise as a highly efficient
+alternative for demanding dynamic problems like coupled $u-p_w$
+without appeal to expensive implicit time integration algorithms. Also
+the procedure employed to design the \acrshort{npc} algorithm open the
+door to revisit a huge variety of time integration schemes developed
+originally for \acrshort{fem}, which can be rearranged to
+\acrshort{mpm} framework with some modifications. Anyway, further
+research should be done to elucidate the formal comprehension of the
+algorithm good performance. This paper also enhances the skills of
+local \textit{max-ent} approximation scheme as a robust and versatile
+tool in the \acrshort{mpm} framework. It also come up as a promising
+alternative to other approximation techniques developed for the
+\acrshort{mpm} to overcome grid crossing limitations and to avoid the
+constriction of the \acrshort{ugimp} of a regular mesh or a high
+density of particles per cell. Future research of the group will be on
+the employ of this scheme to strengthen the localization capabilities of
+\acrshort{mpm} for viscoplastic materials. Finally we remark on the
+possibility of adapting the function $\beta(\vect{x})$ through the finite strain
+tensor in order to guide the shape function in the principal strain
+direction to way select the most suitable set of nodes. Other
+research line is the possibility to adapt the value of $\beta$ to solve the equations
+\acrshort{fem}-like of meshfree-like depending of how behaves the
+region, this could be extremely useful to reproduce such challenging
+scenarios as simulating simultaneously both initialization and
+propagation stages of fast landslides.
 % 

### 2020-04-28 LME-MPM.tex
Finished PNA

@@
   name=$ \Gamma_n$,
-  description={Natural or Nemann boundary conditions over $\partial\varOmega$}
+  description={Natural or Neumann boundary conditions over $\partial\varOmega$}
 }
@@
 techniques. To avoid introducing this nonphysical sources, many
-researchers has proposed alternative time integration
+researchers have proposed alternative time integration
 schemes which reduce the presence of high frequency noises by
-filtering them or increasing\PNA{somehow} the accuracy.\MMP{One of the first attempts of it was
+filtering them or increasing\PNA{somehow} the accuracy.\MMP{One of the first attempts was
 the proposal of an implicit time integration scheme by Guilkey \&
 Weiss \cite{Guilkey_2003}. More recently Wang {\it et al.}
-\cite{Wang_2016} to downsize this spurious noises add a nonvoiscous
+\cite{Wang_2016} downsized these spurious noises by adding a non-viscous
 damping to the linear momentum balance equation, and later Charlton
@@
 effort.} In this paper a less time consuming and high efficient explicit predictor-corrector integration method has been
-proposed. It consists in an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
+proposed. It consists of an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
 has been chosen among other suitable alternatives as those proposed
@@
 \label{sec:conclusions}
-We have developed a novel time integration scheme for
-\acrshort{mpm}. The \acrshort{npc} arise as a highly efficient
-alternative for demanding dynamic problems like coupled $u-p_w$
-without appeal to expensive implicit time integration algorithms. Also
+\PNA{The proposed research has dived into the performance of the \acrfull{mpm} within dynamic problems of very fast loading rate.
+The main goal, which was the enhancement of such a methodology with different time and spatial discretization tools in order to stabilize the solution, has been satisfactory fulfilled.}
+
+\PNA{On the one hand,} a novel time integration scheme for
+\acrshort{mpm} has been carried out. The \acrshort{npc} arises as a highly efficient
+alternative for demanding dynamic problems \PNA{with high frequency of the applied loads.
+In the literature, several approaches of the \acrshort{npc} are proposed in order to compete on accuracy with expensive implicit time integration algorithms.} \PNA{The main achievement of the proposed time discretization has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.}
+Also,
 the procedure employed to design the \acrshort{npc} algorithm open the
 door to revisit a huge variety of time integration schemes developed
-originally for \acrshort{fem}, which can be rearranged to
-\acrshort{mpm} framework with some modifications. Anyway, further
-research should be done to elucidate the formal comprehension of the
-algorithm good performance. This paper also enhances the skills of
-local \textit{max-ent} approximation scheme as a robust and versatile
-tool in the \acrshort{mpm} framework. It also come up as a promising
-alternative to other approximation techniques developed for the
-\acrshort{mpm} to overcome grid crossing limitations and to avoid the
+originally for \acrshort{fem}, which can be rearranged to the
+\acrshort{mpm} framework with the required modifications. \PNA{As well as the implementation of enhanced time integration schemes, further
+research may be done in the comprehension of the
+good performance of the algorithm within non-linear solutions, such as the coupling between different phases or the non-linear constitutive behaviour of the materials: the employment of this scheme to strengthen the localization capabilities of \acrshort{mpm} for viscoplastic materials is on the scope of this research line.
+The comparison with traditional time schemes in the non-linear field will improve the formal understanding of the proposed methodology.}
+
+\PNA{On the other hand, the spatial discretization of the \acrshort{mpm} is enhanced thanks to the powerful skills of the \acrfull{lme} approximation scheme, which has been validated as a robust and versatile
+tool in the \acrshort{mpm} framework.} It also comes up as a promising
+alternative to other approximation techniques\PNA{, developed within the
+\acrshort{mpm} field, in order }to overcome grid crossing limitations and to avoid the
 constriction of the \acrshort{ugimp} of a regular mesh or a high
-density of particles per cell. Future research of the group will be on
-the employ of this scheme to strengthen the localization capabilities of
-\acrshort{mpm} for viscoplastic materials. Finally we remark on the
-possibility of adapting the function $\beta(\vect{x})$ through the finite strain
+density of particles per cell.
+\PNA{Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vect{x})$ through the finite strain
 tensor in order to guide the shape function in the principal strain
-direction to way select the most suitable set of nodes. Other
-research line is the possibility to adapt the value of $\beta$ to solve the equations
+direction to select the most suitable set of nodes adapted to the strain, as well as the possibility of adapting} the value of $\beta$ to solve the equations
 \acrshort{fem}-like of meshfree-like depending of how behaves the
-region, this could be extremely useful to reproduce such challenging
-scenarios as simulating simultaneously both initialization and
-propagation stages of fast landslides.
+region. \PNA{Together with the implementation of non-linear behaviours, previously mentioned, challenging
+scenarios could be reproduced, being the main purpose of the research line the simultaneous simulation of both initialization and
+propagation stages of fast landslides.}
+
 % 

### 2020-04-28 LME-MPM.tex
Nuevas citas CMAME

@@
 \usepackage{float}
+\usepackage{textcomp}
 \usepackage{subfig}
@@
 \newacronym{fem}{FEM}{Finite Element Method}
+\newacronym{efgm}{EFGM}{Element-Free Galerkin Method} 
 \newacronym{lme}{LME}{Local Maximum-Entropy}
@@
 the dynamic regime by other researchers, being important the contributions of Li {\it et al.} (2012)~\cite{Li2012} and Navas {\it et al.}
-(2018)~\cite{Navas:17b,Navas2018a} in the explicit regime and Navas {\it et al.}~\cite{Navas2016,Navas2016b,Navas:17c} and Wriggers and coworkers~\cite{Wriggers18} with implicit schemes. And more
+(2018)~\cite{Navas:17b,Navas2018a} in the explicit regime and Navas
+{\it et al.}~\cite{Navas2016,Navas2016b,Navas:17c} and Wriggers and
+coworkers~\cite{Wriggers18} with implicit schemes. More
 recently, under \acrshort{mpm} framework, the work made by Wobbes {\it et
@@
 \cite{Wang_2016} can totally over-damp the solution in time-dependent
-simulations such as in consolidation process. Within the explicit
-time integration schemes, Lu {\it et al.}\cite{LU_2018} introduced the time-discontinuous Galerkin method to control the spurious noises
+simulations such as in consolidation process. In a recent publication,
+Kularathna \& Soga \cite{Soga_2017} study an implicit treatment of the pressure in MPM algorithm to simulate material incompressibility
+avoiding artificial pressure oscillations by applying
+Chorin\textquotesingle s
+projection. Within the explicit time integration schemes, Lu {\it et al.}\cite{LU_2018} introduced the time-discontinuous Galerkin method to control the spurious noises
 propagation, and later Tran \& Solowski~\cite{Tran2019e}
@@
 $d+1$ neighbouring nodes are chosen as the support, where $d$ is the
-number of dimensions in the problem. Furthermore, with a conveniently
+number of dimensions in the problem. \MMP{Ullah {\it et al.}
+  \cite{Augarde_2013} take advantage of the \acrshort{lme}
+  \short{fem}-compatibility to couple the
+  \acrfull{efgm} and \short{fem} for linear elasticity and for problems with both material and geometrical nonlinearities.}Furthermore, with a conveniently
 adopted \textit{regularization} parameter it is possible to get a 
@@
 application of this capability, where publication oscillations due to
-excess of pore water pressure in consolidation problems are smoothed out by using this technique.}A proof of this statements is observed in figure~\ref{fig:LME_MPM}.
+excess of pore water pressure in consolidation problems are smoothed
+out by using this technique. The employment of smoothing algorithm is
+also straightforward in the fluid-solid interaction problems
+\cite{Arduino_2018}.A proof of this statements is observed in
+figure~\ref{fig:LME_MPM}, where the \acrshort{lme} adaptability is illustrate.}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The following test was proposed to \PNA{validate} \cancel{measure proof} the ability of the proposed
+The following test was proposed to \PNA{validate} the ability of the proposed
 interpolation technique to deal with grid crossing instabilities. It
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-This test was \cancel{taken from PhD thesis of Andersen} \PNA{previously proposed by Andersen} (2009)\cite{thesis_Andersen_2009}. The
+This test was \PNA{previously proposed by Andersen} (2009)\cite{thesis_Andersen_2009}. The
 elastic parameters considered for this test are: 
@@
 cell-crossing and consequently fail. The \acrshort{ugimp} simulation
-is more stable than the one performed by the Q4, \PNA{although} \cancel{Despite this} is still
+is more stable than the one performed by the Q4, \PNA{although} is still
 unstable and could trigger severe oscillations in simulation with

### 2020-05-28 LME-MPM.tex
Versión 2
Cambios MP 28-5-2020

@@
 
-\newcommand{\MMS}[1]{
-  \textcolor{gree}{{#1}}
+\newcommand{\MP}[1]{
+  \textcolor{green}{{#1}}
 }
@@
 
-\title{Enhanced Material Point Method to face
-  dynamic problems: Local-maximum entropy approximation and explicit
-  predictor-corrector scheme\\
-  \PNA{On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme}}
+\title{On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme}
 
@@
 \author{
-Miguel Molinos$^a$
+Miguel Molinos$^a\footnote{Corresponding author: m.molinoss@outlook.es}$
 Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es},
@@
   deformation regime. However, the simulation of shock waves
-  propagation and other high frequency problems is still challenging
+  propagation and \MP{in the large deformation regime} is still challenging
   under this approach due the incapability of the standard \acrshort{mpm} time
-  integration scheme to filter spurious noises. To overcome this
-  limitation in this paper, an Explicit Predictor-Corrector time
-  integration scheme has been proposed. Its \textcolor{red}{powerful}
+  integration scheme to filter spurious noises. \MP{To overcome it ,
+    we propose in this paper an explicit Predictor-Corrector time integration scheme}. Its \textcolor{red}{powerful}
   performance mitigates the presence of spurious oscillations with
@@
   numerical noise in \acrshort{mpm} occurs when the material points
-  cross computational grid boundaries, being this issue motivated by
+  cross computational grid boundaries, being \MP{caused} by
   the lack of smoothness of the interpolation functions. This noise
@@
   solutions as well as aborted simulations in the worst cases. To
-  overcome it, this document adopts the \acrfull{lme} approximation
+  overcome it, \MP{we propose in this work} the \acrfull{lme} approximation
   schemes as a robust substitute of the traditional shape function in
@@
 has increased due to its ability to deal with large strain regime
-without suffer mesh distortion inaccuracies.\PNA{One of the main fields where this method is strong is the dynamic one since the original time integration scheme proposed was the \acrfull{fe}~\cite{Sulsky1994}, carried out in a explicit manner.
+without suffer mesh distortion inaccuracies.\PNA{One of the main
+  fields where this method is strong} \MP{in solid dynamics \PNA{since the original time integration scheme proposed was the \acrfull{fe}~\cite{Sulsky1994}, carried out in a explicit manner.
 However, in this type or problems, the main instabilities of the original \acrshort{mpm} are even marked.}
@@
 or gaps when the material point mesh becomes irregular, which can
-introduce severe inaccuracies as noticed Steffen {\it et al.}
+introduce severe inaccuracies as noticed \MP{by} Steffen {\it et al.}
 (2008)\cite{Steffen2008}. This is similar to the difficulty
@@
 unsatisfactory behaviour when particle/cell ratio
-decreases~\cite{DHAKAL2016301}. Therefore \acrshort{ddmp} a large number of particles is needed for convergence, what
-makes the method very expensive. In recent years the employment of
-spline-lines as shape functions has gain popularity with the introduction of the B-Spline 
-\acrshort{mpm} proposed by Roel Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
+decreases. Therefore \acrshort{ddmp} a large
+number of particles is needed for convergence~\cite{DHAKAL2016301}, what makes the method
+very expensive. In recent years the employment of spline-lines as shape functions has gain popularity with the introduction of the B-Spline 
+\acrshort{mpm} proposed by Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
 this technique allows the employment of unstructured set of notes and
@@
 reconstruction proposed by Wobbes {\it et al.}
-(2018)~\cite{E_Wobbes_2018}. Unfortunately, when particles are spread in
-a challenging way, the quality of the \acrshort{ctls} approximation decreases locally.
+(2018)~\cite{E_Wobbes_2018}. Unfortunately, when particles are spread
+in \MP{some particular special patterns}, the quality of the \acrshort{ctls} approximation \MP{decrease} locally.
 
@@
 Weiss \cite{Guilkey_2003}. More recently Wang {\it et al.}
-\cite{Wang_2016} downsized these spurious noises by adding a non-viscous
+\cite{Wang_2016}} \MP{mitigated} \MMP{these spurious noises by adding a non-viscous
 damping to the linear momentum balance equation, and later Charlton
@@
 promising results but at the expense of increasing the computational
-effort.} In this paper a less time consuming and high efficient explicit predictor-corrector integration method has been
+effort.} In this paper a less time consuming and high efficient explicit predictor-corrector integration method \MP{is}
 proposed. It consists of an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
@@
 by Wilson {\it et al.} (1972)~\cite{Wilson1972} or Chung \& Hulbert
-(1993)~\cite{Geranlized_alpha_1993} because its simplicity and its good
+(1993)~\cite{Geranlized_alpha_1993} because its simplicity and good
 performance dealing with solid dynamic problems under a meshfree
@@
 explicit \acrshort{mpm} algorithm~\cite{Sulsky1994}. Without loosing
-generality, the method is composed by three main steps: (i) a
-variational recovery process, where particle data is projected to the
+generality, the method \MP{consists of} three main steps: (i) a
+variational recovery process, where particle data is projected \MP{onto} the
 grid nodes, (ii) an Eulerian step, where balance of momentum equation
@@
 
-In \acrshort{mpm} the continuum mechanics approach is considered. So on, let
-define a continuum \gls{domain}  occupied by an elastic body like
+In \acrshort{mpm} the continuum mechanics approach is considered. So on, \MP{we will consider a region \gls{domain} }occupied by an elastic body like
 the sketched in the figure~\ref{fig:Continuum-solid}, and \gls{contour} the boundaries of the domain defined by $\partial \varOmega
@@
 field \gls{u} through the following set of governing equations and
-restrictions that must be satisfied.\PNA{First (i) the \textit{compatibility
-  equation}, where the the strain field \gls{strain} is extracted from \gls{u} is defined as:}
+restrictions that must be satisfied.\MP{First (i) we will relate
+  global to local state by the \textit{compatibility equation}, where the the strain field \gls{strain} is extracted from \gls{u} is defined as:}
 \begin{equation}
@@
 \end{equation}
-together with essential boundary conditions of Dirichlet type \gls{dirichlet-boundary}. An additional consideration over the strain field is
-the assumption of inifinitesimal strain, therefore second order terms
-in the spatial derivatives can be neglected.\PNA{Therefore, the stress field \gls{stress} will be considered the corresponding conjugate variable for the strain field, being the one} which satisfies (ii) the \textit{conservation of
-  momentum equation}:
+together with essential boundary conditions of Dirichlet type
+\gls{dirichlet-boundary}.\MP{We will further assume that strains are
+infinitesimal}, therefore second order terms
+in the spatial derivatives can be neglected.\MP{From here}, \PNAthe
+stress field \gls{stress} will be considered the corresponding
+conjugate variable for the strain field, being the one} which
+satisfies (ii) the \textit{conservation of \MP{lineal} momentum equation}:
 \begin{equation}
@@
 together with the natural boundary conditions of the Neumann type \gls{neumann-boundary}.  An aditional component will be (iii) the constitutive equation as a linear
-application from $\Re^n$ to $\Re^n$, which relates the
-strain tensor with the stress tensor:
+application \MP{from $\mathbb{R}^n$ to $\mathbb{R}^n$, which relate stress and strain increments as,}
 \begin{equation}
@@
 \end{equation}
-\PNA{In this research, plane strain Linear Elasticity has been considered.
-Thus the constitutive tensor, \tens{D}, is the well known linear elastic one.} The final restriction is (iv) the mass conservation, which can be obtained by
-setting to zero the total derivative of the density field,
+\PNA{In this research, plane strain Linear Elasticity has been
+  considered. Thus the constitutive tensor, \tens{D}, is the well
+  known linear elastic one.} The final \MP{equation of the set} is (iv) the mass
+conservation, which can be obtained by setting to zero the total derivative of the density field,
 \begin{equation}
@@
 \end{equation}
-satisfying that the Cauchy sequences are convergent in \gls{domain} as well:
+\MP{in which} the Cauchy sequences are convergent in \gls{domain} as well:
 \begin{equation}
@@
 the boundary-value problem of elasticity is the function $\vect{u} \in
-\mathcal{H}^1_0$ such that, for $\vect{u}^{\psi} \in
-\mathcal{H}^1_0$, the following holds:
+\mathcal{H}^1_0$ such that, for \MP{any} $\vect{u}^{\psi} \in
+\mathcal{H}^1_0$,
+the following holds:
 \begin{equation}
@@
 
-In order to obtain a finite set of equations, in contrast with the
-\acrshort{fem}, in \acrshort{mpm} a double discretization procedure is
-performed. First, the continuum \gls{domain} is discretized with a finite sum of material points (also denominated particles the manuscript). Each material point
+\MP{Next, we will discretize the set of equations of the mathematical model using a double discretization procedure.} First, the continuum \gls{domain} is discretized with a finite sum of material points (also denominated particles the manuscript).
+Each material point
 represents a part of the discretized domain $\varOmega_p \subset
@@
 $\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$ respectively are assigned to each material point, which also owns the
-virtual displacement field $\vect{u}^{\psi}_{p}$. Therefore, employing
-the definition of the material integral, where Riemann
-integral definition \cite{Riemann_1854} is recovered as an addition of
-a finite set of points, and their volumes are interpreted as quadrature weights. Consequently,
+virtual displacement field $\vect{u}^{\psi}_{p}$. \MP{Regarding numerical integration, the material derivatives are
+  evaluated using the Riemann integral definition \cite{Riemann_1854}
+  applied to a finite set of points which associated volumes are
+  interpreted as quadrature weights.} Consequently,
 individual terms in \eqref{eq:BalanceMomentum_wf} are solved as follows. 
@@
 \end{itemize}
-where $h$ is the thickness of the continuum in a 2D case. Following, the aforementioned second discretization procedure appears. A background mesh
-composed by a finite set of grid points with coordinates $\vec{x}_I\
+where $h$ is the thickness of the continuum in a 2D case. \MP{Next, we
+  will proceed with the second step of the discretization. It is based on using a background grid } with coordinates $\vec{x}_I\
 , I = 1,2\ldots ,N_n$, is generated, being $N_n$ the number of grid
@@
 
-\subsection{\acrshort{mpm} time integration scheme: the Explicit Predictor-Corrector proposal}
+\subsection{\acrshort{mpm} time integration scheme: the Newmark Predictor-Corrector proposal}
 %\subsection{Explicit predictor-corrector scheme for \acrshort{mpm}.}
@@
 $\vect{f}_I^{int,k}$ can be infinite for an infinitesimal nodal mass
-$\tens{m}$. This issue may lead to numerical issues when nodal acceleration
+$\tens{m}$. This issue may lead to numerical \MP{problems} when nodal acceleration
 is obtained in the evaluation of the Eqs. \eqref{eq:Sulsky-1994-UL-x} and \eqref{eq:Sulsky-1994-UL-v}. Hence, a
@@
 
-This scheme has been proven to damps out the highest frequency noises
+This scheme has been proven to damp out the highest frequency noises
 \cite{Tran2019e}. However, it can present the same numerical instabilities
@@
 In this section, an explicit predictor-corrector time integration
-scheme is proposed. It is based on the Newmark central differences explicit scheme, which is also denominated a-form 
+scheme is proposed. It is based on the Newmark central differences
+explicit scheme, which is also \MP{referred to as} a-form 
 $\gamma = 0.5$ and $\beta = 0$. This method is devoted to solve a system of equations of the type
@@
 \end{equation*}
-\PNA{The nodal \acrshort{mpm} stage allows to apply this method
-in the \acrshort{mpm} framework in a similar manner that the one
-proposed by Tran~\it{et al.}~\cite{Tran2019e}. Taking into account the predictor definition, it is possible to calculate
-nodal velocities and update particles position employing nodal values
+\PNA{The nodal \acrshort{mpm} stage allows to apply this method}
+\MP{within} \PNA{the \acrshort{mpm} framework in a similar manner that the one
+proposed by Tran~\it{et al.}~\cite{Tran2019e}.} \MP{By using the} \PNAthe predictor definition, it is possible to calculate nodal velocities and update particles position employing nodal values
 of velocity and acceleration.}
@@
 equilibrium equation \eqref{eq:particle_balance_forces3}. Next, the
-\textit{corrector} stage is introduced. Due to the fact that nodal
+\textit{corrector} stage is introduced. \MP{As} nodal
 velocities were obtained earlier, this step is computed in the same way as
@@
 \end{equation}
-Finally updated particle kinetics are computed using nodal values as:
+Finally updated particle \MP{accelerations, velocities and positions are updated as},
 \begin{align}
@@
 are computed using the corrected velocities. Therefore here we share similarities
-with the \textit{leapfrog integration} where position is not updated at
+with the \textit{leapfrog \MP{scheme}} where position is not updated at
 full time step, but the velocity is updated at half time steps. Notice
@@
 recently tested under \acrshort{mpm} framework by Wobbes {\it et al.}
-(2020)\cite{Wobbes2020}.\PNA{The performed simulations of \acrshort{mpm}
-within \acrshort{lme} in \cite{Wobbes2020} shows considerably more accurate stress
-approximations than traditional \acrshort{mpm} schemes. However, 
-how the regularization parameter $\beta$
-affects to the accuracy and stability of the solution is not assessed deeply in that research, which is considered interesting in the present manuscript; the tuning of this $\beta$ parameter allows to make the comparison of the accuracy against analogous traditional \acrshort{mpm} shape function.}
-
-The basic idea
-of the shape functions based on such an estimate is to interpret the shape function $N_I(\vec{x})$ as a probability. This allows us to introduce two important limits:
+(2020)\cite{Wobbes2020}. \MP{The simulations presented in \cite{Wobbes2020} of \acrshort{mpm}
+within \acrshort{lme} show considerably more accurate stress
+approximations than traditional \acrshort{mpm} schemes.} \PNA{However, 
+how the regularization parameter $\beta$ affects to the accuracy and
+stability of the solution is not assessed deeply in that research, the tuning of this $\beta$ parameter allows to make the comparison of the accuracy against analogous traditional \acrshort{mpm} shape function.}
+
+The basic idea of the shape functions based on such an estimate is to interpret the shape function $N_I(\vec{x})$ as a probability. This allows us to introduce two important limits:
 the principle of maximum-entropy (\textit{max-ent}) statistical
@@
 functions. To avoid some mesh-dependent issues, in all
-calculations a regular background mesh was set. All simulations were performed with in-hose software.
+calculations a regular background mesh was set. All simulations were
+performed with in-house software.
 
@@
 of the proposed time integration algorithm to avoid velocity
-field instabilities. It consists of a one-dimensional bar of a length of 0.1333 meters, sketched in the
-figure~\ref{fig:Dyka_Bar}. The boundary conditions are: displacements are constrained ($\vect{v} \rvert_{x=L} = 0$) in the right
-border, letting free in the rest of the body and ($\tens{\sigma} \rvert_{x=0} =
-0$). An initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
-left quarter of the bar. Finally, the elastic parameters considered for this test are:
+field instabilities. It consists of a one-dimensional bar of a length
+of 0.1333 meters, sketched in the figure~\ref{fig:Dyka_Bar}. The
+boundary conditions are: displacements are constrained ($\vect{v}
+\rvert_{x=L} = 0$) in the right border, \MP{being free on all other boundaries.} An initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
+left quarter of the bar. Finally, the elastic parameters \MP{chosen} for this test are:
 \begin{itemize} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this case, 0.0001 seconds\PNA{are considered }in the simulation. Therefore, the elastic wave generated travel through the bar
-(from A to C and back to A) at least two times. For the spatial
+\MP{In the proposed exmple, the simulation extends from time zero up to 0.00001 s.
+This time interval allows the elastic wave to travel a distance of 2.6
+lengths of the bar}. For the spatial
 discretization, a set of seven nodal mesh sizes (0.1, 0.3325, 0.5,
@@
 four particles was selected. In the initial layout, particles are
-occupying the exact quadrature points of a linear quadrilateral, with
+\MP{located} the exact quadrature points of a linear quadrilateral, with
 the exception of the \acrshort{ugimp} simulation, where gaps or overlap between
@@
 \end{equation}
-An important consideration regarding modellization concerns to the
+An important consideration regarding modellization concerns the
 background mesh. Notice that free border of the bar has a maximum
@@
 
-A first comparative between the velocity results of both time integration
+A first \MP{comparison} between the \MP{obtained in} both time integration
 schemes is plotted in figure \ref{fig:Dyka-NPC-FE}. It demonstrates the
@@
   }
-  \caption{Comparative of the \acrshort{npc} \textit{versus} the \acrshort{fe}. In the
-    picture the velocity evolution at the point in the bar left side
+  \caption{\MP{comparison of \acrshort{npc} and \acrshort{fe}
+      performances}: In the picture the velocity evolution at the point in the bar left side
     is plotted.}
@@
 
-Figure \eqref{fig:Dyka-LME-gamma} shows the sensibility of the \acrshort{lme}
+Figure \eqref{fig:Dyka-LME-gamma} shows the \MP{sensitivity} of the \acrshort{lme}
 approximation scheme to variations in the parameter
@@
 solutions. This capability could be useful in simulations where
-extremely noise oscillations could damage the solutions like memory
+extremely \MP{noisy} oscillations could damage the solutions like memory
 materials. On the other hand larger values of the parameter $\beta$
-makes the solution tend to the linear \acrshort{fem} solution as the athermal limit is reached \cite{Arroyo2006}. Intermediate values of the
-regularization parameters give us a compromise between the both
-scenarios here described. An additional observation, concerning to the
+make the solution \MP{to tend} to the linear \acrshort{fem} solution as the athermal limit is reached \cite{Arroyo2006}. Intermediate values of the
+regularization parameters give us a compromise \MP{between both scenarios described here}. An additional observation, concerning to the
 solution sensibility depending on the regularization parameters, \PNA{is the behaviour of the solution depending on the decreasing of mesh
@@
   }
-  \caption{Sensitive of LME approximants performance to changes in the
+  \caption{\MP{Sensitivity} of LME approximants performance to changes in the
     dimensionless regularization parameter $\gamma = \beta/h^2$. To
@@
 
-Finally, the \acrshort{otm}~\cite{Li2010} \textit{versus} obtained solution is compared against the one obtained with \acrshort{mpm}, both with same time integration scheme and spatial discretization, and results are shown in figure \ref{fig:Dyka-OTM-MPM}.
+Finally, the \acrshort{otm}~\cite{Li2010} solution is compared against the one obtained with \acrshort{mpm}, both with same time integration scheme and spatial discretization, and results are shown in figure \ref{fig:Dyka-OTM-MPM}.
 In
@@
 \label{sec:conclusions}
-\PNA{The proposed research has dived into the performance of the \acrfull{mpm} within dynamic problems of very fast loading rate.
-The main goal, which was the enhancement of such a methodology with different time and spatial discretization tools in order to stabilize the solution, has been satisfactory fulfilled.}
-
-\PNA{On the one hand,} a novel time integration scheme for
-\acrshort{mpm} has been carried out. The \acrshort{npc} arises as a highly efficient
-alternative for demanding dynamic problems \PNA{with high frequency of the applied loads.
-In the literature, several approaches of the \acrshort{npc} are proposed in order to compete on accuracy with expensive implicit time integration algorithms.} \PNA{The main achievement of the proposed time discretization has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.}
-Also,
-the procedure employed to design the \acrshort{npc} algorithm open the
+\MP{We have proposed in this paper an improved methodology which improves \acrfull{mpm} behaviour in fast dynamics problems.
+Different time and space discretization techniques have been presented, their performance being compared agains other approaches in two benchmark problems.}
+\MP{First,} a novel time integration scheme for
+\acrshort{mpm} has been carried out. The \acrshort{npc} \MP{has been
+  shown to be a highly} efficient alternative for demanding \MP{fast dynamics} problems.
+\PNA{In the literature, several approaches of the \acrshort{npc} are proposed in order to compete on accuracy with expensive implicit time integration algorithms.} \PNA{The main achievement of the proposed time discretization has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.}
+Also, the procedure employed to design the \acrshort{npc} algorithm opens the
 door to revisit a huge variety of time integration schemes developed
-originally for \acrshort{fem}, which can be rearranged to the
-\acrshort{mpm} framework with the required modifications. \PNA{As well as the implementation of enhanced time integration schemes, further
-research may be done in the comprehension of the
-good performance of the algorithm within non-linear solutions, such as the coupling between different phases or the non-linear constitutive behaviour of the materials: the employment of this scheme to strengthen the localization capabilities of \acrshort{mpm} for viscoplastic materials is on the scope of this research line.
+originally for \acrshort{fem}, which can be \MP{implemented within a
+  \acrshort{mpm} framework with the suitable} modifications. \MP{In
+addition to} \PNA{the implementation of enhanced time integration schemes, further
+research} \MP{can be done in the analysis of the good performance} \PNA{of the algorithm within non-linear solutions, such as the coupling between different phases or the non-linear constitutive behaviour of the materials: the employment of this scheme to strengthen the localization capabilities of \acrshort{mpm} for viscoplastic materials is on the scope of this research line.
 The comparison with traditional time schemes in the non-linear field will improve the formal understanding of the proposed methodology.}
@@
 alternative to other approximation techniques\PNA{, developed within the
-\acrshort{mpm} field, in order }to overcome grid crossing limitations and to avoid the
+\acrshort{mpm}} \MP{framework, in order }to overcome grid crossing limitations and to avoid the
 constriction of the \acrshort{ugimp} of a regular mesh or a high
@@
 \PNA{Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vect{x})$ through the finite strain
-tensor in order to guide the shape function in the principal strain
+tensor in order to align the shape functions in the principal strain
 direction to select the most suitable set of nodes adapted to the strain, as well as the possibility of adapting} the value of $\beta$ to solve the equations

### 2020-05-28 _region_.tex
Cambios MP 28-5-2020

@@
 techniques. To avoid introducing this nonphysical sources, many
-researchers has proposed alternative time integration
+researchers have proposed alternative time integration
 schemes which reduce the presence of high frequency noises by
-filtering them or increasing\PNA{somehow} the accuracy.\MMP{One of the first attempts of it was
+filtering them or increasing\PNA{somehow} the accuracy.\MMP{One of the first attempts was
 the proposal of an implicit time integration scheme by Guilkey \&
 Weiss \cite{Guilkey_2003}. More recently Wang {\it et al.}
-\cite{Wang_2016} to downsize this spurious noises add a nonvoiscous
+\cite{Wang_2016}} \MP{mitigated} \MMP{these spurious noises by adding a non-viscous
 damping to the linear momentum balance equation, and later Charlton
@@
 promising results but at the expense of increasing the computational
-effort.} In this paper a less time consuming and high efficient explicit predictor-corrector integration method has been
-proposed. It consists in an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
+effort.} In this paper a less time consuming and high efficient explicit predictor-corrector integration method \MP{is}
+proposed. It consists of an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
 has been chosen among other suitable alternatives as those proposed
 by Wilson {\it et al.} (1972)~\cite{Wilson1972} or Chung \& Hulbert
-(1993)~\cite{Geranlized_alpha_1993} because its simplicity and its good
+(1993)~\cite{Geranlized_alpha_1993} because its simplicity and good
 performance dealing with solid dynamic problems under a meshfree
@@
 \textit{smoother} solutions are obtained. See \cite{Navas2016} for an
-application of this capability, in this publication authors smooth 
-oscillations due to excess of pore water pressure in consolidation
-problems.}A proof of this statements is observed in figure~\ref{fig:LME_MPM}.
+application of this capability, where publication oscillations due to
+excess of pore water pressure in consolidation problems are smoothed
+out by using this technique. The employment of smoothing algorithm is
+also straightforward in the fluid-solid interaction problems
+\cite{Arduino_2018}.A proof of this statements is observed in
+figure~\ref{fig:LME_MPM}, where the \acrshort{lme} adaptability is illustrate.}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The following test was proposed to measure proof the ability of this
+The following test was proposed to \PNA{validate} the ability of the proposed
 interpolation technique to deal with grid crossing instabilities. It
-consists in the simulation of a square block of soil incrementally
+consists of the simulation of a square block of soil incrementally
 loaded by a body force. Details of the problem are sketched in figure~\ref{fig:block}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-This test was taken from PhD thesis of Andersen (2009)\cite{thesis_Andersen_2009}. The
-elastic parameters consider for this test are: 
+This test was \PNA{previously proposed by Andersen} (2009)\cite{thesis_Andersen_2009}. The
+elastic parameters considered for this test are: 
 \begin{itemize} 
@@
 interpolation technique (Q4) turns out to be unstable during
-cell-crossing and consequently fails. The \acrshort{ugimp} simulation
-is more stable than the one performed by the Q4. Despite this is still
+cell-crossing and consequently fail. The \acrshort{ugimp} simulation
+is more stable than the one performed by the Q4, \PNA{although} is still
 unstable and could trigger severe oscillations in simulation with
@@
 \label{sec:conclusions}
-We have developed a novel time integration scheme for \acrshort{mpm}, and
-proved how local \textit{max-ent} approximation scheme could be
-employed as an useful technique in \acrshort{mpm}. The \acrshort{npc} arise as a highly
-efficient alternative for challenging dynamic problems like coupled
-$u-p_w$ without appeal to expensive implicit time integration
-algorithms. Also the procedure employed to design the \acrshort{npc} algorithm open
-the door to revisit a huge variety of time integration schemes
-developed originally for \acrshort{fem}, which can be rearranged to \acrshort{mpm} framework
-with some modifications. Anyway, further research should be done to improve the
-formal comprehension of the algorithm good performance. This paper
-also enhances the suitability of the \acrshort{lme} approximation as a
-general promising alternative to the wide range of approximation.
-techniques developed for the \acrshort{mpm} to overcome grid crossing
-limitations and to avoid the constriction of the \acrshort{ugimp} of a regular mesh
-or a high density of particles per cell. Future research of the
-group will be on the employ of this scheme to improve the localization
-capabilities of \acrshort{mpm} for viscoplastic materials. Finally we remark on
-the possibility of adapting the function $\beta(\vect{x})$ as a second
-order tensor with the aim of adapt the shape function with the strain field which improves the
-performance of it in the aforementioned localization
-capabilities. Other possibility is to adapt the value of $\beta$ to
-solve the equations \acrshort{fem}-like of meshfree-like depending of how behaves
-the region, this could be extremely useful in simulating all together
-initialization and propagation of fast landslides.
-
-\begin{acknowledgements}
-If you'd like to thank anyone, place your comments here
-and remove the percent signs.
-\end{acknowledgements}
+\MP{We have proposed in this paper an improved methodology which improves \acrfull{mpm} behaviour in fast dynamics problems.
+Different time and space discretization techniques have been presented, their performance being compared agains other approaches in two benchmark problems.}
+\MP{First,} a novel time integration scheme for
+\acrshort{mpm} has been carried out. The \acrshort{npc} \MP{has been
+  shown to be a highly} efficient alternative for demanding \MP{fast dynamics} problems.
+\PNA{In the literature, several approaches of the \acrshort{npc} are proposed in order to compete on accuracy with expensive implicit time integration algorithms.} \PNA{The main achievement of the proposed time discretization has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.}
+Also, the procedure employed to design the \acrshort{npc} algorithm opens the
+door to revisit a huge variety of time integration schemes developed
+originally for \acrshort{fem}, which can be \MP{implemented within a
+  \acrshort{mpm} framework with the suitable} modifications. \MP{In
+addition to} \PNA{the implementation of enhanced time integration schemes, further
+research} \MP{can be done in the analysis of the good performance} \PNA{of the algorithm within non-linear solutions, such as the coupling between different phases or the non-linear constitutive behaviour of the materials: the employment of this scheme to strengthen the localization capabilities of \acrshort{mpm} for viscoplastic materials is on the scope of this research line.
+The comparison with traditional time schemes in the non-linear field will improve the formal understanding of the proposed methodology.}
+
+\PNA{On the other hand, the spatial discretization of the \acrshort{mpm} is enhanced thanks to the powerful skills of the \acrfull{lme} approximation scheme, which has been validated as a robust and versatile
+tool in the \acrshort{mpm} framework.} It also comes up as a promising
+alternative to other approximation techniques\PNA{, developed within the
+\acrshort{mpm}} \MP{framework, in order }to overcome grid crossing limitations and to avoid the
+constriction of the \acrshort{ugimp} of a regular mesh or a high
+density of particles per cell.
+\PNA{Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vect{x})$ through the finite strain
+tensor in order to align the shape functions in the principal strain
+direction to select the most suitable set of nodes adapted to the strain, as well as the possibility of adapting} the value of $\beta$ to solve the equations
+\acrshort{fem}-like of meshfree-like depending of how behaves the
+region. \PNA{Together with the implementation of non-linear behaviours, previously mentioned, challenging
+scenarios could be reproduced, being the main purpose of the research line the simultaneous simulation of both initialization and
+propagation stages of fast landslides.}
 
@@
 %%% End:
-\message{ !name(LME-MPM.tex) !offset(-1585) }
+\message{ !name(LME-MPM.tex) !offset(-1592) }

### 2020-05-28 LME-MPM.tex
Highlights

@@
 \author{
-Miguel Molinos$^a\footnote{Corresponding author: m.molinoss@outlook.es}$
+Miguel Molinos$^a$
 Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es},
 Manuel Pastor$^a$
-and Miguel Martín Stickle$^a$ 
+and Miguel Mart\'in Stickle$^a$ 
 }
@@
   integration scheme to filter spurious noises. \MP{To overcome it ,
-    we propose in this paper an explicit Predictor-Corrector time integration scheme}. Its \textcolor{red}{powerful}
-  performance mitigates the presence of spurious oscillations with
-  minimal dissipation in high frequency problems. Other source of
-  numerical noise in \acrshort{mpm} occurs when the material points
-  cross computational grid boundaries, being \MP{caused} by
+    we propose in this paper an explicit Predictor-Corrector time
+    integration scheme}. Its \PNA{powerful} performance mitigates the
+  presence of spurious oscillations with minimal dissipation in high
+  frequency problems. Other source of numerical noise in
+  \acrshort{mpm} occurs when the material points cross computational grid boundaries, being \MP{caused} by
   the lack of smoothness of the interpolation functions. This noise
@@
 \end{keyword}
+
+\begin{highlights}
+\item We have proposed a new and efficient time integration scheme for
+  the \acrshort{mpm}.
+\item The proposal of the \acrshort{lme} approximation technique
+  under the \acrshort{mpm} framework as a robust substitute of the
+  traditional shape function.
+\item Our approach have clear benefits for fast dynamics simulation
+  since reduces the presence of spurious oscillations without
+  damp the solution. 
+\end{highlights}
 

### 2020-05-28 LME-MPM.tex
Authors
Mistake in the Highlights

--- 2020-05-28 LME-MPM.tex
@@
 \author{
-Miguel Molinos$^a\footnote{Corresponding author: m.molinoss@outlook.es}$
+Miguel Molinos$^a$,
 Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es},
 Manuel Pastor$^a$
-and Miguel Martín Stickle$^a$ 
+and Miguel Mart\'in Stickle$^a$ 
 }
@@
   deformation regime. However, the simulation of shock waves
-  propagation and \MP{in the large deformation regime} is still challenging
+  propagation in the large deformation regime is still challenging
   under this approach due the incapability of the standard \acrshort{mpm} time
-  integration scheme to filter spurious noises. \MP{To overcome it ,
-    we propose in this paper an explicit Predictor-Corrector time integration scheme}. Its \textcolor{red}{powerful}
-  performance mitigates the presence of spurious oscillations with
-  minimal dissipation in high frequency problems. Other source of
-  numerical noise in \acrshort{mpm} occurs when the material points
-  cross computational grid boundaries, being \MP{caused} by
+  integration scheme to filter spurious noises. To overcome it, we propose in this paper an explicit Predictor-Corrector time
+    integration scheme. Its powerful performance mitigates the
+  presence of spurious oscillations with minimal dissipation in high
+  frequency problems. Other source of numerical noise in
+  \acrshort{mpm} occurs when the material points cross computational grid boundaries, being caused by
   the lack of smoothness of the interpolation functions. This noise
@@
   solutions as well as aborted simulations in the worst cases. To
-  overcome it, \MP{we propose in this work} the \acrfull{lme} approximation
+  surmount it, we propose in this work the \acrfull{lme} approximation
   schemes as a robust substitute of the traditional shape function in
@@
   degenerate cases resulting from the lack or uniqueness of the
-  triangulation. Furthermore, by modifying a regularization parameter
+  triangulation. Furthermore, by modifying a regularization parameter,
   they are able to behave finite element like or as a meshfree
@@
   with a single shape function family. Finally this paper demonstrates
-  the performance of both improvements thorough numerical examples.    
+  the performance of both improvements through numerical examples.    
 \end{abstract}
@@
 \end{keyword}
+
+\section*{-}
+\centering
+\Large
+\textbf{On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme}\\
+\setlength{\parskip}{1cm plus 5mm minus 4mm}
+Miguel Molinos, Pedro Navas, Manuel Pastor and Miguel Mart\'in-Stickle.
+
+\setlength{\parskip}{1cm plus 5mm minus 4mm}
+%\hline
+\setlength{\parskip}{1cm plus 5mm minus 4mm}
+\large
+\textbf{Highlights}
+\normalsize
+\begin{itemize}
+\item We have proposed a new and efficient time integration scheme for the \acrshort{mpm} in order to dissipate spurious stress oscillations without damping the solution.
+\item The proposal of the \acrshort{lme} approximation technique
+  under the \acrshort{mpm} framework is a robust substitute of the
+  traditional shape functions.
+\item Our approach have clear benefits on large strain fast dynamic simulations, where the grid-crossing pathology appears. 
+\end{itemize}
+
+%\begin{highlights}
+%\end{highlights}
 
@@
 has increased due to its ability to deal with large strain regime
-without suffer mesh distortion inaccuracies.\PNA{One of the main
-  fields where this method is strong} \MP{in solid dynamics \PNA{since the original time integration scheme proposed was the \acrfull{fe}~\cite{Sulsky1994}, carried out in a explicit manner.
-However, in this type or problems, the main instabilities of the original \acrshort{mpm} are even marked.}
-
-\PNA{On the one hand, the main source of instability occurs} when
+without suffering mesh distortion inaccuracies. One of the main
+  fields where this method is strong is the solid dynamics since the original time integration scheme proposed was the \acrfull{fe}~\cite{Sulsky1994}, carried out in an explicit manner.
+However, in this type or problems, the main instabilities of the original \acrshort{mpm} are even marked.
+
+On the one hand, the main source of instability occurs when
 material points cross cell boundaries. This provoked the development
@@
 or gaps when the material point mesh becomes irregular, which can
-introduce severe inaccuracies as noticed \MP{by} Steffen {\it et al.}
+introduce severe inaccuracies as noticed by Steffen {\it et al.}
 (2008)\cite{Steffen2008}. This is similar to the difficulty
@@
 (2018)~\cite{E_Wobbes_2018}. Unfortunately, when particles are spread
-in \MP{some particular special patterns}, the quality of the \acrshort{ctls} approximation \MP{decrease} locally.
-
-This document adopts the \acrfull{lme}, or Local \textit{Max-Ent} approximates, as a robust substitute\PNA{of the aforementioned} shape functions in \acrshort{mpm}. First introduced by Arroyo \& Ortiz
+in some particular special patterns, the quality of the \acrshort{ctls} approximation decreases locally.
+
+This document adopts the \acrfull{lme}, or Local \textit{Max-Ent} approximates, as a robust substitute of the aforementioned shape functions in \acrshort{mpm}. First introduced by Arroyo \& Ortiz
 (2006)~\cite{Arroyo2006}, it belongs to the class of convex 
@@
 recently, under \acrshort{mpm} framework, the work made by Wobbes {\it et
-  al.}(2020)~\cite{Wobbes2020}.\PNA{The proposed research delves into the benefits of
-the regularization parameter, \gls{LME-beta}, and the analogy of the different obtained shape functions derive by the tuning of this parameter and the traditional \acrshort{mpm} ones.}
+  al.}(2020)~\cite{Wobbes2020}. The proposed research delves into the benefits of
+the regularization parameter, \gls{LME-beta}, and the analogy of the different obtained shape functions derive by the tuning of this parameter and the traditional \acrshort{mpm} ones.
 
@@
 schemes which reduce the presence of high frequency noises by
-filtering them or increasing\PNA{somehow} the accuracy.\MMP{One of the first attempts was
+filtering them or increasing somehow the accuracy. One of the first attempts was
 the proposal of an implicit time integration scheme by Guilkey \&
 Weiss \cite{Guilkey_2003}. More recently Wang {\it et al.}
-\cite{Wang_2016}} \MP{mitigated} \MMP{these spurious noises by adding a non-viscous
+\cite{Wang_2016} mitigated these spurious noises by adding a non-viscous
 damping to the linear momentum balance equation, and later Charlton
@@
 simulations such as in consolidation process. In a recent publication,
-Kularathna \& Soga \cite{Soga_2017} study an implicit treatment of the pressure in MPM algorithm to simulate material incompressibility
+Kularathna \& Soga \cite{Soga_2017} studied an implicit treatment of the pressure in MPM algorithm to simulate material incompressibility
 avoiding artificial pressure oscillations by applying
@@
 promising results but at the expense of increasing the computational
-effort.} In this paper a less time consuming and high efficient explicit predictor-corrector integration method \MP{is}
+effort. In this paper a less time consuming and high efficient explicit predictor-corrector integration method is
 proposed. It consists of an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
@@
 
-The aim of this document is to mitigate the spurious oscillations due
+The aim of this document is to mitigate the spurious oscillations due to
 inaccuracies in both space and time discretization by the employment of a
 suitable combination of the \acrshort{lme} family shape functions, and the proposal of an explicit predictor-corrector scheme. The advantages of
-this approach will be illustrated through several challenging test cases\PNA{on the elastic regime}: the
-propagation of shock waves in a elastic bar and the response of a block of soil gradually loaded with gravitational forces.
+this approach will be illustrated through several demanding test cases on the elastic regime: the
+propagation of shock waves in an elastic bar and the response of a block of soil gradually loaded with gravitational forces.
 
@@
 explicit \acrshort{mpm} algorithm~\cite{Sulsky1994}. Without loosing
-generality, the method \MP{consists of} three main steps: (i) a
-variational recovery process, where particle data is projected \MP{onto} the
+generality, the method consists of three main steps: (i) a
+variational recovery process, where particle data is projected onto the
 grid nodes, (ii) an Eulerian step, where balance of momentum equation
@@
 compute the equilibrium equation. In what follows, we will adopt the
-following convention. Three kind of subscript or superscript are used
+following convention. Three kind of subscripts or superscripts are used
 within paper. The subscript $\Box_p$ is used to define a particle
@@
 variables. And finally, the superscript $\Box^{\psi}$ involves a
-virtual magnitude. For the operators, the convention is : $\dot{\Box}$ and
+virtual magnitude. For the operators, the convention is: $\dot{\Box}$ and
 $\ddot{\Box}$ for the first and second time derivative, $\qued \otimes
@@
 denotes the gradient and its symmetric part. Einstein subscripts
-convention is adopted therefore repeated index means addition.\PNA{Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are describe in subsection \ref{sec:derivation-mpm},\ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.}
+convention is adopted therefore repeated index means addition.
+Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are describe in subsection \ref{sec:derivation-mpm},\ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.
 
@@
 
-In \acrshort{mpm} the continuum mechanics approach is considered. So on, \MP{we will consider a region \gls{domain} }occupied by an elastic body like
+In \acrshort{mpm} the continuum mechanics approach is considered. So on, we will consider a region \gls{domain} occupied by an elastic body like
 the sketched in the figure~\ref{fig:Continuum-solid}, and \gls{contour} the boundaries of the domain defined by $\partial \varOmega
@@
 field \gls{u} through the following set of governing equations and
-restrictions that must be satisfied.\MP{First (i) we will relate
-  global to local state by the \textit{compatibility equation}, where the the strain field \gls{strain} is extracted from \gls{u} is defined as:}
+restrictions that must be satisfied. First (i) we will relate
+  global to local state by the \textit{compatibility equation}, where the the strain field \gls{strain} is extracted from \gls{u} is defined as:
 \begin{equation}
@@
 together with essential boundary conditions of Dirichlet type
-\gls{dirichlet-boundary}.\MP{We will further assume that strains are
-infinitesimal}, therefore second order terms
-in the spatial derivatives can be neglected.\MP{From here}, \PNAthe
+\gls{dirichlet-boundary}. We will further assume that strains are
+infinitesimal, therefore second order terms
+in the spatial derivatives can be neglected. From here, the
 stress field \gls{stress} will be considered the corresponding
-conjugate variable for the strain field, being the one} which
-satisfies (ii) the \textit{conservation of \MP{lineal} momentum equation}:
+conjugate variable for the strain field, being the one which
+satisfies (ii) the \textit{conservation of lineal momentum equation}:
 \begin{equation}
@@
 together with the natural boundary conditions of the Neumann type \gls{neumann-boundary}.  An aditional component will be (iii) the constitutive equation as a linear
-application \MP{from $\mathbb{R}^n$ to $\mathbb{R}^n$, which relate stress and strain increments as,}
+application from $\mathbb{R}^n$ to $\mathbb{R}^n$, which relate stress and strain increments as,
 \begin{equation}
@@
 \end{equation}
-\PNA{In this research, plane strain Linear Elasticity has been
+In this research, plane strain Linear Elasticity has been
   considered. Thus the constitutive tensor, \tens{D}, is the well
-  known linear elastic one.} The final \MP{equation of the set} is (iv) the mass
+  known linear elastic one. The final equation of the set is (iv) the mass
 conservation, which can be obtained by setting to zero the total derivative of the density field,
@@
 \end{equation}
-\MP{in which} the Cauchy sequences are convergent in \gls{domain} as well:
+in which the Cauchy sequences are convergent in \gls{domain} as well:
 \begin{equation}
@@
 the boundary-value problem of elasticity is the function $\vect{u} \in
-\mathcal{H}^1_0$ such that, for \MP{any} $\vect{u}^{\psi} \in
+\mathcal{H}^1_0$ such that, for any $\vect{u}^{\psi} \in
 \mathcal{H}^1_0$,
@@
 
-\MP{Next, we will discretize the set of equations of the mathematical model using a double discretization procedure.} First, the continuum \gls{domain} is discretized with a finite sum of material points (also denominated particles the manuscript).
+Next, we will discretize the set of equations of the mathematical model using a double discretization procedure.
+First, the continuum \gls{domain} is discretized with a finite sum of material points (also denominated particles the manuscript).
 Each material point
@@
 $\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$ respectively are assigned to each material point, which also owns the
-virtual displacement field $\vect{u}^{\psi}_{p}$. \MP{Regarding numerical integration, the material derivatives are
+virtual displacement field $\vect{u}^{\psi}_{p}$. Regarding numerical integration, the material derivatives are
   evaluated using the Riemann integral definition \cite{Riemann_1854}
   applied to a finite set of points which associated volumes are
-  interpreted as quadrature weights.} Consequently,
+  interpreted as quadrature weights. Consequently,
 individual terms in \eqref{eq:BalanceMomentum_wf} are solved as follows. 
@@
 \end{itemize}
-where $h$ is the thickness of the continuum in a 2D case. \MP{Next, we
-  will proceed with the second step of the discretization. It is based on using a background grid } with coordinates $\vec{x}_I\
+where $h$ is the thickness of the continuum in a 2D case. Next, we
+  will proceed with the second step of the discretization. It is based on using a background grid with coordinates $\vec{x}_I\
 , I = 1,2\ldots ,N_n$, is generated, being $N_n$ the number of grid
-nodes.\PNA{Spatial derivatives, such as gradients and
-divergences, are computed through the support of the background mesh.}
+nodes. Spatial derivatives, such as gradients and
+divergences, are computed through the support of the background mesh.
 
@@
 \end{equation}
-Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order\PNA{time} integration scheme is required. Therefore, time is
+Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order time integration scheme is required. Therefore, time is
 discretized into a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
@@
 \end{equation}
-\PNA{Traditionally, Eqs.
+Traditionally, Eqs.
 \eqref{eq:particle_balance_forces3} and ~\eqref{eq:Updated_Lagrangian},
-are solved with an explicit forward Euler algorithm. In the following subsection, this and the proposed schemes are described}.
+are solved with an explicit forward Euler algorithm. In the following subsection, this and the proposed schemes are described.
 
@@
 
-\PNA{As was stated previosuly, an explicit forward Euler algorithm has been utilized widely within the \acrshort{MPM} methodology. This scheme has been described in detail by many researchers
-\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and can be sketched by the scheme of the figure~\ref{fig:MPM_algorithm}.}
+As was stated previosuly, an explicit forward Euler algorithm has been utilized widely within the \acrshort{MPM} methodology. This scheme has been described in detail by many researchers
+\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and can be sketched by the scheme of the figure~\ref{fig:MPM_algorithm}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 $\vect{f}_I^{int,k}$ can be infinite for an infinitesimal nodal mass
-$\tens{m}$. This issue may lead to numerical \MP{problems} when nodal acceleration
+$\tens{m}$. This issue may lead to numerical problems when nodal acceleration
 is obtained in the evaluation of the Eqs. \eqref{eq:Sulsky-1994-UL-x} and \eqref{eq:Sulsky-1994-UL-v}. Hence, a
@@
 scheme is proposed. It is based on the Newmark central differences
-explicit scheme, which is also \MP{referred to as} a-form 
+explicit scheme, which is also referred to as a-form 
 $\gamma = 0.5$ and $\beta = 0$. This method is devoted to solve a system of equations of the type
@@
 \end{equation*}
-\PNA{The nodal \acrshort{mpm} stage allows to apply this method}
-\MP{within} \PNA{the \acrshort{mpm} framework in a similar manner that the one
-proposed by Tran~\it{et al.}~\cite{Tran2019e}.} \MP{By using the} \PNAthe predictor definition, it is possible to calculate nodal velocities and update particles position employing nodal values
-of velocity and acceleration.}
+The nodal \acrshort{mpm} stage allows to apply this method
+within the \acrshort{mpm} framework in a similar manner that the one
+proposed by Tran~\textit{et al.}~\cite{Tran2019e}. By using the predictor definition, it is possible to calculate nodal velocities and update particles position employing nodal values
+of velocity and acceleration.
 
@@
 equilibrium equation \eqref{eq:particle_balance_forces3}. Next, the
-\textit{corrector} stage is introduced. \MP{As} nodal
+\textit{corrector} stage is introduced. As nodal
 velocities were obtained earlier, this step is computed in the same way as
@@
 \end{equation}
-Finally updated particle \MP{accelerations, velocities and positions are updated as},
+Finally updated particle accelerations, velocities and positions are updated as,
 \begin{align}
@@
 are computed using the corrected velocities. Therefore here we share similarities
-with the \textit{leapfrog \MP{scheme}} where position is not updated at
+with the \textit{leapfrog scheme} where position is not updated at
 full time step, but the velocity is updated at half time steps. Notice
@@
     \eqref{eq:nodal_external_forces} in the time step $k+1$.
-    \MMP{In those nodes where $\Deriv{\vect{v}_I^{k}}{t} \big\rvert_{\Gamma_d} = 0$,
+    In those nodes where $\Deriv{\vect{v}_I^{k}}{t} \big\rvert_{\Gamma_d} = 0$,
       the acceleration is fixed to zero and nodal forces are stored as
-      reactions.}\\
+      reactions.\\
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
 made with the original \acrshort{mpm}, numerical noises appear when particles
-cross the cell boundaries.\PNA{Solving this issue is the main goal of the employment of the \acrshort{LME} shape functions}.
+cross the cell boundaries. Solving this issue is the main goal of the employment of the \acrshort{LME} shape functions.
 
@@
 recently tested under \acrshort{mpm} framework by Wobbes {\it et al.}
-(2020)\cite{Wobbes2020}. \MP{The simulations presented in \cite{Wobbes2020} of \acrshort{mpm}
+(2020)\cite{Wobbes2020}. The simulations presented in \cite{Wobbes2020} of \acrshort{mpm}
 within \acrshort{lme} show considerably more accurate stress
-approximations than traditional \acrshort{mpm} schemes.} \PNA{However, 
+approximations than traditional \acrshort{mpm} schemes. However, 
 how the regularization parameter $\beta$ affects to the accuracy and
-stability of the solution is not assessed deeply in that research, the tuning of this $\beta$ parameter allows to make the comparison of the accuracy against analogous traditional \acrshort{mpm} shape function.}
+stability of the solution is not assessed deeply in that research.
+The tuning of this $\beta$ parameter allows to make the comparison of the accuracy against analogous traditional \acrshort{mpm} shape function.
 
@@
 function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
-10$^{-6}$\PNA{in this research},  would ensure a reasonable range of
+10$^{-6}$ in this research,  would ensure a reasonable range of
 neighbours (see \cite{Arroyo2006} for details).
@@
 $d+1$ neighbouring nodes are chosen as the support, where $d$ is the
-number of dimensions in the problem. \MMP{Ullah {\it et al.}
-  \cite{Augarde_2013} take advantage of the \acrshort{lme}
+number of dimensions in the problem. Ullah {\it et al.}
+  \cite{Augarde_2013} took advantage of the \acrshort{lme}
   \short{fem}-compatibility to couple the
-  \acrfull{efgm} and \short{fem} for linear elasticity and for problems with both material and geometrical nonlinearities.}Furthermore, with a conveniently
+     \acrfull{efgm} and \short{fem} for linear elasticity and for problems with both material and geometrical non-linearities. Furthermore, with a conveniently
 adopted \textit{regularization} parameter it is possible to get a 
-\acrshort{gimp}-like shape function.\MMP{Finally \short{sph}-like
+\acrshort{gimp}-like shape function. Finally \short{sph}-like
 behaviour can be obtained for lower values of $\gamma$ since the
-support of the shape function is drastically increase, and therefore
+support of the shape function is drastically increased, and therefore
 \textit{smoother} solutions are obtained. See \cite{Navas2016} for an
-application of this capability, where publication oscillations due to
+application of this capability, where oscillations due to
 excess of pore water pressure in consolidation problems are smoothed
-out by using this technique. The employment of smoothing algorithm is
+out by using this technique. The employment of smoothing algorithms is
 also straightforward in the fluid-solid interaction problems
-\cite{Arduino_2018}.A proof of this statements is observed in
-figure~\ref{fig:LME_MPM}, where the \acrshort{lme} adaptability is illustrate.}\\
+\cite{Arduino_2018}. A proof of this statements is observed in
+figure~\ref{fig:LME_MPM}, where the \acrshort{lme} adaptability is illustrated.\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \acrshort{lme} scheme, which uses an anisotropic support to deal with 
-tensile instability.\PNA{This is another benefit of the proposed methodology, that, although is out of the scope of the
-present document, will be incorporated in future research.}
+tensile instability. This is another benefit of the proposed methodology, that, although is out of the scope of the
+present document, will be incorporated in future research.
 
@@
 
-This benchmark was proposed\PNA{by Dyka~\cite{Dyka1995} since allows so study easily the capability}
+This benchmark was proposed by Dyka~\cite{Dyka1995} since allows to study easily the capability
 of the proposed time integration algorithm to avoid velocity
@@
 boundary conditions are: displacements are constrained ($\vect{v}
-\rvert_{x=L} = 0$) in the right border, \MP{being free on all other boundaries.} An initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
-left quarter of the bar. Finally, the elastic parameters \MP{chosen} for this test are:
+\rvert_{x=L} = 0$) in the right border, being free on all other boundaries. An initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
+left quarter of the bar. Finally, the elastic parameters chosen for this test are:
 \begin{itemize} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\MP{In the proposed exmple, the simulation extends from time zero up to 0.00001 s.
+In the proposed example, the simulation extends from time zero up to 0.00001 s.
 This time interval allows the elastic wave to travel a distance of 2.6
-lengths of the bar}. For the spatial
+lengths of the bar. For the spatial
 discretization, a set of seven nodal mesh sizes (0.1, 0.3325, 0.5,
 1.0, 3.3325, 6.665, 10.0 millimeters) are considered. For each element a number of
-four particles was selected. In the initial layout, particles are
-\MP{located} the exact quadrature points of a linear quadrilateral, with
+four particles was selected. In the initial layout, particles are located the exact quadrature points of a linear quadrilateral, with
 the exception of the \acrshort{ugimp} simulation, where gaps or overlap between
@@
 numerical solutions evaluated in the final time step in the position
-of each particle.\PNA{In Fig.
+of each particle.
+In Fig.
 \ref{fig:Dyka-error-evol} the evolution of the RMS is obtained for both time integration schemes.
 The right figure, with the \acrshort{NPC} results, shows lower values of the estimated error, denoting the higher performance of this methodology.
-About the spatial discretization, the \acrshort{LME} schemes show an error comparable to the obtained with the \acrshort{uGIMP}, being even lower close to the grid-crossing region.}
+About the spatial discretization, the \acrshort{LME} schemes show an error comparable to the obtained with the \acrshort{uGIMP}, being even lower close to the grid-crossing region.
 
@@
 
-A first \MP{comparison} between the \MP{obtained in} both time integration
+A first comparison between the obtained one in both time integration
 schemes is plotted in figure \ref{fig:Dyka-NPC-FE}. It demonstrates the
@@
   }
-  \caption{\MP{comparison of \acrshort{npc} and \acrshort{fe}
-      performances}: In the picture the velocity evolution at the point in the bar left side
+  \caption{Comparison of \acrshort{npc} and \acrshort{fe}
+      performances: In the picture the velocity evolution at the point in the bar left side
     is plotted.}
@@
 
-Figure \eqref{fig:Dyka-LME-gamma} shows the \MP{sensitivity} of the \acrshort{lme}
+Figure \eqref{fig:Dyka-LME-gamma} shows the sensitivity of the \acrshort{lme}
 approximation scheme to variations in the parameter
@@
 solutions. This capability could be useful in simulations where
-extremely \MP{noisy} oscillations could damage the solutions like memory
+extremely noisy oscillations could damage the solutions like memory
 materials. On the other hand larger values of the parameter $\beta$
-make the solution \MP{to tend} to the linear \acrshort{fem} solution as the athermal limit is reached \cite{Arroyo2006}. Intermediate values of the
-regularization parameters give us a compromise \MP{between both scenarios described here}. An additional observation, concerning to the
-solution sensibility depending on the regularization parameters, \PNA{is the behaviour of the solution depending on the decreasing of mesh
-size}. For larger mesh sizes, where the relative particle displacement
+make the solution to tend to the linear \acrshort{fem} solution as the athermal limit is reached \cite{Arroyo2006}. Intermediate values of the
+regularization parameters give us a compromise between both scenarios described here. An additional observation, concerning to the
+solution sensibility depending on the regularization parameters, is the behaviour of the solution depending on the decreasing of mesh
+size. For larger mesh sizes, where the relative particle displacement
 is negligible in comparison with the cell size, the global behaviour
-is \acrshort{fem}-like; therefore, larger values of $\gamma$ \PNA{may offer better results}. On the other hand, when mesh size is small enough to produce
+is \acrshort{fem}-like; therefore, larger values of $\gamma$ may offer better results. On the other hand, when mesh size is small enough to produce
 grid-crossing meshfree behaviour is required to ensure the
-convergence of the solution and tiny values of $\gamma$\PNA{may lead to better
-performances}. Convergence plot in figure \eqref{fig:Dyka-error-evol}
+convergence of the solution and tiny values of $\gamma$ may lead to better
+performances. Convergence plot in figure \eqref{fig:Dyka-error-evol}
 shows how the slope, for the larger values of $\gamma$, decreases
 monotonically with the value of the mesh size, in contrast with larger
-values of $\gamma$,\PNA{where the performance is punished with significant
-movement of the particles as far as the mesh size is reduced.} 
+values of $\gamma$, where the performance is punished with significant
+movement of the particles as far as the mesh size is reduced.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   }
-  \caption{\MP{Sensitivity} of LME approximants performance to changes in the
+  \caption{Sensitivity  of LME approximants performance to changes in the
     dimensionless regularization parameter $\gamma = \beta/h^2$. To
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\PNA{The performance of the
+The performance of the
 \acrshort{ugimp}~\cite{Bardenhagen2004} shape function \textit{versus} the \acrshort{lme} approximation scheme with
 a dimensionless regularization parameter $\gamma$ of 4.0 is compared in Figure \ref{fig:Dyka-uGIMP-LME}. Although remarkable differences are not observed, more
-robust behaviour is exhibited by the \acrshort{lme} approximants than the \acrshort{ugimp} shape functions.} Regarding this, notice
+robust behaviour is exhibited by the \acrshort{lme} approximants than the \acrshort{ugimp} shape functions. Regarding this, notice
 the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5
-millimeters.\PNA{The reason is due to an unstable
-increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yield unacceptable results}. A feasible
+millimeters. The reason is due to an unstable
+increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yield unacceptable results. A feasible
 explanation for this phenomena could be the presence of numerical
@@
 should be done in this direction for getting a better comprehension of
-this phenomenon.\PNA{Conversely, this shortcoming is not suffered by \acrshort{lme}, independently of regular or with irregular nodal layout.}
+this phenomenon. Conversely, this shortcoming is not suffered by \acrshort{lme}, independently of regular or with irregular nodal layout.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The following test was proposed to \PNA{validate} the ability of the proposed
+The following test was proposed to validate the ability of the proposed
 interpolation technique to deal with grid crossing instabilities. It
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-This test was \PNA{previously proposed by Andersen} (2009)\cite{thesis_Andersen_2009}. The
+This test was previously proposed by Andersen (2009)\cite{thesis_Andersen_2009}. The
 elastic parameters considered for this test are: 
@@
 cell-crossing and consequently fail. The \acrshort{ugimp} simulation
-is more stable than the one performed by the Q4, \PNA{although} is still
+is more stable than the one performed by the Q4, although is still
 unstable and could trigger severe oscillations in simulation with
@@
 \label{sec:conclusions}
-\MP{We have proposed in this paper an improved methodology which improves \acrfull{mpm} behaviour in fast dynamics problems.
-Different time and space discretization techniques have been presented, their performance being compared agains other approaches in two benchmark problems.}
-\MP{First,} a novel time integration scheme for
-\acrshort{mpm} has been carried out. The \acrshort{npc} \MP{has been
-  shown to be a highly} efficient alternative for demanding \MP{fast dynamics} problems.
-\PNA{In the literature, several approaches of the \acrshort{npc} are proposed in order to compete on accuracy with expensive implicit time integration algorithms.} \PNA{The main achievement of the proposed time discretization has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.}
+We have proposed in this paper an enhanced methodology which improves \acrfull{mpm} behaviour in fast dynamics problems.
+Different time and space discretization techniques have been presented and their performance being compared agains other approaches in two benchmark problems.
+First, a novel time integration scheme for
+\acrshort{mpm} has been carried out. The \acrshort{npc} has been
+  shown to be a highly efficient alternative for demanding fast dynamics problems.
+In the literature, several approaches of the \acrshort{npc} are proposed in order to compete on accuracy with expensive implicit time integration algorithms.
+The main achievement of the proposed time discretization has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.
 Also, the procedure employed to design the \acrshort{npc} algorithm opens the
 door to revisit a huge variety of time integration schemes developed
-originally for \acrshort{fem}, which can be \MP{implemented within a
-  \acrshort{mpm} framework with the suitable} modifications. \MP{In
-addition to} \PNA{the implementation of enhanced time integration schemes, further
-research} \MP{can be done in the analysis of the good performance} \PNA{of the algorithm within non-linear solutions, such as the coupling between different phases or the non-linear constitutive behaviour of the materials: the employment of this scheme to strengthen the localization capabilities of \acrshort{mpm} for viscoplastic materials is on the scope of this research line.
-The comparison with traditional time schemes in the non-linear field will improve the formal understanding of the proposed methodology.}
-
-\PNA{On the other hand, the spatial discretization of the \acrshort{mpm} is enhanced thanks to the powerful skills of the \acrfull{lme} approximation scheme, which has been validated as a robust and versatile
-tool in the \acrshort{mpm} framework.} It also comes up as a promising
-alternative to other approximation techniques\PNA{, developed within the
-\acrshort{mpm}} \MP{framework, in order }to overcome grid crossing limitations and to avoid the
+originally for \acrshort{fem}, which can be implemented within a
+  \acrshort{mpm} framework with the suitable modifications. In
+addition to the implementation of enhanced time integration schemes, further
+research can be done in the analysis of the good performance of the algorithm within non-linear solutions, such as the coupling between different phases or the non-linear constitutive behaviour of the materials: the employment of this scheme to strengthen the localization capabilities of \acrshort{mpm} for viscoplastic materials is on the scope of this research line.
+The comparison with traditional time schemes in the non-linear field will improve the formal understanding of the proposed methodology.
+
+On the other hand, the spatial discretization of the \acrshort{mpm} is enhanced thanks to the powerful skills of the \acrfull{lme} approximation scheme, which has been validated as a robust and versatile
+tool in the \acrshort{mpm} framework. It also comes up as a promising
+alternative to other approximation techniques, developed within the
+\acrshort{mpm} framework, in order to overcome grid crossing limitations and to avoid the
 constriction of the \acrshort{ugimp} of a regular mesh or a high
 density of particles per cell.
-\PNA{Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vect{x})$ through the finite strain
+Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vect{x})$ through the finite strain
 tensor in order to align the shape functions in the principal strain
-direction to select the most suitable set of nodes adapted to the strain, as well as the possibility of adapting} the value of $\beta$ to solve the equations
+direction to select the most suitable set of nodes adapted to the strain, as well as the possibility of adapting the value of $\beta$ to solve the equations
 \acrshort{fem}-like of meshfree-like depending of how behaves the
-region. \PNA{Together with the implementation of non-linear behaviours, previously mentioned, challenging
+region. Together with the implementation of non-linear behaviours, previously mentioned, challenging
 scenarios could be reproduced, being the main purpose of the research line the simultaneous simulation of both initialization and
-propagation stages of fast landslides.}
+propagation stages of fast landslides.
 

### 2020-08-25 Revisiones/Responses to the reviewers.tex
Hoja de respuestas revisores

\documentclass[12pt]{article}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
\usepackage{graphicx}
\usepackage{cite}
\usepackage{color}
\usepackage{bm}

% \geometry{landscape} % rotated page geometry

\title{Response to the reviewers of the manuscript ``On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme"}
\author{Miguel Molinos, Pedro Navas, Manuel Pastor, and Miguel Mart\'in-Stickle}
\date{September 1, 2020}

%\date{} % delete this line to display the current date

%%% BEGIN DOCUMENT
\begin{document}

\maketitle
%\tableofcontents

We  are grateful to the reviewers for taking their time  to review our work. Their comments have helped us to improve the paper. Changes to the original manuscript are given in  color (\textcolor{red}{red} for corrections, \textcolor{blue}{blue} for modified texts)  in the revised version.  A detailed response to both reviewers is given below.

\section*{Response to Reviewer \#1}
{\it
The authors have presented a promissing approach for MPM to surpass the shock wave propagation in the traditional MPM. The paper was very well written and the results suggested that the proposed approach works.
}
\\
\\
The reviewer's positive commentaries are greatly appreciated.
\\
\begin{enumerate}
\item \textit{However, most of the applications presented in this manuscript are relatively simple and does not really demonstrate the capability of the proposed approach. I suggest the authors to extend their manuscript to predict more challenging problems and compare their results to the original MPM solutions.}\\

Authors are completely agree with the proposal. And in analogy with the work of \cite{HAMMERQUIST2017724}, where fast dynamics were also studied. The Sulsky classical example of two colliding disks has been discussed in the new version of the manuscript.

\end{enumerate}

\hspace{5mm}

\section*{Response to Reviewer \#2}

\textit {This is, on the face of it, an interesting piece of work but in its present form I don't think this is ready for CMAME. The paper is too long, rambling and has many grammatical and spelling errors. }\\

Authors really appreciate that the reviewer consider the present research as an interest piece of work. In order to improve the readability of the revised paper, a proofreading is made.\\

\textit{Technical issues for the authors follow:}
 \begin{enumerate}
\item \textit{Cell-crossing is a well known issue with the MPM but in the review no mention is made of CPDI approaches.}\\

A citation of the work of \cite{Sadeghirad_2011} with the CPDI has been added to the state of art.

\item \textit{The development is very confusing and would make more sense were it to be tied to 
the way that GIMP methods are usually stated, i.e. that the standard FE shape functions are replaced by weighting functions comprised of the conjugation of a standard shape function and a particle "characteristic" function. Line 155 demonstrates this, i.e. the use of $N_{Ip}$ before explanation.}\\

The development of the MPM approach has been revised considering the proposal of the reviewer.

\item \textit{There is little discussion on some of the pitfalls of using max-ent, e.g. the need for a convex domain, the issue of determining Lagrange Multiplier solutions for points close to boundaries, i.e. the solutions process here at Eqns 37 and 38.}\\

Further discussion has been added.

\item \textit{Does the use of max-ent solve the problem of imposing Dirichlet boundary conditions in the MPM?}\\

No it does not. Local \textit{max-ent} approximation technique only provides to the MPM an efficient tool to transfer information from particles to nodes and vice versa. The difficulties of imposing Dirichlet boundary conditions (DBC) in the MPM are a direct consequence of discretising the continuum with material points nor with nodes where DBC are imposed. See for instance the work of \cite{Cortis_et_al_2017_IJNME}.

\item \textit{I am sceptical of the novelty of the proposed explicit scheme as there is no mention of the recent XPIC(m) approach of Hammerquist and Nairn or similar approaches used in the Computational Graphics community, e.g. Stomakhin et al. (2013) or the more recent Polypic.}\\

These publications will be added to the state of art of the manuscript. In the humble opinion of the authors, the XPIC approach consists in the stabilisation of the solution through a novel transference procedure. Meanwhile, the algorithm introduced in this research proposes the stabilisation within the adaptation of a FEM time integration scheme for the MPM framework. Hence, both techniques can be employed simultaneously.

\end{enumerate}

 \textit{The numerical examples are not impressive when the message of the paper is that this is good for fast dynamics problems. Compare to papers such as Ma et al. (2009) IJ Impact Engineering}\\

We agree with the reviewer that some of the numerical example does not enough highlights the capabilities of the MPM Newmark Predictor-Corrector scheme. Although the results presented in \cite{MA2009272} are impressive, the proposed examples are out of the scope of the present research. Therefore, in analogy with the work of \cite{HAMMERQUIST2017724}, previously cited by the reviewer, the Sulsky classical example of two colliding disks has been discussed.

\bibliographystyle{unsrt}
\begin{thebibliography}{10}

\bibitem{Cortis_et_al_2017_IJNME}
Cortis, Michael and Augarde, Charles and Coombs, William and Robinson, Scott and Brown, Michael and Brennan, Andrew.
\newblock {Imposition of essential boundary conditions in the material point method}.
\newblock {International Journal for Numerical Methods in Engineering}, 113, 2017.

\bibitem{Sadeghirad_2011}
Sadeghirad, A. and Brannon, R. M. and Burghardt, J.
\newblock {A convected particle domain interpolation technique to extend applicability of the material point method for problems involving massive deformations}.
\newblock {International Journal for Numerical Methods in Engineering}, 86(12) : 1435-1456, 2011.

\bibitem{HAMMERQUIST2017724}
Chad C. Hammerquist and John A. Nairn.
\newblock {A new method for material point method particle updates that reduces noise and enhances stability}.
\newblock {\em Computer Methods in Applied Mechanics and Engineering},  318:724--738, 2017.

\bibitem{MA2009272}
S. Ma and X. Zhang and X.M. Qiu.
\newblock{Comparison study of MPM and SPH in modeling hypervelocity impact problems}.
\newblock{International Journal of Impact Engineering}, 36(2):272--282, 2009.

\end{thebibliography}

\end{document}

%Del revisor 2:
%1- Meter paja de eso y fuera
%2- Yo haria referencia al paper de Wobbes, como lo nombren ellos, y decir que haces referencia a un paper contrastado....
%3- Hablar de eso, que hay pequeña discusion, pues se discute mas... 
%4- No, no lo soluciona, pero en OTM lo hace. Habría que conseguir una conjunción de lo que hace OTM con lo que hacen otros metodos en MPM para imponer boundary conditions....
%5- Leerse que hacen esos pollos, si esta bien y crees que puedes mter algun ejemplo, se puede intentar y asi tb se contenta al revisor 1

### 2020-08-26 LME-MPM.tex
Fuera comentarios
Hoja de respuestas revisores
Cambios en la derivación del modelo MPM

@@
 \usepackage{textcomp}
-\usepackage{subfig}
 \usepackage{color}
@@
   \IfStrEqCase{#1}{
-    {2}{\ensuremath{\int_{\varGamma_d}{#2}\ d\varGamma}}
-    {3}{\ensuremath{\int_{\varOmega}{#2}\ d\varOmega}}
+    {2}{\ensuremath{\int_{\Gamma_d}{#2}\ d\Gamma}}
+    {3}{\ensuremath{\int_{\Omega}{#2}\ d\Omega}}
   }
@@
 {
-  name=$\varOmega$,
+  name=$\Omega$,
   description={Continuum domain}
@@
 {
-  name=$\partial\varOmega$,
-  description={Boundary of the continuum domain $\varOmega$. Also
+  name=$\partial\Omega$,
+  description={Boundary of the continuum domain $\Omega$. Also
     defined as $\Gamma$}
@@
   name=$ \Gamma_d$,
-  description={Essential or Dirichlet boundary conditions over $\partial\varOmega$}
+  description={Essential or Dirichlet boundary conditions over $\partial\Omega$}
 }
@@
   name=$ \Gamma_n$,
-  description={Natural or Neumann boundary conditions over $\partial\varOmega$}
+  description={Natural or Neumann boundary conditions over $\partial\Omega$}
 }
@@
 {
-  name=$\vect{a}$,
+  name=$\vec{a}$,
   description={First order tensor which describes the acceleration field}
@@
 {
-  name=$\vect{v}$,
+  name=$\vec{v}$,
   description={First order tensor which describes the velocity field}
@@
 {
-  name=$\vect{u}$,
+  name=$\vec{u}$,
   description={First order tensor which describes the displacement field}
@@
 {
-  name=$\vect{x}$,
+  name=$\vec{x}$,
   description={First order tensor which describes the global coordinates field}
@@
 {
-  name=$\vect{\xi}$,
+  name=$\vec{\xi}$,
   description={First order tensor which describes the local coordinates field}
@@
 \newacronym{ddmp}{DDMP}{Dual Domain Material Point}
+\newacronym{cpdi}{CPDI}{Convected Particle Domain Interpolation}
 \newacronym{ctls}{CTLS}{Conservative Taylor Least Squares}
@@
 \newacronym{fe}{FE}{Forward Euler}
+\newacronym{dbc}{DBC}{Dirichlet boundary conditions}
+\newacronym{nbc}{NBC}{Neumann boundary conditions}
 
@@
 
-\newcommand{\PNA}[1]{
+\newcommand{\CORRECTIONS}[1]{
   \textcolor{red}{{#1}}
@@
 
-\newcommand{\MMP}[1]{
+\newcommand{\MODIFIED}[1]{
   \textcolor{blue}{{#1}}
@@
 
-\newcommand{\MP}[1]{
-  \textcolor{green}{{#1}}
-}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\journalname{Computer Methods in Applied Mechanics and Engineering}
-
+\journal{Computer Methods in Applied Mechanics and Engineering}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 Manuel Pastor$^a$
-and Miguel Mart\'in Stickle$^a$ 
-}
+and Miguel Mart\'in Stickle$^a$}
 \address{
@@
 
-\section*{-}
+\section*{}
 \centering
@@
 computational cost.  Furthermore, as it is a voxel-based
-discretization technique, it is prone to suffer voxel domains overlap
+discretisation technique, it is prone to suffer voxel domains overlap
 or gaps when the material point mesh becomes irregular, which can
@@
 decreases. Therefore \acrshort{ddmp} a large
-number of particles is needed for convergence~\cite{DHAKAL2016301}, what makes the method
-very expensive. In recent years the employment of spline-lines as shape functions has gain popularity with the introduction of the B-Spline 
+number of particles is needed for convergence~\cite{DHAKAL2016301}, what makes the method very expensive.
+\MODIFIED{To avoid the tensile instabilities quite commons in extensions, Sadeghirad {\it et al.} (2011) \cite{Sadeghirad_et_al_IJNME_2011} developed the \acrshort{cpdi} \cite{Sadeghirad_et_al_IJNME_2011}}.
+In recent years the employment of spline-lines as shape functions has gain popularity with the introduction of the B-Spline
 \acrshort{mpm} proposed by Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
@@
 techniques~\cite{Tran2019e}. These numerical inaccuracies, also known
-as wiggles, arise due to inaccuracies in the time discretization technique.
+as wiggles, arise due to inaccuracies in the time discretisation technique.
 A simple approach to face those spurious noises lies on the addition of nonphysical damping sources to the equilibrium equations. This
@@
 effort. In this paper a less time consuming and high efficient explicit predictor-corrector integration method is
-proposed. It consists of an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
+proposed. It consists of an accommodation of the traditional \acrfull{npc} scheme, widely employed in Finite Element methods. This method
 has been chosen among other suitable alternatives as those proposed
@@
 The aim of this document is to mitigate the spurious oscillations due to
-inaccuracies in both space and time discretization by the employment of a
+inaccuracies in both space and time discretisation by the employment of a
 suitable combination of the \acrshort{lme} family shape functions, and the proposal of an explicit predictor-corrector scheme. The advantages of
@@
 following convention. Three kind of subscripts or superscripts are used
-within paper. The subscript $\Box_p$ is used to define a particle
-variable. While the subscript $\Box_I$ is reserved in this notation for denoting nodal
-variables. And finally, the superscript $\Box^{\psi}$ involves a
-virtual magnitude. For the operators, the convention is: $\dot{\Box}$ and
-$\ddot{\Box}$ for the first and second time derivative, $\qued \otimes
-\qued$ means the dyadic operator, $\Box \cdot \Box$ and $\Box \colon \Box$ means the
-first and second contraction of a tensor, $\Div{\Box}$ denotes the
-divergence operator, and finally $\Grad{\Box}$ and $\GradS{\Box}$
+within paper. The subscript $\square_p$ is used to define a particle
+variable. While the subscript $\square_I$ is reserved in this notation for denoting nodal
+variables. And finally, the superscript $\square^{\psi}$ involves a
+virtual magnitude. For the operators, the convention is: $\dot{\square}$ and
+$\ddot{\square}$ for the first and second time derivative, $\square \otimes
+\square$ means the dyadic operator, $\square \cdot \square$ and $\square \colon \square$ means the
+first and second contraction of a tensor, $\Div{\square}$ denotes the
+divergence operator, and finally $\Grad{\square}$ and $\GradS{\square}$
 denotes the gradient and its symmetric part. Einstein subscripts
@@
 In \acrshort{mpm} the continuum mechanics approach is considered. So on, we will consider a region \gls{domain} occupied by an elastic body like
-the sketched in the figure~\ref{fig:Continuum-solid}, and \gls{contour} the boundaries of the domain defined by $\partial \varOmega
-= \Gamma_d \bigcup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n = \emptyset$.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
+the sketched in the figure~\ref{fig:Continuum-solid}, and \gls{contour} the boundaries of the domain defined by $\partial \Omega
+= \Gamma_d \cup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n = \emptyset$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+%\sidecaption
   \centering
@@
   \caption{Description of the boundary-value-problem in a
-    continuum. Red lines represents the closure $\partial \varOmega$
-    of the domain $\varOmega$ represented in gray.}
+    continuum. Red lines represents the closure $\partial \Omega$
+    of the domain $\Omega$ represented in gray.}
   \label{fig:Continuum-solid}
@@
   \label{eq:Compatibility-equation}
-  \tens{\varepsilon} = \GradS{\vect{u}},
-\end{equation}
-together with essential boundary conditions of Dirichlet type
-\gls{dirichlet-boundary}. We will further assume that strains are
+  \tens{\varepsilon} = \GradS{\vec{u}},
+\end{equation}
+together with essential or \acrfull{dbc} \gls{dirichlet-boundary}. We will further assume that 
+strains are 
 infinitesimal, therefore second order terms
@@
   \label{eq:Balance-momentum}
-\rho \frac{D\vect{v}}{Dt} = \Div{\tens{\sigma}} + \rho \vect{b}
-\end{equation}
-together with the natural boundary conditions of the Neumann type \gls{neumann-boundary}.  An aditional component will be (iii) the constitutive equation as a linear
+\rho \frac{D\vec{v}}{Dt} = \Div{\tens{\sigma}} + \rho \vec{b}
+\end{equation}
+together with the natural of \acrfull{nbc} \gls{neumann-boundary}.  An aditional component will be (iii) the constitutive equation as a linear
 application from $\mathbb{R}^n$ to $\mathbb{R}^n$, which relate stress and strain increments as,
@@
   \label{eq:Rho-material-derivative}
-  \frac{D \rho}{D t} = \dot{\rho} + \rho \Div{\vect{v}} = 0.
+  \frac{D \rho}{D t} = \dot{\rho} + \rho \Div{\vec{v}} = 0.
 \end{equation}
@@
   \label{eq:Hilbert-space}
-  \vect{u}^{\psi} \in \mathcal{H}^1_0(\Omega) = \{ \vect{u}^{\psi} \in
-  \mathcal{H}^1 \mid \vect{u}^{\psi} = \vect{0}\ \text{on}\ \Gamma_d \};
+  \vec{u}^{\psi} \in \mathcal{H}^1_0(\Omega) = \{ \vec{u}^{\psi} \in
+  \mathcal{H}^1 \mid \vec{u}^{\psi} = \vec{0}\ \text{on}\ \Gamma_d \};
 \end{equation}
@@
   \label{eq:cauchy-secuence}
-  \Integral{3}{\vect{u}^{\psi}} < \infty\ \quad\text{and}\quad
+  \Integral{3}{\vec{u}^{\psi}} < \infty\ \quad\text{and}\quad
   \Integral{3}{\tens{\varepsilon}^{\psi}} < \infty.
@@
 The principle of virtual work states that the equilibrium solution to
-the boundary-value problem of elasticity is the function $\vect{u} \in
-\mathcal{H}^1_0$ such that, for any $\vect{u}^{\psi} \in
+the boundary-value problem of elasticity is the function $\vec{u} \in
+\mathcal{H}^1_0$ such that, for any $\vec{u}^{\psi} \in
 \mathcal{H}^1_0$,
 the following holds:
+%%%%%%%%%%%%%%%%%%%%%
 \begin{equation}
@@
 \end{equation}\\
+%%%%%%%%%%%%%%%%%%%%%
 Thus, equation~\eqref{eq:BalanceMomentum_wf}, together with
@@
 \eqref{eq:Rho-material-derivative}, represents the weak form
-formulation of the problem.
-
-Next, we will discretize the set of equations of the mathematical model using a double discretization procedure.
-First, the continuum \gls{domain} is discretized with a finite sum of material points (also denominated particles the manuscript).
-Each material point
-represents a part of the discretized domain $\varOmega_p \subset
-\varOmega$ with $p = 1,2\ldots ,N_p$ where $N_p$ is the number of
-particles. The material point location, $\vec{x}_p$, is defined at the centroid
-of each $\Omega_p$ (see figure~\ref{fig:MPM-discretization} for details).
-Initial values of position,
-velocity, mass, volume and stress denoted by $\vec{x}_p$,
-$\vec{v}_p$, $m_p$,  $V_p$ and $\tens{\sigma}_p$ respectively are assigned to each material point, which also owns the
-virtual displacement field $\vect{u}^{\psi}_{p}$. Regarding numerical integration, the material derivatives are
-  evaluated using the Riemann integral definition \cite{Riemann_1854}
-  applied to a finite set of points which associated volumes are
-  interpreted as quadrature weights. Consequently,
-individual terms in \eqref{eq:BalanceMomentum_wf} are solved as follows. 
-\begin{itemize}
-\item Acceleration forces :
-\begin{equation}
-    \label{eq:particle_acceleration_forces}
-    \Integral{3}{\rho\ \frac{d\vec{v}}{dt} \cdot \vect{u}^{\psi}} =
-    \frac{d\vec{v}_{p}}{dt} \cdot \vect{u}^{\psi}_{p}\ m_p.
-  \end{equation}\\
-\item Internal forces :
-  \begin{equation}
-    \label{eq:particle_internal_forces}
-    \Integral{3}{\tens{\sigma}\ \colon \tens{\varepsilon}^{\psi}} =
-   \tens{\sigma}_{p}\ \colon \tens{\varepsilon}^{\psi}_p \ V_p.
-  \end{equation}\\
-\item Body forces :
-\begin{equation}
-  \label{eq:particle_body_forces}
-  \Integral{3}{\rho\ \vec{b} \cdot \vect{u}^{\psi} } = 
-  \vec{b}_{p} \cdot \vect{u}^{\psi}_p\ m_p.
-\end{equation}\\
-\item Loads :
-\begin{equation}
-  \begin{aligned}
-    \label{eq:particle_load_forces}
-    \Integral{2}{\vec{t}\ \vect{u}^{\psi}} = \Integral{2}{\rho\
-      \vec{t}^s \cdot \vect{u}^{\psi}} = \vec{t}^s_{p} \cdot \vect{u}^{\psi}_{p}\ h^{-1}\ m_p ,
-  \end{aligned} 
-\end{equation}
-\end{itemize}
-where $h$ is the thickness of the continuum in a 2D case. Next, we
-  will proceed with the second step of the discretization. It is based on using a background grid with coordinates $\vec{x}_I\
-, I = 1,2\ldots ,N_n$, is generated, being $N_n$ the number of grid
-nodes. Spatial derivatives, such as gradients and
-divergences, are computed through the support of the background mesh.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
+formulation of the problem. Next, we will discretise the set of equations of the mathematical model using a double discretisation procedure, see figure~\ref{fig:MPM-discretization}.\\
+
+\MODIFIED{First, the velocity field and the virtual displacements fields are discretised in a finite set of nodes $\textbf{X} = \{ \vec{x}_I, I \in \mathcal{B} \} \subset \mathbb{R}^n$, where $\mathcal{B} = 1, \ldots, N_I$.
+The continuum field can be reconstructed with the help of nodal values and an appropriate interpolation function $N_I(\vec{x})$.
+Also spatial derivatives of those quantities, such as gradients and divergences, are computed through the support of the background set of nodes as.}
+\begin{align}
+    \label{eq:variable_reconstruction}
+    \varphi(\vec{x}) &= \sum_{I\ \in\ \mathcal{B}} N_I(\vec{x})\ \varphi_I \\
+    \label{eq:grad_variable_reconstruction}
+    \Grad{\varphi}(\vec{x}) &= \sum_{I\ \in\ \mathcal{B}} \Grad{N_I(\vec{x})}\ \varphi_I
+\end{align}
+\MODIFIED{Secondly, the continuum \gls{domain} is discretised with a finite set of material points (also denominated particles the manuscript) $\hat{\Omega} = \{ \vec{x}_p, p \in \mathcal{C} \} \subset \Omega$, where $\mathcal{C} = 1, \ldots, N_p$.
+Any particle field such as position, velocity, mass, volume and stress denoted by $\vec{x}_p$, $\vec{v}_p$, $m_p$, $V_p$ and $\tens{\sigma}_p$ respectively are assigned to each material point.
+Furthermore, any particle field $\varphi_p$ can be reconstructed within the nodes in the neighbourhood of each particle, $\mathcal{B}_p \subset \mathcal{B}$, and evaluating the interpolation function in the position of each particle as}
+\begin{align}
+    \label{eq:particle_variable_reconstruction}
+\varphi_p &= \sum_{I\ \in\ \mathcal{B}_p} N_I(\vec{x}_p)\ \varphi_I \\
+\Grad{\varphi_p} &= \sum_{I\ \in\ \mathcal{B}_p} \Grad{N_I(\vec{x}_p)}\ \varphi_I
+\end{align}
+\MODIFIED{Regarding numerical integration, the material derivatives are evaluated using the Riemann integral definition \cite{Riemann_1854} applied to a finite set of points which associated volumes $V_p$ are interpreted as quadrature weights.}
+\begin{equation}
+    \label{eq:particle_riemann_integral}
+\Integral{3}{\varphi} = \sum_{p\ \in\ \mathcal{C}} \varphi_p\ V_p 
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+%\sidecaption
   \centering
@@
     \includegraphics[width=\textwidth]{Figures/Mesh-particles-back}}
-  \caption{Description of the spatial discretization for domain presented in the
+  \caption{Description of the spatial discretisation for domain presented in the
     figure~\ref{fig:Continuum-solid}. Blue mesh represent the
     background computational support, and the red mesh conforms the
-    discretized continuum body.}
+    discretised continuum body.}
   \label{fig:MPM-discretization}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Introducing \eqref{eq:particle_acceleration_forces},
-\eqref{eq:particle_internal_forces}, \eqref{eq:particle_body_forces},  \eqref{eq:particle_load_forces} in \eqref{eq:BalanceMomentum_wf},
-approximating the displacement field of the particle
-$p$ as $\vec{u}_{p} = N_{Ip} \vect{u}_I$, $\vec{u}^{\psi}_{p} = N_{Ip} \vect{u}_I^{\psi}$,
-and its gradient as $\tens{\varepsilon}_p = (\vect{u}_I \otimes
-\Grad{N_{Ip}})^s$, $\tens{\varepsilon}_p^{\psi}= (\vect{u}_I^{\psi} \otimes \Grad{N_{Ip}})^s$.
-nodal balance of forces of the continuum yields:
-\begin{equation}
-  \label{eq:particle_balance_forces3}
-  \dot{\vec{p}}_{I}= \tens{m}_{IJ}\dot{\vec{v}}_{J} = \vec{f}_{I}^{int} + \vec{f}_{I}^{ext},
-\end{equation}
-where $\dot{\vec{p}}_{I}$ is the rate of momentum at grid node $I$ and $\tens{m}_{IJ}$, the nodal mass matrix, is obtained through:
-\begin{equation}
-  \label{eq:particle_nod_mass}
-  \tens{m}_{IJ} = N_{Ip} m_p N_{Jp}.
-\end{equation}
-In order to improve the computational efficiency and stability, the nodal mass matrix
-\eqref{eq:particle_nod_mass} can be substituted by the lumped mass
-matrix $\tens{m}_{IJ}^{lumped}$.
-Following, internal and external forces are computed as follows,
-\begin{equation}
-  \label{eq:nodal_internal_forces}
-  \vec{f}_{I}^{int} = - \tens{\sigma}_{p} \cdot \Grad{N_{Ip}} \frac{m_p}{\rho_p}
-\end{equation}
-\begin{equation}
-  \label{eq:nodal_external_forces}
-  \vec{f}_{I}^{ext} = N_{Ip}\ \vec{b}_{p}\ m_p  + N_{Ip}\ \vec{t}^s_{p}\ m_p h^{-1} 
-\end{equation}
-where $\tens{\sigma}_{p} = \tens{\sigma}_{p}(\tens{\varepsilon}_{p})$
+\MODIFIED{Let us illustrate the procedure described above by fully developing the term of the acceleration forces in \eqref{eq:BalanceMomentum_wf}.
+Employing the definition \eqref{eq:variable_reconstruction} the velocity and virtual displacement fields can be approximated within its nodal values.
+Hence, the acceleration forces is reduced to}
+\begin{equation}
+    \label{eq:particle_acceleration_forces_I}
+    \sum_{I,J\ \in\ \mathcal{B}} \Integral{3}{ \rho\ N_J(\vec{x})  \frac{d\vec{v}_J}{dt}\ \cdot N_I(\vec{x})\vec{u}_I^{\psi}}.
+\end{equation}
+\MODIFIED{Rearranging terms in \ref{eq:particle_acceleration_forces_I}, and subtracting from the integral those discrete variables, the following expression is obtained}
+\begin{equation}
+    \label{eq:particle_acceleration_forces_II}
+    \sum_{I,J\ \in\ \mathcal{B}} \vec{u}_I^{\psi} \cdot \Integral{3}{ N_I(\vec{x})\ \rho\ N_J(\vec{x})}\ \frac{d\vec{v}_J}{dt}.
+\end{equation}
+\MODIFIED{Now, employing the particle integral definition \eqref{eq:particle_riemann_integral} to compute the integral of \eqref{eq:particle_acceleration_forces_II}, and simplifying the it, is possible to achieve a discrete expression o the acceleration forces term as}
+%%%%%%%%%%%%%%%%
+\begin{equation}
+\label{eq:particle_acceleration_forces_III}
+\begin{split}
+&\sum_{I,J\ \in\ \mathcal{B}} \vec{u}_I^{\psi} \cdot \sum_{p\ \in\ \mathcal{C}} N_{Ip}\ \rho_p\ N_{Jp}\ V_p\ \frac{d\vec{v}_J}{dt} = \\
+&= \sum_{I,J\ \in\ \mathcal{B}} \vec{u}_I^{\psi} \cdot \sum_{p\ \in\ \mathcal{C}} N_{Ip}\ m_p\ N_{Jp}\ \frac{d\vec{v}_J}{dt} = \\
+&= \tens{m}_{IJ}\ \frac{d\vec{v}_J}{dt}
+\end{split}
+\end{equation}
+%%%%%%%%%%%%%%%%
+\MODIFIED{Where $\tens{m}_{IJ}$, is the nodal mass matrix, and $N_{Ip}, N_{Jp}$ are the interpolation functions for nodes $I,J$ evaluated in the position of each particle $p$.
+In order to improve the computational efficiency and stability, the nodal mass matrix can be substituted by the lumped mass matrix $\tens{m}_{IJ}^{lumped}$.
+The remaining terms of \eqref{eq:BalanceMomentum_wf} are obtained within a similar procedure and can be found in literature, see for instance \cite{Zhang_book_2016}.
+So equation \eqref{eq:BalanceMomentum_wf} has been discretised as}
+%%%%%%%%%%%%%%%%%%%%%
+\begin{equation}
+\label{eq:BalanceMomentum_wf_discretized}
+    \tens{m}_{IJ}\ \frac{d\vec{v}_J}{dt} = \sum_{p\ \in\ \mathcal{C}} - \tens{\sigma}_{p} \cdot \Grad{N_{Ip}} \frac{m_p}{\rho_p} + N_{Ip}\ \vec{b}_{p}\ m_p  + N_{Ip}\ \vec{t}^s_{p}\ m_p h^{-1}
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%
+\MODIFIED{Where $h$ is the soil thickness in 2D, and $\tens{\sigma}_{p} = \tens{\sigma}_{p}(\tens{\varepsilon}_{p})$
 is the particle $p$ stress field, which can be integrated employing
 the suitable constitutive model.
-The strain tensor rate, $\dot{ \tens{\varepsilon}}_{p}$, as a measure of the time derivative of the strain tensor, is updated employing the velocity at the background mesh by the equation:
+The particle strain field is approximated thorough the time integration of the rate of stress tensor, which is computed employing the velocity at the background set of nodes by the equation}
+%%%%%%%%%%%%%%%%%%%%%
 \begin{equation}
@@
   \dot{\tens{\varepsilon}_{p}} = \frac{\Delta
-    \tens{\varepsilon}_{p}}{\Delta t} =
+    \tens{\varepsilon}_{p}}{\Delta t} = \sum_{I\ \in\ \mathcal{B}_p}
   \frac{1}{2} \left[\Grad{N_{Ip}}\ \otimes \vec{v}_{I} + \vec{v}_{I} \otimes
@@
 \end{equation}
-Next, mass conservation is guaranteed by enforcing the null value of
+%%%%%%%%%%%%%%%%%%%%%
+Finally, mass conservation is guaranteed by enforcing the null value of
 the material derivative of the density field $\frac{D \rho}{D t} = 0$.
@@
 \end{equation}
-Finally, to solve the equation \eqref{eq:particle_balance_forces3}, a second order time integration scheme is required. Therefore, time is
-discretized into a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$
-is the total number of time steps. Once the nodal equilibrium equation is solved, the values at the nodes are
-interpolated back into the particles, which are advected
+Observe that to solve the equation \eqref{eq:BalanceMomentum_wf_discretized}, a second order time integration scheme is required. Therefore, time is
+discretised into a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$ is the total number of time steps.
+Once the nodal equilibrium equation is solved, the values at the nodes are interpolated back into the particles, which are advected
 to the new position through:
@@
   \label{eq:Updated_Lagrangian}
-  \dot{\vec{v}}_p = N_{Ip}\ \vec{a}_{I},\quad and\quad
-  \dot{\vec{x}}_{p} = N_{Ip}\ \vec{v}_{I}  
-\end{equation}
-Traditionally, Eqs.
-\eqref{eq:particle_balance_forces3} and ~\eqref{eq:Updated_Lagrangian},
+  \dot{\vec{v}}_p = \sum_{I\ \in\ \mathcal{B}_p} N_{Ip}\ \vec{a}_{I},\quad \text{and} \quad
+  \dot{\vec{x}}_{p} = \sum_{I\ \in\ \mathcal{B}_p} N_{Ip}\ \vec{v}_{I}.  
+\end{equation}
+Traditionally, Eqs. \eqref{eq:BalanceMomentum_wf_discretized} and ~\eqref{eq:Updated_Lagrangian},
 are solved with an explicit forward Euler algorithm. In the following subsection, this and the proposed schemes are described.
 
-\subsection{\acrshort{mpm} time integration scheme: the Newmark Predictor-Corrector proposal}
+\subsection{MPM time integration scheme: the Newmark Predictor-Corrector proposal}
 %\subsection{Explicit predictor-corrector scheme for \acrshort{mpm}.}
@@
 
-As was stated previosuly, an explicit forward Euler algorithm has been utilized widely within the \acrshort{MPM} methodology. This scheme has been described in detail by many researchers
+As was stated previosuly, an explicit forward Euler algorithm has been utilized widely within the \acrshort{mpm} methodology. This scheme has been described in detail by many researchers
 \cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and can be sketched by the scheme of the figure~\ref{fig:MPM_algorithm}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
+\begin{figure}
+%\sidecaption
   \centering
@@
   \label{eq:Sulsky-1994-UL-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\ N_{Ip}^{k}\ \vec{a}_{I}^{k}
+  \vec{v}_p^{k+1} = \vec{v}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ N_{Ip}^{k}\ \vec{a}_{I}^{k},
 \end{equation}
@@
   \label{eq:Sulsky-1994-UL-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ N_{Ip}^{k}\ \vec{v}_{I}^{k}.
+  \vec{x}_p^{k+1} = \vec{x}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ N_{Ip}^{k}\ \vec{v}_{I}^{k}.
 \end{equation}
 However, as Andersen (2009)\cite{thesis_Andersen_2009} pointed out, this algorithm has been shown to be numerically unstable due to that
-$\vect{f}_I^{int,k}$ can be infinite for an infinitesimal nodal mass
-$\tens{m}$. This issue may lead to numerical problems when nodal acceleration
+$\vec{f}_I^{int,k}$ can be infinite for an infinitesimal nodal mass
+$\tens{m}_I$. This issue may lead to numerical problems when nodal acceleration
 is obtained in the evaluation of the Eqs. \eqref{eq:Sulsky-1994-UL-x} and \eqref{eq:Sulsky-1994-UL-v}. Hence, a
@@
   \label{eq:Zhang-2016-UL-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + \Delta t\ \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}, 
+  \vec{x}_p^{k+1} = \vec{x}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}, 
 \end{equation}
@@
   \label{eq:Zhang-2016-UL-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\ \frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I}.
+  \vec{v}_p^{k+1} = \vec{v}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ \frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I}.
 \end{equation}
@@
   \label{eq:Tran-2019-GA-v}
-  \vect{v}_p^{k+1} = \vect{v}_p^{k} + \Delta t\  N_{Ip}^{k}\ \left[(1 - \gamma)\ \vect{a}_I^{k} +
-    \gamma\ \vect{a}_I^{k+1} \right],\\
+  \vec{v}_p^{k+1} = \vec{v}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\  N_{Ip}^{k}\ \left[(1 - \gamma)\ \vec{a}_I^{k} +
+    \gamma\ \vec{a}_I^{k+1} \right],\\
 \end{equation}
@@
 \label{eq:Tran-2019-GA-x}
-  \vect{x}_p^{k+1} = \vect{x}_p^{k} + N_{Ip}^{k} \left[ \Delta t\ \vec{v}_{I}^{k}+ \Delta t^2\left( (\frac{1}{2} - \beta)\
+  \vec{x}_p^{k+1} = \vec{x}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} N_{Ip}^{k} \left[ \Delta t\ \vec{v}_{I}^{k}+ \Delta t^2\left( (\frac{1}{2} - \beta)\
     \vec{a}_{I}^{k} + \beta\ \vec{a}_{I}^{k+1} \right) \right],
@@
   \label{eq:Tran-2019-GA-a}
-  \vect{a}_p^{k+1} = N_{Ip}^{k}\ \vec{a}_{I}^{k+1}.
+  \vec{a}_p^{k+1} = \sum_{I\ \in\ \mathcal{B}_p} N_{Ip}^{k}\ \vec{a}_{I}^{k+1}.
 \end{equation}
@@
 \begin{equation*}
-  \Matrix{M}_{IJ}\ddot{\Vector{d}}_{J} + \Matrix{C}_{IJ}\dot{\Vector{d}}_{J} +
+ \sum_{J\ \in\ \mathcal{B}} \Matrix{M}_{IJ}\ddot{\Vector{d}}_{J} + \Matrix{C}_{IJ}\dot{\Vector{d}}_{J} +
   \Matrix{K}_{IJ}\Vector{d}_{J} = \Vector{F}_{I}.
@@
 where each component of the summation corresponds to a particle of the
-discretization. Also Bardenhagen \& Kober \cite{Bardenhagen2004}
+discretisation. Also Bardenhagen \& Kober \cite{Bardenhagen2004}
 proved that through this information-transference technique mass and momentum are conserved. So for a general particle variable $\Phi_p$, employing the
@@
   \label{eq:Variational-recovery}
-   \Phi_I = \frac{m_p N_{Ip} \Phi_p}{m_I}.
+   \Phi_I = \sum_{p\ \in\ \mathcal{C}} \frac{m_p N_{Ip} \Phi_p}{m_I}.
  \end{equation}
@@
    \label{eq:Predictor-velocity-II}
-   \vec{\tilde{v}}_I^{k+1} = \underbrace{\frac{N_{Ip}^{k} m_p
+   \vec{\tilde{v}}_I^{k+1} = \sum_{p\ \in\ \mathcal{C}} \underbrace{\frac{N_{Ip}^{k} m_p
        \vec{v}_p^k}{m_I}}_{\vec{v}_I^{k}} + (1 - \gamma)\ \Delta t\  \underbrace{\frac{N_{Ip}^{k} m_p \vec{a}_p^k}{m_I}}_{\vec{a}_I^{k}}.
@@
   \label{eq:Predictor-velocity-II}
-  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}.
+  \vec{\tilde{v}}_I^{k+1} =  \sum_{p\ \in\ \mathcal{C}} \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}.
 \end{equation}
@@
 and minimize the computational effort. Once nodal velocities are
-obtained, the essential boundary conditions are imposed over \gls{dirichlet-boundary}. And in the
+obtained, the \acrshort{dbc} are imposed over \gls{dirichlet-boundary}. And in the
 following, the ``classic'' \acrshort{mpm} algorithm continues to reach to the
-equilibrium equation \eqref{eq:particle_balance_forces3}. Next, the
+equilibrium equation \eqref{eq:BalanceMomentum_wf_discretized}. Next, the
 \textit{corrector} stage is introduced. As nodal
@@
   \label{eq:Update-lagrangian-pce}
-        &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
-      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
+        &\vec{a}_p^{k+1} = \sum_{I\ \in\ \mathcal{B}_p} \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\
         \frac{N_{Ip}^k\
         \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
-      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
+      &\vec{x}_p^{k+1} = \vec{x}_p^n + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\
          N_{Ip}^k\ \vec{v}_{I}^{k} +
@@
 also that, with this approach, the calculation of nodal momentum values
-are not required. Due to its simplicity, the proposed scheme can be implemented with minor modifications
-over the standard forward Euler. The full implementation is summarized in the algorithm~\ref{algo:1}.
+are not required.
+Due to its simplicity, the proposed scheme can be implemented with minor modifications over the standard forward Euler.
+The full implementation is summarized in the algorithm~\ref{algo:1}.
 
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
-    \STATE \textbf{Update mass matrix}:
-    \begin{equation*}
-      \tens{m}_{I} = N_{Ip}^{k}\ m_p,
-    \end{equation*}
+    \STATE \textbf{Update mass matrix}.
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
     \begin{equation*}
-      \vec{v}_I^{pred} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
+      \vec{v}_I^{pred} = \sum_{p\ \in\ \mathcal{C}} \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}.
     \end{equation*}
@@
     \STATE \textbf{Deformation tensor increment calculation}.
-    \begin{align*}
-      &\dot{\tens{\varepsilon}_{p}}^{k+1} = \left[ \vec{v}_{I}^{pred} \otimes
-        \Grad{N_{Ip}^{k+1}} \right]^s \\
-      &\Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\ \dot{\tens{\varepsilon}_{p}}^{k+1}
-    \end{align*}
+    \begin{equation*}
+      \dot{\tens{\varepsilon}_{p}}^{k+1} = \sum_{I\ \in\ \mathcal{B}_p} \left[ \vec{v}_{I}^{pred} \otimes \Grad{N_{Ip}^{k+1}} \right]^s\ \quad \text{and}\ \quad \Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\ \dot{\tens{\varepsilon}_{p}}^{k+1}.
+    \end{equation*}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
     \STATE \textbf{Balance of forces calculation}:\\
-    Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
-    \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ by evaluating
-    \eqref{eq:nodal_internal_forces} and
-    \eqref{eq:nodal_external_forces} in the time step $k+1$.
-    In those nodes where $\Deriv{\vect{v}_I^{k}}{t} \big\rvert_{\Gamma_d} = 0$,
-      the acceleration is fixed to zero and nodal forces are stored as
-      reactions.\\
+    Calculate the total grid nodal forces by evaluating the right hand side of 
+    \eqref{eq:BalanceMomentum_wf_discretized} in the time step $k+1$.
+    In those nodes where $\Deriv{\vec{v}_I^{k}}{t} \big\rvert_{\Gamma_d} = 0$, the acceleration is fixed to zero and nodal forces are stored as reactions.\\
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
     \begin{equation*}
-      \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}  
+      \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}.
     \end{equation*}
@@
     \begin{align*}
-      &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
-      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
+      &\vec{a}_p^{k+1} = \sum_{I\ \in\ \mathcal{B}_p} \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k},\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\
         \frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
-      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k},\\
+      &\vec{x}_p^{k+1} = \vec{x}_p^n + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\
          N_{Ip}^k\ \vec{v}_{I}^{k} +
         \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k}
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}.
     \end{align*}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Reset nodal values}
+    \STATE \textbf{Reset nodal values}.
   \end{algorithmic}
@@
 made with the original \acrshort{mpm}, numerical noises appear when particles
-cross the cell boundaries. Solving this issue is the main goal of the employment of the \acrshort{LME} shape functions.
+cross the cell boundaries. Solving this issue is the main goal of the employment of the \acrshort{lme} shape functions.
 
@@
 \begin{align*}
-  \label{eq:RAJAN}
+  %\label{eq:RAJAN}
   \text{(RAJ)} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
@@
 \begin{align*}
-  \label{eq:LME-scheme-pareto-set}
+  %\label{eq:LME-scheme-pareto-set}
   \text{(LME)}_{\beta} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
@@
   \label{eq:LME-grad-p}
-\nabla N_I^* &=& N^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} N^*_J \, \nabla f^*_J\right)
+\nabla N_I^* = N^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} N^*_J \, \nabla f^*_J\right)
 \end{equation}
@@
 described does not requires the employment of this artifices.
-Due to the \short{fem}-compatibility, the \acrshort{lme} shape
+Due to the \acrshort{fem}-compatibility, the \acrshort{lme} shape
 function is degenerated to linear finite element shape function if
 $d+1$ neighbouring nodes are chosen as the support, where $d$ is the
-number of dimensions in the problem. Ullah {\it et al.}
-  \cite{Augarde_2013} took advantage of the \acrshort{lme}
-  \short{fem}-compatibility to couple the
-     \acrfull{efgm} and \short{fem} for linear elasticity and for problems with both material and geometrical non-linearities. Furthermore, with a conveniently
+number of dimensions in the problem.
+Ullah {\it et al.} \cite{Augarde_2013} took advantage of the \acrshort{lme} \acrshort{fem}-compatibility to couple the \acrfull{efgm} and \acrshort{fem} for linear elasticity and for problems with both material and geometrical non-linearities.
+Furthermore, with a conveniently
 adopted \textit{regularization} parameter it is possible to get a 
-\acrshort{gimp}-like shape function. Finally \short{sph}-like
+\acrshort{gimp}-like shape function. Finally \acrshort{sph}-like
 behaviour can be obtained for lower values of $\gamma$ since the
@@
   \subfigure[$\text{LME}_{17}$]{
-    \begin{tabular}{c}      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun}\\
+    \begin{tabular}{c}      
+      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun}\\
       \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun_dx}\\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-In this research and in \cite{Arroyo2006}, $\Beta$ is a scalar as the
+In this research and in \cite{Arroyo2006}, $\beta$ is a scalar as the
 influence area of the shape function is controlled by the Euclidean
@@
 \acrshort{lme} scheme, which uses an anisotropic support to deal with 
-tensile instability. This is another benefit of the proposed methodology, that, although is out of the scope of the
-present document, will be incorporated in future research.
+tensile instability. This is another benefit of the proposed methodology, that, although is out of the scope of the present document, will be incorporated in future research.
+\MODIFIED{Unfortunately, local \textit{max-ent} approximation technique only provides an efficient tool to transfer information from particles to nodes and vice versa to the \acrshort{mpm}.
+Hence, the difficulties of imposing \acrshort{dbc} in the \acrshort{mpm} persists since they are a direct consequence of discretising the continuum with material points instead of nodes, where traditionally \acrshort{dbc} are imposed.
+However, any available technique employed to overcome this situation in the standard \acrshort{mpm} can be translated to the \textit{max-ent} one thanks to the Kronecker-Delta property inherent to it \cite{Arroyo2006}.
+See for instance the work of Cortis {\it et al.} (2018) \cite{Cortis2018a}}.
 
@@
 of 0.1333 meters, sketched in the figure~\ref{fig:Dyka_Bar}. The
-boundary conditions are: displacements are constrained ($\vect{v}
-\rvert_{x=L} = 0$) in the right border, being free on all other boundaries. An initial velocity of $\vect{v}_o = - 5\ m/s$ is given to the
+boundary conditions are: displacements are constrained ($\vec{v}
+\rvert_{x=L} = 0$) in the right border, being free on all other boundaries. An initial velocity of $\vec{v}_o = - 5\ m/s$ is given to the
 left quarter of the bar. Finally, the elastic parameters chosen for this test are:
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}\sidecaption
+\begin{figure}
+%\sidecaption
   \centering
@@
 lengths of the bar. For the spatial
-discretization, a set of seven nodal mesh sizes (0.1, 0.3325, 0.5,
+discretisation, a set of seven nodal mesh sizes (0.1, 0.3325, 0.5,
 1.0, 3.3325, 6.665, 10.0 millimeters) are considered. For each element a number of
@@
   \label{eq:Cel}
-  Cel = \max\{\max_{p \in \Omega_p}\{ \vect{v}_p \} , \max_{p \in \Omega_p}\{ \sqrt{\frac{E_p}{\rho_p}} \} \}.
+  Cel = \max\{\max_{p \in \Omega_p}\{ \vec{v}_p \} , \max_{p \in \Omega_p}\{ \sqrt{\frac{E_p}{\rho_p}} \} \}.
 \end{equation}
@@
   \label{eq:RMS}
-  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vect{v}_p - \hat{\vect{v}}_p \right)^2},
-\end{equation}
-where $\vect{v}_p$ and $\hat{\vect{v}}_p$ are respectively the analytical and
+  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \vec{v}_p - \hat{\vec{v}}_p \right)^2},
+\end{equation}
+where $\vec{v}_p$ and $\hat{\vec{v}}_p$ are respectively the analytical and
 numerical solutions evaluated in the final time step in the position
@@
 \ref{fig:Dyka-error-evol} the evolution of the RMS is obtained for both time integration schemes.
-The right figure, with the \acrshort{NPC} results, shows lower values of the estimated error, denoting the higher performance of this methodology.
-About the spatial discretization, the \acrshort{LME} schemes show an error comparable to the obtained with the \acrshort{uGIMP}, being even lower close to the grid-crossing region.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\begin{figure*}\sidecaption
+The right figure, with the \acrshort{npc} results, shows lower values of the estimated error, denoting the higher performance of this methodology.
+About the spatial discretisation, the \acrshort{lme} schemes show an error comparable to the obtained with the \acrshort{ugimp}, being even lower close to the grid-crossing region.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{figure*}
+%\sidecaption
   \centering
@@
 
-Finally, the \acrshort{otm}~\cite{Li2010} solution is compared against the one obtained with \acrshort{mpm}, both with same time integration scheme and spatial discretization, and results are shown in figure \ref{fig:Dyka-OTM-MPM}.
+Finally, the \acrshort{otm}~\cite{Li2010} solution is compared against the one obtained with \acrshort{mpm}, both with same time integration scheme and spatial discretisation, and results are shown in figure \ref{fig:Dyka-OTM-MPM}.
 In
@@
 predictor-corrector scheme is here employed looking forward to getting better results. For the
-initial spatial discretization four particles per cell
+initial spatial discretisation four particles per cell
 ($\Delta x = 2\ m$) were adopted. The initial layout of particles inside of the
@@
 was noticed previously by \cite{Arroyo2006}, were authors highlighted
-how, by adjusting the spatial variation of $\beta(\vect{x})$, it is
+how, by adjusting the spatial variation of $\beta(\vec{x})$, it is
 possible to select regions of the domain of analysis which are treated
@@
 We have proposed in this paper an enhanced methodology which improves \acrfull{mpm} behaviour in fast dynamics problems.
-Different time and space discretization techniques have been presented and their performance being compared agains other approaches in two benchmark problems.
+Different time and space discretisation techniques have been presented and their performance being compared agains other approaches in two benchmark problems.
 First, a novel time integration scheme for
@@
 In the literature, several approaches of the \acrshort{npc} are proposed in order to compete on accuracy with expensive implicit time integration algorithms.
-The main achievement of the proposed time discretization has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.
+The main achievement of the proposed time discretisation has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.
 Also, the procedure employed to design the \acrshort{npc} algorithm opens the
@@
 
-On the other hand, the spatial discretization of the \acrshort{mpm} is enhanced thanks to the powerful skills of the \acrfull{lme} approximation scheme, which has been validated as a robust and versatile
+On the other hand, the spatial discretisation of the \acrshort{mpm} is enhanced thanks to the powerful skills of the \acrfull{lme} approximation scheme, which has been validated as a robust and versatile
 tool in the \acrshort{mpm} framework. It also comes up as a promising
@@
 density of particles per cell.
-Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vect{x})$ through the finite strain
+Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vec{x})$ through the finite strain
 tensor in order to align the shape functions in the principal strain
-direction to select the most suitable set of nodes adapted to the strain, as well as the possibility of adapting the value of $\beta$ to solve the equations
+direction to select the most suitable set of nodes adapted to the strain as well as the possibility of adapting the value of $\beta$ to solve the equations
 \acrshort{fem}-like of meshfree-like depending of how behaves the

### 2020-08-26 Revisiones/PNA_Responses to the reviewers.tex
Nueva hoja de respuestas

--- 2020-08-25 Revisiones/Responses to the reviewers.tex
@@
 \title{Response to the reviewers of the manuscript ``On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme"}
-\author{Miguel Molinos, Pedro Navas, Manuel Pastor, and Miguel Mart\'in-Stickle}
+\author{Miguel Molinos, Pedro Navas, Manuel Pastor\\
+and Miguel Mart\'in-Stickle}
 \date{September 1, 2020}
@@
 \\
-\begin{enumerate}
-\item \textit{However, most of the applications presented in this manuscript are relatively simple and does not really demonstrate the capability of the proposed approach.
+\textit{However, most of the applications presented in this manuscript are relatively simple and does not really demonstrate the capability of the proposed approach.
 I suggest the authors to extend their manuscript to predict more challenging problems and compare their results to the original MPM solutions.}\\
 
-Authors are completely agree with the proposal.
-And in analogy with the work of \cite{HAMMERQUIST2017724}, where fast dynamics were also studied.
-The Sulsky classical example of two colliding disks has been discussed in the new version of the manuscript.
-
-\end{enumerate}
+Authors agree with the proposal of the reviewer.
+In the first version, aiming to make a readable manuscript, several examples were not shown.
+In this revised version, in order to clarify several questions of both reviewers, and in analogy with the work of Hammerquist \textit{et al.}\cite{HAMMERQUIST2017724}, where fast dynamics were also studied, the classical example of two colliding disks (first proposed by Sulsky) has been discussed.
 
@@
 
+Of course, the employment of the Max-Ent shape function is not free of difficulties.
+Some requirements such as the need for a convex domain, as well as those derived from its calculation (the determination of the Lagrange Multipliers, specially at the boundaries, or the obtainment of the minimizer of the logarithmic function), make the usage of Max-Ent shape functions a challenging tool.
+However, the results depicted in this manuscript will strengthen the motivation of its employment in order to mitigate typical MPM problems such as cell-crossing or stress instabilities.
+
 \item \textit{Does the use of max-ent solve the problem of imposing Dirichlet boundary conditions in the MPM?}\\
 
-No it does not.
-Local \textit{max-ent} approximation technique only provides to the MPM an efficient tool to transfer information from particles to nodes and vice versa.
-The difficulties of imposing Dirichlet boundary conditions (DBC) in the MPM are a direct consequence of discretising the continuum with material points nor with nodes where DBC are imposed.
+Unfortunately, Local \textit{max-ent} approximation technique only provides an efficient tool to transfer information from particles to nodes and vice versa to the MPM.
+The difficulties of imposing Dirichlet boundary conditions (DBC) in the MPM are a direct consequence of discretising the continuum with material points instead of nodes, where traditionally DBC are imposed.
 See for instance the work of \cite{Cortis_et_al_2017_IJNME}.
+However, any available technique employed to overcome this situation in the standard MPM can be translated to the \textit{max-ent} one thanks to the Kronecker-Delta property inherent to \textit{max-ent}.
 
@@
 
-These publications will be added to the state of art of the manuscript.
-In the humble opinion of the authors, the XPIC approach consists in the stabilisation of the solution through a novel transference procedure.
-Meanwhile, the algorithm introduced in this research proposes the stabilisation within the adaptation of a FEM time integration scheme for the MPM framework.
+These interesting publications will be added to the state of art of the revised manuscript.
+In the humble opinion of the authors, the XPIC approach consists of the stabilisation of the solution through a novel transference procedure more than a time integration scheme.
+Nevertheless, the algorithm introduced in this research proposes the stabilisation within the adaptation of the predictor-corrector Newmark algorithm, traditionally employed within FEM schemes, for the MPM framework.
 Hence, both techniques can be employed simultaneously.
@@
 
-We agree with the reviewer that some of the numerical example does not enough highlights the capabilities of the MPM Newmark Predictor-Corrector scheme.
+Contrary to the reviewer's opinion, the provided results are capable to highlight the strong capabilities of the MPM Newmark Predictor-Corrector scheme.
+It is important to remark the extension of this research: in order to isolate the strength of the proposed methodology, covering spatial and time discretization, only linear elastic problems are assessed.
 Although the results presented in \cite{MA2009272} are impressive, the proposed examples are out of the scope of the present research.
-Therefore, in analogy with the work of \cite{HAMMERQUIST2017724}, previously cited by the reviewer, the Sulsky classical example of two colliding disks has been discussed.
+In order to reinforce the benefits of the proposed methodology and in analogy with the work of Hammerquist \textit{et al} \cite{HAMMERQUIST2017724} (previously cited by the reviewer), the classical example of two colliding disks proposed by Sulsky has been discussed.
 

### 2020-08-27 LME-MPM.tex
Descripción del caso de los dos discos

@@
 % Tikz
+% \usepackage{tikz}
+%\usepackage[active,tightpage]{preview}
+%\PreviewEnvironment{tikzpicture}
+%setlength\PreviewBorder{5pt}
 \usepackage{stanli}
@@
 overcome spurious oscillations due to the grid crossing and high
-frequency loads under the context of \acrshort{mpm}. Two different test have
+frequency loads under the context of \acrshort{mpm}. \MODIFIED{Three different test have
 been adopted for this purpose: the benchmark proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995} and the test proposed in the PhD thesis of
-Andersen (2009)\cite{thesis_Andersen_2009}. On the one hand, the accuracy of the \acrfull{npc}
-scheme is compared to the standard \acrfull{fe} in order to assess the performance of the time integration schemes. On the other hand,  \acrshort{lme} solutions
+(1995)\cite{Dyka1995}, the test proposed in the PhD thesis of
+Andersen (2009)\cite{thesis_Andersen_2009} and the classical example of two colliding discs provided by Sulsky {\it et al.} (1994) \cite{Sulsky1994}.
+The first example is devoted to test the accuracy of the \acrfull{npc} scheme is compared to the standard \acrfull{fe} in order to assess the performance of the time integration schemes.
+In the second example,  \acrshort{lme} solutions
 are compared with those provided by \acrfull{ugimp} and Q4 shape
-functions. To avoid some mesh-dependent issues, in all
+functions. Finally, in the third example the present approach is tested under a scenario where shocks and grid crossing occurs.} To avoid some mesh-dependent issues, in all
 calculations a regular background mesh was set. All simulations were
@@
 \end{itemize}
-The gravity force is applied as an external force according to the
-equations \eqref{eq:particle_body_forces} and
-\eqref{eq:nodal_external_forces}. Using a total time period of T (20
+The gravity force is applied as an external force. Using a total time period of T (20
 seconds) to apply the gravity, it is increased from 0 to 9.81$m/s$
@@
   \label{fig:vertical-displacement-block}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Impact of two elastic discs}
+\label{sec:Impact-two-elastic-discs}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\sidecaption
+ \centering
+ \resizebox{0.7\hsize}{!}{
+   \input{Figures/Sulsky_discs.tex}}
+ \caption{Geometrical description of the two colliding discs problem.}
+ \label{fig:Sulsky_discs}
 \end{figure}

### 2020-08-29 Revisiones/PNA_Responses to the reviewers.tex
Pdf revisado y hoja de respuestas actualizada. MMP

@@
 \usepackage{bm}
+\usepackage{amsmath}
 
@@
 
-Further discussion has been added.
-
 Of course, the employment of the Max-Ent shape function is not free of difficulties.
 Some requirements such as the need for a convex domain, as well as those derived from its calculation (the determination of the Lagrange Multipliers, specially at the boundaries, or the obtainment of the minimizer of the logarithmic function), make the usage of Max-Ent shape functions a challenging tool.
+
+Additionally, Arroyo \& Ortiz~\cite{Arroyo2006} briefly discussed the existence of non-convex domains, and proposed some solutions to it. 
+For instance, the possibility of replacing the Euclidean distance $\lVert  x - x_a  \rVert$ in the definition of the shape functions by the length of the shortest path contained within the domain connecting $x$ and $x_a$.
+Or by decomposing the non-convex domain into convex sub-domains.
+On the other hand, this topic has been extensively studied in the context of MLS-based meshfree methods, for instance visibility, diffraction, and constrained path criteria.
+These methods are directly applicable to local \textit{max-ent} approximation.
+
 However, the results depicted in this manuscript will strengthen the motivation of its employment in order to mitigate typical MPM problems such as cell-crossing or stress instabilities.
@@
 
+\bibitem{Arroyo2006}
+Arroyo, M. and Ortiz, M..
+\newblock{Local maximum-entropy approximation schemes: A seamless bridge between finite elements and meshfree methods}.
+\newblock{International Journal for Numerical Methods in Engineering},  2006.
+
 \end{thebibliography}
@@
 \end{document}
-
-%Del revisor 2:
-%1- Meter paja de eso y fuera
-%2- Yo haria referencia al paper de Wobbes, como lo nombren ellos, y decir que haces referencia a un paper contrastado....
-%3- Hablar de eso, que hay pequeña discusion, pues se discute mas... 
-%4- No, no lo soluciona, pero en OTM lo hace. Habría que conseguir una conjunción de lo que hace OTM con lo que hacen otros metodos en MPM para imponer boundary conditions....
-%5- Leerse que hacen esos pollos, si esta bien y crees que puedes mter algun ejemplo, se puede intentar y asi tb se contenta al revisor 1

### 2020-08-29 LME-MPM.tex
Pdf revisado y hoja de respuestas actualizada. MMP

@@
   }
+\usetikzlibrary{arrows.meta}
 
@@
 \newacronym{flip}{FLIP}{Fluid Implicit Particle}
+\newacronym{pic}{PIC}{Particle in Cell}
 \newacronym{gimp}{GIMP}{Generalized Interpolation Material Point}
@@
 \newacronym{npc}{NPC}{Newmark Predictor-Corrector}
+\newacronym{usl}{USL}{Update Stress Last}
+\newacronym{usf}{USF}{Update Stress First}
 \newacronym{fe}{FE}{Forward Euler}
@@
 framework in~\cite{Navas2018a}.  
+\MODIFIED{ Other well known source of energy dissipation and numerical noise is the presence of a non-trivial null space of the linear operator that maps particles values onto nodal values.
+It was earlier identified by Brackbill~\cite{BRACKBILL1988469} as ringing instability in the \acrfull{pic} method.
+A recent development in the field of particle methods is a null-space filter engineered by Gritton \&
+Berzins~\cite{Gritton2017} which overcome this limitation but still introduce unwelcome damping.
+Later, Hammerquist \& Nairn~\cite{HAMMERQUIST2017724} introduced the XPIC as a parametric extension of the aforementioned research with excellent results.}
 
@@
 \end{equation}
-\MODIFIED{Now, employing the particle integral definition \eqref{eq:particle_riemann_integral} to compute the integral of \eqref{eq:particle_acceleration_forces_II}, and simplifying the it, is possible to achieve a discrete expression o the acceleration forces term as}
+\MODIFIED{Now, introducing the particle integral definition \eqref{eq:particle_riemann_integral} to compute the integral of \eqref{eq:particle_acceleration_forces_II}, and simplifying the it, is possible to achieve a discrete expression o the acceleration forces term as}
 %%%%%%%%%%%%%%%%
@@
 
-\subsection{Impact of two elastic discs}
+\MODIFIED{\subsection{Impact of two elastic discs}}
 \label{sec:Impact-two-elastic-discs}
 
+\MODIFIED{The following test is best suited to validate the ability of the discussed
+interpolation technique to deal with grid crossing instabilities.
+Also, it enlightens the energy conservation properties of the integration scheme, since it should remains constant before and after collision.
+The test proposed by Sulsky {\it et al.} (1994) \cite{Sulsky1994} consists in the impact of two identical elastic discs with the following elastic parameters :
+\begin{itemize} 
+\item  Initial density : $20$
+\item  Poisson ratio : $0.3$
+\item  Elastic modulus : $10^5$
+\end{itemize}
+}
+\MODIFIED{The discs starts in the lower left and upper right corners with initial velocities of $(1, 1)$ and $(-1, -1)$, respectively.
+The computational domain consists in a square of 10 meters.
+It is discretised with a cartesian grid with a meshsize of 0.1.
+The courant number is fixed to 0.1 during the whole simulation.
+Details of the problem are sketched in figure~\ref{fig:Sulsky_discs}.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
-\sidecaption
+%\sidecaption
  \centering
@@
  \label{fig:Sulsky_discs}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\MODIFIED{Energy plots in figure~\ref{fig:Sulsky-energy} proofs in one hand the ability of the \acrshort{lme} approximation to mitigate the grid-crossing error as well as the \acrshort{ugimp} interpolants, but without some  of its shortcomings previously mentioned in this paper.
+And in the other hand the energy conservation is also guaranteed with the \acrshort{npc} time integration scheme, unlike what happens in the \acrfull{usf} and \acrfull{usl} schemes.
+Although during impact mechanical energy decreases, no real dissipation occurs since after collision the value is again 5 Jules like before collision.
+Furthermore, kinetic energy has been exactly computed.
+Therefore, this apparently dissipation of mechanical energy is due to a numerical cancellation during the computation of the mechanical energy during post-process stage.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+%\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/Sulsky_energy}
+  }
+  \caption{Energy plots for different interpolation/approximation techniques.
+All simulations where performed with the already tested \acrshort{npc} algorithm.
+The evolution of the total energy of the system is represented with the solid line, the dashed line shows the evolution of the deformation energy, while the doted line represents the evolution of the kinetic energy.}
+  \label{fig:Sulsky-energy}
 \end{figure}

### 2020-09-03 LME-MPM.tex
Nuevo caso (choque de una placa)

--- 2020-08-27 LME-MPM.tex
@@
 The continuum field can be reconstructed with the help of nodal values and an appropriate interpolation function $N_I(\vec{x})$.
-Also spatial derivatives of those quantities, such as gradients and divergences, are computed through the support of the background set of nodes as.}
+Also spatial derivatives of those quantities, such as gradients and divergences, are computed through the support of the background set of nodes as}
 \begin{align}
@@
 \MODIFIED{Let us illustrate the procedure described above by fully developing the term of the acceleration forces in \eqref{eq:BalanceMomentum_wf}.
-Employing the definition \eqref{eq:variable_reconstruction} the velocity and virtual displacement fields can be approximated within its nodal values.
+Employing the definition \eqref{eq:variable_reconstruction}, the velocity and virtual displacement fields can be approximated within its nodal values.
 Hence, the acceleration forces is reduced to}
@@
 %%%%%%%%%%%%%%%%
-\MODIFIED{Where $\tens{m}_{IJ}$, is the nodal mass matrix, and $N_{Ip}, N_{Jp}$ are the interpolation functions for nodes $I,J$ evaluated in the position of each particle $p$.
+\MODIFIED{$\tens{m}_{IJ}$, is the nodal mass matrix, and $N_{Ip}, N_{Jp}$ are the interpolation functions for nodes $I,J$ evaluated in the position of each particle $p$.
 In order to improve the computational efficiency and stability, the nodal mass matrix can be substituted by the lumped mass matrix $\tens{m}_{IJ}^{lumped}$.
@@
 overcome spurious oscillations due to the grid crossing and high
-frequency loads under the context of \acrshort{mpm}. \MODIFIED{Three different test have
+frequency loads under the context of \acrshort{mpm}. \MODIFIED{Three different tests have
 been adopted for this purpose: the benchmark proposed by Dyka \& Ingel
 (1995)\cite{Dyka1995}, the test proposed in the PhD thesis of
-Andersen (2009)\cite{thesis_Andersen_2009} and the classical example of two colliding discs provided by Sulsky {\it et al.} (1994) \cite{Sulsky1994}.
+Andersen (2009)\cite{thesis_Andersen_2009} and the evolution of velocity waves in an elastic square.
 The first example is devoted to test the accuracy of the \acrfull{npc} scheme is compared to the standard \acrfull{fe} in order to assess the performance of the time integration schemes.
@@
 
-\subsection{Impact of two elastic discs}
-\label{sec:Impact-two-elastic-discs}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\MODIFIED{\subsection{Velocity waves in an elastic domain}}
+\label{sec:Velocity-waves-elastic-domain}
+
+\MODIFIED{The following test is best suited to validate the ability of the discussed
+time integration scheme to reproduce 2D wave propagation problem.
+It consists of the side impact of a moving elastic square.
+The square was 50 x 50 mm and modeled with the following elastic parameters :
+\begin{itemize} 
+\item  Initial density : $20$
+\item  Poisson ratio : $0.3$
+\item  Elastic modulus : $10^5$
+\end{itemize}
+}
+
+\MODIFIED{The background set of nodes consists in a cartesian grid with a uniform gap between nodes of 1 mm, and square was discretised with four material points by cell.
+The courant number is fixed to 0.1 during the whole simulation and $\text{LME}_{4.0}$ shape functions where used.
+The square initially move horizontally through the grid at $\text{V}_0 = 1.0$ until it hits an obstacle modelled as a set of nodes with  zero velocity prescribed.
+The collision produce stress waves and cause the square to bounce back.}
+
+\MODIFIED{Snapshots of velocity field magnitude within the square are given in\ref{fig:Magnitude_velocity_impact_square}.
+At early times, \acrshort{npc} and \acrshort{fe} are similar.
+At later times, the \acrshort{fe} introduces significant numerical noise while \acrshort{npc} is almost clean.
+}
+%%%%%%%%%%%%%%%%
 \begin{figure}
-\sidecaption
+%\sidecaption
   \centering
- \resizebox{0.7\hsize}{!}{
-   \input{Figures/Sulsky_discs.tex}}
- \caption{Geometrical description of the two colliding discs problem.}
- \label{fig:Sulsky_discs}
+  \resizebox{\hsize}{!}{
+\includegraphics[scale=1]{Figures/Velocity_FE_vs_NPC_square.png} 
+  }
+  \caption{Snapshots of velocity magnitudes in an elastic square impacted at a point on the right edge. The top row is for \acrshort{npc} updates and the bottom row is for \acrshort{fe} updates.}
+  \label{fig:Magnitude_velocity_impact_square}
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%% 
+\MODIFIED{Energy plots in figure \ref{fig:Energy_impact_square} shows that after collision the total amount of energy is preserved.
+In the bounce back stress wave are still travelling thorough the elastic domain introducing numerical noise due to the inaccuracies of the time integration scheme as figure \ref{fig:Magnitude_velocity_impact_square} proves.
+However, \acrshort{npc} introduces a minimal energy loss (less than 0.1\%) to significantly reduce the numerical noise.
+}
+
+\MODIFIED{Although during impact mechanical energy decreases, no real dissipation occurs since after collision the value is again 25 kJ like before collision.
+Furthermore, kinetic energy has been exactly computed.
+Hence, this apparently dissipation of mechanical energy is probably due to numerical cancellation of shear terms contribution.
+}
+%%%%%%%%%%%%%%%%
+\begin{figure}
+%\sidecaption
+  \centering
+  \resizebox{0.8\hsize}{!}{
+\includegraphics[scale=1]{Figures/Energy_square.png} 
+  }
+  \caption{Snapshots of velocity magnitudes in an elastic square impacted at a point on the right edge. The top row is for \acrshort{npc} updates and the bottom row is for \acrshort{fe} updates.}
+  \label{fig:Energy_impact_square}
+\end{figure}
+%%%%%%%%%%%%%%%%
 

### 2020-09-03 Revisiones/PNA_MMP_Responses to the reviewers.tex
Cambios en la hoja de respuestas

--- 2020-08-29 Revisiones/PNA_Responses to the reviewers.tex
@@
 In the first version, aiming to make a readable manuscript, several examples were not shown.
-In this revised version, in order to clarify several questions of both reviewers, and in analogy with the work of Hammerquist \textit{et al.}\cite{HAMMERQUIST2017724}, where fast dynamics were also studied, the classical example of two colliding disks (first proposed by Sulsky) has been discussed.
+In this revised version, in order to clarify several questions of both reviewers, we have introduced an additional case of study which consists in the simulation of a side impact in an elastic square.
+This test has been conveniently adapted from the work of Hammerquist \& Nairn \cite{HAMMERQUIST2017724}, where fast dynamics were also studied.
 
@@
 
-Of course, the employment of the Max-Ent shape function is not free of difficulties.
-Some requirements such as the need for a convex domain, as well as those derived from its calculation (the determination of the Lagrange Multipliers, specially at the boundaries, or the obtainment of the minimizer of the logarithmic function), make the usage of Max-Ent shape functions a challenging tool.
+Of course, the employment of the \textit{max-ent} approximants is not free of difficulties.
+Some requirements such as the need for a convex domain, as well as those derived from its calculation (the determination of the Lagrange Multipliers, specially at the boundaries, or the obtainment of the minimizer of the logarithmic function), make the usage of it a challenging tool.
 
@@
 
-Unfortunately, Local \textit{max-ent} approximation technique only provides an efficient tool to transfer information from particles to nodes and vice versa to the MPM.
-The difficulties of imposing Dirichlet boundary conditions (DBC) in the MPM are a direct consequence of discretising the continuum with material points instead of nodes, where traditionally DBC are imposed.
-See for instance the work of \cite{Cortis_et_al_2017_IJNME}.
-However, any available technique employed to overcome this situation in the standard MPM can be translated to the \textit{max-ent} one thanks to the Kronecker-Delta property inherent to \textit{max-ent}.
+Unfortunately, local \textit{max-ent} approximation technique only provides an efficient tool to transfer information from particles to nodes and vice versa to the MPM.
+Hence, the difficulties of imposing Dirichlet boundary conditions (DBC) in the MPM persists since they are a direct consequence of discretising the continuum with material points instead of nodes, where traditionally DBC are imposed.
+However, any available technique employed to overcome this situation in the standard MPM can be translated to the \textit{max-ent} one thanks to the Kronecker-Delta property inherent to it \cite{Arroyo2006}.
+See for instance the work of Cortis {\it et al.} (2018) \cite{Cortis_et_al_2017_IJNME}.
 
@@
 
-Contrary to the reviewer's opinion, the provided results are capable to highlight the strong capabilities of the MPM Newmark Predictor-Corrector scheme.
+Contrary to the reviewer's opinion, the provided results are capable to highlight the strong capabilities of the MPM Newmark Predictor-Corrector scheme (NPC).
 It is important to remark the extension of this research: in order to isolate the strength of the proposed methodology, covering spatial and time discretization, only linear elastic problems are assessed.
-Although the results presented in \cite{MA2009272} are impressive, the proposed examples are out of the scope of the present research.
-In order to reinforce the benefits of the proposed methodology and in analogy with the work of Hammerquist \textit{et al} \cite{HAMMERQUIST2017724} (previously cited by the reviewer), the classical example of two colliding disks proposed by Sulsky has been discussed.
+Although the results presented in Ma {\it et al.} \cite{MA2009272} are impressive, the proposed examples are out of the scope of the present research.
+In order to reinforce the benefits of the proposed methodology and in analogy with the work of Hammerquist \& Nairn \cite{HAMMERQUIST2017724} (previously cited by the reviewer), a 2D wave propagation problem has been simulated.
+This new test highlights the capabilities of the NPC to reproduce complex wave patterns under challenging loads such as impacts.
+While at the simultanesly minimices the presence of numerical noise and preserves the solution.
 

### 2020-09-03 LME-MPM.tex
Cambios en el manuscrito

@@
 tensile instability. This is another benefit of the proposed methodology, that, although is out of the scope of the present document, will be incorporated in future research.
-\MODIFIED{Unfortunately, local \textit{max-ent} approximation technique only provides an efficient tool to transfer information from particles to nodes and vice versa to the \acrshort{mpm}.
-Hence, the difficulties of imposing \acrshort{dbc} in the \acrshort{mpm} persists since they are a direct consequence of discretising the continuum with material points instead of nodes, where traditionally \acrshort{dbc} are imposed.
-However, any available technique employed to overcome this situation in the standard \acrshort{mpm} can be translated to the \textit{max-ent} one thanks to the Kronecker-Delta property inherent to it \cite{Arroyo2006}.
-See for instance the work of Cortis {\it et al.} (2018) \cite{Cortis2018a}}.
+
+\MODIFIED{Unfortunately, the employment of \textit{max-ent} approximants is not free of pitfalls.
+Some requirements such as the need for a convex domain, as well as those derived from its calculation (the determination of the Lagrange Multipliers, specially at the boundaries, or the obtainment of the minimizer of the logarithmic function), make the usage of it a challenging tool.
+Concerning the convex domain requirement, Arroyo \& Ortiz~\cite{Arroyo2006} briefly discussed the existence of non-convex domains, and proposed some solutions to it.
+For instance, the possibility of replacing the Euclidean distance $\lVert x - x_a \rVert$ in the definition of the shape functions by the length of the shortest path contained within the domain connecting $x$ and $x_a$.
+Or by decomposing the non-convex domain into convex sub-domains.}
+
+\MODIFIED{Of course the requirement of convex domain is not exclusive from \textit{max-ent}, it also concerns to the remaining interpolation techniques in the \acrshort{mpm} and other meshfree methods.
+For instance, this topic has been extensively studied in the context of MLS-based meshfree methods, for instance visibility, diffraction, and constrained path criteria.
+These methods are directly applicable to local \textit{max-ent} approximation.
+}
+
+\MODIFIED{Despite these drawbacks, the results depicted in this manuscript will strengthen the motivation of its employment in order to mitigate typical \acrshort{mpm} problems such as cell-crossing or stress instabilities in a wide range of problem.}
 
@@
 It consists of the side impact of a moving elastic square.
-The square was 50 x 50 mm and modeled with the following elastic parameters :
+The square was 50 x 50 m and modeled with the following elastic parameters :
 \begin{itemize} 
-\item  Initial density : $20$
+\item  Initial density : $20 kg/m^3$
 \item  Poisson ratio : $0.3$
-\item  Elastic modulus : $10^5$
+\item  Elastic modulus : $0.1 MPa$
 \end{itemize}
@@
 The courant number is fixed to 0.1 during the whole simulation and $\text{LME}_{4.0}$ shape functions where used.
-The square initially move horizontally through the grid at $\text{V}_0 = 1.0$ until it hits an obstacle modelled as a set of nodes with  zero velocity prescribed.
+The square initially move horizontally through the grid at $\text{V}_0 = 1.0 m/s$ until it hits an obstacle modelled as a set of nodes with  zero velocity prescribed.
 The collision produce stress waves and cause the square to bounce back.}
@@
   }
-  \caption{Snapshots of velocity magnitudes in an elastic square impacted at a point on the right edge. The top row is for \acrshort{npc} updates and the bottom row is for \acrshort{fe} updates.}
+  \caption{Total energy (kinetic energy plus strain energy) evolution for the square. Solid line represent total energy, dashed line represent strain energy, and dotted line represent kinetic energy.}
   \label{fig:Energy_impact_square}
@@
 Different time and space discretisation techniques have been presented and their performance being compared agains other approaches in two benchmark problems.
-First, a novel time integration scheme for
-\acrshort{mpm} has been carried out. The \acrshort{npc} has been
-  shown to be a highly efficient alternative for demanding fast dynamics problems.
+First, a novel time integration scheme for \acrshort{mpm} has been carried out.
+The \acrshort{npc} has been shown to be a highly efficient alternative for demanding fast dynamics problems.
 In the literature, several approaches of the \acrshort{npc} are proposed in order to compete on accuracy with expensive implicit time integration algorithms.
-The main achievement of the proposed time discretisation has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.
+The main achievement of the proposed time discretisation has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme, \MODIFIED{with a minimal loose of energy as in highlighted in \ref{sec:Velocity-waves-elastic-domain} }.
 Also, the procedure employed to design the \acrshort{npc} algorithm opens the
 door to revisit a huge variety of time integration schemes developed
-originally for \acrshort{fem}, which can be implemented within a
-  \acrshort{mpm} framework with the suitable modifications. In
-addition to the implementation of enhanced time integration schemes, further
-research can be done in the analysis of the good performance of the algorithm within non-linear solutions, such as the coupling between different phases or the non-linear constitutive behaviour of the materials: the employment of this scheme to strengthen the localization capabilities of \acrshort{mpm} for viscoplastic materials is on the scope of this research line.
+originally for \acrshort{fem}, which can be implemented within a \acrshort{mpm} framework with the suitable modifications.
+In addition to the implementation of enhanced time integration schemes, further research can be done in the analysis of the good performance of the algorithm within non-linear solutions, such as the coupling between different phases or the non-linear constitutive behaviour of the materials: the employment of this scheme to strengthen the localization capabilities of \acrshort{mpm} for viscoplastic materials is on the scope of this research line.
 The comparison with traditional time schemes in the non-linear field will improve the formal understanding of the proposed methodology.

### 2020-09-09 LME-MPM.tex
Cambios I (9-9-2020)

@@
 \usepackage{cancel}
+\usepackage{ulem}
+%\usepackage{adjustbox}
+\usepackage{rotating}
+\usepackage{diagbox}
 
@@
     LME$_{\beta}$ Pareto set}
+}
+
+\newglossaryentry{LME-gamma}
+{
+  name=$\widehat{\gamma}$,
+  description={Dimensionless parameter to control the value of the
+    thermalization parameter $\beta$ of the \acrshort{lme} shape functions.}
+}
+
+\newglossaryentry{gamma-npc}
+{
+  name=$\gamma$,
+  description={Time integration parameter for the \acrshort{npc} algorithm}
 }
@@
 \newcommand{\CORRECTIONS}[1]{
-  \textcolor{red}{{#1}}
+  \textcolor{green}{{#1}}
 }
@@
   propagation in the large deformation regime is still challenging
-  under this approach due the incapability of the standard \acrshort{mpm} time
+  under this approach due \textcolor{green}{to} the incapability of the standard \acrshort{mpm} time
   integration scheme to filter spurious noises. To overcome it, we propose in this paper an explicit Predictor-Corrector time
@@
 has increased due to its ability to deal with large strain regime
-without suffering mesh distortion inaccuracies. One of the main
-  fields where this method is strong is the solid dynamics since the original time integration scheme proposed was the \acrfull{fe}~\cite{Sulsky1994}, carried out in an explicit manner.
-However, in this type or problems, the main instabilities of the original \acrshort{mpm} are even marked.
-
-On the one hand, the main source of instability occurs when
-material points cross cell boundaries. This provoked the development
+without suffering mesh distortion inaccuracies. One of the main fields where this method is \textcolor{green}{widely used} is solid dynamics.
+
+On one hand, the main source of instability occurs when
+material points cross cell boundaries. This \textcolor{green}{issue led to} the development
 of other interpolation techniques to overcome this limitation such as
@@
 (2008)\cite{Steffen2008}. This is similar to the difficulty
-encountered by the finite element methods due to element distortion.
+encountered by the finite element method due to element distortion.
 A more robust alternative is the \acrfull{ddmp} method proposed by Zhang {\it et al.}
@@
 unsatisfactory behaviour when particle/cell ratio
-decreases. Therefore \acrshort{ddmp} a large
-number of particles is needed for convergence~\cite{DHAKAL2016301}, what makes the method very expensive.
-\MODIFIED{To avoid the tensile instabilities quite commons in extensions, Sadeghirad {\it et al.} (2011) \cite{Sadeghirad_et_al_IJNME_2011} developed the \acrshort{cpdi} \cite{Sadeghirad_et_al_IJNME_2011}}.
-In recent years the employment of spline-lines as shape functions has gain popularity with the introduction of the B-Spline
-\acrshort{mpm} proposed by Tielen {\it et al.} (2017)~\cite{TIELEN2017265},
-this technique allows the employment of unstructured set of notes and
-particles. More recently, approximants derived from minimization has
-been introduced in to the \acrshort{mpm} framework with the \acrfull{ctls}
+decreases.
+Therefore \acrshort{ddmp} \textcolor{green}{requires} a large number of particles for convergence~\cite{DHAKAL2016301}, what makes the method \textcolor{green}{computationally} expensive.
+\textcolor{blue}{To avoid tensile instabilities that are quite common in extension, Sadeghirad {\it et al.} (2011) \cite{Sadeghirad_et_al_IJNME_2011} developed the \acrshort{cpdi} \cite{Sadeghirad_et_al_IJNME_2011}}.
+In recent years, the employment of spline-lines as shape functions has \textcolor{green}{gained} popularity with the introduction of the B-Spline
+\acrshort{mpm} proposed by Tielen {\it et al.} (2017)~\cite{TIELEN2017265}, \textcolor{green}{in which} unstructured set of \textcolor{green}{nodes} and
+particles \textcolor{green}{can be considered} . More recently, approximants derived from minimization \textcolor{green}{have}
+been introduced \textcolor{green}{into} the \acrshort{mpm} framework with the \acrfull{ctls}
 reconstruction proposed by Wobbes {\it et al.}
@@
 approximation schemes and provides a seamless transition between
-\acrshort{fem} and meshfree interpolations. The
-approximation scheme is based on a compromise between minimizing the
-width of the shape function support and maximizing the information
-entropy of the approximation. The \acrshort{lme} approximation
-may be regarded as a regularization, or \textit{thermalization}, of
+\acrshort{fem} and meshfree interpolations. The \textcolor{green}{\acrshort{lme}}
+approximation is based on a compromise between minimizing the
+width of the shape function support and maximizing the
+entropy of the approximation \textcolor{green}{\cite{Arroyo2006}}. The \acrshort{lme} approximation
+may be regarded as a regularization, or \textcolor{green}{(in analogy to statistical mechanics)} \textit{thermalization}, of
 Delaunay triangulation which effectively resolves the degenerate cases
-resulting from the lack of uniqueness or the triangulation. \acrshort{lme} basis functions possess many desirable properties for
+resulting from the lack \textcolor{green}{or}  uniqueness \textcolor{green}{of}  the triangulation. \acrshort{lme} basis functions possess many desirable properties for
 meshfree algorithms. First of all, they are entirely defined by the
@@
 satisfy the partition of unity property, and provide an exact
-approximation for related functions~\cite{Arroyo2006}.
+approximation \textcolor{green}{of affine}  functions~\cite{Arroyo2006}.
 Important contributions on the Maximum-Entropy have been made by Sukumar and coworkers~\cite{Sukumar15} with Cell-based techniques and the ones carried within the \acrfull{otm} method.
 The latter methodology has been proven to have a good performance under
-the dynamic regime by other researchers, being important the contributions of Li {\it et al.} (2012)~\cite{Li2012} and Navas {\it et al.}
+the dynamic regime being \textcolor{green}{worth mentioning} the contributions of Li {\it et al.} (2012)~\cite{Li2012} and Navas {\it et al.}
 (2018)~\cite{Navas:17b,Navas2018a} in the explicit regime and Navas
@@
 coworkers~\cite{Wriggers18} with implicit schemes. More
-recently, under \acrshort{mpm} framework, the work made by Wobbes {\it et
-  al.}(2020)~\cite{Wobbes2020}. The proposed research delves into the benefits of
-the regularization parameter, \gls{LME-beta}, and the analogy of the different obtained shape functions derive by the tuning of this parameter and the traditional \acrshort{mpm} ones.
+recently, under \acrshort{mpm} framework, the work made by Wobbes {\it et al.}(2020)~\cite{Wobbes2020}.
+The proposed research delves into the benefits of the regularization parameter, \gls{LME-beta}, and the analogy of the different shape functions \textcolor{green}{derived} by the tuning of this parameter and the traditional \acrshort{mpm} ones.
 
 The aforementioned techniques are devoted to mitigate the
-``grid crossing'' error. Nevertheless, in the presence of shock waves spurious,
-numerical noises appear despite of the employment of these
-techniques~\cite{Tran2019e}. These numerical inaccuracies, also known
+``grid crossing'' error. Nevertheless, in the presence of shock waves, spurious
+numerical noises \textcolor{green}{might} appear despite of the employment of these techniques~\cite{Tran2019e}. These numerical inaccuracies, also known
 as wiggles, arise due to inaccuracies in the time discretisation technique.
@@
 schemes which reduce the presence of high frequency noises by
-filtering them or increasing somehow the accuracy. One of the first attempts was
-the proposal of an implicit time integration scheme by Guilkey \&
-Weiss \cite{Guilkey_2003}. More recently Wang {\it et al.}
+filtering them or increasing somehow the accuracy.
+One of the first attempts was the proposal of an implicit time integration scheme by Guilkey \& Weiss \cite{Guilkey_2003}.
+More recently Wang {\it et al.}
 \cite{Wang_2016} mitigated these spurious noises by adding a non-viscous
@@
 proposed. It consists of an accommodation of the traditional \acrfull{npc} scheme, widely employed in Finite Element methods. This method
-has been chosen among other suitable alternatives as those proposed
+has \textcolor{green}{already} been chosen \textcolor{green}{in ~\cite{Navas2018a}}  among other suitable alternatives as those proposed
 by Wilson {\it et al.} (1972)~\cite{Wilson1972} or Chung \& Hulbert
@@
 performance dealing with solid dynamic problems under a meshfree
-framework in~\cite{Navas2018a}.  
-\MODIFIED{ Other well known source of energy dissipation and numerical noise is the presence of a non-trivial null space of the linear operator that maps particles values onto nodal values.
+framework.  
+\textcolor{blue}{Other well known source of energy dissipation and numerical noise is the presence of a non-trivial null space of the linear operator that maps particles values onto nodal values.
 It was earlier identified by Brackbill~\cite{BRACKBILL1988469} as ringing instability in the \acrfull{pic} method.
@@
 
-The article is organised as follows. Section \ref{sec:meshfree-methodology}
+The article is organised as follows : Section \ref{sec:meshfree-methodology}
 is devoted to describe the meshfree methodology adopted in this
@@
 \ref{sec:local-max-ent}. In Section
-\ref{sec:Application-linear-elasticity-dynamic-problems} applications
-to prove the numerical accuracy of the proposed approach are
+\ref{sec:Application-linear-elasticity-dynamic-problems}\textcolor{green}{,} applications to prove the numerical accuracy of the proposed approach are
 presented. Finally, conclusions and future research topics are exposed in Section \ref{sec:conclusions}.
@@
 compute the equilibrium equation. In what follows, we will adopt the
-following convention. Three kind of subscripts or superscripts are used
-within paper. The subscript $\square_p$ is used to define a particle
+following convention: \textcolor{blue}{Any vectorial field is defined with an overarrow as $\vec{\square}$}.
+Three kind of subscripts or superscripts are used within paper.
+The subscript $\square_p$ is used to define a particle
 variable. While the subscript $\square_I$ is reserved in this notation for denoting nodal
@@
 first and second contraction of a tensor, $\Div{\square}$ denotes the
-divergence operator, and finally $\Grad{\square}$ and $\GradS{\square}$
-denotes the gradient and its symmetric part. Einstein subscripts
-convention is adopted therefore repeated index means addition.
-Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are describe in subsection \ref{sec:derivation-mpm},\ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.
+divergence operator, and finally $\Grad{\square}$ and $\GradS{\square}$ denotes the gradient and its symmetric part.
+Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are \textcolor{green}{described} in subsection \ref{sec:derivation-mpm}, \ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.
 
@@
 
-In \acrshort{mpm} the continuum mechanics approach is considered. So on, we will consider a region \gls{domain} occupied by an elastic body like
+In \acrshort{mpm} the continuum mechanics approach is considered. We consider a region \gls{domain} occupied by an elastic body like
 the sketched in the figure~\ref{fig:Continuum-solid}, and \gls{contour} the boundaries of the domain defined by $\partial \Omega
@@
 field \gls{u} through the following set of governing equations and
-restrictions that must be satisfied. First (i) we will relate
-  global to local state by the \textit{compatibility equation}, where the the strain field \gls{strain} is extracted from \gls{u} is defined as:
+restrictions that must be satisfied. First (i) we relate global to local state by the \textit{compatibility equation} \textcolor{green}{where the strain field \gls{strain} is defined by}:
 \begin{equation}
@@
 \end{equation}
-together with essential or \acrfull{dbc} \gls{dirichlet-boundary}. We will further assume that 
-strains are 
-infinitesimal, therefore second order terms
-in the spatial derivatives can be neglected. From here, the
-stress field \gls{stress} will be considered the corresponding
+together with essential or \acrfull{dbc} \textcolor{green}{at} \gls{dirichlet-boundary}. We will further assume that 
+strains are infinitesimal. The stress field \gls{stress} is considered the corresponding
 conjugate variable for the strain field, being the one which
-satisfies (ii) the \textit{conservation of lineal momentum equation}:
+satisfies (ii) the \textit{conservation of \textcolor{green}{linear} momentum equation}:
 \begin{equation}
@@
 \end{equation}
-together with the natural of \acrfull{nbc} \gls{neumann-boundary}.  An aditional component will be (iii) the constitutive equation as a linear
-application from $\mathbb{R}^n$ to $\mathbb{R}^n$, which relate stress and strain increments as,
+together with the natural of \acrfull{nbc} \textcolor{green}{at} \gls{neumann-boundary}.
+An \textcolor{green}{additional} component \textcolor{green}{is} (iii) the constitutive equation which relates stress and strain increments as,
 \begin{equation}
   \label{eq:Constitutive-equation}
-\tens{\sigma} = \tens{D} \colon \tens{\varepsilon}.
-\end{equation}
-In this research, plane strain Linear Elasticity has been
-  considered. Thus the constitutive tensor, \tens{D}, is the well
-  known linear elastic one. The final equation of the set is (iv) the mass
-conservation, which can be obtained by setting to zero the total derivative of the density field,
+\tens{\textcolor{green}{\Delta} \sigma} = \tens{D} \colon \tens{\textcolor{green}{\Delta} \varepsilon}.
+\end{equation}
+In this research, plane strain linear elasticity \textcolor{green}{is} considered. The final equation of the set is (iv) the mass conservation, which can be \textcolor{green}{expressed by} 
 \begin{equation}
   \label{eq:Rho-material-derivative}
-  \frac{D \rho}{D t} = \dot{\rho} + \rho \Div{\vec{v}} = 0.
+    \dot{\rho} + \rho \Div{\vec{v}} = 0.
 \end{equation}
@@
 \end{equation}
-in which the Cauchy sequences are convergent in \gls{domain} as well:
+\textcolor{green}{where $\vec{u}^{\psi} \in \mathcal{H}^1$ means that}
 \begin{equation}
@@
    \tens{\varepsilon}^{\psi}}.
-\end{equation}\\
+\end{equation}
 %%%%%%%%%%%%%%%%%%%%%
@@
 
-\MODIFIED{First, the velocity field and the virtual displacements fields are discretised in a finite set of nodes $\textbf{X} = \{ \vec{x}_I, I \in \mathcal{B} \} \subset \mathbb{R}^n$, where $\mathcal{B} = 1, \ldots, N_I$.
-The continuum field can be reconstructed with the help of nodal values and an appropriate interpolation function $N_I(\vec{x})$.
+\textcolor{blue}{First, the velocity field and the virtual displacements fields are discretised in a finite set of nodes $\textbf{X} = \{ \vec{x}_I, I \in \mathcal{B} \} \subset \mathbb{R}^{2}$, where $\mathcal{B} = 1, \ldots, n_I$.
+An approximation of the continuum field can be obtained with the help of nodal values and an appropriate interpolation functions $N_I(\vec{x})$.
 Also spatial derivatives of those quantities, such as gradients and divergences, are computed through the support of the background set of nodes as}
@@
     \label{eq:grad_variable_reconstruction}
-    \Grad{\varphi}(\vec{x}) &= \sum_{I\ \in\ \mathcal{B}} \Grad{N_I(\vec{x})}\ \varphi_I
+    \Grad{\varphi}(\vec{x}) &= \sum_{I\ \in\ \mathcal{B}} \varphi_I\ \otimes \Grad{N_I(\vec{x})}
 \end{align}
-\MODIFIED{Secondly, the continuum \gls{domain} is discretised with a finite set of material points (also denominated particles the manuscript) $\hat{\Omega} = \{ \vec{x}_p, p \in \mathcal{C} \} \subset \Omega$, where $\mathcal{C} = 1, \ldots, N_p$.
-Any particle field such as position, velocity, mass, volume and stress denoted by $\vec{x}_p$, $\vec{v}_p$, $m_p$, $V_p$ and $\tens{\sigma}_p$ respectively are assigned to each material point.
-Furthermore, any particle field $\varphi_p$ can be reconstructed within the nodes in the neighbourhood of each particle, $\mathcal{B}_p \subset \mathcal{B}$, and evaluating the interpolation function in the position of each particle as}
+\textcolor{blue}{Secondly, the continuum \gls{domain} is discretised with a finite set of material points (also denominated particles the manuscript) $\hat{\Omega} = \{ \vec{x}_p, p \in \mathcal{C} \} \subset \Omega$, where $\mathcal{C} = 1, \ldots, n_p$.
+Any particle field such as position, velocity, mass, volume and stress denoted by $\vec{x}_p$, $\vec{v}_p$, $m_p$, $V_p$ and $\tens{\sigma}_p$, respectively, are assigned to each material point.
+Furthermore, any particle field $\varphi_p$ can be approximated within the nodes in the neighbourhood of each particle, $\mathcal{B}_p \subset \mathcal{B}$, and evaluating the interpolation function in the position of each particle as}
 \begin{align}
@@
 \varphi_p &= \sum_{I\ \in\ \mathcal{B}_p} N_I(\vec{x}_p)\ \varphi_I \\
-\Grad{\varphi_p} &= \sum_{I\ \in\ \mathcal{B}_p} \Grad{N_I(\vec{x}_p)}\ \varphi_I
+\Grad{\varphi_p} &= \sum_{I\ \in\ \mathcal{B}_p} \varphi_I \otimes \Grad{N_I(\vec{x}_p)}
 \end{align}
-\MODIFIED{Regarding numerical integration, the material derivatives are evaluated using the Riemann integral definition \cite{Riemann_1854} applied to a finite set of points which associated volumes $V_p$ are interpreted as quadrature weights.}
+\textcolor{blue}{The integrals appearing in the weak form \eqref{eq:BalanceMomentum_wf} are evaluated by means of the Riemann integral \cite{Riemann_1854} applied to a finite set of points with associated volumes $V_p$ interpreted as quadrature weights.}
 \begin{equation}
@@
 \end{equation}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \caption{Description of the spatial discretisation for domain presented in the
-    figure~\ref{fig:Continuum-solid}. Blue mesh represent the
+    figure~\ref{fig:Continuum-solid}. Blue mesh represents the
     background computational support, and the red mesh conforms the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\MODIFIED{Let us illustrate the procedure described above by fully developing the term of the acceleration forces in \eqref{eq:BalanceMomentum_wf}.
+\textcolor{blue}{Let us illustrate the procedure described above by fully developing the term of the acceleration forces in \eqref{eq:BalanceMomentum_wf}.
 Employing the definition \eqref{eq:variable_reconstruction}, the velocity and virtual displacement fields can be approximated within its nodal values.
@@
 \end{equation}
-\MODIFIED{Rearranging terms in \ref{eq:particle_acceleration_forces_I}, and subtracting from the integral those discrete variables, the following expression is obtained}
+\textcolor{blue}{Rearranging terms in \ref{eq:particle_acceleration_forces_I} and keeping in mind that $\vec{u}_I^{\psi}$ and $\vec{v}_J$ are nodal evaluations of $\vec{u}^{\psi}$ and $\vec{v}$, respectively,  the following expression is obtained}
 \begin{equation}
@@
 \end{equation}
-\MODIFIED{Now, introducing the particle integral definition \eqref{eq:particle_riemann_integral} to compute the integral of \eqref{eq:particle_acceleration_forces_II}, and simplifying the it, is possible to achieve a discrete expression o the acceleration forces term as}
+\textcolor{blue}{and by means of \eqref{eq:particle_riemann_integral}, and keeping in mind that expression \eqref{eq:particle_acceleration_forces_II} is for any $\vec{u}^{\psi} \in
+\mathcal{H}^1_0$, the following discrete expression of the acceleration can be derived}
 %%%%%%%%%%%%%%%%
@@
 \begin{split}
-&\sum_{I,J\ \in\ \mathcal{B}} \vec{u}_I^{\psi} \cdot \sum_{p\ \in\ \mathcal{C}} N_{Ip}\ \rho_p\ N_{Jp}\ V_p\ \frac{d\vec{v}_J}{dt} = \\
-&= \sum_{I,J\ \in\ \mathcal{B}} \vec{u}_I^{\psi} \cdot \sum_{p\ \in\ \mathcal{C}} N_{Ip}\ m_p\ N_{Jp}\ \frac{d\vec{v}_J}{dt} = \\
+&\sum_{I,J\ \in\ \mathcal{B}}\ \sum_{p\ \in\ \mathcal{C}} N_{Ip}\ \rho_p\ N_{Jp}\ V_p\ \frac{d\vec{v}_J}{dt} = \\
+&=\sum_{I,J\ \in\ \mathcal{B}}\ \sum_{p\ \in\ \mathcal{C}} N_{Ip}\ m_p\ N_{Jp}\ \frac{d\vec{v}_J}{dt} = \\
 &= \tens{m}_{IJ}\ \frac{d\vec{v}_J}{dt}
@@
 %%%%%%%%%%%%%%%%
-\MODIFIED{$\tens{m}_{IJ}$, is the nodal mass matrix, and $N_{Ip}, N_{Jp}$ are the interpolation functions for nodes $I,J$ evaluated in the position of each particle $p$.
-In order to improve the computational efficiency and stability, the nodal mass matrix can be substituted by the lumped mass matrix $\tens{m}_{IJ}^{lumped}$.
+\textcolor{blue}{Where $\tens{m}_{IJ}$, is the nodal mass matrix, and $N_{Ip}, N_{Jp}$ are the interpolation functions for nodes $I,J$ evaluated at the position of each particle $p$.
+In order to improve computational efficiency and stability, the nodal mass matrix can be substituted by the lumped mass matrix $\tens{m}_{IJ}^{lumped}$.
 The remaining terms of \eqref{eq:BalanceMomentum_wf} are obtained within a similar procedure and can be found in literature, see for instance \cite{Zhang_book_2016}.
-So equation \eqref{eq:BalanceMomentum_wf} has been discretised as}
+Therefore equation \eqref{eq:BalanceMomentum_wf} can be discretised as}
 %%%%%%%%%%%%%%%%%%%%%
@@
 \label{eq:BalanceMomentum_wf_discretized}
-    \tens{m}_{IJ}\ \frac{d\vec{v}_J}{dt} = \sum_{p\ \in\ \mathcal{C}} - \tens{\sigma}_{p} \cdot \Grad{N_{Ip}} \frac{m_p}{\rho_p} + N_{Ip}\ \vec{b}_{p}\ m_p  + N_{Ip}\ \vec{t}^s_{p}\ m_p h^{-1}
+    \tens{m}_{IJ}\ \frac{d\vec{v}_J}{dt} = \sum_{p\ \in\ \mathcal{C}} - \underbrace{\tens{\sigma}_{p} \cdot \Grad{N_{Ip}} V_p}_{f^{int}_I}\ + \underbrace{N_{Ip}\ \vec{b}_{p}\ m_p  +\ N_{Ip}\ \vec{t}_{p}\ V_p\ h^{-1}}_{f^{ext}_I}
 \end{equation}
 %%%%%%%%%%%%%%%%%%%%%
-\MODIFIED{Where $h$ is the soil thickness in 2D, and $\tens{\sigma}_{p} = \tens{\sigma}_{p}(\tens{\varepsilon}_{p})$
-is the particle $p$ stress field, which can be integrated employing
-the suitable constitutive model.
-The particle strain field is approximated thorough the time integration of the rate of stress tensor, which is computed employing the velocity at the background set of nodes by the equation}
+\textcolor{blue}{Where $h$ is the solid thickness in 2D and $\tens{\sigma}_{p} = \tens{\sigma}_{p}(\tens{\varepsilon}_{p})$
+is the stress field at particle $p$, which can be obtained after considering a suitable constitutive model.
+The particle strain field is approximated thorough the time integration of the rate of strain tensor, that is computed employing the velocity at the background set of nodes by means of the equation}
 %%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%
-Finally, mass conservation is guaranteed by enforcing the null value of
-the material derivative of the density field $\frac{D \rho}{D t} = 0$.
-This leads to a suitable equation to update the density field:
+Finally, mass conservation is guaranteed by \textcolor{green}{means of \eqref{eq:Rho-material-derivative} which can be rewritten in terms of the rate of strain tensor $\dot{\tens{\varepsilon}}$ as}
 \begin{equation}
@@
 \end{equation}
-Observe that to solve the equation \eqref{eq:BalanceMomentum_wf_discretized}, a second order time integration scheme is required. Therefore, time is
-discretised into a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$ is the total number of time steps.
+\textcolor{green}{Equation \eqref{eq:BalanceMomentum_wf_discretized} is a second order ordinary differential equation in time and a time integration scheme is required.} \textcolor{green}{To this end}, time is discretised into a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$ is the total number of time steps.
 Once the nodal equilibrium equation is solved, the values at the nodes are interpolated back into the particles, which are advected
@@
 Traditionally, Eqs. \eqref{eq:BalanceMomentum_wf_discretized} and ~\eqref{eq:Updated_Lagrangian},
-are solved with an explicit forward Euler algorithm. In the following subsection, this and the proposed schemes are described.
+are solved with an explicit forward Euler algorithm. In the following subsection, this \textcolor{green}{well known algorithm} and the proposed schemes are described.
 
@@
 
-As was stated previosuly, an explicit forward Euler algorithm has been utilized widely within the \acrshort{mpm} methodology. This scheme has been described in detail by many researchers
+As stated previously, an explicit forward Euler algorithm has been utilized widely within the \acrshort{mpm} methodology. This scheme has been described in detail by many researchers
 \cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and can be sketched by the scheme of the figure~\ref{fig:MPM_algorithm}.
@@
 first publication on \acrshort{mpm} \cite{Sulsky1994}, the nodal acceleration
-was employed to update the particles as
+was \textcolor{green}{considered} to update the particles \textcolor{green}{by}
 \begin{equation}
   \label{eq:Sulsky-1994-UL-v}
-  \vec{v}_p^{k+1} = \vec{v}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ N_{Ip}^{k}\ \vec{a}_{I}^{k},
+  \vec{v}_p^{k+1} = \vec{v}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ N_{Ip}\ \vec{a}_{I}^{k},
 \end{equation}
@@
   \label{eq:Sulsky-1994-UL-x}
-  \vec{x}_p^{k+1} = \vec{x}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ N_{Ip}^{k}\ \vec{v}_{I}^{k}.
-\end{equation}
-However, as Andersen (2009)\cite{thesis_Andersen_2009} pointed out, this algorithm has been shown to be numerically unstable due to that
-$\vec{f}_I^{int,k}$ can be infinite for an infinitesimal nodal mass
-$\tens{m}_I$. This issue may lead to numerical problems when nodal acceleration
-is obtained in the evaluation of the Eqs. \eqref{eq:Sulsky-1994-UL-x} and \eqref{eq:Sulsky-1994-UL-v}. Hence, a
+  \vec{x}_p^{k+1} = \vec{x}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ N_{Ip}\ \vec{v}_{I}^{k}.
+\end{equation}
+However, as Andersen (2009)\cite{thesis_Andersen_2009} pointed out, this algorithm has been shown to be numerically unstable due to \textcolor{green}{the fact} that nodal forces can be infinite for an infinitesimal nodal mass $\tens{m}_I$.
+This issue may lead to numerical problems when nodal acceleration is obtained in the evaluation of the Eqs.
+\eqref{eq:Sulsky-1994-UL-x} and \eqref{eq:Sulsky-1994-UL-v}.
+Hence, a
 corrected version of this algorithm was proposed by Zhang {\it et al.}
@@
   \label{eq:Zhang-2016-UL-x}
-  \vec{x}_p^{k+1} = \vec{x}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ \frac{N_{Ip}^{k}\ \vec{p}_{I}^{k}}{\tens{m}_I}, 
+  \vec{x}_p^{k+1} = \vec{x}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ \frac{N_{Ip}\ \vec{p}_{I}^{k}}{\tens{m}_I}, 
 \end{equation}
@@
   \label{eq:Zhang-2016-UL-v}
-  \vec{v}_p^{k+1} = \vec{v}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ \frac{N_{Ip}^{k}\ \vec{f}_{I}^{k}}{\tens{m}_I}.
+  \vec{v}_p^{k+1} = \vec{v}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\ \frac{N_{Ip}\ \vec{f}_{I}^{k}}{\tens{m}_I}.
 \end{equation}
@@
 (1993)\cite{Geranlized_alpha_1993}, but with the particularity that
-the acceleration is evaluated both in the beginning and the end of the
-time step.
+the acceleration is evaluated both \textcolor{green}{at} the beginning and \textcolor{green}{at} the end of the time step.
 \begin{equation}
   \label{eq:Tran-2019-GA-v}
-  \vec{v}_p^{k+1} = \vec{v}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\  N_{Ip}^{k}\ \left[(1 - \gamma)\ \vec{a}_I^{k} +
+  \vec{v}_p^{k+1} = \vec{v}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\  N_{Ip}\ \left[(1 - \gamma)\ \vec{a}_I^{k} +
     \gamma\ \vec{a}_I^{k+1} \right],\\
@@
 \label{eq:Tran-2019-GA-x}
-  \vec{x}_p^{k+1} = \vec{x}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} N_{Ip}^{k} \left[ \Delta t\ \vec{v}_{I}^{k}+ \Delta t^2\left( (\frac{1}{2} - \beta)\
+  \vec{x}_p^{k+1} = \vec{x}_p^{k} + \sum_{I\ \in\ \mathcal{B}_p} N_{Ip} \left[ \Delta t\ \vec{v}_{I}^{k}+ \Delta t^2\left( (\frac{1}{2} - \beta)\
     \vec{a}_{I}^{k} + \beta\ \vec{a}_{I}^{k+1} \right) \right],
@@
   \label{eq:Tran-2019-GA-a}
-  \vec{a}_p^{k+1} = \sum_{I\ \in\ \mathcal{B}_p} N_{Ip}^{k}\ \vec{a}_{I}^{k+1}.
+  \vec{a}_p^{k+1} = \sum_{I\ \in\ \mathcal{B}_p} N_{Ip}\ \vec{a}_{I}^{k+1}.
 \end{equation}
@@
 In this section, an explicit predictor-corrector time integration
-scheme is proposed. It is based on the Newmark central differences
-explicit scheme, which is also referred to as a-form 
-$\gamma = 0.5$ and $\beta = 0$. This method is devoted to solve a system of equations of the type
+scheme is proposed, \textcolor{green}{which} is based on the Newmark central differences explicit scheme. This method is devoted to solve  system of equations of the type
 \begin{equation*}
@@
 within the \acrshort{mpm} framework in a similar manner that the one
-proposed by Tran~\textit{et al.}~\cite{Tran2019e}. By using the predictor definition, it is possible to calculate nodal velocities and update particles position employing nodal values
+proposed by Tran~\textit{et al.}~\cite{Tran2019e}. By using the predictor \textcolor{green}{step}  it is possible to calculate nodal velocities and update particles position employing nodal values
 of velocity and acceleration.
@@
 \cite{Xiaojian94}. The ``classic'' \acrfull{npc} algorithm starts with a
-predicted value of the nodal velocities at the $(k+1)$th time step, denoted by $\vec{\tilde{v}}_I^{k+1}$, which is calculated as follows:
+predicted value of the nodal velocities at the $(k+1)$th time step, denoted by $\vec{v}_{I}^{pred}$, which is calculated as follows:
 \begin{equation}
   \label{eq:Predictor-velocity-I}
-  \vec{\tilde{v}}_I^{k+1} = \vec{v}_I^k + (1 - \gamma)\ \Delta t\ \vec{a}_I^k.
+  \vec{v}_{I}^{pred} = \vec{v}_I^k + (1 - \gamma)\ \Delta t\ \vec{a}_I^k.
 \end{equation}
@@
 The \textit{user-defined}
-parameter $\gamma \geq 0$ that appears in In \eqref{eq:Predictor-velocity-I}, influences both the predictor accuracy
+parameter $\gamma \geq 0$ that appears in \sout{In} \eqref{eq:Predictor-velocity-I}, influences both the predictor accuracy
 and the stability of the algorithm. As pointed out Liu
@@
 $ 0 < \gamma \leq 0.25$.
-
-To accommodate this step to \acrshort{mpm} framework, it is necessary to get
-the nodal values of the velocity and acceleration throughout a variational
-recovery process where particles quantities are transferred to the
-mesh nodes. This technique arises as a generalization of the super-convergent recovery
-procedures described by Zienkiewicz \& Zhu \cite{ZZ1992_I} (\textit{ZZ})
-in the context of \acrshort{fem}. In \acrshort{mpm}, Gauss quadratures are not employed. However, 
-integrals are computed following the Riemann integral definition,
-where each component of the summation corresponds to a particle of the
-discretisation. Also Bardenhagen \& Kober \cite{Bardenhagen2004}
-proved that through this information-transference technique mass and momentum are conserved. So for a general particle variable $\Phi_p$, employing the
-\textit{ZZ} technique, it is possible to get its nodal homologous $\Phi_I$  as:
+To accommodate this step to \acrshort{mpm} framework, it is necessary to get the nodal values of the velocity and acceleration throughout a variational recovery process where particles quantities are transferred to the mesh nodes.
+This technique arises as a generalization of the super-convergent recovery
+procedures described by Zienkiewicz \& Zhu \cite{ZZ1992_I} (\textit{ZZ}) in the context of \acrshort{fem}.
+Bardenhagen \& Kober \cite{Bardenhagen2004} proved that through this information-transference technique mass and momentum are conserved.
+For a general particle variable $\Phi_p$ it is possible to get its nodal homologous $\Phi_I$ \textcolor{green}{by means of the \textit{ZZ} technique}  as:
 \begin{equation}
@@
  procedure described in the equation \eqref{eq:Variational-recovery}
- is employed, obtainen the following expression:
+ is employed, \textcolor{green}{obtaining} the following expression:
  \begin{equation}
    \label{eq:Predictor-velocity-II}
-   \vec{\tilde{v}}_I^{k+1} = \sum_{p\ \in\ \mathcal{C}} \underbrace{\frac{N_{Ip}^{k} m_p
-       \vec{v}_p^k}{m_I}}_{\vec{v}_I^{k}} + (1 - \gamma)\ \Delta t\  \underbrace{\frac{N_{Ip}^{k} m_p \vec{a}_p^k}{m_I}}_{\vec{a}_I^{k}}.
- \end{equation}
-Nonetheless this way of computing the predictor stage can introduce
-instabilities due to numerical cancellation likewise the original
-Sulky algorithm. Thankfully, this can be avoided easily by the
-equivalent formulation proposed as follows: 
+   \vec{v}_{I}^{pred} = \sum_{p\ \in\ \mathcal{C}} \underbrace{\frac{N_{Ip} m_p
+       \vec{v}_p^k}{m_I}}_{\vec{v}_I^{k}} + (1 - \gamma)\ \Delta t\  \underbrace{\frac{N_{Ip} m_p \vec{a}_p^k}{m_I}}_{\vec{a}_I^{k}}.
+ \end{equation}
+\textcolor{green}{However} this way of computing the predictor stage can introduce instabilities due to numerical cancellation likewise the original Sulky algorithm.
+This \textcolor{green}{issue} can be avoided easily by the equivalent formulation inspired in the \textit{ZZ} technique,
 \begin{equation}
   \label{eq:Predictor-velocity-II}
-  \vec{\tilde{v}}_I^{k+1} =  \sum_{p\ \in\ \mathcal{C}} \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}.
-\end{equation}
-This way of computing the nodal predictor is both numerically stable
+  \vec{v}_{I}^{pred} =  \sum_{p\ \in\ \mathcal{C}} \frac{ N_{Ip} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}.
+\end{equation}
+This way of computing the nodal predictor is numerically stable
 and minimize the computational effort. Once nodal velocities are
-obtained, the \acrshort{dbc} are imposed over \gls{dirichlet-boundary}. And in the
-following, the ``classic'' \acrshort{mpm} algorithm continues to reach to the
-equilibrium equation \eqref{eq:BalanceMomentum_wf_discretized}. Next, the
-\textit{corrector} stage is introduced. As nodal
-velocities were obtained earlier, this step is computed in the same way as
-in \acrshort{fem},
+obtained, the \acrshort{dbc} are imposed over \gls{dirichlet-boundary}.
+Next the \textit{corrector}  \textcolor{green}{step} is introduced.
+\textcolor{green}{Predicted} nodal velocities obtained in \eqref{eq:Predictor-velocity-II}, \textcolor{green}{are now corrected by the equation}
 \begin{equation}
   \label{eq:Corrector-velocity}
-  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}.
-\end{equation}
-Finally updated particle accelerations, velocities and positions are updated as,
+  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I}.
+\end{equation}
+Finally particle accelerations, velocities and positions are updated as,
 \begin{align}
-  \label{eq:Update-lagrangian-pce}
-        &\vec{a}_p^{k+1} = \sum_{I\ \in\ \mathcal{B}_p} \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      \label{eq:Update-lagrangian-pce-a}    
+        &\vec{a}_p^{k+1} = \sum_{I\ \in\ \mathcal{B}_p} \frac{N_{Ip}\vec{f}_{I}^{k}}{\tens{m}_I}\\
+        \label{eq:Update-lagrangian-pce-v}  
       &\vec{v}_p^{k+1} = \vec{v}_p^n + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\
-        \frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+        \frac{N_{Ip}\
+        \vec{f}_{I}^{k}}{\tens{m}_I}\\
+        \label{eq:Update-lagrangian-pce-u}
       &\vec{x}_p^{k+1} = \vec{x}_p^n + \sum_{I\ \in\ \mathcal{B}_p} \Delta t\
-         N_{Ip}^k\ \vec{v}_{I}^{k} +
-        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k}.
+         N_{Ip}\ \vec{v}_{I}^{k} +
+        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}\
+        \vec{f}_{I}^{k}}{\tens{m}_I}.
 \end{align}
-Notice that particle displacements are computed using the corrected
-nodal velocities as well as the accelerations with the velocities
-of the predictor. However, particle velocities and accelerations
-are computed using the corrected velocities. Therefore here we share similarities
-with the \textit{leapfrog scheme} where position is not updated at
-full time step, but the velocity is updated at half time steps. Notice
-also that, with this approach, the calculation of nodal momentum values
-are not required.
+\textcolor{blue}{In our proposed scheme, accelerations \eqref{eq:Update-lagrangian-pce-a} and velocities \eqref{eq:Update-lagrangian-pce-v} are computed with information coming from the predictor step.
+On the other hand, positions \eqref{eq:Update-lagrangian-pce-u} are evaluated with information coming from the corrector step in the velocity term, while acceleration term introduces information from the corrector.} Therefore it share clear similarities with the \textit{leapfrog scheme} \cite{Zhang_book_2016}, where position is not updated at full time step, but the velocity is updated at half time steps.
+Notice also that, with this approach, the calculation of nodal momentum values are not required.
 Due to its simplicity, the proposed scheme can be implemented with minor modifications over the standard forward Euler.
-The full implementation is summarized in the algorithm~\ref{algo:1}.
+The full implementation is summarized in the algorithm \ref{alg:the_npc_alg}.
 
 \begin{algorithm}
-  \floatname{algorithm}{Algorithm 1}
-  \renewcommand{\thealgorithm}{}
-  \caption{\acrfull{npc} scheme} \label{algo:1}
+\caption{\acrfull{npc} scheme}
+\label{alg:the_npc_alg}
   \begin{algorithmic}[1]
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Explicit Newmark Predictor}:\\
+    \STATE \textbf{Explicit Newmark Predictor}.\\
     \begin{equation*}
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Impose essential boundary conditions}:\\
+    \STATE \textbf{Impose essential boundary conditions}.\\
     At the fixed boundary, set $\vec{v}_{I}^{pred} = 0$. 
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Update the density field}:
+    \STATE \textbf{Update the density field}.
     \begin{equation*}
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Balance of forces calculation}:\\
+    \STATE \textbf{Balance of forces calculation}.\\
     Calculate the total grid nodal forces by evaluating the right hand side of 
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Explicit Newmark Corrector}:
+    \STATE \textbf{Explicit Newmark Corrector}.
     \begin{equation*}
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \STATE \textbf{Update particles lagrangian quantities}:
+    \STATE \textbf{Update particles lagrangian quantities}.
     \begin{align*}
@@
 The popularity of the \acrshort{mpm} has increased notoriously during
-the recent years due to its ability to deal with large strain problems
-without mesh distorsion issues inherent to mesh based methods like
-\acrshort{fem}, see Wi{\c{e}}ckowski \cite{Wieckowski2004}. However, in the simulations
-made with the original \acrshort{mpm}, numerical noises appear when particles
-cross the cell boundaries. Solving this issue is the main goal of the employment of the \acrshort{lme} shape functions.
-
+the recent years due to its ability to deal with large strain problems without mesh distorsion issues inherent to mesh based methods like \acrshort{fem}, see Wi{\c{e}}ckowski \cite{Wieckowski2004}.
+However, in the simulations
+made with the original \acrshort{mpm}, numerical noises appear when particles cross the cell boundaries. Solving this issue is the main goal of the employment of the \acrshort{lme} shape functions.
 \acrfull{lme} approximation schemes were
-first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} and has been
-recently tested under \acrshort{mpm} framework by Wobbes {\it et al.}
-(2020)\cite{Wobbes2020}. The simulations presented in \cite{Wobbes2020} of \acrshort{mpm}
-within \acrshort{lme} show considerably more accurate stress
-approximations than traditional \acrshort{mpm} schemes. However, 
-how the regularization parameter $\beta$ affects to the accuracy and
-stability of the solution is not assessed deeply in that research.
+first introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} and has been recently tested under \acrshort{mpm} framework by Wobbes {\it et al.} (2020)\cite{Wobbes2020}.
+The simulations presented in \cite{Wobbes2020} of \acrshort{mpm} within \acrshort{lme} show considerably more accurate stress approximations than traditional \acrshort{mpm} schemes.
+However, how the regularization parameter $\beta$ affects to the accuracy and stability of the solution is not assessed deeply in that research.
 The tuning of this $\beta$ parameter allows to make the comparison of the accuracy against analogous traditional \acrshort{mpm} shape function.
@@
 
-Taking the definition of entropy as a measure of how uncertainty a
-random variable is averaged on all its possible outcomes. And adopting
-the Shannon's entropy as the starting point:
+\textcolor{green}{Following \cite{Arroyo2006}, entropy of a discrete random variable can be defined as the} uncertainty \textcolor{green}{of the} random variable.
+\textcolor{green}{A measure of this uncertainty can be obtained by means of Shannon's entropy}:
 \begin{equation}
   \label{eq:Shannon-entropy}
-  H(p_1(\vec{x}),\ldots,p_n(\vec{x})) = -\sum^{N_n}_{I=1}{p_I(\vec{x})\log p_I }
-\end{equation}
-where $p_I(\vec{x})$ is the probability, equivalent to the mentioned
-shape function $N_I(\vec{x})$, satisfying both the zeroth and
-first-order consistency. The least-biased approximation scheme is
+  H(p_1,\ldots,p_n) = -\sum^{N_n}_{I=1}{p_I\ \log p_I }
+\end{equation}
+where $p_I$ \textcolor{green}{stand for probability of the random variable outcomes.
+By interpreting these probabilities as the shape functions $N_I(\vec{x})$ of an approximation scheme, equation \eqref{eq:Shannon-entropy} can be regarded as a measure of the uncerteinty of the approximation.} \textcolor{green}{Thus, according to Jaynes's principle of maximum entropy \cite{Jaynes1957},} the least-biased approximation scheme is
 given by
@@
 \end{align*}
-To reach to a compromise between two competing objectives, a Pareto set is defined by \cite{Arroyo2006} as,
+To reach to a compromise between \textcolor{green}{the} two competing objectives, a Pareto set is \textcolor{green}{considered}  \cite{Arroyo2006}
 \begin{align*}
@@
 \end{eqnarray}
-The regularization parameter $\beta$ of \acrshort{lme} shape functions may be
-controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
-\cite{Arroyo2006}, where $h$ is defined as a measure of the nodal
+The regularization parameter $\beta$ of \acrshort{lme} shape functions may be controlled by adjusting a dimensionless parameter\footnote{\textcolor{blue}{To avoid confusion with the \gls{gamma-npc} parameter of the \acrshort{npc}, the dimensionless parameter defined by Arroyo \& Ortiz \cite{Arroyo2006} as $\gamma$ will be represent by \gls{LME-gamma} to preserve as much as possible the original notation.}}, \textcolor{green}{$\widehat{\gamma}=\beta h^2$} \cite{Arroyo2006}, where $h$ is defined as a measure of the nodal
 spacing. 
 Since $N_I$ is defined in the entire domain, in practice, the
-function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance,
-10$^{-6}$ in this research,  would ensure a reasonable range of
-neighbours (see \cite{Arroyo2006} for details).
-This tolerance defines the limit values of the influence radius and is used thereafter to
-find the neighbour nodes of a given integration point.
+function $\exp(-\beta \vec{r} )$ truncated  by  a given tolerance, 10$^{-6}$ in this research,  would ensure a reasonable range of neighbours (see \cite{Arroyo2006} for details).
+This tolerance defines the limit values of the influence radius and is used thereafter to find the neighbour nodes of a given integration point.
 An additional remark is that, analogous to alternative non-polynomial meshfree basis functions, the \acrshort{lme} approximation scheme requires more than $d+1$ nodes to determine the values of the shape functions as well as their derivatives at any point in the convex hull of the nodal set, where $d$ is the dimension of the problem.
@@
 This interpolation technique avoids important shortcomings when using
-\acrshort{gimp} or B-Spline \acrshort{mpm} regarding the computational domain boundaries
-(see Steffen {\it et al.} (2008)\cite{Steffen2008b}), which are related to the
-additional considerations in the application of the boundary
+\acrshort{gimp} or B-Spline \acrshort{mpm} regarding the computational domain boundaries (see Steffen {\it et al.} (2008)\cite{Steffen2008b}), which are related to additional considerations in the application of the boundary
 conditions.
@@
 Some researchers have solved this problem with the so called ``extra'' or ``ghost'' nodes.
-These nodes require especial treatment, similar
-to those employed in the \acrfull{sph}, for
-further details see Liu \& Liu (2003)\cite{Liu2003}. The approach here
-described does not requires the employment of this artifices.
+These nodes require especial treatment, similar to those employed in the \acrfull{sph}, for
+further details see Liu \& Liu (2003)\cite{Liu2003}. The approach here described does not require the employment of this artifices.
 Due to the \acrshort{fem}-compatibility, the \acrshort{lme} shape
-function is degenerated to linear finite element shape function if
-$d+1$ neighbouring nodes are chosen as the support, where $d$ is the
-number of dimensions in the problem.
+function is degenerated to linear finite element shape function if $d+1$ neighbouring nodes are chosen as the support, where $d$ is the number of dimensions in the problem.
+\textcolor{blue}{Figure \ref{fig:LME_MPM} shows that larger values of the parameter $\beta$ make the solution to tend to the linear \acrshort{fem} solution as the athermal limit is reached \cite{Arroyo2006}}.
 Ullah {\it et al.} \cite{Augarde_2013} took advantage of the \acrshort{lme} \acrshort{fem}-compatibility to couple the \acrfull{efgm} and \acrshort{fem} for linear elasticity and for problems with both material and geometrical non-linearities.
-Furthermore, with a conveniently
-adopted \textit{regularization} parameter it is possible to get a 
-\acrshort{gimp}-like shape function. Finally \acrshort{sph}-like
-behaviour can be obtained for lower values of $\gamma$ since the
-support of the shape function is drastically increased, and therefore
-\textit{smoother} solutions are obtained. See \cite{Navas2016} for an
-application of this capability, where oscillations due to
-excess of pore water pressure in consolidation problems are smoothed
-out by using this technique. The employment of smoothing algorithms is
-also straightforward in the fluid-solid interaction problems
-\cite{Arduino_2018}. A proof of this statements is observed in
-figure~\ref{fig:LME_MPM}, where the \acrshort{lme} adaptability is illustrated.\\
+Furthermore, with a conveniently adopted \textit{regularization} parameter it is possible to get a \acrshort{gimp}-like shape function.
+Finally \acrshort{sph}-like behaviour can be obtained for lower values of \textcolor{green}{$\widehat{\gamma}$} since the support of the shape function is drastically increased, and therefore \textit{smoother} solutions are obtained.
+See \cite{Navas2016} for an application of this capability, where oscillations due to excess of pore water pressure in consolidation problems are smoothed out by using this technique.
+The employment of smoothing algorithms is also straightforward in the fluid-solid interaction problems \cite{Arduino_2018}.
+\textcolor{blue}{This behaviour was noticed previously by \cite{Arroyo2006}, were authors highlighted how, by adjusting the spatial variation of $\beta(\vec{x})$, it is possible to select regions of the domain of analysis which are treated by finite elements and regions that are treated in the style of meshfree methods, with seamless transitions between those regions.
+The aforementioned adaptability can be appreciated in figure~\ref{fig:LME_MPM}} \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     approximation for a two-dimensional arrangement of nodes, and
-    spatial derivatives for several values of $\gamma = \beta/h^2$.}
+    spatial derivatives for several values of $\widehat{\gamma} = \beta h^2$.}
   \label{fig:LME_MPM}
@@
 
-\MODIFIED{Unfortunately, the employment of \textit{max-ent} approximants is not free of pitfalls.
+\textcolor{blue}{Unfortunately, the employment of \textit{max-ent} approximants is not free of pitfalls.
 Some requirements such as the need for a convex domain, as well as those derived from its calculation (the determination of the Lagrange Multipliers, specially at the boundaries, or the obtainment of the minimizer of the logarithmic function), make the usage of it a challenging tool.
@@
 For instance, the possibility of replacing the Euclidean distance $\lVert x - x_a \rVert$ in the definition of the shape functions by the length of the shortest path contained within the domain connecting $x$ and $x_a$.
-Or by decomposing the non-convex domain into convex sub-domains.}
-
-\MODIFIED{Of course the requirement of convex domain is not exclusive from \textit{max-ent}, it also concerns to the remaining interpolation techniques in the \acrshort{mpm} and other meshfree methods.
+Or by decomposing the non-convex domain into convex sub-domains.
+Of course the requirement of convex domain is not exclusive from \textit{max-ent}, it also concerns to the remaining interpolation techniques in the \acrshort{mpm} and other meshfree methods.
 For instance, this topic has been extensively studied in the context of MLS-based meshfree methods, for instance visibility, diffraction, and constrained path criteria.
@@
 
-\MODIFIED{Despite these drawbacks, the results depicted in this manuscript will strengthen the motivation of its employment in order to mitigate typical \acrshort{mpm} problems such as cell-crossing or stress instabilities in a wide range of problem.}
+\textcolor{blue}{Despite these drawbacks, the results depicted in this manuscript will strengthen the motivation of its employment in order to mitigate typical \acrshort{mpm} problems such as cell-crossing or stress instabilities in a wide range of problems.}
 
@@
 overcome spurious oscillations due to the grid crossing and high
-frequency loads under the context of \acrshort{mpm}. \MODIFIED{Three different tests have
-been adopted for this purpose: the benchmark proposed by Dyka \& Ingel
-(1995)\cite{Dyka1995}, the test proposed in the PhD thesis of
-Andersen (2009)\cite{thesis_Andersen_2009} and the evolution of velocity waves in an elastic square.
-The first example is devoted to test the accuracy of the \acrfull{npc} scheme is compared to the standard \acrfull{fe} in order to assess the performance of the time integration schemes.
-In the second example,  \acrshort{lme} solutions
-are compared with those provided by \acrfull{ugimp} and Q4 shape
-functions. Finally, in the third example the present approach is tested under a scenario where shocks and grid crossing occurs.} To avoid some mesh-dependent issues, in all
-calculations a regular background mesh was set. All simulations were
-performed with in-house software.
-
-\subsection{Dyka's bar \cite{Dyka1995}}
+frequency loads under the context of \acrshort{mpm}. Three different tests have been adopted for this purpose:
+
+%\begin{itemize}
+%    \item The first example is the well known benchmark proposed by Dyka \& %Ingel (1995)\cite{Dyka1995}.
+It is devoted to test the accuracy of the %\acrfull{npc} scheme.
+Several comparison have been performed:
+%    \begin{enumerate}
+%        \item  
+%        \item Comparison \acrshort{fe} \textit{versus} \acrshort{npc}.
+%Evolution of the velocity at the point on the left side.
+In this case, the %standard linear interpolation (Q4) has been established.
+%        \item Comparison MPM-LME$_{2.0}$-NPC \textit{versus} %MPM-LME$_{3.0}$-NPC \textit{versus} MPM-LME$_{4.0}$
+%        \item MPM-LME$_{4.0}$-NPC \textit{versus} MPM-uGIMP-NPC
+%        \item MPM-LME$_{4.0}$-NPC \textit{versus} OTM-LME$_{4.0}$-NPC
+%    \end{enumerate}
+%    
+%    \item the test proposed in the PhD thesis of Andersen %(2009)\cite{thesis_Andersen_2009}
+
+%    \acrshort{lme} solutions
+%    are compared with those provided by \acrfull{ugimp} and Q4 shape
+%    functions.
+
+%    \item the evolution of velocity waves in an elastic square. 
+%    in the third example the present approach is tested under a scenario %where shocks and grid crossing occurs
+%\end{itemize}
+
+ %To avoid some mesh-dependent issues, in all calculations a regular background mesh was set.
+
+ %All simulations were performed with in-house software.
+
+\subsection{Dyka\textquotesingle s bar \cite{Dyka1995}}
 \label{sec:dyka-bar}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the proposed example, the simulation extends from time zero up to 0.00001 s.
+In the proposed example, the simulation extends from time zero up to \textcolor{green}{$10^{-4}$} s.
 This time interval allows the elastic wave to travel a distance of 2.6
-lengths of the bar. For the spatial
-discretisation, a set of seven nodal mesh sizes (0.1, 0.3325, 0.5,
-1.0, 3.3325, 6.665, 10.0 millimeters) are considered. For each element a number of
-four particles was selected. In the initial layout, particles are located the exact quadrature points of a linear quadrilateral, with
-the exception of the \acrshort{ugimp} simulation, where gaps or overlap between
-voxels of each particle are not allowed. In those cases, each particle
-occupies the center of each cell quarter. For all simulations, time step
-is controlled by a Courant-Friedrichs-Levy condition of 0.1, were the adopted
-celerity is computed as:
+lengths of the bar.
+For the spatial discretisation, a set of seven nodal mesh sizes (0.1, 0.3325, 0.5, 1.0, 3.3325, 6.665, 10.0 millimeters) are considered.
+For each element a number of four particles was selected.
+In the initial layout, particles are located the exact quadrature points of a linear quadrilateral, with the exception of the \acrshort{ugimp} simulation, where gaps or overlap between
+voxels of each particle are not allowed.
+In those cases, each particle occupies the center of each cell quarter.
+For all simulations, time step is controlled by a Courant-Friedrichs-Levy condition of 0.1 , were the adopted celerity is computed as:
 \begin{equation}
@@
 required in order to accommodate the unconstrained displacement of the
-particles in the left border of the bar. Naturally this problem arises
-when the mesh size is small enough that relative displacement of the
-particles is larger then the distance to the border, so grid crossing
-phenomena could appear even in those cases with infinitesimal
-displacements.
-
-In this case, an analytical solution can be obtained
-through the characteristics method, described in the appendix
-\ref{app:analytical_sol}. To measure the convergence of the solutions
+particles in the left border of the bar. This problem arises
+when the mesh size is small enough that relative displacement of the particles is larger \textcolor{green}{than} the distance to the border, so grid crossing phenomena could appear even in those cases with infinitesimal displacements.
+In this case, an analytical solution can be obtained through the characteristics method, described in the appendix~\ref{app:analytical_sol}.
+\textcolor{blue}{This section contains a large number of comparisons, which have been summarised in Table \ref{tab:dyka-cases-summarized}.
+FFirst, we analyze the convergence of the time integration scheme for different mesh sizes, and the interpolation techniques, \ref{sec:Convergence-analysis}.
+Later, we focus on how each combination of interpolation technique and time integration scheme is able to damp the numerical noise: comparison between \acrshort{fe} and \acrshort{npc}, \ref{sec:FE-vs-NPC}, the response of the \acrshort{lme} approximation for different $\widehat{\gamma}$ values,  \ref{sec:Sensitive-analysis-gamma}, the well known \acrshort{ugimp} shape function is compared with the \acrshort{lme} approximation, \ref{sec:LME-vs-uGIMP}, and finally a comparison between the \acrshort{otm} method \textit{versus} the \acrshort{mpm}, using the same time integration scheme and interpolation technique, \ref{sec:OTM-vs-MPM}.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{sidewaystable}
+\centering
+\begin{tabular}{c|c|c|c|c|c|}
+\cline{2-6}
+                                    & \ref{sec:Convergence-analysis} 
+                                    & \ref{sec:FE-vs-NPC} 
+                                    & \ref{sec:Sensitive-analysis-gamma} 
+                                    & \ref{sec:LME-vs-uGIMP} & 
+                                    \ref{sec:OTM-vs-MPM}\\ \hline
+\multicolumn{1}{|l|}{\diagbox[]{MPM-Q4-FE }{MPM-Q4-NPC }}  & 
+\diagbox[]{x}{x} &  
+\diagbox[]{x}{x} & 
+ & 
+ & 
+ \\ \hline
+\multicolumn{1}{|l|}{\diagbox[]{MPM-uGIMP-FE}{MPM-uGIMP-NPC}} &  \diagbox[]{x}{x} & 
+ &
+ &
+\diagbox[]{ -}{x} &
+ \\ \hline
+\multicolumn{1}{|l|}{\diagbox[]{MPM-LME$_{2.0}$-FE}{MPM-LME$_{2.0}$-NPC}} & \diagbox[]{x}{x} &  
+ &
+ \diagbox[]{ -}{x} &
+ &    
+ \\ \hline
+\multicolumn{1}{|l|}{\diagbox[]{MPM-LME$_{3.0}$-FE}{MPM-LME$_{3.0}$-NPC}} & \diagbox[]{x}{x} & 
+ &
+ \diagbox[]{ -}{x}  &
+ &
+ \\ \hline
+\multicolumn{1}{|l|}{\diagbox[]{MPM-LME$_{4.0}$-FE}{MPM-LME$_{4.0}$-NPC}} & \diagbox[]{x}{x} &
+ & 
+ \diagbox[]{ -}{x} &
+ \diagbox[]{ -}{x} &
+ \diagbox[]{ -}{x} \\ \hline
+\multicolumn{1}{|l|}{\diagbox[]{OTM-LME$_{4.0}$-FE}{OTM-LME$_{4.0}$-NPC}} &
+ &
+ & 
+ &
+ &
+ \diagbox[]{ -}{x}  \\ \hline
+\end{tabular}
+\caption{Table with all the permutations for the Dyka bar \cite{Dyka1995}.}
+\label{tab:dyka-cases-summarized}
+\end{sidewaystable}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{Convergence analysis}
+\label{sec:Convergence-analysis}
+
+To measure the convergence of the solutions
 for the different time integration and approximation schemes the
@@
 numerical solutions evaluated in the final time step in the position
-of each particle.
-In Fig.
-\ref{fig:Dyka-error-evol} the evolution of the RMS is obtained for both time integration schemes.
-The right figure, with the \acrshort{npc} results, shows lower values of the estimated error, denoting the higher performance of this methodology.
-About the spatial discretisation, the \acrshort{lme} schemes show an error comparable to the obtained with the \acrshort{ugimp}, being even lower close to the grid-crossing region.
-
+of each particle. In Fig. \ref{fig:Dyka-error-evol} the evolution of the RMS is obtained for both time integration schemes. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A first comparison between the obtained one in both time integration
-schemes is plotted in figure \ref{fig:Dyka-NPC-FE}. It demonstrates the
-superior performance of the \acrshort{npc} \textit{versus} the \acrshort{fe}. In the \acrshort{npc} the
-spurious oscillations are quickly mitigated in the first time steps,
-and the error is not propagated in time, opposite to the results of the \acrshort{fe} scheme, where the
-simulation becomes unstable after $6E^{5}$ seconds.
+The right figure, with the \acrshort{npc} results, shows lower values of the estimated error, denoting the higher performance of this methodology.
+About the spatial discretisation, the \acrshort{lme} schemes show an error comparable to the obtained with the \acrshort{ugimp}, being even lower close to the \textit{grid-crossing region}.
+\textcolor{blue}{In this region the performance is punished with significant movement of the particles as far as the mesh size is reduced.}
+
+\textcolor{blue}{Figure \eqref{fig:Dyka-error-evol} also highlights how on the one hand the slope of the \acrshort{lme} error decreases monotonously for the lower $\widehat{\gamma}$ values up to the \textit{grid-crossing region}, where more error accumulates.
+And on the other hand, the slope of the error is punished for the higher values of $\widehat{\gamma}$ in \acrshort{lme}, \acrshort{ugimp} or bi-linear shape functions.
+This occurs earlier than in the previous case, during the \textit{transition region}.}
+
+\textcolor{blue}{Finally, notice the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5 millimeters in figure \eqref{fig:Dyka-error-evol}.
+The reason is due to an unstable increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yield unacceptable results.
+A feasible explanation for this phenomena could be the presence of numerical cancellation which could produce gaps between voxels.
+Further research should be done in this direction for getting a better comprehension of this phenomenon.
+Conversely, this shortcoming is not suffered by \acrshort{lme}, independently of regular or irregular nodal layout.}
+
+\subsubsection{FE \textit{versus} NPC}
+\label{sec:FE-vs-NPC}
+
+\textcolor{blue}{A first comparison of the performance of both time integration schemes is presented in figure \ref{fig:Dyka-NPC-FE}.
+Both integration schemes show numerical oscillations with respect to the analytical solution all over the simulation time, being worse just after jump discontinuities.
+However, the \acrshort{npc} approach damps out these oscillations faster than the \acrshort{fe} scheme.
+The oscillations of the \acrshort{npc} almost disappeared before reaching subsequent jump discontinuities, while those of \acrshort{fe} do not.
+Moreover, oscillations of the \acrshort{fe} seams to increase further after each jump discontinuity and an unstable tendency can by foreseen.
+This unstable tendency is not appreciated in the \acrshort{npc} integration scheme.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\subsubsection{Sensitive analysis to $\widehat{\gamma}$ parameter}
+\label{sec:Sensitive-analysis-gamma}
+
 Figure \eqref{fig:Dyka-LME-gamma} shows the sensitivity of the \acrshort{lme}
 approximation scheme to variations in the parameter
-$\gamma$, which is the one that controls the value of the regularization parameter
-$\beta$ together with of the mesh size. Notice how lower values of
-gamma exhibits a behaviour with a soft decay in some parts of the
-simulation due to the increase of nodes adopted to regularize the
-solutions. This capability could be useful in simulations where
-extremely noisy oscillations could damage the solutions like memory
-materials. On the other hand larger values of the parameter $\beta$
-make the solution to tend to the linear \acrshort{fem} solution as the athermal limit is reached \cite{Arroyo2006}. Intermediate values of the
-regularization parameters give us a compromise between both scenarios described here. An additional observation, concerning to the
-solution sensibility depending on the regularization parameters, is the behaviour of the solution depending on the decreasing of mesh
-size. For larger mesh sizes, where the relative particle displacement
-is negligible in comparison with the cell size, the global behaviour
-is \acrshort{fem}-like; therefore, larger values of $\gamma$ may offer better results. On the other hand, when mesh size is small enough to produce
-grid-crossing meshfree behaviour is required to ensure the
-convergence of the solution and tiny values of $\gamma$ may lead to better
-performances. Convergence plot in figure \eqref{fig:Dyka-error-evol}
-shows how the slope, for the larger values of $\gamma$, decreases
-monotonically with the value of the mesh size, in contrast with larger
-values of $\gamma$, where the performance is punished with significant
-movement of the particles as far as the mesh size is reduced.
+$\widehat{\gamma}$, which is the one that controls the value of the regularization parameter
+$\beta$ \textcolor{green}{together with the nodal spacing parameter $h$}.
+\textcolor{green}{It can be observed that for} lower values of $\widehat{\gamma}$ the numerical solution presents a faster decay of the spurious oscillations.
+This capability could be useful in simulations where
+extremely noisy oscillations could damage the solutions like memory materials.  An additional observation, concerning to the
+solution sensibility depending on the regularization parameters, is the behaviour of the solution depending on the decreasing of mesh size.
+For larger mesh sizes, where the relative particle displacement is negligible in comparison with the cell size, the global behaviour is \acrshort{fem}-like, therefore, larger values of $\widehat{\gamma}$ may offer better results.
+On the other hand, when mesh size is small enough to produce grid-crossing, meshfree behaviour is required to ensure the convergence of the solution and tiny values of $\widehat{\gamma}$ may lead to better performances.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \caption{Sensitivity  of LME approximants performance to changes in the
-    dimensionless regularization parameter $\gamma = \beta/h^2$. To
-    illustrate it, the velocity evolution at the point in the bar left side
-    is plotted.}
+    dimensionless regularization parameter \textcolor{green}{$\widehat{\gamma}$}. To illustrate it, the velocity evolution at the point in the bar left side is plotted.}
   \label{fig:Dyka-LME-gamma}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The performance of the
-\acrshort{ugimp}~\cite{Bardenhagen2004} shape function \textit{versus} the \acrshort{lme} approximation scheme with
-a dimensionless regularization parameter $\gamma$ of 4.0 is compared in Figure \ref{fig:Dyka-uGIMP-LME}. Although remarkable differences are not observed, more
-robust behaviour is exhibited by the \acrshort{lme} approximants than the \acrshort{ugimp} shape functions. Regarding this, notice
-the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5
-millimeters. The reason is due to an unstable
-increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yield unacceptable results. A feasible
-explanation for this phenomena could be the presence of numerical
-cancellation which could produce gaps between voxels. Further research
-should be done in this direction for getting a better comprehension of
-this phenomenon. Conversely, this shortcoming is not suffered by \acrshort{lme}, independently of regular or with irregular nodal layout.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{LME \textit{versus} uGIMP}
+\label{sec:LME-vs-uGIMP}
+
+The performance of the \acrshort{ugimp}~\cite{Bardenhagen2004} shape function \textit{versus} the \acrshort{lme} approximation scheme with a dimensionless regularization parameter $\widehat{\gamma}$ of 4.0 is compared in Figure \ref{fig:Dyka-uGIMP-LME}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Finally, the \acrshort{otm}~\cite{Li2010} solution is compared against the one obtained with \acrshort{mpm}, both with same time integration scheme and spatial discretisation, and results are shown in figure \ref{fig:Dyka-OTM-MPM}.
-In
-this case, the performance of \acrshort{mpm} presents better robustness and stability than the
-\acrshort{otm}. During the first half of the simulation both method 
-seem to perform in a similar way, but during the second half of the
-simulation after the elastic wave has travel from the free border to
-the fixed one and back, in \acrshort{otm} the solution becomes more noisy than the
-one performed by \acrshort{mpm}.  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ Although remarkable differences are not observed under a regular mesh, \textcolor{green}{\acrshort{lme} approximants seems to fits better than \acrshort{ugimp} after the jump.}
+
+\subsubsection{OTM \textit{versus} MPM}
+\label{sec:OTM-vs-MPM}
+
+Finally, the \acrshort{mpm} \textcolor{green}{approach is compared with the \acrfull{otm}~\cite{Li2010} method, both with same time integration scheme, spatial discretisation and interpolation technique}.
+Results \textcolor{green}{of the comparison} are shown in figure \ref{fig:Dyka-OTM-MPM}.
+During the first half of the simulation both \textcolor{green}{methods} seem to perform in a similar way, but during the second half of the simulation after the elastic wave has \textcolor{green}{traveled} from the free border to
+the fixed one and back, in \acrshort{otm} the solution becomes more noisy than the one performed by \acrshort{mpm} .   
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\clearpage
 \subsection{Rigid block}
@@
 The following test was proposed to validate the ability of the proposed
-interpolation technique to deal with grid crossing instabilities. It
-consists of the simulation of a square block of soil incrementally
-loaded by a body force. Details of the problem are sketched in figure~\ref{fig:block}
+interpolation technique to deal with grid crossing instabilities.
+\textcolor{green}{A solid elastic square block is} incrementally loaded \textcolor{green}{only considering} body forces.
+Details of the problem are sketched in figure~\ref{fig:block}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{itemize}
-The gravity force is applied as an external force. Using a total time period of T (20
-seconds) to apply the gravity, it is increased from 0 to 9.81$m/s$
-with a sinusoidal function until T/2 and then maintained constant until T
+The gravity force is applied as an external force. Using a total time period T of 20 seconds to apply the gravity, it is increased from 0 to 9.81$m/s$
+with a sinusoidal function until T/2 seconds and then maintained constant until T
 in order to reach the equilibrium state:
@@
 Courant number of 0.1. On the other hand, the explicit
-predictor-corrector scheme is here employed looking forward to getting better results. For the
-initial spatial discretisation four particles per cell
+predictor-corrector scheme \textcolor{green}{proposed in previous sections} is employed. For the initial spatial discretisation four particles per cell
 ($\Delta x = 2\ m$) were adopted. The initial layout of particles inside of the
@@
 quadratic finite element. For the \acrshort{ugimp} shape function the initial
-position of each particle is located in the center of each voxel, due
-to the fact that in the initial situation, the voxel domain should not
-overlap each others.
+position of each particle is located in the center of each voxel \textcolor{green}{as} in the initial situation voxel domains should not overlap.
 
@@
     = 6\cdot 10^3\ kg/m^3$). Numerical parameters considered for the
-    simulation are : Local \textit{max-ent} shape function $\gamma =3$
+    simulation are : Local \textit{max-ent} shape function $\widehat{\gamma} =3$
     and explicit PC scheme with CFL 0.1.}
@@
 displacement evolution of a point in the free surface of the
-block. This figure shows how simulations performed with a bi-linear
-interpolation technique (Q4) turns out to be unstable during
-cell-crossing and consequently fail. The \acrshort{ugimp} simulation
-is more stable than the one performed by the Q4, although is still
-unstable and could trigger severe oscillations in simulation with
-non-linear  materials. The \acrshort{lme} simulation was performed
+block. \textcolor{purple}{This figure shows how simulations performed with a bi-linear interpolation technique (Q4) turns out to be unstable during
+cell-crossing and consequently fail.
+FEM-Q4 ARE NOT UNSTABLE AND MPM-Q4-NPC DO NO APPEAR IN THIS FIGURE SO CANNOT BE SHOWN.} \textcolor{purple}{The \acrshort{ugimp} simulation is more stable than the one performed by the Q4, although is still unstable NOT MORE THAN THE OTHERS} and could trigger severe oscillations in simulation with non-linear  materials.
+The \acrshort{lme} simulation was performed
 using two kinds of shape functions, one with a low value of the
-dimensionless parameter, $\gamma = 0.8$, and other with a larger value
-of it, $\gamma = 3.0$. Notice that the results are both stable, but
-the larger values of $\gamma$ give us a very stable solution. This is
-due to the fact that with larger value of $\gamma$, the shape
+dimensionless parameter, $\widehat{\gamma} = 0.8$, and other with a larger value
+of it, $\widehat{\gamma} = 3.0$. Notice that the results \textcolor{purple}{are both stable NOT MORE THAN THE REST}, but
+the larger values of $\widehat{\gamma}$ give us a very stable solution. This is
+due to the fact that with larger value of $\widehat{\gamma}$, the shape
 functions behaves in a similar way to the \acrshort{fem}, which performs very
 accurate in those cases with a reasonable mesh distorsion, and with a
-lower value it behaves in a similar way to the \acrshort{ugimp}. This behaviour
-was noticed previously by \cite{Arroyo2006}, were authors highlighted
-how, by adjusting the spatial variation of $\beta(\vec{x})$, it is
-possible to select regions of the domain of analysis which are treated
-by finite elements and regions that are treated in the style of
-meshfree methods, with seamless transitions between those regions. 
+lower value it behaves in a similar way to the \acrshort{ugimp}. \textcolor{purple}{COMPARISON WITH ANALYTICAL SOLUTION MIGHT BE WORTH IT} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\MODIFIED{\subsection{Velocity waves in an elastic domain}}
+\subsection{Velocity waves in an elastic domain}
 \label{sec:Velocity-waves-elastic-domain}
 
-\MODIFIED{The following test is best suited to validate the ability of the discussed
-time integration scheme to reproduce 2D wave propagation problem.
+\textcolor{blue}{The following test is intended to validate the ability of the discussed time integration schemes to reproduce 2D wave propagation problems.
 It consists of the side impact of a moving elastic square.
@@
 
-\MODIFIED{The background set of nodes consists in a cartesian grid with a uniform gap between nodes of 1 mm, and square was discretised with four material points by cell.
+\textcolor{blue}{The background set of nodes consists of a cartesian grid with a uniform gap between nodes of 1 m, and four material points per cell were considered.
 The courant number is fixed to 0.1 during the whole simulation and $\text{LME}_{4.0}$ shape functions where used.
@@
 
-\MODIFIED{Snapshots of velocity field magnitude within the square are given in\ref{fig:Magnitude_velocity_impact_square}.
+\textcolor{blue}{Snapshots of velocity field magnitude within the square are given in Figure\ref{fig:Magnitude_velocity_impact_square}.
 At early times, \acrshort{npc} and \acrshort{fe} are similar.
-At later times, the \acrshort{fe} introduces significant numerical noise while \acrshort{npc} is almost clean.
-}
+At later times, the \acrshort{fe} introduces significant numerical noise as compared with \acrshort{npc}.
+}
+
 %%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%
-\MODIFIED{Energy plots in figure \ref{fig:Energy_impact_square} shows that after collision the total amount of energy is preserved.
-In the bounce back stress wave are still travelling thorough the elastic domain introducing numerical noise due to the inaccuracies of the time integration scheme as figure \ref{fig:Magnitude_velocity_impact_square} proves.
-However, \acrshort{npc} introduces a minimal energy loss (less than 0.1\%) to significantly reduce the numerical noise.
-}
-
-\MODIFIED{Although during impact mechanical energy decreases, no real dissipation occurs since after collision the value is again 25 kJ like before collision.
-Furthermore, kinetic energy has been exactly computed.
-Hence, this apparently dissipation of mechanical energy is probably due to numerical cancellation of shear terms contribution.
-}
-%%%%%%%%%%%%%%%%
-\begin{figure}
-%\sidecaption
-  \centering
-  \resizebox{0.8\hsize}{!}{
-\includegraphics[scale=1]{Figures/Energy_square.png} 
-  }
-  \caption{Total energy (kinetic energy plus strain energy) evolution for the square. Solid line represent total energy, dashed line represent strain energy, and dotted line represent kinetic energy.}
-  \label{fig:Energy_impact_square}
-\end{figure}
-%%%%%%%%%%%%%%%%
 
@@
 We have proposed in this paper an enhanced methodology which improves \acrfull{mpm} behaviour in fast dynamics problems.
-Different time and space discretisation techniques have been presented and their performance being compared agains other approaches in two benchmark problems.
+Different time and space discretisation techniques have been presented and their performance being compared agains other approaches in \textcolor{green}{three} benchmark problems.
 First, a novel time integration scheme for \acrshort{mpm} has been carried out.
+The \acrfull{npc}.
 The \acrshort{npc} has been shown to be a highly efficient alternative for demanding fast dynamics problems.
 In the literature, several approaches of the \acrshort{npc} are proposed in order to compete on accuracy with expensive implicit time integration algorithms.
-The main achievement of the proposed time discretisation has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme, \MODIFIED{with a minimal loose of energy as in highlighted in \ref{sec:Velocity-waves-elastic-domain} }.
+The main achievement of the proposed time discretisation has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.
 Also, the procedure employed to design the \acrshort{npc} algorithm opens the
@@
 
-On the other hand, the spatial discretisation of the \acrshort{mpm} is enhanced thanks to the powerful skills of the \acrfull{lme} approximation scheme, which has been validated as a robust and versatile
-tool in the \acrshort{mpm} framework. It also comes up as a promising
-alternative to other approximation techniques, developed within the
-\acrshort{mpm} framework, in order to overcome grid crossing limitations and to avoid the
-constriction of the \acrshort{ugimp} of a regular mesh or a high
-density of particles per cell.
+On the other hand, the spatial discretisation of the \acrshort{mpm} is enhanced thanks to the powerful skills of the \acrfull{lme} approximation scheme, which has been validated as a robust and versatile tool in the \acrshort{mpm} framework.
+It also comes up as a promising alternative to other approximation techniques, developed within the \acrshort{mpm} framework, in order to overcome grid crossing limitations and to avoid the constriction of the \acrshort{ugimp} of a regular mesh or a high density of particles per cell.
 Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vec{x})$ through the finite strain
@@
 \acrshort{fem}-like of meshfree-like depending of how behaves the
-region. Together with the implementation of non-linear behaviours, previously mentioned, challenging
-scenarios could be reproduced, being the main purpose of the research line the simultaneous simulation of both initialization and
+region.
+Together with the implementation of non-linear behaviours, previously mentioned, challenging scenarios could be reproduced, being the main purpose of the research line the simultaneous simulation of both initialization and
 propagation stages of fast landslides.

### 2020-09-09 LME-MPM.tex
Cambios II (9-9-2020)

@@
 overcome spurious oscillations due to the grid crossing and high
-frequency loads under the context of \acrshort{mpm}. Three different tests have been adopted for this purpose:
-
-%\begin{itemize}
-%    \item The first example is the well known benchmark proposed by Dyka \& %Ingel (1995)\cite{Dyka1995}.
-It is devoted to test the accuracy of the %\acrfull{npc} scheme.
-Several comparison have been performed:
-%    \begin{enumerate}
-%        \item  
-%        \item Comparison \acrshort{fe} \textit{versus} \acrshort{npc}.
-%Evolution of the velocity at the point on the left side.
-In this case, the %standard linear interpolation (Q4) has been established.
-%        \item Comparison MPM-LME$_{2.0}$-NPC \textit{versus} %MPM-LME$_{3.0}$-NPC \textit{versus} MPM-LME$_{4.0}$
-%        \item MPM-LME$_{4.0}$-NPC \textit{versus} MPM-uGIMP-NPC
-%        \item MPM-LME$_{4.0}$-NPC \textit{versus} OTM-LME$_{4.0}$-NPC
-%    \end{enumerate}
-%    
-%    \item the test proposed in the PhD thesis of Andersen %(2009)\cite{thesis_Andersen_2009}
-
-%    \acrshort{lme} solutions
-%    are compared with those provided by \acrfull{ugimp} and Q4 shape
-%    functions.
-
-%    \item the evolution of velocity waves in an elastic square. 
-%    in the third example the present approach is tested under a scenario %where shocks and grid crossing occurs
-%\end{itemize}
-
- %To avoid some mesh-dependent issues, in all calculations a regular background mesh was set.
-
- %All simulations were performed with in-house software.
+frequency loads under the context of \acrshort{mpm}.
+Three different tests have been adopted for this purpose: The first example is the well known benchmark proposed by Dyka \& Ingel (1995)\cite{Dyka1995}.
+It is devoted to test the accuracy of the \acrfull{npc} scheme.
+The second example is the test proposed in the PhD thesis of Andersen (2009)\cite{thesis_Andersen_2009} where the evolution of velocity waves in an elastic square.
+In the third example the present approach is tested under a scenario where shocks and grid crossing occurs.
+All simulations were performed with in-house software.
 
@@
 displacement evolution of a point in the free surface of the
-block. \textcolor{purple}{This figure shows how simulations performed with a bi-linear interpolation technique (Q4) turns out to be unstable during
-cell-crossing and consequently fail.
-FEM-Q4 ARE NOT UNSTABLE AND MPM-Q4-NPC DO NO APPEAR IN THIS FIGURE SO CANNOT BE SHOWN.} \textcolor{purple}{The \acrshort{ugimp} simulation is more stable than the one performed by the Q4, although is still unstable NOT MORE THAN THE OTHERS} and could trigger severe oscillations in simulation with non-linear  materials.
-The \acrshort{lme} simulation was performed
-using two kinds of shape functions, one with a low value of the
-dimensionless parameter, $\widehat{\gamma} = 0.8$, and other with a larger value
-of it, $\widehat{\gamma} = 3.0$. Notice that the results \textcolor{purple}{are both stable NOT MORE THAN THE REST}, but
-the larger values of $\widehat{\gamma}$ give us a very stable solution. This is
-due to the fact that with larger value of $\widehat{\gamma}$, the shape
-functions behaves in a similar way to the \acrshort{fem}, which performs very
-accurate in those cases with a reasonable mesh distorsion, and with a
-lower value it behaves in a similar way to the \acrshort{ugimp}. \textcolor{purple}{COMPARISON WITH ANALYTICAL SOLUTION MIGHT BE WORTH IT} 
+block.
+\textcolor{green}{This figure shows how the \acrshort{mpm} simulation performed with a bi-linear interpolation technique (Q4) turns out to be unstable during cell-crossing and consequently fail}.
+\textcolor{green}{The \acrshort{lme} simulation was performed using two kinds of shape functions, one with a low value of the dimensionless parameter, $\widehat{\gamma} = 0.8$, and other with a larger value of it, $\widehat{\gamma} = 3.0$.
+Both simulations behaves with minimal oscillations, also not appreciable difference is observed between them.
+The \acrshort{ugimp} simulation is more stable than the one performed with the \acrshort{mpm}-Q4 and behaves like the \acrshort{lme} simulations.
+Finally, we have compared our results against two contrasted techniques.
+The \acrshort{fem} solution has been done with a regular mesh of linear quadrilaterals, meanwhile the \acrshort{otm} solution has been done with \acrshort{lme} approximation.
+The final displacement in both solutions oscillates around a value of 0.59 m.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{itemize} 
-\item  Initial density : $20 kg/m^3$
+\item  Initial density : $20\ kg/m^3$
 \item  Poisson ratio : $0.3$
-\item  Elastic modulus : $0.1 MPa$
+\item  Elastic modulus : $0.1\ MPa$
 \end{itemize}
 }
-
 \textcolor{blue}{The background set of nodes consists of a cartesian grid with a uniform gap between nodes of 1 m, and four material points per cell were considered.
-The courant number is fixed to 0.1 during the whole simulation and $\text{LME}_{4.0}$ shape functions where used.
+The courant number is fixed to 0.1 during the whole simulation and $\text{LME}_{3.0}$ shape functions where used.
 The square initially move horizontally through the grid at $\text{V}_0 = 1.0 m/s$ until it hits an obstacle modelled as a set of nodes with zero velocity prescribed.
-The collision produce stress waves and cause the square to bounce back.}
-
-\textcolor{blue}{Snapshots of velocity field magnitude within the square are given in Figure\ref{fig:Magnitude_velocity_impact_square}.
-At early times, \acrshort{npc} and \acrshort{fe} are similar.
-At later times, the \acrshort{fe} introduces significant numerical noise as compared with \acrshort{npc}.
-}
-
+The collision produce stress waves and cause the square to bounce back.
+Snapshots of velocity field magnitude within the square are given in figure
+~\ref{fig:Magnitude_velocity_impact_square}}. 
 %%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%% 
+\textcolor{blue}{At early times, \acrshort{npc} and \acrshort{fe} are similar.
+At later times, the \acrshort{fe} introduces significant numerical noise as compared with \acrshort{npc}.
+At the end of the simulation, the filtering process when \acrshort{npc} is used leads to a negligible loss of mechanical energy (about 0.1\%).
+Finally, let us consider an unstructured background mesh.}
+%%%%%%%%%%%%%%%%
+\begin{figure}
+%\sidecaption
+  \centering
+  \resizebox{\hsize}{!}{
+\includegraphics[scale=0.8]{Figures/Velocity-structured-unstructured-lme-ugimp.png}
+  }
+  \caption{Sensitive of \acrshort{ugimp} and \acrshort{lme} to the randomness in the layout of the background set of nodes.
+On the left side of the image we can see sketches of the two meshes that have been used.
+And on the right side, snapshots with the velocity magnitudes in each case.
+All the simulation where carried out with the proposed \acrshort{npc}.}
+  \label{fig:Magnitude_velocity_impact_square_structured_unestructured}
+\end{figure}
+%%%%%%%%%%%%%%%%
+\textcolor{blue}{ As we can see in figure~\ref{fig:Magnitude_velocity_impact_square_structured_unestructured}, the \acrshort{lme} approximation preserves the solution even though the mesh is not structured.
+Meanwhile, the \acrshort{ugimp} is not able to deal with the unstructured mesh as expected.
+It goes without saying that there is no point in using unstructured meshes in this type of situation.
+Despite this, the \acrshort{lme} approach shows remarkable robustness in dealing with an unstructured mesh.
+This is useful in more complicated computational domains where structured mesh are not possible.}
 

### 2020-09-10 Revisiones/PNA_MMP_Responses to the reviewers.tex

@@
 Their comments have helped us to improve the paper.
-Changes to the original manuscript are given in  color (\textcolor{red}{red} for corrections, \textcolor{blue}{blue} for modified texts)  in the revised version.
+Changes to the original manuscript are given in  color \textcolor{blue}{red} for corrections and for modified text in the revised version.
 A detailed response to both reviewers is given below.
@@
 
-The development of the MPM approach has been revised considering the proposal of the reviewer.
+Unfortunately, the \textit{max-ent} approximation can not be expressed as the conjugation of a standard shape function and a particle "characteristic" function.
+Furthermore, in order to improve the readability of the development of the MPM, the approach has been revised with a detailed explanation.
 
@@
 
-Additionally, Arroyo \& Ortiz~\cite{Arroyo2006} briefly discussed the existence of non-convex domains, and proposed some solutions to it.
-For instance, the possibility of replacing the Euclidean distance $\lVert  x - x_a  \rVert$ in the definition of the shape functions by the length of the shortest path contained within the domain connecting $x$ and $x_a$.
-Or by decomposing the non-convex domain into convex sub-domains.
+On the other hand, the special case of non-convex domains was discussed by Arroyo \& Ortiz~\cite{Arroyo2006}.
+Some of the solutions proposed by the aforementioned authors are : the possibility of replacing the Euclidean distance $\lVert  x - x_a  \rVert$ in the definition of the shape functions by the length of the shortest path contained within the domain connecting $x$ and $x_a$.
+Or the decomposition of the non-convex domain into convex sub-domains.
+
 On the other hand, this topic has been extensively studied in the context of MLS-based meshfree methods, for instance visibility, diffraction, and constrained path criteria.
@@
 
-However, the results depicted in this manuscript will strengthen the motivation of its employment in order to mitigate typical MPM problems such as cell-crossing or stress instabilities.
+However, the results depicted in this manuscript will strengthen the motivation of its employment in order to mitigate typical MPM problems such as cell-crossing, stress instabilities and the use of unstructured mesh.
 

### 2020-09-10 LME-MPM.tex

@@
   propagation in the large deformation regime is still challenging
-  under this approach due \textcolor{green}{to} the incapability of the standard \acrshort{mpm} time
+  under this approach due \textcolor{red}{to} the incapability of the standard \acrshort{mpm} time
   integration scheme to filter spurious noises. To overcome it, we propose in this paper an explicit Predictor-Corrector time
@@
 has increased due to its ability to deal with large strain regime
-without suffering mesh distortion inaccuracies. One of the main fields where this method is \textcolor{green}{widely used} is solid dynamics.
+without suffering mesh distortion inaccuracies. \textcolor{blue}{One of the main fields where this method is widely used is solid dynamics.}
 
 On one hand, the main source of instability occurs when
-material points cross cell boundaries. This \textcolor{green}{issue led to} the development
+material points cross cell boundaries. \textcolor{blue}{This issue led to} the development
 of other interpolation techniques to overcome this limitation such as
@@
 decreases.
-Therefore \acrshort{ddmp} \textcolor{green}{requires} a large number of particles for convergence~\cite{DHAKAL2016301}, what makes the method \textcolor{green}{computationally} expensive.
-\textcolor{blue}{To avoid tensile instabilities that are quite common in extension, Sadeghirad {\it et al.} (2011) \cite{Sadeghirad_et_al_IJNME_2011} developed the \acrshort{cpdi} \cite{Sadeghirad_et_al_IJNME_2011}}.
-In recent years, the employment of spline-lines as shape functions has \textcolor{green}{gained} popularity with the introduction of the B-Spline
-\acrshort{mpm} proposed by Tielen {\it et al.} (2017)~\cite{TIELEN2017265}, \textcolor{green}{in which} unstructured set of \textcolor{green}{nodes} and
-particles \textcolor{green}{can be considered} . More recently, approximants derived from minimization \textcolor{green}{have}
-been introduced \textcolor{green}{into} the \acrshort{mpm} framework with the \acrfull{ctls}
+\textcolor{blue}{Therefore \acrshort{ddmp} requires a large number of particles for convergence~\cite{DHAKAL2016301}, what makes the method computationally expensive.} \textcolor{blue}{To avoid tensile instabilities that are quite common in extension, Sadeghirad {\it et al.} (2011) \cite{Sadeghirad_et_al_IJNME_2011} developed the \acrshort{cpdi} \cite{Sadeghirad_et_al_IJNME_2011}}.
+In recent years, the employment of spline-lines as shape functions \textcolor{blue}{has gained popularity with the introduction of the B-Spline
+\acrshort{mpm} proposed by Tielen {\it et al.} (2017)~\cite{TIELEN2017265}, in which unstructured set of nodes and
+particles can be considered}. More recently, approximants derived from minimization \textcolor{blue}{have
+been introduced into the \acrshort{mpm} framework} with the \acrfull{ctls}
 reconstruction proposed by Wobbes {\it et al.}
@@
 approximation schemes and provides a seamless transition between
-\acrshort{fem} and meshfree interpolations. The \textcolor{green}{\acrshort{lme}}
+\acrshort{fem} and meshfree interpolations. The \textcolor{red}{\acrshort{lme}}
 approximation is based on a compromise between minimizing the
 width of the shape function support and maximizing the
-entropy of the approximation \textcolor{green}{\cite{Arroyo2006}}. The \acrshort{lme} approximation
-may be regarded as a regularization, or \textcolor{green}{(in analogy to statistical mechanics)} \textit{thermalization}, of
+entropy of the approximation \cite{Arroyo2006}. The \acrshort{lme} approximation
+may be regarded as a regularization, or \textcolor{blue}{(in analogy to statistical mechanics)} \textit{thermalization}, of
 Delaunay triangulation which effectively resolves the degenerate cases
-resulting from the lack \textcolor{green}{or}  uniqueness \textcolor{green}{of}  the triangulation. \acrshort{lme} basis functions possess many desirable properties for
+resulting from the lack \textcolor{blue}{or uniqueness of the triangulation}. \acrshort{lme} basis functions possess many desirable properties for
 meshfree algorithms. First of all, they are entirely defined by the
@@
 satisfy the partition of unity property, and provide an exact
-approximation \textcolor{green}{of affine}  functions~\cite{Arroyo2006}.
-Important contributions on the Maximum-Entropy have been made by Sukumar and coworkers~\cite{Sukumar15} with Cell-based techniques and the ones carried within the \acrfull{otm} method.
+approximation \textcolor{blue}{of affine functions~\cite{Arroyo2006}.} Important contributions on the Maximum-Entropy have been made by Sukumar and coworkers~\cite{Sukumar15} with Cell-based techniques and the ones carried within the \acrfull{otm} method.
 The latter methodology has been proven to have a good performance under
-the dynamic regime being \textcolor{green}{worth mentioning} the contributions of Li {\it et al.} (2012)~\cite{Li2012} and Navas {\it et al.}
+the dynamic regime being \textcolor{blue}{worth mentioning} the contributions of Li {\it et al.} (2012)~\cite{Li2012} and Navas {\it et al.}
 (2018)~\cite{Navas:17b,Navas2018a} in the explicit regime and Navas
@@
 recently, under \acrshort{mpm} framework, the work made by Wobbes {\it et al.}(2020)~\cite{Wobbes2020}.
-The proposed research delves into the benefits of the regularization parameter, \gls{LME-beta}, and the analogy of the different shape functions \textcolor{green}{derived} by the tuning of this parameter and the traditional \acrshort{mpm} ones.
+The proposed research delves into the benefits of the regularization parameter, \gls{LME-beta}, and the analogy of the different shape functions \textcolor{blue}{derived} by the tuning of this parameter and the traditional \acrshort{mpm} ones.
 
@@
 ``grid crossing'' error. Nevertheless, in the presence of shock waves, spurious
-numerical noises \textcolor{green}{might} appear despite of the employment of these techniques~\cite{Tran2019e}. These numerical inaccuracies, also known
+numerical noises \textcolor{blue}{might} appear despite of the employment of these techniques~\cite{Tran2019e}. These numerical inaccuracies, also known
 as wiggles, arise due to inaccuracies in the time discretisation technique.
@@
 effort. In this paper a less time consuming and high efficient explicit predictor-corrector integration method is
-proposed. It consists of an accommodation of the traditional \acrfull{npc} scheme, widely employed in Finite Element methods. This method
-has \textcolor{green}{already} been chosen \textcolor{green}{in ~\cite{Navas2018a}}  among other suitable alternatives as those proposed
+proposed. It consists of an accommodation of the traditional \acrfull{npc} scheme, widely employed in Finite Element methods. \textcolor{blue}{This method
+has already been chosen in ~\cite{Navas2018a} among other suitable alternatives} as those proposed
 by Wilson {\it et al.} (1972)~\cite{Wilson1972} or Chung \& Hulbert
@@
 \ref{sec:local-max-ent}. In Section
-\ref{sec:Application-linear-elasticity-dynamic-problems}\textcolor{green}{,} applications to prove the numerical accuracy of the proposed approach are
+\ref{sec:Application-linear-elasticity-dynamic-problems}, applications to prove the numerical accuracy of the proposed approach are
 presented. Finally, conclusions and future research topics are exposed in Section \ref{sec:conclusions}.
@@
 divergence operator, and finally $\Grad{\square}$ and $\GradS{\square}$ denotes the gradient and its symmetric part.
-Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are \textcolor{green}{described} in subsection \ref{sec:derivation-mpm}, \ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.
+Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are \textcolor{blue}{described} in subsection \ref{sec:derivation-mpm}, \ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.
 
@@
 field \gls{u} through the following set of governing equations and
-restrictions that must be satisfied. First (i) we relate global to local state by the \textit{compatibility equation} \textcolor{green}{where the strain field \gls{strain} is defined by}:
+restrictions that must be satisfied. First (i) we relate global to local state by the \textit{compatibility equation} \textcolor{blue}{where the strain field \gls{strain} is defined by}:
 \begin{equation}
@@
 \end{equation}
-together with essential or \acrfull{dbc} \textcolor{green}{at} \gls{dirichlet-boundary}. We will further assume that 
+\textcolor{blue}{together with essential or \acrfull{dbc} at \gls{dirichlet-boundary}.} We will further assume that 
 strains are infinitesimal. The stress field \gls{stress} is considered the corresponding
 conjugate variable for the strain field, being the one which
-satisfies (ii) the \textit{conservation of \textcolor{green}{linear} momentum equation}:
+satisfies (ii) the \textit{conservation of \textcolor{red}{linear} momentum equation}:
 \begin{equation}
@@
 \end{equation}
-together with the natural of \acrfull{nbc} \textcolor{green}{at} \gls{neumann-boundary}.
-An \textcolor{green}{additional} component \textcolor{green}{is} (iii) the constitutive equation which relates stress and strain increments as,
+\textcolor{blue}{together with the natural of \acrfull{nbc} at \gls{neumann-boundary}. An additional component is (iii) the constitutive equation which relates stress and strain increments as,}
+{\color{red}
 \begin{equation}
   \label{eq:Constitutive-equation}
-\tens{\textcolor{green}{\Delta} \sigma} = \tens{D} \colon \tens{\textcolor{green}{\Delta} \varepsilon}.
-\end{equation}
-In this research, plane strain linear elasticity \textcolor{green}{is} considered. The final equation of the set is (iv) the mass conservation, which can be \textcolor{green}{expressed by} 
+\tens{\Delta \sigma} = \tens{D} \colon \tens{\Delta \varepsilon}.
+\end{equation}
+}
+\textcolor{blue}{
+In this research, plane strain linear elasticity is considered. The final equation of the set is (iv) the mass conservation, which can be expressed by} 
 \begin{equation}
@@
 \end{equation}
-\textcolor{green}{where $\vec{u}^{\psi} \in \mathcal{H}^1$ means that}
+\textcolor{blue}{where $\vec{u}^{\psi} \in \mathcal{H}^1$ means that}
 \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%
-Finally, mass conservation is guaranteed by \textcolor{green}{means of \eqref{eq:Rho-material-derivative} which can be rewritten in terms of the rate of strain tensor $\dot{\tens{\varepsilon}}$ as}
+Finally, mass conservation is guaranteed by \textcolor{blue}{means of \eqref{eq:Rho-material-derivative} which can be rewritten in terms of the rate of strain tensor $\dot{\tens{\varepsilon}}$ as}
 \begin{equation}
@@
 \end{equation}
-\textcolor{green}{Equation \eqref{eq:BalanceMomentum_wf_discretized} is a second order ordinary differential equation in time and a time integration scheme is required.} \textcolor{green}{To this end}, time is discretised into a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$ is the total number of time steps.
-Once the nodal equilibrium equation is solved, the values at the nodes are interpolated back into the particles, which are advected
+\textcolor{blue}{Equation \eqref{eq:BalanceMomentum_wf_discretized} is a second order ordinary differential equation in time and a time integration scheme is required.} \textcolor{blue}{To this end, time is discretised into a finite set of time steps $k = 1\ldots ,Nt$, where $k$ is the current time step and $N_t$ is the total number of time steps.} Once the nodal equilibrium equation is solved, the values at the nodes are interpolated back into the particles, which are advected
 to the new position through:
@@
 Traditionally, Eqs. \eqref{eq:BalanceMomentum_wf_discretized} and ~\eqref{eq:Updated_Lagrangian},
-are solved with an explicit forward Euler algorithm. In the following subsection, this \textcolor{green}{well known algorithm} and the proposed schemes are described.
+are solved with an explicit forward Euler algorithm. In the following subsection, \textcolor{blue}{this well known algorithm and the proposed schemes are described.}
 
@@
 like \cite{Guilkey_2003,Charlton_2017,Tran2019e}. In the
-first publication on \acrshort{mpm} \cite{Sulsky1994}, the nodal acceleration
-was \textcolor{green}{considered} to update the particles \textcolor{green}{by}
+first publication on \acrshort{mpm} \cite{Sulsky1994}, \textcolor{blue}{the nodal acceleration
+was considered to update the particles by}
 \begin{equation}
@@
 \end{equation}
-However, as Andersen (2009)\cite{thesis_Andersen_2009} pointed out, this algorithm has been shown to be numerically unstable due to \textcolor{green}{the fact} that nodal forces can be infinite for an infinitesimal nodal mass $\tens{m}_I$.
+However, as Andersen (2009)\cite{thesis_Andersen_2009} pointed out, this algorithm has been shown to be numerically unstable due to \textcolor{red}{the fact} that nodal forces can be infinite for an infinitesimal nodal mass $\tens{m}_I$.
 This issue may lead to numerical problems when nodal acceleration is obtained in the evaluation of the Eqs.
@@
 (1993)\cite{Geranlized_alpha_1993}, but with the particularity that
-the acceleration is evaluated both \textcolor{green}{at} the beginning and \textcolor{green}{at} the end of the time step.
+the acceleration is evaluated both \textcolor{red}{at} the beginning and \textcolor{red}{at} the end of the time step.
 \begin{equation}
@@
 
-In this section, an explicit predictor-corrector time integration
-scheme is proposed, \textcolor{green}{which} is based on the Newmark central differences explicit scheme. This method is devoted to solve  system of equations of the type
+\textcolor{blue}{In this section, an explicit predictor-corrector time integration
+scheme is proposed, which is based on the Newmark central differences explicit scheme.} This method is devoted to solve  system of equations of the type
+{\color{red}
 \begin{equation*}
@@
 \end{equation*}
+}
 The nodal \acrshort{mpm} stage allows to apply this method
 within the \acrshort{mpm} framework in a similar manner that the one
-proposed by Tran~\textit{et al.}~\cite{Tran2019e}. By using the predictor \textcolor{green}{step}  it is possible to calculate nodal velocities and update particles position employing nodal values
+proposed by Tran~\textit{et al.}~\cite{Tran2019e}. By using the predictor \textcolor{blue}{step}  it is possible to calculate nodal velocities and update particles position employing nodal values
 of velocity and acceleration.
@@
 \cite{Xiaojian94}. The ``classic'' \acrfull{npc} algorithm starts with a
-predicted value of the nodal velocities at the $(k+1)$th time step, denoted by $\vec{v}_{I}^{pred}$, which is calculated as follows:
+predicted value of the nodal velocities at the $(k+1)$th time step, {\color{blue}denoted by $\vec{v}_{I}^{pred}$, which is calculated as follows:
 \begin{equation}
@@
 \end{equation}
-
+}
 The \textit{user-defined}
-parameter $\gamma \geq 0$ that appears in \sout{In} \eqref{eq:Predictor-velocity-I}, influences both the predictor accuracy
+parameter $\gamma \geq 0$ that appears in \eqref{eq:Predictor-velocity-I}, influences both the predictor accuracy
 and the stability of the algorithm. As pointed out Liu
@@
 Bardenhagen \& Kober \cite{Bardenhagen2004} proved that through this information-transference technique mass and momentum are conserved.
-For a general particle variable $\Phi_p$ it is possible to get its nodal homologous $\Phi_I$ \textcolor{green}{by means of the \textit{ZZ} technique}  as:
+For a general particle variable $\Phi_p$ it is possible to get its nodal homologous $\Phi_I$ \textcolor{blue}{by means of the \textit{ZZ} technique as:}
+{\color{red}
 \begin{equation}
@@
  \end{equation}
+ }
  Therefore, to get an analogous expression for
@@
  procedure described in the equation \eqref{eq:Variational-recovery}
- is employed, \textcolor{green}{obtaining} the following expression:
+ is employed, \textcolor{red}{obtaining} the following expression:
+ {\color{red}
  \begin{equation}
@@
  \end{equation}
-\textcolor{green}{However} this way of computing the predictor stage can introduce instabilities due to numerical cancellation likewise the original Sulky algorithm.
-This \textcolor{green}{issue} can be avoided easily by the equivalent formulation inspired in the \textit{ZZ} technique,
+ }
+\textcolor{blue}{However}, this way of computing the predictor stage can introduce instabilities due to numerical cancellation likewise the original Sulky algorithm.
+This \textcolor{blue}{issue} can be avoided easily by the equivalent formulation inspired in the \textit{ZZ} technique,
+{\color{red}
 \begin{equation}
@@
 \end{equation}
+}
 This way of computing the nodal predictor is numerically stable
@@
 obtained, the \acrshort{dbc} are imposed over \gls{dirichlet-boundary}.
-Next the \textit{corrector}  \textcolor{green}{step} is introduced.
-\textcolor{green}{Predicted} nodal velocities obtained in \eqref{eq:Predictor-velocity-II}, \textcolor{green}{are now corrected by the equation}
+\textcolor{blue}{Next the \textit{corrector}  step is introduced.
+Predicted nodal velocities obtained in \eqref{eq:Predictor-velocity-II}, are now corrected by the equation}
 \begin{equation}
@@
 \textcolor{blue}{In our proposed scheme, accelerations \eqref{eq:Update-lagrangian-pce-a} and velocities \eqref{eq:Update-lagrangian-pce-v} are computed with information coming from the predictor step.
-On the other hand, positions \eqref{eq:Update-lagrangian-pce-u} are evaluated with information coming from the corrector step in the velocity term, while acceleration term introduces information from the corrector.} Therefore it share clear similarities with the \textit{leapfrog scheme} \cite{Zhang_book_2016}, where position is not updated at full time step, but the velocity is updated at half time steps.
+On the other hand, positions \eqref{eq:Update-lagrangian-pce-u} are evaluated with information coming from the corrector step in the velocity term, while acceleration term introduces information from the corrector.
+Therefore it shares clear similarities with the \textit{leapfrog scheme} \cite{Zhang_book_2016},} where position is not updated at full time step, but the velocity is updated at half time steps.
 Notice also that, with this approach, the calculation of nodal momentum values are not required.
@@
 
-\textcolor{green}{Following \cite{Arroyo2006}, entropy of a discrete random variable can be defined as the} uncertainty \textcolor{green}{of the} random variable.
-\textcolor{green}{A measure of this uncertainty can be obtained by means of Shannon's entropy}:
+\textcolor{blue}{Following \cite{Arroyo2006}, entropy of a discrete random variable can be defined as the uncertainty of the random variable.
+A measure of this uncertainty can be obtained by means of Shannon's entropy}:
 \begin{equation}
@@
 \end{equation}
-where $p_I$ \textcolor{green}{stand for probability of the random variable outcomes.
-By interpreting these probabilities as the shape functions $N_I(\vec{x})$ of an approximation scheme, equation \eqref{eq:Shannon-entropy} can be regarded as a measure of the uncerteinty of the approximation.} \textcolor{green}{Thus, according to Jaynes's principle of maximum entropy \cite{Jaynes1957},} the least-biased approximation scheme is
+where $p_I$ \textcolor{blue}{stands for probability of the random variable outcomes.
+By interpreting these probabilities as the shape functions $N_I(\vec{x})$ of an approximation scheme, equation \eqref{eq:Shannon-entropy} can be regarded as a measure of the uncertainty of the approximation.
+Thus, according to Jaynes's principle of maximum entropy \cite{Jaynes1957},} the least-biased approximation scheme is
 given by
@@
 \end{align*}
-To reach to a compromise between \textcolor{green}{the} two competing objectives, a Pareto set is \textcolor{green}{considered}  \cite{Arroyo2006}
+\textcolor{blue}{To reach a compromise between the two competing objectives, a Pareto set is considered}  \cite{Arroyo2006}
 \begin{align*}
@@
 \end{eqnarray}
-The regularization parameter $\beta$ of \acrshort{lme} shape functions may be controlled by adjusting a dimensionless parameter\footnote{\textcolor{blue}{To avoid confusion with the \gls{gamma-npc} parameter of the \acrshort{npc}, the dimensionless parameter defined by Arroyo \& Ortiz \cite{Arroyo2006} as $\gamma$ will be represent by \gls{LME-gamma} to preserve as much as possible the original notation.}}, \textcolor{green}{$\widehat{\gamma}=\beta h^2$} \cite{Arroyo2006}, where $h$ is defined as a measure of the nodal
+The regularization parameter $\beta$ of \acrshort{lme} shape functions may be controlled by adjusting a dimensionless parameter\footnote{\textcolor{blue}{To avoid confusion with the \gls{gamma-npc} parameter of the \acrshort{npc}, the dimensionless parameter defined by Arroyo \& Ortiz \cite{Arroyo2006} as $\gamma$ will be represent by \gls{LME-gamma} to preserve as much as possible the original notation.}}, \textcolor{blue}{$\widehat{\gamma}=\beta h^2$} \cite{Arroyo2006}, where $h$ is defined as a measure of the nodal
 spacing. 
@@
 Furthermore, with a conveniently adopted \textit{regularization} parameter it is possible to get a \acrshort{gimp}-like shape function.
-Finally \acrshort{sph}-like behaviour can be obtained for lower values of \textcolor{green}{$\widehat{\gamma}$} since the support of the shape function is drastically increased, and therefore \textit{smoother} solutions are obtained.
+Finally \acrshort{sph}-like behaviour can be obtained for lower values of \textcolor{blue}{$\widehat{\gamma}$} since the support of the shape function is drastically increased, and therefore \textit{smoother} solutions are obtained.
 See \cite{Navas2016} for an application of this capability, where oscillations due to excess of pore water pressure in consolidation problems are smoothed out by using this technique.
@@
 \textcolor{blue}{This behaviour was noticed previously by \cite{Arroyo2006}, were authors highlighted how, by adjusting the spatial variation of $\beta(\vec{x})$, it is possible to select regions of the domain of analysis which are treated by finite elements and regions that are treated in the style of meshfree methods, with seamless transitions between those regions.
-The aforementioned adaptability can be appreciated in figure~\ref{fig:LME_MPM}} \\
+The aforementioned adaptability can be appreciated in figure~\ref{fig:LME_MPM}.} \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Concerning the convex domain requirement, Arroyo \& Ortiz~\cite{Arroyo2006} briefly discussed the existence of non-convex domains, and proposed some solutions to it.
-For instance, the possibility of replacing the Euclidean distance $\lVert x - x_a \rVert$ in the definition of the shape functions by the length of the shortest path contained within the domain connecting $x$ and $x_a$.
-Or by decomposing the non-convex domain into convex sub-domains.
+For instance, the possibility of replacing the Euclidean distance $\lVert x - x_a \rVert$ in the definition of the shape functions by the length of the shortest path contained within the domain connecting $x$ and $x_a$; or by decomposing the non-convex domain into convex sub-domains.
 Of course the requirement of convex domain is not exclusive from \textit{max-ent}, it also concerns to the remaining interpolation techniques in the \acrshort{mpm} and other meshfree methods.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the proposed example, the simulation extends from time zero up to \textcolor{green}{$10^{-4}$} s.
+In the proposed example, the simulation extends from time zero up to \textcolor{blue}{$10^{-4}$} s.
 This time interval allows the elastic wave to travel a distance of 2.6
@@
 particles in the left border of the bar. This problem arises
-when the mesh size is small enough that relative displacement of the particles is larger \textcolor{green}{than} the distance to the border, so grid crossing phenomena could appear even in those cases with infinitesimal displacements.
+when the mesh size is small enough that relative displacement of the particles is larger \textcolor{red}{than} the distance to the border, so grid crossing phenomena could appear even in those cases with infinitesimal displacements.
 In this case, an analytical solution can be obtained through the characteristics method, described in the appendix~\ref{app:analytical_sol}.
 \textcolor{blue}{This section contains a large number of comparisons, which have been summarised in Table \ref{tab:dyka-cases-summarized}.
-FFirst, we analyze the convergence of the time integration scheme for different mesh sizes, and the interpolation techniques, \ref{sec:Convergence-analysis}.
-Later, we focus on how each combination of interpolation technique and time integration scheme is able to damp the numerical noise: comparison between \acrshort{fe} and \acrshort{npc}, \ref{sec:FE-vs-NPC}, the response of the \acrshort{lme} approximation for different $\widehat{\gamma}$ values,  \ref{sec:Sensitive-analysis-gamma}, the well known \acrshort{ugimp} shape function is compared with the \acrshort{lme} approximation, \ref{sec:LME-vs-uGIMP}, and finally a comparison between the \acrshort{otm} method \textit{versus} the \acrshort{mpm}, using the same time integration scheme and interpolation technique, \ref{sec:OTM-vs-MPM}.}
+First, the convergence of the time integration scheme for different mesh sizes, and the interpolation techniques is analyzed in  \ref{sec:Convergence-analysis}.
+Later, interest focuses on how each combination of interpolation technique and time integration scheme is able to damp the numerical noise by: the comparison between \acrshort{fe} and \acrshort{npc}, \ref{sec:FE-vs-NPC}; the response of the \acrshort{lme} approximation for different $\widehat{\gamma}$ values,  \ref{sec:Sensitive-analysis-gamma}; the comparison between the well-known \acrshort{ugimp} shape function against the \acrshort{lme} approximation, \ref{sec:LME-vs-uGIMP}, and finally a comparison between the \acrshort{otm} method \textit{versus} the \acrshort{mpm}, using the same time integration scheme and interpolation technique, \ref{sec:OTM-vs-MPM}.}
 
@@
 \textcolor{blue}{Figure \eqref{fig:Dyka-error-evol} also highlights how on the one hand the slope of the \acrshort{lme} error decreases monotonously for the lower $\widehat{\gamma}$ values up to the \textit{grid-crossing region}, where more error accumulates.
-And on the other hand, the slope of the error is punished for the higher values of $\widehat{\gamma}$ in \acrshort{lme}, \acrshort{ugimp} or bi-linear shape functions.
+And, on the other hand, the slope of the error is punished for the higher values of $\widehat{\gamma}$ in \acrshort{lme}, \acrshort{ugimp} or bi-linear shape functions.
 This occurs earlier than in the previous case, during the \textit{transition region}.}
@@
 \textcolor{blue}{Finally, notice the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5 millimeters in figure \eqref{fig:Dyka-error-evol}.
-The reason is due to an unstable increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yield unacceptable results.
+The reason is due to an unstable increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yields unacceptable results.
 A feasible explanation for this phenomena could be the presence of numerical cancellation which could produce gaps between voxels.
@@
 The oscillations of the \acrshort{npc} almost disappeared before reaching subsequent jump discontinuities, while those of \acrshort{fe} do not.
-Moreover, oscillations of the \acrshort{fe} seams to increase further after each jump discontinuity and an unstable tendency can by foreseen.
+Moreover, oscillations of the \acrshort{fe} seems to increase further after each jump discontinuity and an unstable tendency can by foreseen.
 This unstable tendency is not appreciated in the \acrshort{npc} integration scheme.}
@@
 
-Figure \eqref{fig:Dyka-LME-gamma} shows the sensitivity of the \acrshort{lme}
+\textcolor{blue}{Figure \eqref{fig:Dyka-LME-gamma} shows the sensitivity of the \acrshort{lme}
 approximation scheme to variations in the parameter
 $\widehat{\gamma}$, which is the one that controls the value of the regularization parameter
-$\beta$ \textcolor{green}{together with the nodal spacing parameter $h$}.
-\textcolor{green}{It can be observed that for} lower values of $\widehat{\gamma}$ the numerical solution presents a faster decay of the spurious oscillations.
+$\beta$ together with the nodal spacing parameter $h$.
+It can be observed that for lower values of $\widehat{\gamma}$ the numerical solution presents a faster decay of the spurious oscillations.
 This capability could be useful in simulations where
@@
 For larger mesh sizes, where the relative particle displacement is negligible in comparison with the cell size, the global behaviour is \acrshort{fem}-like, therefore, larger values of $\widehat{\gamma}$ may offer better results.
-On the other hand, when mesh size is small enough to produce grid-crossing, meshfree behaviour is required to ensure the convergence of the solution and tiny values of $\widehat{\gamma}$ may lead to better performances.
+On the other hand, when mesh size is small enough to produce grid-crossing, meshfree behaviour is required to ensure the convergence of the solution and tiny values of $\widehat{\gamma}$ may lead to better performances.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \caption{Sensitivity  of LME approximants performance to changes in the
-    dimensionless regularization parameter \textcolor{green}{$\widehat{\gamma}$}. To illustrate it, the velocity evolution at the point in the bar left side is plotted.}
+    dimensionless regularization parameter \textcolor{blue}{$\widehat{\gamma}$}. To illustrate it, the velocity evolution at the point in the bar left side is plotted.}
   \label{fig:Dyka-LME-gamma}
@@
 
-The performance of the \acrshort{ugimp}~\cite{Bardenhagen2004} shape function \textit{versus} the \acrshort{lme} approximation scheme with a dimensionless regularization parameter $\widehat{\gamma}$ of 4.0 is compared in Figure \ref{fig:Dyka-uGIMP-LME}.
+\textcolor{blue}{The performance of the \acrshort{ugimp}~\cite{Bardenhagen2004} shape function \textit{versus} the \acrshort{lme} approximation scheme with a dimensionless regularization parameter $\widehat{\gamma}$ of 4.0 is compared in Figure \ref{fig:Dyka-uGIMP-LME}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- Although remarkable differences are not observed under a regular mesh, \textcolor{green}{\acrshort{lme} approximants seems to fits better than \acrshort{ugimp} after the jump.}
+ Although remarkable differences are not observed under a regular mesh, \acrshort{lme} approximants seems to fits better than \acrshort{ugimp} after the jump.}
 
@@
 
-Finally, the \acrshort{mpm} \textcolor{green}{approach is compared with the \acrfull{otm}~\cite{Li2010} method, both with same time integration scheme, spatial discretisation and interpolation technique}.
-Results \textcolor{green}{of the comparison} are shown in figure \ref{fig:Dyka-OTM-MPM}.
-During the first half of the simulation both \textcolor{green}{methods} seem to perform in a similar way, but during the second half of the simulation after the elastic wave has \textcolor{green}{traveled} from the free border to
-the fixed one and back, in \acrshort{otm} the solution becomes more noisy than the one performed by \acrshort{mpm} .   
+\textcolor{blue}{Finally, the \acrshort{mpm} approach is compared with the \acrfull{otm}~\cite{Li2010} method, both with same time integration scheme, spatial discretisation and interpolation technique.
+Results of the comparison are shown in figure \ref{fig:Dyka-OTM-MPM}.
+During the first half of the simulation both methods seem to perform in a similar way, but during the second half of the simulation after the elastic wave has traveled from the free border to
+the fixed one and back, in \acrshort{otm} the solution becomes more noisy than the one performed by \acrshort{mpm}.}   
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 interpolation technique to deal with grid crossing instabilities.
-\textcolor{green}{A solid elastic square block is} incrementally loaded \textcolor{green}{only considering} body forces.
-Details of the problem are sketched in figure~\ref{fig:block}
+\textcolor{blue}{A solid elastic square block is incrementally loaded only considering body forces.} Details of the problem are sketched in figure~\ref{fig:block}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In order to get a stable solution, time step was conducted by a
-Courant number of 0.1. On the other hand, the explicit
-predictor-corrector scheme \textcolor{green}{proposed in previous sections} is employed. For the initial spatial discretisation four particles per cell
+Courant number of 0.1. \textcolor{blue}{On the other hand, the explicit
+predictor-corrector scheme proposed in previous sections is employed.} For the initial spatial discretisation four particles per cell
 ($\Delta x = 2\ m$) were adopted. The initial layout of particles inside of the
@@
 position corresponds to the location of the gauss-points in a standard
-quadratic finite element. For the \acrshort{ugimp} shape function the initial
-position of each particle is located in the center of each voxel \textcolor{green}{as} in the initial situation voxel domains should not overlap.
+quadratic finite element. \textcolor{blue}{For the \acrshort{ugimp} shape function the initial
+position of each particle is located in the center of each voxel as in the initial situation voxel domains should not overlap.}
 
@@
 block.
-\textcolor{green}{This figure shows how the \acrshort{mpm} simulation performed with a bi-linear interpolation technique (Q4) turns out to be unstable during cell-crossing and consequently fail}.
-\textcolor{green}{The \acrshort{lme} simulation was performed using two kinds of shape functions, one with a low value of the dimensionless parameter, $\widehat{\gamma} = 0.8$, and other with a larger value of it, $\widehat{\gamma} = 3.0$.
-Both simulations behaves with minimal oscillations, also not appreciable difference is observed between them.
+\textcolor{blue}{This figure shows how the \acrshort{mpm} simulation, performed with a bi-linear interpolation technique (Q4), turns out to be unstable during cell-crossing and consequently fail.
+The \acrshort{lme} simulation was performed using two kinds of shape functions, one with a low value of the dimensionless parameter, $\widehat{\gamma} = 0.8$, and other with a larger value of it, $\widehat{\gamma} = 3.0$.
+Both simulations behave with minimal oscillations; also not appreciable differences are observed between them.
 The \acrshort{ugimp} simulation is more stable than the one performed with the \acrshort{mpm}-Q4 and behaves like the \acrshort{lme} simulations.
-Finally, we have compared our results against two contrasted techniques.
+Finally, these results are compared against two contrasted techniques.
 The \acrshort{fem} solution has been done with a regular mesh of linear quadrilaterals, meanwhile the \acrshort{otm} solution has been done with \acrshort{lme} approximation.
@@
 
-\subsection{Velocity waves in an elastic domain}
+\subsection{2D elastic wave propagation}
 \label{sec:Velocity-waves-elastic-domain}
 
-\textcolor{blue}{The following test is intended to validate the ability of the discussed time integration schemes to reproduce 2D wave propagation problems.
-It consists of the side impact of a moving elastic square.
-The square was 50 x 50 m  and modeled with the following elastic parameters :
+\textcolor{blue}{The following test is intended to validate the ability of the discussed time integration schemes in order to reproduce the wave propagation in 2D.
+The impact of an elastic square plate against a vertical wall is assessed.
+The square plate dimensions are 50 x 50 m and their elastic parameters are:
 \begin{itemize} 
@@
 }
-\textcolor{blue}{The background set of nodes consists of a cartesian grid with a uniform gap between nodes of 1 m, and four material points per cell were considered.
-The courant number is fixed to 0.1 during the whole simulation and $\text{LME}_{3.0}$ shape functions where used.
-The square initially move horizontally through the grid at $\text{V}_0 = 1.0 m/s$ until it hits an obstacle modelled as a set of nodes with zero velocity prescribed.
-The collision produce stress waves and cause the square to bounce back.
-Snapshots of velocity field magnitude within the square are given in figure
-~\ref{fig:Magnitude_velocity_impact_square}}. 
+\textcolor{blue}{The background set of nodes is composed by a cartesian grid with an uniform spatial discretisation of 1 m.
+Four material points per cell are considered.
+The Courant number is fixed to 0.1 during the whole simulation and $\text{LME}_{3.0}$ shape functions are employed.
+A horizontal velocity of the square plate of $\text{V}_0 = 1.0 m/s$ until the shock against the obstacle, which has been modelled as a set of nodes with prescribed velocity equal to zero.
+Stress waves are produced by the aforementioned shock what causes the square to bounce back.
+Both \acrshort{NPC} and \acrshort{FE} schemes are compared.
+Spatial distribution of the velocity field inside the square plate obtained with both schemes at different times are given in figure ~\ref{fig:Magnitude_velocity_impact_square}}.
 %%%%%%%%%%%%%%%%
@@
   }
-  \caption{Snapshots of velocity magnitudes in an elastic square impacted at a point on the right edge. The top row is for \acrshort{npc} updates and the bottom row is for \acrshort{fe} updates.}
+  \caption{Spatial distribution of the magnitude of the velocity field in an elastic square plate impacted on the right edge.
+The top row depicts the \acrshort{npc} results meanwhile the bottom row represents the \acrshort{fe} ones at different instants.}
   \label{fig:Magnitude_velocity_impact_square}
@@
 %%%%%%%%%%%%%%%% 
-\textcolor{blue}{At early times, \acrshort{npc} and \acrshort{fe} are similar.
-At later times, the \acrshort{fe} introduces significant numerical noise as compared with \acrshort{npc}.
-At the end of the simulation, the filtering process when \acrshort{npc} is used leads to a negligible loss of mechanical energy (about 0.1\%).
-Finally, let us consider an unstructured background mesh.}
+\textcolor{blue}{At early times, \acrshort{npc} and \acrshort{fe} behvae in a similar manner.
+However, at later times, the \acrshort{fe} scheme introduces significant numerical noise compared with the \acrshort{npc} one.
+At the end of the simulation, the filtering process when \acrshort{npc} is used leads to a negligible loss of mechanical energy (about 0.1\%).}
+
+\textcolor{blue}{Finally, an unstructured background mesh is proposed in order to validate the performance of the \acrshort{lme} shape function against the \acrshort{ugimp} one.}
 %%%%%%%%%%%%%%%%
@@
   }
-  \caption{Sensitive of \acrshort{ugimp} and \acrshort{lme} to the randomness in the layout of the background set of nodes.
-On the left side of the image we can see sketches of the two meshes that have been used.
-And on the right side, snapshots with the velocity magnitudes in each case.
-All the simulation where carried out with the proposed \acrshort{npc}.}
+  \caption{Sensitivity analysis of \acrshort{ugimp} and \acrshort{lme} schemes to the randomness in the layout of the background set of nodes.
+On the left column, sketches of the two employed meshes are depicted.
+On the right side, spatial distribution of the velocity magnitudes are shown for each case.
+All the simulation where carried out with the proposed \acrshort{npc} scheme.}
   \label{fig:Magnitude_velocity_impact_square_structured_unestructured}
@@
 %%%%%%%%%%%%%%%%
-\textcolor{blue}{ As we can see in figure~\ref{fig:Magnitude_velocity_impact_square_structured_unestructured}, the \acrshort{lme} approximation preserves the solution even though the mesh is not structured.
+\textcolor{blue}{ As it is observed in figure~\ref{fig:Magnitude_velocity_impact_square_structured_unestructured}, the \acrshort{lme} approximation preserves the solution even though the mesh is not structured.
 Meanwhile, the \acrshort{ugimp} is not able to deal with the unstructured mesh as expected.
-It goes without saying that there is no point in using unstructured meshes in this type of situation.
-Despite this, the \acrshort{lme} approach shows remarkable robustness in dealing with an unstructured mesh.
-This is useful in more complicated computational domains where structured mesh are not possible.}
+%It goes without saying that there is no point in using unstructured meshes in this type of situation.
+%Despite this, 
+Thus, the \acrshort{lme} approach shows remarkable robustness in dealing with an unstructured mesh.
+This is useful when more complex domains are to be discretised since the employment of  structured mesh is not possible.}
 
@@
 We have proposed in this paper an enhanced methodology which improves \acrfull{mpm} behaviour in fast dynamics problems.
-Different time and space discretisation techniques have been presented and their performance being compared agains other approaches in \textcolor{green}{three} benchmark problems.
+Different time and space discretisation techniques have been presented and their performance being compared agains other approaches in three benchmark problems.
 First, a novel time integration scheme for \acrshort{mpm} has been carried out.
@@
 On the other hand, the spatial discretisation of the \acrshort{mpm} is enhanced thanks to the powerful skills of the \acrfull{lme} approximation scheme, which has been validated as a robust and versatile tool in the \acrshort{mpm} framework.
-It also comes up as a promising alternative to other approximation techniques, developed within the \acrshort{mpm} framework, in order to overcome grid crossing limitations and to avoid the constriction of the \acrshort{ugimp} of a regular mesh or a high density of particles per cell.
+It also comes up as a promising alternative to other approximation techniques, developed within the \acrshort{mpm} framework, in order to overcome grid crossing limitations and to avoid the constriction of the \acrshort{ugimp} of a regular mesh or a high density of particles per cell \textcolor{blue}{as was observed in section \ref{sec:Velocity-waves-elastic-domain}}.
 Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vec{x})$ through the finite strain

### 2020-09-10 Revisiones/PNA_MMP_Responses to the reviewers.tex
Cambios en la hoja de respuestas

@@
 Their comments have helped us to improve the paper.
-Changes to the original manuscript are given in  color \textcolor{blue}{red} for corrections and for modified text in the revised version.
+Changes to the original manuscript are given in  color \textcolor{red}{red} for corrections and  \textcolor{blue}{blue} for modified text in the revised version.
 A detailed response to both reviewers is given below.
@@
 Unfortunately, the \textit{max-ent} approximation can not be expressed as the conjugation of a standard shape function and a particle "characteristic" function.
-Furthermore, in order to improve the readability of the development of the MPM, the approach has been revised with a detailed explanation.
+However, in order to improve the readability of the MPM development, the approach has been revised with a detailed explanation.
 
@@
 Some requirements such as the need for a convex domain, as well as those derived from its calculation (the determination of the Lagrange Multipliers, specially at the boundaries, or the obtainment of the minimizer of the logarithmic function), make the usage of it a challenging tool.
+However, the results depicted in this manuscript will strengthen the motivation of its employment in order to mitigate typical MPM problems such as cell-crossing, stress instabilities and the use of unstructured mesh.
 
-On the other hand, the special case of non-convex domains was discussed by Arroyo \& Ortiz~\cite{Arroyo2006}.
+Concerning the first issue mentioned by the reviewer, the special case of non-convex domains was discussed by Arroyo \& Ortiz~\cite{Arroyo2006}.
 Some of the solutions proposed by the aforementioned authors are : the possibility of replacing the Euclidean distance $\lVert  x - x_a  \rVert$ in the definition of the shape functions by the length of the shortest path contained within the domain connecting $x$ and $x_a$.
 Or the decomposition of the non-convex domain into convex sub-domains.
-
-On the other hand, this topic has been extensively studied in the context of MLS-based meshfree methods, for instance visibility, diffraction, and constrained path criteria.
+This topic has also been extensively studied in the context of MLS-based meshfree methods, for instance visibility, diffraction, and constrained path criteria.
 These methods are directly applicable to local \textit{max-ent} approximation.
-
-However, the results depicted in this manuscript will strengthen the motivation of its employment in order to mitigate typical MPM problems such as cell-crossing, stress instabilities and the use of unstructured mesh.
 
@@
 However, any available technique employed to overcome this situation in the standard MPM can be translated to the \textit{max-ent} one thanks to the Kronecker-Delta property inherent to it \cite{Arroyo2006}.
-See for instance the work of Cortis {\it et al.} (2018) \cite{Cortis_et_al_2017_IJNME}.
+See for instance the work of Cortis {\it et al.} (2018) \cite{Cortis_et_al_2017_IJNME} as example of how DBC can be imposed in the MPM.
 
@@
 
-These interesting publications will be added to the state of art of the revised manuscript.
-In the humble opinion of the authors, the XPIC approach consists of the stabilisation of the solution through a novel transference procedure more than a time integration scheme.
-Nevertheless, the algorithm introduced in this research proposes the stabilisation within the adaptation of the predictor-corrector Newmark algorithm, traditionally employed within FEM schemes, for the MPM framework.
-Hence, both techniques can be employed simultaneously.
+These interesting publications will be added to the state of art of the revised manuscript.In the humble opinion of the authors, the XPIC approach is dedicated to mitigate the null space error produced during the transfer of information between particles and nodes.
+Therefore, it is related to the spatial discretisation in stead of temporal.
+Meanwhile, the algorithm introduced in this research proposes the stabilisation within the adaptation of the predictor-corrector algorithm, which has been used traditionally in FEM to deal with fast dynamics.
+To the author\textquotesingle s knowledge, this is the first attempt to adapt the  traditional predictor-corrector for the MPM framework.
 
@@
 
-Contrary to the reviewer's opinion, the provided results are capable to highlight the strong capabilities of the MPM Newmark Predictor-Corrector scheme (NPC).
+Contrary to the reviewer\textquotesingle s opinion, the provided results are capable to highlight the strong capabilities of the MPM Newmark Predictor-Corrector scheme (NPC).
 It is important to remark the extension of this research: in order to isolate the strength of the proposed methodology, covering spatial and time discretization, only linear elastic problems are assessed.
+
 Although the results presented in Ma {\it et al.} \cite{MA2009272} are impressive, the proposed examples are out of the scope of the present research.
-In order to reinforce the benefits of the proposed methodology and in analogy with the work of Hammerquist \& Nairn \cite{HAMMERQUIST2017724} (previously cited by the reviewer), a 2D wave propagation problem has been simulated.
+In order to reinforce the benefits of the proposed methodology, we propose a 2D wave propagation problem has been simulated.
+It is analogous to the work of Hammerquist \& Nairn \cite{HAMMERQUIST2017724} (previously cited by the reviewer).
 This new test highlights the capabilities of the NPC to reproduce complex wave patterns under challenging loads such as impacts.
-While at the simultanesly minimices the presence of numerical noise and preserves the solution.
+Which is more, it is able to reduce the presence of numerical noise compared with the FE solution.
+Additionally, the robustness of the local \textit{max-ent} approximation is exposed dealing with unstructured mesh.
 

### 2020-09-10 LME-MPM.tex
Change in figure 14
Cambios en la hoja de respuestas

@@
 Stress waves are produced by the aforementioned shock what causes the square to bounce back.
-Both \acrshort{NPC} and \acrshort{FE} schemes are compared.
+Both \acrshort{npc} and \acrshort{fe} schemes are compared.
 Spatial distribution of the velocity field inside the square plate obtained with both schemes at different times are given in figure ~\ref{fig:Magnitude_velocity_impact_square}}.
@@
 On the left column, sketches of the two employed meshes are depicted.
-On the right side, spatial distribution of the velocity magnitudes are shown for each case.
+On the right side, spatial distribution of the velocity magnitudes are shown for each case at second 2.66.
 All the simulation where carried out with the proposed \acrshort{npc} scheme.}

### 2020-09-11 LME-MPM.tex
Nueva cita

@@
 \textcolor{blue}{Other well known source of energy dissipation and numerical noise is the presence of a non-trivial null space of the linear operator that maps particles values onto nodal values.
-It was earlier identified by Brackbill~\cite{BRACKBILL1988469} as ringing instability in the \acrfull{pic} method.
+It was earlier identified by Brackbill (1984)~\cite{BRACKBILL1988469} as ringing instability in the \acrfull{pic} method.
 A recent development in the field of particle methods is a null-space filter engineered by Gritton \&
-Berzins~\cite{Gritton2017} which overcome this limitation but still introduce unwelcome damping.
-Later, Hammerquist \& Nairn~\cite{HAMMERQUIST2017724} introduced the XPIC as a parametric extension of the aforementioned research with excellent results.}
+Berzins (2017)~\cite{Gritton2017} which overcome this limitation but still introduce unwelcome damping.
+Later, Hammerquist \& Nairn (2017)~\cite{HAMMERQUIST2017724} introduced the XPIC as a parametric extension of the aforementioned research with excellent results.}
 
@@
 
-\textcolor{blue}{The following test is intended to validate the ability of the discussed time integration schemes in order to reproduce the wave propagation in 2D.
+\textcolor{blue}{This benchmark has been conveniently adapted from the one proposed by  Hammerquist \& Nairn (2017)~\cite{HAMMERQUIST2017724}, it is intended to validate the ability of the discussed time integration schemes in order to reproduce the wave propagation in 2D.
 The impact of an elastic square plate against a vertical wall is assessed.

### 2020-09-11 LME-MPM.tex
Cambios Miguel

--- 2020-09-10 LME-MPM.tex
@@
   \acrfull{mpm} has arisen in the recent years as an
-  alternative to \acrfull{fem} under the large
-  deformation regime. However, the simulation of shock waves
+  alternative to \acrfull{fem} under \sout{the} large
+  \textcolor{green}{deformations} \sout{deformation regime}. However, the simulation of shock waves
   propagation in the large deformation regime is still challenging
@@
   schemes as a robust substitute of the traditional shape function in
-  \acrshort{mpm}. \acrshort{lme} approximation may be regarded as a
+  \acrshort{mpm}. \sout{ \acrshort{lme} approximation may be regarded as a
   \textit{thermalization} of Delaunay triangulation which resolves the
@@
   with a single shape function family. Finally this paper demonstrates
-  the performance of both improvements through numerical examples.    
+  the performance of both improvements through numerical examples.} \textcolor{green}{The performance of both improvements is validated by the high quality results of the numerical examples}    
 \end{abstract}
@@
 \begin{itemize}
-\item We have proposed a new and efficient time integration scheme for the \acrshort{mpm} in order to dissipate spurious stress oscillations without damping the solution.
-\item The proposal of the \acrshort{lme} approximation technique
-  under the \acrshort{mpm} framework is a robust substitute of the
-  traditional shape functions.
-\item Our approach have clear benefits on large strain fast dynamic simulations, where the grid-crossing pathology appears. 
+\item \sout{We have proposed a} A new \textcolor{green}{accurate} and efficient time integration scheme for the \acrshort{mpm} is proposed.
+\sout{in order to dissipate spurious stress oscillations without damping the solution.}
+\item The \sout{proposal of the} \acrfull{lme} approximation technique  \sout{under the} is a robust substitute of the traditional shape functions \textcolor{green}{within the} \acrshort{mpm} framework .
+\item \sout{Our} \textcolor{green}{The proposed approach might improve} \sout{have clear benefits on}  large strain fast dynamic \acrshort{mpm} simulations \sout{, where the grid-crossing pathology appears.} as grid-crossing pathology are clearly mitigated.
 \end{itemize}
@@
 inaccuracies in both space and time discretisation by the employment of a
-suitable combination of the \acrshort{lme} family shape functions, and the proposal of an explicit predictor-corrector scheme. The advantages of
+suitable combination of the \acrshort{lme} family shape functions, and the proposal of an \sout{explicit} predictor-corrector scheme. The advantages of
 this approach will be illustrated through several demanding test cases on the elastic regime: the
@@
 research, first \acrshort{mpm} procedure is introduced in
-\ref{sec:derivation-mpm}, second the explicit predictor-corrector
+\ref{sec:derivation-mpm}, second the \sout{explicit} predictor-corrector
 time integration scheme is presented in \ref{sec:epc-algor-mpm}, and
@@
 compute the equilibrium equation. In what follows, we will adopt the
-following convention: \textcolor{blue}{Any vectorial field is defined with an overarrow as $\vec{\square}$}.
-Three kind of subscripts or superscripts are used within paper.
-The subscript $\square_p$ is used to define a particle
-variable. While the subscript $\square_I$ is reserved in this notation for denoting nodal
-variables. And finally, the superscript $\square^{\psi}$ involves a
-virtual magnitude. For the operators, the convention is: $\dot{\square}$ and
-$\ddot{\square}$ for the first and second time derivative, $\square \otimes
-\square$ means the dyadic operator, $\square \cdot \square$ and $\square \colon \square$ means the
-first and second contraction of a tensor, $\Div{\square}$ denotes the
+following convention: \textcolor{blue}{Any \sout{vectorial} \textcolor{green}{vector} field is defined with an overarrow as $\vec{\square}$}.
+Three kind of subscripts or superscripts are \sout{used within paper} \textcolor{green}{considered:} \sout{The} subscript $\square_p$ is used to define a particle
+variable, \sout{. While the} subscript $\square_I$ is reserved \sout{in this notation} for \sout{denoting} nodal variables, \sout{And finally, the} superscript $\square^{\psi}$ involves a
+virtual magnitude. \sout{For the operators, the convention is} \textcolor{green}{The convention adopted for the operators is as folows:} $\dot{\square}$ and
+$\ddot{\square}$ \textcolor{green}{are considered} for the first and second time derivative, $\square \otimes
+\square$ means the dyadic operator, $\square \cdot \square$ and $\square \colon \square$ \sout{means the first and second contraction of a tensor} \textcolor{green}{are the single and double contraction of tensor index}, $\Div{\square}$ denotes the
 divergence operator, and finally $\Grad{\square}$ and $\GradS{\square}$ denotes the gradient and its symmetric part.
@@
 the sketched in the figure~\ref{fig:Continuum-solid}, and \gls{contour} the boundaries of the domain defined by $\partial \Omega
-= \Gamma_d \cup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n = \emptyset$.
+= \Gamma_d \cup \Gamma_n$ \sout{and} \textcolor{green}{where} $\Gamma_d \cap  \Gamma_n = \emptyset$.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \eqref{eq:Rho-material-derivative}, represents the weak form
-formulation of the problem. Next, we will discretise the set of equations of the mathematical model using a double discretisation procedure, see figure~\ref{fig:MPM-discretization}.\\
+\sout{formulation} of the problem. Next, we will discretise the set of equations of the mathematical model using a double discretisation procedure, see figure~\ref{fig:MPM-discretization}.\\
 
 \textcolor{blue}{First, the velocity field and the virtual displacements fields are discretised in a finite set of nodes $\textbf{X} = \{ \vec{x}_I, I \in \mathcal{B} \} \subset \mathbb{R}^{2}$, where $\mathcal{B} = 1, \ldots, n_I$.
-An approximation of the continuum field can be obtained with the help of nodal values and an appropriate interpolation functions $N_I(\vec{x})$.
+An approximation of the continuum field can be obtained with the help of nodal values and \sout{an} appropriate interpolation functions $N_I(\vec{x})$.
 Also spatial derivatives of those quantities, such as gradients and divergences, are computed through the support of the background set of nodes as}
@@
 \end{align}
-\textcolor{blue}{Secondly, the continuum \gls{domain} is discretised with a finite set of material points (also denominated particles the manuscript) $\hat{\Omega} = \{ \vec{x}_p, p \in \mathcal{C} \} \subset \Omega$, where $\mathcal{C} = 1, \ldots, n_p$.
+\textcolor{blue}{Secondly, the continuum \gls{domain} is discretised with a finite set of material points (also \sout{denominated} \textcolor{green}{known as} particles \textcolor{green}{in this} \sout{the} manuscript) $\hat{\Omega} = \{ \vec{x}_p, p \in \mathcal{C} \} \subset \Omega$, where $\mathcal{C} = 1, \ldots, n_p$.
 Any particle field such as position, velocity, mass, volume and stress denoted by $\vec{x}_p$, $\vec{v}_p$, $m_p$, $V_p$ and $\tens{\sigma}_p$, respectively, are assigned to each material point.
@@
 As stated previously, an explicit forward Euler algorithm has been utilized widely within the \acrshort{mpm} methodology. This scheme has been described in detail by many researchers
-\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and can be sketched by the scheme of the figure~\ref{fig:MPM_algorithm}.
+\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} \textcolor{purple}{and can be sketched by the scheme of the figure~\ref{fig:MPM_algorithm}.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 }
-The nodal \acrshort{mpm} stage allows to apply this method
+\sout{The nodal \acrshort{mpm} stage} \textcolor{green}{The presence of a background grid of nodes} allows to apply this \textcolor{green}{integration} method
 within the \acrshort{mpm} framework in a similar manner that the one
@@
   \label{eq:Corrector-velocity}
-  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I}.
+  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k}}{\tens{m}_I}.
 \end{equation}
@@
 \end{align}
-\textcolor{blue}{In our proposed scheme, accelerations \eqref{eq:Update-lagrangian-pce-a} and velocities \eqref{eq:Update-lagrangian-pce-v} are computed with information coming from the predictor step.
+\textcolor{blue}{In \sout{our} \textcolor{green}{the} proposed scheme, accelerations \eqref{eq:Update-lagrangian-pce-a} and velocities \eqref{eq:Update-lagrangian-pce-v} are computed with information coming from the predictor step.
 On the other hand, positions \eqref{eq:Update-lagrangian-pce-u} are evaluated with information coming from the corrector step in the velocity term, while acceleration term introduces information from the corrector.
-Therefore it shares clear similarities with the \textit{leapfrog scheme} \cite{Zhang_book_2016},} where position is not updated at full time step, but the velocity is updated at half time steps.
+Therefore, \sout{it shares clear} \textcolor{green}{it can be appreciated some} similarities with the \textit{leapfrog scheme} \cite{Zhang_book_2016},} where position is not updated at full time step, but the velocity is updated at half time steps.
 Notice also that, with this approach, the calculation of nodal momentum values are not required.
@@
 By interpreting these probabilities as the shape functions $N_I(\vec{x})$ of an approximation scheme, equation \eqref{eq:Shannon-entropy} can be regarded as a measure of the uncertainty of the approximation.
-Thus, according to Jaynes's principle of maximum entropy \cite{Jaynes1957},} the least-biased approximation scheme is
-given by
+Thus, according to Jaynes's principle of maximum entropy \cite{Jaynes1957},} the least-biased approximation scheme \sout{is} \textcolor{green}{can be} given by
 \begin{align*}
@@
 \textcolor{blue}{This section contains a large number of comparisons, which have been summarised in Table \ref{tab:dyka-cases-summarized}.
-First, the convergence of the time integration scheme for different mesh sizes, and the interpolation techniques is analyzed in  \ref{sec:Convergence-analysis}.
-Later, interest focuses on how each combination of interpolation technique and time integration scheme is able to damp the numerical noise by: the comparison between \acrshort{fe} and \acrshort{npc}, \ref{sec:FE-vs-NPC}; the response of the \acrshort{lme} approximation for different $\widehat{\gamma}$ values,  \ref{sec:Sensitive-analysis-gamma}; the comparison between the well-known \acrshort{ugimp} shape function against the \acrshort{lme} approximation, \ref{sec:LME-vs-uGIMP}, and finally a comparison between the \acrshort{otm} method \textit{versus} the \acrshort{mpm}, using the same time integration scheme and interpolation technique, \ref{sec:OTM-vs-MPM}.}
+First, \sout{the convergence of the time integration scheme for different mesh sizes, and the interpolation techniques is analyzed in  \ref{sec:Convergence-analysis}} \textcolor{green}{a convergence study regarding the integration scheme and interpolation technique is performed}.
+\sout{ Later, interest focuses on how each combination of interpolation technique and time integration scheme is able to damp the numerical noise by the comparison between \acrshort{fe} and \acrshort{npc}, \ref{sec:FE-vs-NPC}}.
+\textcolor{green}{Second}, \textcolor{green}{comparison of the capabilities of the \acrshort{npc} and \acrshort{fe} algorithms to damp out numerical noise is analysed in \ref{sec:FE-vs-NPC}}.
+\textcolor{green}{Third}, the response of the \acrshort{lme} approximation for different $\widehat{\gamma}$ values \textcolor{green}{is study in}  \ref{sec:Sensitive-analysis-gamma}.
+\textcolor{green}{Fourth}, comparison between the well-known \acrshort{ugimp} shape function against the \acrshort{lme} approximation \textcolor{green}{is performed in} \ref{sec:LME-vs-uGIMP}.
+Finally, a comparison between the \acrshort{mpm} and the \acrfull{otm} method, using the same time integration scheme and interpolation technique, \textcolor{green}{is conducted in} \ref{sec:OTM-vs-MPM}.}
 
@@
 
-\textcolor{blue}{Figure \eqref{fig:Dyka-error-evol} also highlights how on the one hand the slope of the \acrshort{lme} error decreases monotonously for the lower $\widehat{\gamma}$ values up to the \textit{grid-crossing region}, where more error accumulates.
-And, on the other hand, the slope of the error is punished for the higher values of $\widehat{\gamma}$ in \acrshort{lme}, \acrshort{ugimp} or bi-linear shape functions.
-This occurs earlier than in the previous case, during the \textit{transition region}.}
-
-\textcolor{blue}{Finally, notice the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5 millimeters in figure \eqref{fig:Dyka-error-evol}.
-The reason is due to an unstable increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yields unacceptable results.
-A feasible explanation for this phenomena could be the presence of numerical cancellation which could produce gaps between voxels.
+\textcolor{blue}{Figure \eqref{fig:Dyka-error-evol} also highlights how on the one hand the slope of the \acrshort{lme} error decreases monotonously for the lower $\widehat{\gamma}$ values up to the \textit{grid-crossing region} \textcolor{green}{(dark grey region)}, where more error \sout{accumulates} \textcolor{green}{is accumulated}.
+\sout{And, On the other hand, the slope of the error is punished for the higher values of $\widehat{\gamma}$ in \acrshort{lme}, \acrshort{ugimp} or bi-linear shape functions.
+This occurs earlier than in the previous case, during the \textit{transition region}.} \textcolor{green}{On the other hand, when higher values of $\widehat{\gamma}$ are considered in \acrshort{lme} and also for the \acrshort{ugimp} and the bi-linear shape functions, the change in error slope occurs in the \textit{transition region} (middle grey region).
+It might be concluded that the latter methods are more sensitive to grid crossing than the former}}
+
+\textcolor{blue}{Finally, \sout{notice} the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5 millimeters in figure \eqref{fig:Dyka-error-evol} \textcolor{green}{is remarkable}.
+The reason is due to an unstable increasing \sout{of the} error suffered during \acrshort{ugimp} simulations \sout{of} \textcolor{green}{for} these mesh sizes.
+\sout{which yields unacceptable results.} A feasible explanation for this phenomena could be the presence of numerical cancellation which could produce gaps between voxels.
 Further research should be done in this direction for getting a better comprehension of this phenomenon.
@@
 
-\textcolor{blue}{A first comparison of the performance of both time integration schemes is presented in figure \ref{fig:Dyka-NPC-FE}.
+\textcolor{blue}{A \sout{first} comparison of the performance of both time integration schemes is presented in figure \ref{fig:Dyka-NPC-FE}.
 Both integration schemes show numerical oscillations with respect to the analytical solution all over the simulation time, being worse just after jump discontinuities.
@@
 
-\textcolor{blue}{Finally, the \acrshort{mpm} approach is compared with the \acrfull{otm}~\cite{Li2010} method, both with same time integration scheme, spatial discretisation and interpolation technique.
+\textcolor{blue}{Finally, the \acrshort{mpm} approach is compared with the \acrfull{otm}~\cite{Li2010} method, both with the same time integration scheme, spatial discretisation and interpolation technique.
 Results of the comparison are shown in figure \ref{fig:Dyka-OTM-MPM}.
@@
 In order to get a stable solution, time step was conducted by a
-Courant number of 0.1. \textcolor{blue}{On the other hand, the explicit
+Courant number of 0.1. \textcolor{blue}{\sout{On the other hand, the} The explicit
 predictor-corrector scheme proposed in previous sections is employed.} For the initial spatial discretisation four particles per cell
@@
 block.
-\textcolor{blue}{This figure shows how the \acrshort{mpm} simulation, performed with a bi-linear interpolation technique (Q4), turns out to be unstable during cell-crossing and consequently fail.
-The \acrshort{lme} simulation was performed using two kinds of shape functions, one with a low value of the dimensionless parameter, $\widehat{\gamma} = 0.8$, and other with a larger value of it, $\widehat{\gamma} = 3.0$.
-Both simulations behave with minimal oscillations; also not appreciable differences are observed between them.
+\textcolor{blue}{\textcolor{green}{No results can be appreciated for the \acrshort{mpm} simulation with a bi-linear interpolation technique (Q4) as a clear unstable behaviour is observed within the first time steps.} The \acrshort{lme} simulation was performed using two kinds of shape functions, one with a low value of the dimensionless parameter, $\widehat{\gamma} = 0.8$, and other with a larger value of it, $\widehat{\gamma} = 3.0$.
+Both simulations behave with minimal oscillations and no appreciable differences are observed between them.
 The \acrshort{ugimp} simulation is more stable than the one performed with the \acrshort{mpm}-Q4 and behaves like the \acrshort{lme} simulations.
@@
 The Courant number is fixed to 0.1 during the whole simulation and $\text{LME}_{3.0}$ shape functions are employed.
-A horizontal velocity of the square plate of $\text{V}_0 = 1.0 m/s$ until the shock against the obstacle, which has been modelled as a set of nodes with prescribed velocity equal to zero.
-Stress waves are produced by the aforementioned shock what causes the square to bounce back.
+A horizontal velocity of the square plate of $\text{V}_0 = 1.0 m/s$ \textcolor{green}{is considered} until the \sout{shock} \textcolor{green}{the plate impacts} against the obstacle \textcolor{green}{generating stress waves}.
+\textcolor{green}{The obstacle is} \sout{which has been} modelled as a set of nodes with prescribed velocity equal to zero.
+\sout{Stress waves are produced by the aforementioned shock what causes the square to bounce back}.
 Both \acrshort{npc} and \acrshort{fe} schemes are compared.
@@
 %%%%%%%%%%%%%%%% 
-\textcolor{blue}{At early times, \acrshort{npc} and \acrshort{fe} behvae in a similar manner.
+\textcolor{blue}{At early times, \acrshort{npc} and \acrshort{fe} behave in a similar manner.
 However, at later times, the \acrshort{fe} scheme introduces significant numerical noise compared with the \acrshort{npc} one.
-At the end of the simulation, the filtering process when \acrshort{npc} is used leads to a negligible loss of mechanical energy (about 0.1\%).}
+\sout{At the end of the simulation, the filtering process when \acrshort{npc} is used leads to a negligible loss of mechanical energy (about 0.1\%).}}
 
@@
 %Despite this, 
-Thus, the \acrshort{lme} approach shows remarkable robustness in dealing with an unstructured mesh.
-This is useful when more complex domains are to be discretised since the employment of  structured mesh is not possible.}
+Thus, the \acrshort{lme} approach \textcolor{green}{adopted in the present work} shows a remarkable robustness \sout{in} dealing with \sout{an} unstructured meshes.
+\sout{This is useful when more complex domains are to be discretised since the employment of  structured mesh is not possible.} \textcolor{green}{From this last comparison it can be deduced that \acrshort{lme}  might be an adequate choice approximation technique when dealing with complex domains where a structured mesh is usually not possible } }
 
@@
 \label{sec:conclusions}
-We have proposed in this paper an enhanced methodology which improves \acrfull{mpm} behaviour in fast dynamics problems.
-Different time and space discretisation techniques have been presented and their performance being compared agains other approaches in three benchmark problems.
-First, a novel time integration scheme for \acrshort{mpm} has been carried out.
-The \acrfull{npc}.
-The \acrshort{npc} has been shown to be a highly efficient alternative for demanding fast dynamics problems.
-In the literature, several approaches of the \acrshort{npc} are proposed in order to compete on accuracy with expensive implicit time integration algorithms.
-The main achievement of the proposed time discretisation has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.
-Also, the procedure employed to design the \acrshort{npc} algorithm opens the
-door to revisit a huge variety of time integration schemes developed
-originally for \acrshort{fem}, which can be implemented within a \acrshort{mpm} framework with the suitable modifications.
-In addition to the implementation of enhanced time integration schemes, further research can be done in the analysis of the good performance of the algorithm within non-linear solutions, such as the coupling between different phases or the non-linear constitutive behaviour of the materials: the employment of this scheme to strengthen the localization capabilities of \acrshort{mpm} for viscoplastic materials is on the scope of this research line.
-The comparison with traditional time schemes in the non-linear field will improve the formal understanding of the proposed methodology.
-
-On the other hand, the spatial discretisation of the \acrshort{mpm} is enhanced thanks to the powerful skills of the \acrfull{lme} approximation scheme, which has been validated as a robust and versatile tool in the \acrshort{mpm} framework.
+We have proposed in this paper an enhanced methodology which improves \acrfull{mpm} behaviour in fast dynamic problems.The proposed improvements implemented in the present work are twofold: First, the \acrfull{npc} time integration algorithm to update particles' information, and second, the \acrfull{lme} approximation scheme to define the shape functions.
+The performance of both improvements has been assessed with three different benchmarks: Dyka's bar, a solid block under gravity loading and 2D elastic waves propagation.
+
+The main achievements of the proposed time discretisation have been observed within Dyka's bar \ref{sec:dyka-bar}, where lower error values are obtained compared with the \acrfull{fe} scheme ones.
+Furthermore, the \acrshort{npc} approach has shown a more stable performance compared with the \acrshort{fe} scheme, being able to dump out spurious numerical oscillations where the \acrshort{fe} scheme could not.
+As per the promising results obtained with the \acrshort{npc} algorithm, the procedure employed in the present work opens the
+possibility to revisit a huge variety of time integration schemes developed
+originally for \acrshort{fem}, which can be implemented within a \acrshort{mpm} framework with few modifications.
+In addition to the implementation of enhanced time integration schemes, further research can be done in the analysis of the good performance of the algorithm within non-linear models, both material and geometric nonlinearity.
+
+Regarding the spatial discretisation the \acrfull{lme} approximation scheme has been validated as a robust and versatile tool in the \acrshort{mpm} framework.
 It also comes up as a promising alternative to other approximation techniques, developed within the \acrshort{mpm} framework, in order to overcome grid crossing limitations and to avoid the constriction of the \acrshort{ugimp} of a regular mesh or a high density of particles per cell \textcolor{blue}{as was observed in section \ref{sec:Velocity-waves-elastic-domain}}.
-Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vec{x})$ through the finite strain
-tensor in order to align the shape functions in the principal strain
-direction to select the most suitable set of nodes adapted to the strain as well as the possibility of adapting the value of $\beta$ to solve the equations
-\acrshort{fem}-like of meshfree-like depending of how behaves the
-region.
+Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vec{x})$ through the \sout{finite strain tensor} \textcolor{green}{deformation gradient} in order to align the shape functions in the principal strain direction to select the most suitable set of nodes adapted to the strain.
+\textcolor{green}{Another possibility could be to adapt} \sout{as well as the possibility of adapting} the value of $\beta$ to solve the equations
+\acrshort{fem}-like \sout{of} \textcolor{green}{or} meshfree-like depending \sout{of how behaves the region.} \textcolor{green}{on the behaviour of the region}.
 Together with the implementation of non-linear behaviours, previously mentioned, challenging scenarios could be reproduced, being the main purpose of the research line the simultaneous simulation of both initialization and

### 2020-09-11 Revisiones/PNA_MMP_Responses to the reviewers.tex
Updates from Overleaf
Final pedro

@@
 and Miguel Mart\'in-Stickle}
-\date{September 1, 2020}
+\date{September 11, 2020}
 
@@
 \\
+
 \textit{However, most of the applications presented in this manuscript are relatively simple and does not really demonstrate the capability of the proposed approach.
@@
 In the first version, aiming to make a readable manuscript, several examples were not shown.
-In this revised version, in order to clarify several questions of both reviewers, we have introduced an additional case of study which consists in the simulation of a side impact in an elastic square.
+In this revised version, in order to clarify several questions of both reviewers, we have introduced an additional case of study which consists in the simulation of a side impact in an elastic square plate.
 This test has been conveniently adapted from the work of Hammerquist \& Nairn \cite{HAMMERQUIST2017724}, where fast dynamics were also studied.
@@
 
-Authors really appreciate that the reviewer consider the present research as an interest piece of work. In order to improve the readability of the revised paper, a proofreading is made.\\
+Authors really appreciate that the reviewer consider the present research as an interest piece of work.
+In order to improve the readability of the revised paper, a proofreading is made.
+Changes are found in the revised manuscript on \textcolor{blue}{blue} colour.\\
 
@@
 
-These interesting publications will be added to the state of art of the revised manuscript.In the humble opinion of the authors, the XPIC approach is dedicated to mitigate the null space error produced during the transfer of information between particles and nodes.
-Therefore, it is related to the spatial discretisation in stead of temporal.
+These interesting publications will be added to the state of art of the revised manuscript.
+In the humble opinion of the authors, the XPIC approach is dedicated to mitigate the null space error produced during the transfer of information between particles and nodes.
+Therefore, it is related to the spatial discretisation instead of the temporal one.
 Meanwhile, the algorithm introduced in this research proposes the stabilisation within the adaptation of the predictor-corrector algorithm, which has been used traditionally in FEM to deal with fast dynamics.
-To the author\textquotesingle s knowledge, this is the first attempt to adapt the  traditional predictor-corrector for the MPM framework.
+To the author\textquotesingle s knowledge, this is the first attempt to adapt the  traditional predictor-corrector scheme for the MPM framework.
 
@@
 Although the results presented in Ma {\it et al.} \cite{MA2009272} are impressive, the proposed examples are out of the scope of the present research.
-In order to reinforce the benefits of the proposed methodology, we propose a 2D wave propagation problem has been simulated.
+In order to reinforce the benefits of the proposed methodology, we propose a 2D wave propagation problem.
 It is analogous to the work of Hammerquist \& Nairn \cite{HAMMERQUIST2017724} (previously cited by the reviewer).
-This new test highlights the capabilities of the NPC to reproduce complex wave patterns under challenging loads such as impacts.
-Which is more, it is able to reduce the presence of numerical noise compared with the FE solution.
-Additionally, the robustness of the local \textit{max-ent} approximation is exposed dealing with unstructured mesh.
+This new test highlights the capabilities of the NPC to reproduce complex wave propagation patterns under challenging loads such as impacts.
+Moreover, it is capable to reduce the presence of numerical noise compared with the FE solution.
+Additionally, the robustness of the local \textit{max-ent} approximation dealing with unstructured mesh is depicted.
 
@@
 
-\bibitem{Cortis_et_al_2017_IJNME}
-Cortis, Michael and Augarde, Charles and Coombs, William and Robinson, Scott and Brown, Michael and Brennan, Andrew.
-\newblock {Imposition of essential boundary conditions in the material point method}.
-\newblock {International Journal for Numerical Methods in Engineering}, 113, 2017.
+\bibitem{HAMMERQUIST2017724}
+Chad C. Hammerquist and John A. Nairn.
+\newblock {A new method for material point method particle updates that reduces noise and enhances stability}.
+\newblock {Computer Methods in Applied Mechanics and Engineering},  318: 724--738, 2017.
 
@@
 \newblock {A convected particle domain interpolation technique to extend applicability of the material point method for problems involving massive deformations}.
-\newblock {International Journal for Numerical Methods in Engineering}, 86(12) : 1435-1456, 2011.
+\newblock {International Journal for Numerical Methods in Engineering}, 86(12): 1435-1456, 2011.
 
-\bibitem{HAMMERQUIST2017724}
-Chad C. Hammerquist and John A. Nairn.
-\newblock {A new method for material point method particle updates that reduces noise and enhances stability}.
-\newblock {\em Computer Methods in Applied Mechanics and Engineering},  318:724--738, 2017.
+\bibitem{Arroyo2006}
+Arroyo, M. and Ortiz, M.
+\newblock{Local maximum-entropy approximation schemes: A seamless bridge between finite elements and meshfree methods}.
+\newblock{International Journal for Numerical Methods in Engineering},  65(13): 2167--2202, 2006.
+
+\bibitem{Cortis_et_al_2017_IJNME}
+Cortis, Michael and Augarde, Charles and Coombs, William and Robinson, Scott and Brown, Michael and Brennan, Andrew.
+\newblock {Imposition of essential boundary conditions in the material point method}.
+\newblock {International Journal for Numerical Methods in Engineering}, 113: 130--152, 2017.
 
 \bibitem{MA2009272}
-S. Ma and X. Zhang and X.M. Qiu.
+Ma, S., Zhang, X.  and  Qiu, X.M.
 \newblock{Comparison study of MPM and SPH in modeling hypervelocity impact problems}.
-\newblock{International Journal of Impact Engineering}, 36(2):272--282, 2009.
-
-\bibitem{Arroyo2006}
-Arroyo, M. and Ortiz, M..
-\newblock{Local maximum-entropy approximation schemes: A seamless bridge between finite elements and meshfree methods}.
-\newblock{International Journal for Numerical Methods in Engineering},  2006.
+\newblock{International Journal of Impact Engineering}, 36(2): 272--282, 2009.
 

### 2020-09-11 LME-MPM.tex

--- 2020-09-11 LME-MPM.tex
@@
 \begin{abstract}
-  \acrfull{mpm} has arisen in the recent years as an
-  alternative to \acrfull{fem} under the large
-  deformation regime. However, the simulation of shock waves
-  propagation in the large deformation regime is still challenging
-  under this approach due \textcolor{red}{to} the incapability of the standard \acrshort{mpm} time
+  \acrfull{mpm} has arisen in the recent years as an alternative to \acrfull{fem} under large
+  \textcolor{blue}{deformations}. However, the simulation of shock waves
+  propagation in the large deformation regime is still challenging  under this approach due to the incapability of the standard \acrshort{mpm} time
   integration scheme to filter spurious noises. To overcome it, we propose in this paper an explicit Predictor-Corrector time
@@
   schemes as a robust substitute of the traditional shape function in
-  \acrshort{mpm}. \acrshort{lme} approximation may be regarded as a
-  \textit{thermalization} of Delaunay triangulation which resolves the
-  degenerate cases resulting from the lack or uniqueness of the
-  triangulation. Furthermore, by modifying a regularization parameter,
-  they are able to behave finite element like or as a meshfree
-  method. This capability allows to face a wide range of physics
-  with a single shape function family. Finally this paper demonstrates
-  the performance of both improvements through numerical examples.    
+  \acrshort{mpm}. \textcolor{blue}{The performance of both improvements is validated by the high quality
+   results of the numerical examples}.
 \end{abstract}
@@
 inaccuracies in both space and time discretisation by the employment of a
-suitable combination of the \acrshort{lme} family shape functions, and the proposal of an explicit predictor-corrector scheme. The advantages of
+suitable combination of the \acrshort{lme} family shape functions, and the proposal of a predictor-corrector scheme. The advantages of
 this approach will be illustrated through several demanding test cases on the elastic regime: the
@@
 research, first \acrshort{mpm} procedure is introduced in
-\ref{sec:derivation-mpm}, second the explicit predictor-corrector
+\ref{sec:derivation-mpm}, second the predictor-corrector
 time integration scheme is presented in \ref{sec:epc-algor-mpm}, and
@@
 information and a set of background nodes is employed to
-compute the equilibrium equation. In what follows, we will adopt the
-following convention: \textcolor{blue}{Any vectorial field is defined with an overarrow as $\vec{\square}$}.
-Three kind of subscripts or superscripts are used within paper.
-The subscript $\square_p$ is used to define a particle
-variable. While the subscript $\square_I$ is reserved in this notation for denoting nodal
-variables. And finally, the superscript $\square^{\psi}$ involves a
-virtual magnitude. For the operators, the convention is: $\dot{\square}$ and
-$\ddot{\square}$ for the first and second time derivative, $\square \otimes
-\square$ means the dyadic operator, $\square \cdot \square$ and $\square \colon \square$ means the
-first and second contraction of a tensor, $\Div{\square}$ denotes the
-divergence operator, and finally $\Grad{\square}$ and $\GradS{\square}$ denotes the gradient and its symmetric part.
-Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are \textcolor{blue}{described} in subsection \ref{sec:derivation-mpm}, \ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.
+compute the equilibrium equation. \textcolor{blue}{The described methodology is sketched by the scheme of the figure~\ref{fig:MPM_algorithm}.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+%\sidecaption
+  \centering
+  \resizebox{0.8\hsize}{!}{
+    \includegraphics[width=\textwidth]{./Figures/MPM_scheme_horizontal}
+  }
+  \caption{Description of the three steps in \acrshort{mpm} standard algorithm.}
+  \label{fig:MPM_algorithm}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ In what follows, we will adopt the following convention: \textcolor{blue}{Any vector field is defined with an overarrow as $\vec{\square}$}.
+Three kind of subscripts or superscripts are  considered:  subscript $\square_p$ is used to define a particle variable,  subscript $\square_I$ is reserved for nodal variables, superscript $\square^{\psi}$ involves a virtual magnitude.
+\textcolor{blue}{The convention adopted for the operators is as folows:} $\dot{\square}$ and $\ddot{\square}$ \textcolor{blue}{are considered} for the first and second time derivative, $\square \otimes \square$ means the dyadic operator, $\square \cdot \square$ and $\square \colon \square$ \textcolor{blue}{are the single and double contraction of tensor index}, $\Div{\square}$ denotes the divergence operator, and finally $\Grad{\square}$ and $\GradS{\square}$ denotes the gradient and its symmetric part.
+Following, the \acrshort{mpm} methodology, the explicit predictor-corrector scheme and \acrshort{lme} approximation shape functions are \textcolor{red}{described} in subsection \ref{sec:derivation-mpm}, \ref{sec:epc-algor-mpm} and \ref{sec:local-max-ent} respectively.
 
@@
 the sketched in the figure~\ref{fig:Continuum-solid}, and \gls{contour} the boundaries of the domain defined by $\partial \Omega
-= \Gamma_d \cup \Gamma_n$ and $\Gamma_d \cap  \Gamma_n = \emptyset$.
+= \Gamma_d \cup \Gamma_n$  \textcolor{red}{where} $\Gamma_d \cap  \Gamma_n = \emptyset$.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{align}
-\textcolor{blue}{Secondly, the continuum \gls{domain} is discretised with a finite set of material points (also denominated particles the manuscript) $\hat{\Omega} = \{ \vec{x}_p, p \in \mathcal{C} \} \subset \Omega$, where $\mathcal{C} = 1, \ldots, n_p$.
+\textcolor{blue}{Secondly, the continuum \gls{domain} is discretised with a finite set of material points (also known as particles in this manuscript) $\hat{\Omega} = \{ \vec{x}_p, p \in \mathcal{C} \} \subset \Omega$, where $\mathcal{C} = 1, \ldots, n_p$.
 Any particle field such as position, velocity, mass, volume and stress denoted by $\vec{x}_p$, $\vec{v}_p$, $m_p$, $V_p$ and $\tens{\sigma}_p$, respectively, are assigned to each material point.
@@
 As stated previously, an explicit forward Euler algorithm has been utilized widely within the \acrshort{mpm} methodology. This scheme has been described in detail by many researchers
-\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009} and can be sketched by the scheme of the figure~\ref{fig:MPM_algorithm}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-%\sidecaption
-  \centering
-  \resizebox{0.8\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/MPM_scheme_horizontal}
-  }
-  \caption{Description of the three steps in \acrshort{mpm} standard algorithm.}
-  \label{fig:MPM_algorithm}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Other authors have proposed many others time integration alternatives
-like \cite{Guilkey_2003,Charlton_2017,Tran2019e}. In the
+\cite{Sulsky1994}, \cite{Bardenhagen2002}, \cite{thesis_Andersen_2009}. Other authors have proposed many others time integration alternatives like \cite{Guilkey_2003,Charlton_2017,Tran2019e}. In the
 first publication on \acrshort{mpm} \cite{Sulsky1994}, \textcolor{blue}{the nodal acceleration
@@
 }
-The nodal \acrshort{mpm} stage allows to apply this method
-within the \acrshort{mpm} framework in a similar manner that the one
+\textcolor{blue}{The presence of a background grid of nodes} allows to apply this \textcolor{red}{integration} method within the \acrshort{mpm} framework in a similar manner that the one
 proposed by Tran~\textit{et al.}~\cite{Tran2019e}. By using the predictor \textcolor{blue}{step}  it is possible to calculate nodal velocities and update particles position employing nodal values
@@
 \end{align}
-\textcolor{blue}{In our proposed scheme, accelerations \eqref{eq:Update-lagrangian-pce-a} and velocities \eqref{eq:Update-lagrangian-pce-v} are computed with information coming from the predictor step.
+\textcolor{blue}{In the proposed scheme, accelerations \eqref{eq:Update-lagrangian-pce-a} and velocities \eqref{eq:Update-lagrangian-pce-v} are computed with information coming from the predictor step.
 On the other hand, positions \eqref{eq:Update-lagrangian-pce-u} are evaluated with information coming from the corrector step in the velocity term, while acceleration term introduces information from the corrector.
-Therefore it shares clear similarities with the \textit{leapfrog scheme} \cite{Zhang_book_2016},} where position is not updated at full time step, but the velocity is updated at half time steps.
+Therefore, it can be appreciated some similarities with the \textit{leapfrog scheme} \cite{Zhang_book_2016},} where position is not updated at full time step, but the velocity is updated at half time steps.
 Notice also that, with this approach, the calculation of nodal momentum values are not required.
@@
     Calculate the total grid nodal forces by evaluating the right hand side of 
-    \eqref{eq:BalanceMomentum_wf_discretized} in the time step $k+1$.
+    \eqref{eq:BalanceMomentum_wf_discretized} with the information from the predictor step.
     In those nodes where $\Deriv{\vec{v}_I^{k}}{t} \big\rvert_{\Gamma_d} = 0$, the acceleration is fixed to zero and nodal forces are stored as reactions.\\
@@
 By interpreting these probabilities as the shape functions $N_I(\vec{x})$ of an approximation scheme, equation \eqref{eq:Shannon-entropy} can be regarded as a measure of the uncertainty of the approximation.
-Thus, according to Jaynes's principle of maximum entropy \cite{Jaynes1957},} the least-biased approximation scheme is
-given by
+Thus, according to Jaynes's principle of maximum entropy \cite{Jaynes1957},} the least-biased approximation scheme  \textcolor{red}{can be} given by
 \begin{align*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the proposed example, the simulation extends from time zero up to \textcolor{blue}{$10^{-4}$} s.
+In the proposed example, the simulation extends from time zero up to \textcolor{red}{$10^{-4}$} s.
 This time interval allows the elastic wave to travel a distance of 2.6
@@
 \textcolor{blue}{This section contains a large number of comparisons, which have been summarised in Table \ref{tab:dyka-cases-summarized}.
-First, the convergence of the time integration scheme for different mesh sizes, and the interpolation techniques is analyzed in  \ref{sec:Convergence-analysis}.
-Later, interest focuses on how each combination of interpolation technique and time integration scheme is able to damp the numerical noise by: the comparison between \acrshort{fe} and \acrshort{npc}, \ref{sec:FE-vs-NPC}; the response of the \acrshort{lme} approximation for different $\widehat{\gamma}$ values,  \ref{sec:Sensitive-analysis-gamma}; the comparison between the well-known \acrshort{ugimp} shape function against the \acrshort{lme} approximation, \ref{sec:LME-vs-uGIMP}, and finally a comparison between the \acrshort{otm} method \textit{versus} the \acrshort{mpm}, using the same time integration scheme and interpolation technique, \ref{sec:OTM-vs-MPM}.}
+First, a convergence study regarding the integration scheme and interpolation technique is performed in  \ref{sec:Convergence-analysis}.
+Second, comparison of the capabilities of the \acrshort{npc} and \acrshort{fe} algorithms to damp out numerical noise is analysed in \ref{sec:FE-vs-NPC}.
+Third, the response of the \acrshort{lme} approximation for different $\widehat{\gamma}$ values is study in  \ref{sec:Sensitive-analysis-gamma}.
+Fourth, comparison between the well-known \acrshort{ugimp} shape function against the \acrshort{lme} approximation is performed in \ref{sec:LME-vs-uGIMP}.
+Finally, a comparison between the \acrshort{mpm} and the \acrfull{otm} method, using the same time integration scheme and interpolation technique, is conducted in \ref{sec:OTM-vs-MPM}.}
 
@@
 
-\textcolor{blue}{Figure \eqref{fig:Dyka-error-evol} also highlights how on the one hand the slope of the \acrshort{lme} error decreases monotonously for the lower $\widehat{\gamma}$ values up to the \textit{grid-crossing region}, where more error accumulates.
-And, on the other hand, the slope of the error is punished for the higher values of $\widehat{\gamma}$ in \acrshort{lme}, \acrshort{ugimp} or bi-linear shape functions.
-This occurs earlier than in the previous case, during the \textit{transition region}.}
-
-\textcolor{blue}{Finally, notice the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5 millimeters in figure \eqref{fig:Dyka-error-evol}.
-The reason is due to an unstable increasing of the error suffered during \acrshort{ugimp} simulations of these mesh sizes which yields unacceptable results.
+\textcolor{blue}{Figure \eqref{fig:Dyka-error-evol} also highlights how on the one hand the slope of the \acrshort{lme} error decreases monotonously for the lower $\widehat{\gamma}$ values up to the \textit{grid-crossing region} (dark grey region), where more error is accumulated.
+On the other hand, when higher values of $\widehat{\gamma}$ are considered in \acrshort{lme} and also for the \acrshort{ugimp} and the bi-linear shape functions, the change in error slope occurs in the \textit{transition region} (middle grey region).
+It might be concluded that the latter methods are more sensitive to grid crossing than the former}.
+
+\textcolor{blue}{Finally,  the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5 millimeters in figure \eqref{fig:Dyka-error-evol} is remarkable.
+The reason is due to an unstable increasing \sout{of the} error suffered during \acrshort{ugimp} simulations for these mesh sizes.
 A feasible explanation for this phenomena could be the presence of numerical cancellation which could produce gaps between voxels.
@@
 In order to get a stable solution, time step was conducted by a
-Courant number of 0.1. \textcolor{blue}{On the other hand, the explicit
+Courant number of 0.1. \textcolor{blue}{The explicit
 predictor-corrector scheme proposed in previous sections is employed.} For the initial spatial discretisation four particles per cell
@@
 block.
-\textcolor{blue}{This figure shows how the \acrshort{mpm} simulation, performed with a bi-linear interpolation technique (Q4), turns out to be unstable during cell-crossing and consequently fail.
-The \acrshort{lme} simulation was performed using two kinds of shape functions, one with a low value of the dimensionless parameter, $\widehat{\gamma} = 0.8$, and other with a larger value of it, $\widehat{\gamma} = 3.0$.
-Both simulations behave with minimal oscillations; also not appreciable differences are observed between them.
+\textcolor{blue}{No results can be appreciated for the \acrshort{mpm} simulation with a bi-linear interpolation technique (Q4) as a clear unstable behaviour is observed within the first time steps.The \acrshort{lme} simulation was performed using two kinds of shape functions, one with a low value of the dimensionless parameter, $\widehat{\gamma} = 0.8$, and other with a larger value of it, $\widehat{\gamma} = 3.0$.
+Both simulations behave with minimal oscillations and no appreciable differences are observed between them.
 The \acrshort{ugimp} simulation is more stable than the one performed with the \acrshort{mpm}-Q4 and behaves like the \acrshort{lme} simulations.
@@
 The Courant number is fixed to 0.1 during the whole simulation and $\text{LME}_{3.0}$ shape functions are employed.
-A horizontal velocity of the square plate of $\text{V}_0 = 1.0 m/s$ until the shock against the obstacle, which has been modelled as a set of nodes with prescribed velocity equal to zero.
-Stress waves are produced by the aforementioned shock what causes the square to bounce back.
+A horizontal velocity of the square plate of $\text{V}_0 = 1.0 m/s$ is considered until the the plate impacts against the obstacle generating stress waves.
+The obstacle is modelled as a set of nodes with prescribed velocity equal to zero.
 Both \acrshort{npc} and \acrshort{fe} schemes are compared.
@@
 %%%%%%%%%%%%%%%% 
-\textcolor{blue}{At early times, \acrshort{npc} and \acrshort{fe} behvae in a similar manner.
+\textcolor{blue}{At early times, \acrshort{npc} and \acrshort{fe} behave in a similar manner.
 However, at later times, the \acrshort{fe} scheme introduces significant numerical noise compared with the \acrshort{npc} one.
-At the end of the simulation, the filtering process when \acrshort{npc} is used leads to a negligible loss of mechanical energy (about 0.1\%).}
+}
 
@@
 %Despite this, 
-Thus, the \acrshort{lme} approach shows remarkable robustness in dealing with an unstructured mesh.
-This is useful when more complex domains are to be discretised since the employment of  structured mesh is not possible.}
+Thus, the \acrshort{lme} approach adopted in the present work shows a remarkable robustness \sout{in} dealing with unstructured meshes.
+From this last comparison it can be deduced that \acrshort{lme}  might be an adequate choice approximation technique when dealing with complex domains where a structured mesh is usually not possible .}
 
@@
 \label{sec:conclusions}
-We have proposed in this paper an enhanced methodology which improves \acrfull{mpm} behaviour in fast dynamics problems.
-Different time and space discretisation techniques have been presented and their performance being compared agains other approaches in three benchmark problems.
-First, a novel time integration scheme for \acrshort{mpm} has been carried out.
-The \acrfull{npc}.
-The \acrshort{npc} has been shown to be a highly efficient alternative for demanding fast dynamics problems.
-In the literature, several approaches of the \acrshort{npc} are proposed in order to compete on accuracy with expensive implicit time integration algorithms.
-The main achievement of the proposed time discretisation has been observed within the Dyka's bar \ref{sec:dyka-bar}, obtaining lower values of the error than the ones obtained with the \acrfull{fe} scheme.
-Also, the procedure employed to design the \acrshort{npc} algorithm opens the
-door to revisit a huge variety of time integration schemes developed
-originally for \acrshort{fem}, which can be implemented within a \acrshort{mpm} framework with the suitable modifications.
-In addition to the implementation of enhanced time integration schemes, further research can be done in the analysis of the good performance of the algorithm within non-linear solutions, such as the coupling between different phases or the non-linear constitutive behaviour of the materials: the employment of this scheme to strengthen the localization capabilities of \acrshort{mpm} for viscoplastic materials is on the scope of this research line.
-The comparison with traditional time schemes in the non-linear field will improve the formal understanding of the proposed methodology.
-
-On the other hand, the spatial discretisation of the \acrshort{mpm} is enhanced thanks to the powerful skills of the \acrfull{lme} approximation scheme, which has been validated as a robust and versatile tool in the \acrshort{mpm} framework.
-It also comes up as a promising alternative to other approximation techniques, developed within the \acrshort{mpm} framework, in order to overcome grid crossing limitations and to avoid the constriction of the \acrshort{ugimp} of a regular mesh or a high density of particles per cell \textcolor{blue}{as was observed in section \ref{sec:Velocity-waves-elastic-domain}}.
-Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vec{x})$ through the finite strain
-tensor in order to align the shape functions in the principal strain
-direction to select the most suitable set of nodes adapted to the strain as well as the possibility of adapting the value of $\beta$ to solve the equations
-\acrshort{fem}-like of meshfree-like depending of how behaves the
-region.
-Together with the implementation of non-linear behaviours, previously mentioned, challenging scenarios could be reproduced, being the main purpose of the research line the simultaneous simulation of both initialization and
-propagation stages of fast landslides.
+We have proposed in this paper an enhanced methodology which improves \acrfull{mpm} behaviour in fast dynamic problems.\textcolor{blue}{The proposed improvements implemented in the present work are twofold: First, the \acrfull{npc} time integration algorithm to update particles' information, and second, the \acrfull{lme} approximation scheme to define the shape functions.
+The performance of both improvements has been assessed with three different benchmarks: Dyka's bar, a solid block under gravity loading and 2D elastic waves propagation.}
+
+\textcolor{blue}{The main achievements of the proposed time discretisation have been observed within Dyka's bar \ref{sec:dyka-bar}, where lower error values are obtained compared with the \acrfull{fe} scheme ones.
+Furthermore, the \acrshort{npc} approach has shown a more stable performance compared with the \acrshort{fe} scheme, being able to dump out spurious numerical oscillations where the \acrshort{fe} scheme could not}.
+As per the promising results obtained with the \acrshort{npc} algorithm, the procedure employed in the present work opens the possibility to revisit a huge variety of time integration schemes developed originally for \acrshort{fem}, which can be implemented within a \acrshort{mpm} framework with few modifications.
+In addition to the implementation of enhanced time integration schemes, further research can be done in the analysis of the good performance of the algorithm within non-linear models, both material and geometric nonlinearity.
+
+Regarding the spatial discretisation the \acrfull{lme} approximation scheme has been validated as a robust and versatile tool in the \acrshort{mpm} framework.
+It also comes up as a promising alternative to other approximation techniques, developed within the \acrshort{mpm} framework, in order to overcome grid crossing limitations and to avoid the constriction of the \acrshort{ugimp} of a regular mesh or a high density of particles per cell \textcolor{blue}{as it was observed in section \ref{sec:Velocity-waves-elastic-domain}}.
+Several research lines of the \acrshort{lme} scheme dive into the improvement of the methodology, focusing in the optimization of the calculation of the shape function and the possibility of adapting the parameter $\beta(\vec{x})$ through the \textcolor{red}{deformation gradient} in order to align the shape functions in the principal strain direction to select the most suitable set of nodes adapted to the strain.
+\textcolor{blue}{Another possibility could be to adapt}  the value of $\beta$ to solve the equations \acrshort{fem}-like \textcolor{red}{or} meshfree-like depending  \textcolor{red}{on the behaviour of the region}.
+Together with the implementation of non-linear behaviours, previously mentioned, challenging scenarios could be reproduced, being the main purpose of the research line the simultaneous simulation of both initialization and propagation stages of fast landslides.
 

### 2020-09-11 LME-MPM.tex

@@
 \normalsize
+{\color{blue}
 \begin{itemize}
-\item \sout{We have proposed a} A new \textcolor{green}{accurate} and efficient time integration scheme for the \acrshort{mpm} is proposed.
-\sout{in order to dissipate spurious stress oscillations without damping the solution.}
-\item The \sout{proposal of the} \acrfull{lme} approximation technique  \sout{under the} is a robust substitute of the traditional shape functions \textcolor{green}{within the} \acrshort{mpm} framework .
-\item \sout{Our} \textcolor{green}{The proposed approach might improve} \sout{have clear benefits on}  large strain fast dynamic \acrshort{mpm} simulations \sout{, where the grid-crossing pathology appears.} as grid-crossing pathology are clearly mitigated.
+\item A new accurate and efficient time integration scheme for the \acrshort{mpm} is proposed.
+\item The \acrfull{lme} approximation technique is a robust substitute of the traditional shape functions within the \acrshort{mpm} framework .
+\item The proposed approach might improve large strain fast dynamic \acrshort{mpm} simulations as grid-crossing pathology are clearly mitigated.  
 \end{itemize}
-
+}
 %\begin{highlights}
@@
 \eqref{eq:Constitutive-equation} and
-\eqref{eq:Rho-material-derivative}, represents the weak form
-\sout{formulation} of the problem. Next, we will discretise the set of equations of the mathematical model using a double discretisation procedure, see figure~\ref{fig:MPM-discretization}.\\
+\eqref{eq:Rho-material-derivative}, represents the weak form of the problem.
+Next, we will discretise the set of equations of the mathematical model using a double discretisation procedure, see figure~\ref{fig:MPM-discretization}.\\
 
 \textcolor{blue}{First, the velocity field and the virtual displacements fields are discretised in a finite set of nodes $\textbf{X} = \{ \vec{x}_I, I \in \mathcal{B} \} \subset \mathbb{R}^{2}$, where $\mathcal{B} = 1, \ldots, n_I$.
-An approximation of the continuum field can be obtained with the help of nodal values and \sout{an} appropriate interpolation functions $N_I(\vec{x})$.
+An approximation of the continuum field can be obtained with the help of nodal values and appropriate interpolation functions $N_I(\vec{x})$.
 Also spatial derivatives of those quantities, such as gradients and divergences, are computed through the support of the background set of nodes as}
@@
 \textcolor{blue}{Finally,  the absence of \acrshort{ugimp} values for a mesh size of 0.3325 and 0.5 millimeters in figure \eqref{fig:Dyka-error-evol} is remarkable.
-The reason is due to an unstable increasing \sout{of the} error suffered during \acrshort{ugimp} simulations for these mesh sizes.
+The reason is due to an unstable increasing error suffered during \acrshort{ugimp} simulations for these mesh sizes.
 A feasible explanation for this phenomena could be the presence of numerical cancellation which could produce gaps between voxels.
@@
 
-\textcolor{blue}{A \sout{first} comparison of the performance of both time integration schemes is presented in figure \ref{fig:Dyka-NPC-FE}.
+\textcolor{blue}{A comparison of the performance of both time integration schemes is presented in figure \ref{fig:Dyka-NPC-FE}.
 Both integration schemes show numerical oscillations with respect to the analytical solution all over the simulation time, being worse just after jump discontinuities.
@@
 %Despite this, 
-Thus, the \acrshort{lme} approach adopted in the present work shows a remarkable robustness \sout{in} dealing with unstructured meshes.
+Thus, the \acrshort{lme} approach adopted in the present work shows a remarkable robustness dealing with unstructured meshes.
 From this last comparison it can be deduced that \acrshort{lme}  might be an adequate choice approximation technique when dealing with complex domains where a structured mesh is usually not possible .}

### 2020-09-11 Revisiones/PNA_MMP_Responses to the reviewers.tex

@@
 \usepackage{amsmath}
+\usepackage{ulem}
 
@@
 
-Unfortunately, local \textit{max-ent} approximation technique only provides an efficient tool to transfer information from particles to nodes and vice versa to the MPM.
+Unfortunately, local \textit{max-ent} approximation technique only provides an efficient tool to transfer information from particles to nodes and vice versa \sout{to the MPM}.
 Hence, the difficulties of imposing Dirichlet boundary conditions (DBC) in the MPM persists since they are a direct consequence of discretising the continuum with material points instead of nodes, where traditionally DBC are imposed.
@@
 
-Contrary to the reviewer\textquotesingle s opinion, the provided results are capable to highlight the strong capabilities of the MPM Newmark Predictor-Corrector scheme (NPC).
+\sout{Contrary to the reviewer\textquotesingle s opinion,} In the authors' opinnion, the provided results are capable to highlight the \sout{strong} capabilities of the \acrshort{LME-}MPM-NPC proposed in the present work.
 It is important to remark the extension of this research: in order to isolate the strength of the proposed methodology, covering spatial and time discretization, only linear elastic problems are assessed.

### 2020-10-05 Revisiones/PNA_MMP_Responses to the reviewers.tex
Ok

--- 2020-09-11 Revisiones/PNA_MMP_Responses to the reviewers.tex
@@
 
-Unfortunately, local \textit{max-ent} approximation technique only provides an efficient tool to transfer information from particles to nodes and vice versa to the MPM.
+Unfortunately, local \textit{max-ent} approximation technique only provides an efficient tool to transfer information from particles to nodes and vice versa.
 Hence, the difficulties of imposing Dirichlet boundary conditions (DBC) in the MPM persists since they are a direct consequence of discretising the continuum with material points instead of nodes, where traditionally DBC are imposed.
@@
 
-Contrary to the reviewer\textquotesingle s opinion, the provided results are capable to highlight the strong capabilities of the MPM Newmark Predictor-Corrector scheme (NPC).
+In the authors' opinion, the provided results are capable to highlight the capabilities of the LME-MPM-NPC proposed in the present work.
 It is important to remark the extension of this research: in order to isolate the strength of the proposed methodology, covering spatial and time discretization, only linear elastic problems are assessed.

### 2020-11-09 Revisiones/PNA_MMP_Responses to the reviewers.tex
Updates from Overleaf

--- 2020-09-11 Revisiones/PNA_MMP_Responses to the reviewers.tex
@@
 
-\sout{Contrary to the reviewer\textquotesingle s opinion,} In the authors' opinnion, the provided results are capable to highlight the \sout{strong} capabilities of the \acrshort{LME-}MPM-NPC proposed in the present work.
+\sout{Contrary to the reviewer\textquotesingle s opinion,} In the authors' opinion, the provided results are capable to highlight the \sout{strong} capabilities of the \acrshort{LME-}MPM-NPC proposed in the present work.
 It is important to remark the extension of this research: in order to isolate the strength of the proposed methodology, covering spatial and time discretization, only linear elastic problems are assessed.

### 2020-11-09 LME-MPM.tex
Updates from Overleaf
Version para el CMAME

@@
   \resizebox{0.8\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/MPM_scheme_horizontal}
+    \includegraphics[width=\textwidth]{./Figures-MPM-scheme-horizontal}
   }
@@
   \resizebox{0.5\hsize}{!}{
-    \includegraphics[width=\textwidth]{Figures/Continuum-solid}}
+    \includegraphics[width=\textwidth]{Figures-Continuum-solid}}
   \caption{Description of the boundary-value-problem in a
@@
   \resizebox{0.5\hsize}{!}{
-    \includegraphics[width=\textwidth]{Figures/Mesh-particles-back}}
+    \includegraphics[width=\textwidth]{Figures-Mesh-particles-back}}
   \caption{Description of the spatial discretisation for domain presented in the
@@
 \begin{equation}
-  \label{eq:Predictor-velocity-II}
+  \label{eq:Predictor-velocity-III}
   \vec{v}_{I}^{pred} =  \sum_{p\ \in\ \mathcal{C}} \frac{ N_{Ip} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}.
@@
 \textcolor{blue}{Next the \textit{corrector}  step is introduced.
-Predicted nodal velocities obtained in \eqref{eq:Predictor-velocity-II}, are now corrected by the equation}
+Predicted nodal velocities obtained in \eqref{eq:Predictor-velocity-III}, are now corrected by the equation}
 \begin{equation}
@@
 
-This approximation scheme represents an optimal compromise, in the sense of
-Pareto, between the \textit{unbiased statistical inference} based on
+This approximation scheme represents an optimal compromise, in the sense of Pareto, between the \textit{unbiased statistical inference} based on
 the nodal data which leads to the principle of \textit{Maximum-Entropy}
@@
     \begin{tabular}{c}
-      \includegraphics[width=0.14\textwidth]{Figures/MPM_Shape_Fun}\\
-      \includegraphics[width=0.14\textwidth]{Figures/MPM_Shape_Fun_dx}\\
-      \includegraphics[width=0.14\textwidth]{Figures/MPM_Shape_Fun_dy}
+      \includegraphics[width=0.14\textwidth]{Figures-MPM-Shape-Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures-MPM-Shape-Fun-dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures-MPM-Shape-Fun-dy}
     \end{tabular}
@@
     \begin{tabular}{c}      
-      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun}\\
-      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun_dx}\\
-      \includegraphics[width=0.14\textwidth]{Figures/LME_17_3_Shape_Fun_dy}
+      \includegraphics[width=0.14\textwidth]{Figures-LME-17-3-Shape-Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures-LME-17-3-Shape-Fun-dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures-LME-17-3-Shape-Fun-dy}
     \end{tabular}
@@
     \begin{tabular}{c}
-      \includegraphics[width=0.14\textwidth]{Figures/GIMP_Shape_Fun}\\
-      \includegraphics[width=0.14\textwidth]{Figures/GIMP_Shape_Fun_dx}\\
-      \includegraphics[width=0.14\textwidth]{Figures/GIMP_Shape_Fun_dy}
+      \includegraphics[width=0.14\textwidth]{Figures-GIMP-Shape-Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures-GIMP-Shape-Fun-dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures-GIMP-Shape-Fun-dy}
     \end{tabular}
@@
   \subfigure[$\text{LME}_{10}$]{
-    \begin{tabular}{c} \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun}\\ \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun_dx}\\      \includegraphics[width=0.14\textwidth]{Figures/LME_10_0_Shape_Fun_dy}
+    \begin{tabular}{c}
+     \includegraphics[width=0.14\textwidth]{Figures-LME-10-0-Shape-Fun}\\ 		   \includegraphics[width=0.14\textwidth]{Figures-LME-10-0-Shape-Fun-dx}\\      \includegraphics[width=0.14\textwidth]{Figures-LME-10-0-Shape-Fun-dy}
     \end{tabular}
@@
     \begin{tabular}{c}
-      \includegraphics[width=0.14\textwidth]{Figures/LME_5_0_Shape_Fun}\\
-      \includegraphics[width=0.14\textwidth]{Figures/LME_5_0_Shape_Fun_dx}\\
-      \includegraphics[width=0.14\textwidth]{Figures/LME_5_0_Shape_Fun_dy}
+      \includegraphics[width=0.14\textwidth]{Figures-LME-5-0-Shape-Fun}\\
+      \includegraphics[width=0.14\textwidth]{Figures-LME-5-0-Shape-Fun-dx}\\
+      \includegraphics[width=0.14\textwidth]{Figures-LME-5-0-Shape-Fun-dy}
     \end{tabular}
@@
   \resizebox{\hsize}{!}{
-    \input{Figures/Dyka_bar.tex}}
+    \input{Figures-Dyka-bar.tex}}
   \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
@@
   \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Error_evol}
+    \includegraphics[width=\textwidth]{./Figures-Error-evol}
   }
@@
   \resizebox{0.9\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_01}
+    \includegraphics[width=\textwidth]{./Figures-Velocity-FE-vs-PCE-CFL-01}
   }
@@
   \resizebox{0.9\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_LME_gamma_comparative}
+    \includegraphics[width=\textwidth]{./Figures-Velocity-LME-gamma-comparative}
   }
@@
   \resizebox{0.9\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_uGIMP_vs_LME_Dyka}
+    \includegraphics[width=\textwidth]{./Figures-Velocity-uGIMP-vs-LME-Dyka}
   }
@@
   \resizebox{0.9\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
+    \includegraphics[width=\textwidth]{./Figures-Velocity-MPM-vs-OTM-Dyka}
   }
@@
   \resizebox{0.7\hsize}{!}{
-    \input{Figures/Block.tex}}
+    \input{Figures-Block.tex}}
   \caption{Geometrical description of a soil block }.
@@
   \subfigure[t = 0 seconds.]{
-    \includegraphics[width=0.3\textwidth]{Figures/Block_LME3_PCE_a_t0}
+    \includegraphics[width=0.3\textwidth]{Figures-Block-LME3-PCE-a-t0}
   }
   \subfigure[t = 5 seconds.]{
-    \includegraphics[width=0.3\textwidth]{Figures/Block_LME3_PCE_b_t025}
+    \includegraphics[width=0.3\textwidth]{Figures-Block-LME3-PCE-b-t025}
   }
   \subfigure[t = 20 seconds]{
-    \includegraphics[width=0.3\textwidth]{Figures/Block_LME3_PCE_c_t1}
+    \includegraphics[width=0.3\textwidth]{Figures-Block-LME3-PCE-c-t1}
   }
@@
   \resizebox{\hsize}{!}{
-    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
+    \includegraphics[width=\textwidth]{./Figures-Block-CFL-01-Comparative}
   }
@@
   \resizebox{\hsize}{!}{
-\includegraphics[scale=1]{Figures/Velocity_FE_vs_NPC_square.png} 
+\includegraphics[scale=1]{Figures-Velocity-FE-vs-NPC-square.png} 
   }
@@
   \resizebox{\hsize}{!}{
-\includegraphics[scale=0.8]{Figures/Velocity-structured-unstructured-lme-ugimp.png}
+\includegraphics[scale=0.8]{Figures-Velocity-structured-unstructured-lme-ugimp.png}
   }
@@
 % name your BibTeX data base
-\bibliography{Biblio/Biblio}
+\bibliography{Biblio}
 \end{document}

### 2020-11-09 Figures/Dyka_Analytical.py

@@ -1,361 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from mpl_toolkits.mplot3d import Axes3D
-from matplotlib import cm
-from matplotlib.ticker import LinearLocator
-from matplotlib.ticker import FixedLocator
-from matplotlib.ticker import FormatStrFormatter
-
-
-def find_nearest(array, value):
-    array = np.asarray(array)
-    idx = (np.abs(array - value)).argmin()
-    return idx
-
-def Get_Riemann_I(Stress_I,Velocity_I):
-    R_I = (0.5/StaticVisco)*(- Stress_I + Velocity_I*StaticVisco)
-    return R_I
-
-def Get_Riemann_II(Stress_II,Velocity_II):
-    R_II = (0.5/StaticVisco)*(Stress_II + Velocity_II*StaticVisco)
-    return R_II
-
-# Material properties
-L = 0.1333
-E = 200*10**9 # Pa
-rho = 7833 # kg/m³
-CEL = 5033 # m/s , np.sqrt(E/rho)
-# L = 1
-# E = 1 # Pa
-# rho = 1 # kg/m³
-# CEL = 1 # m/s
-
-T_go = L/CEL #
-T_end = 16*T_go
-
-# Spatial mesh
-# dx = 0.000001
-dx = 0.001
-
-# Time mesh
-dt =  0.000001
-# dt =  0.1
-
-# Discretize domain
-N_x = int(L/dx)
-X = np.linspace(0,L,N_x)
-# Discretize time
-N_t = int(T_end/dt)
-T = np.linspace(0,T_end,N_t)
-
-# Initial conditions
-v0 = -5
-# v0 = -1
-Stress = np.zeros([N_t,N_x])
-Velocity = np.zeros([N_t,N_x])
-for x in range(0,N_x):
-    if X[x] <= 0.25*L :
-        Velocity[0,x] = v0
-    else :
-        Velocity[0,x] = 0
-
-        
-# Get the static viscosity
-StaticVisco = np.sqrt(E*rho)
-
-        
-# figures
-Show_grafs = True
-format_fig = 'png'
-        
-################################################################
-####################### Loop in time ###########################
-################################################################
-for t in range(0,N_t):
-    
-    ############################################################    
-    ##################### Solve domain #########################
-    ############################################################
-    for x in range(1,N_x-1):
-
-        # Get boundary values through characteristics lines
-        t_I = T[t] - X[x]/CEL
[…]

### 2020-11-09 Figures/Scene_Na.py

@@ -1,264 +1,0 @@
-# Recorded script from Mayavi2
-from numpy import array
-try:
-    engine = mayavi.engine
-except NameError:
-    from mayavi.api import Engine
-    engine = Engine()
-    engine.start()
-if len(engine.scenes) == 0:
-    engine.new_scene()
-# ------------------------------------------- 
-from mayavi.modules.outline import Outline
-outline = Outline()
-module_manager = engine.scenes[0].children[0].children[0].children[0]
-engine.add_filter(outline, module_manager)
-# outline.outline_filter.input_connection = <tvtk.tvtk_classes.algorithm_output.AlgorithmOutput object at 0x7f82116ed770>
-outline.manual_bounds = True
-outline.bounds = array([-1.9,  1. , -1. ,  1. , -1. ,  1. ])
-outline.bounds = array([-1.9,  1. , -1. ,  1. , -1. ,  1. ])
-outline.bounds = array([-1.9,  1.9, -1. ,  1. , -1. ,  1. ])
-outline.bounds = array([-1.9,  1.9, -1. ,  1. , -1. ,  1. ])
-outline.bounds = array([-1.9,  1.9, -1.9,  1. , -1. ,  1. ])
-outline.bounds = array([-1.9,  1.9, -1.9,  1. , -1. ,  1. ])
-outline.bounds = array([-1.9,  1.9, -1.9,  1.9, -1. ,  1. ])
-outline.bounds = array([-1.9,  1.9, -1.9,  1.9, -1. ,  1. ])
-outline.bounds = array([-1.9,  1.9, -1.9,  1.9,  0. ,  1. ])
-outline.bounds = array([-1.9,  1.9, -1.9,  1.9,  0. ,  1. ])
-outline.bounds = array([-1.9,  1.9, -1.9,  1.9,  0. ,  4. ])
-outline.bounds = array([-1.9,  1.9, -1.9,  1.9,  0. ,  4. ])
-scene = engine.scenes[0]
-scene.scene.camera.position = [7.734688192344844, 7.734688192344844, 8.19470485206996]
-scene.scene.camera.focal_point = [0.0, 0.0, 0.4600166597251145]
-scene.scene.camera.view_angle = 30.0
-scene.scene.camera.view_up = [0.0, 0.0, 1.0]
-scene.scene.camera.clipping_range = [5.48912328832708, 21.372954126716014]
-scene.scene.camera.compute_view_plane_normal()
-scene.scene.render()
[…]

### 2020-11-09 Figures/Scene_dxNa.py

@@ -1,250 +1,0 @@
-# Recorded script from Mayavi2
-from numpy import array
-try:
-    engine = mayavi.engine
-except NameError:
-    from mayavi.api import Engine
-    engine = Engine()
-    engine.start()
-if len(engine.scenes) == 0:
-    engine.new_scene()
-# ------------------------------------------- 
-scene = engine.scenes[0]
-scene.scene.camera.position = [12.405354476130022, 12.405354476130022, 12.405354476130022]
-scene.scene.camera.focal_point = [0.0, 0.0, 0.0]
-scene.scene.camera.view_angle = 30.0
-scene.scene.camera.view_up = [0.0, 0.0, 1.0]
-scene.scene.camera.clipping_range = [15.574096976424016, 28.98128583252587]
-scene.scene.camera.compute_view_plane_normal()
-scene.scene.render()
-scene.scene.camera.position = [10.252359071181836, 10.252359071181836, 10.252359071181836]
-scene.scene.camera.focal_point = [0.0, 0.0, 0.0]
-scene.scene.camera.view_angle = 30.0
-scene.scene.camera.view_up = [0.0, 0.0, 1.0]
-scene.scene.camera.clipping_range = [11.88229052088975, 25.19625194124579]
-scene.scene.camera.compute_view_plane_normal()
-scene.scene.render()
-scene.scene.camera.position = [9.945049557847135, 11.27617527668267, 9.448622121496244]
-scene.scene.camera.focal_point = [0.0, 0.0, 0.0]
-scene.scene.camera.view_angle = 30.0
-scene.scene.camera.view_up = [-0.3759940360636462, -0.37748496147533483, 0.8462467658458346]
-scene.scene.camera.clipping_range = [11.808094532000167, 25.289649404646994]
-scene.scene.camera.compute_view_plane_normal()
-scene.scene.render()
-scene.scene.camera.position = [8.219049221361265, 9.319153121225344, 7.808778612806812]
-scene.scene.camera.focal_point = [0.0, 0.0, 0.0]
-scene.scene.camera.view_angle = 30.0
-scene.scene.camera.view_up = [-0.3759940360636462, -0.37748496147533483, 0.8462467658458346]
-scene.scene.camera.clipping_range = [8.757014816682595, 22.161522221770895]
-scene.scene.camera.compute_view_plane_normal()
-scene.scene.render()
-scene.scene.camera.position = [6.792602662282036, 7.701779439029209, 6.453536043641991]
[…]

### 2020-11-09 Figures/Scene_dxNa_LME.py

@@ -1,92 +1,0 @@
-# Recorded script from Mayavi2
-from numpy import array
-try:
-    engine = mayavi.engine
-except NameError:
-    from mayavi.api import Engine
-    engine = Engine()
-    engine.start()
-if len(engine.scenes) == 0:
-    engine.new_scene()
-# ------------------------------------------- 
-module_manager = engine.scenes[0].children[0].children[0].children[0]
-module_manager.scalar_lut_manager.lut_mode = 'jet'
-module_manager.vector_lut_manager.lut_mode = 'jet'
-scene = engine.scenes[0]
-scene.scene.background = (1.0, 1.0, 1.0)
-module_manager.scalar_lut_manager.title_text_property.shadow_offset = array([ 1, -1])
-module_manager.scalar_lut_manager.title_text_property.shadow_offset = array([ 1, -1])
-module_manager.scalar_lut_manager.title_text_property.color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
-module_manager.scalar_lut_manager.label_text_property.shadow_offset = array([ 1, -1])
-module_manager.scalar_lut_manager.label_text_property.shadow_offset = array([ 1, -1])
-module_manager.scalar_lut_manager.label_text_property.color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
-module_manager.vector_lut_manager.title_text_property.shadow_offset = array([ 1, -1])
-module_manager.vector_lut_manager.title_text_property.shadow_offset = array([ 1, -1])
-module_manager.vector_lut_manager.title_text_property.color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
-module_manager.vector_lut_manager.label_text_property.shadow_offset = array([ 1, -1])
-module_manager.vector_lut_manager.label_text_property.shadow_offset = array([ 1, -1])
-module_manager.vector_lut_manager.label_text_property.color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
-surface = engine.scenes[0].children[0].children[0].children[0].children[0]
-surface.actor.property.ambient_color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
-surface.actor.property.color = (0.5254901960784314, 0.5254901960784314, 0.5254901960784314)
[…]

### 2020-11-09 Figures/Shape_Fun_GIMP.py

@@ -1,105 +1,0 @@
-#!/opt/anaconda3/bin/python3
-
-from mayavi import mlab
-import numpy as np
-
-def GIMP(L, lp, Xp, Xi):
-    """"""
-    if (np.abs(Xp-Xi) >= L+lp):
-        Sip = 0
-    elif (-L-lp < Xp-Xi <= -L+lp):
-        Sip = (1/(4*L*lp))*(L+lp+Xp-Xi)**2
-    elif (-L+lp < Xp-Xi <= -lp):
-        Sip = 1 + (Xp-Xi)/(L)
-    elif (-lp < Xp-Xi <= lp):
-        Sip = 1 - ((Xp - Xi)**2 + (lp)**2)/(2*L*lp)
-    elif (lp < Xp-Xi <= L-lp):
-        Sip = 1 - (Xp-Xi)/(L)
-    elif (L-lp < Xp-Xi <= L+lp):
-        Sip = (1/(4*L*lp))*(L+lp-Xp+Xi)**2
-    return Sip
-
-def d_GIMP(L, lp, Xp, Xi):
-    """"""
-    if (np.abs(Xp-Xi) >= L+lp):
-        d_Sip = 0
-    elif (-L-lp < Xp-Xi <= -L+lp):
-        d_Sip = (1/(2*L*lp))*(L+lp+Xp-Xi)
-    elif (-L+lp < Xp-Xi <= -lp):
-        d_Sip = 1/L
-    elif (-lp < Xp-Xi <= lp):
-        d_Sip = -(Xp - Xi)/(L*lp)
-    elif (lp < Xp-Xi <= L-lp):
-        d_Sip = -1/L
-    elif (L-lp < Xp-Xi <= L+lp):
-        d_Sip = -(1/(2*L*lp))*(L+lp-Xp+Xi)
-    return d_Sip
-
-
-def print_dx_GIMP(Show_grafs):
-    N = 50
-    xp = yp = np.linspace(-2, 2, N)
-    Xp, Yp = np.meshgrid(xp, yp, indexing='ij', sparse=False)
-    Sip_dxdy = np.zeros([N,N])
-    xi = yi = 0
-    L = 1.
-    lp = 1/4.
-
-    format_fig = 'png'
-
-    for i in range(0,N):
-        for j in range(0,N):
-            Sip_dxdy[i][j] = d_GIMP(L,lp,xp[i],xi) * GIMP(L,lp,yp[j],yi) 
[…]

### 2020-11-09 Figures/Shape_Fun_LME.py

@@ -1,305 +1,0 @@
-#!/home/migmolper2/anaconda3/bin/python3
-
-from mayavi import mlab
-import numpy as np
-
-"""
-  Shape functions based in :
-  " Local maximum-entropy approximation schemes : a seamless 
-  bridge between finite elements and meshfree methods "
-  by M.Arroyo and M.Ortiz, 2006.
-
-  Here we employ the same nomenclature as in the paper. With the single
-  different of the "l" variable wich represents the distances between the
-  evaluation point and the neighborhood nodes.
-
-  List of functions :
-  - LME_lambda_NR
-  - LME_fa
-  - LME_p
-  - LME_r
-  - LME_J
-  - LME_dp
-"""
-
-def LME_fa(l_a, lambda_a, Beta_a):
-    """
-    """
-    return - Beta_a * np.dot(l_a, l_a) + np.dot(l_a,lambda_a)
-
-def LME_p(l, lambda_a, Beta_a):
-    """
-    Get the value of the shape function "pa" (1 x neighborhood) in the
-    neighborhood nodes.
-    
-    Input parameters :
-    -> l : Matrix with the distances to the
-    neighborhood nodes (neiborghood x dim).
-    -> lambda : Initial value of the lagrange multipliers (1 x dim).
-    -> Beta : Tunning parameter (scalar).
-    """
-    
-    # Definition of some parameters
-    N_a = np.shape(l)[0]
-    N_dim = 2
-    Z = 0.0
-    Z_m1 = 0.0
-
-    # Vector with the values of the shape-function in the nodes
-    p = np.zeros([N_a])
-
-    # Get Z and the numerator
-    for a in range(0,N_a):
-        la = l[a,:]
-        p[a] = np.exp(LME_fa(la,lambda_a,Beta_a))
-        Z += p[a]
-
-    # Get the inverse of Z
-    Z_m1 = 1/Z
-
-    # Divide by Z and get the final value
-    for a in range(0,N_a):
-        p[a] *= Z_m1
-      
-    # Return the value of the shape function
-    return p
-
-
-def LME_r(l,p):
-    """
-    Get the gradient "r" (dim x 1) of the function log(Z) = 0.
-    Input parameters :
-    -> l : Matrix with the distances to the 
-    neighborhood nodes (neighborhood x dim).
[…]

### 2020-11-09 Figures/Shape_Fun_MPM.py

@@ -1,94 +1,0 @@
-#!/opt/anaconda3/bin/python3
-
-from mayavi import mlab
-import numpy as np
-
-def MPM(L, Xp, Xi):
-    """"""
-    if (np.abs(Xp-Xi) >= L):
-        Sip = 0
-    elif (-L <= Xp-Xi <= 0):
-        Sip = 1-np.abs(Xp-Xi)/L
-    elif (L >= Xp-Xi >=0):
-        Sip = 1-np.abs(Xp-Xi)/L
-    return Sip
-
-def d_MPM(L, Xp, Xi):
-    """"""
-    if (np.abs(Xp-Xi) >= L):
-        Sip = 0
-    elif (-L <= Xp-Xi <= 0):
-        Sip = 1/L
-    elif (L >= Xp-Xi >=0):
-        Sip = -1/L
-    return Sip
-
-def print_dx_MPM(Show_grafs):
-    N = 50
-    xp = yp = np.linspace(-2, 2, N)
-    Xp, Yp = np.meshgrid(xp, yp, indexing='ij', sparse=False)
-    Sip_dxdy = np.zeros([N,N])
-    xi = yi = 0
-    L = 1.
-    format_fig = 'png'
-
-    for i in range(0,N):
-        for j in range(0,N):
-            Sip_dxdy[i][j] = d_MPM(L,xp[i],xi) * MPM(L,yp[j],yi)
-           
-           
-    surf = mlab.mesh(Xp, Yp, Sip_dxdy)
-    
-    if Show_grafs:
-        mlab.axes(surf)
-        mlab.outline(surf)
-        mlab.show(surf)
-
-def print_dy_MPM(Show_grafs):
-    N = 50
-    xp = yp = np.linspace(-2, 2, N)
-    Xp, Yp = np.meshgrid(xp, yp, indexing='ij', sparse=False)
-    Sip_dxdy = np.zeros([N,N])
-    xi = yi = 0
-    L = 1.
-    lp = 1/4.
-    format_fig = 'png'
-
-    for i in range(0,N):
-        for j in range(0,N):
-            Sip_dxdy[i][j] = MPM(L,xp[i],xi) * d_MPM(L,yp[j],yi) 
-            
-
-    surf = mlab.mesh(Xp, Yp, Sip_dxdy)
-    # surf.actor.actor.scale = (0.25, 0.25, 1.0)
-    
-    if Show_grafs:
-        mlab.axes(surf)
-        mlab.outline(surf)
[…]

### 2020-11-09 Figures/Timoshenko_Analytical.py

@@ -1,36 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-L = 8
-c = 0.5
-D= 2*c
-# c = np.sqrt(3)/2
-nu = 0.3
-E = 3E5
-P = 100
-I = (1/12)*(2*c)**3
-
-DeltaX = 0.1
-Nx = int(L/DeltaX)
-Ny = int(2*c/DeltaX)
-x0 = np.linspace(0,L,Nx)
-y0 = np.linspace(-c,c,Ny)
-X0, Y0 = np.meshgrid(x0, y0, indexing='ij', sparse=False)
-
-Xf = np.zeros([Nx,Ny])
-Yf = np.zeros([Nx,Ny])
-
-for i in range(0,Nx):
-    for j in range(0,Ny):
-
-        Xf[i][j] = X0[i][j] + P*Y0[i][j]/(6*E*I)*((6*L-3*X0[i][j])*X0[i][j] + (2+nu)*(Y0[i][j]**2 - (D**2)/4 ))
-        Yf[i][j] = Y0[i][j] - P/(6*E*I)*(3*nu*Y0[i][j]**2*(L-X0[i][j]) + (4+5*nu)*X0[i][j]*(D**2)/4 + (3*L-X0[i][j])*X0[i][j]**2)
-
-
-fig, ax = plt.subplots()
-# ax.scatter(X0,Y0)
-ax.scatter(Xf,Yf)
-ax.axis('equal')
-fig.tight_layout()
-plt.grid()
-plt.show()

### 2020-11-25 LME-MPM.tex
Nuevos highlights

@@
 \usepackage[acronym]{glossaries}
-
 \makeglossaries
@@
 \begin{itemize}
-\item A new accurate and efficient time integration scheme for the \acrshort{mpm} is proposed.
-\item The \acrfull{lme} approximation technique is a robust substitute of the traditional shape functions within the \acrshort{mpm} framework .
-\item The proposed approach might improve large strain fast dynamic \acrshort{mpm} simulations as grid-crossing pathology are clearly mitigated.  
+\item An efficient time integration scheme for the \acrshort{mpm} is proposed.
+\item The Local Maximum-Entropy approximants as an alternative of the standard \acrshort{mpm} shape functions.
+\item This approach might improve large strain fast dynamic MPM simulations. 
 \end{itemize}
@@
 
-\subsubsection{Sensitive analysis to $\widehat{\gamma}$ parameter}
+\subsubsection{Sensitive analysis to \texorpdfstring{$\widehat{\gamma}$}{gamma}  parameter}
 \label{sec:Sensitive-analysis-gamma}
